% Santo Daime: Preces
% ===================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

% use Roman numerals for song (prayer) numbering:
\renewcommand{\thesongnum}{\Roman{songnum}}
% no chords here, so line spacing will be less:
\chordsoff
% separate verses (translations of the prayers) more:
%\versesep 30pt plus 0pt minus 8pt

% Use this to specify a translation title within a verse, eg
% \translationtitle{EN}{Greed}
\newcommand{\translationtitle}[2]{
  \vspace{3ex}\textbf{[#1]} \textit{#2}\vspace{1.618034ex}
}
% Use this to create a vertical space between "paragraphs"
%within verses:
\newcommand{\parspace}{\vspace{1ex}}

% Setup the color for note mark superscripts to be the same as chords'
% color:
\definecolor{notemarkcolor}{rgb}{0,0,0}%
\colorlet{notemarkcolor}{chordcolor}%

% Redefine \up macro to use notemarkcolor
\renewcommand{\up}[1]{
  \textsuperscript{\color{notemarkcolor}#1}%
}

% Environment for a multiline note to be used within a song environment:
\newenvironment{note}{%
  \yesendsongvfill%
  \vfill%
  \beginverse*%
  \small%
  \begin{itshape}%
}{%
  \end{itshape}%
  \endverse%
}


\beginsong{Sinal da Cruz}
  \beginverse
    \up{1}Pelo sinal da Santa Cruz,
    \up{2}livrai-nos, Deus, nosso Senhor,
    \up{3}dos nossos inimigos
    \parspace
    \up{4}Em nome do Pai,
    \up{5}do Filho e
    \up{6}do Espírito \up{7}Santo.
    \parspace
    Amém.
  \endverse
  \beginverse
    \translationtitle{EN}{Sign of the Cross}
    \up{1}By the sign of the Holy Cross,
    \up{2}deliver us, God, our Lord,
    \up{3}from our enemies
    \parspace
    \up{4}In the name of the Father,
    \up{5}the Son, and
    \up{6}the Holy \up{7}Spirit.
    \parspace
    Amen.
  \endverse
  \begin{note}
    While speaking the prayer, synchronously make
    the sign of the Cross with with your right thumb
    on your \up{1}forehead,
    on your \up{2}mouth, and
    on your \up{3}chest.
    \parspace
    Then, with your right hand, touch
    your \up{4}forehead,
    your \up{5}chest,
    your \up{6}left shoulder and \up{7}right shoulder.
  \end{note}
\endsong


\beginsong{Credo}
  \beginverse
    Creio em Deus Pai todo Poderoso,
    Criador do Céu e da terra.
    \parspace
    Creio em Jesus Cristo, um só seu filho, Nosso
    Senhor, o qual for concebido por obra e graça do
    Espírito Santo. Nasceu da Maria Virgem;
    padeceu sob o poder de Pôncio Pilatos;
    foi crucificado, morto e sepultado. Desceu aos
    infernos, ao terceiro dia ressurgiu dos mortos,
    Subiu ao Céu e Pai Todo-poderoso, de onde há de vir
    a julgar os vivos e os mortos.
    \parspace
    Creio no Espirito Santo, na Santa Igreja,
    na comunhão dos Santos, na remissão
    dos pecados, na ressurreição da carne,
    na vida eterna.
    \parspace
    Amém.
  \endverse
  \beginverse
    \translationtitle{EN}{Creed}
    I believe in God, the Father Almighty,
    Creator of Heaven and earth.
    \parspace
    I believe in Jesus Christ, His only Son, Our Lord,
    who was conceived through the work and grace of
    the Holy Spirit. He was born of the Virgin Mary;
    suffered under the power of Pontius Pilate;
    was crucified, died, and was buried. He decended
    into Hell; on the third day he rose again from
    the dead. He ascended into Heaven and is seated
    at the right hand of God, the Father Almighty, from
    where He come to judge the living and the dead.
    \parspace
    I believe in the Holy Spirit, the Holy Church,
    the communion of Saints, the forgiveness of sins,
    the resurrection of the body, and life everlasting.
    \parspace
    Amen.
  \endverse
%% Skip the Finnish version for now, to save space
%   \beginverse
%     \translationtitle{FI}{Uskontunnustus}
%     Minä uskon Jumalaan, Isään, Kaikkivaltiaaseen,
%     taivaan ja maan Luojaan;
%     \parspace
%     ja Jeesukseen Kristukseen, Jumalan ainoaan Poikaan,
%     meidän Herraamme, joka sikisi Pyhästä Hengestä,
%     syntyi neitsyt Mariasta, kärsi Pontius Pilatuksen
%     aikana, ristiinnaulittiin, kuoli ja haudattiin,
%     astui alas tuonelaan, nousi kolmantena päivänä
%     kuolleista, astui ylös taivaisiin, istuu Jumalan,
%     Isän, Kaikkivaltiaan, oikealla puolella ja on sieltä
%     tuleva tuomitsemaan eläviä ja kuolleita;
%     \parspace
%     ja Pyhään Henkeen, pyhän yhteisen seurakunnan,
%     pyhäin yhteyden, syntien anteeksiantamisen,
%     ruumiin ylösnousemisen ja iankaikkisen elämän.
%     \parspace
%     Aamen.
%   \endverse
\endsong


\beginsong{Rosario I (trabalho officiais)}
  \beginverse
    \textnote{Ao rezar o terço, só diz a cada dezena:}
    \parspace
    Gloria ao Pai, ao Filho, ao Espírito Santo.
    Assim como era no princípio, agora e sempre,
    por todos os séculos dos séculos.
    \parspace
    Amém.
  \endverse
  \beginverse
    \translationtitle{EN}{The Rosary I (official work)}
    \textnote{While praying the Rosary, after every decade:}
    \parspace
    Glory to the Father, to the Son and to the Holy Spirit.
    As it was in the beginning, is now, and ever shall be,
    for all the ages of the ages.
    \parspace
    Amen.
  \endverse
\endsong


\beginsong{Rosario II (Santa Missa)}
  \beginverse
    \textnote{Ao rezar o terço, só diz a cada dezena:}
    \parspace
    Gloria ao Pai, ao Filho, ao Espírito Santo.
    Assim como era no princípio, agora e sempre,
    por todos os séculos dos séculos.
    \parspace
    Amém.
    \parspace\parspace
    Oh! meu Jesus, perdoai-me, livrai-me do fogo do
    inferno. Levai as almas todas para o Céu, e soccorei
    principalmente aquelas que mais precísarem.
    \parspace
    Amém.
  \endverse
  \beginverse
    \translationtitle{EN}{The Rosary II (Santa Missa)}
    \textnote{While praying the Rosary, after every decade:}
    \parspace
    Glory to the Father, to the Son and to the Holy Spirit.
    As it was in the beginning, is now, and ever shall be,
    for all the ages of the ages.
    \parspace
    Amen.
    \parspace\parspace
    Oh my Jesus, forgive me, and save me from the fires
    of hell. Lead all souls into heaven, and especially
    help those in most need.
    \parspace
    Amen.
  \endverse
\endsong


\beginsong{Pai nosso}
  \beginverse
    Pai nosso,
    que estais no Céu,
    santificado seja o Vosso Nome.
    Vamos nós ao Vosso Reino.
    Seja feita a Vossa Vontade,
    assim na terra como no Céu.
    O pão nosso de cada dia nos daí hoje, Senhor.
    Perdoai as nossas dividas,
    assim como nós perdoamos os nossos devedores.
    Não nos deixas, Senhor, cair em tentação,
    mas livrai-me e defendei-me, Senhor,
    de todo mal.
    \parspace
    Amém, Jesus, Maria, José.
  \endverse
  \beginverse
    \translationtitle{EN}{Our Father}
    Our Father,
    who art in Heaven,
    hallowed be Thy Name.
    Let us go into Thy Kingdom.
    Thy Will be done,
    on earth as it is in Heaven.
    Give us this day our daily bread, Lord.
    Forgive us our debts,
    as we forgive our debtors.
    Let us not fall in temptation,
    but deliver me and defend me, Lord,
    from all evil.
    \parspace
    Amen, Jesus, Mary, Joseph.
  \endverse
\endsong


\beginsong{Ave Maria}
  \beginverse
    Ave Maria,
    cheia de Graça!
    O Senhor é convosco.
    Bendita sois Vós entre as mulheres.
    Bendito é o fruto do Vosso ventre, Jesus.
    Santa Maria, Mãe de Deus,
    rogai a Deus por nos pecadores,
    agora e na hora de nossa morte.
    \parspace
    Amém, Jesus, Maria, José.
  \endverse
  \beginverse
    \translationtitle{EN}{Hail Mary}
    Hail Mary,
    full of grace!
    The Lord is with Thee.
    Blessed art Thou amongst women!
    Blessed is the fruit of Thy womb, Jesus.
    Holy Mary, Mother of God,
    pray to God for us sinners,
    now and at the hour of our death.
    \parspace
    Amen, Jesus, Mary, Joseph.
  \endverse
\endsong


\beginsong{Chave de Harmonia}
  \beginverse
    Desejo Harmonia, Amor, Verdade e Justiça a todos os
    meus irmãos. Com as forças reunidas das silenciosas
    vibrações dos nossos pensamentos, somos fortes,
    sádios e felizes, formando assim um elo de
    fraternidade universal. Estou satisfeito e em paz
    com o universo inteiro e desejo que todos os seres
    realizam as suas aspirações mais íntímas. Dou graças
    ao Pai Invisivel por ter estabelecido a Harmonia,
    o Amor, a Verdade e a Justiça entre todos os seus
    filhos.
    \parspace
    Assim seja, Amém.
  \endverse
  \beginverse
    \translationtitle{EN}{Key of Harmony}
    I wish Harmony, Love, Truth and Justice to all my
    brothers and sisters. With the united forces of the
    silent vibrations of our thoughts, we are strong,
    healthy and happy, thus forming a link of universal
    fraternity. I am satisfied and in peace with the
    whole universe, and I wish that all beings achieve
    their most intimate aspirations. I give thanks to
    my Invisible Father for having established Harmony,
    Love, Truth and Justice among all his children.
    \parspace
    So be it, Amen.
  \endverse
\endsong


\beginsong{Consagração do Aposento}
  \beginverse
    Dentro do Circulo Infinito da Divina Presença que
    me envolve inteiramente, afirmo:
    \parspace
    Há uma só presença aqui --- é a da HARMONIA que faz
    vibrar todos os corações de felicidade e alegria.
    Quem quer que aqui entre, sentirá as vibrações da
    Divina Harmonia.
    \parspace
    Há uma só presença aqui --- e a do AMOR. Deus é o
    Amor que envolve todos os seres num só sentimento
    de unidade. Este recinto está cheio da presença do
    Amor. No Amor eu vivo, me movo e existo. Quem quer
    que aqui entre, sentirá a pura e Santa Presença do
    Amor.
    \parspace
    Há uma só presença aqui --- é a da VERDADE. Tudo
    que aqui existe, tudo o que aqui se fala, tudo o
    que aqui se pensa é a expressão da Verdade. Quem
    quer que aqui entre, sentirá a Presença da Verdade.
    \parspace
    Há uma só presença aqui --- é a da JUSTIÇA.
    A Justiça reina neste recinto. Todos os atos aqui
    praticados são regidos e inspirados pela Justiça.
    Quem quer que aqui entre, sentirá
    a Presença da Justiça.
    \parspace
    Há uma só presença aqui --- é a presença de Deus,
    o BEM. Nenhum mal pode entrar aqui. Não há mal em
    Deus. Deus, o Bem, reside aqui. Quem quer que aqui
    entre, sentirá a Presença Divina do Bem.
    \parspace
    Há uma só presença aqui --- e a presença de Deus,
    a VIDA. Deus é a Vida essencial de todos os seres.
    É a saúde do corpo e da mente. Quem quer que aqui
    entre, sentirá a Divina Presença da Vida e da Saúde.
    \parspace
    Há uma só presença aqui --- é a presença de Deus,
    a PROSPERIDADE. Deus é Prosperidade, pois Ele faz
    tudo crescer e prosperar. Deus se expressa na
    Prosperidade de tudo o que aqui é empreendido em
    seu nome. Quem quer que aqui entre, sentirá
    a Divina Presença da Prosperidade e da Abundância.
    \parspace
    Pelo símbolo esotérico das Asas Divinas, estou
    em vibração harmoniosa com as correntes universais
    da Sabedoria, do Poder e da Alegria. A Presença
    da Divina Sabedoria manifesta-se aqui. A presença
    da Alegria Divina é profundamente sentida por todos
    os que aqui entram.
    \parspace
    Na mais perfeita comunhão entre o meu eu inferior
    e o meu Eu Superior, que é Deus em mim, consagro
    este recinto à perfeita expressão de todas as
    qualidades divinas que há em mim, e em todos os
    seres.
    \parspace
    As vibrações do meu pensamento são forças de Deus
    em mim, que aqui ficam armazenadas e daqui se
    irradiam para todos os seres, constituindo este
    lugar um centro de emissão e recepção de tudo
    quanto é Bom, Alegre, e Próspero.
    \parspace
    \textbf{ORAÇÃO}
    \parspace
    Agradeço-te o Deus, porque este recinto está cheio
    da Tua Presença.
    \parspace
    Agradeço-te, porque vivo e me movo por Ti.
    \parspace
    Agradeço-te, porque vivo em tua Vida, Verdade e
    Saúde, Prosperidade, Paz, Sabedoria, Alegria e Amor.
    \parspace
    Agradeço-te, porque todos que entrarem aqui sentirão
    Tua Presença.
    \parspace
    Agradeço-te, porque estou em Harmonia, Amor, Verdade
    e Justiça com todos os seres.
    \parspace
    Amém.
  \endverse
  \brk
  \beginverse
    \translationtitle{EN}{Consecration of the Space}
    In the Infinite Circle of the Divine Presence which
    completely envelopes me, I affirm that:
    \parspace
    There is only one presence here --- it is HARMONY,
    which makes all hearts vibrate with happiness and
    joy. Whoever enters here will feel the vibration
    of Divine Harmony.
    \parspace
    There is only one presence here --- it is LOVE.
    God is love, which envelops all beings in a single
    feeling of unity. This space is filled with the
    presence of love. In Love, I live, I move and I
    exist. Whoever enters here will feel the pure and
    holy Presence of Love.
    \parspace
    There is only one presence here --- it is TRUTH.
    All that exists here, all that is spoken here,
    all that is thought here is the expression of
    Truth. Whoever enters here will feel the Presence
    of Truth.
    \parspace
    There is only one presence here --- it is JUSTICE.
    Justice reigns in this space. Every act practiced
    here is ruled and inspired by Justice. Whoever
    enters here will feel the Presence of Justice.
    \parspace
    There is only one presence here --- it is the
    presence of God, who is GOODNESS. No evil can enter
    here. There is no evil in God. God, who is Goodness,
    dwells here. Whoever enters here will feel the
    Divine Presence of Goodness.
    \parspace
    There is only one presence here --- it is the
    presence of God, who is LIFE. God is the essential
    Life of all beings. He is the health of body and
    mind. Whoever enters here will feel the Divine
    Presence of life and Health.
    \parspace
    There is only one presence here --- it is the
    presence of God, who is PROSPERITY. God is
    Prosperity because He makes everything grow and
    prosper. God expresses Himself through the
    Prosperity of all that is carried out in His name.
    Whoever enters here will feel the Divine Presence
    of Prosperity and Abundance.
    \parspace
    Through the esoteric symbol of the Divine Wings,
    I am in harmonious vibration with the universal
    currents of Wisdom, Power and Joy. The Presence
    of Divine Wisdom is manifested here. The Presence
    of Divine Joy is deeply felt by all those who enter
    here.
    \parspace
    In the perfect communion between my lower self and
    my Higher Self, which is God in me, I consecrate
    this space to the perfect expression of all divine
    qualities which are in me and in all beings.
    \parspace
    The vibrations of my thoughts are the forces of God
    in me, which are stored here and hence radiated to
    all beings, thus establishing this place as a center
    of giving and receiving of all that is Good, Joyful
    and Prosperous.
    \parspace
    \textbf{PRAYER}
    \parspace
    I thank You, Oh God, for this space is filled with
    Your Presence.
    \parspace
    I thank you, for I live and move within You.
    \parspace
    I thank You, for I live in Your Life, Truth, Health,
    Prosperity, Peace, Wisdom, Joy and Love.
    \parspace
    I thank You, for all who enter here will feel Your
    Presence.
    \parspace
    I thank You, for I am in Harmony, Love, Truth and
    Justice with all beings.
    \parspace
    Amen.
  \endverse
\endsong


\beginsong{Prece de Carita}
  \beginverse
    Deus, nosso Pai que sois todo Poder e Bondade, dai
    a força àquele que passa pela provação.
    \ind Dai a luz àquela que procura a verdade.
    \ind Ponde no coração do homem a compaixão e a caridade.
    \ind Deus! Dai ao viajor a estrela guia; ao aflito,
    a consolação; ao doente, o repouso!
    \ind Pai, dai ao culpado, o arrependimento; ao espírito,
    a verdade; à criança, o guia; ao órfão, o pai!
    \ind Senhor, que a Vossa bondade se estenda sobre tudo
    que criastes.
    \ind Piedade, Senhor, para aqueles que Vos não conhecem.
    \ind Esperança para aqueles que sofrem.
    \ind Que a Vossa bondade permita aos espíritos
    consoladores derramarem por toda a parte a paz, a
    esperança e a fé.
    \ind Deus! Um raio, uma faísca do Vosso amor pode abraçar
    a terra.
    \ind Deixa-nos beber na fonte dessa bondade fecunda
    e infinita e todas as lágrimas secarão e todas as
    dores se acalmarão.
    \ind Um só coração, um só pensamento subirá até Vós,
    como um grito de reconhecimento e de Amor.
    \ind Como Moisés sobre as montanha nós Vós esperamos
    com os braços abertos.
    \ind O Poder, o Bondade, o Beleza, o Perfeição, e
    queremos de alguma sorte merecer a Vossa infinita
    misericórdia.
    \ind Deus, dai-nos a força de ajudar o progresso a fim
    de subir-nos até Vós.
    \ind Dai-nos a caridade pura, dai-nos a fé e a razão.
    \ind Dai-nos a simplicidade que fará de nossas almas o
    espelho aonde se deve refletir a Vossa imagem.
    \parspace
    Amém.
  \endverse
  \brk
  \beginverse
    \translationtitle{EN}{Prayer of Carita}
    God, our Father who is all Power and Kindness,
    give strength to those who're going through
    their trials.
    \ind Give light to those who are seeking the truth.
    \ind Put in the hearts of men compassion and charity.
    \ind God, give to the one who travels, a guiding star;
    to the afflicted, consolation; to the sick, rest.
    \ind Father, give to the guilty, repentance; to the
    spirit, truth; to the child, a guide; to the orphan,
    a father.
    \ind Lord, may Your kindness spread above all that You
    have created.
    \ind Mercy, Lord, for those who don't know You.
    \ind Hope for those who suffer.
    \ind May Your kindness allow the consoling spirits to
    spread everywhere Peace, Hope and Faith.
    \ind God, one ray, one spark of Your Love can enlighten
    the earth.
    \ind Let us drink in the fountain of this fertile and
    infinite kindness, and all tears will dry, and all pains
    will quiet down.
    \ind One single heart, one single thought will go up to
    You, like a cry of thankfullness and of love.
    \ind Like Moses on the mountain, we await for You with
    open arms.
    \ind Oh Power, oh Kindness, oh Beauty, oh Perfection,
    we want, in some way, to deserve Your infinite Mercy!
    \ind God, give us the strength to support the progress,
    in order to rise up to You.
    \ind Give us pure Charity, give us Faith and Reason.
    \ind Give us the simplicity that will make our souls the
    mirror where Your image must be reflected.
    \parspace
    Amen.
  \endverse
\endsong


\beginsong{Salve Rainha}
  \beginverse
    Deus Vós salve, oh! Rainha, Mãe de Misericórdia,
    vida, doçura, esperança nossa, salve!
    \parspace
    A Vós bradamos, os degredados filhos de Eva.
    \parspace
    A Vós suspiramos, gemendo, e chorando neste vale de
    lágrimas.
    \parspace
    Eia pois, advogada nossa, esses Vossos olhos
    misericordiosos a nós volveis.
    \parspace
    E depois deste desterro mostrai nos Jesus.
    \parspace
    Bendito e o fruto do Vosso Ventre!
    \parspace
    Oh! Clemente, oh! Piedosa, oh! Doce, Sempre Virgem
    Maria!
    \parspace
    Rogai a Deus por nós, Santíssima Mãe de Deus, para
    que sejamos dignos de alcançar as promessas de nosso
    Senhor Jesus Cristo, Senhor nosso.
    \parspace
    Amém. Jesus, Maria, e José.
  \endverse
  \beginverse
    \translationtitle{EN}{Hail Holy Queen}
    Hail Holy Queen, Mother of Mercy, our life, our
    sweetness and our hope.
    \parspace
    To You do we cry, poor banished children of Eve;
    \parspace
    to You do we send up our sighs, mourning and weeping
    in this valley of tears.
    \parspace
    Turn then, O most Gracious Advocate, Your eyes of
    mercy towards us.
    \parspace
    And after this, our exile, show unto us the blessed
    fruit of your womb, Jesus.
    \parspace
    O! Clement, o! loving, o! sweet Virgin Mary!
    \parspace
    Pray for us o Holy Mother of God, that we may be
    worthy of the promises of our Lord Jesus Christ,
    our Lord forever.
    \parspace
    Amen. Jesus, Mary and Joseph.
  \endverse
\endsong


\beginsong{Encerramento}
  \beginverse
    Louvado seja Deus nas alturas!
    \textnote{E todos respondem:}
    Para que sempre seja louvada
    a nossa Mãe Maria Santíssima,
    sobre toda a humanidade.
    Amém!
  \endverse
  \beginverse
    \translationtitle{EN}{Closing}
    Praised be God in the Heights!
    \textnote{And all respond:}
    May our Mother, the Most Holy Mary,
    be forever praised above all humanity.
    Amen!
  \endverse
\endsong


\beginsong{Sinal da Cruz}
  \beginverse
    \up{1}Pelo sinal da Santa Cruz,
    \up{2}livrai-nos, Deus, nosso Senhor,
    \up{3}dos nossos inimigos
    \parspace
    \up{4}Em nome do Pai,
    \up{5}do Filho e
    \up{6}do Espírito \up{7}Santo.
    \parspace
    Amém.
  \endverse
  \beginverse
    \translationtitle{EN}{Sign of the Cross}
    \up{1}By the sign of the Holy Cross,
    \up{2}deliver us, God, our Lord,
    \up{3}from our enemies
    \parspace
    \up{4}In the name of the Father,
    \up{5}the Son, and
    \up{6}the Holy \up{7}Spirit.
    \parspace
    Amen.
  \endverse
  \begin{note}
    While speaking the prayer, synchronously make
    the sign of the Cross with with your right thumb
    on your \up{1}forehead,
    on your \up{2}mouth, and
    on your \up{3}chest.
    \parspace
    Then, with your right hand, touch
    your \up{4}forehead,
    your \up{5}chest,
    your \up{6}left shoulder and \up{7}right shoulder.
  \end{note}
\endsong
