% Santo Daime Preces: abertura
% ============================
%
% Note that this file is supposed to be wrapped in 'songs' environment.


% use Roman numerals for song (prayer) numbering:
\renewcommand{\thesongnum}{\Roman{songnum}}
\setcounter{songnum}{1}


\beginsong{Sinal da Cruz}[tags={bailado, São Miguel, Mesa Branca}]
  \begin{passage}[PT]{}\obeylines
    \up{1}Pelo sinal da Santa Cruz,
    \up{2}livrai-nos, Deus, nosso Senhor,
    \up{3}dos nossos inimigos
    \polpar
    \up{4}Em nome do Pai, \up{5}do Filho e \up{6}do Espírito \up{7}Santo.
    \polpar
    Amém.
  \end{passage}
  \begin{passage}[EN]{Sign of the Cross}\obeylines
    \up{1}By the sign of the Holy Cross,
    \up{2}deliver us, God, our Lord,
    \up{3}from our enemies
    \polpar
    \up{4}In the name of the Father, \up{5}the Son, and \up{6}the Holy \up{7}Spirit.
    \polpar
    Amen.
  \end{passage}
  \begin{passage}[FI]{Ristinmerkki}\obeylines
    \up{1}Pyhällä ristinmerkillä
    \up{2}Vapauta meidät Jumala, Herramme
    \up{3}Vihollisistamme
    \polpar
    \up{4}Isän, \up{5}Pojan ja \up{6}Pyhän \up{7}Hengen nimeen.
    \polpar
    Aamen.
  \end{passage}
  %\vspace*{\fill}
  \hardbrk
  \vspace*{\fill}
  \begin{passage}*[PT]{}\obeylines
    Enquanto recita a oração, faça sincronizadamente
    o sinal da Cruz com seu polegar direito
    na sua \up{1}testa,
    na sua \up{2}boca e
    no seu \up{3}peito.
    \polpar
    Em seguida, com a sua mão direita, toque
    na sua \up{4}testa,
    no seu \up{5}peito,
    no seu \up{6}ombro esquerdo e no seu \up{7}ombro direito.
  \end{passage}
  \begin{passage}*[EN]{}\obeylines
    While speaking the prayer, synchronously make
    the Sign of the Cross with with your right thumb
    on your \up{1}forehead,
    on your \up{2}mouth, and
    on your \up{3}chest.
    \polpar
    Then, with your right hand, touch
    your \up{4}forehead,
    your \up{5}chest,
    your \up{6}left shoulder and \up{7}right shoulder.
  \end{passage}
  \begin{passage}*[FI]{}\obeylines
    Lausuessasi rukousta, tee samanaikaisesti
    Ristinmerkki oikean kätesi peukalolla
    \up{1}otsallesi,
    \up{2}suullesi ja
    \up{3}rinnallesi.
    \polpar
    Sitten, kosketa oikealla kädelläsi
    \up{4}otsaasi,
    \up{5}rintaasi,
    \up{6}vasenta olkaasi ja \up{7}oikeaa olkaasi.
  \end{passage}
  \vspace*{\fill}
\endsong


\scleardpage
\beginsong{Credo}[tags={bailado}]
  \begin{passage}[PT]{}
    Creio em Deus Pai todo Poderoso,
    Criador do Céu e da terra.
    \par
    Creio em Jesus Cristo, um só seu filho, Nosso
    Senhor, o qual for concebido por obra e graça do
    Espírito Santo. Nasceu da Maria Virgem;
    padeceu sob o poder de Pôncio Pilatos;
    foi crucificado, morto e sepultado. Desceu aos
    infernos, ao terceiro dia ressurgiu dos mortos,
    Subiu ao Céu e Pai Todo-poderoso, de onde há de vir
    a julgar os vivos e os mortos.
    \par
    Creio no Espirito Santo, na Santa Igreja,
    na comunhão dos Santos, na remissão
    dos pecados, na ressurreição da carne,
    na vida eterna.
    \par
    Amém.
  \end{passage}
  \hardbrk
  \begin{passage}[EN]{Creed}
    I believe in God, the Father Almighty,
    Creator of Heaven and earth.
    \par
    I believe in Jesus Christ, His only Son, Our Lord,
    who was conceived through the work and grace of
    the Holy Spirit. He was born of the Virgin Mary;
    suffered under the power of Pontius Pilate;
    was crucified, died, and was buried. He decended
    into Hell; on the third day he rose again from
    the dead. He ascended into Heaven and is seated
    at the right hand of God, the Father Almighty, from
    where He come to judge the living and the dead.
    \par
    I believe in the Holy Spirit, the Holy Church,
    the communion of Saints, the forgiveness of sins,
    the resurrection of the body, and life everlasting.
    \par
    Amen.
  \end{passage}
  \begin{passage}[FI]{Uskontunnustus}
    Minä uskon Jumalaan, Isään, Kaikkivaltiaaseen, taivaan ja maan Luojaan; ja
    \par
    Jeesukseen Kristukseen, Jumalan ainoaan Poikaan, meidän Herraamme,
    joka sikisi Pyhän Hengen toimesta ja armosta, syntyi neitsyt Mariasta,
    kärsi Pontius Pilatuksen aikana, ristiinnaulittiin, kuoli ja haudattiin,
    astui alas tuonelaan, nousi kolmantena päivänä kuolleista, astui ylös
    taivaisiin, istuu Jumalan, Isän, Kaikkivaltiaan, oikealla puolella ja on
    sieltä tuleva tuomitsemaan eläviä ja kuolleita; ja
    \par
    Pyhään Henkeen, pyhään yhteiseen seurakuntaan, pyhäin yhteyteen, syntien
    anteeksiantamiseen, ruumiin ylösnousemiseen ja iankaikkiseen elämään.
    \par
    Aamen.
  \end{passage}
\endsong


\scleardpage
\beginsong{Pai nosso \& Ave Maria}[tags={3x}]
  \vspace*{6ex}
  \begin{passage}[PT]{Pai nosso}
    Pai nosso,
    que estais no Céu,
    santificado seja o Vosso Nome.
    \par
    Vamos nós ao Vosso Reino.
    \par
    Seja feita a Vossa Vontade,
    assim na terra como no Céu.
    \par
    O pão nosso de cada dia nos daí hoje, Senhor.
    \par
    Perdoai as nossas dividas,
    assim como nós perdoamos os nossos devedores.
    \par
    Não nos deixas, Senhor, cair em tentação,
    mas livrai-me e defendei-me, Senhor,
    de todo mal.
    \par
    Amém, Jesus, Maria, José.
  \end{passage}
  \begin{passage}[PT]{Ave Maria}
    Ave Maria,
    cheia de Graça!
    O Senhor é convosco.
    \par
    Bendita sois Vós entre as mulheres.
    Bendito é o fruto do Vosso ventre, Jesus.
    \par
    Santa Maria, Mãe de Deus,
    rogai a Deus por nos pecadores,
    agora e na hora de nossa morte.
    \par
    Amém, Jesus, Maria, José.
  \end{passage}
  \vspace{\fill}
  \hardbrk
  \vspace*{11.5ex} % to align with the previous page
  \begin{passage}[EN]{Our Father}
    Our Father,
    who art in Heaven,
    hallowed be Thy Name.
    \par
    Let us go into Thy Kingdom.
    \par
    Thy Will be done,
    on earth as it is in Heaven.
    \par
    Give us this day our daily bread, Lord.
    \par
    Forgive us our debts,
    as we forgive our debtors.
    \par
    Let us not fall in temptation,
    but deliver me and defend me, Lord,
    from all evil.
    \par
    Amen, Jesus, Mary, Joseph.
  \end{passage}
  \begin{passage}[EN]{Hail Mary}
    Hail Mary,
    full of grace!
    The Lord is with Thee.
    \par
    Blessed art Thou amongst women!
    Blessed is the fruit of Thy womb, Jesus.
    \par
    Holy Mary, Mother of God,
    pray to God for us sinners,
    now and at the hour of our death.
    \par
    Amen, Jesus, Mary, Joseph.
  \end{passage}
  \vspace{\fill}
  \hardbrk
  \vspace*{11.5ex} % to align with the previous page
%   \begin{passage}[FI]{Isä meidän {\scriptsize(Kemi)}}
%     Isä meidän, joka olet taivaassa,
%     pyhitetty olkoon sinun nimesi.
%     \par
%     Menkäämme valtakuntaasi.
%     \par
%     Tapahtukoon sinun tahtosi niin
%     maan päällä kuin taivaassa.
%     \par
%     Anna meille tänä päivänä meidän
%     jokapäiväinen leipämme, Herra.
%     \par
%     Anna meille meidän velkamme anteeksi,
%     niin kuin mekin anteeksi annamme velallisillemme.
%     \par
%     Äläkä anna meidän langeta kiusaukseen,
%     vaan vapauta ja suojele minut,
%     Herra, kaikelta pahalta.
%     \par
%     Aamen, Jeesus, Maria, Joosef
%   \end{passage}
  \begin{passage}[FI]{Isä meidän {\scriptsize(ev.lut.)}}
    Isä meidän, joka olet taivaassa,
    pyhitetty olkoon sinun nimesi.
    \par
    Tulkoon sinun valtakuntasi.
    \par
    Tapahtukoon sinun tahtosi,
    myös maan päällä niin kuin taivaassa.
    \par
    Anna meille tänä päivänä
    meidän jokapäiväinen leipämme.
    \par
    Ja anna meille meidän syntimme anteeksi,
    niin kuin mekin anteeksi annamme niille,
    jotka ovat meitä vastaan rikkoneet.
    \par
    Äläkä saata meitä kiusaukseen,
    vaan päästä meidät pahasta.
    \par
    Sillä sinun on valtakunta,
    voima ja kunnia iankaikkisesti.
    \par
    Aamen, Jeesus, Maria, Joosef.
  \end{passage}
  \begin{passage}[FI]{Terve Maria}
    Terve Maria, armoitettu,
    Herra sinun kanssasi.
    \par
    Siunattu sinä naisten joukossa,
    ja siunattu kohtusi hedelmä, Jeesus.
    \par
    Pyhä Maria, Jumalan äiti, rukoile meidän
    syntisten puolesta nyt, ja kuolemamme hetkenä.
    \par
    Aamen, Jeesus, Maria, Joosef
  \end{passage}
  \vspace*{\fill}
\endsong


\beginsong{O Terço I (trabalho officiais)}[tags={bailado}]
  \begin{passage}[PT]{}
    \passagenote*{Ao rezar o terço, só diz a cada dezena:}
    Gloria ao Pai, ao Filho, ao Espírito Santo.
    Assim como era no princípio, agora e sempre,
    por todos os séculos dos séculos. Amém.
  \end{passage}
  \begin{passage}[EN]{The Rosary I}
    \passagenote*{While praying the Rosary, after every decade:}
    Glory to the Father, to the Son and to the Holy Spirit.
    As it was in the beginning, is now, and ever shall be,
    for all the ages of the ages. Amen.
  \end{passage}
  \begin{passage}[FI]{Rukousnauha I}
    \passagenote*{Rukoillessa Rukousnauhaa, jokaisen kymmenikön jälkeen:}
    Kunnia olkoon Isälle, Pojalle ja Pyhälle Hengelle,
    niin kuin oli alussa, nyt on ja aina,
    kautta vuosisatojen.\\
    Aamen.
  \end{passage}
\endsong


\begin{intersong}
  \begin{passage}[PT]{}
    \passagenote{Ao fim do terço, (normalmente) a comandante do pelotão feminino:}
    Em nome de Deus Pai Todo-Poderoso, da Virgem Soberana Mãe,
    do Nosso Senhor Jesus Cristo, do Patriarca São José e de
    todos os Seres Divinos da Corte Celestial, com a ordem de
    nosso Mestre Império Juramidam, estão abertos os nossos
    trabalhos, meus irmãos e minhas irmãs. Que Deus e a Virgem Mãe
    sejam nossos guias para sempre. Amém!
    \passagenote*{Todos se benzem.}
  \end{passage}
  \begin{passage}[EN]{ }% The whitespace in { } is intentional!
    \passagenote*{At the end of Rosary, (usually) the commander of the feminine batallion:}
    In the name of God the Almighty Father, of the Sovereign Virgin
    Mother, of Our Lord Jesus Christ, of the Patriarch Saint Joseph and of
    all the Divine Beings of the Celestial Court, with the order of our Master
    Governor Juramidam, our works are open, my brothers and sisters.
    May God and the Virgin Mother be our guides forever. Amen!
    \passagenote*{All make the sign of the cross.}
  \end{passage}
  % This is 'unofficial' Finnish translation by larva:
  \begin{passage}[FI]{ }% The whitespace in { } is intentional!
    \passagenote*{Rukousnauhan lopussa (yleensä) naispataljoonan komentaja:}
    Jumalan kaikkivaltiaan Isän, Ylimmäisen Neitsyt-Äidin,
    meidän Herramme Jeesus Kristuksen, patriarkka Pyhän Joosefin ja
    kaikkien Taivaallisen Hovin Jumalallisten Olentojen nimissä,
    Mestarimme Valtias Juramidamin valtuuttamina, julistamme työmme alkaneeksi,
    veljet ja sisaret. Jumala ja Neitsyt-Äiti olkoot oppaamme ikuisesti. Aamen!
    \passagenote*{Kaikki tekevät ristinmerkin.}
  \end{passage}
  \vfill
\end{intersong}


\beginsong{O Terço II (Santa Missa)}[tags={Santa Missa}]
  \begin{passage}[PT]{}
    \passagenote*{Ao rezar o terço, só diz a cada dezena:}
    Gloria ao Pai, ao Filho, ao Espírito Santo.
    Assim como era no princípio, agora e sempre,
    por todos os séculos dos séculos. Amém.
    \par
    Oh! meu Jesus, perdoai-me, livrai-me do fogo do
    inferno. Levai as almas todas para o Céu, e soccorei
    principalmente aquelas que mais precísarem. Amém.
  \end{passage}
  \begin{passage}[EN]{The Rosary II}
    \passagenote*{While praying the Rosary, after every decade:}
    Glory to the Father, to the Son and to the Holy Spirit.
    As it was in the beginning, is now, and ever shall be,
    for all the ages of the ages. Amen.
    \par
    Oh my Jesus, forgive me, and save me from the fires
    of hell. Lead all souls into heaven, and especially
    help those in most need. Amen.
  \end{passage}
  \begin{passage}[FI]{Rukousnauha II}
    \passagenote*{Rukoillessa Rukousnauhaa, jokaisen kymmenikön jälkeen:}
    Kunnia olkoon Isälle, Pojalle ja Pyhälle Hengelle,
    niin kuin oli alussa, nyt on ja aina,
    kautta vuosisatojen.\\
    Aamen.
    \par
    Oi, Jeesukseni! Anna minulle anteeksi ja vapauta
    minut helvetin tulelta. Johdata kaikki
    sielut taivaaseen ja auta erityisesti niitä,
    jotka sitä eniten tarvitsevat. Aamen.
  \end{passage}
\endsong


\sclearpage
\beginsong{Chave de Harmonia}[by={O Circulo Esoterico da comunhão do Pensamento (São Paulo, Brasil)},tags={trabalhos de mesa}]
  \begin{passage}[PT]{}
    Desejo Harmonia, Amor, Verdade e Justiça a todos os
    meus irmãos.
    \par
    Com as forças reunidas das silenciosas vibrações
    dos nossos pensamentos, somos fortes, sádios e
    felizes, formando assim um elo de fraternidade
    universal.
    \par
    Estou satisfeito e em paz com o universo inteiro
    e desejo que todos os seres realizam as suas
    aspirações mais íntímas.
    \par
    Dou graças ao Pai Invisivel por ter estabelecido
    a Harmonia, o Amor, a Verdade e a Justiça entre
    todos os seus filhos.
    \par
    Assim seja, Amém.
  \end{passage}
  \hardbrk
  \begin{passage}[EN]{Key of Harmony}
    I wish Harmony, Love, Truth and Justice to all my
    brothers and sisters.
    \par
    With the united forces of the silent vibrations
    of our thoughts, we are strong, healthy and happy,
    thus forming a link of universal fraternity.
    \par
    I am satisfied and in peace with the whole
    universe, and I wish that all beings achieve their
    most intimate aspirations.
    \par
    I give thanks to my Invisible Father for having
    established Harmony, Love, Truth and Justice among
    all his children.
    \par
    So be it, Amen.
  \end{passage}
  \begin{passage}[FI]{Harmonian avain}
    Toivon harmoniaa, rakkautta, totuutta ja oikeutta kaikille sisaruksilleni.
    \par
    Ajatustemme hiljaisten värähtelyjen yhdistettyjen voimien kautta, olemme
    vahvoja, terveitä ja onnellisia rakentaen näin maailmanlaajuisen
    sisarusyhteyden.
    \par
    Olen tyytyväinen ja rauhassa koko maailmankaikkeuden kanssa ja toivon,
    että kaikki olennot toteuttavat syvimmät pyrkimyksensä.
    \par
    Kiitän näkymätöntä Isää hänen luomastaan harmoniasta, rakkaudesta,
    totuudesta ja oikeudesta kaikkien lastensa kesken.
    \par
    Näin olkoon, Aamen.
  \end{passage}
\endsong


\scleardpage
\beginsong{Consagração do Aposento}[by={O Circulo Esoterico da comunhão do Pensamento (São Paulo, Brasil)}]
  \begin{passage}[PT]{}
    \passagenote*{Nos trabalhos de mesa: após Hinos da Oração}
    \par
    Dentro do Circulo Infinito da Divina Presença que
    me envolve inteiramente, afirmo:
    \par
    Há uma só presença aqui --- é a da HARMONIA que faz
    vibrar todos os corações de felicidade e alegria.
    Quem quer que aqui entre, sentirá as vibrações da
    Divina Harmonia.
    \par
    Há uma só presença aqui --- é a do AMOR. Deus é o
    Amor que envolve todos os seres num só sentimento
    de unidade. Este recinto está cheio da presença do
    Amor. No Amor eu vivo, me movo e existo. Quem quer
    que aqui entre, sentirá a pura e Santa Presença do
    Amor.
    \par
    Há uma só presença aqui --- é a da VERDADE. Tudo
    que aqui existe, tudo o que aqui se fala, tudo o
    que aqui se pensa é a expressão da Verdade. Quem
    quer que aqui entre, sentirá a Presença da Verdade.
    \par
    Há uma só presença aqui --- é a da JUSTIÇA.
    A Justiça reina neste recinto. Todos os atos aqui
    praticados são regidos e inspirados pela Justiça.
    Quem quer que aqui entre, sentirá
    a Presença da Justiça.
    \par
    Há uma só presença aqui --- é a presença de Deus,
    o BEM. Nenhum mal pode entrar aqui. Não há mal em
    Deus. Deus, o Bem, reside aqui. Quem quer que aqui
    entre, sentirá a Presença Divina do Bem.
    \par
    Há uma só presença aqui --- é a presença de Deus,
    a VIDA. Deus é a Vida essencial de todos os seres.
    É a saúde do corpo e da mente. Quem quer que aqui
    entre, sentirá a Divina Presença da Vida e da Saúde.
    \par
    Há uma só presença aqui --- é a presença de Deus,
    a PROSPERIDADE. Deus é Prosperidade, pois Ele faz
    tudo crescer e prosperar. Deus se expressa na
    Prosperidade de tudo o que aqui é empreendido em
    seu nome. Quem quer que aqui entre, sentirá
    a Divina Presença da Prosperidade e da Abundância.
    \hardbrk\par
    Pelo símbolo esotérico das Asas Divinas, estou
    em vibração harmoniosa com as Correntes Universais
    da Sabedoria, do Poder e da Alegria. A Presença
    da Divina Sabedoria manifesta-se aqui. A presença
    da Alegria Divina é profundamente sentida por todos
    os que aqui entram.
    \par
    Na mais perfeita comunhão entre o meu eu inferior
    e o meu Eu Superior, que é Deus em mim, consagro
    este recinto à perfeita expressão de todas as
    qualidades Divinas que há em mim, e em todos os
    seres.
    \par
    As vibrações do meu pensamento são forças de Deus
    em mim, que aqui ficam armazenadas e daqui se
    irradiam para todos os seres, constituindo este
    lugar um centro de emissão e recepção de tudo
    quanto é BOM, ALEGRE, e PRÓSPERO.
    \par
    \vspace{1ex}
    \textbf{ORAÇÃO}
    \par
    Agradeço-Te o Deus, porque este recinto está cheio
    da Tua Presença.
    \par
    Agradeço-Te, porque vivo e me movo por Ti.
    \par
    Agradeço-Te, porque vivo em tua Vida, Verdade e
    Saúde, Prosperidade, Paz, Sabedoria, Alegria e Amor.
    \par
    Agradeço-Te, porque todos que entrarem aqui sentirão
    Tua Presença.
    \par
    Agradeço-Te, porque estou em Harmonia, Amor, Verdade
    e Justiça com todos os seres.
    \par
    Amém.
  \end{passage}
  \begin{passage}[EN]{Consecration of the Space}
    \passagenote*{In sitting works: after Oração}
    \par
    Inside the Infinite Circle of the Divine Presence
    which completely surrounds me, I affirm that:
    \par
    There is only one presence here --- it is HARMONY,
    which makes all hearts vibrate with joy and happiness.
    Those who choose to enter here will feel the vibration
    of Divine Harmony.
    \par
    There is only one presence here --- it is LOVE.
    God is love, which embraces all beings in one
    feeling of unity. This space is filled with the
    presence of Love. In Love, I live, I move and I
    exist. Those who choose to enter here will feel
    the pure and holy Presence of Love.
    \par
    There is only one presence here --- it is TRUTH.
    All that exists here, all that is spoken here,
    all that is thought here is the expression of
    Truth. Those who choose to enter here will feel
    the Presence of Truth.
    \par
    There is only one presence here --- it is JUSTICE.
    Justice reigns in this space. Everything practiced
    here is inspired and ruled by Justice. Those who
    choose to enter here will feel the Presence of
    Justice.
    \par
    There is only one presence here --- it is the
    presence of God, the BENEFICIENT. No evil can enter
    here. There is no evil in God. God, the Beneficient,
    dwells here. Those who choose to enter here will
    feel the Divine Presence of the Beneficient.
    \par
    There is only one presence here --- it is the
    presence of God, who is LIFE. God is the essential
    Life of all beings, the health of body and mind.
    Those who choose to enter here will feel the Divine
    Presence of Life and Health.
    \par
    There is only one presence here --- it is the
    presence of God, who is PROSPERITY. God is
    Prosperity because He makes everything grow and
    prosper. God expresses Himself through the
    Prosperity of all that is undertaken in His name.
    Those who choose to enter here will feel the
    Divine Presence of Prosperity and Abundance.
    \par
    Through the esoteric symbol of the Divine Wings,
    I am in harmonious vibration with the universal
    currents of Wisdom, Power and Joy. The Presence
    of Divine Wisdom is manifested here. The Presence
    of Divine Joy is deeply felt by all those who choose
    to enter here.
    \par
    In the perfect communion between my lower self and
    my Higher Self, which is God in me, I consecrate
    this space to the perfect expression of all Divine
    qualities which are in me and in all beings.
    \par
    The vibrations of my thoughts are the forces of God
    in me, which are stored here and hence radiate to
    all beings, thus establishing this place as a center
    of giving and receiving of all that is GOOD, JOYFUL
    and PROSPEROUS.
    \par
    \vspace{1ex}
    \textbf{PRAYER}
    \par
    I thank You, oh God, for this space is filled with
    Your Presence.
    \par
    I thank you, for I live and move within You.
    \par
    I thank You, for I live in Your Life, Truth, Health,
    Prosperity, Peace, Wisdom, Joy and Love.
    \par
    I thank You, for all those who enter here will feel
    Your Presence.
    \par
    I thank You, for I am in Harmony, Love, Truth and
    Justice with all beings.
    \par
    Amen.
  \end{passage}
  \begin{passage}[FI]{Paikan pyhittäminen}
    \passagenote*{Istumatöissä: Oraçãon jälkeen}
    \par
    Jumalallisen läsnäolon äärettömästä piiristä käsin,
    joka ympäröi minut täysin, todistan:
    \par
    Täällä on vain yksi läsnäolo, HARMONIAN läsnäolo,
    joka saa kaikkien sydämet värähtelemään  onnea ja
    iloa. Kuka tahansa, joka tulee tähän tilaan, saa
    tuntea jumalallisen harmonian värähtelyn.
    \par
    Täällä on vain yksi läsnäolo, RAKKAUDEN läsnäolo.
    Jumala on rakkaus, joka syleilee kaikkia olentoja
    kaikenkattavalla ykseyden tunteella. Tämä paikka on
    täynnä rakkauden läsnäoloa. Rakkaudessa minä elän,
    liikun ja olen. Kuka tahansa, joka tulee tähän tilaan,
    saa tuntea rakkauden puhtaan ja pyhän läsnäolon.
    \par
    Täällä on vain yksi läsnäolo, TOTUUS. Kaikki mitä
    täällä on, kaikki mitä täällä puhutaan, kaikki mitä
    täällä ajatellaan on totuuden ilmaisua. Kuka tahansa,
    joka tulee tähän tilaan, saa tuntea totuuden läsnäolon.
    \par
    Täällä on vain yksi läsnäolo, OIKEUS. Oikeus hallitsee
    tässä paikassa. Kaikki täällä tehdyt teot ovat oikeuden
    johtamia ja inspiroimia. Kuka tahansa, joka tulee tähän
    tilaan, saa tuntea oikeuden läsnäolon.
    \par
    Täällä on vain yksi läsnäolo, Jumalan läsnäolo, HYVYYS.
    Mikään paha ei pääse tänne. Jumalassa ei ole pahaa.
    Jumala, joka on hyvyys, asuu täällä. Kuka tahansa, joka
    tulee tähän tilaan, saa tuntea hyvyyden jumalallisen
    läsnäolon.
    \par
    Täällä on vain yksi läsnäolo, Jumalan läsnäolo, joka on
    ELÄMÄ. Jumala on kaikkien olentojen elämän ydin.
    Mielen ja ruumiin terveys. Kuka tahansa, joka tulee
    tähän tilaan, saa tuntea elämän ja terveyden jumalallisen
    läsnäolon.
    \par
    Täällä on vain yksi läsnäolo, KUKOISTUS. Jumala on kukoistus,
    koska Hän saa kaiken kasvamaan ja menestymään.
    Jumala ilmaisee itseään kaiken sen kukoistamisessa,
    mihin täällä ryhdytään Hänen nimessään. Kuka tahansa,
    joka tulee tähän tilaan, tuntee kukoistamisen ja
    yltäkylläisyyden jumalallisen läsnäolon.
    \par
    Jumalallisten siipien esoteerisen symbolin kautta
    värähtelen harmoniassa VIISAUDEN, VOIMAN ja ILON
    universaalien virtausten kanssa. Jumalallisen viisauden
    läsnäolo ilmentyköön täällä. Jumalallisen ilon
    läsnäolon tuntevat syvästi kaikki ne, jotka tähän
    tilaan saapuvat.
    \par
    Mitä täydellisimmässä yhteydessä alemman minäni ja
    korkeamman minäni välillä, joka on Jumala minussa,
    pyhitän tämän paikan kaikkien niiden jumalallisten
    ominaisuuksien täydelliselle ilmaisulle, jotka ovat
    minussa ja kaikissa olennoissa.
    \par
    AJATUSTENI värähtelyt ovat Jumalan voimia minussa,
    jotka kootaan täällä ja lähetetään täältä kaikille
    olennoille, niin että tästä paikasta tulee keskus,
    josta lähetetään ja vastaanotetaan kaikkea, mikä on
    HYVÄÄ, ILOISTA ja KUKOISTAVAA.
    \par
    \vspace{1ex}
    \textbf{RUKOUS}
    \par
    Kiitän sinua, oi Jumala, koska tämä paikka on täynnä
    sinun läsnäoloasi.
    \par
    Kiitän sinua, koska elän ja liikun sinussa.
    \par
    Kiitän sinua, koska elän sinun Elämässäsi, Totuudessasi,
    Terveydessäsi, Kukoistuksessasi, Rauhassasi,
    Viisaudessasi, Ilossasi ja Rakkaudessasi.
    \par
    Kiitän sinua, koska kaikki jotka saapuvat tänne saavat
    tuntea sinun läsnäolosi.
    \par
    Kiitän sinua, koska olen Harmoniassa, Rakkaudessa,
    Totuudessa ja Oikeudessa kaikkien olentojen kanssa.
    \par
    Aamen.
  \end{passage}
\endsong
