% Santo Daime Preces: encerramento
% ================================
%

% use Roman numerals for song (prayer) numbering:
\renewcommand{\thesongnum}{\Roman{songnum}}
\setcounter{songnum}{1}

\beginsong{Pai nosso \& Ave Maria}[tags={3x}]
  \vspace*{3.65ex}
  \begin{passage}[PT]{Pai nosso}
    Pai nosso,
    que estais no Céu,
    santificado seja o Vosso Nome.
    \par
    Vamos nós ao Vosso Reino.
    \par
    Seja feita a Vossa Vontade,
    assim na terra como no Céu.
    \par
    O pão nosso de cada dia nos daí hoje, Senhor.
    \par
    Perdoai as nossas dividas,
    assim como nós perdoamos os nossos devedores.
    \par
    Não nos deixas, Senhor, cair em tentação,
    mas livrai-me e defendei-me, Senhor,
    de todo mal.
    \par
    Amém, Jesus, Maria, José.
  \end{passage}
  \begin{passage}[PT]{Ave Maria}
    Ave Maria,
    cheia de Graça!
    O Senhor é convosco.
    \par
    Bendita sois Vós entre as mulheres.
    Bendito é o fruto do Vosso ventre, Jesus.
    \par
    Santa Maria, Mãe de Deus,
    rogai a Deus por nos pecadores,
    agora e na hora de nossa morte.
    \par
    Amém, Jesus, Maria, José.
  \end{passage}
  \vspace{\fill}
  \hardbrk
  \vspace*{10ex} % to align with the previous page
  \begin{passage}[EN]{Our Father}
    Our Father,
    who art in Heaven,
    hallowed be Thy Name.
    \par
    Let us go into Thy Kingdom.
    \par
    Thy Will be done,
    on earth as it is in Heaven.
    \par
    Give us this day our daily bread, Lord.
    \par
    Forgive us our debts,
    as we forgive our debtors.
    \par
    Let us not fall in temptation,
    but deliver me and defend me, Lord,
    from all evil.
    \par
    Amen, Jesus, Mary, Joseph.
  \end{passage}
  \begin{passage}[EN]{Hail Mary}
    Hail Mary,
    full of grace!
    The Lord is with Thee.
    \par
    Blessed art Thou amongst women!
    Blessed is the fruit of Thy womb, Jesus.
    \par
    Holy Mary, Mother of God,
    pray to God for us sinners,
    now and at the hour of our death.
    \par
    Amen, Jesus, Mary, Joseph.
  \end{passage}
  \vspace{\fill}
  \hardbrk
  \vspace*{10ex} % to align with the previous page
  \begin{passage}[FI]{Isä Meidän}
    Isä meidän, joka olet taivaassa,
    pyhitetty olkoon sinun nimesi.
    \par
    Menkäämme valtakuntaasi.
    \par
    Tapahtukoon sinun tahtosi niin
    maan päällä kuin taivaassa.
    \par
    Anna meille tänä päivänä meidän
    jokapäiväinen leipämme, Herra.
    \par
    Anna meille meidän velkamme anteeksi,
    niin kuin mekin anteeksi annamme velallisillemme.
    \par
    Äläkä anna meidän langeta kiusaukseen,
    vaan vapauta ja suojele minut,
    Herra, kaikelta pahalta.
    \par
    Aamen, Jeesus, Maria, Joosef
  \end{passage}
  \begin{passage}[FI]{Terve Maria}
    Terve Maria, armoitettu,
    Herra sinun kanssasi.
    \par
    Siunattu sinä naisten joukossa,
    ja siunattu kohtusi hedelmä, Jeesus.
    \par
    Pyhä Maria, Jumalan äiti, rukoile meidän
    syntisten puolesta nyt, ja kuolemamme hetkenä.
    \par
    Aamen, Jeesus, Maria, Joosef
  \end{passage}
  \vspace*{\fill}
\endsong


\beginsong{Credo}[tags={Mesa Branca, São Miguel}]
  \begin{passage}[PT]{}
    Creio em Deus Pai todo Poderoso,
    Criador do Céu e da terra.
    \par
    Creio em Jesus Cristo, um só seu filho, Nosso
    Senhor, o qual for concebido por obra e graça do
    Espírito Santo. Nasceu da Maria Virgem;
    padeceu sob o poder de Pôncio Pilatos;
    foi crucificado, morto e sepultado. Desceu aos
    infernos, ao terceiro dia ressurgiu dos mortos,
    Subiu ao Céu e Pai Todo-poderoso, de onde há de vir
    a julgar os vivos e os mortos.
    \par
    Creio no Espirito Santo, na Santa Igreja,
    na comunhão dos Santos, na remissão
    dos pecados, na ressurreição da carne,
    na vida eterna.
    \par
    Amém.
  \end{passage}
  \hardbrk
  \begin{passage}[EN]{Creed}
    I believe in God, the Father Almighty,
    Creator of Heaven and earth.
    \par
    I believe in Jesus Christ, His only Son, Our Lord,
    who was conceived through the work and grace of
    the Holy Spirit. He was born of the Virgin Mary;
    suffered under the power of Pontius Pilate;
    was crucified, died, and was buried. He decended
    into Hell; on the third day he rose again from
    the dead. He ascended into Heaven and is seated
    at the right hand of God, the Father Almighty, from
    where He come to judge the living and the dead.
    \par
    I believe in the Holy Spirit, the Holy Church,
    the communion of Saints, the forgiveness of sins,
    the resurrection of the body, and life everlasting.
    \par
    Amen.
  \end{passage}
  \begin{passage}[FI]{Uskontunnustus}
    Minä uskon Jumalaan, Isään, Kaikkivaltiaaseen, taivaan ja maan Luojaan; ja
    \par
    Jeesukseen Kristukseen, Jumalan ainoaan Poikaan, meidän Herraamme,
    joka sikisi Pyhän Hengen toimesta ja armosta, syntyi neitsyt Mariasta,
    kärsi Pontius Pilatuksen aikana, ristiinnaulittiin, kuoli ja haudattiin,
    astui alas tuonelaan, nousi kolmantena päivänä kuolleista, astui ylös
    taivaisiin, istuu Jumalan, Isän, Kaikkivaltiaan, oikealla puolella ja on
    sieltä tuleva tuomitsemaan eläviä ja kuolleita; ja
    \par
    Pyhään Henkeen, pyhään yhteiseen seurakuntaan, pyhäin yhteyteen, syntien
    anteeksiantamiseen, ruumiin ylösnousemiseen ja iankaikkiseen elämään.
    \par
    Aamen.
  \end{passage}
\endsong


\sclearpage
\beginsong{Prece de Cáritas}[tags={cura},by={Medium Madame W. Krell (25 de Dezembro de 1873 em Bordeaux, França)}]
  \begin{passage}[PT]{}
    Deus, nosso Pai que sois todo Poder e Bondade, dai
    a força àquele que passa pela provação.
    \par
    Dai a luz àquela que procura a verdade.
    \par
    Ponde no coração do homem a compaixão e a caridade.
    \par
    Deus! Dai ao viajor a estrela guia; ao aflito,
    a consolação; ao doente, o repouso!
    \par
    Pai, dai ao culpado, o arrependimento; ao espírito,
    a verdade; à criança, o guia; ao órfão, o pai!
    \par
    Senhor, que a Vossa bondade se estenda sobre tudo
    que criastes.
    \par
    Piedade, Senhor, para aqueles que Vos não conhecem.
    \par
    Esperança para aqueles que sofrem.
    \par
    Que a Vossa bondade permita aos espíritos
    consoladores derramarem por toda a parte a paz, a
    esperança e a fé.
    \par
    Deus! Um raio, uma faísca do Vosso amor pode abraçar
    a terra.
    \par
    Deixa-nos beber na fonte dessa bondade fecunda
    e infinita e todas as lágrimas secarão e todas as
    dores se acalmarão.
    \par
    Um só coração, um só pensamento subirá até Vós,
    como um grito de reconhecimento e de Amor.
    \par
    Como Moisés sobre as montanha nós Vós esperamos
    com os braços abertos. ---
    O Poder, o Bondade, o Beleza, o Perfeição ---
    e queremos de alguma sorte merecer a Vossa infinita
    misericórdia.
    \par
    Deus, dai-nos a força de ajudar o progresso a fim
    de subir-nos até Vós.
    \par
    Dai-nos a caridade pura.
    \par
    Dai-nos a fé e a razão.
    \par
    Dai-nos a simplicidade que fará de nossas almas o
    espelho aonde se deve refletir a Vossa imagem.
    \par
    Amém.
  \end{passage}
  \begin{passage}[EN]{Prayer of Caritas}
    God, our Father who is all Power and Kindness,
    give strength to those who're going through
    their trials.
    \par
    Give light to those who are seeking the truth.
    \par
    Put in the hearts of men compassion and charity.
    \par
    God, give to the one who travels, a guiding star;
    to the afflicted, consolation; to the sick, rest.
    \par
    Father, give to the guilty, repentance; to the
    spirit, truth; to the child, a guide; to the orphan,
    a father.
    \par
    Lord, may Your kindness spread above all that You
    have created.
    \par
    Mercy, Lord, for those who don't know You.
    \par
    Hope for those who suffer.
    \par
    May Your kindness allow the consoling spirits to
    spread everywhere Peace, Hope and Faith.
    \par
    God, one ray, one spark of Your Love can enlighten
    the earth.
    \par
    Let us drink in the fountain of this fertile and
    infinite kindness, and all tears will dry, and all pains
    will quiet down.
    \par
    One single heart, one single thought will go up to
    You, like a cry of thankfullness and of love.
    \par
    Like Moses on the mountain, we await for You with
    open arms. --- Oh Power, oh Kindness, oh Beauty, oh Perfection --- we want, in some way, to deserve Your infinite Mercy!
    \par
    God, give us the strength to support the progress,
    in order to rise up to You.
    \par
    Give us pure Charity, give us Faith and Reason.
    \par
    Give us the simplicity that will make our souls the
    mirror where Your image must be reflected. Amen.
  \end{passage}
  \begin{passage}[FI]{Caritan rukous}
    Jumala, Isämme kaikki voima ja hyvyys, anna voimaa sille, joka käy läpi koettelemuksia.
    \par
    Anna Valoa sille, joka etsii totuutta.
    \par
    Aseta ihmisen sydämeen myötätuntoa ja hyväntekeväisyyttä.
    \par
    Jumala! Anna kulkijalle opastava tähti;
    ahdistetulle lohtu ja sairaalle lepo!
    \par
    Isä, anna syylliselle katumus; hengelle totuus;
    lapselle opas ja orvolle Isä!
    \par
    Herra, ulottukoon Hyvyytesi kaiken luomasi ylle.
    \par
    Armoa, Herra, heille, jotka eivät Sinua tunne.
    \par
    Toivoa niille, jotka kärsivät.
    \par
    Hyvyytesi sallikoon lohduttavien henkien jakaa
    kaikkialle rauhaa, toivoa ja uskoa.
    \par
    Jumala! Yksi säde, yksi rakkautesi kipinä voi
    syleillä koko maata.
    \par
    Anna meidän juoda tästä hedelmällisestä ja
    ikuisesta lähteestä, ja kaikki kyyneleet kuivuvat
    ja kaikki kivut tyyntyvät.
    \par
    Yksi ainoa sydän, yksi ainoa ajatus nousee
    luoksesi kuin tunnistamisen ja rakkauden
    huuto.
    \par
    Kuin Mooses vuorella me odotamme Sinua
    avosylin --- Oi voima! Oi hyvyys! Oi kauneus!
    Oi täydellisyys! --- ja tahdomme jollakin tavalla
    ansaita rajattoman armosi.
    \par
    Jumala, anna meille voimaa auttamaan luoksesi nousemisen edistymistä.
    \par
    Anna meille vilpitöntä armeliaisuutta.
    \par
    Anna meille uskoa ja peruste.
    \par
    Anna meille yksinkertaisuutta, joka tekee sielustamme peilin,
    jossa kuvasi tulee näkyä.
    Aamen.
  \end{passage}
\endsong


\beginsong{Salve Rainha}
  \begin{passage}[PT]{}
    Deus Vós salve, oh! Rainha, Mãe de Misericórdia,
    vida, doçura, esperança nossa, salve!
    \par
    A Vós bradamos, os degredados filhos de Eva.
    A Vós suspiramos, gemendo, e chorando neste
    vale de lágrimas.
    \par
    Eia pois, advogada nossa, esses Vossos olhos
    misericordiosos a nós volveis.
    E depois deste desterro mostrai-nos Jesus.
    Bendito é o fruto do Vosso Ventre!
    \par
    Oh! Clemente, oh! Piedosa, oh! Doce, sempre
    Virgem Maria!
    Rogai a Deus por nós, Santíssima Mãe de Deus,
    para que sejamos dignos de alcançar as promessas
    de nosso Senhor Jesus Cristo, Senhor nosso.
    \par
    Amém, Jesus, Maria, e José.
  \end{passage}
  \hardbrk
  \begin{passage}[EN]{Hail Holy Queen}
    Hail Holy Queen, Mother of Mercy, our life, our
    sweetness and our hope.
    \par
    To You do we cry, poor banished children of Eve;
    to You do we send up our sighs, mourning and
    weeping in this valley of tears.
    \par
    Turn then, O most Gracious Advocate, Your eyes
    of mercy towards us. And after this, our exile, show unto us the
    blessed fruit of your womb, Jesus.
    \par
    O! Clement, o! loving, o! sweet Virgin Mary!
    Pray for us o Holy Mother of God, that we may
    be worthy of the promises of our Lord Jesus Christ,
    our Lord forever.
    \par
    Amen, Jesus, Mary and Joseph.
  \end{passage}
  \begin{passage}[FI]{Terve, Kuningatar}
    Jumala varjelkoon sinua, oi kuningatar, laupeuden äiti, elämä, ihanuus ja toivomme, terve!
    \par
    Sinua huudamme, Eevan karkotetut lapset. Sinulle huokaamme vaikeroiden ja
    itkien tässä kyynelten laaksossa.
    \par
    Eijaa, puolustajamme, käännä puoleemme laupias katseesi. Ja tämän
    maanpaon jälkeen näytä meille Jeesus. Siunattu olkoon kohtusi hedelmä!
    \par
    Oi armelias! Oi uskollinen! Oi suloinen ikuisesti Neitsyt Maria,
    rukoile Jumalaa puolestamme, kaikkein Pyhin Jumalan Äiti, jotta
    olisimme arvolliset saavuttamaan lupaukset, jotka on antanut
    Herramme Jeesus Kristus, meidän Herramme.
    \par
    Aamen, Jeesus, Maria ja Joosef.
  \end{passage}
\endsong


\beginsong{Encerramento}
  \begin{passage}[PT]{}
    \passagenote*{Dirigente do trabalho pronuncia:}
    Em nome de Deus Pai Todo-Poderoso, da Virgem
    Soberana Mãe, do Patriarca São José e de todos
    os Seres Divinos da Corte Celestial, e com
    a Ordem do nosso Mestre Império Juramidam,
    está encerrado o nosso trabalho, meus irmãos
    e minhas irmãs.
    \textbf{Louvado seja Deus nas alturas!}
    \par
    \passagenote{E todos respondem:}
    Para que sempre seja louvada a nossa Mãe Maria
    Santíssima, sobre toda a humanidade. Amém!
  \end{passage}
  \begin{passage}[EN]{Closing}
    \passagenote*{Leader of the work pronounces:}
    In the name of God the Almighty Father, of the Sovereign
    Virgin Mother, of the Patriarch Saint Joseph and of all
    the Divine Beings of the Celestial Court, and with
    the Order of our Master Governor Juramidam,
    our work is ended, my brothers and my sisters.
    \textbf{Praised be God in the Heights!}
    \par
    \passagenote{And all respond:}
    May our Mother, the Most Holy Mary, be forever
    praised above all humanity. Amen!
  \end{passage}
  \begin{passage}[FI]{Lopetus}
    \passagenote*{Työn komentaja lausuu:}
    %% % This is 'unofficial' Finnish translation by larva,
    %% % commented out to fit on one page
    % Jumalan kaikkivaltiaan Isän, Ylimmäisen Neitsyt-Äidin,
    % Patriarkka Pyhän Joosefin ja kaikkien Taivaallisen Hovin
    % Jumalallisten Olentojen nimissä, ja Mestarimme Valtias Juramidamin
    % valtuuttamina, julistamme työmme päättyneeksi, veljet ja sisaret.
    \ldots\textbf{Ylistetty olkoon Jumala korkeuksissa!}
    \par
    \passagenote{Ja kaikki vastaavat:}
    Ikuisesti olkoon ylistetty Äitimme, Kaikkein Pyhin Maria,
    koko ihmiskuntaa ylempi. Aamen!
  \end{passage}
\endsong


\beginsong{Sinal da Cruz}[tags={bailado, São Miguel, Mesa Branca}]
  \begin{passage}[PT]{}*
    \pup{1}Pelo sinal da Santa Cruz,
    \pup{2}livrai-nos, Deus, nosso Senhor,
    \pup{3}dos nossos inimigos
    \polpar
    \pup{4}Em nome do Pai, \pup{5}do Filho e \pup{6}do Espírito \pup{7}Santo.
    \polpar
    Amém.
  \end{passage}
  \begin{passage}[EN]{Sign of the Cross}*
    \pup{1}By the sign of the Holy Cross,
    \pup{2}deliver us, God, our Lord,
    \pup{3}from our enemies
    \polpar
    \pup{4}In the name of the Father, \pup{5}the Son, and \pup{6}the Holy \pup{7}Spirit.
    \polpar
    Amen.
  \end{passage}
  \begin{passage}[FI]{Ristinmerkki}*
    \pup{1}Pyhällä ristinmerkillä
    \pup{2}Vapauta meidät Jumala, Herramme
    \pup{3}Vihollisistamme
    \polpar
    \pup{4}Isän, \pup{5}Pojan ja \pup{6}Pyhän \pup{7}Hengen nimeen.
    \polpar
    Aamen.
  \end{passage}
%   %% Commented out to fit on one page %%
%   \hardbrk
%   \vspace*{\fill}
%   \begin{passage}[NOTE]{}*
%     While speaking the prayer, synchronously make
%     the sign of the Cross with with your right thumb
%     on your \pup{1}forehead,
%     on your \pup{2}mouth, and
%     on your \pup{3}chest.
%     \polpar
%     Then, with your right hand, touch
%     your \pup{4}forehead,
%     your \pup{5}chest,
%     your \pup{6}left shoulder and \pup{7}right shoulder.
%   \end{passage}
  \vspace*{\fill}
\endsong
