% Santo Daime: Hinos Diversos de Cura
% ===================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Com Fé em Deus}[by={Madr. Júlia},key={C},sks={D, C}]
  \audio{https://www.nossairmandade.com/hymn/690/ComF\%C3\%A9EmDeus}
  \newchords{chords_comfeemdeus_a}\newchords{chords_comfeemdeus_b}
  \mnbeginchorus\memorize[chords_comfeemdeus_a]
    \[^\mn{G}]Com fé \[^\mn{C}]em |\[\mncii{E}{C}C]Deus, eu \[\mnc{E}G7]vou me \[^\mn{D}]levan|\[\mnc{C}C]tar\[\bm] \altchords{\id[1]{(D)}|D A7 |D}
    Com fé \[^\mn{E}]em |\[^\mn{G}\mn{E}]Deus, E\[\mnc{G}G7]le vai me a\[^\mn{F}]ju|\[\mnc{E}C]dar\[\bm] \altchords{| - A7 |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_comfeemdeus_b]
    \[^\mn{C}]Com fé \[^\mn{E}]em |\[\mnc{G}C]Deus \[^\mn{C}]e na Vir\[\mnc{F}F]gem da Concei|\[\mnc{C}C]ção\[\bm] \altchords{|D G |D}
    \[^\mn{G}]Esta \[^\mn{C}]ba|\[\mnc{E}Am]ta\[^\mn{C}]lha nós te\[\mnc{E}G7]mos que a\[^\mn{D}]traves|\[\mnc{C}C]sar\[\bm] \altchords{|Bm A7 |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_comfeemdeus_a]
    Vamos se|^guir, meus ir^mãos, vamos se|^guir^
    No ca|minho da Sem^pre Virgem Ma|^ri^a
  \endchorus\glueverses\beginchorus\replay[chords_comfeemdeus_b]
    Que |^Ela é a ^nossa prote|^to^ra
    E nos |^guia no ca^minho da salva|^ção^
  \endchorus
  \beginchorus\replay[chords_comfeemdeus_a]
    Eu devo a|^mar minha ^Mãe lá nas al|^tu^ras
    Que me en|sina eu sa^ir das amar|^gu^ras
  \endchorus\glueverses\beginchorus\replay[chords_comfeemdeus_b]
    Estou a|^qui, vim cum^prir minha mis|^são^
    Com fé em |^Deus e na Vir^gem da Concei|^ção^
  \endchorus
  \translationoff
  \begin{translation}
    With faith in God, I'm going to stand up
    With faith in God, He's going to help me
    With faith in God and in the Virgin of Conception
    This battle we've to go through
    \nextverse
    Let's follow, my brothers, let's follow
    In the path of the Ever Virgin Mary
    For She is our Protector
    And who guides us in the path of salvation
    \nextverse
    I have to love my Mother up in the heights
    Who teaches me how to leave the sorrows
    I am here, I came to fulfill my mission
    With faith in God and in the Virgin of Conception
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4.
        \repeat volta 2 {
          g8\sectionmark "1.A" g c | e4( c8) c e e d d | c2~ c8 c c e | g4( e8) e g g g f | e2~ e8
        } \break
        \repeat volta 2 {
          c8\sectionmark "1.B" c e | g8. c,16 c8 c f f f f | c2~ c8 g g c | e8. c16 c8 c e e d d | c2~ c8
        } \break
        \repeat volta 2 {
          g8\sectionmark "2.A" g c | e4 c8 c e e d d | c2. c8 e | g8. e16 e8 e g g g f | e2 e8
        } \break
        \repeat volta 2 {
          r8\sectionmark "2.B" e4 | g8. c,16 c8 c f f f f | c2 c4 g8 c | e8. c16 c8 c e e d d | c2~ c8
        } \break
        \repeat volta 2 {
          g8\posectionmark "3.A" g c | e4 c8 c e e d d | c2 c8 c c e | g8. e16 e8 e g g g f | e2 e8
        } \break
        \repeat volta 2 {
          c8\sectionmark "3.B" c e | g4 c,8 c f f f f | c2~ c8 g g c | e8. c16 c8 c e e d d | c2~ c8
        }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Com fé em | Deus __ eu vou me le -- van -- | tar; __
      Com fé em | Deus __ E -- le vai me~a -- ju -- | dar. __
      \set stanza = "1.B"
      Com fé em | Deus e na Vir -- gem da Con -- cei -- | ção; __
      Es -- ta ba -- | ta -- lha nós te -- mos que~a -- tra -- ves -- | sar. __
      \set stanza = "2."
      Va -- mos se -- | guir meus ir -- mãos va -- mos se -- | guir;
      No ca -- | mi -- nho da Sem -- pre Vir -- gem Ma -- | ri -- a.
      \set stanza = "2.B"
      Que | E -- la é a nos -- sa pro -- te -- | to -- ra;
      E nos | gui -- a no ca -- mi -- nho~da sal -- va -- | ção. __
      \set stanza = "3."
      Eu de -- vo~a -- | mar mi -- nha Mãe lá nas al -- | tu -- ras;
      Que me en -- | si -- na eu sa -- ir das a -- mar -- | gu -- ras.
      \set stanza = "3.B"
      Es -- tou a -- | qui vim cum -- prir mi -- nha mis -- | são; __
      Com fé em | Deus e na Vir -- gem da Con -- cei -- | ção. __
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 g:7 | c1 | c2 g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c2 f2 | c1 | a2:m g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c2 g:7 | c1 | c2 g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c2 f2 | c1 | a2:m g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c2 g:7 | c1 | c2 g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c2 f2 | c1 | a2:m g:7 | c2~ c8
      }
    }
    \layout { #(layout-set-staff-size 12) } % to fit on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{A Cura \\ Eu Venho Acrescentar}[by={Padr. Alfredo},key={A},sks={A, B, C}]
  \audio{https://www.nossairmandade.com/hymn/105/EuVenhoAcrescentar}
  \mnbeginchorus\memorize
    \[^\mn{E}]Eu |\[\mnciii{C#}{B}{C#}A]venho \[\mnc{D}E7]a\[^\mn{G#}]cres\[^\mn{B}]cen|\[\mnc{A}A]tar\[\bm] \altchords{\id[1]{(C)}|C G7 |C}
    \[^\mn{C#}]A\[^\mn{E}]qui |\[\mnc{A}(F#m)]dentro \[\mnc{B}(Bm)]des\[^\mn{F#}]te po|\[D]der\[\bm] \altchords{|(Am) (Dm) |F}
    A |\[\mnc{D}(Bm)]cu\[^\mn{F#}]ra \[\mnc{A}D]Deus é quem |\[\mncii{E}{C#}A]dá\[\bm] \altchords{|(Dm) F |C}
    \[^\mn{E}]E |\[\mncii{C#}{B}(F#m)]é \[^\mn{C#}]se \[\mnc{D}E7]bem \[^\mn{G#}]me\[^\mn{B}]re|\[\mnc{A}A]cer\[\bm] \altchords{|(Am) G7 |C}
  \mnendchorus
  \notesoff
  \beginchorus
    E |^é se ^bem mere|^cer^
    Da ver|^dade ^{e do a}|^mor^
    |^Deus e ^a Virgem |^Mãe^
    E |^Je^sus Reden|^tor^
  \endchorus
  \beginchorus
    Patri|^ar^ca São Jo|^sé^
    E |^todos ^seres di|^vi^nos
    Nos |^dão a ^graça da |^vi^da
    São |^João é o ^nosso ca|^mi^nho
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4
      \repeat volta 2 {
        e8(\pomark e8) | \once\slurSolid cis'4( b8)( cis8) d4 gis,8 b8 | a2. cis8 e8
        | a4. a8 b4 fis8 fis8 | fis2( fis4)( fis4)
        | d4. fis8 a4 a8 a8 | e2( cis4) e4
        | cis4( b8)( cis8) d4 gis,8 b8 | a2( a4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu __ _ | ve -- _ nho a -- cres -- cen -- | tar;
        A -- qui | den -- tro des -- te po -- | der; __ _
        A | cu -- ra Deus é quem | dá; __ _
        E | é __ _ se bem me -- re -- | cer. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        E  __ _ | é __ _ se bem me -- re -- | cer;
        Da ver -- | da -- de e do a -- | mor; __ _ _
        | Deus e a Vir -- gem | Mãe; __ _
        E | Je -- _ _ sus Re -- den -- | tor. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Pa -- tri -- | ar -- _ _ ca São Jo -- | sé;
        E __ _ | to -- dos se -- res di -- | vi -- nos;
        Nos | dão a gra -- ça da | vi -- da;
        São | Jo -- ão é~o nos -- so ca -- | mi -- nho.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a2 e2:7 | a1 | \parenthesize fis2:m \parenthesize b2:m | d1
        | \parenthesize b2:m d2 | a1 | \parenthesize fis2:m e:7 | a2.
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I come to add here within this power
    Healing, God is who gives it and if one really deserves it
    \nextverse
    And if one really deserves it, of truth and of love
    God and the Virgin Mother and Jesus the Redeemer
    \nextverse
    The Patriarch Saint Joseph and all divine beings
    Give us the grace of life, Saint John is our path
  \end{translation}
\endsong


\beginsong{Peço a Vós Minha Firmeza \\ Meu Deus}[by={Padr. Valdete},key={Am},sks={Bm, Am},tags={2x}]
  \audio{https://www.nossairmandade.com/hymn/154/MeuDeus}
  \newchords{chords_pecoavos_a}\newchords{chords_pecoavos_b}
  \mnbeginchorus\memorize[chords_pecoavos_a]
    \[^\mn{E}]Meu |\[\mnc{A}Am]Deus,\[\bm] \[^\mn{B}]meu |\[\mncii{G#}{E}E]Pai,\[\bm] minha |\[\mncii{D}{B}E7/D]Mãe \[\bm] \altchords{\id[1]{(Bm)}|Bm |F\# |F\#7/E}
    Eu pe|\[\mnc{E}E7]ço \[^\mn{D}]que \[\mnc{C}(C)]Vós \[^\mn{B}]me |\[Am]cu\[\bmc\mn{A}]re \altchords{|F\#7 (D) |Bm}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_pecoavos_b]
    \[^\mn{A}]A \[^\mn{C}]ma|\[\mncii{E}{D}Am/E]téria \[\mnc{B}(Bm7&5)]das \[^\mn{A}]do|\[\mnc{G#}E]en\[^\mn{E}]ças\[\bm] \altchords{|Bm/F\# (C\#m7b5) |F\#}
    E \[^\mn{G#}]o \[^\mn{B}]es|\[\mnc{E}E7]píri\[^\mn{D}]to \[\bmc\mn{B}]do \[^\mn{G#}]es|\[\mnc{A}Am]cu\[\bm]ro \altchords{|F\#7 |Bm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_pecoavos_a]
    Meu |^Deus,^ meu |^Pai,^ minha |^Mãe ^
    Eu peço |^para Vós ^me cu|^rar^
  \endchorus\glueverses\beginchorus\replay[chords_pecoavos_b]
    A ma|^téria ^{das do}|^enças^
    O es|^pírito um ^bom lu|^gar^
  \endchorus
  \beginchorus\replay[chords_pecoavos_a]
    Meu |^Deus,^ meu |^Pai,^ minha |^Mãe ^
    Eu sei que |^Vós já ^me cu|^rou^
  \endchorus\glueverses\beginchorus\replay[chords_pecoavos_b]
    Peço a |^Vós mi^{nha fir}|^meza^
    Para |^sempre eu ^dar va|^lor ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \repeat volta 2 {
        e4\pomark | a2. b4 | \once\slurSolid gis4( e2) e8 e8
        | \once\slurSolid d4( b4.)( b8) b8 b8 | e4( e8) d8 c4. b8 | b4( a2)
      }
      \repeat volta 2 {
        a8 c8 | e4. d8 b4. a8 | gis4 e4.( e8) gis8 b8
        | e4 e8 d8 b4. gis8 | a2( a4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Meu | Deus, meu | Pai, __ _ mi -- nha | Mãe; __ _ _
        Eu pe -- | ço __ _ que Vós me | cu -- re.
      }
      \repeat volta 2 {
        A ma -- | té -- ria das do -- | en -- ças;
        E o es -- | pí -- ri -- to do es -- | cu -- ro.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Meu | Deus, meu | Pai, __ _ mi -- nha | Mãe; __ _
        Eu pe -- ço | pa -- ra Vós me cu -- | rar. __ _
      }
      \repeat volta 2 {
        A ma -- | té -- ria das do -- | en -- ças; __ _
        O es -- | pí -- ri -- to~um bom lu -- | gar. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Meu | Deus, meu | Pai, __ _ mi -- nha | Mãe; __ _
        Eu sei que | Vós __ _ já me cu -- | rou. __ _
      }
      \repeat volta 2 {
        Pe -- ço~a | Vós mi -- nha fir -- | me -- za; __ _
        Pa -- ra | sem -- pre eu dar va -- | lor. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a1:m | e | e:7/d | e2:7 \parenthesize c2 | a2.:m
      }
      \repeat volta 2 {
        s4 | a2:m/e \parenthesize b2:m7.5- | e1 | e:7 | a2.:m
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    My God, My Father, My Mother, I ask that you cure me
    The body of illness, and the spirit of darkness
    \nextverse
    My God, My Father, My Mother, I ask for you to heal me
    The body of sickness, (and to give my) spirit a good place
    \nextverse
    My God, My Father, My Mother, I know that you've already healed me
    I ask you for my firmness, so that I always give worth
  \end{translation}
\endsong

