% Santo Daime: Nova Era (Padr. Alfredo)
% =====================================
%
\audio[title={santodaime.org}]{https://hinos.santodaime.org/acervo/padrinho-alfredo/nova-era}
\audio[title={Estudo Fino}]{https://estudofino.org/nova-era}
\audio[title={Nossa Irmandade}]{https://nossairmandade.com/hinario/8/NovaEra}
\audio[title={SoundCloud}]{https://soundcloud.com/canaljagube/sets/hinario-nova-era_oficial}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Nova Era}[by={Padr. Alfredo}, key={C}, gk={C, C--D}, off={Nena}]
  \audio[key=Am]{https://soundcloud.com/canaljagube/01-nova-era?in=canaljagube/sets/hinario-nova-era_oficial}
  \audio[]{https://nossairmandade.com/hymn/103/NovaEra}
  \mnbeginchorus\memorize
    \[^\mn{C}]Quem \[^\mn{B}]be|\[\mnc{A}Am]leza \[^\mn{G}]no \[\bmc\mn{C}]u\[^\mn{E}]ni|\[\mnc{G}C]ver\[^\mn{E}]so
    \[\mnc{A}(Am)]Meu \[^\mn{E}]Pai |\[\mnc{G}G]es\[^\mn{E}]tá \[\mnc{A}F]me \[^\mn{G}]gui|\[\mnc{C}C]an\[\bm]do
  \mnendchorus
  \notesoff
  \beginchorus
    E quanto |^mais eu ^me en|^trego \altchords{\id[1]{(D)}|Bm |D}
    ^Mais E|^le vai ^me lim|^pan^do \altchords{(Bm) |A G |D}
  \endchorus
  \beginchorus
    Eu vou se|^guindo, ^ensi|^nando\jw
    O ^{que meu} |^Pai dei^xou na |^Ter^ra
  \endchorus
  \beginchorus
    Na co|^lheita ^de ir|^mãos
    Quem ^vem com|^por a ^Nova |^E^ra
  \endchorus
  \beginchorus
    Eu con|^vido\jw os ^meus ir|^mãos
    Se ^ale|^grar na ^nossa |^fes^ta
  \endchorus
  \beginchorus
    Esque|^cer a ^ilu|^são
    E ^{se fir}|^mar bem ^na flo|^res^ta
  \endchorus
  \beginchorus
    Na flo|^resta ^temos |^tudo
    ^Ela, |^Mamãe ^e Pa|^pai ^
  \endchorus
  \beginchorus
    Toda |^fonte ^de ri|^queza;\jw
    A ^Natu|^reza\jw e ^muito |^mais ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "Nova Era"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize c8 c \pomark b | a4( a8) g c4. e8 | g4. e8 a4. e8
        | g4. e8 a4. g8 | c,2( c8)
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        "" Quem be -- | le -- za no u -- ni -- | ver -- so;
        Meu Pai | es -- tá me gui -- | an -- do.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        E quan -- to | mais "" eu me en -- | tre -- go;
        Mais E -- | le vai me lim -- | pan -- do.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Eu vou se -- | guin _ -- do, en -- si -- | nan -- do;~O
        que meu | Pai dei -- xou na | Ter -- ra.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        "" Na co -- | lhei _ -- ta de ir -- | mãos;
        Quem vem com -- | por a No -- va | E -- ra.
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \repeat volta 2 {
        "" Eu con -- | vi _ -- do~os meus ir -- | mãos;
        Se a -- le -- | grar na nos -- sa | fes -- ta.
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      \repeat volta 2 {
        "" Es -- que -- | cer __ _ a i -- lu -- | são;
        E se fir -- | mar bem na flo -- | res -- ta.
      }
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7."
      \repeat volta 2 {
        "" Na flo -- | res _ -- ta te -- mos | tu -- do;
        E -- la, | Ma -- mãe e Pa -- | pai. __ _
      }
    }
    theLyricsEight = \lyricmode {
      \set stanza = "8."
      \repeat volta 2 {
        "" To -- da | fon _ -- te de ri -- | que -- za;~A % This is seen with and without 'a', but apparently with 'a' is more correct grammatically
        Na -- tu -- | re -- za~e mui -- to | mais. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1:m | c2 \parenthesize a:m
        | g2 f | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    What beauty in the universe; my Father is guiding me
    And the more I surrender myself, the more He keeps cleansing me
    \nextverse
    I keep following and teaching what my Father left on Earth
    In the gathering of the brothers and sisters, who come to compose the New Age
    \nextverse
    I invite my brothers and sisters to be joyful in our celebration
    To forget the illusion and firm yourselves well in the forest
    \nextverse
    In the forest we have everything: Her, Mother and Father
    Every source of wealth is Nature and so much more
  \end{translation}
\endsong


\beginsong{Demonstração}[by={Padr. Alfredo}, key={A}, gk={A, G\shrp{}--A}, off={Aucineide}]
  \audio{https://nossairmandade.com/hymn/104/Demonstra\%C3\%A7\%C3\%A3o}
  \audio[key=G]{https://soundcloud.com/canaljagube/02-demonstracao?in=canaljagube/sets/hinario-nova-era_oficial}
  \newchords{chords_demonstracao_a}
  \newchords{chords_demonstracao_b}
  \newchords{chords_demonstracao_c}
  % verse 1
  \mnbeginchorus\memorize[chords_demonstracao_a]
    \[^\mn{E}]Eu \[^\mn{D}]a|\[\mnc{C#}A]pren\[^\mn{B}]di \[\mnc{D}E7]nes\[^\mn{C#}]te |\[\mnc{A}A]mundo \[\bmc\mn{C#}]não \[^\mn{E}]fa|\[\mnc{A}F#m]zer \[^\mn{F#}]mal \[\bmc\mnc{B}]a nin|\[\mnc{F#}D]guém\[\bm]
    \[^\mnc{D}]E de|\[\mnc{B}Bm]sejo \[\bm]de\[^\mn{A}]mons|\[\mnc{G#}E]trar \[\bmc\mn{E}]be\[^\mn{G#}]le|zas \[^\mn{F#}]que \[\mnc{A}E7]meu \[^\mn{G#}]Pai |\[\mnc{E}A]tem \[\bm]
  \mnendchorus\glueverses\mnbeginverse\memorize[chords_demonstracao_b]
    \[^\mn{E}]Es\[^\mn{D}]te |\[\mnc{C#}A]San\[^\mn{B}]to \[\mnc{D}E7]So\[^\mn{C#}]be|\[\mnc{A}A]rano \[\bmc\mn{C#}]de \[^\mn{E}]Po|\[\mnc{A}F#m]der \[^\mn{F#}]U\[\bmc\mn{B}]niver|\[\mnc{F#}D]sal \[\bm]
  \mnendverse\glueverses\mnbeginchorus\memorize[chords_demonstracao_c]
    \[^\mauii{E}{D}]Quem des|\[\mauc{D}Bm]troi \[^\mn{F#}]a \[\bmc\mn{B}]na\[^\mn{A}]tu|\[A]re\[^\mn{E}]za\jw es\[\bmc\mn{C#}]tá \[^\mn{E}]fe|\[\mnc{D}Bm]din\[^\mn{B}]do\jw o \[\mnc{G#}E7]nos\[^\mn{B}]so |\[\mnc{A}A]Pai \[\bm]
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_demonstracao_a]
    O nosso |^Pai e ^nossa |^Mãe ^nos o|^lha to^do mo|^men^to
    Nos dá |^tudo\jw em ^abun|^dância ^a sa|úde\jw e\jw o ^ali|^men^to
    \endchorus\glueverses\beginverse\replay[chords_demonstracao_b]
    Quem não |^reco^nhece\jw a |^força ^do Di|^vino\jw O^nipo|^ten^te
    \endverse\glueverses\beginchorus\replay[chords_demonstracao_c]
    Está vi|^vendo ^no es|^curo\jw e ^cami|^nhando\jw in^consci|^en^te
  \endchorus
  % verse 3
  \beginchorus\replay[chords_demonstracao_a]
    Se a|^lertem ^toda |^gente ^que ha|^bita\jw a^qui na |^ter^ra
    Olhem\jw o |^sol e ^os pla|^netas: ^neles |não e^xiste |^guer^ra
    \endchorus\glueverses\beginverse\replay[chords_demonstracao_b]
    Quem tra|^balha ^neste |^mundo ^sem ao |^Mestre ^respei|^tar ^
    \endverse\glueverses\beginchorus\replay[chords_demonstracao_c]
    Ele |^dá a ^disci|^plina\jw e ^muda |^pra ou^tro lu|^gar ^
  \endchorus
  \ifchorded\ifshowaltchords\small % for altchords (G)
    \beginverse % put all glued verses into one env.
      \altchords{\id[1]{(G)}|G D7 |G |Em |C}
      \altchords{|Am |D | - D7 |G}
      \altchords{|G D7 |G |Em |C}
      \altchords{|Am |G |Am D7 |G}
    \endverse
  \fi\fi
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "Demonstração"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4.
      \mark \markup \with-color #darkgreen \italic "Final: toque tudo"
      \sectionLabel "A"
      \repeat volta 2 {
        \parenthesize e8 \pomark e d
        | cis4 b d cis | a4.( a8) cis4 e
        | a fis b b | fis2( 4)
        d8 d
        | b4 b b a | gis4.( 8) e'4 gis
        | gis fis a gis | e2( 8)
      }
      \break
      \sectionLabel "B"
      r8 e8 d
      | cis4 b d cis | a4. a8 cis4 e
      | a fis b b | fis2( 8)
      \break
      \sectionLabel "C"
      \repeat volta 2 {
        << \parenthesize d8 \altmark "ii" \single\altcol \parenthesize e >> << d \single\altcol e >> << d \single\altcol e >>
        | d4 fis b a | a e8 e cis4 e
        | d b gis b | a2( 8)
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        "" Eu a -- | pren -- di nes -- te | mun -- do Não fa -- | zer mal a nin -- | guém; __ _
        E de -- | se -- jo de -- mons -- | trar __ _ Be -- le -- | zas que meu Pai | tem. __ _
      }
      \set stanza = "1.B"
      Es -- te | San -- to So -- be -- | ra -- no De Po -- | der U -- ni -- ver -- | sal. __ _
      \set stanza = "1.C"
      \repeat volta 2 {
        "" Quem des -- | troi a na -- tu -- | re -- za Es -- tá fe -- | din -- do~o nos -- so | Pai. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        O nos -- so | Pai e nos -- sa | Mãe __ _ Nos o -- | lha to -- do mo -- | men -- to;
        Nos dá | tu -- do~em a -- bun -- | dân -- cia: A sa -- | ú -- de~e~o a -- li -- | men -- to.
      }
      \set stanza = "2.B"
      Quem não | re -- co -- nhe -- ce~a | for -- ça Do Di -- | vi -- no~O -- ni -- po -- | ten -- te.
      \set stanza = "2.C"
      \repeat volta 2 {
        Es -- tá vi -- | ven -- do no es -- | cu -- ro E ca -- mi -- | nhan -- do~in -- con -- sci -- | en -- te.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        "" Se a -- | ler -- tem to -- da | gen -- te Que ha -- | bi -- ta~a -- qui na | ter -- ra;
        O -- lhem~o | sol e os pla -- | ne -- tas: Ne -- les | não e -- xis -- te | guer -- ra.
      }
      \set stanza = "3.B"
      Quem tra -- | ba -- lha nes -- te | mun -- do Sem ao | Mes -- tre res -- pei -- | tar; __ _
      \set stanza = "3.C"
      \repeat volta 2 {
        "" E -- le | dá a dis -- ci -- | pli -- na E mu -- da | pra ou -- tro lu -- | gar. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4.
        | a2 e2:7 | a1
        | fis:m | d
        | b:m | e
        | e2 e2:7 | a2~8
      }
      s4.
      | a2 e2:7 | a1
      | fis:m | d2~8
      \repeat volta 2 {
        s4.
        | b1:m | a
        | b2:m e:7 | a2~8
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    I learned in this world not to harm anyone
    And I wish to demonstrate beauties that my Father has
    This Sovereign Saint of Universal Power
    Those who destroy nature are hurting our Father
    \nextverse
    Our Father and our Mother watch us every moment
    Give us everything in abundance: health and sustenance
    Whoever doesn't recognize the force of the Divine Omnipotent
    Is living in darkness and walking unconsciously
    \nextverse
    Awaken everybody who dwells here on earth
    Look at the sun and the planets: in them war doesn't exist
    Whoever works in this world without respecting the Master
    He gives them discipline and moves them to another place
  \end{translation}
\endsong


\beginsong{A Cura \\ Eu Venho Acrescentar}[by={Padr. Alfredo}, off={Liza}, key={A}, gk={A, A\flt{}--A}]
  % Also in songs_cura_diversos.tex
  \audio{https://www.nossairmandade.com/hymn/105/EuVenhoAcrescentar}
  \audio[key=A]{https://soundcloud.com/canaljagube/03-eu-venho-acrescentar?in=canaljagube/sets/hinario-nova-era_oficial}
  \mnbeginchorus\memorize
    \[^\mn{E}]Eu |\[\mnciii{C#}{B}{C#}A]venho \[\mnc{D}E7]a\[^\mn{G#}]cres\[^\mn{B}]cen|\[\mnc{A}A]tar\[\bm]{} \altchords{\id[1]{(B)}|B F\shrp{}7 |B}
    \[^\mn{C#}]A\[^\mn{E}]qui |\[\mnc{A}(F#m)]dentro \[\mnc{B}(Bm)]des\[^\mn{F#}]te po|\[D]der\[\bm]{} \altchords{|(G\shrp{}m) (C\shrp{}m) |E}
    A |\[\mnc{D}(Bm)]cu\[^\mn{F#}]ra \[\mnc{A}D]Deus é quem |\[\mnc{E}A]dá\[\bmc\mn{C#}]{} \altchords{|(C\shrp{}m) E |B}
    \[^\mn{E}]E |\[\mncii{C#}{B}(F#m)]é \[^\mn{C#}]se \[\mnc{D}E7]bem \[^\mn{G#}]me\[^\mn{B}]re|\[\mnc{A}A]cer\[\bm]{} \altchords{|(G\shrp{}m) F\shrp{}7 |B}
  \mnendchorus
  \notesoff
  \beginchorus
    E |^é se ^bem mere|^cer^
    Da ver|^dade ^{e do a}|^mor^
    |^Deus e ^a Virgem |^Mãe^
    E |^Je^sus Reden|^tor^
  \endchorus
  \beginchorus
    Patri|^ar^ca São Jo|^sé^ \altchords{\id[2]{(C)}|C G7 |C}
    E |^todos ^seres di|^vi^nos \altchords{|(Am) (Dm) |F}
    Nos |^dão a ^graça da |^vi^da \altchords{|(Dm) F |C}
    São |^João é o ^nosso ca|^mi^nho \altchords{|(Am) G7 |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "A Cura"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative e' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4
      \repeat volta 2 {
        e8(\pomark e8) | \once\slurSolid cis'4( b8)( cis8) d4 gis,8 b8 | a2. cis8 e8
        | a4. a8 b4 fis8 fis8 | fis2( fis4)( fis4)
        | d4. fis8 a4 a8 a8 | e2( cis4) e4
        | cis4( b8)( cis8) d4 gis,8 b8 | a2( a4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu __ _ | ve -- _ nho a -- cres -- cen -- | tar;
        A -- qui | den -- tro des -- te po -- | der; __ _
        A | cu -- ra Deus é quem | dá; __ _
        E | é __ _ se bem me -- re -- | cer. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        E  __ _ | é __ _ se bem me -- re -- | cer;
        Da ver -- | da -- de e do a -- | mor; __ _ _
        | Deus e a Vir -- gem | Mãe; __ _
        E | Je -- _ _ sus Re -- den -- | tor. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Pa -- tri -- | ar -- _ _ ca São Jo -- | sé;
        E __ _ | to -- dos se -- res di -- | vi -- nos;
        Nos | dão a gra -- ça da | vi -- da;
        São | Jo -- ão é~o nos -- so ca -- | mi -- nho.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a2 e2:7 | a1 | \parenthesize fis2:m \parenthesize b2:m | d1
        | \parenthesize b2:m d2 | a1 | \parenthesize fis2:m e:7 | a2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I come to add here within this power
    Healing, God is who gives it and if one really deserves it
    \nextverse
    And if one really deserves it, of truth and of love
    God and the Virgin Mother and Jesus the Redeemer
    \nextverse
    The Patriarch Saint Joseph and all divine beings
    Give us the grace of life, Saint John is our path
  \end{translation}
\endsong


\beginsong{Calma \\ Sou Filho do Meu Pai}[by={Padr. Alfredo}, off={Akira}, key={A}, gk={A, A\flt{}--A}]
  \audio[key=G]{https://soundcloud.com/canaljagube/04-a-verdade-e-uma-so?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio[]{https://nossairmandade.com/hymn/106/SouFilhoDoMeuPai}
  \newchords{chords_calma_a}\newchords{chords_calma_b}
  % verse 1
  \mnbeginchorus\memorize[chords_calma_a]
    \[^\mn{E}]Sou |\[\mnc{A}A]filho \[^\mn{C#}]do \[^\mn{E}]meu \[\bmc\mn{A}]Pai, e \[^\mn{G#}]meu |\[\mnc{B}Bm]Pai é \[^\mn{F#}]quem me \[\mnc{E}E]dá
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_calma_b]
    \[^\mn{C#}]Para |\[\mnc{F#}F#m]Deus tu\[^\mn{E}]{do\jw está} \[\mnc{B}Bm]feito, \[^\mn{G#}]não \[^\mn{B}]pre|\[\mnc{E}E]cisa \[^\mn{B}]{se\jw a}\[^\mn{C#}]ve\[\mnc{A}A]xar
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_calma_a]
    Va|^mos seguir com ^calma, que com |^calma Deus es^tá
  \endchorus\glueverses\beginchorus\replay[chords_calma_b]
    |^No céu e nos ^astros, na flo|^resta, vento\jw e ^mar
  \endchorus
  % verse 3
  \beginchorus\replay[chords_calma_a]
    No |^homem na mu^lher, e em |^toda cria^ção \altchords{\id[1]{(G)}|G |Am D}
  \endchorus\glueverses\beginchorus\replay[chords_calma_b]
    Deixa |^tudo\jw aconte^cer no po|^der de São Jo^ão \altchords{|Em Am |D G}
  \endchorus
  % verse 4
  \beginchorus\replay[chords_calma_a]
    Deste |^lado e do ^outro, a ver|^dade\jw é uma ^só
  \endchorus\glueverses\beginchorus\replay[chords_calma_b]
    O meu |^Mestre\jw está se^guro, junto |^com\jw a força mai^or
  \endchorus
  % verse 5
  \beginchorus\replay[chords_calma_a]
    Esta |^é uma cla^reza que me |^veio do as^tral \altchords{\id[2]{(B)}|B |C\shrp{}m F\shrp{}}
  \endchorus\glueverses\beginchorus\replay[chords_calma_b]
    |^Andar direi^tinho na dou|^trina do meu ^Pai \altchords{|G\shrp{}m C\shrp{}m |F\shrp{} B}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "Calma"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4
      \mark \markup \with-color #darkgreen \italic "Final: toque tudo"
      \sectionLabel "A"
      \repeat volta 2 {
        \parenthesize e8 \pomark e | a,8 a cis e a8( a) a gis | b b fis fis e4
      }
      \sectionLabel "B"
      \repeat volta 2 {
        \parenthesize cis8 \parenthesize cis | fis fis e e b( b) gis b | e e b cis a4
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        "" Sou | fi -- lho do meu Pai, __ _
        E meu | Pai é quem me dá.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Pa -- ra | Deus tu -- do~es -- tá fei -- to,
        Não pre -- | ci -- sa se~a -- ve -- xar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        "" Va -- | mos se -- guir com cal -- ma,
        Que com | cal -- ma Deus es -- tá
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        "" "" | No céu e nos as -- tros,
        Na flo -- | res -- ta, ven -- to~e mar.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        "" No | ho -- mem na mu -- lher, __ _
        E em | to -- da cri -- a -- ção.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Dei -- xa | tu -- do~a -- con -- te -- cer, __ _
        No po -- | der de São Jo -- ão.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Des -- te | la -- do e do ou -- tro,
        A ver -- | da -- de~é u -- ma só.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        O meu | Mes -- tre~es -- tá se -- gu -- ro,
        Jun -- to | com~a for -- ça mai -- or.
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        Es -- ta | é u -- ma cla -- re -- za,
        Que me | vei -- o do as -- tral.
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        "" "" | An -- dar di -- rei -- ti -- nho,
        Na dou -- | tri -- na do meu Pai.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a1 | b2:m e4
      }
      \repeat volta 2 {
        s4 | fis2:m b:m | e:7 a4
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I am a son of my Father, and my Father is who gives to me
    For God all is done, there is no need to hurry
    \nextverse
    Let's follow with calmness, because with calmness God is
    In the sky and in the astral bodies, in the forest, wind and sea
    \nextverse
    In man in woman, and in all of creation
    He lets let everything happen in the power of St. John
    \nextverse
    On this side and the other, the truth is just one
    My Master is secure, together with the higher force
    \nextverse
    This is a clarity that came to me from the astral
    To walk straight and narrow in the doctrine of my Father
  \end{translation}
\endsong


\beginsong{Pai dos Pais}[by={Padr. Alfredo}, off={Alvino}, key={C}, gk={D, C--E}]
  \audio[key=C]{https://soundcloud.com/canaljagube/05-cuidado-do-padrinho?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio[]{https://nossairmandade.com/hymn/107/PaiDosPais}
  \newchords{chords_paidospais_a}\newchords{chords_paidospais_b}
  \transpose{-2}
  % verse 1
  \beginchorus\memorize[chords_paidospais_a]
    \[^\mn{D}]Quan\[^\mn{E}]to |\[\mnc{F#}D]mais \[^\mn{A}]an\[\mnc{E}A]do \[^\mn{D}]mais |\[\mnc{B}Bm]ve\[^\mn{A}]jo
    \[\bmc\mn{D}]E a|viso aos \[\bmc\mn{E}]meus \[^\mn{D}]ir|\[\mnc{F#}D]mãos \[\bm]
  \endchorus\glueverses\beginchorus\memorize[chords_paidospais_b]
    \[^\mn{D}]Cui|\[\mnc{B}Bm]da\[\bmc\mn{A}]do, \[^\mn{D}]cui|\[\mnc{F#}D]da\[\bm]do
    \[^\mn{D}]Do \[^\mn{E}]Pa|\[^\mn{F#}]drinho \[^\mn{A}]Se\[\mnc{E}A]bas\[^\mn{F#}]ti|\[\mnc{D}D]ão \[\bm]
  \endchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_paidospais_a]
    O cui|^dado ^do Pa|^drinho\jw \altchords{\id[1]{(D)}|D A |Bm}
    É ^um a|viso ^de ir|^mão ^ \altchords{| - |D}
  \endchorus\glueverses\beginchorus\replay[chords_paidospais_b]
    Um, |^um, ^um, hum, |^hum ^ \altchords{|Bm |D}
    Se a|\noteson{}cor\[\mnd{A}]dem\notesoff{} ^meus ir|^mãos ^ \altchords{| - A |C}
  \endchorus
  % verse 3
  \beginchorus\replay[chords_paidospais_a]
    Salve\jw o |^grande ^Pai dos |^Pais
    ^Viva\jw a |Nossa ^Virgem |^Mãe ^
  \endchorus\glueverses\beginchorus\noteson
    Viva |\[Bm]nós \[\mnd{A}]co\[\bmc\mnd{D}]mo seus |\[D]fi\[\bm]lhos
    Viva |nos\[\mnd{A}]sa \[A]salva|\[D]ção \[\bm]
  \endchorus
  % verse 4
  \beginchorus\replay[chords_paidospais_a]
    Para |^ser fi^lho de |^Deus \altchords{\id[2]{(E)}|E B |C\shrp{}m}
    ^É pre|ciso ^todo\jw a|^mor ^ \altchords{| - |E}
  \endchorus\glueverses\beginchorus\noteson
    Ser fi|\[Bm]el \[\mnd{A}]{e\jw o}\[\bmc\mnd{D}]bedi|\[D]en\[\bm]te \altchords{|C\shrp{}m |E}
    A Jesus |Cris\[\mnd{A}]to \[A]Reden|\[D]tor \[\bm] \altchords{| - B |E}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "Pai dos Pais"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \transpose d c \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 4
      \sectionLabel "A"
      \repeat volta 2 {
        d8 \pomark e | fis4 a e d | b( a) d d | d d8 \parenthesize d e4 d | fis2.
      } \break
      \sectionLabel "B"
      \repeat volta 2 {
        d8( d8) | b4. \altcol \parenthesize a8 \altmark "3. & 4." << a4 \single\altcol d >> d | fis2( fis8) \parenthesize d d e | fis4 << fis8 \single\altcol a \altmark "2., 3., 4." \single\altcol ( >> a) e4 fis | d2.
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Quan -- to | mais an -- do mais | ve -- jo;
        E a -- | vi -- so aos meus ir -- | mãos.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Cui _ -- | da _ -- do, cui -- | da -- do;
        "" Do Pa -- | dri -- nho Se -- bas -- ti -- | ão.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        O cui -- | da -- do do Pa -- | dri -- nho;~É
        um a -- | vi -- so "" de ir -- | mão.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Um, __ _ | um, "" um, hum, | hum; __ _
        "" Se a -- | cor -- \altcol dem __ _ meus ir -- | mãos.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Sal -- ve~o | gran -- de Pai dos | Pais; __ _
        Vi -- va~a | Nos -- sa "" Vir -- gem | Mãe.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Vi -- va | nós \altcol co -- \altcol mo seus | fi -- lhos;
        "" Vi -- va | nos -- \altcol sa __ _ sal -- va -- | ção.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Pa -- ra | ser fi -- lho de | Deus; __ _
        É pre -- | ci -- so "" to -- do~a -- | mor.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Ser fi -- | el \altcol e~o -- \altcol be -- di -- | en -- te;
        A Je -- sus | Cris -- \altcol to __ _ Re -- den -- | tor.
      }
    }
    theChords = \transpose d c \chordmode {
      \repeat volta 2 {
        s4 | d2 a2 | b1:m | b:m | d2.
      }
      \repeat volta 2 {
        s4 | b1:m | d | d2 a | d2.
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    The more I walk the more I see, and I warn my brothers and sisters
    The warning, the warning, of Padrinho Sebastião
    \nextverse
    The warning of Padrinho is a warning from a brother
    Um, um, um, hum, hum, wake up my brothers and sisters
    \nextverse
    Hail the great Father of fathers, viva our Virgin Mother
    Viva us as Your children, viva our salvation
    \nextverse
    To be a child of God one needs complete love
    To be faithful and obedient to Jesus Christ the Redeemer
  \end{translation}
\endsong


\beginsong{O Barquinho}[by={Padr. Alfredo}, off={Artur}, key={Bm}, gk={Cm, (Bm)--(Cm)}]
  \audio[]{https://nossairmandade.com/hymn/108/OBarquinho}
  \audio[key=Am]{https://soundcloud.com/canaljagube/06-barquinho?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \transpose{2}
  \newchords{chords_barquinho_a}\newchords{chords_barquinho_b}
  % verse 1
  \beginchorus\memorize[chords_barquinho_a]
    \[^\mn{E}]Meu |\[\mnc{A}Am]Pai \[^\mn{C}]é \[\bmc\mn{B}]tu\[^\mn{C}]{do\jw e} |\[^\mn{A}]to\[\bm]do, \[^\mn{C}]meu |\[^\mn{A}]Pai \[^\mn{C}]não \[\bmc\mn{A}]é \[^\mn{C}]ru|\[\mnc{E}E]im \[\bm]
  \endchorus\glueverses
  \beginchorus\memorize[chords_barquinho_b]
    \[^\mn{E}]Eu a|\[\mnc{A}Am]cre\[^\mn{E}]di\[\bmc\mn{C}]{to\jw em} \[^\mn{B}]meu |\[^\mn{A}]Pai \[\bm]e \[^\mn{C}]a|\[^\mn{A}]cre\[^\mn{C}]di\[\bmc\mn{A}]to \[^\mn{C}]em |\[\mnc{E}E]mim \[\bm]
    Sou |\[\mnc{A}Am]fi\[^\mn{E}]lho \[\bmc\mn{C}]da \[^\mn{B}]Ra|\[^\mn{A}]inha \[\bmc\mn{E}]e \[^\mn{C}]vi|\[\mnc{B}E]vo \[^\mn{D}]nes\[\mnc{C}E7]te \[^\mn{B}]jar|\[\mnc{A}Am]dim \[\bm]
  \endchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_barquinho_a]
    Na|^vego ^nesta |força ^do su|premo ^Cria|^dor ^ \altchords{\id[1]{(Am)}|Am | - | - |E}
  \endchorus\glueverses\beginchorus\replay[chords_barquinho_b]
    No bar|^quinho ^da fir|meza, ^da jus|tiça\jw e ^do a|^mor ^ \altchords{|Am | - | - |E}
    Com |^mamãe ^natu|reza, ^mãe do |^nosso ^Salva|^dor ^ \altchords{|Am | - |E E7 |Am}
  \endchorus
  % verse 3
  \beginchorus\replay[chords_barquinho_a]
    No |^meio ^destas |ondas ^me le|vas a ^conhe|^cer ^ \altchords{\id[2]{(Cm)}|Cm | - | - |G}
  \endchorus\glueverses\beginchorus\replay[chords_barquinho_b]
    O |^poder ^destas |ilhas ^no seu |divi^no po|^der ^ \altchords{|Cm | - | - |G}
    Terre|^motos ^e vul|cões ^ faz |^tudo\jw es^treme|^cer ^ \altchords{|Cm | - |G G7 |Cm}
  \endchorus
  % verse 4
  \beginchorus\replay[chords_barquinho_a]
    Só a |^força ^do meu |Pai é ^quem faz |tudo ^renas|^cer ^ \altchords{\id[3]{(Dm)}|Dm | - | - |A}
  \endchorus\glueverses\beginchorus\replay[chords_barquinho_b]
    O |^Santo Po^der da |vida ^se trans|forma\jw e ^faz cres|^cer ^ \altchords{|Dm | - | - |A}
    Viva |^terra, ^viva\jw o |mar, e ^viva |^o a^manhe|^cer \altchords{|Dm | - |A A7 |Dm}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "O Barquinho"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \transpose a b \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \sectionLabel "A"
      \repeat volta 2 {
        e8( \pomark e) | a4 c b c | a4.( a8) a4 c | a c a c | e2.
      }
      \sectionLabel "B"
      \repeat volta 2 {
        e8( e) | a4 e8( e) c4 b | a4.( a8) a4 c | a c a c | e2.
        e8( e) | a4 e c b | a4.( a8) \parenthesize e4 c' | b d c b | a2.
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Meu __ _ | Pai é tu -- do~e | to _ -- do
        Meu | Pai não é ru -- | im.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Eu a -- | cre -- di _ -- to~em meu | Pai __ _
        E a -- | cre -- di -- to em | mim;
        Sou __ _ | fi -- lho da Ra -- | i -- nha
        E vi -- | vo nes -- te jar -- | dim.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Na _ -- | ve -- go nes -- ta | for -- ça
        Do su -- | pre -- mo Cri -- a -- | dor.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        No bar -- | qui -- nho __ _ da fir -- | me -- za
        Da jus -- | ti -- ça~e do a -- | mor;
        Com __ _ | ma -- mãe na -- tu -- | re -- za
        Mãe do | nos -- so Sal -- va -- | dor.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        No __ _ | mei -- o des -- tas | on -- das
        Me le -- | vas a co -- nhe -- | cer.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        O __ _ | po -- der __ _ des -- tas | i -- lhas 
        No seu | di -- vi -- no po -- | der;
        Ter -- re -- | mo -- tos e vul -- | cões __ _
        "" Faz | tu -- do~es -- tre -- me -- | cer.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Só a | for -- ça do meu | Pai
        É quem faz | tu -- do re -- nas -- | cer.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        O __ _ | San -- to Po -- der da | vi -- da
        Se trans -- | for -- ma~e faz cres -- | cer;
        Vi -- va | ter -- ra, vi -- va~o | mar
        E vi -- va | o a -- ma -- nhe -- | cer.
      }
    }
    theChords = \transpose a b \chordmode {
      \repeat volta 2 {
        s4 | a1:m | a:m | a:m | e2.
      }
      \repeat volta 2 {
        s4 | a1:m | a:m | a:m | e
        | a1:m | a:m | e2 e:7 | a2.:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    My Father is everything and all, my Father is not bad
    I believe in my Father and I believe in me
    I am son of the Queen and I live in this garden
    \nextverse
    I navigate in this force of the supreme Creator
    In the little boat of firmness, of justice and love
    With Mother nature, the Mother of our Savior
    \nextverse
    In the midst of these waves You take me to understand
    The power of these islands in their divine power
    Earthquakes and volcanoes make everything shake
    \nextverse
    Only the force of my Father is what makes everything be reborn
    The Holy Power of life that transforms and makes grow
    Viva the Earth, viva the Sea, and viva the dawn
  \end{translation}
\endsong


\beginsong{Dia das Mães}[by={Padr. Alfredo}, off={Madr. Rita}, key={C}, gk={C, (B)--(C)}]
  \audio[key=A]{https://soundcloud.com/canaljagube/07-dia-das-maes?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/109/M\%C3\%A3eDasM\%C3\%A3es}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{G}]Fir|\[\mnc{C}C]mei-\[^\mn{E}]me \[\mnc{G}G7]na \[^\mn{F}]lu\[^\mn{E}]a |\[\mnc{D}C]chei\[^\mn{C}]a \[\bm]
    \[^\mn{G}]No |\[^\mn{C}]gran\[^\mn{E}]de \[\bmc\mnc{G}]di\[^\mn{F}]a \[^\mn{E}]das |\[\mncadj{3ex}{D}Dm]Mães \[\bm]
    Pe|\[\mnc{G}G]dindo con\[\bmc\mn{B}]forto\jw a \[^\mn{D}]meu |\[^\mn{G}]Pai \[\bm]
    \[^\mnc{D}]E pe|\[^\mn{G}]dindo \[\mnc{F}G7]bên\[^\mn{E}]ção, Ma|\[\mncii{D}{C}C]mãe \[\bm]
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    A |^bênção ^para vi|^ver ^ \altchords{\id[1]{(B)}|B F\shrp{}7 |B}
    E co|lher esta ^grande fa|^mília ^ \altchords{| - |C\shrp{}m}
    Para\jw um |^dia ^apresen|tar ^ \altchords{|F\shrp{} | \e }
    No |Reino da ^Sobera|^nia ^ \altchords{| - F\shrp{}7 |B}
  \endchorus
  % verse 3
  \beginchorus
    Oh! |^San^ta Mãe das |^Mães ^
    Em |todo\jw o\jw uni^verso im|^pera ^
    Prote|^gei a ^nossa fa|mília ^
    Com minha |Mãe que me ^trouxe\jw em ma|^téria ^
  \endchorus
  % verse 4
  \beginchorus
    A Dou|^trina ^{é verda}|^deira ^ \altchords{\id[2]{(A)}|A E7 |A}
    O Santo |Daime em ^tudo se |^soma ^ \altchords{| - |Bm}
    O |^Mestre\jw é o ^de Naza|ré ^ \altchords{|E | \e}
    E\jw o mis|tério é ^da Ama|^zônia ^ \altchords{| - E7 |A}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "Dia das Mães"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative g'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8( \pomark g8) | c4.( e,8) g4 f8 e | d4( c4.) \parenthesize g'8 g8( g8)
        | c4( c8) e,8 g4 f8 e | e4( d2) d8( d8)
        | g,4( g8) g8 b4 b8 d8 | g2( g8) \parenthesize d8 d8( d)
        | g4( g8) g8 f4 e8 e | d4( c2)
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Fir _ -- | mei- me na lu -- a | chei -- a;
        "" No __ _ | gran _ -- de di -- a das | Mães; __ _
        Pe _ -- | din -- do con -- for -- to~a meu | Pai; __ _
        "" E pe -- | din _ -- do bên -- ção, Ma -- | mãe. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        A __ _ | bên -- ção pa -- ra vi -- | ver; __ _
        "" E co -- | lher es -- ta gran -- de fa -- | mí -- lia;
        Pa -- ra~um | di _ -- a a -- pre -- sen -- | tar; __ _
        "" No __ _ | Rei -- no da So -- be -- ra -- | ni -- a.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Oh! __ _ | San _ -- ta Mãe das | Mães; __ _
        "" Em __ _ | to -- do~o~u -- ni -- ver -- so im -- | pe -- ra;
        Pro -- te -- | gei __ _ a nos -- sa fa -- | mí -- lia;
        Com mi -- nha | Mãe que me trou -- xe~em ma -- | té -- ria.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        A Dou -- | tri -- na é ver -- da -- | dei -- ra;
        O San -- to | Dai -- me em tu -- do se | so -- ma;
        O __ _ | Mes -- tre~é o de Na -- za -- | ré; __ _
        "" E~o mis -- | té -- rio é da A -- ma -- | zô -- nia.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 g:7 | c1
        | c1 | d1:m
        | g1 | g1
        | g2 g:7 | c2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I firmed myself in the full moon on this great Mother's Day
    Asking for comfort from my Father and asking for a blessing, Mother
    \nextverse
    The blessing to live and gather this great family
    To one day present in the Kingdom of Sovereignty
    \nextverse
    Oh! Holy Mother of Mothers reigns over the entire universe
    Protect our family with my mother who brought me into the world
    \nextverse
    The Doctrine is true, the Holy Daime is the sum of all things
    The Master is the one of Nazareth and the mystery is of the Amazon
  \end{translation}
\endsong


\beginsong{Parabéns}[by={Padr. Alfredo}, off={Daniélle e Paula}, key={C}, gk={C, B\flt{}--D}]
  \audio[key=C]{https://soundcloud.com/canaljagube/08-parabens?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/110/Parab\%C3\%A9ns}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{C}]Salve |\[\mnc{F}F]todos fes\[\bm]tejos \[^\mn{G}]de |\[^\mn{A}]mai\[\bm]o \altchords{\id[1]{(D)}|G | \e}
    Lin\[^\mn{G}]da |\[^\mn{F}]festa da \[\bm]Virgem \[^\mn{E}]Ma|\[\mnc{G}G]ri\[\bm]a \altchords{| - |A}
    Sal\[^\mn{E}]{ve\jw a} |\[\mnc{C}C]Mãe, \[^\mn{A}]o \[\bmc\mn{C}]Filho\jw e \[^\mn{F}]as |\[\mnc{E}Am]flo\[\bm]res \altchords{|D |Bm}
    \[^\mn{G}]Sal\[^\mn{E}]{ve\jw o} |\[\mnc{C}C]Pai \[^\mn{A}]em \[\bmc\mn{C}]nossa\jw har\[^\mn{E}]mo|\[^\mn{C}]ni\[\up{1}C7]a \altchords{|D | \up{1}D7}
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    Salve |^os ani^versari|an^tes
    Que agra|decem a ^Deus neste |^di^a
    Só can|^tando\jw o can^tar com a|^mor ^
    Espa|^lhando paz ^e ale|gri^a
  \endchorus
  % verse 3
  \beginchorus
    Nova|^mente gi^rando\jw os fes|te^jos
    Nesta |roda que ^vai e que |^vem ^
    Viva |^os ani^versari|^an^tes
    Para|^béns, para^béns, para|béns ^
  \endchorus
  % verse 4
  \beginchorus
    Para|^béns, para^béns, para|béns ^
    Nesta |roda não ^falta nin|^guém ^
    Viva |^todos os ^aniver|^sá^rios
    Para|^béns, para^béns, para|béns \up{1}para^béns
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "Parabens"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        c8 \pomark c | f4 f8 f f4 f8 g8 | a2( \parenthesize a8)( \parenthesize a8) a8 g8
        | f4 f8 f8 f4 f8 e8 | g2( g4) g8 e8
        | c4( c8) a8 c4 c8 f8 | e2( e4) g8 e8
        | c4( c8) a8 c4 c8 e8
      } \alternative {
        { | c4( c8 c8) \parenthesize c4 }
        { | c4( c8 c8) \parenthesize c4 }
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Sal -- ve | to -- dos fes -- te -- jos de | mai -- o; __ _
        Lin -- da | fes -- ta da Vir -- gem Ma -- | ri -- a;
        Sal -- ve~a | Mãe, __ _ o Fi -- lho~e as | flo -- res;
        Sal -- ve~o | Pai __ _ em nos -- sa~har -- mo --
      } \alternative {
        { | ni _ _ -- a. }
        { | ni _ _ -- a. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Sal -- ve | os a -- ni -- ver -- sa -- ri -- | an -- tes;
        Que a -- gra -- | de -- cem a Deus nes -- te | di -- a;
        Só can -- | tan -- do~o can -- tar com a -- | mor; __ _
        Es -- pa -- | lhan -- do paz e a -- le --
      } \alternative {
        { | gri _ _ -- a. }
        { | gri _ _ -- a. }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        No -- va -- | men -- te gi -- ran -- do~os fes -- | te -- jos; __ _
        Nes -- ta | ro -- da que vai e que | vem; __ _
        Vi -- va | os a -- ni -- ver -- sa -- ri -- | an -- tes;
        Pa -- ra -- | béns, pa -- ra -- béns, pa -- ra --
      } \alternative {
        { | béns. __ _ _ "" }
        { | béns. __ _ _ "" }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Pa -- ra -- | béns, pa -- ra -- béns, pa -- ra -- | béns; __ _ _
        Nes -- ta | ro -- da não fal -- ta nin -- | guém; __ _
        Vi -- va | to -- dos os a -- ni -- ver -- | sá -- rios
        Pa -- ra -- | béns, pa -- ra -- béns, pa -- ra --
      } \alternative {
        { | béns, pa -- ra -- béns }
        { | béns. __ _ _ "" }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
      s4 | f1 | f1
      | f | g
      | c | a:m
      | c
      } \alternative {
        { | c2 c4:7 }
        { | c2. }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Hail all the May festivities, the beautiful feast of the Virgin Mary
    Hail the Mother, the Son and the flowers, hail the Father in our harmony
    \nextverse
    Hail all celebrating birthdays who are grateful to God on this day
    Only singing the songs with love, and spreading peace and joy
    \nextverse
    Once again the festivities turn in this wheel that comes and goes
    Viva all celebrating birthdays, happy birthday\ldots
    \nextverse
    Happy birthday\ldots{} In this circle no one is missing
    Viva all celebrating birthdays, happy birthday, happy birthday\ldots
  \end{translation}
\endsong


\beginsong{Me Abençoa}[by={Padr. Alfredo}, off={Aucinete}, key={Dm}, gk={Dm, Cm--E\flt{}m}, tags={valsa}]
  \audio[key=Cm]{https://soundcloud.com/canaljagube/09-me-abencoa?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/111/MeAben\%C3\%A7oaDivinoPapai}
  \newchords{chords_me_abencoa_a}\newchords{chords_me_abencoa_b}
  \meter{3}{4}
  % verse 1
  \mnbeginchorus\memorize[chords_me_abencoa_a]
    \[^\mn{A}]Me |\[Dm]aben|çoa \[^\mn{G}]Di|\[\mncii{B&}{G}Em7&5]vino \[^\mn{E}]Pa|\[\mnc{C#}A]pai, \[^\mn{G}]e |\[Gm]a\[^\mn{F}]ben|\[\mnc{A}Dm]ço\[^\mn{F}]a \[^\mn{D}]Ma|\[^\mn{A}]mãe
    \[^\mn{D}]Pa\[^\mn{F}]ra |\[\mnc{E}Em7&5]sem\[^\mn{D}]pre |\[\mnc{C#}A7]eu Vos \[^\mn{B&}]a|\[\mnc{A}Dm]mar | \e
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_me_abencoa_b]
    \[^\mn{A}]Me |\[Dm]aben|çoa \[^\mn{G}]Di|\[\mncii{B&}{G}Em7&5]vino \[^\mn{E}]Pa|\[\mnc{C#}A]pai, \[^\mn{G}]e |\[Gm]a\[^\mn{F}]ben|\[\mnc{A}Dm]ço\[^\mn{F}]a \[^\mn{D}]Ma|\[^\mn{A}]mãe
    \[^\mn{D}]Pa\[^\mn{F}]ra |\[\mnc{E}Em7&5]sem\[^\mn{D}]pre |\[\mnc{C#}A]eu Vos \[^\mn{E}]lou|\[\mnc{D}Dm]var | \e
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_me_abencoa_a]
    Me |^aben|çoa Di|^{vina Ma}|^mãe, e |^aben|^çoa Pa|pai
    Para |^sempre |^eu enxer|^gar | \e
  \endchorus\glueverses
  \beginchorus\replay[chords_me_abencoa_b]
    Me |^aben|çoa Di|^{vina Ma}|^mãe, e |^aben|^çoa Pa|pai
    Para |^sempre |^acompa|^nhar | \e
  \endchorus
  % verse 3
  \beginchorus\replay[chords_me_abencoa_a]
    Jo|^guei a |minha tar|^{rafa no} |^meio, e |^com espe|^rança me |veio
    A |^praia |^da beira-|^mar | \e
  \endchorus\glueverses
  \beginchorus\replay[chords_me_abencoa_b]
    Os |^peixes |que eu pe|^{guei nela} |^veio, e |^com cer|^teza\jw ensi|nei
    Para |^sempre |^saber na|^dar | \e
  \endchorus
  % verse 4
  \beginchorus\replay[chords_me_abencoa_a]
    A|^gora |vamos can|^{tar com a}|^mor e |^vamos bai|^{lar meus} ir|mãos
    Para |^sempre |^nós feste|^jar | \e
  \endchorus\glueverses
  \beginchorus\replay[chords_me_abencoa_b]
    A |^Deus e a |Virgem Ma|^{ria no} |^Céu, com |^a do|^çura do |mel
    Na |^terra, no |^vento\jw e no |^mar | \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "Me Abençoa"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative a'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 3/4 \partial 4
      \mark \markup \with-color #darkgreen \italic "Final: toque tudo"
      \sectionLabel "A"
      \repeat volta 2 {
        a4 \pomark | a2 a4 | a4 a4 g4 | bes4 g4 e4 | cis2 g'4
        | g4( g4) f4 | a4 f d | a << d \altmark "3." \single\altcol a >> f'
        | e2 d4 | cis4 cis4 bes'4 | a2.~ | a2
      }
      \sectionLabel "B"
      \repeat volta 2 {
        a4 | a4( a4) a4 | a4 a4 g4 | bes4 g4 e4 | cis2 g'4
        | g2 f4 | a4 f d | a \parenthesize d f
        | e4( e4) d4 | cis4 cis4 e4 | d2.~| d2
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Me | a -- ben -- | ço -- a Di -- | vi -- no Pa -- | pai,
        E | a _ -- ben -- | ço -- a Ma -- | mãe;
        Pa -- ra | sem -- pre | eu Vos a -- | mar. | _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Me | a _ -- ben -- | ço -- a Di -- | vi -- no Pa -- | pai,
        E | a -- ben -- | ço -- a Ma -- | mãe;
        Pa -- ra | sem _ -- pre | eu Vos lou -- | var. | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Me | a -- ben -- | ço -- a Di -- | vi -- na Ma -- | mãe,
        E | a _ -- ben -- | ço -- a Pa -- | pai;
        Pa -- ra | sem -- pre | eu en -- xer -- | gar. | _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Me | a _ -- ben -- | ço -- a Di -- | vi -- na Ma -- | mãe,
        E  | a -- ben -- | ço -- a Pa -- | pai;
        Pa -- ra | sem _ -- pre | a -- com -- pa -- | nhar. | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Jo -- | guei a | mi -- nha tar -- | ra -- fa no | meio,
        E | com es -- pe -- | ran -- ça me | vei -- \altcol o;
        A | prai -- a | da bei -- ra- mar. | _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Os | pei _ -- xes | que eu pe -- | guei ne -- la | veio,
        E | com cer -- | te -- za~en -- si -- | nei;
        Pa -- ra | sem _ -- pre | sa -- ber na -- | dar. | _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        A -- | go -- ra | va -- mos can -- | tar com a -- | mor,
        E | va -- mos bai -- | lar meus ir -- | mãos;
        Pa -- ra | sem -- pre | nós fes -- te -- | jar. | _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        A | Deus e a | Vir -- gem Ma -- | ri -- a no | Céu,
        Com | a do -- | çu -- ra do | mel; ""
        Na | ter -- ra, no | ven -- to~e no | mar. | _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4
        | d2.:m | d:m | e:m7.5- | a
        | g:m | d:m | d:m
        | e:m7.5- | a:7 | d:m | d2:m
      }
      \repeat volta 2 {
        s4
        | d2.:m | d:m | e:m7.5- | a
        | g:m | d:m | d:m
        | e:m7.5- | a | d:m | d2:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Bless me Divine Daddy and bless me Mama, so I may always love you
    Bless me Divine Daddy and bless me dear Mama
    To praise you forever
    \nextverse
    Bless me Divine Mama and bless me Daddy, so that I can always see
    Bless me Divine Mama and bless Daddy
    To always accompany You
    \nextverse
    I cast my net in the midst of the sea and with hope it came to me,
    \ind to the beach of the seaside
    The fish that I caught came into the net and with certainty I taught them
    To always know how to swim
    \nextverse
    Now let us sing with love and let's dance my brothers and sisters, to celebrate forever
    God and the Virgin Mary in heaven with the sweetness of honey
    On the Earth, the wind and sea
  \end{translation}
\endsong


\beginsong{Mensagem}[by={Padr. Alfredo}, off={Ricardo Tadeu}, key={G}, gk={G, G--G}, tags={mazurca}]
  \audio[key=G]{https://soundcloud.com/canaljagube/10-mensagem?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/112/VouCantarEstaMensagem}
  \meter{6}{4}
  \mnbeginchorus\memorize
    \[^\mn{B}]Vou \[^\mn{D}]can|\[\mnc{G}G]tar \[^\mn{F#}]es\[^\mn{E}]ta \[^\mn{D}]men\[\bmc\mn{G}]sagem
    \[^\mn{E}]Que \[^\mn{D}]meu |\[^\mn{G}]Mestre \[^\mn{E}]me man\[\mnc{A}Am]dou
    \lrep \[^\mn{E}]Doutri|\[\mnc{A}Am]nar o mun\[^\mn{B}]{do\jw in}\[\mnc{G}G]teiro
    \[^\mn{B}]Na |\[\mnc{D}D7]ordem do Pai \[^\mn{A}]Cri\[^\mn{B}]a\[\mnc{G}G]dor \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    Com |^ordem da Mãe Di^vina \altchords{\id[1]{(A)}|A}
    Ao guer|reiro\jw Arcanjo São Mi^guel \altchords{| - Bm}
    \lrep Aí |^tem a disci^plina \altchords{|Bm A}
    Para |^nossa\jw educação no ^céu \rrep \altchords{|E7 A}
  \endchorus
  \beginchorus
    Sem a|^mor não tem cari^dade
    Sem a |força não tem uni^ão
    \lrep Vai do|^er a disci^plina
    Do guer|^reiro São Sebasti^ão \rrep
  \endchorus
  \beginchorus
    Quem man|^dou foi a Ra^inha
    Quem cas|tiga é São Iri^neu
    \lrep Depen|^dendo da igno^rância
    Cada |^um se destrói por si ^mesmo \rrep
  \endchorus
  \beginchorus
    Estou fa|^zendo\jw o que Ele ^disse
    Se cum|prindo a sua jus^tiça
    \lrep E as do|^enças vão se transfor^mando
    Do cor|^reio da má no^tícia \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-09
    % \header {
    %   title = "Mensagem"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 6/4 \partial 4.
      \sectionLabel "A"
      \repeat segno 2 {
        \parenthesize b8 \pomark << b \altmark "2." \once\slurUp \single\altcol d \single\altcol ( >> d) | g4 fis8( fis8) e8 d8  g4 g4 e8 d8
        | g8( g8) g8( g8) e8 e8  a4( a8)
        \sectionLabel "B"
        \repeat volta 2 {
          \parenthesize e8 e8( e8) | a8( a8) a8( a8) a8 b8  g4 g4 b,8( b8)
          | d8( d8) d8 d8 a8 b8  g4( g8)
        }
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat segno 2 {
        "" Vou can -- | tar es _ -- ta men -- sa -- gem
        Que meu | Mes _ -- tre __ _ me man -- dou. __ _
        \set stanza = "1.B"
        \repeat volta 2 {
          "" Dou -- tri -- | nar __ _ o __ _ mun -- do~in -- tei -- ro
          Na __ _ | or -- dem do Pai Cri -- a -- dor. __ _
        }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat segno 2 {
        "" \altcol Com __ _ | or -- dem da Mãe Di -- vi -- na
        Ao guer -- | rei -- ro~Ar -- can -- jo São Mi -- guel. __ _

        \set stanza = "2.B"
        \repeat volta 2 {
          "" Aí __ _ | tem __ _ a __ _ dis -- ci -- pli -- na
          Pa -- ra | nos -- sa~e -- du -- ca -- ção no céu. __ _
        }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat segno 2 {
        "" Sem a -- | mor não tem ca -- ri -- da -- de
        Sem a | for -- ça não tem u -- ni -- ão. __ _
        \set stanza = "3.B"
        \repeat volta 2 {
          "" Vai do -- | er __ _ a __ _ dis -- ci -- pli -- na
          Do guer -- | rei -- ro São Se -- bas -- ti -- ão. __ _
        }
      }
    }
    theLyricsFour = \lyricmode {
      \repeat segno 2 {
        \set stanza = "4.A"
        "" Quem man -- | dou foi __ _ a Ra -- i -- nha
        Quem cas -- | ti -- ga é São I -- ri -- neu __ _
        \set stanza = "4.B"
        \repeat volta 2 {
          "" De -- pen -- | den -- do da i -- g -- no -- rân -- cia
          Ca -- da | um se des -- trói por si mes -- mo.
        }
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat segno 2 {
        Es -- tou fa -- | zen -- do~o que E -- le dis -- se
        Se cum -- | prin -- do a su -- a jus -- ti -- ça.
        \set stanza = "5.B"
        \repeat volta 2 {
          E as do -- | en -- ças vão se trans -- for -- man -- do
           Do cor -- | rei _ -- o da má no -- tí -- cia.
        }
      }
    }
    theChords = \chordmode {
      \repeat segno 2 {
        s4. | g2. g2.
        | g2. a4.:m
        \repeat volta 2 {
          s4. | a2.:m g2.
          | d2.:7 g4.
        }
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]\scriptsize % to fit on same page
    I am going to sing this message, because my Master ordered me
    To indoctrinate the whole world in the order of the Father Creator
    \nextverse
    With the order of the Divine Mother, of the warrior Archangel St. Michael
    Within is the discipline, for our education in heaven
    \nextverse
    Without love there is no charity, without strength there is no union
    The discipline of warrior St. Sebastião is going to be painful
    \nextverse
    Who ordered was the Queen, who punishes is Saint Irineu
    And depending on the (degree of) ignorance, each one destroys his/herself
    \nextverse
    I am doing what He said, his justice is being fulfilled
    And the illnesses will transform themselves from the mail of bad news
  \end{translation}
\endsong


\beginsong{A Deus Eu Agradeço}[by={Padr. Alfredo}, off={Carlos Raulino}, key={C}, gk={D, C--D}]
  \audio[key=C]{https://soundcloud.com/canaljagube/11-a-deus-eu-agradeco?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/113/ADeusEuAgrade\%C3\%A7o}
  \newchords{chords_deuseuagradeco_a}\newchords{chords_deuseuagradeco_b}
  % verse 1
  \mnbeginchorus\memorize[chords_deuseuagradeco_a]
    \[^\mn{C}]A |\[\mnc{F}F]Deus eu agra\[\bmc\mn{A}]de\[^\mn{F}]ço e a |\[\mnc{E}C]to\[^\mn{C}]da na\[^\mn{E}]tu\[\bmc\mn{G}]reza \altchords{\id[1]{(D)}|G |D}
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_deuseuagradeco_b]
    |\[\mnc{D}G]Pelo céu a\[\bm]zul, \[^\mn{G}]{o\jw so,} a |\[\mnc{C}C]lua\jw e as es\[\bmc\mn{E}]trelas \altchords{|A |D}
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_deuseuagradeco_a]
    Oh! |^Minha Mãe Di^vina eu tam|^bém Vos agra^deco
  \endchorus\glueverses
  \beginchorus\replay[chords_deuseuagradeco_b]
    |^Pelo que co^nheço\jw o que o{\ifchorded-\fi}b{\ifchorded-\fi}|^tenho\jw e que re^cebo
  \endchorus
  % verse 3
  \beginchorus\replay[chords_deuseuagradeco_a]
    An|^dar na paz dos ^santos prote|^ção dos anjos ^vem
  \endchorus\glueverses
  \beginchorus\replay[chords_deuseuagradeco_b]
    Pres|^tar bem aten^ção que no |^mundo tudo ^tem
  \endchorus
  % verse 4
  \beginchorus\replay[chords_deuseuagradeco_a]
    A|^lerta para\jw o ^tempo que o |^mesmo\jw está che^gado
  \endchorus\glueverses
  \beginchorus\replay[chords_deuseuagradeco_b]
    Quem |^falou do meu ^Mestre com cer|^teza vai fi^cando
  \endchorus
  % verse 5
  \beginchorus\replay[chords_deuseuagradeco_a]
    |^Anjos e ar^canjos deste |^dia de na^tal \altchords{\id[2]{(E)}|A |E}
  \endchorus\glueverses
  \beginchorus\replay[chords_deuseuagradeco_b]
    São Jo|^sé, São Zarca^rias e o |^príncipe\jw Imperi^al \altchords{|B |E}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "A Deus Eu Agradeço"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 8
      \mark \markup \with-color #darkgreen \italic "Final: toque tudo (no 5º verso)"
      \sectionLabel "1-4.A"
      \repeat segno 4 {
        \repeat volta 2 {
          c8 | f8 f f f a f f f | e c c e g4 \parenthesize g8
        } \break
        \sectionLabel "1-4.B"
        \repeat volta 2 {
          \parenthesize c,8 | d8 d d d d8 \parenthesize g,16( \parenthesize g16) g8 g8 | c8 c16( c16) c8 c8 e4 \parenthesize e8
        }
      }
      \sectionLabel "5.A"
      \repeat volta 2 {
        r8 \pomark | f8 f f f a f f f | e c c e g4
      } \alternative {
        { r8 }
        { }
      }
      \sectionLabel "5.B"
      \repeat volta 2 {
        c,8 c8 | d8 d d d d8 g,8 g8 g8 | c8 c16 c16 c8 c8 e4
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        A | Deus eu a -- gra -- de -- ço,
        e a | to -- da na -- tu -- re -- za.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        "" | Pe -- lo céu a -- zul, ""
        o so, a | lu -- a e as es -- tre -- las.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Oh! | Mi -- nha Mãe Di -- vi -- na,
        eu tam -- | bém Vos a -- gra -- de -- co.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        "" | Pe -- lo que co -- nhe -- ço,~o
        que o -- b -- | te -- nho e que re -- ce -- bo.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        An -- | dar na paz dos san -- tos,
        pro -- te -- | ção dos an -- jos vem. ""
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Pres -- | tar bem a -- ten -- ção, "" ""
        que no | mun -- do __ _ tu -- do tem. ""
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        A -- | ler -- ta pa -- ra~o tem -- po,
        que o | mes -- mo~es -- tá che -- ga -- do.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Quem | fa -- lou do meu Mes -- tre, __ _
        com cer -- | te -- za __ _ vai fi -- can -- do.
      }
      \set stanza = "5.A"
      \repeat volta 2 {
        | An -- jos e ar -- can -- jos,
        des -- te | di -- a de na -- tal.
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        São Jo -- | sé, São Zar -- ca -- ri -- as,
        e o | prín -- ci -- pe~Im -- pe -- ri -- al.
      }
    }
    theChords = \chordmode {
      % v 1-4
      \repeat segno 4 {
        \repeat volta 2 {
          s8 | f1 | c2.~8
        }
        \repeat volta 2 {
          s8 | g1 | c2.~8
        }
      }
      % v 5
      \repeat volta 2 {
        s8 | f1 | c2.
      } \alternative {
        { s8 }
        { }
      }
      \repeat volta 2 {
        s4 | g1 | c2.
      }
    }
    \layout { #(layout-set-staff-size 14.6) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN] \ifshowlilypond\scriptsize\fi
    To God I give thanks, and to all of nature
    For the blue sky, the sun, the moon and the stars
    \nextverse
    Oh! My Divine Mother, I also thank you
    For what I know, what I obtain and what I receive
    \nextverse
    To walk in the peace of saints, protection of the angels comes
    To pay close attention, for the world has everything
    \nextverse
    Be alert for the times, for the time is arriving
    Who spoke against my Master will surely stay behind
    \nextverse
    Angels and archangelks, of this Christmas day
    Saint Joseph, Saint Zacariah and the Imperial Prince
  \end{translation}
\endsong


\beginsong{Senhor Juramidam}[by={Padr. Alfredo}, off={Elizabeth Mendes}, key={C}, gk={C, B--D}]
  \audio[key=C]{https://nossairmandade.com/hymn/114/OSenhorJuramidam}
  \audio[key=C]{https://soundcloud.com/canaljagube/12-juramidam?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \newchords{chords_senhorjuramidam_a}\newchords{chords_senhorjuramidam_b}
  % verse 1
  \mnbeginchorus\memorize[chords_senhorjuramidam_a]
    \[^\mn{C}]O \[^\mn{E}]Se|\[\mnc{G}C]nhor Ju\[^\mn{F#}]ra\[^\mn{E}]mi\[\bmc\mn{G}]dam \[^\mnc{C}]é \[^\mn{E}]quem |\[\mnc{G}G]vem me \[^\mn{F#}]en\[^\mn{A}]si\[\mnc{E}C]nar
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_senhorjuramidam_b]
    \[^\mn{G}]É \[^\mn{E}]pre|\[\mnc{C}Am]ci\[^\mn{A}]so \[^\mn{C}]ter a\[\mnc{E}C]mor \[^\mnc{G}]e \[^\mn{E}]é |\[\mnc{C}Am]pre\[^\mn{A}]ci\[^\mn{C}]so re\[\mnc{E}C]zar
    \[^\mn{G}]Pa\[^\mn{E}]ra |\[\mnc{C}Am]po\[^\mn{A}]der \[^\mn{C}]mere\[\mnc{E}C]cer \[^\mn{G}]{e\jw é} \[^\mn{E}]pre|\[\mnc{C}F]ci\[^\mn{A}]so \[^\mn{C}]se ca\[C]lar
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_senhorjuramidam_a]
    Quem |^não ouve os ^hinos não de|^vem mais procu^rar
  \endchorus\glueverses
  \beginchorus\replay[chords_senhorjuramidam_b]
    Não vai |^ouvir a meu ^Pai, O Mes|^tre que sempre\jw es^ta
    Não ou|^ve a natu^reza\jw e não po|^de partici^par
  \endchorus
  % verse 3
  \beginchorus\replay[chords_senhorjuramidam_a]
    Eu o|^lhando para\jw oi ^céu, vejo |^estrelas bri^lhar \altchords{\id[1]{(B)}|B |F\shrp{} B}
  \endchorus\glueverses
  \beginchorus\replay[chords_senhorjuramidam_b]
    É um |^grande livro\jw a^ceso, que po|^demos se fir^mar \altchords{|G\shrp{}m B |G\shrp{}m B}
    O lei|^a quem mere^cer e quem |^souber respei^tar \altchords{|G\shrp{}m B |E B}
  \endchorus
  % verse 4
  \beginchorus\replay[chords_senhorjuramidam_a]
    Neste |^livro se en^contra nossa |^Mãe e nosso ^Pai \altchords{\id[2]{(D)}|D |A D}
  \endchorus\glueverses
  \beginchorus\replay[chords_senhorjuramidam_b]
    E to|^dos seres di^vinos que to|^dos brilham i^guais \altchords{|Bm D |Bm D}
    Aonde\jw es|^tá a divin^dade não e|^xiste Sata^nás \altchords{|Bm D |G D}
  \endchorus
  % verse 5
  \beginchorus\replay[chords_senhorjuramidam_a]
    Para |^ser filho de ^Deus é pre|^ciso mais a^mar
  \endchorus\glueverses
  \beginchorus\replay[chords_senhorjuramidam_b]
    Não que|^rer ser tão a^mado e nem |^tão conside^rado
    Neste |^mundo deser^dado sem an|^tes conside^rar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Senhor Juramidam"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \mark \markup \with-color #darkgreen \italic "Final: toque tudo"
      \sectionLabel "A"
      \repeat volta 2 {
        \parenthesize c8 \pomark e | g g fis e g8( g8) c,8 e | g g fis a e4
      }
      \sectionLabel "B"
      \repeat volta 2 {
        g8 e | c a c c e8( e8) g8 e | c8 a c c e8( e8)
        g8 e | c a c c e8( e8) g8 e | c8 a c c c4
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        O Se -- | nhor Ju -- ra -- mi -- dam __ _
        É quem | vem me en -- si -- nar.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        É pre -- | ci -- so ter a -- mor __ _
        E é | pre -- ci -- so re -- zar; __ _
        Pa -- ra | po -- der me -- re -- cer __ _
        E~é pre -- | ci -- so se ca -- lar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        "" Quem | não ou -- ve os hi -- nos
        Não de -- | vem mais pro -- cu -- rar.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Não vai | ou -- vir a meu Pai __ _
        O Mes -- | tre que sem -- pre~es -- ta; __ _
        Não ou -- | ve a na -- tu -- re -- za~E
        não po -- | de par -- ti -- ci -- par.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Eu o -- | lhan -- do pa -- ra~oi céu __ _
        Ve -- jo | es -- tre -- las bri -- lhar.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        É um | gran -- de li -- vro~a -- ce -- so
        Que po -- | de -- mos se fir -- mar; __ _
        O lei -- | a quem me -- re -- cer __ _
        E quem | sou -- ber res -- pei -- tar.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Nes -- te | li -- vro se en -- con -- tra
        Nos -- sa | Mãe e nos -- so Pai.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        E to -- | dos se -- res di -- vi -- nos
        Que to -- | dos bri -- lham i -- guais;
        A -- on -- de~es -- | tá a di -- vin -- da -- de
        Não e -- | xis -- te Sa -- ta -- nás.
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        Pa -- ra | ser fi -- lho de Deus __ _
        É pre -- | ci -- so mais a -- mar.
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Não que -- | rer ser tão a -- ma -- do
        E nem | tão con -- si -- de -- ra -- do;
        Nes -- te | mun -- do de -- ser -- da -- do
        Sem an -- | tes con -- si -- de -- rar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | g2 c4
      }
      \repeat volta 2 {
        s4 | a2:m c | a2:m c
        | a2:m c | f2 c4
      }
    }
    \layout { #(layout-set-staff-size 14.6) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN] \ifshowlilypond\scriptsize\fi
    The Lord Juramidam is who comes to teach me.
    One needs to love and one needs to pray.
    In order to deserve and one needs to be quiet
    \nextverse
    Those who don't hear the hymns no longer seek.
    They will not hear my Father, the Master who is ever present.
    They will not hear nature and they will not be able to participate.
    \nextverse
    When I look to the sky, I see the stars shining.
    It is a great book that is accessible, in which we can firm ourselves.
    It is read by those who are deserving and those who show respect.
    \nextverse
    In this book we find our Mother and our Father.
    And all the divine beings, they all shine equally.
    Where there is divinity Satan does not exist.
    \nextverse
    To be a son of God one must love more.
    Not to want to be so loved, and neither to be so considered.
    In this forsaken world without considering others first.
  \end{translation}
\endsong


\beginsong{Dimensão Espiritual}[by={Padr. Alfredo}, off={Lúcia Arruda}, tags={valsa}, key={Bm}, gk={Bm, B\flt{}m--C\shrp{}m}]
  \audio[key=Bm]{https://soundcloud.com/canaljagube/13-dimensao-espiritual?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio[]{https://nossairmandade.com/hymn/115/Dimens\%C3\%A3oEspiritual}
  \meter{3}{4}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{E}]Eu |\[\mnc{A}A]amo a |\[^\mn{C#}]Deus \[^\mn{D}]nas \[^\mn{C#}]al|\[^\mn{E}]tu|ras \altchords{\id[1]{C\shrp{}m}|B | - | - | \e}
    Di|mensão es|\[A7]piritu|\[\mnc{F#}D]al | \e \altchords{| - |B7 |E | \e}
    \lrep \[^\mauii{B}{F#}]E |\[\mnc{B}E]amo a |minha Mãe|\[\mnc{E}A]zi\[^\mn{C#}]nha \[^\mn{B}]do |\[^\mn{A}]Céu \altchords{|F\shrp{} | - |B | \e}
    Na |terra |\[F#m]e \[^\mn{G#}]no \[^\mn{A}]as|\[\mnc{B}Bm]tral | \e \rrep \altchords{| - |G\shrp{}m |C\shrp{}m | - }
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    A|^doro\jw a San|ta\jw Estrela |Sol | \e
    Com |Vossa luz |^do me vi|^ver | \e
    \lrep Ve|^nero as |noites de |^luar Ma|mãe
    Que\jw é |para\jw a Se|^nhora\jw eu lhe |^ver | \e \rrep
  \endchorus
  % verse 3
  \beginchorus
    Es|^trelas |bem peque|ni|nas
    Gra|vitam |^no firma|^men|to
    \lrep Fir|^meza |no cora|^ção do meu |Pai
    E |firmeza |^no pensa|^men|to \e \rrep
  \endchorus
  % verse 4
  \beginchorus
    Pe|^netro |na natu|re|za
    Na |sua |^imensi|^dão. | \e
    \lrep Pe|^dindo con|forto da |^vida\jw a meu |Pai
    Se|nhor, Meu |^Jurami|^dam | \e \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Dimensão Espiritual"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative f'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key b \minor \time 3/4 \partial 4
      \sectionLabel "A"
      \repeat segno 2 {
        e4 \pomark | a( a) a | cis, d cis | e2.( | e2) e4 | e( e) e | e e e | fis2.( | fis2)
        \sectionLabel "B"
        \repeat volta 2 {
          << fis4 \single\altcol b,4 \altmark "ii" >> | b( b) b | b b b | e cis b | a2 a4 | a4( a4) a4 | a4 gis a | b2.( | b2)
        }
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat segno 2 {
        Eu | a -- mo a | Deus nas al -- | tu -- | ras;
        Di -- | men -- são es -- | pi -- ri -- tu -- | al. __ | _
        \set stanza = "1.B"
        \repeat volta 2 {
          E | a -- mo a | mi -- nha Mãe -- | zi -- nha do | Céu;
          Na | ter -- _ ra | e no as -- | tral. __ | _
        }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat segno 2 {
        A -- | do -- ro~a San -- | ta~Es -- tre -- la | Sol; __ | _
        Com | Vos -- sa luz | do me vi -- | ver. __ | _
        \set stanza = "2.B"
        \repeat volta 2 {
          Ve -- | ne -- ro as | noi -- tes de | lu -- ar Ma -- | mãe;
          Que~é | pa -- ra~a Se -- | nho -- ra~eu lhe | ver. __ | _
        }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat segno 2 {
        Es -- | tre _ -- las | bem pe -- que -- | ni -- | nas;
        Gra -- | vi _ -- tam | no fir -- ma -- | men -- | to.
        \set stanza = "3.B"
        \repeat volta 2 {
          Fir -- | me _ -- za | no co -- ra -- | ção do meu | Pai;
          E | fir -- me -- za | no pen -- sa -- | men -- | to.
        }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat segno 2 {
        Pe -- | ne _ -- tro | na na -- tu -- | re -- | za;
        Na | su _ -- a | i -- men -- si -- | dão. __ | _
        \set stanza = "4.B"
        \repeat volta 2 {
          Pe -- | din -- do con -- | for -- to da | vi -- da~a meu | Pai;
          Se -- | nhor, __ _ Meu | Ju -- ra -- mi -- | dam. __ | _
        }
      }
    }
    theChords = \chordmode {
      \repeat segno 2 {
        s4 | a2. | a | a | a | a a:7 | d | d2
        \repeat volta 2 {
          s4 | e2. | e | a | a | a | fis:m | b:m | b2:m
        }
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I love God in the heights, spiritual dimension
    And I love my dear Mother of Heaven
    On the Earth and in the astral
    \nextverse
    I adore the Holy Star Sun, with Your light of well-being
    I venerate the nights of moonlight Mamãe
    That are for me to see You
    \nextverse
    Tiny little stars gravitate in the firmament
    Firmness in the heart of my Father
    And firmness in thought
    \nextverse
    I penetrate nature in its immensity
    Asking comfort of life from my Father,
    My Lord Juramidam
  \end{translation}
\endsong


\beginsong{Valorizar}[ititle={Convite}, by={Padr. Alfredo}, off={Sebastião Raulino}, key={G}, gk={G, (G\flt{})--(G)}]
  \audio{https://nossairmandade.com/hymn/116/OMestreFezOConvite}
  \audio[key=F]{https://soundcloud.com/canaljagube/14-convite?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{D}]O |\[G]Mestre fez \[\bmc\mnc{E}]o \[^\mn{D}]con|\[^\mn{G}]vi\[\bm]te
    \[^\mn{B}]Pa\[^\mn{D}]ra |todos \[\bmc\mn{E}]tra\[^\mn{D}]ba|\[\mnc{F#}D]lhar \[\bm]
    \[^\mn{D}]{E va}|lori\[\bmc\mn{E}]zar \[^\mn{D}]a |\[\mnc{C}C]vida\jw
    O \[\mnc{A}(Am6)]nos\[^\mn{F#}]so |\[\mnc{D}D]Mestre a\[\mnc{A}D7]on\[^\mn{B}]de\jw es|\[\mnc{G}G]ta \[\bm]
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    Dar va|^lor ao ^Cria|dor ^ \altchords{\id[1]{(G\flt{})}|G\flt{}| \e}
    Dar va|lor à ^Cria|^ção ^ \altchords{| - |D\flt{} }
    Dar va|lor ao ^Pai Di|^vino \altchords{| - |C\flt{}}
    ^{E a} |^Virgem da ^Concei|^ção ^ \altchords{(A\flt{}m6) |D\flt{} D\flt{}7 |G\flt{}}
  \endchorus
  % verse 3
  \beginchorus
    A Ra|^inha ^da Flo|res^ta
    Cria |tudo har^moni|^za^do
    Toda |cor e ^toda |^flor
    ^Dentro |^do jar^dim dou|^ra^do
  \endchorus
  % verse 4
  \beginchorus
    Salve\jw a |^luz e ^salve\jw a |for^ça
    O po|der e ^o sa|^ber ^
    Salve, |salve\jw o ^nosso |^Mestre\jw
    A ^{força\jw a}|^onde ^pode |^ser ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Valorizar"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative f'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 4
      \repeat volta 2 {
        d8( \pomark d8) | d4 d8( d) e4 d | g2( g4) b,8 d | d4 d8( d) e4 d | fis2( fis4)
        d8 d | d4 d e d | c'4.( c8) a4 fis | d4 d8( d) a4 b | g2( g4)
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        O __ _ | Mes -- tre fez o con -- | vi -- te;
        Pa -- ra | to -- dos __ _ tra -- ba -- | lhar; __ _
        E va -- | lo -- ri -- zar a | vi -- da;~O
        nos -- so | Mes -- tre a -- on -- de~es -- | ta. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Dar va -- | lor ao __ _ Cri -- a -- | dor; __ _
        Dar va -- | lor à __ _ Cri -- a -- | ção; __ _
        Dar va -- | lor ao Pai Di -- | vi -- no;
        E a | Vir -- gem da Con -- cei -- | ção. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        A Ra -- | i -- nha __ _ da Flo -- | res -- ta;
        Cri -- a | tu -- do har -- mo -- ni -- | za -- do;
        To -- da | cor e to -- da | flor; __ _
        Den -- tro | do jar -- _ dim dou -- | ra -- do.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Sal -- ve~a | luz e __ _ sal -- ve~a | for -- ça;
        O po -- | der e __ _ o sa -- | ber; __ _
        Sal -- ve, | sal -- ve~o nos -- so | Mes -- tre;~A
        for -- ça~a -- | on -- de __ _ po -- de | ser. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | g1 | g | g | d
        | d | c2 \parenthesize a:m6 | d d:7 | g2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    The Master invited everyone to work
    And to value life, our Master where He is
    \nextverse
    To value the Creator, to value Creation
    To value the Divine Father and the Virgin of Conception
    \nextverse
    The Queen of the Forest creates everything in harmony
    Every color and every flower within the golden garden
    \nextverse
    Hail the light and hail the force, the power and the knowledge
    Hail, hail our Master, the force wherever it may be
  \end{translation}
\endsong


\beginsong{Rota}[by={Padr. Alfredo}, off={Sid Matos}, key={C}, gk={D, C--E}, tags={valsa}]
  \audio[key=C]{https://soundcloud.com/canaljagube/15-vamos-conhecer?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/117/Rota}
  \meter{3}{4}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{G}]Vi|\[\mnc{C}C]sando\jw es\[^\mn{E}]te |\[^\mn{C}]rumo
    Va|mos \[\mnc{B}Cmaj7]co\[^\mn{D}]nhe|\[\mnc{G}G]cer
    O tra|ba\[^\mn{B}]lho \[^\mn{D}]do |\[\mnc{G}G7]Mes\[^\mn{F}]{tre\jw}
    E \[^\mn{D}]Seu |\[^\mn{B}]grande \[^\mn{G}]po|\[\mnc{C}C]der
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    Se|^guindo\jw esta |rota \altchords{\id[1]{(D)}|D | \e}
    Nós |va^{mos che}|^gar \altchords{| - Dmaj7 |A }
    No cen|tral da Dou|^trina\jw \altchords{| - |A7}
    A on|de\jw o Mestre\jw es|^ta \altchords{| - |D}
  \endchorus
  % verse 3
  \beginchorus
    É |^grande fes|tejo\jw
    E gran|de ^disci|^plina
    Acom|panhar o |^Mestre
    Nesta |Santa Dou|^trina
  \endchorus
  % verse 4
  \beginchorus
    Aten|^ção na jor|nada \altchords{\id[2]{(E)}|E | \e}
    Vamos |ver ^como |^é \altchords{| - Emaj7 |B}
    O tra|balho do |^Mestre \altchords{| - |B7}
    Je|sus nossa |^fé \altchords{| - |E}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Rota"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 4
      \repeat volta 2 {
        g8( \pomark g) | c4 c e | c c c8( c) | c4 b d | g,4( g)
        g8 g | g4 b d | g f d8( d) | b4 b g | c4( c4)
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Vi _ -- | san -- do~es -- te | ru -- mo;
        Va _ -- | mos co -- nhe -- | cer; __ _
        O tra -- | ba -- lho do | Mes -- tre;~E
        Seu __ _ | gran -- de po -- | der. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Se _ -- | guin -- do~es -- ta | ro -- ta;
        Nós __ _ | va -- mos che -- | gar; __ _
        No cen -- | tral da Dou -- | tri -- na;~A --
        on _ -- | de~o Mes -- tre~es -- | ta. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        É __ _ | gran -- de fes -- | te -- jo;~E
        gran _ -- | de dis -- ci -- | pli -- na;
        A -- com -- | pa -- nhar o | Mes -- tre;
        Nes -- ta | San -- ta Dou -- | tri -- na.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        A -- ten -- | ção na jor -- | na -- da;
        Va -- mos | ver co -- mo | é; __ _
        O tra -- | ba -- lho do | Mes -- tre;
        Je _ -- | sus nos -- sa | fé. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2. | c | c4 c2:maj7 | g2.
        | g | g:7 | g:7 | c2
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Observing this direction, let us discover
    The work of the Master, and His great power
    \nextverse
    Following this route we will arrive
    To the center of the Doctrine, where the Master is
    \nextverse
    It's a great celebration and great discipline
    To accompany the Master in this Holy Doctrine
    \nextverse
    Attention in the journey, let us see how it is
    The work of our Master, Jesus, our faith
  \end{translation}
\endsong


\beginsong{História}[by={Padr. Alfredo}, off={Glauco Vilas Boas}, key={Bm}, gk={Cm, (Bm)--(Cm)}, tags={mazurca}]
  \audio[key=Bm]{https://soundcloud.com/canaljagube/16-com-certeza-a-minha?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/118/Hist\%C3\%B3ria}
  \meter{6}{4}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{F#}]Com cer|\[\mnc{B}Bm]teza a \[^\mn{B}]mi\[^\mn{C#}]{nha\jw his}\[\mnc{D}D]tória \altchords{\id[1]{(Am) \capo{2}}|Am C}
    \[^\mn{B}]Por |\[Bm]onde eu \[^\mn{A#}]já \[^\mn{C#}]pas\[\mnc{F#}F#]sei \altchords{|Am E}
    Mos|trando a San\[^\mn{A#}]ta \[^\mn{C#}]Dou\[\mnc{F#}F#7]tri\[^\mn{C#}]na \altchords{| - E7}
    \[^\mn{E}]A |\[^\mn{D}]to\[^\mn{C#}]dos eu \[^\mn{A#}]en\[^\mn{C#}]si\[\mnc{B}Bm]nei \altchords{| - Am}
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    Com fir|^meza\jw a nossa Dou^trina
    Por |^onde esta pas^sando
    Mostra |Vossa disci^plina
    E a |todos está ensi^nando
  \endchorus
  % verse 3
  \beginchorus
    Viva\jw os |^mestres desta ^força \altchords{\id[2]{(Cm)}|Cm E\flt{}}
    Que |^{é quem} nos traz o re^médio \altchords{|Cm G}
    Con|tido no Santo ^Daime \altchords{| - G7}
    Ele vai |dando a quem lhe ^pede \altchords{| - Cm}
  \endchorus
  % verse 4
  \beginchorus
    Rece|^bemos com a^mor
    Enquanto\jw o |^nosso mundo\jw está gi^rando
    Como\jw é |bom cantar em ^roda
    Com nosso |Mestre nos ensi^nando
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "História"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative g'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key b \minor \time 6/4 \partial 4
      \repeat volta 2 {
        fis8 \pomark fis8
        | b4 b8( b) b,8 cis  d4( d8)( << d8) \single\altcol\parenthesize b8 \altmark "4." >> \altcol\parenthesize b8 b
        | b8( b) b8( b) ais8 cis  fis,4( fis) fis8( fis)
        | fis8( fis) fis( fis) ais cis  fis4 cis8( cis8) e8( e)
        | d8( d) cis8 cis ais cis  b4( b)
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Com cer -- | te -- za a mi -- nha~his -- tó -- ria; __ _
        "" Por | on _ -- de eu já pas -- sei; __ _
        Mos _ -- | tran -- do a San -- ta Dou -- tri -- na; __ _
        A __ _ | to _ -- dos eu en -- si -- nei. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Com fir -- | me -- za~a nos -- sa Dou -- tri -- na; __ _
        "" Por | on _ -- de es -- ta pas -- san -- do;
        Mos -- tra | Vos _ -- sa __ _ dis -- ci -- pli -- na; __ _
        E a | to -- dos es -- tá en -- si -- nan -- do.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Vi -- va~os | mes -- tres __ _ des -- ta for -- ça; __ _
        "" Que | é quem nos traz o re -- mé -- dio;
        Con _ -- | ti _ -- do no San -- to Dai -- me;
        E -- le vai | dan _ -- do a quem lhe pe -- de.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Re -- ce -- | be -- mos __ _ com a -- mor; __ _
        \altcol En -- \altcol quan -- to~o | nos -- so mun -- do~es -- tá gi -- ran -- do;
        Co -- mo~é | bom __ _ can _ -- tar em ro -- da;
        Com nos -- so | Mes _ -- tre nos en -- si -- nan -- do.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4
        | b2.:m d
        | b:m fis
        | fis fis:7
        | fis:7 b2:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    With certainty, my history, where I have already been
    Showing the Holy Doctrine I taught for everyone
    \nextverse
    With firmness, our Doctrine, wherever it is passing
    It shows Your discipline and is teaching everyone
    \nextverse
    Viva the masters of this force, who are who bring us the remedy
    Contained in the Holy Daime, He gives to those who ask Him
    \nextverse
    We receive with love while our world is turning
    How good it is to sing in a circle with our Master teaching us
  \end{translation}
\endsong


\beginsong{Relógio do Tempo}[by={Padr. Alfredo}, off={Josiana Mota}, key={C}, gk={D, C--D}]
  \audio[key=C]{https://soundcloud.com/canaljagube/17-relogio-do-tempo?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/119/Rel\%C3\%B3gioDoTempo}
  \newchords{chords_relogio_a}\newchords{chords_relogio_b}
  % verse 1
  \mnbeginchorus\memorize[chords_relogio_a]
    \[^\mn{G}]Quan\[^\mn{E}]do |\[\mncii{C}{A}Am]{é de manhã}\[\bmc\mn{C}]zinha para |\[\mncii{B}{G}G]mim \[\bm]
    Já é |\[\mnc{C}Am]meio-di\[^\mn{B}]{a\jw em} \[\bmc\mn{D}]ponto \[^\mn{A}]para\jw al|\[\mnc{G}G]guém \[\bm]
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_relogio_b]
    \[^\mauiic{C}{G}]Pa\[^\mauc{B}]ra |\[\mauiic{A}{C}\up{1}C \up{2}(Am)]{muitos es}\[^\mauc{B}]sa \[\bmc\mau{C}]hora já \[^\mnc{D}]é |\[\mnc{E}C]tar\[^\mn{G}]de \[\bm]
    E \[^\mn{A}]outro |\[^\mn{E}]tanto\jw a\jw i\[^\mnc{C}]lu\[^\mn{E}]mi\[\mnc{D}\up{1}G \up{2}(G7)]nária \[^\mnc{B}]lo\[^\mn{D}]go |\[\mnc{C}C]vem \[\bm]
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_relogio_a]
    Bem ce|^dinho é i^dade da cri|^ança ^ \altchords{\id[1]{(D)}|Bm |A}
    Logo |^mais vem vindo ^a maturi|^da^de \altchords{|Bm |A}
  \endchorus\glueverses
  \beginchorus\replay[chords_relogio_b]
    Prepa|^{rando para\jw a} ^hora da co|^lheita ^ \altchords{|\up{1}D \up{2}(Bm) |D}
    Colher de |tudo que plan^{tou nesta} ver|^da^de \altchords{| - \up{1}A \up{2}(A7) |D}
  \endchorus
  % verse 3
  \beginchorus\replay[chords_relogio_a]
    Neste |^mundo boas ^árvore dá bom |^fruto ^
    Depen|^dendo da ^sua\jw utili|^da^de
  \endchorus\glueverses
  \beginchorus\replay[chords_relogio_b]
    O nosso |^{Mestre nos} fa^lou da laran|^jeira ^
    Carre|gada de la^{ranja\jw em} seu hi|^ná^rio
  \endchorus
  % verse 4
  \beginchorus\replay[chords_relogio_a]
    Finda\jw o |^dia, vem a ^noite, é des|^canso ^
    Para |^quem cuida da ^sua\jw ativi|^da^de
  \endchorus\glueverses
  \beginchorus\replay[chords_relogio_b]
    Passa\jw a |^sombra, já nos ^vem o novo |^dia ^
    Pleno de |luz, o Sol com ^{sua clari}|^da^de
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Relógio do Tempo"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative a'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \sectionLabel "A"
      \repeat volta 2 {
        r8 \pomark g8 e | c8 a a a c c16( c16) c8 c | b4( g2) g8 g8 | c8( c) c b d d a a | g2( g8)
      }
      \sectionLabel "B:i"
      \parenthesize g8 g g   | c8 c c c   c c c d | e4 g4. \parenthesize g8 a a | e e c e d d b d | c2( c8)
      \sectionLabel "B:ii"
      \parenthesize c8 c b | a8 a a b c c c d | e4 g4. \parenthesize g8 a a | e e c e d d b d | c2 (c8)
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Quan -- do | é de ma -- nhã -- zi -- nha __ _ pa -- ra | mim; __ _
        Já é | mei -- o -- di -- a~em pon -- to pa -- ra~al -- | guém. __ _
      }
      \set stanza = "1.B:i"
      "" Pa -- ra | mui -- tos es -- sa ho -- ra já é | tar -- de;
      E ou -- tro | tan -- to~a~i -- lu -- mi -- ná -- ria lo -- go | vem. __ _
      \set stanza = "1.B:ii"
      "" Pa -- ra | mui -- tos es -- sa ho -- ra já é | tar -- de;
      E ou -- tro | tan -- to~a~i -- lu -- mi -- ná -- ria lo -- go | vem. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Bem ce -- | di -- nho é i -- da -- de __ _ da cri -- | an -- ça;
        Lo -- go | mais vem vin -- do a ma -- tu -- ri -- | da -- de.
      }
      \set stanza = "2.B:i"
      "" Pre -- pa -- | ran -- do pa -- ra~a ho -- ra da co -- | lhei -- ta;
      Co -- lher de | tu -- do que plan -- tou nes -- ta ver -- | da -- de.
      \set stanza = "2.B:ii"
      "" Pre -- pa -- | ran -- do pa -- ra~a ho -- ra da co -- | lhei -- ta;
      Co -- lher de | tu -- do que plan -- tou nes -- ta ver -- | da -- de.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Nes -- te | mun -- do bo -- as ár -- vo -- re dá bom | fru -- to;
        De -- pen -- | den _ -- do da su -- a~u -- ti -- li -- | da -- de.
      }
      \set stanza = "3.B:i"
      O nos -- so | Mes -- tre nos fa -- lou da la -- ran -- | jei -- ra;
      "" Car -- re -- | ga -- da de la -- ran -- ja~em seu hi -- | ná -- rio.
      \set stanza = "3.B:ii"
      O nos -- so | Mes -- tre nos fa -- lou da la -- ran -- | jei -- ra;
      "" Car -- re -- | ga -- da de la -- ran -- ja~em seu hi -- | ná -- rio.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Fin -- da~o | di -- a, vem a noi -- te, __ _ é des -- | can -- so;
        Pa -- ra | quem cui -- da da su -- a~a -- ti -- vi -- | da -- de.
      }
      \set stanza = "4.B:i"
      "" Pas -- sa~a | som -- bra, já nos vem o no -- vo | di -- a;
      Ple -- no de | luz, o Sol com su -- a cla -- ri -- | da -- de.
      \set stanza = "4.B:ii"
      "" Pas -- sa~a | som -- bra, já nos vem o no -- vo | di -- a;
      Ple -- no de | luz, o Sol com su -- a cla -- ri -- | da -- de.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1:m | g | a:m | g2~8
      }
      s4. | c1 | c | c2 g2 | c2~8
      s4. | a1:m | c | c2 g2:7 | c2~8
    }
    \layout { #(layout-set-staff-size 13.4) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN] \ifshowlilypond\scriptsize\fi
    When it is early morning for me, it's already midday for someone else
    For many it is already late, and for others the first light is about to come
    \nextverse
    Very early is the age of the child, soon enough comes maturity
    Preparing for the hour of the harvest, to harvest everything you planted in this truth
    \nextverse
    In this world a good tree gives good fruit, depending on its usefulness
    Our Master told us of the orange tree, laden with oranges in His hinário
    \nextverse
    The day ends, the night comes and it is rest, for those who carry out their activity
    The dark passes, the new day comes, full of light, the sun with its clarity
  \end{translation}
\endsong


\beginsong{A Justiça É Reta}[by={Padr. Alfredo}, off={Júlia}, key={Dm}, gk={Dm, Cm--E\flt{}m}, tags={valsa}]
  \audio[key=Cm]{https://soundcloud.com/canaljagube/18-a-justica-e-reta?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/120/AJusti\%C3\%A7a\%C3\%89Reta}
  \newchords{chords_justicareta_a}\newchords{chords_justicareta_b}
  \meter{3}{4}
  % verse 1
  \mnbeginchorus\memorize[chords_justicareta_a]
    \[^\mn{D}]Eu |\[\mnc{A}Dm]a\[^\mn{D}]mo |\[\mnc{B&}Em7&5]{bem es}\[^\mn{A}]sas |\[\mnc{G}A]for\[^\mn{E}]ças | \e
    \[^\mn{G}]Com |\[Gm]e\[^\mn{E}]las |\[\mnc{A}A]sigo can|\[\mnc{F}Dm]tan\[^\mn{D}]do | \e
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_justicareta_b]
    \[^\mn{A}]Bo\[^\mn{D}]ni|\[\mnc{F}Dm/F]císsi\[^\mn{D}]mo Je|\[\mnc{A}Dm]sus \[^\mn{D}]e \[^\mn{F}]Ma|\[A]ri\[^\mn{E}]a | \e
    \[^\mn{C#}]Com\jw o \[^\mn{E}]Di|\[^\mn{A}]vi\[^\mn{E}]no |\[\mnc{G}A7]Es\[^\mn{F}]píri\[^\mn{E}]to |\[\mnc{D}Dm]San|to
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_justicareta_a]
    Can|^tar amor |^{e ale}|^gria | \e
    Bus|^cando es|^tar com o |^Pai | \e
  \endchorus\glueverses
  \beginchorus\replay[chords_justicareta_b]
    Já |^disse to|^dos se pre|^parem | \e
    Ninguém |sabe |^aonde |^vai | \e
  \endchorus
  % verse 3
  \beginchorus\replay[chords_justicareta_a]
    Se|^guir real|^mente\jw a dou|^trina | \e
    E |^não alte|^rar nem um |^til | \e
  \endchorus\glueverses
  \beginchorus\replay[chords_justicareta_b]
    A jus|^{tiça é} |^reta e |^justa | \e
    E\jw a ma|téria vi|^ve por um |^fio | \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "A Justiça É Reta"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 3/4 \partial 2
      \sectionLabel "A"
      \repeat volta 2 {
        r4 \pomark d4 | a'4( a4) d,4 | bes'4 bes a | g4 e2~ | e2 g4
        | g4( g) e | a4 a a | f4( d2)~ | d4
      } \break
      \sectionLabel "B"
      \repeat volta 2 {
        \parenthesize a4 d | f8( f8) d4 d | a d f | f4 e2~ | e4 cis e
        | a4( a) e | g4 f8( f8) e4 | d2.( | d4)
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu | a _ -- mo | bem es -- sas | for -- ças; | _
        Com | e _ -- las | si -- go can -- | tan -- do. | _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Bo -- ni -- | cís -- si -- mo Je -- | sus e Ma -- | ri -- a; | _
        Com~o Di -- | vi _ -- no | Es -- pí -- ri -- to | San -- | to.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Can -- | tar a -- mor | e a -- le -- | gri -- a; | _
        Bus -- | can -- do es -- | tar com o | Pai. __ _ | _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        "" Já | dis _ -- se to -- | dos se pre -- | pa -- rem; | _
        Nin -- guém | sa _ -- be | a -- on _ -- de | vai. __ | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Se -- | guir re -- al -- | men -- te~a dou -- | tri -- na; | _
        E | não al -- te -- | rar nem um | til. __ _ | _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        A jus -- | ti _ -- ça é | re -- ta e | jus -- ta; | _
        E~a ma -- | té -- ria vi -- | ve por __ _ um | fio. __ | _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | d2.:m | e:m7.5- | a | a
        | g:m | a | d:m | d4:m
      }
      \repeat volta 2 {
        s2 | d2.:m/f | d:m | a | a
        | a | a:7 | d:m | d4:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I truly love these forces, with them I follow singing
    Most benevolent Jesus and Mary with the Divine Holy Spirit
    \nextverse
    To sing love and joy, seeking to be with the Father
    I already said all should prepare themselves, no on knows where they go
    \nextverse
    To truly follow the doctrine, and not alter even a tilde
    The justice is correct and fair, and the body hangs by a thread
  \end{translation}
\endsong


\beginsong{Contato}[by={Padr. Alfredo}, off={Bia}, key={C}, gk={D, C--D}]
  \audio[key=G]{https://soundcloud.com/canaljagube/19-contato?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/121/Contato}
  \newchords{chords_contato_a}\newchords{chords_contato_b}
  % verse 1
  \mnbeginchorus\memorize[chords_contato_a]
    \[^\mn{C}]Meu |\[\mnc{G}G]Pai, eu \[^\mn{B}]es\[\bmc\mn{D}]tou em \[^\mn{A}]seu \[^\mn{B}]con|\[\mnc{C}Am]ta\[^\mn{A}]to \[\bm]
    Meu |\[\mnc{G}G]Pai, con\[^\mnc{B}]ti\[\bmc\mn{D}]nuo a\jw o\[^\mnc{A}]b\[^\mn{B}]ser|\[\mnc{C}C]var \[\bm]
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_contato_b]
    \[^\mnc{C}]E pe\[^\mn{B}]lo |\[\mnc{A}F]giro que \[^\mnc{B}]o \[\bmc\mn{C}]tem\[^\mn{B}]{po\jw es}\[^\mn{C}]tá \[^\mn{D}]mos|\[\mnc{E}C]tran\[^\mn{G}]do \[\bm]
    \[^\mn{A}]É |\[^\mn{E}]tempo \[^\mn{C}]de \[^\mn{E}]vi\[\mnc{D}G7]ver e \[^\mn{C}]de \[^\mn{B}]a|\[\mnc{C}C]mar \[\bm]
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_contato_a]
    Meu |^Pai, em Vos^sa Santa Bon|^dade ^ \altchords{\id[1]{(D)}|A |Bm}
    Meu |^Pai, o que pu^der vou ensi|^nar ^ \altchords{|A |D}
  \endchorus\glueverses
  \beginchorus\replay[chords_contato_b]
    Filhos da |^Terra conti^nuam duvi|^dando ^ \altchords{|G |D}
    É |hora de vi^ver e de re|^zar ^ \altchords{| - A7 |D}
  \endchorus
  % verse 3
  \beginverse\replay[chords_contato_a]
    Meu |^Pai, Vos en^contro sobre |^tudo ^
    E sobre |^tudo nós de^vemos Lhe\jw ado|^rar ^
  \endverse\glueverses
  \beginverse\replay[chords_contato_a]
    Mãe Di|^vina\jw eterna^mente com\jw o Di|^vino ^
    Eterna|^mente\jw a vida\jw e^terna vigo|^rar ^
  \endverse\glueverses
  \beginchorus\replay[chords_contato_b]
    E mesmo |^que os tempos ^estejam fin|^dando ^
    Meu |pai e minha ^Mãe vamos lou|^var ^
  \endchorus
  \begin{translation}[EN]\iflyriconly\else\scriptsize\fi % to fit on one page
    My Father, I am in contact with You; my Father, I continue to observe
    And by the turn that the time is showing, it's the time to live and to love
    \nextverse
    My Father, in Your Holy Goodness; my Father, I will teach what I am able to
    The children of earth continue to doubt; It is the time to live and to pray
    \nextverse
    My Father, I meet You above all things and above all things we must adore You
    Divine Mother, eternally with the Divine, eternally invigorating eternal life
    And even if the times are nearing the end, let's praise my Father and my Mother
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Contato"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \sectionLabel "A"
      \repeat volta 2 {
        r8 \pomark c8( c8) | g8( g8) g8 b d d a b | c4 a4. \parenthesize a8 a8( a8)
        | g8( g8) g8 b d d a b | c2~8
      }
      \sectionLabel "B"
      \repeat volta 2 {
        c8 c b | a a a b c b c d | e4 g2 a4
        | e8 e c e d d c b | c2~8
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Meu __ _ | Pai, __ _ eu es -- tou em seu con -- | ta -- to;
        "" Meu __ _ | Pai, __ _ con -- ti -- nuo a~o -- b -- ser -- | var. _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        E pe -- lo | gi -- ro que o tem -- po~es -- tá mos -- | tran -- do;
        É | tem -- po de vi -- ver e de a -- | mar. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Meu __ _ | Pai, __ _ em Vos -- sa San -- ta Bon -- | da -- de;
        "" Meu __ _ | Pai, o que pu -- der vou en -- si -- | nar. _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Fi -- lhos da | Ter -- ra con -- ti -- nu -- am du -- vi -- | dan -- do;
        É | ho -- ra de vi -- ver e de re -- | zar. _
      }
    }
    theLyricsThree = \lyricmode {
      \repeat volta 2 {
        <<
          {
            \set stanza = "3.A:i"
            Meu __ _ | Pai, __ _ Vos en -- con -- tro so -- bre | tu -- do;
            E so -- bre | tu -- do nós de -- ve -- mos Lhe~a -- do -- | rar; _
          }
          \new Lyrics { \set associatedVoice = "theMelody"
            \set stanza = "3.A:ii"
            Mãe Di -- | vi -- na~e -- ter -- na -- men -- te com~o Di -- | vi -- no;
            E -- ter -- na -- | men -- te~a vi -- da~e -- ter -- na vi -- go -- | rar. _
          }
        >>
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        E mes -- mo | que os tem -- pos es -- te -- jam fin -- | dan -- do;
        Meu | pai e mi -- nha Mãe va -- mos lou -- | var. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | g1 | a:m | g | c2~8
      }
      \repeat volta 2 {
        s4. | f1 | c | c2 g:7 | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Meu Pai}[by={Padr. Alfredo}, off={Celso Ferrareze}, key={C}, gk={C, B\flt{}--E}]
  \audio[key=C]{https://soundcloud.com/canaljagube/20-meu-pai?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/122/MeuPai}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{E}]Meu |\[\mnc{G}C]Pai, meu \[\bmc\mn{E}]Pai, \[^\mn{F}]meu |\[^\mn{G}]Pai\[\bmc\mncadj{-.2ex}{E}] \altchords{\id[1]{(D}|D | \e}
    A|\[\mnc{D}Am]qui \[^\mn{C}]a\[\bmc\mn{A}]on\[^\mn{C}]{de\jw es}|\[\mnc{E}C]tou\[\bm] \altchords{|Bm |D}
    Para |\[\mnc{D}Am]te \[^\mn{C}]a\[\bmc\mn{A}]gra\[^\mn{C}]de|\[\mnc{E}C]cer\[\bm] \altchords{|Bm |D}
    \[^\mn{C}]Dai\[^\mn{E}]me |\[\mnc{D}G]for\[^\mn{C}]{ça\jw e} \[\mnc{A}F]dai\[^\mn{C}]{me\jw a}|\[C]mor\[\bm] \altchords{|A G |D}
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    Daime |^força\jw e ^daime\jw a|mor^ \altchords{\id[2]{(E)}|E | \e}
    Meu |^Pai a^onde\jw es|^tou^ \altchords{|C\shrp{}m |E}
    Para |^em Vós ^traba|^lhar^ \altchords{|C\shrp{}m |E}
    Com fir|^meza\jw e ^com vi|^gor^ \altchords{|B A |E}
  \endchorus
  \begin{translation}[EN]
    My Father, my Father, my Father
    Here where I am
    To give you thanks
    Give me strength and give me love
    \nextverse
    Give me strength and give me love
    My Father where I am
    So I can work in You
    With firmness and with vigor
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Meu Pai"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        e8( \pomark e) | g4 g e f | \once\slurSolid g2( e4) e | d c a c | e2.
        e8 e | d4 c a c | e2. c8 e | d4 c a4 c | c2.
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Meu __ _ | Pai, meu Pai, meu | Pai; _
        A -- | qui a -- on -- de~es -- | tou;
        Pa -- ra | te a -- gra -- de -- | cer;
        Dai -- me | for -- ça~e dai -- me~a -- | mor.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Dai -- me | for -- ça~e dai -- me~a -- | mor; _
        Meu | Pai a -- on -- de~es -- | tou;
        Pa -- ra | em Vós tra -- ba -- | lhar;
        Com fir -- | me -- za~e com vi -- | gor.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | c | a:m | c | a:m | c | g2 f2 | c2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Mamãe Vosso Brilho É Tão Lindo}[by={Padr. Alfredo}, off={Jonas e Unaqui}, key={Bm}, gk={Bm, (Bm)--(Cm)}, tags={valsa}]
  \audio[key=Am]{https://soundcloud.com/canaljagube/21-mamae-vosso-brilho-e-tao?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/123/Mam\%C3\%A3eVossoBrilho\%C3\%89T\%C3\%A3oLindo}
  \meter{3}{4}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{F#}]Ma|\[\mnc{B}Bm]mãe Vos\[^\mn{D}]so |\[^\mn{F#}]bri\[^\mn{D}]{lho\jw é} \[^\mn{C#}]tão |\[^\mn{B}]lin|\[B7]do \altchords{\id[1]{(Cm)}|Cm | - | - |C7}
    A |\[\mnc{E}Em]sombra \[^\mn{G}]{é\jw a}|\[^\mn{B}]pe\[^\mn{G}]nas \[^\mn{F#}]um |\[^\mn{E}]véu | \e \altchords{|Fm | - | - | \e}
    Vos\[^\mn{F#}]sa |\[\mnc{C#}F#]face |\[F#7]i\[^\mn{D}]lu\[^\mn{E}]mi|\[\mnc{F#}Bm]nada \altchords{|G |G7 |Cm}
    Ma|\[\mnc{E}Em]mãe da |\[\mnc{D}Em7/D]ter\[^\mn{C#}]ra, \[^\mn{B}]Ma|\[\mnc{A#}F#]mãe \[^\mn{C#}]do |\[\mnc{B}Bm]céu | \e \altchords{|Fm |Fm7/E\flt{} |G |Cm | \e}
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    E |^Sois a |luz, Mãe da |luz |^ \e \altchords{|Cm | - | - |C7}
    A |^luz que |vem de Je|sus | \e \altchords{|Fm | - | - | \e}
    E|^terno |^brilho do |^sol \altchords{|G |G7 |Cm}
    |^Vida, ca|^minho, a |^todos con|^duz | \e \altchords{|Fm |Fm7/E\flt{} |G |Cm | \e}
  \endchorus
  \noteson
  % verse 3
  \mnbeginchorus
    \ind \[\mn{F#}]No |\[\mnc{B}Bm]claro,\jw a \[\mn{D}]pre|\[\mn{F#}]sen\[\mn{D}]ça \[\mn{C#}]de |\[\mn{B}]Deus |\[B7]{} \e \altchords{|Cm | - | - |C7}
    \ind Para |\[\mnc{E}Em]sempre \[\mn{G}]eu |\[\mncii{B}{G}]sou, \[\mn{F#}]sou |\[\mn{E}]eu | \e \altchords{|Fm | - | - | \e}
    \ind \[\mn{F#}]Cons|\[\mnc{C#}F#]tante sa|\[F#7]ú\[\mn{D}]de \[\mn{E}]em |\[\mnc{F#}Bm]si \altchords{|G |G7 |Cm}
    \ind \[\mn{F#}]A |\[\mnc{D}Em7/D]vi\[\mn{C#}]da \[\mn{B}]que |\[\mnc{A#}F#7]nunca \[\mn{C#}]mor|\[\mnc{B}Bm]reu \altchords{|Fm7/E\flt{} |G7 |Cm}
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Mamãe Vosso Brilho É Tão Lindo"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative fis' {
      \set melismaBusyProperties = #'() \slurDashed
      \key b \minor \time 3/4 \partial 4
      \sectionLabel "1.-2."
      \repeat segno 2 {
        \repeat volta 2 {
          fis4 | b4( b) d | fis d cis | b2.( | b4)( b) b | e( e) g | b g fis | e2.~ | e4( e) fis
          | cis2 cis4 | cis d e | fis( fis fis) | e( e) e d cis b | ais( ais) cis | b2.~ | b2
        }
      } \break
      \sectionLabel "3."
      \repeat volta 2 { \slurSolid
        fis4 \pomark | b4 b d | fis d cis | b2.~ | b4 b b | e e g | b( g) fis | e2.~ | e2 fis4
        | cis cis cis | cis d e | fis2 fis,4 | d' cis b | ais ais cis | b2
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
         Ma -- | mãe Vos -- so | bri -- lho~é tão | lin -- | do; __ _
         A | som -- bra é~a -- | pe -- nas um | véu; __ | _
         Vos -- sa | fa -- ce | i -- lu -- mi -- | na -- da;
         Ma -- | mãe __ _ da | ter -- ra, Ma -- | mãe __ _ do | céu. | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        E | Sois __ _ a | luz, Mãe da | luz; __ | _ _
        A | luz __ _ que | vem de Je -- | sus; __ | _ _
        E -- | ter -- no | bri -- lho do | sol; __ _ _
        | Vi -- da, ca -- | mi -- nho, a | to -- dos con -- | duz. | _
      }
      \set stanza = "3."
      \repeat volta 2 {
        No | cla -- ro,~a pre -- | sen -- ça de | Deus; | _
        Pa -- ra | sem -- pre eu | sou, _ sou | eu; | _
        Cons -- | tan -- te sa -- | ú -- de em | si;
        A | vi -- da que | nun -- ca mor -- | reu.
      }
    }
    theChords = \chordmode {
      \repeat segno 2 {
        \repeat volta 2 {
          s4 | b2.:m | b:m | b:m | b:7 | e:m | e:m | e:m | e:m
          | fis | fis:7 | b:m | e:m | b:m | fis | b:m | b2:m
        }
      }
      \repeat volta 2 {
        s4 | b2.:m | b:m | b:m | b:7 | e:m | e:m | e:m | e:m
        | fis | fis:7 | b:m | e:m7/d | fis:7 | b2:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Mama, Your brilliance is so beautiful; darkness is but a veil
    Your illuminated face, Mama of the earth, Mama of Heaven
    \nextverse
    And You are the light, Mother of light; The light that comes from Jesus
    Eternal brilliance of the sun, life, path, directs everyone
    \nextverse
    In the clarity, the presence of God; forever I am, it is I
    Constant yearning in You, the life that never died
  \end{translation}
\endsong


\beginsong{Criancinha}[by={Padr. Alfredo}, off={Anamélia}, key={C}, gk={B, C--E}]
  \audio[key=C]{https://soundcloud.com/canaljagube/22-criancinha?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/124/Criancinha}
  \newchords{chords_criancinha_a}\newchords{chords_criancinha_b}
  % verse 1
  \mnbeginchorus\memorize[chords_criancinha_a]
    |\[\mnc{G}G]Mais u\[^\mn{B}]ma \[\bmc\mn{D}]vez eu \[^\mn{A}]vou \[^\mnc{B}]di|\[\mnc{C}C]zer \[\bm] \altchords{\id[1]{(D)}|A |D}
    |\[\mnc{G}G]Que Je\[^\mn{B}]sus \[\bmc\mn{D}]Cristo \[^\mn{A}]es\[^\mn{B}]tá |\[\mnc{C}C]cer\[\bm]to \altchords{|A |D}
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_criancinha_b]
    \[^\mn{C}]O \[^\mn{E}]es|\[\mnc{C}C]pírito \[^\mn{E}]é \[\bmc\mn{C}]forte Vós \[^\mn{E}]meu |\[\mnc{G}G]Pai\[\mnc{F}G7] \altchords{|D |A A7}
    Mas a |\[\mnc{G}G]car\[^\mn{B}]ne \[\mnc{D}G7]também \[^\mn{A}]é \[^\mn{B}]a |\[\mnc{C}C]Terra \[\bm] \altchords{|A A7 |D}
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus\replay[chords_criancinha_a]
    \noteson\[\mnd{C}]Da\notesoff{}|^í só ^o Santo per|^dão ^
    |^Para total^mente ficar |^per^to
  \endchorus\glueverses
  \beginchorus\replay[chords_criancinha_b]
    |^Para total^mente ter fir|^me^za
    É pre|^ciso total^mente ficar |^cer^to
  \endchorus
  % verse 3
  \beginchorus\replay[chords_criancinha_a]
    |^Como\jw um santo ^filho de Ma|^ri^a \altchords{\id[2]{(E)}|B |E}
    Ino|^cência de ^uma crian|^ci^nha \altchords{|B |E}
  \endchorus\glueverses
  \beginchorus\replay[chords_criancinha_b]
    Sois bon|^dade, sois be^leza, Vós meu |^Pai^ \altchords{|E |B B7}
    Minha |^Mãe, Vós sois pu^reza\jw e sois Ra|^i^nha \altchords{|B B7 |E}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Criancinha"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \sectionLabel "A"
      \repeat volta 2 {
        \parenthesize c4 \pomark | g8( g8) \parenthesize g8 b d d a b | c2( c4) \parenthesize c8 \parenthesize c8
        | g8( g) g8 b d d a b | c2 c4
      } \break
      \sectionLabel "B"
      \repeat volta 2 {
        \parenthesize c8 \parenthesize e | c8. c16 c8 e8 c8. c16 c8 e8 | g2( f4) f8 f
        | g,8( g8 g8) b8 d d a b | c2 c4
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        "" | Mais __ _ u -- ma vez eu vou di -- | zer; __ _
        "" "" | Que __ _ Je -- sus Cris -- to es -- tá | cer -- to.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        O es -- | pí -- ri -- to é for -- te Vós meu | Pai; __ _
        Mas a | car _ _ -- ne tam -- bém é a | Ter -- ra.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Da -- | í __ _ "" só o San -- to per -- | dão; __ _
        "" "" | Pa -- ra to -- tal -- men -- te fi -- car | per -- to.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        "" "" | Pa -- ra to -- tal -- men -- te ter fir -- | me -- za;
        É pre -- | ci -- so to -- tal -- men -- te fi -- car | cer -- to.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        "" | Co -- mo~um san -- to fi -- lho de Ma -- | ri -- a;
        I -- no -- | cên _ -- cia de u -- ma cri -- an -- | ci -- nha.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Sois bon -- | da -- de, sois be -- le -- za, Vós meu | Pai; __ _
        Mi -- nha | Mãe, Vós sois pu -- re -- za~e sois Ra -- | i -- nha.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | g1 | c | g | c2.
      }
      \repeat volta 2 {
        s4 | c1 | g2 g:7 | g2 g:7 | c2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    One more time I'm going to say that Jesus Christ is correct
    The spirit is strong, You my Father; but the flesh also is the Earth
    \nextverse
    From here, only Holy Forgiveness; to totally stay close
    To totally have firmness, one needs to become completely correct
    \nextverse
    Like a Holy child of Mary, innocence of a little child
    You are goodness, are beauty, You my Father; My Mother, You are purity and are Queen
  \end{translation}
\endsong


\beginsong{Oh! Virgem da Conceição}[ititle={O Mestre Encantando na Mata}, by={Padr. Alfredo}, off={Meire}, key={Am}, gk={Am, (G\shrp{}m)--(Cm)}, tags={valsa}]
  \audio[key=Am]{https://soundcloud.com/canaljagube/23-virgem-da-conceicao?in=ivo-nei/sets/nova-era-padrinho-alfredo}
  \audio{https://nossairmandade.com/hymn/125/Oh!VirgemDaConcei\%C3\%A7\%C3\%A3o}
  \meter{3}{4}
  \newchords{chords_ohvirgem_a}\newchords{chords_ohvirgem_b}
  % verse 1
  \mnbeginverse\memorize[chords_ohvirgem_a]
    \[^\mn{E}]Oh! |\[\mnc{A}Am]Virgem |da Con\[^\mn{C}]cei|\[^\mn{A}]ção | \e
    \[^\mn{E}]Oh! |\[^\mn{A}]Minha \[^\mn{E}]San|\[^\mn{C}]tíssi\[^\mn{A}]ma \[^\mn{C}]Se|\[\mnc{E}(C)]nho|\[Am]ra
    \[^\mn{A}]Habi|\[\mnc{D}Dm]tai o |\[^\mn{F}]meu \[^\mn{D}]pen\[^\mn{B}]sa|\[\mnc{A}Am]men|to
    Ha\[^\mnc{C}]bi|\[\mnc{E}(C)]{tai\jw o} meu \[^\mn{C}]co|\[\mnc{A}Am]ra\[^\mn{E}]ção \[^\mn{C}]a|\[\mnc{B}E]go|ra
    Ha\[^\mnc{C}]bi|\[\mnc{D}Dm]tai o |\[^\mn{F}]meu \[^\mn{D}]pen\[^\mn{B}]sa|\[\mnc{A}Am]men|to
    Ha\[^\mnc{C}]bi|\[\mnc{E}(C)]{tai\jw o} meu \[^\mn{C}]co|\[\mnc{A}Am]ra\[^\mn{E}]ção \[^\mn{C}]Se|\[\mnc{B}E]nho|ra
  \mnendverse\glueverses
  \mnbeginchorus\memorize[chords_ohvirgem_b]
    \[^\mn{E}]Oh! |\[\mnc{A}Am]Vir\[^\mn{G#}]{}|\[^\mn{A}]gem Mãe \[^\mn{B}]Di|\[\mnc{C}(C)]vi|\[\mnc{A}Am]na
    \[^\mn{E}]Oh! |\[^\mn{A}]Vir\[^\mn{E}]gem |\[\mauiic{C}{C}\up{1}F \up{2}(E7)]Nos\[^\mauii{B}{A}]sa \[^\mauii{C}{C}]Se|\[\mauiic{A}{C}\up{1}C \up{2}(Am)]nho|ra
  \mnendchorus
  \notesoff
  % verse 2
  \beginverse\replay[chords_ohvirgem_a]
    Pre|^sente de |Aniver|sá|rio
    Salve, |salve\jw o bom |Mestre\jw Iri|^neu |^ \e
    Santo |^Daime, |Sabedo|^ri|a
    Esta |^força\jw o meu |^Mestre me |^deu | \e
    Nosso |^chefe Se|nhor São Jo|^ão | \e
    Repas|^sou e meu |^pai rece|^beu | \e
  \endverse\glueverses
  \beginchorus\replay[chords_ohvirgem_b]
    O |^Mestre |que nos en|^si|^na
    Para |sempre co|^{nosco vi}|^veu | \e
  \endchorus
  % verse 3
  \beginverse\replay[chords_ohvirgem_a]\ifshowlilypond\normalsize\fi % to fit on a spread
    E |^vive no |meu cora|ção | \e
    Tão su|blime a |vida de |^Deus |^ \e
    Eterna|^mente\jw eu Vos |agrade|^cer | \e
    Esta |^vida nos|^{so Pai} nos |^deu | \e
    Vosso |^brilho nos |fortale|^ceu | \e
    Para |^sempre ser |^{um filho} |^Seu | \e
  \endverse\glueverses
  \beginchorus\replay[chords_ohvirgem_b]\ifshowlilypond\normalsize\fi % to fit on a spread
    O |^Mestre\jw encan|tado na |^ma|^ta
    Esta |Santa Dou|^{trina nos} |^deu | \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Oh! Virgem da Conceição"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 4
      \sectionLabel "A"
      e4 \pomark | a4( a) a | a a c | a2.( | a4) \parenthesize e e | a a e | c a c | \once\slurUp e2.( | \once\slurUp e8)( << e) \parenthesize \single\altcol a, \altmark "3." >> a4 a
      | d4( d) d | f d b | a2.( | a4) a c | e e c | a e c' | b2.( | b4)( b) c
      | d4( d) d | f d b | a2.( | a4) a c | e e c | a e c' | b2.( | b4)( b)
      \sectionLabel "B"
      \repeat volta 2 {
        e4 | a( a)( gis) | a a b | c2. | a4 \parenthesize e e | a( a) e
      } \alternative {
        { | c4 a c | c2.( | c2) }
        { | c4 b c | a2.( | a2) }
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Oh! | Vir _ -- gem | da Con -- cei -- | ção; __ | _
      "" Oh! | Mi -- nha San -- | tíssi -- ma Se -- | nho -- | ra;
      "" Ha -- bi -- | tai __ _ o | meu pen -- sa -- | men -- | to;
      Ha -- bi -- | tai~o meu co -- | ra -- ção a -- | go -- | ra;
      Ha -- bi -- | tai __ _ o | meu pen -- sa -- | men -- | to;
      Ha -- bi -- | tai~o meu co -- | ra -- ção Se -- | nho -- | ra. __ _
      \set stanza = "1.B"
      \repeat volta 2 {
        Oh! | Vir _ _ -- | gem Mãe Di -- | vi -- | na;
        "" Oh! | Vir _ -- gem
      } \alternative {
        { | Nos -- sa Se -- | nho -- | ra. }
        { | Nos -- sa Se -- | nho -- | ra. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Pre -- | sen -- te de | A -- ni -- ver -- | sá -- | rio;
      Sal -- ve, | sal -- ve~o bom | Mes -- tre~I -- ri -- | neu; __ | _
      "" San -- to | Dai _ -- me, | Sa -- be -- do -- | ri -- | a;
      Es -- ta | for -- ça~o meu | Mes -- tre me | deu; __ | _
      Nos -- so | che -- fe Se -- | nhor São Jo -- | ão; __ | _
      Re -- pas -- | sou e meu | pai re -- ce -- | beu. __ | _ _
      \set stanza = "2.B"
      \repeat volta 2 {
        O | Mes _ -- tre | que nos en -- | si -- | na;
        Pa -- ra | sem -- pre co --
      } \alternative {
        { | nos -- co vi -- | veu. __ | _ }
        { | nos -- co vi -- | veu. __ | _ }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
        E | vi -- ve no | meu co -- ra -- | ção; __ | _
        Tão su -- | bli -- me a | vi -- da de | Deus; __ | _
        \altcol E -- ter -- na -- | men -- te~eu Vos | a -- gra -- de -- | cer; __ | _
        Es -- ta | vi -- da nos -- | so Pai nos | deu; __ | _
        Vos -- so | bri -- lho nos | for -- ta -- le -- | ceu; __ | _
        Pa -- ra | sem -- pre ser | um fi -- lho | Seu. __ | _ _
      \set stanza = "3.B"
      \repeat volta 2 {
        O | Mes -- tre~en -- can -- | ta -- do na | ma -- | ta;
        Es -- ta | San -- ta Dou --
      } \alternative {
        { | tri -- na nos | deu. __ | _ }
        { | tri -- na nos | deu. __ | _ }
      }
    }
    theChords = \chordmode {
       s4 | a2.:m | a:m | a:m | a:m
       | a:m | a:m | \parenthesize c | a:m
       | d:m | d:m | a:m | a:m
       | \parenthesize c | a:m | e | e
       | d:m | d:m | a:m | a:m
       | \parenthesize c | a:m | e | e2
      \repeat volta 2 {
        s4 | a2.:m | a:m | \parenthesize c | a:m | a:m
      } \alternative {
        { | f | c | c2 }
        { | e2.:7 | a:m | a2:m }
      }
    }
    \layout { #(layout-set-staff-size 10.2) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]\tiny % to fit on same page
    Oh! Virgin of the Conception; oh! My Most Holy Lady
    Inhabit my thoughts; inhabit my heart now
    Inhabit my thoughts; inhabit my heart, My Lady
    \ind Oh! Virgin Divine Mother; oh! Virgin Our Lady
    \nextverse
    Birthday present; hail, hail the good Master Irineu
    Santo Daime, Wisdom; this force the Master gave me
    Our chief, Lord Saint John; passed it on and my father received it
    \ind The Master who teaches us; he always lived with us
    \nextverse
    And lives in my heart; so sublime the life of God
    Eternally I thank You; this life our Father gave us
    Your shine strengthened us; forever to be a son of Yours
    \ind The Enchanted Master in the forest; gave us this Holy Doctrine
  \end{translation}
\endsong
