% Santo Daime: Hinos da Santa Maria
% =================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Quem Procurar Esta Casa}[by={Mestre Irineu Serra}, ph={I}, key={Am}, sks={Am, Gm--G\shrp{}m--(Am)}]
  % Also in: Cruzeirinho
  \audio{https://www.nossairmandade.com/hymn/90/QuemProcurarEstaCasa}
  \mnbeginchorus\memorize
    |\[\mnc{A}Am]Quem pro\[^\mn{B}]cu\[\bmc\mn{C}]rar \[^\mn{B}]es\[^\mn{A}]ta |\[\mnc{F}Dm/F]ca\[\mnc{D}Dm]sa \altchords{\id{(Em) \capo{5}}|Em |Am/C Am}
    |\[\mnc{A}F]Que a\[^\mn{B}]qui \[\mnc{C}(Bm7&5)]ne\[^\mn{B}]la \[^\mn{A}]che|\[\mnc{E}E]gar \[(E7)] \altchords{|C (F\shrp{}m7\flt{}5) |B (B7)}
    \lrep \[^\mn{E}]En|\[\mnc{A}Am]contra \[^\mn{B}]{com a} \[\mnc{C}(C)]Vir\[^\mn{B}]gem \[^\mn{A}]Ma|\[\mncii{D}{F}Dm]ri\[\mnc{A}(F)]a \altchords{|Em (G) |Am (C)}
    |\[\mnc{E}Am]Su\[^\mn{F}]a \[^\mn{E}]sa\[\mnc{D}E7]úde \[^\mn{C}]E\[^\mn{B}]la |\[\mnc{A}Am]dá \[\bm] \rrep \altchords{|Em B7 |Em}
  \mnendchorus
  \notesoff
  \beginchorus
    Mi|^nha Sempre ^Virgem Ma|^ri^a \altchords{\id[4]{ED (Am)}|Am |Dm}
    |^Perdoai ^{os filhos} |^seus ^ \altchords{|F G |C}
    \lrep |^Vós como ^Mãe sobe|^ra^na \altchords{|Am |Dm F}
    |^A Divi^na Mãe de |^Deus^ \rrep \altchords{|E E7 |Am}
  \endchorus
  \beginchorus
    |^Eu peço a ^vós, bem con|^tri^to \altchords{\id[5]{AP (Am)}|Am C |F Dm}
    Fa|^zendo as mi^{nhas ora}|^ções ^ \altchords{|Am C |E}
    \lrep |^Peço a vós ^a Santa |^Lu^z \altchords{|Am C |Dm F}
    |^Para ilumi^nar o meu per|^dão ^ \rrep \altchords{|E Dm |Am}
  \endchorus
  \beginchorus
    |^Aqui den^tro desta |^ca^sa \altchords{\id[6]{simples (Am)}|Am |Dm}
    |^Tem tudo ^{que procu}|^rar ^ \altchords{|Am |E}
    \lrep |^Seguindo ^o bom ca|^mi^nho \altchords{|Am |Dm}
    |^Fazer bem, ^não fazer |^mal ^ \rrep \altchords{|E |Am}
  \endchorus
  \brk
  %% This note only in Santa Maria hinos:
  \textnote{Este hino é cantado antes da consagração de Santa Maria.}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative a'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \parenthesize e4\posectionmark "A" \genmark "(2.)" | a4 a8 b8 c4 b8 a8 | f2 d4( d4)
      | a'4 a8 b8 c4 b8 a8 | e2.
      \repeat volta 2 {
        \parenthesize e4\sectionmark "B" \genmark "(1.)" | a,4 a8 b8 c4 b8 a8 | \once\slurSolid d4.( f8)( a2)
        \slurDashed
        | e8( e8) f8 e8 d8( d8) c8 b8
      } \alternative {
        { | a2. }
        { | a2. \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 | Quem pro -- cu -- rar es -- ta | ca -- sa; __ _
      | Que a -- qui ne -- la che -- | gar;
      \repeat volta 2 {
        \set stanza = "1.B"
        En -- | con -- tra com~a Vir -- gem Ma -- | ri -- _ a;
        | Su -- _ a sa -- ú -- de E -- la
      } \alternative {
        { | dá. }
        { | dá. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Mi -- | nha Sem -- pre Vir -- gem Ma -- | ri  -- a; __ _
      | Per -- do -- ai os fi -- lhos | seus.
      \repeat volta 2 {
        \set stanza = "2.B"
        \skip 1 | Vós co -- mo Mãe so -- be -- | ra -- _ na;
        | A __ _ Di -- vi -- na __ _ Mãe de
      } \alternative {
        { | Deus. }
        { | Deus. }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
        \skip 1 Eu pe -- ço~a vós bem con -- | tri -- to;
        Fa -- | zen -- do~as mi -- nhas o -- ra -- | ções.
      \repeat volta 2 {
        \set stanza = "3.B"
        \skip 1 | Pe -- ço~a vós a San -- ta | Luz; __ _ _
        | Pa -- ra~i -- lu -- mi -- nar o meu per --
      } \alternative {
        { | dão. }
        { | dão. }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 | A -- qui den -- tro des -- ta ca -- sa; __ _
      | Tem tu -- do que pro -- cu -- | rar.
      \repeat volta 2 {
        \set stanza = "4.B"
        \skip 1 | Se -- guin -- do o bom ca -- | mi -- _ nho;
        | Fa -- _ zer bem não __ _ fa -- zer
      } \alternative {
        { | mal. }
        { | mal. }
      }
    }
    theChords = \chordmode {
      s4 | a1:m | d2:m/f d:m
      | f2 \parenthesize b:m7.5- | e \parenthesize e4:7
      \repeat volta 2 {
        s4 | a2:m \parenthesize c | d:m \parenthesize f
        | a:m e:7
      } \alternative {
        { | a2.:m }
        { | a2.:m }
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}\footnotesize % to fit whole song on one spread
    Whoever arrives at this house and comes into it here
    Encounters the Virgin Mary, she is who gives you your well being
    \nextverse
    My Always Virgin Mary, forgive Your children
    You as Sovereign Mother, the Divine Mother of God
    \nextverse
    I beg You so contritely doing my prayers
    I ask Your Holy Light to illuminate my release
    \nextverse
    Here in this house there is everything to find
    Following the right path, doing the right and not the wrong
  \end{translation}
\endsong


\beginsong{Ave Maria}[by={Padr. Alfredo},tags={valsa},key={G},sks={A, G}]
  \audio[key={A}]{https://www.nossairmandade.com/hymn/547/AveMaria}
  \audio[key={A}]{https://www.youtube.com/watch?v=kSjNgg_-iD0&t=200s}
  \transpose{-2}
  \meter{3}{4}
  \newchords{chords_avemaria_a}\newchords{chords_avemaria_b}
  \mnbeginchorus\memorize[chords_avemaria_a]
    |\[\mnc{A}A]Ave Ma|\[\mnc{E}E]ria pa|\[\mnc{C#}E7]ra me \[^\mn{B}]lemb|\[\mnc{A}A]rar
    \[^\mn{B}]Que |\[\mnc{C#}F#m]é \[^\mn{B}]min\[^\mn{A}]ha |\[\mnc{E}E]Mãe \[^\mn{B}]mãe |\[\mnc{D}\up{1}Bm7 \up{2}(E7)]do \[^\mn{C#}]nos\[^\mn{/}]so |\[\mnc{/}\up{1}E \up{2}(A)]Pai
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_avemaria_b]
    |\[\mnc{A}A7]San\[^\mn{B}]ta \[^\mn{C#}]Ma|\[\mnc{D}D]ria \[^\mn{F#}]para |\[\mnc{B}Bm]não \[^\mn{A}]es\[^\mn{F#}]que|\[\mnc{E}A]cer
    |\[\mnc{F#}\up{1}F#m7 \up{2}(D)]{Que o} \[^\mn{E}]nosso |\[\mnc{B}\up{1}Bm \up{2}(E)]{Pai é} \[^\mn{C#}]o |\[\mnc{/}\up{1}Bm7 \up{2}(E7)]Rei \[^\mn{C#}]do \[^\mn{/}]Po|\[\mnc{/}\up{1}E \up{2}(A)]der
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_avemaria_a]
    |^Tem vosso |^Filho o |^Príncipe da |^Paz
    Que |^{é quem} se|^gura o ba|^{lanço do} |^Pai
  \endchorus\glueverses\beginchorus\replay[chords_avemaria_b]
    To|^do mundo |^geme e vai |^estreme|^cer
    Só |^{não Jesus} |^{Cristo e} quem lhe |^obede|^cer
  \endchorus
  \beginchorus\replay[chords_avemaria_a]
    |^Palavras |^minhas pa|^lavras de |^Deus
    Pe|^dindo e ro|^gando |^{por todos} |^seres
  \endchorus\glueverses\beginchorus\replay[chords_avemaria_b]
    Que |^nos aco|^berte e quem |^quiser se|^guir
    E a |^{vossa von}|^{tade há} |^{de se cump}|^rir
  \endchorus
  \beginchorus\replay[chords_avemaria_a]
    Eu |^estou a|^qui a|^li, estou |^lá
    |^Em toda |^parte que |^{me procu}|^rar
  \endchorus\glueverses\beginchorus\replay[chords_avemaria_b]
    Eu |^sou peque|^nino mas |^{dá para} ser |^ver
    Sou |^{o infi}|^{nito para} |^{quem perce}|^ber
  \endchorus
  \brk
  \beginchorus\replay[chords_avemaria_a]
    Vou |^esclare|^cendo não |^vim enga|^nar \altchords{\id[3]{O (G)}|G | | | \e}
    Meu |^Pai reu|^niu e man|^{dou apu}|^rar \altchords{|\up{1}G \up{2}Em |D |\up{1}Am7 \up{2}C |\up{1}D \up{2}G \e}
  \endchorus\glueverses\beginchorus\replay[chords_avemaria_b]
    Se|^gurem o ba|^lanço não vão |^esmore|^cer \altchords{|G |C |Am |D}
    Que |^{esta vi}|^{tória vai} |^aconte|^cer \altchords{|D |Am |\up{1}Am \up{2}D |\up{1}D \up{2}G}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose a g \relative a'' {
      \key a \major \time 3/4
      \repeat volta 2 {
        a4\posectionmark "A" a4 a4 | e4 e4 e4 | cis4 cis4 b4 | a2 b4
        | cis4 b4 a4 | e'2 b4
      } \alternative {
        { | d4 cis4 d4 | e2. }
        { | d4 cis4 b4 | a2. }
      }
      \repeat volta 2 {
        | a4\sectionmark "B" b4 cis4 | d4 d4 fis8 fis8 | b4 a4 fis4 | e2.
      } \alternative {
        { | fis4 e4 e4 | b4 b4 cis4 | d4 cis4 d4 | e2. }
        { | fis4 e4 e4 | b4 b4 cis4 | e4 cis4 b4 | a2. \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        | A -- ve Ma -- | ri -- a pa -- | ra me lem -- | brar;
        Que | é mi -- nha | Mãe mãe
      } \alternative {
        { | do nos -- so | Pai; }
        { | do nos -- so | Pai. }
      } \break
      \repeat volta 2 {
        | San -- ta Ma -- | ri -- a pa -- ra | não es -- que -- | cer;
      } \alternative {
        { | Que~o nos -- so | Pai é o | Rei do Po -- | der; }
        { | Que~o nos -- so | Pai é o | Rei do Po -- | der. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        | g2. | d | d:7 | g
        | e:m | d
      } \alternative {
       { | a:m7 | d }
       { | d:7 | g }
      }
      \repeat volta 2 {
        | g:7 | c | a:m | g
      } \alternative {
        { | e:m7 | a:m | a:m7 | d }
        { | c | d | d:7 | g }
      }
    }
    \layout { #(layout-set-staff-size 15) } % to fit whole song on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Hail Mary, for me to remember
    That She is my Mother, mother of our Father
    \nextverse
    Holy Mary, for me not to forget
    That our Father is the King of Power
    \nextverse
    It is Your Son, The Prince of Peace
    That is He who holds the balance of His Father
    \nextverse
    Everybody groans and is going to tremble
    But not Jesus Christ and whoever obeys Him
    \nextverse
    Words of mine, words of God
    Begging and praying for all beings
    \nextverse
    To protect us and those who want to follow
    And Your Will will be fulfilled
    \nextverse
    I am here, over there, I am there
    In every part that you look for me
    \nextverse
    I am very small but can be seen
    I am the infinite for those who perceive
    \nextverse
    I keep clarifying I didn't come to deceive
    My Father reunited and commanded purification
    \nextverse
    Hold the shaking, don't become discouraged
    Because this victory is going to happen
  \end{translation}
\endsong


\beginsong{Santa Maria \\ Conhece Santa Maria}[by={Padr. Alfredo},key={C},sks={D, C}]
  \audio[key=D]{https://www.nossairmandade.com/hymn/560/SantaMaria}
  \transpose{-2}
  \newchords{chords_conhece_santa_maria_a}\newchords{chords_conhece_santa_maria_b}
  \mnbeginchorus\memorize[chords_conhece_santa_maria_a]
    \[^\mn{A}]Quem não con|\[\mnc{D}D]hece Santa \[^\mn{F#}]Ma|\[^\mn{A}]ria \[^\mn{F#}]e faz |\[\mnc{G}G]uso \[^\mn{D}]dela todo |\[\mnc{F#}D]dia
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_conhece_santa_maria_b]
    \[^\mn{D}]Vive |\[\mnc{E}A]sempre \[\mnc{B}G]em \[^\mn{D}]ago|\[\mnc{F#}D]nia \[^\mn{D}]mas a|\[\mnc{E}A]gora che\[\mnc{B}G]gou \[^\mn{D}]como eu que|\[D]ria
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_conhece_santa_maria_a]
    Meu Se|^nhor São João Ba|tista, Jesus |^Cristo e São Jo|^sé
    \endchorus\glueverses\beginchorus\replay[chords_conhece_santa_maria_b]
    A|^gora che^gou como eu que|^ria, a|^gora che^gou como Deus |^quer
  \endchorus
  \beginchorus\replay[chords_conhece_santa_maria_a]
    Che|^gando como Deus |quer, da|^í tudo fica |^bem
    \endchorus\glueverses\beginchorus\replay[chords_conhece_santa_maria_b]
    Che|^gando ^como meu Pai |^quer, che|^gou como ^eu quero tam|^bém
  \endchorus
  \beginchorus\replay[chords_conhece_santa_maria_a]
    Na Von|^tade da Virgem Ma|ria, ela a|^gora vai vigo|^rar \altchords{\id[3]{O (C)}|C | |F |C}
    \endchorus\glueverses\beginchorus\replay[chords_conhece_santa_maria_b]
    |^Ela ^é do meu co|^mando e |^manda ^eu coman|^dar \altchords{|Dm |Am |G |C}
  \endchorus
  \beginchorus\replay[chords_conhece_santa_maria_a]
    Eu co|^mando aquele que |crê em Jesus |^Cristo e São Jo|^ão
    \endchorus\glueverses\beginchorus\replay[chords_conhece_santa_maria_b]
    Que |^esta ^é a Ver|^dade que |^temos na ^nossa uni|^ão
  \endchorus
  \beginchorus\replay[chords_conhece_santa_maria_a]
    Vou di|^zendo assim para |todos e |^quero cumprir o que |^digo
    \endchorus\glueverses\beginchorus\replay[chords_conhece_santa_maria_b]
    Quem |^não for ^me aju|^dando não |^prova que ^é meu a|^migo
  \endchorus\brk
  \beginchorus\replay[chords_conhece_santa_maria_a]
    Para |^todos nos manda esta |ordem a|^gora respeita quem |^quer
    \endchorus\glueverses\beginchorus\replay[chords_conhece_santa_maria_b]
    Mas a|^qui eu ^digo a |^todos vamos |^ser todos ^como Deus |^quer
  \endchorus\brk
  \beginchorus\replay[chords_conhece_santa_maria_a]
    Olhem |^todos bem para o |Sol, e todos |^olhem bem para |^mim
    \endchorus\glueverses\beginchorus\replay[chords_conhece_santa_maria_b]
    Se a|^inda ^tem confu|^são, mas meu |^Pai não ^pratica as|^sim
  \endchorus
  \beginchorus\replay[chords_conhece_santa_maria_a]
    Deus |^Pai e Espírito |Santo na |^nossa Mãe Se en|^cerra
    \endchorus\glueverses\beginchorus\replay[chords_conhece_santa_maria_b]
    Vamos |^todos ^afirmar |^paz, deixa |^quem quiser ^afirmar |^guerra
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose d c \relative d'' {
      \key d \major \time 4/4 \partial 4.
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        \parenthesize a8\posectionmark "A" a8( a8) | d4. d8 d4 d8 fis8 | a2 a4 fis8 fis8
        | g4. g8 d8 d8 d8 d8
      } \alternative {
        { | fis2( fis8) }
        { | fis2( fis4) }
      }
      \repeat volta 2 {
        \parenthesize d8(\sectionmark "B" \parenthesize d8) | e4. e8 b4 d8 d8 | fis2 fis4 d8 d8
        | e4 e8 e8 b8 d8 d8 d8 | d2( d4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Quem não con -- | he -- ce San -- ta Ma -- | ri -- a;
        E faz | u -- so de -- la to -- do
      } \alternative {
         { | di -- a. }
         { | di -- a. }
      }
      \repeat volta 2 {
        Vi -- ve | sem -- pre em a -- go -- | ni -- a;
        Mas a -- | go -- ra che -- gou co -- mo~eu que -- | ri -- a.
      }
    }
    theChords = \transpose d c \chordmode {
      \repeat volta 2 {
        s4. | d1 | d | g
      } \alternative {
        { | d2~ d8 }
        { | d2. }
      }
      \repeat volta 2 {
        s4 | a2 g | d1 | a2 g | d2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Whoever doesn't know Santa Maria and uses her every day
    Lives always in agony, but now it arrived as I wanted
    \nextverse
    My Lord St. John the Baptist, Jesus Christ and St. Joseph
    Now it arrived as I wanted, now it arrived as God wants
    \nextverse
    Arriving as God wants, then everything is fine
    We arrive as my Father wants, it arrived as I also want
    \nextverse
    In the Will of the Virgin Mary, now She will take action
    She is of my Command and orders me to command
    \nextverse
    I command those who believe in Jesus Christ and St. John
    Because this is the Truth that we have in our union
    \nextverse
    Thus I keep telling everyone and I want to fulfill what I say
    Whoever doesn't try to help me doesn't prove that he's my friend
    \nextverse
    This order is sent for everyone, now, whoever wants to, respect it
    But here I say to all, let us all be as God wants
    \nextverse
    Everyone, look well to the Sun, and everyone, look well to me
    If you still have confusion, but my Father doesn't practice thus
    \nextverse
    God the Father and Holy Spirit are enclosed in our Mother
    Let's all affirm peace, let whoever wants to affirm war
  \end{translation}
\endsong


\beginsong{Amor, Verdade e Justiça \\ Vou Receber Minha Mãe}[by={Padr. Alfredo},key={C},sks={C}]
  \audio{https://www.nossairmandade.com/hymn/479/VouReceberMinhaM\%C3\%A3e}
  \newchords{chords_amorverdade_a}\newchords{chords_amorverdade_b}
  \mnbeginchorus\memorize[chords_amorverdade_a]
    \[^\mn{G}]Vou \[^\mn{E}]re|\[\mnc{C}C]ceber minha \[\mnc{A}Fmaj7]{Mãe dentro} |do \[^\mn{G}]meu co\[^\mn{C}]ra\[\mnc{G}C]ção
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_amorverdade_b]
    \[^\mn{G}]Par\[^\mn{E}]{a eu} |\[\mnc{C}Am]poder \[^\mn{B}]ca\[^\mn{A}]min\[\mnc{D}G]har \[^\mn{G}]nes\[^\mn{E}]te |\[\mnc{C}F]mun\[^\mn{A}]do \[^\mn{C}]{de i}lu\[C]são
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_amorverdade_a]
    Vou co|^locar minha ^{Mãe bem} jun|tinho do meu ^Pai
    \endchorus\glueverses\beginchorus\replay[chords_amorverdade_b]
    Vida, |^paz e harmo^nia, com is|^to nos satis^faz
  \endchorus
  \beginchorus\replay[chords_amorverdade_a]
    Amor, |^verdade e jus^{tiça, fé,} fir|meza e consci^ência \altchords{\id[3]{O (C)}|C F |- C}
    \endchorus\glueverses\beginchorus\replay[chords_amorverdade_b]
    Sere|^nidade e res^peito são par|^tes da provi^dência \altchords{|C Dm |- C}
  \endchorus
  \beginchorus\replay[chords_amorverdade_a]
    Calma |^e tranqüili^dade, obedi|ência e co^ragem
    \endchorus\glueverses\beginchorus\replay[chords_amorverdade_b]
    Humi|^lhação e pru^dência são par|^tes desta i^magem
  \endchorus
  \beginchorus\replay[chords_amorverdade_a]
    Este |^é o Amor Di^{vino do} Tro|no Celesti^al
    \endchorus\glueverses\beginchorus\replay[chords_amorverdade_b]
    Que res|^plandece nas ^matas ilumi|^nando todos i^guais
  \endchorus
  \beginchorus\replay[chords_amorverdade_a]
    Ilumi|^nando todos i^guais, exami|nando um por ^um
    \endchorus\glueverses\beginchorus\replay[chords_amorverdade_b]
    Casti|^gando os menti^rosos nesta |^linha do Tu^cum
  \endchorus
  \beginchorus\replay[chords_amorverdade_a]
    São Mi|^guel e todos Ar^canjos da Vir|gem da Concei^ção
    \endchorus\glueverses\beginchorus\replay[chords_amorverdade_b]
    Que são |^as nobres de^fesas que te|^mos em nossas ^mãos
  \endchorus
  \brk
  \beginchorus\replay[chords_amorverdade_a]
    Digo a |^todos meus ir^mãos e fico e|terno agrade^cido
    \endchorus\glueverses\beginchorus\replay[chords_amorverdade_b]
    Rece|^ba com ale^gria o que lhe |^é ofere^cido
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c''' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8\posectionmark "A" e | c c c c a'4 a8 a | a g g c g4
      } \break
      \repeat volta 2 {
        g8\sectionmark "B" e | c c b a d4 g8 e | c a c c c4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Vou re -- | ce -- ber min -- ha Mãe;
        Dent -- ro | do meu co -- ra -- ção.
      }
      \repeat volta 2 {
        Pa -- ra~eu | po -- der ca -- min -- har;
        Nes -- te | mun -- do de~i -- lu -- são.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 f:maj7 | f:maj7 c4
      }
      \repeat volta 2 {
        s4 | a2:m g | f c4
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I'm going to receive my Mother within my heart
    So that I can walk in this world of illusion
    \nextverse
    I'm going to place my Mother right next to my Father
    Life, peace and harmony, with this we are satisfied
    \nextverse
    Love, Truth, Justice, Faith, firmness and conscience
    Serenity and respect are parts of providence
    \nextverse
    Calmness and tranquility, obedience and courage
    Humility and prudence are parts of this image
    \nextverse
    This is the Divine Love of the Celestial Throne
    That shines in the forest illuminating all equally
    \nextverse
    Illuminating all equally, examining one by one
    Punishing the liars in this line of the Tucum
    \nextverse
    St. Michael and all the archangels of the Virgin of Conception
    Are the noble defenses that we have in our hands
    \nextverse
    I say to all my brothers and sisters and I am eternally grateful
    Receive with happiness what is offered to you
  \end{translation}
\endsong


\beginsong{Santa Maria \\ Louvada Seja}[by={Paulo Roberto},key={Am},sks={Am, Gm}]
  \newchords{chords_louvada_a}\newchords{chords_louvada_b}
  \mnbeginchorus\memorize[chords_louvada_a]
    \[^\mn{E}]Louvada |\[\mnc{A}Am]seja nos\[^\mn{E}]sa \[^\mn{C}]Mãe Santa \[^\mn{B}]Ma|\[^\mn{A}]ria
    Que \[^\mn{E}]nos \[\mnc{G}G]dá a a\[^\mn{F}]le|\[\mnc{E}C]gria de \[^\mn{C}]com \[\mnc{D}Bm7&5]{Ela fes}\[^\mn{C}]te|\[\mnc{E}E]jar
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_louvada_b]
    \[^\mn{D}]A uni|\[Dm]{ão do} Sag\[\bm]rado Vos\[^\mn{E}]so |\[\mnc{C}Am]Filho
    Com o Di\[\bm]vino Pai \[^\mn{E}]E|\[\mnc{B}\up{1}Bm7&5 \up{2}(E7)]{terno, para} \[^\mn{C}]sem\[^\mn{B}]pre eu de\[^\mn{/}]{vo a}|\[\up{1}\mnc{E}E \up{2}\mnc{A}(Am)]mar
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_louvada_a]
    Eu peço a |^Vós na esperança de um |dia
    Eu mais ^a minha fa|^mília junto a ^{Vós me} apresen|^tar
    \endchorus\glueverses\beginchorus\replay[chords_louvada_b]
    Para lou|^var, amar ^e teste|^mnhar
    Ofere^cer meu cora|^{ção para ser} Vosso al|^tar
  \endchorus
  \beginchorus\replay[chords_louvada_a]
    Louvado |^seja Jesus Cristo Reden|tor
    E Vosso im^pério de A|^mor com to^{dos Seres} Di|^vinos
    \endchorus\glueverses\beginchorus\replay[chords_louvada_b]
    Agra|^deço todo es^se conheci|^mento
    Esta ^força e o vi|^{gor quem} recebemos em nossos |^hinos
  \endchorus
  \beginchorus\replay[chords_louvada_a]
    Santa Ma|^ria está chegando e vai fi|car
    Para ^todos reu|^nir, e sa^{ber se} respei|^tar
    \endchorus\glueverses\beginchorus\replay[chords_louvada_b]
    Andan|^{do na} est^rada com a|^mor
    Com fir^meza sem te|^{mor, e com} calma alcan|^çar
  \endchorus
  \brk
  \beginchorus\replay[chords_louvada_a]
    Agra|^deço, ontem, hoje, todo |dia
    Santa ^Paz e uni|^ão, da Luz ^{de Santa} Ma|^ria
    \endchorus\glueverses\beginchorus\replay[chords_louvada_b]
    A Vós eu |^peço na espe^rança de che|^gar
    Sempre a ^Vossa prote|^{ção, para eu} poder atraves|^sar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize e8\posectionmark "A" e8 e8 | a8 a8 a8 e8 c'8 c8 c8 b8 | a8 a8 a8 e8 g8 g8 g8 f8
        | e8 e8 e8 c8 d8 d8 d8 c8 | e2~ e8
      }
      \repeat volta 2 {
        \parenthesize d8\sectionmark "B" d8 d8 | d4 d8 d8 d8 d8 d8 e8 | c8. c16 c8 c8 c8 c8 c8 e8
      } \alternative {
        { | b8. b16 b8 b8 c8 b8 b8 b8 | e2~ e8 }
        { | b8. b16 b8 b8 c8 b8 b8 a8 | a2~ a8 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Lou -- va -- da | se -- ja nos -- sa Mãe San -- ta Ma -- | ri -- a;
        Que nos dá a a -- le -- | gri -- a
        de com E -- la fes -- te -- | jar. __
      }
      \repeat volta 2 {
        A u -- ni -- | ão do Sag -- ra -- do Vos -- so | Fil -- ho;
        Com~o Di -- vi -- no Pai E --
      } \alternative {
        { | ter -- no pa -- ra sem -- pre~eu de -- vo~a -- | mar; __ }
        { | ter -- no pa -- ra sem -- pre~eu de -- vo~a -- | mar. __ }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1:m | a2:m g | c b:m7.5- | e2~ e8
      }
      \repeat volta 2 {
        s4. | d1:m | a:m
      } \alternative {
        { | b:m7.5- | e2~ e8 }
        { | e1:7 | a2:m~ a8:m }
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Praised be our Mother, Holy Mary
    Who gives us the joy of celebrating with Her
    The union of Your Sacred Son
    With the Divine Eternal Father, I must forever love
    \nextverse
    I ask You with the hope of one day
    I and my family to come near You and present ourselves
    To praise, to love and to testify
    To offer my heart to be Your altar
    \nextverse
    Praised be Jesus Christ the Redeemer
    Your Empire of Love with all the divine beings
    I give thanks for the knowledge
    This force and this vigor, that we receive in our hymns
    \nextverse
    Holy Mary is arriving and is going to stay
    To gather everyone, and learn to respect
    Walking the path with love
    With firmness, without fear, and attain with calmness
    \nextverse
    I give thanks, yesterday, today and every day
    So much peace and union, from the Light of Holy Mary
    I ask You in hope of arriving
    Always Your protection, so I can cross beyond
  \end{translation}
\endsong


\beginsong{E ê Santa Maria}[by={Maria Alice},key={D},sks={D}]
  \audio[]{https://www.youtube.com/watch?v=kSjNgg\_-iD0\&t=1131s}
  \mnbeginchorus\memorize
    \[^\mn{A}]E |\[\mnc{A}D]ê \[^\mn{F#}]San\[^\mn{E}]ta \[^\mn{F#}]Ma|\[^\mn{E}]ri\[^\mn{D}]a, \[^\mn{A}]e |\[^\mn{A}]ê \[^\mn{F#}]San\[^\mn{E}]ta \[^\mn{F#}]Ma|\[^\mn{E}]ri\[^\mn{D}]a
    \[^\mn{A}]Nos \[^\mn{D}]con\[^\mn{F#}]for|\[\mncii{E}{A}A7]tai nes\[^\mn{C#}]ta a\[^\mn{E}]go|\[\mnc{D}D]nia
  \mnendchorus
  \notesoff
  \beginchorus
    E |^ê Mamãe Ju|rema, e |ê Mamãe Ju|rema \altchords{\id[3]{O (F)}|F | | | \e}
    A sua |^folha tem lei su|^prema \altchords{|C |F}
  \endchorus
  \beginchorus
    E |^ê Meu Rei O|gum, com |a lança na |mão
    Defende a |^Lei, sois guardi|^ão
  \endchorus
  \beginchorus
    E |^ê meu Rei O|gum, e |ê meu Rei O|gum
    Vai orde|^nando de um a |^um
  \endchorus
  \beginchorus
    E |^ê meu Rei O|gum, den|tro da vira|ção
    Guarda Ma|^mãe no cora|^ção
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \key d \major \time 4/4 \partial 4
      \repeat volta 2 {
        a4\pomark | a'2~ a8 fis8 e8 fis8 | e4 d2 a4
        | a'2~ a8 fis8 e8 fis8 | e4 d4. a8 d8 fis8
        | e4 a,4. a8 cis8 e8
        \set melismaBusyProperties = #'() \slurDashed
        | d2( d4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        E | ê __ San -- ta Ma -- | ri -- a, e | ê __ San -- ta Ma -- | ri -- a;
        Nos con -- for -- | ta -- i nes -- ta~a -- go -- | ni -- a.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d1 | d | d | d
        | a:7 | d2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    It's Santa Maria, it's Santa Maria
    Comfort me in this agony
    \nextverse
    It's Mamãe Jurema, it's Mamãe Jurema
    Your leaf is supreme law
    \nextverse
    It's my King Ogum, with a lance in the hand
    Defend the Law, you are the guardian
    \nextverse
    It's my King Ogum, it's my King Ogum
    Keeps ordering one by one
    \nextverse
    It's my King Ogum, in the breeze
    Keep Mamãe in the heart
  \end{translation}
\endsong


\beginsong{Minha Santa Maria é Livre}[by={Nonato Texeira},key={A},sks={A}]
  \audio{https://www.youtube.com/watch?v=kSjNgg_-iD0&t=836s}
  \transpose{2}
  \newchords{chords_minhasantamariaelivre_a}\newchords{chords_minhasantamariaelivre_b}
  \mnbeginchorus\memorize[chords_minhasantamariaelivre_a]
    \[^\mn{B}]Min\[^\mn{C}]ha |\[\mnc{D}G]Santa Ma\[^\mn{B}]ri\[^\mn{G}]{a é} |\[\mnc{G}Em7]livre
    \[^\mn{F#}]No \[^\mn{G}]lu|\[\mnc{A}Am7]gar on\[^\mn{C}]de E\[^\mn{E}]{la es}|\[\mnc{D}D]tá
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_minhasantamariaelivre_b]
    \[^\mn{F#}]Mas \[^\mn{G}]a |\[\mnc{A}Am]gente \[^\mn{C}]é \[\bm]que l\[^\mn{E}]{he a}|\[\mnc{D}G]cusa
    Quan\[^\mn{B}]{do a} \[\mnc{G}Em]gen\[^\mn{E}]te |\[\mnc{C}Am7]usa sem \[^\mn{A}]sa\[\mnc{F#}D7]ber \[^\mn{D}]u|\[\mnc{G}G]sar
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_minhasantamariaelivre_a]
    Santa Ma|^ria é nossa |^Mãe \altchords{\id[3]{O (A)}|A | \e}
    É nossas |^filhas e nossas mu|^lheres \altchords{|Bm |E}
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_minhasantamariaelivre_b]
    Mas é pre|^ciso ^muito A|^mor \altchords{|Bm |E}
    E ^todas |^elas se ^consag|^rar \altchords{|D E |A}
  \endchorus
  \beginchorus\replay[chords_minhasantamariaelivre_a]
    Aqui |^dentro desta irman|^dade
    Alguns ir|^mãos precisam enten|^der
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_minhasantamariaelivre_b]
    Que para u|^sar a San^ta Ma|^ria
    É com ^leal|^dade pra lhe ^defen|^der
  \endchorus
  \beginchorus\replay[chords_minhasantamariaelivre_a]
    Mas é com |^fé e paci|^ência
    Que para |^todos vai se liber|^tar
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_minhasantamariaelivre_b]
    Quem estiver |^firme ^vai sor|^rir
    Quem não ^esti|^ver pode a^té cho|^rar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose g a \relative g' {
      \key g \major \time 4/4 \partial 4
      \repeat volta 2 {
        b8\posectionmark "A" c | d4 d8 d b4 g | g'2 g4 fis8 g
        | a4 a8 c, c4 e4 | d2.
      }
      \partial 4 \repeat volta 2 {
        fis8\sectionmark "B" g | a4 a8 c,8 c4 e | d8 d d b g4 e
        | c'8 c c a fis4 d | g2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Min -- ha | San -- ta Ma -- ri -- a~é | liv -- re;
        No lu -- | gar on -- de E -- la~es -- | tá.
      }
      \repeat volta 2 {
        Mas a | gen -- te é que lhe~a -- | cu -- sa;
        Quan -- do~a gen -- te | u -- sa sem sa -- ber u -- | sar.
      }
    }
    theChords = \transpose g a \chordmode {
      \repeat volta 2 {
        s4 | g1 | e:m7
        | a:m7 | d2.
      }
      \repeat volta 2 {
        s4 | a1:m | g2 e:m
        | a:m d:7 | g2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    My Santa Maria is free
    In the place where She is
    But one may accuse
    When one uses without knowing how
    \nextverse
    Santa Maria is our Mother
    Is our daughters and our wives
    But it takes a lot of Love
    And everyone to consecrate
    \nextverse
    Here within this brotherhood
    Some brothers need to learn
    How to use Santa Maria
    And to defend Her with loyalty
    \nextverse
    But it is with faith and patience
    That all will be liberated
    Who will be firm will smile
    Who won‘t can still be crying
  \end{translation}
\endsong


\beginsong{Santa Maria foi quem me Chamou}[by={Ronaldo Rocha},tags={mazurca},key={C},sks={D, C}]
  \audio{https://www.youtube.com/watch?v=kSjNgg_-iD0&t=1269s}
  \meter{6}{4}
  \mnbeginchorus\memorize
    \[^\mn{G}]Santa Ma|\[\mnc{C}C]ria foi \[^\mn{G}]quem \[^\mn{C}]me \[^\mn{E}]cha\[^\bmc\mn{C}]mou
    \[^\mn{G}]{E convi}|\[\mnc{C}Am]dou-me a \[^\mn{G}]o\[^\mn{C}]be\[^\mn{E}]de\[\bmc\mnc{D}G]cer
    Para eu |\[^\mn{B}]ver \[^\mn{G}]a \[^\mn{B}]tu\[^\mn{D}]a \[^\bmc\mn{G}]Luz
    E con\[^\mn{A}]he|\[\mnc{G}G7]cer o \[^\mn{F}]Vos\[^\mn{E}]so \[^\mn{D}]po\[\bmc\mnc{C}C]der
  \mnendchorus
  \notesoff
  \beginchorus
    Foi a|^{i que} eu me fir\[\bm]mei \altchords{\id[3]{O (C)}|C (G)}
    Foi a|^{i que} eu enxer^guei \altchords{|C Dm}
    Meu São Jo|ão, meu São Jo\[\bm]ão \altchords{|C G}
    Na Vossa |^Glória e no Vosso po^der \altchords{|G C}
  \endchorus
  \beginchorus
    Ele me |^disse tu segue em \[\bm]frente
    Ele me |^disse presta aten^ção
    Que esta |Luz sempre reina\[\bm]rá
    Na Santa |^Casa de São Jo^ão
  \endchorus
  \beginchorus
    Cada ca|^beça tem sua jus\[\bm]tiça
    Cada jus|^tiça traz sua ra^zão
    Cada |flor traz o seu per\[\bm]fume
    E cada A|^mor tem o seu cora^ção
  \endchorus
  \beginchorus
    Eu agra|^deço a meu Senhor Je\[\bm]sus
    Eu agra|^deço à minha ^Mãe
    Eu agra|deço a meu São Jo\[\bm]ão
    E eu agra|^deço aos meus ir^mãos \tonextsongmark
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \key c \major \time 6/4 \partial 4.
      \repeat volta 2 {
        g8\pomark g g | c c c g c e c4. g8 g g
        | c c c g c e d2
        d8 d | b4 g b8 d g4. g8 g a
        | g4 g8 f e d c4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        San -- ta Ma -- | ri -- a foi quem me cha -- mou;
        E con -- vi -- | dou -- me a o -- be -- de -- cer;
        Pa -- ra~eu | ver a tu -- a Luz;
        E con -- he -- | cer o Vos -- so po -- der;
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1.
        | a2.:m g
        | g1.
        | g2.:7 c4.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Santa Maria was who called me; And invited me to obey
    So I would see your Light; And know Your power
    \nextverse
    It was there that I firmed myself; It was there that I witnessed
    My St. John, my St. John; In Your Glory and Your power
    \nextverse
    He told me follow in front; He told me to pay attention
    For this Light always will reign; In the Holy House of St. John
    \nextverse
    Each head has its justice; Each justice brings its reason
    Each flower brings its perfume; And each Love has its heart
    \nextverse
    I thank my Lord Jesus; I am thankful to my Mother
    I thank my St. John; I thank my brothers and sisters
  \end{translation}
\endsong


\beginsong{Uma Bela História}[by={Lúcio Mortimer},tags={mazurca},key={C},sks={D, C}]
  \audio{https://www.nossairmandade.com/hymn/1438/UmaBelaHist\%C3\%B3ria}
  \meter{6}{4}
  \mnbeginchorus\memorize
    \[^\mn{G}]Eu \[^\mn{E}]vou \[^\mn{D}]con|\[\mnc{C}C]tar u\[^\mn{G}]ma \[^\mn{E}]bel\[^\mn{D}]{a his}\[^\bm\mn{C}]tória
    Da plan|\[Am]tinha que mais \[^\mn{B}]tem \[^\mn{C}]a\[\bmc\mnc{D}G]mor
    \[^\mn{F}]E\[^\mn{E}]la |\[^\mn{D}]era \[^\mn{G}]bem \[^\mn{F}]pe\[^\mn{E}]que\[^\bm\mn{D}]nina
    \[^\mn{G}]Pad\[^\mn{B}]rin\[^\mn{D}]ho |\[\mnc{G}G7]viu e \[^\mn{F}]a\[^\mn{E}]ben\[^\mn{D}]ço\[\bmc\mnc{C}C]ou
  \mnendchorus
  \notesoff
  \beginchorus
    Ele |^disse preste aten\[\bm]ção \altchords{\id[3]{O (C)}|C}
    Aqui |^tem uma força di^vina \altchords{|C Dm}
    Quem sou|ber dar consagra\[\bm]ção \altchords{| \e}
    Tem uma |^Mãe que nos en^sina \altchords{|G C}
  \endchorus
  \beginchorus
    Ela |^cura e ali\[\bm]menta
    O a|^mor em nosso cora^ção
    O seu per|fume nos aca\[\bm]lenta
    E nos con|^forta em nossa mis^são
  \endchorus
  \beginchorus
    Um anjo |^veio e foi di\[\bm]zendo
    No |^sonho de nosso Pad^rinho
    Com esta |planta também se \[\bm]cura
    E tem mais |^Luz no seu ca^minho
  \endchorus
  \beginchorus
    Com o galho |^verde em sua \[\bm]mão
    O anjo |^veio e fez a profe^cia
    Agora |vamos ter uni\[\bm]ão
    E mais res|^peito à Santa Ma^ria
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \key c \major \time 6/4 \partial 4.
      \repeat volta 2 {
        g8\pomark e' d | c4 c8 g e' d c4 c c8 c
        | c c c c b c d2 f8 e
        | d4 d8 g, f' e d4 d8 g, b d
        | g8. g16 g8 f e d c4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu vou con -- | tar u -- ma be -- la~his -- tó -- ria;
        Da plan -- | tin -- ha que mais tem a -- mor;
        E -- la | e -- ra bem pe -- que -- ni -- na;
        Pad -- rin -- ho | vi -- u e a -- ben -- ço -- ou;
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1.
        | a2.:m g
        | g1.
        | g2.:7 c4.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}\scriptsize % smaller to fit whole song on a spread
    I'll tell a nice story, the plant that has more love
    She was a little one that Padrinho saw and blessed
    \nextverse
    He said pay attention, here there is a divine force
    Whoever knows how to consecrate has a Mother who teaches us
    \nextverse
    It heals and nurtures the love in our heart
    Her perfume soothes us and comforts us in our mission
    \nextverse
    An angel came and said in the dream of our Padrinho
    With this plant he can also heal himself and has more Light on the path
    \nextverse
    With the green branch in his hand the angel came and made the prophecy
    Now we are going to have union and more respect for the Santa Maria
  \end{translation}
\endsong


\beginsong{Salve Rainha}[by={Alex Polari},tags={valsa},key={C},sks={D, C}]
  \audio[key={C}]{https://www.youtube.com/watch?v=kSjNgg_-iD0&t=1493s}
  \meter{3}{4}
  \mnbeginverse
    |\[\mnc{C}C]Santa \[^\mn{E}]Ma|\[^\mn{G}]ria que |\[\mnc{A}Am]vei\[^\mn{G}]o do |\[\mnc{E}C]Céu
    Pra m\[^\mn{C}]{e a}|\[\mnc{A}Am]gra\[^\mn{G}]ci|\[\mnc{D}G]ar, pra m\[^\mn{B}]{e a}|\[\mnc{A}F]gra\[^\mn{G}]ci|\[\mnc{C}C]ar
    \[^\mn{G}]Pra me a|\[\mnc{C}Am]gra\[^\mn{D}]ci|\[\mnc{C}C]ar, pra me a|\[\mnc{E}Am]gra\[^\mn{A}]ci|\[\mnc{G}G]ar
  \mnendverse
  \notesoff
  \beginverse
    |^Santa Ma|ria que mi|^nha Mãe man|^dou \altchords{\id[3]{alt. (C)}|C | |F |C}
    Veio |^para u|^nir, veio |^para u|^nir \altchords{|Am |Dm |F |C}
    Veio |^para u|^nir, veio |^para u|^nir \altchords{|C | |Am |G}
  \endverse
  \beginverse
    |^O seu per|fume re|^sume a |^terra
    Veio |^pra mos|^trar, veio |^pra mos|^trar
    Veio |^pra mos|^trar, veio |^pra mos|^trar
  \endverse
  \beginverse
    |^Este mis|tério é mi|^nha Mãe que |^dá
    Ela |^vai rei|^nar, ela |^vai rei|^nar
    Ela |^vai rei|^nar, ela |^vai rei|^nar
  \endverse
  \beginverse
    |^Tanto po|der pre|^sente es|^tá
    Vamos |^se ca|^lar, vamos |^se ca|^lar
    Vamos |^se ca|^lar, vamos |^se ca|^lar
  \endverse
  \beginverse
    |^Neste si|lêncio é |^que Deus es|^tá
    Vamos |^escu|^tar, vamos |^escu|^tar
    Vamos |^escu|^tar, vamos |^escu|^tar
  \endverse
  \beginverse
    |^Se escutarem |hino tra|^tem de gra|^var
    Sou |^eu quem |^mando, para |^te brin|^dar
    Sou |^eu quem |^mando, para |^te brin|^dar
  \endverse
  \beginverse
    |^Salve Ra|inha do|^na deste en|^sino
    Eu a|^penas |^zelo, vós que |^deter|^mina
    Eu a|^penas |^zelo, vós que |^deter|^mina
  \endverse
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' { \key c \major \time 3/4
      | c4\pomark c e | g g g | a g g | e2 e8 c8
      | a2 g4 | d'2 d8 b8 | a2 g4 | c2 g8 g
      | c2 d4 | c2 c8 c8 | e2 a4 | g2. \bar "|."
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      | San -- ta Ma -- | ri -- a que | vei -- o do | Céu;
      Pra me~a -- | gra -- ci -- | ar, pra me~a -- | gra -- ci -- | ar;
      Pra me~a -- | gra -- ci -- | ar, pra me~a -- | gra -- ci -- | ar;
    }
    theChords = \chordmode {
      | c2. | c | a:m | c
      | a:m | g | f | c
      | a:m | c | a:m | g
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Holy Mary who comes from Heaven
    To grace me, to grace me
    To grace me, to grace me
    \nextverse
    Holy Mary whom my Mother sent
    Came to me, came to me
    Came to me, came to me
    \nextverse
    Her perfume embraces the earth
    Came to show me, came to show me
    Came to show me, came to show me
    \nextverse
    My Mother who gives this mystery
    She will reign, she will reign
    She will reign, she will reign
    \nextverse
    So much Power is present
    Let us be quiet, let us be quiet
    Let us be quiet, let us be quiet
    \nextverse
    In this silence God abides
    Let us listen, let us listen
    Let us listen, let us listen
  \end{translation}
\endsong


\beginsong{Santa Maria \\ Declaração}[by={Sonia Maria Palhares},tags={2x},key={D},sks={D}]
  \audio{https://www.youtube.com/watch?v=kSjNgg_-iD0&t=1630s}
  \musicnote{Tocar 2 vezes}
  \mnbeginchorus\memorize
    \[^\mn{A}]Eu |\[\mnc{D}D]venho \[^\mn{A}]tra\[\bm\mn{D}]zer
    U\[^\mn{A}]ma |\[^\mn{D}]decla\[^\mn{E}]ra\[\mnc{C#}A]ção
    \[^\mn{E}]Que vem |da Virgem Ma\[A7]ria
    E do meu |\[\mn{F}]Sen\[^\mn{E}]hor São \[^\mn{F#}]Jo\[\mnc{D}D]ão
  \mnendchorus
  \notesoff
  \beginchorus
    Que é |^pra se estu^dar \altchords{\id[2]{MK (D)} |D}
    Que é |pra se ca^lar \altchords{|Bm A}
    Junto |com a Santa Ma^ria \altchords{|- A7}
    Que é pra |^Ela escu^tar \altchords{|- D}
  \endchorus
  \begin{translation}
    I come to bring
    A declaration
    That comes from the Virgin Mary
    And of my Lord Saint John
    \nextverse
    That is from studying oneself
    That is from quieting oneself
    Together with the Santa Maria
    In order to listen to Her
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \key d \major \time 4/4 \partial 8
      \repeat volta 2 {
        a8\pomark | d4 d8 a d4 \parenthesize d8 a | d4 d8 e cis4 e8 e
        | e e e e e e e e | f e e fis d4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu | ven -- ho tra -- zer;
        \parenthesize U -- ma | de -- cla -- ra -- ção;
        Que vem | da Vir -- gem Ma -- ri -- a;~E
        do meu | Sen -- hor São Jo -- ão.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Que~é | pra se~es -- tu -- dar;
        \skip 1 Que~é | pra se ca -- lar;
        Jun -- to | com~a San -- ta Ma -- ri -- a;
        Que~é pra | E -- la es -- cu -- tar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | d1
        | d2 a2
        | s2 a2:7
        | a2:7 d4.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Luz de Jesus \\ O Virgem Mãe}[by={Isabela Coutinho},key={Dm},sks={Dm, Cm, Bm}]
  \audio{https://www.youtube.com/watch?v=kSjNgg_-iD0&t=1709s}
  \musicnote{2º verso tem acordes e melodia ligeiramente diferentes.}
  \mnbeginchorus\memorize
    \[^\mn{A}]Oh! \[^\mn{D}]Vir\[^\mn{E}]gem |\[\mnc{F}Dm]Mãe, \[^\mn{E}]eu \[^\mn{D}]pe\[^\mn{E}]{ço à} \[\bmc\mn{F}]Vós \[^\mn{A}]um \[^\mn{B&}]d|i\[^\mn{A}]a \altchords{\id[1]{(Am)}|Am | \e}
    \[^\mn{G}]A \[^\mn{F}]San\[\mnc{E}Em7&5]ta \[^\mn{A}]Ma\[^\mn{B&}]r|i\[^\mn{A}]a \[^\mn{G}]eu \[^\mn{F}]sa\[\mnc{E}A]ber \[^\mn{B&}]a\[^\mn{A}]m|ar\[\bm] \altchords{Bm7\flt{}5 | - E | \e}
    E \[^\mn{B&}]fir\[^\mn{A}]mar |\[\mnc{G}Gm]sem\[^\mn{F}]pre \[^\mn{E}]o \[^\mn{D}]meu \[\mnc{C#}A]pen\[^\mn{A}]sa\[^\mn{B&}]m|en\[^\mn{A}]to \altchords{|Dm E | \e}
    \[^\mn{D}]Nest\[^\mn{E}]{e en}\[\mnc{F}Dm]ten\[^\mn{A}]di\[^\mn{B&}]m|en\[^\mn{A}]to \[^\mn{G}]par\[^\mn{F}]{a eu} \[\mnc{E}A7]pod\[^\mn{D}]er \[^\mn{C#}]me \[^\mn{E}]sal|\[\mnc{D}Dm]var \[\bm] \altchords{Am | - E7 |Am}
  \mnendchorus
  \beginchorus
    Ó! Meu que|\[Dm]rido e San\[\bm]to Padr|inho \altchords{|Am | \e}
    No di\[A]{a de} \[\mnlow{A}]sua \[\mnlow{A}]pas|sagem consa\[Em7&5]grou a \[\mnlow{B&}]u\[\mnlow{B&}]ni|\[A]ão\[\bm] \altchords{E | - Bm7\flt{}5 |E \e}
    E foi lim|\[Gm]{par bem} o \[A]seu terre|iro \altchords{|Dm E | \e}
    Nos dei\[Dm]xando o \[\mnlow{A}]seu \[\mnlow{A}]a|\[Gm]mor dentro de \[A7]cada cora|\[Dm]ção\[\bm]
     \altchords{Am |Dm E7 |Am}
  \endchorus
  \notesoff
  \beginchorus
    Esta mis|^são agora é ^do seu f|ilho \altchords{|Am | \e}
    Que tem ^nosso am|or e nossa ^gratid|ão^ \altchords{Bm7\flt{}5 | - E | \e}
    E nele es|^{tá a luz} de ^Jesus Cr|isto \altchords{|Dm E | \e}
    Que se ^traduz|indo o nome ^{é Ju}rami|^dam^ \altchords{Am | - E7 |Am}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        a8\pomark d e | f e d e f4 a8 bes~ | bes a g f e8( e8) a8 << \parenthesize a bes( >>
        | bes) a g f e8( e8) bes'8 << \parenthesize bes a( >> | a2)~ a8 a bes a
        | g( f) e d cis4 a'8 bes~ | bes a d, e f8( f8) a8 << \parenthesize a bes( >>
        bes) a g f e d cis e | d2~ d8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Oh! Vir -- gem | Mãe
        Eu pe -- ço~à Vós um di -- _ a;
        A San -- ta __ _ Ma -- ri -- _ a eu sa -- ber __ _ a -- mar; __ _ _
        E fir -- mar | sem -- pre o meu pen -- sa -- men -- _ to;
        Nes -- te~en -- ten -- _ di -- men -- _ to pa -- ra~eu  -- po -- der me sal -- | var. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Ó! Meu que -- | ri -- do e San -- to Pa -- dri -- _ nho;
        No di -- a de sua \parenthesize pas -- | sa -- gem con -- sa -- grou a u -- \parenthesize ni -- ão; _
        E foi lim -- | par __ _ bem o seu ter -- rei -- _ ro;
        Nos dei -- xan -- do~o seu \parenthesize a -- | mor den -- tro de ca -- da co -- ra -- ção. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Es -- ta mis -- | são ago -- ra é do seu fi -- _ lho;
        Que tem nos -- _ so~a -- mor __ _ e nos -- sa gra -- _ ti -- dão; __ _ _
        E ne -- le~es -- | tá a luz de Je -- sus Cris -- _ to;
        Que se tra -- _ du -- zin -- _ do~o no -- me é Ju -- ra -- mi -- | dam. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | d2:m d:m | d:m e:m7.5-
        | e:m7.5- a | a a
        | g:m a | a d:m
        | d:m a:7 | d:m~ d8:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    O Virgin Mother, I ask of you that some day
    I may know how to love Santa Maria
    And always secure my thought
    In this comprehension so that I may save myself.
    \nextverse
    Oh! My dear and holy Padrinho
    On the day of your passage, you consecrated the Union
    And you cleaned your terrace well
    Leaving with us your love, inside of each heart.
    \nextverse
    This mission now is of your son
    Who has our love and our gratitude
    And in him is the love of Jesus Christ
    Whose name translates as Juramidam.
  \end{translation}
\endsong


\beginsong{São Paulo}[by={Glauco Villas Boas},key={Am},sks={Am}]
  \audio{https://www.nossairmandade.com/hymn/1626/S\%C3\%A3oPaulo}
  \newchords{chords_saopaulo_a}
  \newchords{chords_saopaulo_b}
  \mnbeginchorus\memorize[chords_saopaulo_a]
    \[^\mn{C}]Vi\[^\mn{B}]va |\[\mnc{A}Am]Ca\[^\mn{G}]sa \[^\mn{F}]de \[^\mn{E}]Ma|\[\mnc{D}Dm]ri\[^\mn{E}]a, \[^\mn{F}]vi\[^\mn{E}]va |\[\mnc{D}E7]E\[^\mn{E}]la \[^\mn{F}]co\[^\mn{E}]mo es|\[\mnc{A}Am]tá
  \mnendchorus
  \mnbeginchorus\memorize[chords_saopaulo_b]
    \ind \[^\mn{A}]Va\[^\mn{B}]mos |\[\mnc{C}Am]todos \[\mnc{B}E7]fi\[^\mn{A}]car |\[\mnc{C}Am]fir\[^\mn{B}]mes
    \ind \[^\mn{A}]Ca\[^\mn{B}]da |\[^\mn{C}]um em \[\mnc{B}E7]seu \[^\mn{A}]lu|\[\mnc{C}Am]gar
    \ind \[^\mn{B}]Que \[^\mn{A}]vai \[^\mn{B}]che|\[\mnc{C}C]gar \[^\mn{E}]mais apa|\[\mnc{D}Bm7&5]rel\[^\mn{C}]ho
    \ind \[^\mn{B}]Para \[^\mn{C}]mais |\[\mnc{E}E7]for\[^\mn{D}]ça a\[^\mn{C}]pa\[^\mn{B}]rel|\[\mnc{A}Am]har
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_saopaulo_a]
    Esta |^casa é de Ma|^ria e de Jesus |^Cristo Reden|^tor
  \endchorus
  \beginchorus\replay[chords_saopaulo_b]
    \ind Eu vou |^receber ^esta |^força
    \ind A for|ça do ^meu Se|^nhor
    \ind Para fun|^dar com meu São |^Paulo
    \ind Uma |^Casa de A|^mor
  \endchorus
  \beginchorus\replay[chords_saopaulo_a]
    Viva |^Casa de Ma|^ria e viva |^Mamãe Ieman|^já
  \endchorus
  \beginchorus\replay[chords_saopaulo_b]
    \ind Vamos |^todos ^balan|^çando
    \ind Como |nas on^das do |^mar
    \ind É meu |^Pai que está apu|^rando
    \ind O que |^tem para apu|^rar
  \endchorus
  \brk
  \beginchorus\replay[chords_saopaulo_a]
    Ó! Mi|^nha Santa Ma|^ria vem a|^qui nos perfu|^mar
  \endchorus
  \beginchorus\replay[chords_saopaulo_b]
    \ind Vem a|^qui ti^rar o |^medo
    \ind Vem a|qui nos ^clare|^ar
    \ind Que o co|^mando é de São |^Pedro
    \ind Ninguém |^queira duvi|^dar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c''' {
      \key a \minor \time 4/4 \partial 2
      \repeat volta 2 {
        c4\posectionmark "A" b | a g f e | d4. e8 f4 e | d e f e | a,2
      } \break
      \repeat volta 2 {
        a4\sectionmark "B" b | c c b a | c4. b8 a4 b | c c b a | c4. b8 a4 b
        c e e e | d4. c8 b4 c | e d c b | a2
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Vi -- va Ca -- sa de Ma -- ri -- a,
        vi -- va e -- la co -- mo~es -- tá;
      }
      \repeat volta 2 {
        Va -- mos to -- dos fi -- car fir -- mes;
        Ca -- da um em seu lu -- gar;
        Que vai che -- gar mais a -- pa -- rel -- ho;
        Para mais for -- ça~a pa -- rel -- har.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | a1:m | d:m | e:7 | a2:m
      }
      \repeat volta 2 {
        s2 | a2:m e:7 | a1:m | a2:m e:7 | a1:m
        | c | b:m7.5- | e:7 | a2:m
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Viva House of Mary, Viva as it is
    \nextverse
    Let‘s all become firm
    Each one in his place
    For the mediumship will develop
    With more force to work
    \nextverse
    This house is of Mary and of Jesus Christ Redeemer
    \nextverse
    I go to receive this force
    The force of my Lord
    To establish with my St. Paul
    A House of Love
    \nextverse
    Viva House of Mary and Viva Mother Yemanja
    \nextverse
    We will all be shaking
    As in the waves of the sea
    It is my Father who is selecting
    What He has to select
    \nextverse
    Oh! My Saint Mary comes here perfuming us
    \nextverse
    Comes here to take off the fear
    Comes here clear us
    That the command is of St. Peter
    Nobody wants to doubt
  \end{translation}
\endsong


\beginsong{São Damião}[by={Madr. Cristina Raulino},key={Dm},sks={Dm, Am}]
  \newchords{chords_saodamiao_a}\newchords{chords_saodamiao_b}
  \mnbeginchorus\memorize[chords_saodamiao_a]
    \[\mn{D}]Santa \[\mn{F}]Ma|\[\mnc{A}Dm]ria \[\mnc{G}A7]me \[\mn{A}]mos|\[\mnc{D}Dm]trou \altchords{\id[3]{O (Am)}|Am | \e}
    \[\mn{A}]O ca|\[\mnc{G}C]min\[\mn{F}]ho \[\mnc{E}A7]do \[\mn{A}]Sen|\[\mnc{D}Dm]hor \altchords{|Dm |Am}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_saodamiao_a]
    \[\mn{D}]Dai-\[\mn{E}]me, |\[\mnc{F}Dm]dai-\[\mn{G}]me, \[\mn{A}]dai-\[\mn{B&}]me |\[\mnc{G}Gm]Luz \altchords{|Am |Dm}
    Dai-\[\mn{F}]me, |\[\mnc{E}A7]dai-\[\mn{F}]me o \[\mn{G}]Seu \[\mn{A}]a|\[\mnc{D}Dm]mor \altchords{|E7 |Am}
  \mnendchorus
  \mnbeginchorus\replay[chords_saodamiao_a]
    \[\mn{A}]O |\[Dm]San\[\mn{D}]to \[\mn{E}]que \[\mn{F}]me |\[\mnc{G}Gm]guia  \altchords{|Am |Dm}
    Meu \[\mn{F}]Sen|\[\mnc{E}A7]hor \[\mn{F}]São \[\mn{G}]Da\[\mn{A}]mi|\[\mnc{D}Dm]ão \altchords{|E7 |Am}
  \mnendchorus\glueverses\mnbeginchorus\replay[chords_saodamiao_b]
    \[\mn{A}]Vós |\[\mnc{D}Dm]sois \[\mn{E}]a \[\mn{F}]min\[\mn{G}]ha |\[\mnc{E}A]força \altchords{|Am |E7}
    \[\mn{D}]Vós |\[\mnc{C#}A7]sois \[\mn{D}]o \[\mn{E}]meu \[\mn{F}]per|\[\mnc{D}Dm]dão \altchords{|E7 |Am}
  \mnendchorus
  \mnbeginchorus\replay[chords_saodamiao_a]
    \[\mn{A}]A |\[Dm]Vós \[\mn{F}]me \[\mn{E}]o\[\mn{D}]fe|\[\mnc{C#}A]reço \altchords{|Am |E7}
    \[\mn{D}]Em |\[\mnc{E}A7]San\[\mn{D}]ta \[\mn{E}]co\[\mn{F}]mun|\[\mnc{D}Dm]hão \altchords{|E7 |Am}
  \mnendchorus\glueverses\mnbeginchorus\replay[chords_saodamiao_b]
    \[\mn{D}]Dai-\[\mn{E}]me |\[\mnc{F}Dm]for\[\mn{G}]ça, \[\mn{A}]dai-\[\mn{B&}]me a|\[\mnc{G}Gm]mor \altchords{|Am |Dm}
    Dai-\[\mn{F}]me, |\[\mnc{E}A7]dai-\[\mn{F}]me \[\mn{G}]u\[\mn{A}]ni|\[\mnc{D}Dm]ão \altchords{|E7 |Am}
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \key d \minor \time 4/4 \partial 2
      \repeat volta 2 {
        d4\sectionmark "1.A" d8 f | a4 a g a | d,2 a'4 a | g f e a | d,2
      } \break
      \repeat volta 2 {
        d4\sectionmark "1.B" e | f g a bes | g2 g4 f | e f g a | d,2
      } \break
      \repeat volta 2 {
        r4\sectionmark "2.A" a' | a d, e f | g4. g8 g4 f | e f g a | d,2
      } \break
      \repeat volta 2 {
        r4\sectionmark "2.B" a' | d, e f g | e2 e4 d | cis d e f | d2
      } \break
      \repeat volta 2 {
        r4\posectionmark "3.A" a'4 | a f e d | cis2 cis4 d | e d e f | d2
      } \break
      \repeat volta 2 {
        d4\sectionmark "3.B" e | f g a bes | g2 g4 f | e f g a | d,2
      }
    }
    % Note: repeats for lyrics are not written here, as Lilypond creates extra
    % bar lines if a repeat starts with a rest and there are repeated lyrics.
    % Omitting the repeats has no consequences, except if this data is later
    % used in some other way, where \unfoldRepeats command is used (does not
    % matter with MIDI output, only on layout).
    theLyricsOne = \lyricmode {
      \set stanza = "1."
        San -- ta Ma -- | ri -- a me mos -- | trou;
        O ca -- | min -- ho do Sen -- | hor;
        Dai- -- me,  | dai- -- me, dai- -- me | Luz;
        Dai- -- me,  | dai- -- me~o Seu a  -- | mor.
      \set stanza = "2."
        O | San -- to que me | gui -- a;
        Meu Sen -- | hor São Da -- mi -- | ão;
        Vós | sois a min -- ha | for -- ça;
        Vós | sois o meu per -- | dão.
      \set stanza = "3."
        A | Vós me o -- fe | re -- ço;
        Em | San -- ta co -- mun -- | hão;
        Dai- -- me  | for -- ça, dai- -- me~a -- | mor;
        Dai- -- me,  | dai- -- me u -- ni -- | ão.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | d:m a:7 | d1:m | c2 a:7 | d:m
      }
      \repeat volta 2 {
        s2 | d1:m | g:m | a:7 | d2:m 
      }
      \repeat volta 2 {
        s2 | d1:m | g:m | a:7 | d2:m
      }
      \repeat volta 2 {
        s2 | d1:m | a | a:7 | d2:m
      }
      \repeat volta 2 {
        s2 | d1:m | a | a:7 | d2:m
      }
      \repeat volta 2 {
        s2 | d1:m | g:m | a:7 | d2:m
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Santa Maria showed Me
    The way of the Lord
    Give me, give me, give me Light
    Give me, give me, Your love
    \nextverse
    The saint that guides me
    My Lord Saint Damian
    You are my strength
    You are my forgiveness
    \nextverse
    To You I offer myself
    In holy communion
    Give me strength
    Give me, give me union
  \end{translation}
\endsong


\beginsong{Estrelas Divinas}[by={Madr. Tetê}, key={C}, sks={C}]
  \audio{https://www.nossairmandade.com/hymn/1921/EstrelasDivinas}
  \mnbeginchorus
    \[\mn{C}]Louva\[\mn{E}]do |\[\mnc{G}C]seja \[\mn{E}]meu \[\mn{C}]Di\[\mnc{A}Am]vi\[\mn{G}]no |\[\mnc{E}C]Pai
    \[\mn{C}]Meu Di\[\mnc{A}Am]vi\[\mn{G}]no |\[\mnc{E}C]Pai, \[\mn{C}]lou\[\mnc{D}G7]va\[\mn{E}]do |\[\mnc{C}C]seja
  \mnendchorus\glueverses\mnbeginchorus
    \[\mn{C}]San\[\mn{B}]ta \[\mn{C}]Ma|\[\mnc{D}G]ria \[\mn{C}]a\[\mnc{A}Am]qui \[\mn{E}]na |\[\mnc{C}C]terra
    Nos en\[\mn{B}]tre\[\mnc{A}Am]gan\[\mn{E}]do a |\[\mnc{D}G7]paz para \[\mn{C}]ven\[\mn{A}]cer \[\mn{E}]a |\[\mnc{C}C]guerra
  \mnendchorus
  \mnbeginchorus
    \[\mn{C}]Va\[\mn{E}]mos, |\[\mnc{G}C]va\[\mn{E}]mos \[\mnc{C}Am]meus \[\mn{A}]ir|\[\mnc{G}C]mãos
    \[\mn{E}]Va\[\mn{G}]mos |\[\mnc{E}Am]todos, va\[\mn{D}]mos \[\mnc{C}F]ca\[\mn{F}]min|\[\mnc{E}C]har
  \mnendchorus\glueverses\mnbeginchorus
    \[\mn{B}]Que \[\mn{C}]a |\[\mnc{D}G]or\[\mn{C}]dem \[\mnc{A}Am]vem \[\mn{E}]se|\[\mnc{C}C]vera
    É \[\mn{B}]da \[\mnc{A}Am]Vir\[\mn{E}]gem |\[\mnc{D}G7]Mãe e \[\mn{C}]de \[\mn{A}]São \[\mn{E}]Jo|\[\mnc{C}C]ão
  \mnendchorus
  \mnbeginchorus
    \[\mn{C}]Meu São \[\mn{E}]Jo|\[\mnc{G}C]ão é \[\mn{E}]quem \[\mn{C}]es\[\mnc{A}Am]tá \[\mn{G}]man|\[\mnc{E}C]dan\[\mn{C}]do
    É quem es\[\mnc{A}Am]tá \[\mn{G}]vi|\[\mnc{E}C]bran\[\mn{C}]do e é quem \[\mnc{D}G7]vai \[\mn{E}]bril|\[\mnc{C}C]har
  \mnendchorus\glueverses\mnbeginchorus
    \[\mn{B}]Com \[\mn{C}]as |\[\mnc{D}G]Es\[\mn{C}]tre\[\mnc{A}Am]las \[\mn{E}]Di|\[\mnc{C}C]vinas
    \[\mn{B}]De \[\mnc{A}Am]Je\[\mn{E}]sus |\[\mnc{D}G7]Cristo e de \[\mn{C}]San\[\mn{A}]ta \[\mn{E}]Ma|\[\mnc{C}C]ria
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    \layout { #(layout-set-staff-size 14) } % to fit all on one spread
    theMelody = \relative c'' {
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        c8\sectionmark "1.A" c e | g g e c a'4 g | e4 c8 c a'4 g | e4. c8 d4 e | c2 c8
      }
      \repeat volta 2 {
        c8\sectionmark "1.B" b c | d4 d8 c a4 e'4 | c8 c c b a4 e' | d8 d d c a4 e'4 | c2 c8
      } \break
      \repeat volta 2 {
        r8\sectionmark "2.A" c e | g4. e8 c4 a'4 | g2 e4 g | e8 e e d c4 f | e2~ e8
      }
      \repeat volta 2 {
        r8\sectionmark "2.B" b c | d4. c8 a4 e' | c8 c c b a4 e'4 | d d8 c a4 e'4 | c2~ c8
      } \break
      \repeat volta 2 {
        c8\posectionmark "3.A" c e | g g e c a'4 g | e8 c c c a'4 g | e8 c c c d4 e | c2~ c8
      }
      \repeat volta 2 {
        r8\sectionmark "3.B" b c | d4. c8 a4 e' | c c8 b8 a4 e' | d8 d d c a4 e'4 | c2 c8
      }
    }
    theLyricsOne = \lyricmode {
      % Lyric \repeats omitted, because of Lilypond's "repeat starts with rest and
      % has lyrics" problem.
      \set stanza = "1."
        Lou -- va -- do | se -- ja meu Di -- vi -- no | Pai;
        Meu Di -- vi -- no | Pai, lou -- va -- do | se -- ja.
        San -- ta Ma -- | ri -- a a -- qui na | terra;
        Nos en -- tre -- gan -- do~a | paz pa -- ra ven -- cer a | guer -- ra.
      \set stanza = "2."
        Va -- mos, | va -- mos meus ir -- | mãos;
        Va -- mos | to -- dos, va -- mos ca -- min -- | har. __
        Que a | or -- dem vem se -- | ve -- ra;
        É da Vir -- gem | Mãe e de São Jo -- | ão. __
      \set stanza = "3."
        Meu São -- Jo -- | ão é quem es -- tá man -- | dan -- do;~É
        quem es -- tá vi -- | bran -- do~e é quem vai bril -- | har. __
        Com as | Es -- tre -- las Di -- | vi -- nas;
        De Je -- sus | Cris -- to~e de San -- ta Ma -- | ri -- a.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 a:m | c a:m | c g:7 | c~ c8
      }
      \repeat volta 2 {
        s4. | g2 a:m | c a:m | g:7 g:7 | c~ c8
      }
      \repeat volta 2 {
        s4. | c2 a:m | c c | a:m f | c~ c8
      }
      \repeat volta 2 {
        s4. | g2 a:m | c a:m | g:7 g:7 | c~ c8
      }
      \repeat volta 2 {
        s4. | c2 a:m | c a:m | c g:7 | c~ c8
      }
      \repeat volta 2 {
        s4. | g2 a:m | c a:m | g:7 g:7 | c~ c8
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Praised be my Divine Father
    My Divine Father, praised be.
    Holy Mary here on earth
    We are bringing peace
    So that we will win the war.
    \nextverse
    Let's go, my brothers and sisters
    Let's all go, let's follow the path
    For the order comes severely
    From the Virgin Mother and St. John.
    \nextverse
    My St. John is who is ordering
    And he is who is vibrating
    And he will shine
    Along with the divine stars
    Of Jesus Christ
    And of the Holy Mary.
  \end{translation}
\endsong


\beginsong{São Irineu}[by={Solon Brito},tags={2x},key={C},sks={C, A}]
  \audio[key={C}]{https://soundcloud.com/zenashe_use/sao-irine-solo-brito-3-pad-maurilio}
  \musicnote{Tocar 2 vezes}
  \mnbeginchorus
    \[\mn{G}]Oh! meu |\[G]São \[\mn{E}]I\[\mn{D}]ri\[\mnc{C}C]neu|' \e \altchords{\id[1]{(A)}|E A | \e}
    \[\mn{G}]Aju|\[G]dai os \[\mn{E}]fi\[\mn{D}]lhos \[\mnc{C}C]seus|' \e \altchords{|E A | \e}
  \mnendchorus\mnbeginchorus
    \[\mn{G}]Minha |\[G]Santa Ma\[\mnc{C}C]ri|a \altchords{|E A | \e}
    \[\mn{G}]Se|nho\[\mn{E}]ra \[\mn{C}]da \[\mnc{G}G]Paz|' \e \altchords{|- E | \e}
    Aju|dai os \[\mn{E}]fi\[\mn{D}]lhos \[\mnc{C}C]seus|' \e \altchords{|- A | \e}
    \[\mn{G}]Assim |\[G7]como \[\mn{E}]meu \[\mn{D}]Pai \[\mnc{C}C]faz|' \e \altchords{|E7 A | \e}
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2021-08
    theMelody = \relative c''' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8\posectionmark "A" g | g4 e8 d c2~ | c2.
        g'8 g | g g e d c2~ | c2.
      } \break
      \repeat volta 2 {
        g'8\sectionmark "B" g | g4 g8 g8 c2 | c2.~ c8
        g8 | g4 e8 c g'2~ | g2.
        g8 g | g g e d c2~ | c2.
        g'8 g | g g e d c2~ | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        Oh! meu São I -- ri -- neu; __
        A -- ju -- dai os fi -- lhos seus. __
      } \repeat volta 2 {
        Mi -- nha San -- ta Ma -- ri -- a; __
        Se -- nho -- ra da Paz; __
        A -- ju -- dai os fi -- lhos seus; __
        As -- sim co -- mo meu Pai faz. __
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | g2 c2 | c1
        | g2 c2 | c2.
      }
      \repeat volta 2 {
        s4 | g2 c2 | c1
        | c2 g2 | g1
        | g2 c2 | c1
        | g2:7 c2 | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Oh! My Saint Irineu
    Help your children
    \nextverse
    My Holy Mary
    Lady of Peace
    Help your children
    Just like my father does
  \end{translation}
\endsong


\beginsong{Forças da Rainha da Floresta}[ititle={Santa Maria vem chegando}, by={Irineu Barsé}, tags={valsa}, key={Am}, sks={Bm, (Am)--(Cm)}]
  \meter{3}{4}
  \mnbeginchorus\memorize
    \[^\mn{E}]Santa Ma|\[\mnc{E}Am]ria vem che|\[\mnc{D}E]gando nes\[^\mn{E}]se \[^\mn{F}]ba\[^\mn{E}]ta|\[\mnc{C}Am]lhã\[^\mn{A}]o |\[A7] \e
    \[^\mn{E}]Trazendo as |\[\mnc{A}Dm]for\[^\mn{G}]ças da Ra|\[A7]in\[^\mn{F}]ha \[^\mn{E}]da \[^\mn{F}]flo|\[\mnc{E}Dm]res\[^\mn{D}]ta | \e
    São es\[^\mn{E}]sas |\[\mnc{F}Dm]forças vinda |\[G]de nos\[^\mn{A}]sa Se|\[C]nho\[^\mn{E}]ra |\[F] \e
    \[^\mn{D}]Que cen\[^\mn{C}]tra|\[\mnc{B}Dm7]lizam essa |\[E]luz a\[^\mn{C}]qui \[^\mn{B}]na |\[Am]ter\[^\mn{A}]ra | \e
  \mnendchorus
  \notesoff
  \beginchorus
    Eu vou pe|^dindo sempre |^a minha co|^ragem |^ \e
    Para se|^guir nesta ba|^talha do a|^mor | \e
    Com o com|^forto |^da minha mãe|^zinha |^ \e
    Com sua |^luz |^com seu resplen|^dor | \e
  \endchorus
  \noteson
  \mnbeginchorus
    \ind \[\mn{E}]Eu \[\mn{A}]vou \[\mn{G}]se|\[\mnc{F}Dm]guindo sem\[\mn{E}]pre \[\mn{D}]no \[\mn{C}]ca|\[\mnc{B}G]minho
    \ind \[\mn{D}]Sem\[\mn{G}]pre \[\mn{F}]gui|\[\mnc{E}C]ado pe\[\mn{D}]la \[\mn{C}]luz \[\mn{B}]di|\[\mnc{A}F]vina
    \ind \[\mn{E}]Sem\[\mn{F}]pre \[\mn{E}]bus|\[\mnc{D}Dm7]can\[\mn{B}]do apren|\[E]der nes\[\mn{C}]ta \[\mn{B}]dou|\[Am]tri\[\mn{A}]na | \e
  \mnendchorus
  \notesoff
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 4.
      \mark \markup {"4x"} \bar ".|:" \repeat volta 4 {
        e8\posectionmark "1. & 2." e8 e8 | e'4. e8 e8 e8 | d8.( d16 d8) e8 f8 e8  | c4 a2~ | a4. e'8 e8 e8 | a4. g8 g8 g8 | g4. f8 e8 f8 | e4( d2)~ | d4. d8 d8 e8
        | f4.( f8) f8( f8) | f4. f8 a8 a8 | a4 e2~ | e4. d8 d8 c8
        | b4.( b8 b8 b8) | b4. b8 c8 b8 | b4( a2)~ | a4.
      } \break
      \repeat volta 2 {
        e'8\sectionmark "3." a8 g8 | f8 f8 f8 e8 d8 c8 | b4 b8 d8 g8 f8 | e8 e8 e8 d8 c8 b8 | a4 a8 e'8 f8 e8
        | d4. b8 b8 b8 | b4. b8 c8 b8 | b4 a2~ | a4.
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 4 {
        \set stanza = "1."
        San -- ta Ma -- | ri -- a vem che -- |gan -- do nes -- se ba -- ta -- | lhã -- o; __ _
        Tra -- zen -- do~as | for -- ças da Ra -- | in -- ha da flo -- | res -- ta; __ _
        São es -- sas | for -- ças vin -- da | de nos -- sa Se -- | nho -- ra; __ _
        Que cen -- tra -- | li -- zam es -- sa | luz a -- qui na | ter -- ra. __ _
      }
      \repeat volta 2 {
        \set stanza = "3."
        Eu vou se -- | guin -- do sem -- pre no ca -- | min -- ho;
        Sem -- pre gui -- | a -- do pe -- la luz di -- | vi -- na;
        Sem -- pre bus -- | can -- do a -- pren -- | der nes -- ta dou -- | tri -- na. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Eu vou pe -- | din -- do sem -- pre | a __ _ _ min -- ha co  -- | ra -- gem; __ _
        Pa -- ra se -- | guir nes -- ta ba  -- |tal -- ha do a -- | mor; __ _ _
        Com o com -- | for __ _ -- to __ _ | da min -- ha mãe -- | zin -- ha; __ _
        Com su -- a | luz __ _ _ _ | com seu res -- plen -- | dor. __ _ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a2.:m | e | a:m | a:7
        | d:m | a:7 | d:m | d:m
        | d:m | g | c | f
        | d:m7 | e | a:m | a4.:m
      }
      \repeat volta 2 {
        s4. | d2.:m | g | c | f | d:m7 | e | a:m | a4.:m
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Santa Maria has been arriving in this company
    Bringing the forces of the Queen of the Forest
    They are these forces that come from our Lady
    That centralize this Light here on Earth
    \nextverse
    I will always ask for my courage
    To follow in this battle of love
    With the comfort of my mother
    With her light, with her radiance
    \nextverse
    I will always follow the Path
    Always guided by the Divine Light
    Always seeking to learn in this doctrine
  \end{translation}
\endsong

