% Santo Daime: O Chaveirão
% ========================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Hospede}[by={Glauco Villas Boas}, key={Am},gk={Am, Bm}]
  % Offered to Padr. Eduardo
  \audio[key=Am]{https://www.nossairmandade.com/hymn/2249/Hospede}
  \newchords{chords_hospede_a}\newchords{chords_hospede_b}
  \mnbeginchorus\memorize[chords_hospede_a]
    |\[\mnc{A}Am]Eu convi\[\bm]dei \[^\mn{B}]no \[^\mn{C}]meu |\[\mnc{D}Dm]so\[\bm]nho
    Meu |Mestre va\[\mnc{F}(F)]mos passe|\[\mnc{E}E]ar
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_hospede_b]
    \[^\mn{E}]Meu |\[\mnc{D}Dm]mestre \[\bmc\mn{F}]veio co|\[\mncii{E}{C}Am]migo
    \[\bmc\mn{E}]Na minha |\[\mncii{D}{B}E7]casa \[\bmc\mn{D}]me \[^\mn{G#}]visi|\[\mnc{A}Am]tar
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_hospede_a]
    |^Eu abra^çando o meu |^Mes^tre
    |Ai, meu ^Deus como é |^bom
  \endchorus\glueverses\beginchorus\replay[chords_hospede_b]
    |^Eu abra^çando meu |^Mestre
    Lem^brei do meu |^Pai, lembrei ^de Salo|^mão
  \endchorus
  \beginchorus\replay[chords_hospede_a]
    |^{O meu} ^Mestre me |^dis^se
    |Filho eu não ^vim passe|^ar
  \endchorus\glueverses\beginchorus\replay[chords_hospede_b]
    |^Vou estar ^sempre con|^tigo
    ^Bem ao teu |^lado, eu não ^vou te dei|^xar
  \endchorus
  \beginchorus\replay[chords_hospede_a]
    |^Nesta pas^sagem do |^Mes^tre
    |Vejam o que ^Ele me |^deu
  \endchorus\glueverses\beginchorus\replay[chords_hospede_b]
    |^Um ga^lhinho de ar|^ruda
    ^Com a |^benção do ^Mestre Iri|^neu
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-08
    theMelody = \relative a'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \repeat volta 2 {
        r4\posectionmark "A" | a4 a8 a8 a4 b,8 c8 | d2 d4( d4)
        | d4 d8 d8 f4 f8 f8 | e2.(
      }
      \repeat volta 2 {
        \parenthesize e4)\sectionmark "B" | d4. d8 f4 f8 f8 | e4. c8 e8( e8)( e8) e8
        | d4( d8) b8 d4 gis,8 gis8 | a2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      | Eu con -- vi -- dei no meu | so -- nho;
      Meu | Mes -- tre va -- mos pas -- se -- | ar.
      \set stanza = "1.B"
      Meu | Mes -- tre vei -- o co -- | mi -- go;
      Na mi -- _ nha | ca -- _ sa me vi -- si -- | tar.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      | Eu a -- bra -- çan -- do~o meu | Mes -- tre; __ _
      | Ai __ _ meu Deus como é | bom.
      \set stanza = "2.B"
      \skip 1 | Eu~a -- bra -- çan -- do meu | Mestre
      Lem -- brei __ _ do meu | Pai lem -- brei de Sa -- lo -- | mão.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      | O __ _ meu Mes -- tre me | dis -- se; __ _
      | Fi -- lho~eu não vim pas -- se -- | ar.
      \set stanza = "3.B"
      \skip 1 | Vou~es -- tar sem -- pre con -- | ti -- go;
      Bem __ _ ao teu | la -- do~eu não vou te dei -- | xar.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      | Nes -- ta pas -- sa -- gem do | Mes -- tre; __ _
      | Ve -- jam~o que E -- le me | deu.
      \set stanza = "4.B"
      \skip 1 | Um ga -- lhinho de ar -- | ru -- da;
      Com __ _ _ a | ben -- ção do Mes -- tre~I -- ri -- | neu.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a1:m | d:m
        | d2:m \parenthesize f | e2.
      }
      \repeat volta 2 {
        s4 | d1:m | a:m
        | e:7 | a2.:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    In my dream I invited my Master, let's walk
    My Master came near to visit me in my house
    \nextverse
    Embracing my Master, oh, how good my God is
    Embracing my Master I remembered my Father, I remembered Solomon
    \nextverse
    My Master said to me, child I did not come walk
    I will always be with you, right by your side, I will not leave you
    \nextverse
    In this passage of the Master, look what he gave me
    A sprig of rue with the blessing of Mestre Irineu
  \end{translation}
\endsong


\beginsong{Caboclo Véio}[by={Glauco Villas Boas}]
  \audio[key=Dm]{https://www.nossairmandade.com/hymn/2250/CabocloV\%C3\%A9io}
  \newchords{chords_cabocloveio_a}\newchords{chords_cabocloveio_b}
  \mnbeginverse\memorize[chords_cabocloveio_a]
    \[^\mn{D}]Cabo\[^\mn{F}]clo |\[\mnc{A}Dm]Véio vem a\[^\mn{F}]qui bus\[^\mn{E}]car um |\[^\mn{D}]povo
    Pra nós \[^\mn{F}]can|\[^\mn{A}]tar e vossa \[^\mn{F}]luz bri\[^\mn{D}]lhar de |\[\mnc{E}A]novo
  \mnendverse
  \mnbeginchorus\memorize[chords_cabocloveio_b]
    Da alta es|\[Gm]fera manda a nossa luz bril|hante
    para nós neste ins|\[A]tante ver quem sois Jurami|\[\up{2}(Dm)]dam
  \mnendchorus
  \notesoff
  \beginverse\replay[chords_cabocloveio_a]
    Me apresen|^tar também é o que mais |quero
    Só apa|relho quando tu estiver mais |^sério
  \endverse
  \beginchorus\replay[chords_cabocloveio_b]
    Bem cami|^nhando como filho verda|deiro
    Me apresento por in|^teiro, vou mostrar todo mis|^tério
  \endchorus
  \beginverse\replay[chords_cabocloveio_a]
    Juntando a |^glória do meu Senhor Jesus |Cristo
    Com a fir|meza do meu Santo Iri|^neu
  \endverse
  \beginchorus\replay[chords_cabocloveio_b]
    Todos as es|^trelas do universo se ajun|taram
    Num só verso da Ra|^inha e veja que festa se |^deu
  \endchorus
  \begin{translation}[EN]
    Caboclo Véio comes here to search for a people
    To sing for us and to shine your light anew
    \nextverse
    From the high sphere he sends our shining light
    For us in this instant to see who is Juramidam
    \nextverse
    To present to me also is what I want more
    Only the body when you are more serious
    \nextverse
    Traveling well as a true child
    I present myself completely, I will reveal all mystery
    \nextverse
    Joining the glory of my Lord Jesus Christ
    With the firmness of my St. Irineu
    \nextverse
    All the stars of the universe gathered
    Behind the Queen and watch what celebration is given
  \end{translation}
\endsong
