% Santo Daime: Hinos Diversos (Unilaiva)
% ======================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Elevei o Pensamento}[by={Ricardo Morais}, key={D}, gk={D, C--A}]
  \audio[key={D}]{https://www.nossairmandade.com/hymn/25/EleveiOPensamento}
  \audio[key={D}]{https://soundcloud.com/beijamima/elevei-meu-pensamento}
  \mnbeginchorus\memorize
    \[^\mn{D}]Ele\[\bm]vei o \[^\mn{C#}]pensa|\[\mnc{B}Bm]men\[\bm]to | \e \altchords{\id[1]{(C)}|Am | \e}
    A \[\bm]Deus la \[^\mn{C#}]nas \[^\mn{D}]al|\[\mnc{E}Em]tu\[\bm]ras | \e \altchords{|Dm | \e}
    \[^\mn{A}]Para \[\bmc\mn{C#}]eu re\[^\mn{B}]conhe|\[\mnc{A}A]cer\[\bm]{} | \e \altchords{|G | \e}
    O bri\[\bmc\mn{B}]lho da \[^\mn{C#}]for\[^\mn{E}]mo|\[\mnc{D}D]su\[\bm]ra | \e \altchords{|C | \e}
  \mnendchorus
  \notesoff
  \beginchorus
    O bri^lho da formo|^su^ra | \e \altchords{\id[2]{(F)}|Dm | \e}
    É u^ma luz de a|^len^to | \e \altchords{|Gm | \e}
    Que lim^pa meu cora|^ção^ | \e \altchords{|C | \e}
    E vigo^ra meu pensa|^men^to | \e \altchords{|F | \e}
  \endchorus
  \beginchorus
    A^qui eu vou can|^tan^do | \e \altchords{\id[3]{(G)}|Em | \e}
    Que a ^minha lida e |^es^sa | \e \altchords{|Am | \e}
    Viva ^Rei Jurami|^dam^ | \e \altchords{|D | \e}
    E a Ra^inha da flo|^res^ta | \e \altchords{|G | \e}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 2.
      \repeat volta 2 {
        \parenthesize d8 d8 \pomark d8 d8 cis8 cis8 | b2 b2~ | b4
        \parenthesize b8 b8 b8 b8 cis8 d8 | e2 e2~ | e4
        a,8 a8 cis8 cis8 b8 b8 | a1~ | a8( \parenthesize a8)
        a8 a8 b8 b8 cis8 e8 | d2 d2~ | d4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      E -- le -- vei o pen -- sa -- | men -- to; __ | _
      \skip 1 A Deus la nas al -- | tu -- ras; __ | _
      Pa -- ra eu re -- co -- nhe -- | cer; __ | _ _
      O bri -- lho da for -- mo -- | su -- ra. __ | _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      O bri -- lho da for -- mo -- | su -- ra; __ | _
      É u -- ma luz de a -- | len -- to; __ | _
      Que lim -- pa meu co -- ra -- | ção; __ | _
      E vi -- go -- ra meu pen -- sa -- | men -- to; __ | _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1 A -- qui eu vou can -- | tan -- do; __ | _
      Que a mi -- nha li -- da~e | es -- sa; __ | _
      Vi -- va Rei Ju -- ra -- mi -- | dam; __ | _
      E a Ra -- i -- nha da flo -- | res -- ta; __ | _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2. | b1:m | b:m
        | e:m | e:m
        | a | a
        | d | d4
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I raised up my thought to God there in the heights,
    For me to recognize the brilliance of beauty
    \nextverse
    The brilliance of beauty, it is a light of vital breath
    Who cleans my heart and invigorates my thoughts
    \nextverse
    Here I go singing because this is my task
    Viva King Juramidam and the Queen of the Forest
  \end{translation}
\endsong


\beginsong{O Bálsamo do Céu}[by={Baixinha}, tags={valsa}, key={Dm}, gk={Dm, Cm--D\shrp{}m}]
  % Also in songs_portuguese.tex (without lilypond notation)
  % Could this hymn be received by Isabel Barsé instead, as stated in nossairmandade.com?
  \audio[key=Dm]{https://www.nossairmandade.com/hymn.php?hid=2097}
  \audio[key=Dm]{https://soundcloud.com/lvaro-xi/b-lsamo-do-c-u}
  \meter{3}{4}
  \mnbeginchorus
    \lrep \[\mn{A}]O |\[\mnc{D}Dm]bálsamo \[\mn{E}]do |\[\mnc{F}F]Céu \[\mn{A}]des|\[\mnc{E}A]ceu \[\mn{F}]à |\[\mnc{E}Dm]Ter\[\mn{D}]ra \rrep
    \lrep \[\mn{A}]As |\[\mnc{B&}Gm]flo\[\mn{A}]res \[\mn{G}]da |\[\mnc{F}F]Ter\[\mn{E}]ra \[\mn{D}]rece|\[\mnc{A}A7]be\[\mn{C#}]ram \[\mn{E}]a |\[\mnc{D}Dm]Luz \rrep
  \mnendchorus
  \beginchorus\memorize
    \ind \lrep \[\mn{A}]Os |\[\mnc{D}Dm]homens \[\mn{E}]na |\[\mn{F}]Ter\[\mn{D}]ra \[\mn{F}]pre|\[\mnc{E}A]ci\[\mn{C#}]sam \[\mn{E}]do |\[\mnc{D}Dm]Bem \rrep
    \ind \lrep Meu |\[Gm]Pai é quem |\[F]manda mensa|\[A7]geiros do A|\[Dm]lém \rrep
  \endchorus
  \beginchorus
    \ind \lrep ^Os |^seres ^di|^vi^nos ^quem |^vem ^nos ^cu|^rar \rrep\notesoff
    \ind \lrep Com seus |^raios de |^Luz vem nos |^ilumi|^nar \rrep
  \endchorus
  \begin{translation}
    The balsam of Heaven came down to Earth
    The flowers of the Earth received the Light
    \nextverse
    The men of the Earth need the goodness
    My Father is who orders the messengers from beyond
    \nextverse
    The divine beings that come to heal us
    With their rays of light they come to illuminate us
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      % transcribed by larva on 2022-08
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 3/4 \partial 4
      \repeat volta 2 {
        a4 \sectionmark "1.A" | d8 d8 d4 e4 | f2 a4 | e2 f4 | e4 d4
      }
      \repeat volta 2 {
        a'4 \sectionmark "1.B" | bes4 a4 g4 | f4 e4 d8 d8 | a4 cis4 e4 | d2
      }
      \repeat volta 2 {
        a4 \sectionmark "2.A" | d4 d4 e4 | f4 d4 f4 | e4 cis4 e4 | d2
      }
      \repeat volta 2 {
        a'4 \sectionmark "2.B" | bes4 a4 g4 | f4 e4 d8 d8 | a4 cis4 e8 e8 | d2
      }
      \repeat volta 2 {
        a4 \posectionmark "3.A" | d4 d4 e4 | f4 d4 f4 | e4 cis4 e4 | d2
      }
      \repeat volta 2 {
        a'8 \sectionmark "3.B" a8 | bes4 a4 g4 | f4 e4 d4 | a4 cis4 e4 | d2
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        O | bál -- sa -- mo do | Céu des -- | ceu à | Ter -- ra.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        As | flo -- res da | Ter -- ra re -- ce -- | be -- ram a | Luz.
      }
      \set stanza = "2.A"
      \repeat volta 2 {
        Os | ho -- mens na | Ter -- ra pre -- | ci -- sam do | Bem.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Meu | Pai é quem | man -- da men -- sa -- | gei -- ros do A -- | lem.
      }
      \set stanza = "3.A"
      \repeat volta 2 {
        Os | se -- res di -- | vi -- nos quem | vem nos cu -- | rar.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Com seus | rai -- os de | Luz vem nos | i -- lu -- mi -- | nar.
      }
    }
    theChords = \chordmode {
      % 1st verse
      \repeat volta 2 {
        s4 | d2.:m | f | a | d2:m
      }
      \repeat volta 2 {
        s4 | g2.:m | f | a:7 | d2:m
      }
      % 2nd verse
      \repeat volta 2 {
        s4 | d2.:m | d:m | a | d2:m
      }
      \repeat volta 2 {
        s4 | g2.:m | f | a:7 | d2:m
      }
      % 3rd verse
      \repeat volta 2 {
        s4 | d2.:m | d:m | a | d2:m
      }
      \repeat volta 2 {
        s4 | g2.:m | f | a:7 | d2:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Saint Germain}[by={Léo Artese}, tags={valsa}, key={Bm}, gk={Cm, (Bm)--(Cm)}]
  \audio[key=Em]{https://soundcloud.com/sergio-moreira-slmore/24-saint-germain}
  \audio[key=Em]{https://www.youtube.com/watch?v=wZ5x4su95eg}
  \newchords{chords_saintgermain_a}\newchords{chords_saintgermain_b}
  \meter{3}{4}
  \transpose{-5}
  \mnbeginverse\memorize[chords_saintgermain_a]
    \[^\mn{B}]Vou \[^\mn{G}]di|\[\mnc{E}Em]zer |{ } o que |deves fa|zer \[^\mn{G}]pa\[^\mn{E}]ra |\[\mnc{F#}B7]al\[^\mn{D#}]can|\[^\mn{B}]çar |{ }{ }{ } | \e
    \[^\mn{B}]Um \[^\mn{G}]lu|\[\mnc{E}Em]gar |{ } na infi|nita cons|ciên\[^\mn{G}]cia \[^\mn{E}]de |\[\mnc{F#}B7]Deus |{ }{ }{ } |{ }{ }{ } | \e
    \mnendverse\glueverses\mnbeginchorus\memorize[chords_saintgermain_b]
    \[^\mn{F#}]Com\[^\mn{G}]preen|\[\mnc{A}Am]der |{ } que \[^\mn{B}]Deus |\[^\mn{C}]é{ } |{ }{ } \[^\mn{E}]tu|\[\mnc{B}Em]do |{ }{ } \[^\mn{G}]que |\[^\mn{E}]há | \e
    \[^\mn{G}]Eu |\[\mnc{F#}B7]e |{ }{ } \[^\mn{D#}]vo|\[^\mn{B}]cê, |{ } \[^\mn{G}]meu \[^\mn{F#}]ir|\[\mnc{E}Em]mão |{ }{ }{ } |\[\up{1}(E7)]{ } | \e
  \mnendchorus
  \notesoff
  \beginverse\replay[chords_saintgermain_a]
    Eu sou |^Luz, |{ } sou A|mor, sou Sa|úde, eu sou |^Perfei|ção |{ }{ }{ } | \e
    Sei que eu |^sou |{ } a pre|sença de |Deus em a|^ção |{ }{ }{ } |{ }{ }{ }  | \e
    \endverse\glueverses\beginchorus\replay[chords_saintgermain_b]
    Sou que |^sou, |{ } sou fi|lho |{ }{ } da |^Cri|{ }{ } a|ção | \e
    Eu |^e |{ }{ } vo|cê, |{ } meu ir|^mão |{ }{ }{ } |^{ } | \e
  \endchorus
  \beginverse\replay[chords_saintgermain_a]
    Eu Sou |^Pai, |{ } eu sou |Mãe, sou Fi|lho também |^sou Ir|mão |{ }{ }{ } | \e
    Sou o |^Yin |{ } e o |Yang em per|feita uni|^ão |{ }{ }{ } |{ }{ }{ } | \e
    \endverse\glueverses\beginchorus\replay[chords_saintgermain_b]
    Sou a |^Cha{ - }|{ } ma Vio|le{ - }|{ } ta em |^ex{ - }|{ }{ } pan|são | \e
    Sou |^Saint |{ } Ger|main, |{ } meu ir|^mão |{ }{ }{ } |^{ } | \e
  \endchorus
  \beginverse\replay[chords_saintgermain_a]
    Vás bus|^car |{ } a cons|ciência do |Cristo In|^teri|or |{ }{ }{ } | \e
    Prati|^can{ - }|{ } do o a|mor que não |tem condi|^ção |{ }{ }{ } |{ }{ }{ } | \e
    \endverse\glueverses\beginchorus\replay[chords_saintgermain_b]
    Nova |^e|{ } ra, na |ter|ra se i|^ni|{ }{ } ci|ou | \e
    Quem |^é |{ } vo|cê, |{ } meu ir|^mão? |{ }{ }{ } |^{ } | \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-10
    theMelody = \transpose e b, \relative b'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key e \minor \time 3/4 \partial 2
      b4 _\posectionmark "A" g4 | e2.~ | e4 e4 e4 | e e e | e g e | fis2 dis4 | b2.~ | b2.~ | b4
      b'4 g4 | e2.~ | e4 e4 e4 | e e e | e g e | fis2.~ | fis2.~ | fis2.~ | fis4
      \repeat volta 2 {
        fis4 \sectionmark "B" g | a2.~ | a4 a4 b4 | c2.( | c2) e4 | b2.~ | b2 g4 | e2.~ | e2
        g4 | fis2.~ | fis2 dis4 | b2.~ | b4 g'4 fis4 | e2.~ | e2.~
      } \alternative {
        { | e2.~ | e4 }
        { | e2.~ \repeatTie | e4 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Vou di -- | zer __ | _ o que | de -- ves fa -- | zer pa -- ra | al -- can -- | çar; __ | _ | _
      Um lu -- | gar __ | _ na~in -- fi -- | ni -- ta cons -- | ciên -- cia de | Deus. __ | _ | _ | _
      \set stanza = "1.B"
      \repeat volta 2 {
        Com -- preen -- | der __ | _ Que Deus | é __ | _ tu -- | do __ | _ que | há; __ | _
        Eu | e __ | _ vo -- | cê, __ | _ meu ir -- | mão. __ | _ | _ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Eu sou | Luz, __ | _  sou A -- | mor, sou Sa -- | ú -- de,~eu sou | Per -- fei -- | ção; __ | _ | _
      Sei que~eu | sou __ | _ a pre -- | sen -- ça de | Deus em a -- | ção. __ | _ | _  | _
      \set stanza = "2.B"
      \repeat volta 2 {
        Sou que | sou, __ | _ sou fi -- | lho __ | _ da | Cri -- | _ a -- | ção; __ | _
        Eu | e __ | _ vo -- | cê, __ | _ meu ir -- | mão. __ | _ | _ | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      Eu sou | Pai, __ | _ eu sou | Mãe, sou Fi -- | lho, tam -- bém | sou Ir -- | mão; __ | _ | _
      Sou o | Yin __ | _ e o | Yang em per -- | fei -- ta~u -- ni -- | ão. __ | _ | _ | _
      \set stanza = "3.B"
      \repeat volta 2 {
        Sou a | Cha -- | _ ma Vio -- | le -- | _ ta~em | ex -- | _ pan -- | são; __ | _
        Sou | Saint __ | _ Ger -- | main, __ | _ meu ir -- | mão. __ | _ | _ | _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      Vás bus -- | car __ | _ a cons -- | ciên -- cia do | Cris -- to In -- | te -- ri -- | or; __ | _ | _
      Pra -- ti -- | can -- | _ do~o a -- | mor que não | tem con -- di -- | ção. __ | _ | _ | _
      \set stanza = "4.B"
      \repeat volta 2 {
        No -- va | e -- | _ ra, na | ter -- | ra se~i -- | ni -- | _ ci -- | ou; __ | _
        Quem | é __ | _ vo -- | cê, __ | _ meu ir -- | mão? __ | _ | _ | _
      }
    }
    theChords = \transpose e b, \chordmode {
      r2 | e2.:m | e:m | e:m | e:m
      | b2.:7 | b:7 | b:7 | b:7
      | e2.:m | e2.:m | e:m | e:m
      | b2.:7 | b:7 | b:7 | b4:7
      \repeat volta 2 {
        s2 | a2.:m | a:m | a:m | a:m
        | e2.:m | e2.:m | e:m | e:m
        | b2.:7 | b:7 | b:7 | b:7
        | e2.:m | e2.:m
      } \alternative {
        { | e2.:7 | e4:7 }
        { | e2.:m | e4:m }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \iflyriconly\forcebrk\fi
  \begin{translation}
    I will tell you what you must do to achieve
    A place in the infinite consciousness of God
    Understanding that God is all there is
    I and you, my brother
    \nextverse
    I am Light, I am Love, I am Health, I am Perfection
    I know that I am the presence of God in action
    I am who I am, I am a child of Creation
    I and you, my brother
    \nextverse
    I am a Father, I am a Mother, I am a Son, I am a brother too
    I am Yin and Yang in perfect union
    I am the expanding Violet Flame
    I am Saint Germain, my brother
    \nextverse
    Go seek the consciousness of the Inner Christ
    Practicing the love that has no condition
    A new age on Earth has begun
    Who are you, my brother?
  \end{translation}
  % Only on if no lilypond, for the song to fit a spread:
  \ifshowlilypond\else%
    \begin{explanation}
      \textbf{Saint Germain} (also sometimes referred to as Master Rákóczi or Master R)
      is a legendary spiritual master of the ancient wisdom in various Theosophical
      and post-Theosophical teachings, said to be responsible for the New Age culture
      of the Age of Aquarius and identified with the Count Saint Germain (fl. 1710–-1784).
    \end{explanation}
  \fi
\endsong


\beginsong{Chamei Mamãe Jurema}[by={Padr. Valdete}, key={Bm}, gk={Cm, (Bm)--Cm--D\shrp{}m}]
  \audio{https://nossairmandade.com/hymn/149/ChameiMam\%C3\%A3eJurema}
  \audio[key=Bm]{https://soundcloud.com/spencer-stewart-3/15-chamei-mamae-jurema-06}
  \audio[key=Bm]{https://www.youtube.com/watch?v=hCAdRdcadVU}
  \mnbeginchorus\memorize
    \[^\mn{F#}]Cha|\[\mnc{B}Bm]mei \[\bmc\mn{D}]Mamãe Ju|\[^\mn{C#}]re\[^\mn{B}]ma\[\bm], \[^\mn{F#}]cha|\[^\mn{B}]mei \[^\mn{C#}]Ma\[\mnc{D}B7]mãe \[^\mn{C#}]Ie\[^\mn{B}]man|\[\mnc{E}Em]já \[\bm]
    \lrep \[^\mn{E}]Cha|\[Em]mei Papai \[\bmc\mn{G}]Ogum \[^\mn{F#}]da |\[\mnc{D}Bm]Ma\[^\mn{B}]ta\[\bm], \[^\mn{D}]cha|\[\mnc{C#}F#]mei Pa\[^\mn{D}]pai \[\mnc{E}F#7]O\[^\mn{D}]gum \[^\mn{C#}]do |\[\mnc{B}Bm]Mar \[\up{1}B7]{} \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    Cha|^mei to^dos os ca|boclos^, cha|mei to^dos Ori|^xás ^
    \lrep Cha|^mei to^das as fa|^langes^, que Deus do|^mina na ^terra e no |^mar ^ \rrep
  \endchorus
  \beginchorus
    Cha|^mei to^das essas |forças^, para |virem ^me aju|^dar ^
    \lrep Me |^defender ^das tenta|^ções^, que |^so querem ^me derri|^bar ^ \rrep
  \endchorus
  \beginchorus
    Tenho |^fé no ^meu Pai E|terno^, e na |minha Mãe ^Imacu|^la^da
    \lrep Que |^com meu Se^nhor São Mi|^guel^, eu |^vou ven^cer a jor|^na^da \rrep
  \endchorus
  \beginchorus
    É |^so pres^tar aten|ção^, na li|ção que es^ta estu|^dan^do
    \lrep |^Para ^poder pas|^sar^, nas |^provas ^que vem che|^gan^do \rrep
  \endchorus
  \beginchorus\ifshowlilypond\normalsize\fi % to fit on a spread
    Es|^tuda ^com aten|ção^, na es|cola que se ^matricu|^lou ^
    \lrep Para pro|^var que ^é bom a|^luno^: e es|^ta com o ^seu Profes|^sor ^ \rrep
  \endchorus
  \beginchorus\ifshowlilypond\normalsize\fi % to fit on a spread
    |^Eu pro^meto a meu |Mestre^, que eu |vou pi^sar no ba|^ten^te
    \lrep |^Que de a^gora pra |^frente, e ^olho por |^olho e ^dente por |^den^te \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2023-02
    theMelody = \relative fis' {
      \set melismaBusyProperties = #'() \slurDashed
      \key b \minor \time 4/4 \partial 4.
      r8 \posectionmark "A" fis8( fis8) | b4. ( b8 ) d8( d8)( d8) d8 | cis4( b2)
      fis8( fis8) | b8( b8)( b8) cis8 d4 cis8 b8 | e2( e8)
      \repeat volta 2 {
        \parenthesize e8 \sectionmark "B" e8( e8) | e4( e8) e8 g4 g8 fis8 | d4( b8)( b8)
        \parenthesize d8( \parenthesize d8) d8( d8) | cis4( cis8) d8 e4 d8 cis8
      } \alternative {
        { | b2( b8) }
        { | b2( b8) \dacapo s16 \bar "|." } % s16 is to allow space for D.C.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Cha -- _ | mei __ _ Ma -- mãe __ _ Ju -- | re -- ma;
      cha -- _ | mei __ _ _ Ma -- mãe Ie -- man -- | já; __ _
      \repeat volta 2 {
        \skip 1 Cha -- _ | mei Pa -- pai O -- gum da | Ma -- ta; __ _
        \skip 1 \skip 1 cha -- _ | mei Pa -- pai O -- gum do
      } \alternative {
        { | Mar. __ _ }
        { | Mar. __ _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Cha -- _ | mei to -- dos __ _ os ca -- | bo -- clos,
      cha -- _ | mei __ _ _ to -- dos O -- ri -- | xás; __ _
      \repeat volta 2 {
        \skip 1 Cha -- _ | mei __ _ to -- das as fa -- | lan -- ges, __ _
        \skip 1 que Deus do -- | mi -- na na ter -- ra~e no 
      } \alternative {
        { | mar. __ _ }
        { | mar. __ _ }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Cha -- _ | mei to -- das __ _ es -- sas | for -- ças,
      pa -- ra | vi -- _ _ rem me a -- ju -- | dar; __ _
      \repeat volta 2 {
        \skip 1 Me __ _ | de -- fen -- der das ten -- ta -- ções, __ _ _
        \skip 1 \skip 1 que __ _ so que -- rem me der -- ri -- 
      } \alternative {
        { | bar. __ _ }
        { | bar. __ _ }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      Te -- nho | fé no meu __ _ Pai E -- | ter -- no,
      e na | mi -- _ nha Mãe I -- ma -- cu -- | la -- da;
      \repeat volta 2 {
        \skip 1 Que __ _ | com meu Se -- nhor São Mi -- | guel, __ _ _
        \skip 1 \skip 1 eu __ _ | vou __ _ ven -- cer a jor --
      } \alternative {
        { | na -- da. }
        { | na -- da. }
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
        É __ _ | so pres -- tar __ _ a -- ten -- | ção, __ _
        na li -- | ção __ _ que es -- ta es -- tu -- | dan -- do;
      \repeat volta 2 {
        \skip 1 \skip 1 \skip 1 | Pa -- _ ra po -- der pas -- | sar, __ _ _
        \skip 1 \skip 1 nas __ _ | pro -- _ vas que vem che --
      } \alternative {
        { | gan -- do. }
        { | gan -- do. }
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
        Es -- _ | tu -- da com __ _ a -- ten -- ção; __ _
        na es -- | co -- la que se ma -- tri -- cu -- | lou, __ _
      \repeat volta 2 {
          Pa -- ra pro -- | var __ _ que é bom a -- | lu -- no: __ _
          \skip 1 \skip 1 e es -- | ta com o seu Pro -- fes --
      } \alternative {
        { | sor. __ _ }
        { | sor. __ _ }
      }
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7."
      \skip 1 \skip 1 | Eu pro -- me -- _ to~a meu | Mes -- tre,
      que eu | vou __ _ _ pi -- sar no ba -- | ten -- te;
      \repeat volta 2 {
        \skip 1 \skip 1 \skip 1 | Que de a -- go -- ra pra | fren -- te,
        e o -- _ lho por | o -- lho e den -- te por
      } \alternative {
        { | den -- te. }
        { | den -- te. }
      }
    }
    theChords = \chordmode {
        s4. | b1:m | b1:m | b2:m b2:7 | e'2:m~8
      \repeat volta 2 {
        s4. | \once \set chordChanges = ##f e'1:m | b1:m | fis2 fis2:7
      } \alternative {
        { | b2:m b8:7 }
        { | b2.:m~8 }
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    I called on Mother Jurema, I called on Mother Yemanja
    I called on Father Ogum of the forest, I called on Father Ogum of the sea
    \nextverse
    I called on all the caboclos, I called on all the Orixás
    I called on all the phalanxes that God rules on land and sea
    \nextverse
    I called on all these forces to come and help me
    To defend me from the temptations that only want to bring me down
    \nextverse
    I have faith in my Eternal Father and in my Immaculate Mother
    that with my Lord Saint Michael, I will overcome the journey
    \nextverse
    Just pay attention to the lesson you are studying
    So that you can pass the tests that are coming
    \nextverse
    Study attentively in the school you enrolled in
    To prove that you are a good student and are with your Teacher
    \nextverse
    I promise my Master that I will work hard
    From now on it's an eye for an eye and a tooth for a tooth.
  \end{translation}
\endsong


\beginsong{Verdade Pura}[by={William Vilas Boas}, key={Gm}, gk={Gm}]
  \audio[key=Gm]{https://www.youtube.com/watch?v=VtNEgkn707I}
  \mnbeginchorus\memorize
    \lrep \[^\mn{D}]Esta é \[\bmc\mn{B&}]a \[^\mn{A}]dou|\[\mnc{D}Gm]tri\[\bm]na, | do Sol \[\bmc\mn{E&}]e \[^\mn{D}]da |\[\mnc{C}Cm]Lu\[\bm]a |\[Cm6]{} \e
    \[^\mn{A}]E \[\bm]das \[^\mn{G}]Es|\[\mnc{F#}D]tre\[\bmc\mn{D}]las, |\[D7]{} e da \[^\mn{E&}]Ver\[\bmc\mn{D}]da\[^\mn{C}]de |\[\mnc{D}Gm]Pu\[\bm]ra |\[\up{2}(G7)]{} \e \rrep
    \ind \lrep \[^\mn{D}]Para \[\bmc\mn{E&}]com\[^\mn{D}]preen|\[\mnc{C}Cm]der, pa\[^\mn{D}]ra \[\bmc\mn{B&}]com\[^\mn{D}]preen|\[^\mn{C}]der
    \ind \[^\mn{A}]É \[^\mn{B&}]ter \[^\mn{C}]e\[\bmc\mn{D}]du\[^\mn{C}]ca|\[\mnc{B&}B&]ção, \[^\mn{A}]é \[^\mn{B&}]ter \[^\mn{C}]e\[\bmc\mn{D}]du\[^\mn{C}]ca|\[^\mn{B&}]ção
    \ind Não \[\bmc\mn{C}]se \[^\mn{B&}]jul|\[\mnc{A}D]gar,\[\bm]{} |\[D7]{} nem jul\[\bmc\mn{B&}]gar os \[^\mn{A}]seus ir|\[\mnc{/}Gm]mãos\[\bm]{} |\[\up{1}G7]{} \e \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep Quem ^mais quer |^ser ^ | é quem ^menos |^é ^ |^
    Sigamos ^o ex|^em^plo |^ do bom Je^sus de Naza|^ré ^ |^ \e \rrep
    \ind Tanto ^que so|^freu, tanto ^que so|freu
    \ind Que se ^humi|^lhou, que se ^humi|lhou
    \ind So^freu na |^cruz^ |^ e a todos ^Ele perdo|^ou ^ |\[G7]{} \e
    \ind Tanto \[\bm]que so|\[Cm]freu, tanto \[\bm]que so|freu
    \ind Que se \[\bm]humi|\[B&]lhou, que se \[\bm]humi|lhou
    \ind Mor\[\bm]reu na |\[D]cruz\[\bm]{} |\[D7]{} para ensi\[\bm]nar o que é o A|\[Gm]mor \[\bm]{} | \e
  \endchorus
  \begin{translation}\scriptsize % to fit on a page
    This is the doctrine of the Sun and the Moon
    And of the Stars and the Pure Truth
    \ind To understand, to understand
    \ind It's education, it's education
    \ind Do not judge yourself or judge your brothers
    \nextverse
    Who more wants to be, is who least is
    Let us follow the example of the good Jesus of Nazareth
    \ind So much he suffered, so much he suffered
    \ind Who humbled himself, who humbled himself
    \ind \up{1}Suffered on the cross, and all He forgave
    \ind \up{2}He died on the cross to teach what love is
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-07
    \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \key g \minor \time 4/4 \partial 2.
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        d8( \posectionmark "A" d) bes'4 a
        | d,2( d2)~ | d4 d8 d8 es4 d4 | c2( c2)~ | \once\slurDown c8\parenthesize a' a8( a) a4 g4
        | fis2 d2~ | d8 d8 8 es d8( d) c( c)
      } \alternative {
        { | d2( d2)~ | d4 }
        { | d2( d2)~ | d4 }
      } \break
      \repeat volta 2 {
        d8 \sectionmark "B" d es4 d
        | c c8 d es4 d | c8 \parenthesize a bes c d4 c | bes8 \parenthesize a bes c d4 c | bes bes c bes
        | a1~ | a8( a8) a8 a bes bes a a
      } \alternative {
        { | d1~ | d4 }
        { | g,1~ | g4 \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Es -- ta~é a dou -- | tri -- na | _
        Do Sol e da | Lu -- a; | _ _
        E __ _ das Es -- | tre -- las | _
        E da Ver -- da -- _ de __ _
      } \alternative {
        { | Pu -- ra. | _ }
        { | Pu -- ra. | _ }
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Pa -- ra com -- preen -- | der
        Pa -- ra com -- preen -- | der;
        É ter e -- du -- ca -- | ção
        É ter e -- du -- ca -- | ção;
        Não se jul -- | gar __ | _ _
        Nem jul -- gar os seus ir --
      } \alternative {
        { | mãos. | _ }
        { | mãos. | _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Quem __ _ mais quer | ser __ _ | _
        É quem me -- nos | é; __ _ | _
        Si -- ga -- mos o ex -- | em -- plo | _
        Do bom Je -- sus de Na -- za --
      } \alternative {
        { | ré. __ _ | _ }
        { | ré. __ _ | _}
      }
      <<
        {
          \set stanza = "2.B:i"
          \repeat volta 2 {
            Tan -- to que so -- | freu
            Tan -- to que so -- | freu;
            \skip 1 Que se hu -- mi -- | lhou
            \skip 1 Que se hu -- mi -- | lhou;
            So -- freu na | cruz | _
            E~a to -- dos E -- le per -- do --
          } \alternative {
            { | ou. | _ }
            { | | }
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "2.B:ii"
          \repeat volta 2 {
            Tan -- to que so -- | freu
            Tan -- to que so -- | freu;
            \skip 1 Que se hu -- mi -- | lhou
            \skip 1 Que se hu -- mi -- | lhou;
            Mor -- reu na | cruz | _
            Pa -- ra~en -- si -- nar o que~é~o A-
          } \alternative {
            { }
            { | _ | _ | mor. | _ }
          }
        }
      >>
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2.
        | g1:m | 1 | c:m | c:m6
        | d | d:7
      } \alternative {
        { | g1:m | 4 }
        { | g1:m | g4:7~ }
      }
      \repeat volta 2 {
        2.
        | c1:m | 1 | bes
        | bes | d | d:7
      } \alternative {
        { | g1:m | g4:7 }
        { | g1:m | 4~ }
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\ifchorded\else\sclearpage\fi
\beginsong{Santíssimo Daime}[by={José Ricardo}, off={Cyrenia}, key={Am}, gk={Am, Gm--Bm}]
  \audio{https://nossairmandade.com/hymn/2172/Sant\%C3\%ADssimoDaime}
  \audio[key=Am]{https://soundcloud.com/igreja-mestre-irineu/santissimo-daime}
  \audio[key=Am]{https://www.youtube.com/watch?v=hoYtePc5ICg}
  \mnbeginchorus\memorize
    \[^\mn{A}]Eu que\[^\mn{C}]ro |\[\mnc{E}Am]mais\[\bm]{} \[^\mn{D}]é \[^\mn{E}]to\[^\mn{D}]mar |\[^\mn{A}]Dai\[\bm]me \altchords{\id[1]{(Bm)}|Bm | \e}
    Eu \[^\mn{C}]que\[^\mn{E}]ro |\[^\mn{A}]mais\[\bm]{} \[^\mn{G}]é \[^\mn{A}]me \[^\mn{G}]cu|\[\mnc{D}Dm]rar \[\bm]{} \altchords{| - |Em}
    De tudo o |que ainda me \[\bm]pega nes\[^\mn{F}]ses |\[\mnc{A}Am]di\[\bm]as \altchords{| - |Bm}
    \[^\mn{A}]Um di\[^\mn{C}]a a|\[\mnc{E}E]in\[E7]{-} \[^\mn{D}]{da eu} \[^\mn{E}]che\[^\mn{D}]go |\[\mnc{A}Am]lá \[\bm]{} \altchords{|F\shrp{} F\shrp{}7 |Bm}
  \mnendchorus
  \notesoff
  \beginchorus
    Eu chego |^lá \noteson\[\mnlow{D}]{e é} \[\mnlow{E}]pa\[\mnlow{D}]ra\notesoff{} ^nunca mais vol|tar ^
    Voltar pras |tre\noteson\[\mnlow{G}]vas \[\mnlow{A}]des\[\mnlow{G}]se\notesoff{} ^mundo de ilu|^são ^
    Falso bri|lhante, por^tal da escuri|^dão ^
    Com Deus eu |^que^{-ro é} sempre es|^tar ^
  \endchorus
  \beginchorus
    Pra cami|^nhar \noteson\[\mnlow{D}]nes\[\mnlow{E}]se \[\mnlow{D}]de\notesoff{}^serto, eu tomo |Dai^me \altchords{\id[2]{(Gm)}|Gm | \e}
    Qual beija-|flor \noteson\[\mnlow{G}]eu \[\mnlow{A}]vou \[\mnlow{G}]be\notesoff{}^bendo desse a|^mor ^ \altchords{| - |Cm}
    O Santo |Daime é que ^mata a minha |^se^de \altchords{| - |Gm}
    E me dá |^bri\noteson\[\mnlow{D}]lho \[\mnlow{E}]pra eu \[\mnlow{D}]po\notesoff{}^der continu|^ar ^ \altchords{|D D7 |Gm}
  \endchorus
  \beginchorus
    O Santo |^Dai\noteson\[\mnlow{D}]me, \[\mnlow{E}]a\[\mnlow{D}]go\notesoff{}^ra vou afir|mar ^
    É Jesus |Cris\noteson\[\mnlow{G}]to \[\mnlow{A}]que \[\mnlow{G}]vol\notesoff{}^tou com Seu A|^mor ^
    Miseri|córdia, Bon^dade Infi|^ni^ta
    Eu agra|^de^{-ço e} dou lou|^vor ^
  \endchorus
  \beginchorus
    Se a|^cor\noteson\[\mnlow{D}]dem \[\mnlow{E}]meus \[\mnlow{D}]ir\notesoff{}^mãos pra esse a|mor ^
    E compre|en\noteson\[\mnlow{G}]dam \[\mnlow{A}]es\[\mnlow{G}]se\notesoff{} ^tempo em que vi|^ve^mos
    É prova|ção mas é ^a transforma|^ção ^
    A grande |^chan\[\mnlow{D}]ce \[\mnlow{E}]pa\[\mnlow{D}]ra a\notesoff{} ^ilumina|^ção ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-07
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \key a \minor \time 4/4 \partial 4.
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        \parenthesize a8 \pomark a c | e8( \altcol\parenthesize d \altmark "2., 3., 4., 5." \altcol\parenthesize e \altcol\parenthesize d \parenthesize e) d8 e d | a2( \parenthesize a8)
        a8 c e | a8( \altcol\parenthesize g \altmark "2., 3., 4., 5." \altcol\parenthesize a \altcol\parenthesize g \parenthesize a) g8 a g | d2( \parenthesize d8)
        d8 d d | d8( d8) d8 d d d d f | a2( \parenthesize a8)
        a,8 a8 c | e8( \altcol \parenthesize d \altmark "3., 5." \altcol \parenthesize e \altcol \parenthesize d \parenthesize e8) d e d | a2~ a8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu que -- ro | mais __ _ _ _ _ é to -- mar | Dai -- me;
        Eu que -- ro | mais __ _ _ _ _ é me cu -- | rar; __ _
        De tu -- do~o | que ain -- da me pe -- ga nes -- ses | di -- as;
        Um di -- a~a -- | in -- _ _ _ _ da~eu che -- go | lá. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Eu che -- go | lá \altcol e~é \altcol pa -- \altcol ra nun -- ca mais vol -- | tar; __ _
        Vol -- tar pras | tre -- \altcol vas \altcol des -- \altcol se mun -- do de~i -- lu -- | são; __ _
        Fal -- so bri -- | lhan -- _ te, por -- tal da~es -- cu -- ri -- | dão; __ _
        Com Deus eu | que -- _ _ _ _ ro~é sem -- pre~es -- | tar. _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        \set stanza = "3."
        Pra ca -- mi -- | nhar \altcol nes -- \altcol se \altcol de -- ser -- to,~eu to -- mo | Dai -- me;
        Qual bei -- ja -- | flor \altcol eu \altcol vou \altcol be -- ben -- do des -- se~a -- | mor; __ _
        O San -- to | Dai -- me é que ma -- ta~a mi -- nha | se -- de;
        E me dá | bri -- \altcol lho \altcol pra~eu \altcol po -- der con -- ti -- nu -- | ar. _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        O San -- to | Dai -- \altcol me, \altcol a -- \altcol go -- ra vou a -- fir -- | mar; __ _
        É Je -- sus | Cris -- \altcol to \altcol que \altcol vol -- tou com Seu A -- | mor; __ _
        Mi -- se -- ri -- | cór -- _ dia, Bon -- da -- de In -- fi -- | ni -- ta;
        Eu a -- gra -- | de -- _ _ _ _ ço~e dou lou -- | vor. _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \repeat volta 2 {
        \skip 1 Se a -- | cor -- \altcol dem \altcol meus \altcol ir -- mãos pra es -- se~a -- | mor; __ _
        E com -- pre -- | en -- \altcol dam \altcol es -- \altcol se tem -- po~em que vi -- | ve -- mos;
        É pro -- va -- | ção _ mas é a trans -- for -- ma -- | ção; __ _
        A gran -- de | chan -- \altcol ce \altcol pa -- \altcol ra~a i -- lu -- mi -- na -- | ção. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4.
        | a1:m | a:m
        | a:m | d:m
        | d:m | a:m
        | e2 e:7 | a2:m~ 8
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation} % to fit on one spread
    What I want more is to drink Daime, what I want more is to heal myself
    Of everything that still gets me these days, one day I'll get there
    \nextverse
    I get there and it's never to return, to return to the darkness of this world of illusion
    Fake brilliance, portal of darkness; with God I always want to be
    \nextverse
    To walk in this desert, I drink Daime; like hummingbird I am drinking from this love
    The Santo Daime is what quenches my thirst, and it gives me brightness so I can carry on
    \nextverse
    The Santo Daime, now I will affirm, it is Jesus Christ who has returned with His Love
    Mercy, Infinite Goodness; I give thanks and praise
    \nextverse
    Wake up my brothers for this love, and understand this time we live in
    It's ordeal but it's the transformation, the big chance for enlightenment
  \end{translation}
\endsong


\beginsong{Defuma Com as Ervas da Jurema}[by={?}, key={Am}, gk={Am, G\shrp{}--(Am)}]
  \audio[key=Am]{https://www.recantodasletras.com.br/audios/cancoes/83252}
  \mnbeginchorus\memorize
    \[^\mn{E}]De|\[\mnc{A}Am]fuma com \[^\mn{B}]as \[\bmc\mn{C}]ervas \[^\mn{B}]da \[^\mn{A}]Ju|\[^\mn{C}\mn{A}]{re}ma \[\bm]
    \[^\mn{E}]De|\[^\mn{A}]fuma com \[^\mn{B}]as \[\bmc\mn{C}]ervas \[^\mn{B}]{de Ie}\[^\mn{A}]man|\[\mnc{B}E]já \[\bm]
    De|\[^\mn{G#}]fuma com \[^\mn{A}]o \[\bmc\mn{B}]som da \[^\mn{A}]ca\[^\mn{G#}]cho|\[^\mn{B}\mn{G#}]{ei}ra \[\bm]
    \[^\mn{B}]De|\[^\mn{G#}]fuma é \[^\mn{A}]a \[\bmc\mn{B}]hora \[^\mn{A}]de \[^\mn{G#}]lim|\[\mnc{A}Am]par \[\bm]
  \mnendchorus
  \beginchorus\notesoff
    Eu sou guer|^reiro e vou cha^mar os meus ca|boclos ^
    Que vem das |matas, vem da ^terra e vem do |^mar ^
    Chamo as fa|lange de O^gum Seu Sete |Flechas ^
    chamo os fle|cheiros para ^poder ajun|^tar ^
  \endchorus
  \mnbeginverse
    \ind \[\mn{A}]Ju|\[\mncadj{1ex}{F}F]re\[\bm]ma, | \[\mn{D}]esta \[\bm]casa é \[\mn{C}]de \[\mn{B}]Ma|\[\mncii{A}{E}Am]ri\[\bm]a
    \ind | \[\mn{C}]Defu\[\bm]mar com \[\mn{G}]har\[\mn{F#}]mo|\[\mncii{F}{E}E]{ni}\[\bm]a
    \ind |\[E7] \[\mn{D}]Queirar a \[\bmc\mn{B}]todos \[\mn{C}]per\[\mn{D}]do|\[\mnc{E}Am]ar \[\bm]
    \ind \[\mn{A}]Ju|\[\mncadj{1ex}{F}F]re\[\bm]ma, | \[\mn{D}]junto \[\bm]com a San\[\mn{C}]ta \[\mn{B}]Ma|\[\mncii{A}{E}Am]ri\[\bm]a
    \ind | \[\mn{C}]Nos traz \[\bm]paz e \[\mn{G}]a\[\mn{F#}]le|\[\mncii{F}{E}E]{gri}\[\bm]a
    \ind |\[E7] \[\mn{D}]Queira a \[\bmc\mn{C}]todos \[\mn{B}]confor|\[\mnc{A}Am]tar \[\bm]
  \mnendverse
  \ifshowlilypond\translationoff\fi
  \begin{translation}
    Smudge with the herbs of Jurema, smudge with the herbs of Iemanjá
    Smudge with the sound of the waterfall; smudge, it's time to cleanse
    \nextverse
    I'm a warrior and I'm going to call my caboclos
    That come from the forests, the land and the sea
    I call the phalanx of Ogum, Your Seven Arrows, I call the fletchers to gather
    \nextverse
    Jurema, this house belongs to Maria; smudge with harmony; want everyone to forgive
    Jurema, together with Santa Maria, bring us peace and joy
    Please comfort everyone
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-10
    \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 4 {
        \mark \markup {"4x"} \bar ".|:"
        \parenthesize e8 \posectionmark "1., 2." e8( e8) | a,8 a a b c c b a | \once\slurSolid c8( a8) a4.
        \parenthesize e'8 e8( e8) | a,8 a a b c c b a | b2~ 8
        \parenthesize b8 b8( b8) | gis8 gis gis a b b a gis | \once\slurSolid b8( gis8) gis4.
        \parenthesize b8 b8( b8) | gis8 gis gis a b b a gis | a2~ 8
      }
      \slurSolid
      r8 \sectionmark "3." a'4 | a4.( f8) f2~
      | f4 d8 d d d c' b | a4.( e8) e2~
      | e4 c8 c c c g' fis | f4.( e8) e2~
      | e4 d8 d8 b8 b c d | e2~ 8
      r8 a4 | a4.( f8) f2~
      | f4 d8 d d d c' b | a4.( e8) e2~
      | e4 c8 c c c g' fis | f4.( e8) e2~
      | e4 d8 d8 c8 c b b | a2~ 8
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 De _ -- | fu -- ma com as er -- vas da Ju -- | re _ -- ma;
        \skip 1 De _ -- | fu -- ma com as er -- vas de~Ie -- man -- | já; _
        \skip 1 De _ -- | fu -- ma com o som da ca -- cho -- | ei _ -- ra;
        \skip 1 De _ -- | fu -- ma é a ho -- ra de lim -- | par. _
      }
      \set stanza = "3."
      Ju -- | re _ -- ma, | _ es -- ta ca -- sa~é de Ma -- | ri _ -- a; | _
      De -- fu -- mar com har -- mo -- | ni _ -- a; | _
      Quei -- rar~a to -- dos per -- do -- | ar; _
      Ju -- | re _ -- ma, | _ jun -- to com~a San -- ta Ma -- | ri _ -- a; | _
      Nos traz paz e a -- le -- | gri _ -- a; | _
      Quei -- ra~a to -- dos con -- for -- | tar. _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Eu sou guer -- | rei -- ro~e vou cha -- mar os meus ca -- | bo _ -- clos;
        Que vem das | ma -- tas, vem da ter -- ra~e vem do | mar; _
        Cha -- mo~as fa -- | lan -- ge de O -- gum Seu Se -- te | Fle _ -- chas;
        cha -- mo~os fle -- | chei -- ros pa -- ra po -- der a -- jun -- | tar. _
      }
    }
    theChords = \chordmode {
      \repeat volta 4 {
        s4.
        | a1:m | a:m | a:m | e
        | e | e | e | a2:m~ 8
      }
      s4.
      | f1 | f1 | a:m | a:m
      | e | e:7 | a:m
      | f1 | f1 | a:m | a:m
      | e | e:7 | a2:m~ 8
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Pena de Prata}[by={Sonia Maria Palhares}, key={Dm}, gk={Dm, Cm--F\shrp{}m}]
  \audio[key=Dm]{https://nossairmandade.com/hymn.php?hid=1377}
  \mnbeginchorus\memorize
    \[^\mn{A}]No |\[\mnc{D}Dm]al\[^\mn{F}]to \[\bmc\mn{E}]da \[^\mn{C#}]mon\[^\mn{E}]ta|-\[^\mn{D}]nha \[\bm] \altchords{\id[1]{(Em)}|Em | \e}
    \[^\mn{A}]Lá no |\[^\mn{D}]al\[^\mn{F}]to \[\bmc\mn{E}]mui\[^\mn{D}]to a\[^\mn{E}]lé|\[A]m \[\bm] \altchords{| - |B}
    Tem um |palá\[\bm]cio de \[^\mn{G}]ge|\[\mncadj{1ex}{F}Gm]{-lo} \[^\mn{E}]tão \[^\mn{D}]su\[\bmc\mn{C#}]bli\[^\mn{A}]me \altchords{| - |Am}
    \[^\mn{E}]Que vi|\[A]ra \[^\mn{G}]á\[\mnc{F}A7]gua \[^\mn{E}]tam\[^\mn{D}]bé|\[Dm]m \[\bm] \altchords{|B B7 |Em}
  \mnendchorus
  \notesoff
  \beginchorus
    A |^água ^vai pra ma|-ta ^
    Mãe Ju|rema a^bençoo|^u ^
    Uma |cabo^cla de pe|^{-na} cor de ^prata
    Que Pai |^Oxa^lá crio|^u ^
  \endchorus
  \beginchorus
    O |^Sol bri^lha na Ter|-ra ^
    E dá |luz aos ^que sofre|^u ^
    E |põe um ^Ser Divi|^{-no} em cada ^folha
    Pra cu|^rar os ^filhos Seu|^s ^
  \endchorus
  \beginchorus
    Minha |^Mãe, mi^nha Rai|-nha ^
    Quero as |almas i^lumina|^r ^
    Com es|se cris^tal tão pu|^{-ro} e verda^deiro
    Que vei|^o me a^companha|^r ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-10
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4
      \repeat volta 2 {
        a8( a) | d4 f e cis8 e8~ | e8 d8~ 2
        a8 a | d4 f8( f8) e4 d8 e8~ | e2.
        e8( e8) | e4 e e e8 g8~ | g8 f e d cis a e' e
        | e4 g f e8 d8~ | d2.
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        No __ _ | al -- to da mon -- ta -- | _ nha; _
        Lá no | al -- to __ _ mui -- to~a -- lém; | _
        Tem um | pa -- lá -- cio de ge -- | _ lo tão su -- bli -- me;
        Que vi -- | ra á -- gua tam -- bém. | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        A __ _ | á -- gua vai pra ma -- | _ ta; _
        Mãe Ju -- | re -- ma a -- ben -- ço -- ou; | _
        U -- ma | ca -- bo -- cla de pe -- | _ na cor de pra -- ta;
        Que Pai | O -- xa -- lá cri -- ou. | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        O __ _ | Sol bri -- lha na Ter -- | _ ra; _
        E dá | luz aos __ _ que so -- freu; | _
        E __ _ | põe um Ser Di -- vi -- | _ no~em ca -- da fo -- lha;
        Pra cu -- | rar os fi -- lhos Seus. | _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Mi -- nha | Mãe, mi -- nha Ra -- i -- | _ nha; _
        Que -- ro~as | al -- mas i -- lu -- mi -- nar; | _
        Com es -- | se cris -- tal tão pu -- | _ ro~e ver -- da -- dei -- ro;
        Que vei -- | o me~a -- com -- pa -- nhar. | _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4
        | d1:m | d:m | d:m | a
        | a | g:m | a2 a2:7 | d2.:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    On the heights of the mountain, there in the heights far always
    Is an ice palace so sublime that it turns into water
    \nextverse
    The water comes by the forest, mother Jurema blesses it
    A cabocla of silver feathers that Father Oxala created
    \nextverse
    The Sun shines on the Earth and gives light to those who suffer
    And puts a Divine being in every leaf to heal His children
    \nextverse
    My Mother, my Queen, I want to illuminate the souls
    With this crystal so pure and true, that comes to accompany me
  \end{translation}
\endsong


\beginsong{Coração Alado}[by={Madr. Regina Pereira}, key={Dm}, gk={Dm, Cm--E\flt{}m}, tags={valsa}]
  \audio[key=Am]{https://soundcloud.com/canaljagube/coracao-alado}
  \audio[key=Dm]{https://www.youtube.com/watch?v=S8LsAn4BGU0}
  \newchords{chords_coracaoalado_a}\newchords{chords_coracaoalado_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_coracaoalado_a]
    \[^\mn{A}]Nes|\[\mnc{D}Dm]{se dom} \[^\mn{E}]Di|\[\mnc{F}F]vino ouço |\[\mnc{E}A]o \[^\mn{D}]men\[^\mn{C#}]sa|\[\mnc{D}Dm]geiro
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_coracaoalado_b]
    \[^\mn{D}]Que é o |\[Dm]Se\[^\mn{G}]nhor \[^\mn{A}]do |\[\mnc{B&}Gm]tempo, em |mar\[^\mn{G}]cha \[^\mn{F}]se |\[\mnc{E}C]põe
    E|le \[^\mn{F}]vem \[^\mn{G}]lem|\[\mnc{A}A]brar, que o |tem\[^\mn{F}]po \[^\mn{E}]vol|\[\mnc{D}Dm]tou
    E que o |Rei\[^\mn{E}]no \[^\mn{F}]de |\[\mncii{G}{E}Gm6]Paz |\[^\mn{G}]e \[^\mn{E}]de \[^\mn{D}]A|\[\mnc{C#}A]mor com cer|\[A7]te\[^\mn{D}]za \[^\mn{E}]vi|\[\mnc{D}Dm]rá
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_coracaoalado_a]
    Con|^centre na |^força do |^seu pensa|^mento \altchords{\id[1]{Am}|Am |C |E |Am}
    \endchorus\glueverses\beginchorus\replay[chords_coracaoalado_b]
    E Res|^pire na |^força des|se beija-|^flor \altchords{|Am |Dm | - |G}
    Que |te ali|^menta e te |dá o a|^lento \altchords{| - |E | - |Am}
    Co|ração a|^lado |voa na |^força do |^seu beija-|^flor \altchords{| - |Dm6 | - |E |E7 |Am}
  \endchorus
  \beginchorus\replay[chords_coracaoalado_a]
    Co|^ração a|^lado, o se|^gredo é can|^tar
    \endchorus\glueverses\beginchorus\replay[chords_coracaoalado_b]
    Nes|^{sa vira}|^ção que |o tempo |^dá
    O |vento que |^sopra faz |alivi|^ar
    Tan|gendo a tris|^teza |e toda |^dor pra |^outro lu|^gar
  \endchorus
  \beginchorus\replay[chords_coracaoalado_a]
    |^Neste oce|^ano va|^mos nave|^gar
    \endchorus\glueverses\beginchorus\replay[chords_coracaoalado_b]
    Es|^tar no bar|^quinho, a fir|meza é can|^tar
    Com |os meus ir|^mãos, pres|tando aten|^ção
    |Nessa jor|^nada do |Rei Salo|^mão e do |^meu São Jo|^ão
  \endchorus
  \beginchorus\replay[chords_coracaoalado_a]
    Meu |^Pai eu lhe |^peço, me |^dê a ben|^ção
    \endchorus\glueverses\beginchorus\replay[chords_coracaoalado_b]
    Pa|^{ra eu} se|^guir nessa |apura|^ção
    A|legre con|^tente com |os meus ir|^mãos
    |Nessa mis|^são |da Virgem |^Mãe e de |^Jurami|^dam
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-11
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \key d \minor \time 3/4 \partial 4
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        \parenthesize a4 \posectionmark "A" | d d e | f f f8( f) | e4 d cis | d( d)
      }
      \repeat volta 2 {
        \altcol\grace d4 d4 \posectionmark "B" | d g a | bes( bes) bes | bes g f | e2
        e4 | e f g | a( a) a | a f e | d4( d4)(
        d4) | d e f | g4( g4)( e4) | g e d | cis4( cis4)
        cis4 | cis d e | d2
      }
    }
    theLyricsOne = \lyricmode { \set includeGraceNotes = ##f
      \set stanza = "1."
      \repeat volta 2 {
        Nes -- | se dom Di -- | vi -- no ou -- ço | o men -- sa -- | gei -- ro.
      }
      \repeat volta 2 {
        Que~é~o | Se -- nhor do | tem -- po, em | mar -- cha se | põe;
        E -- | le vem lem -- | brar, que o | tem -- po vol -- | tou;
        E que~o | Rei -- no de | Paz __ _ _ | e de A -- | mor com cer -- | te -- za vi -- | rá.
      }
    }
    theLyricsTwo = \lyricmode { \set includeGraceNotes = ##t
      \set stanza = "2."
      \repeat volta 2 {
        Con -- | cen -- tre na | for -- ça do __ _ | seu pen -- sa -- | men -- to.
      }
      \repeat volta 2 {
        \altcol E Res -- | pi -- re na | for -- ça des -- | se bei -- ja -- | flor;
        Que | te a -- li -- | men -- ta~e te | dá o a -- | len -- to;
        Co -- | ra -- ção a -- | la -- _ do | vo -- a na | for -- ça do | seu bei -- ja -- | flor.
      }
    }
    theLyricsThree = \lyricmode { \set includeGraceNotes = ##f
      \set stanza = "3."
      \repeat volta 2 {
        Co -- | ra -- ção a -- | la -- do,~o se -- _ | gre -- do~é can -- | tar. __ _
      }
      \repeat volta 2 {
        Nes -- | sa vi -- ra -- | ção __ _ que | o tem -- po | dá;
        O | ven -- to que | so -- pra faz | a -- li -- vi -- | ar; __ _
        Tan -- | gen -- do~a tris -- | te -- _ za | e to -- da | dor __ _ pra | ou -- tro lu -- | gar.
      }
    }
    theLyricsFour = \lyricmode { \set includeGraceNotes = ##f
      \set stanza = "4."
      \repeat volta 2 {
        \skip 1 | Nes -- te~o -- ce -- | a -- no va -- _ | mos na -- ve -- | gar. __ _
      }
      \repeat volta 2 {
        Es -- | tar no bar -- | qui -- nho,~a fir -- | me -- za~é can -- | tar;
        Com | os meus ir -- | mãos, __ _ pres -- | tan -- do~a -- ten -- | ção; __ _ _
        | Nes -- sa jor -- | na -- da do | Rei Sa -- lo -- | mão e do | meu São Jo -- | ão.
      }
    }
    theLyricsFive = \lyricmode { \set includeGraceNotes = ##f
      \set stanza = "5."
      \repeat volta 2 {
        Meu | Pai eu lhe | pe -- ço, me __ _ | dê a ben -- | ção. __ _
      }
      \repeat volta 2 {
        Pa -- | ra eu se -- | guir nes -- sa | a -- pu -- ra -- | ção;
        A -- | le -- gre con -- | ten -- te com | os meus ir -- | mãos; __ _ _
        | Nes -- sa mis -- | são __ _ _ | da Vir -- gem | Mãe e de | Ju -- ra -- mi -- | dam.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d2.:m | f | a | d2:m
      }
      \repeat volta 2 { % must have the invisible grace note here
        \grace s4 s4 | d2.:m | g:m | g:m | c
        | c | a | a | d:m
        | d:m| g:m | g:m | a
        | a:7 | d2:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    In this divine gift, I hear the messenger
    Who is the Lord of time, setting out on a journey
    He comes to remind us that time has returned
    And that the Kingdom of Peace and Love will surely come
    \nextverse
    Focus on the power of your thoughts
    And breathe in the strength of that hummingbird
    That nourishes you and gives you courage
    A winged heart soars in the strength of your hummingbird
    \nextverse
    Winged heart, the secret is to sing
    In this breeze that time provides
    The wind that blows brings relief
    Chasing away sadness and all pain to another place
    \nextverse
    In this ocean, we will sail
    Being on the little boat, the firmness is in singing
    With my brothers, paying attention
    On this journey of King Solomon and my Saint John
    \nextverse
    My Father, I ask for your blessing
    So I can continue in this investigation
    Joyful and content with my brothers
    In this mission of the Virgin Mother and Juramidam
  \end{translation}



\endsong


