% Santo Daime: Hinos do Encerramento
% ==================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Meu Deus, Meu São João}[by={Padr. Alfredo},key={C},gk={C, B\flt{}--D},tags={valsa}]
  \audio{https://www.nossairmandade.com/hymn/612/MeuDeus,MeuS\%C3\%A3oJo\%C3\%A3o}
  \newchords{chords_meudeusmeusaojoao_a}\newchords{chords_meudeusmeusaojoao_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_meudeusmeusaojoao_a]
    \[^\mn{E}]Meu |\[\mncii{D}{A}Dm]Deus |\[\mnc{C}Fmaj7]{meu São} \[^\mn{E}]Jo|\[\mnc{C}C]ão | \e \altchords{\id[1]{(D)}|Em |Gmaj7 |D | \e}
    \[^\mn{E}]Den|\[^\mn{G}]tro desta |Vos\[^\mn{F#}]sa \[^\mn{A}]mis|\[\mnc{E}Am]são | \e \altchords{| | |Bm | \e}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_meudeusmeusaojoao_b]
    \[^\mn{E}]Se |\[\mnc{G}C]passa |mui\[^\mn{F#}]ta a\[^\mn{G}]mar|\[\mnc{A}Am]gu\[^\mn{E}]ra \altchords{|D | |Bm }
    \[^\mn{C}]E |\[\mnc{D}Dm]mui\[^\mn{A}]ta |\[\mnc{C}Fmaj7]ingra\[^\mn{E}]ti|\[\mnc{C}C]dão | \e \altchords{|Em |Gmaj7 |D | \e}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_meudeusmeusaojoao_a]
    Só |^se se|^{gue nesta} |^li|nha
    Dei|xando |a ilu|^são | \e
    \endchorus\glueverses\beginchorus\replay[chords_meudeusmeusaojoao_b]
    Sa|^indo da |i-g-no|^rância
    E |^tendo |^educa|^ção | \e
  \endchorus
  \beginchorus\replay[chords_meudeusmeusaojoao_a]
    Pe|^di fir|^meza a meu |^Mes|tre
    E |a Vos|sa reden|^ção | \e
    \endchorus\glueverses\beginchorus\replay[chords_meudeusmeusaojoao_b]
    Perdo|^ai es|tes sofre|^dores
    Que |^zombam |^neste sa|^lão | \e
  \endchorus
  \beginchorus\replay[chords_meudeusmeusaojoao_a]
    Escla|^reço |^estes en|^si|nos
    Da |Virgem |da Concei|^ção | \e
    \endchorus\glueverses\beginchorus\replay[chords_meudeusmeusaojoao_b]
    Pe|^dindo o |Vosso con|^forto
    E a |^Vossa san|^{ta prote}|^ção | \e
  \endchorus
  \brk
  \beginchorus\replay[chords_meudeusmeusaojoao_a]
    Que |^brilho |^{tem este} |^di|a
    |Dentro da |nossa ses|^são | \e
    \endchorus\glueverses\beginchorus\replay[chords_meudeusmeusaojoao_b]
    Fes|^tejos |do nosso |^Pai
    Lou|^vores |^{à São Jo}|^ão | \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 2
      \repeat volta 2 {
        \altcol\parenthesize c4\altmark "4." \posectionmark "A" e4 | d2( a4) | c c e | c2.( | c2) \parenthesize e4
        | g4( g) g | g fis a | e2.~ | e4(
      } \break
      \repeat volta 2 {
        \altcol\parenthesize e4)\altmark "3." \sectionmark "B" e4 | g( g) g | g fis g | a( e) c
        | d( d) a | c c e | c2.~ | c4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        \skip 1 Meu | Deus __ _ | meu São Jo -- | ão; __ | _
        Den -- | tro des -- ta | Vos -- sa mis -- | são. __ | _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        \skip 1 Se | pas -- _ sa | mui -- ta~a -- mar -- | gu -- ra;
        E | mui -- _ ta | in -- gra -- ti -- | dão. __ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        \skip 1 Só | se se -- | gue nes -- ta | li -- | nha;
        Dei -- | xan -- _ do | a i -- lu -- | são. __ | _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 Sa -- | in -- do da | i -- g -- no -- | rân -- cia;
        E | ten -- _ do | e -- du -- ca -- | ção. __ | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        \skip 1 Pe -- | di fir -- | me -- za~a meu | Mes -- | tre;
        E | a __ _ Vos -- | sa re -- den -- | ção. __ | _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \altcol Per -- do -- | ai __ _ es -- | tes so -- fre -- | do -- res;
        Que | zom -- _ bam | nes -- te sa -- | lão. __ | _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        \altcol Es -- cla -- | re -- ço | es -- tes en -- | si -- | nos;
        Da | Vir -- _ gem | da Con -- cei -- | ção. __ | _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        \skip 1 Pe -- | din -- do o | Vos -- so con -- | for -- to;~E
        a | Vos -- sa san -- | ta pro -- te -- | ção. __ | _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        \skip 1 Que | bri -- lho | tem es -- te | di -- | a;
        \skip 1 | Den -- tro da | nos -- sa ses -- | são. __ | _
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        \skip 1 Fes -- | te -- _ jos | do nos -- so | Pai; __ _
        Lou -- | vo -- _ res | à São Jo -- | ão. __ | _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | d2.:m | f:maj7 | c | c
        | c | c | a:m | a4:m
      }
      \repeat volta 2 {
        s2 | c2. | c | a:m | d:m | f:maj7 | c | c4
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    My God, my Saint John, within this your mission
    One experiences much bitterness and much ingratitude
    \nextverse
    One can only follow in this line by dropping the illusion
    By dropping the ignorance and becoming respectful
    \nextverse
    I asked firmness of my Master and Your redemption
    Forgive these suffering beings who mock this \emph{salão}
    \nextverse
    I clarify these teachings of the Virgin of Conception
    Asking Your comfort and your holy protection
    \nextverse
    What brilliance this day has within our session
    Celebrations of our Father, praises to Saint John
  \end{translation}
\endsong


\beginsong{Meu Rei Salomão}[by={Madr. Cristina},key={G},gk={G, (F\shrp{})--(G)},tags={2x}]
  \audio{https://www.nossairmandade.com/hymn/1204/MeuReiSalom\%C3\%A3o}
  \mnbeginchorus\memorize
    |\[\mnc{D}G]Eu como \[\bmc\mnc{E}Cmaj7]fi\[^\mn{D}]lha \[^\mn{B}]de |\[\mnc{G}G]Vós \[\bm]
    |\[^\mn{G}]Dentro \[\bmc\mn{B}]des\[^\mn{G}]te \[^\mn{F#}]sa|\[\mnc{E}C]lão \[\bm]
    Eu |\[\mnc{A}Am]quero \[\bmc\mn{C}]se\[^\mn{A}]guir \[^\mn{F#}]com |\[\mncii{G}{D}G]Vós \[\bm]
    De |\[\mnc{E}C]todo \[\bmc\mnc{F#}D7]meu \[^\mn{E}]co\[^\mn{D}]ra|\[\mnc{G}G]ção \[\bm]
  \mnendchorus
  \notesoff
  \beginchorus
    |^Eu peço ^{a minha} |^Mãe ^
    |Dentro do ^meu cora|^ção ^
    Para |^sempre ^eu ser fe|^liz ^
    |^Com meu Se^nhor São Jo|^ão ^
  \endchorus
  \beginchorus
    \noteson\[\mnlow{B}]Cu\notesoff|^rando ^{e ensi}|^nan^do
    |Com to^da perfei|^ção ^
    Se|^guindo ^neste ca|^mi^nho
    |^Com o meu ^Rei Salo|^mão ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 4
      \repeat volta 2 {
        \altcol\parenthesize b4\altmark "3." \pomark | d4( d8) d8 e4 d8 b | g2( g2) g'4( g8) g8 b4 g8 fis8 | e2. e8( e8)
        | a4. a8 c4 a8 fis8 | g2( d4)( d4) | e4( e8) e8 fis4 e8 d8 | g2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 | Eu co -- mo fi -- lha de | Vós; __ _
        | Den -- _ tro des -- te sa -- | lão;
        Eu __ _ | que -- ro se -- guir com | Vós; __ _
        De  | to -- _ do meu co -- ra -- | ção.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        \skip 1 | Eu pe -- ço a mi -- nha | Mãe; __ _
        | Den -- tro do meu co -- ra -- | ção;
        Pa -- ra | sem -- pre eu ser fe -- | liz; __ _ _
        | Com meu Se -- nhor São Jo -- | ão.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Cu -- | ran -- _ do e en -- si -- | nan -- do;
        | Com __ _ to -- da per -- fei -- | ção;
        Se -- _ | guin -- do nes -- te ca -- | mi -- nho; __ _
        | Com o meu Rei Sa -- lo -- | mão.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | g2 c2:maj7 | g1 | g1 | c
        | a:m | g | c2 d:7 | g2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I, as a daughter of Yours, inside of this \emph{salão}
    I want to follow with You, with all my heart
    \nextverse
    I beg my Mother inside of my heart
    That I may always be happy with my Lord Saint John
    \nextverse
    Healing and teaching with all perfection
    Following in this path with my King Solomon
  \end{translation}
\endsong


\beginsong{Sou Brilho do Sol}[by={Padr. Sebastião}, key={C}, gk={D, C--F\shrp{}m}]
  \audio{https://www.nossairmandade.com/hymn/99/BrilhoDoSol}
  \transpose{-2}
  \mnbeginchorus\memorize
    \lrep \[^\mn{A}]Eu |\[\mnc{D}D]sou \[^\mn{F#}]bri\[^\mn{E}]lho \[^\mn{D}]do \[\bm]sol, |sou \[^\mn{F#}]bri\[^\mn{E}]lho \[^\mn{D}]da \[\mnc{F#}Bm/F#]lua \rrep
    \lrep \[^\mn{F#}]Dou |\[\mnc{G}G]bri\[^\mn{F#}]lho \[^\mn{E}]as \[^\mn{D}]es\[\mnc{F#}D]trelas, \[^\mn{D}]por\[^\mn{F#}]que |\[\mnc{E}A7]todas \[^\mn{B}]me\jw a\[^\mn{C#}]com\[\mnc{D}D]panham \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep Eu |^sou brilho do ^mar |eu vivo no ^vento \rrep
    \lrep Eu |^brilho na flo^resta porque |^ela me per^tence \rrep
  \endchorus
  \textnotefornext{suomeksi:}
  \beginchorus
    \lrep Olen |^paiste aurin^gon, |sekä loiste ^kuun \rrep \altchords{\id[1]{(D)}|D | - Bm/F\shrp{}}
    \lrep Va|^laisen tähdis^tön, koska se |^on mun seura^nain \rrep \altchords{|G D |A7 D}
  \endchorus
  \beginchorus
    \lrep Olen |^välke meren^pinnan, hen|gitän tuules^sa \rrep
    \lrep Loistan |^metsän sydä^messä, sillä se |^kuuluu minul^le \rrep
  \endchorus
  \textnotefornext{in English:}
  \beginchorus
    \lrep I |^am the shine of ^sun, I |am the shine of ^moon \rrep
    \lrep I |^give shine to the ^stars, because they |^all accompany ^me \rrep
  \endchorus
  \beginchorus
    \lrep I |^am the shine of ^sea, |I live in the ^wind \rrep
    \lrep I |^shine in the ^forest, because |^she belongs to ^me \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-07
    % \header {
    %   title = "Sou Brilho do Sol"
    %   composer = "Padr. Sebastião"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \transpose d c \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 8
      \repeat segno 2 {
        \sectionLabel "A"
        \repeat volta 2 {
          a8\pomark | d8 fis e d d2 | d8 fis8 e d fis4 fis8
        } \break
        \sectionLabel "B"
        \repeat volta 2 {
          fis8 | g8. fis16 e8 d fis8. fis16 d8 fis | e8. e16 b8 cis d4 d8
        }
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \repeat segno 2 {
        \repeat volta 2 {
          \set stanza = "1.A"
          Eu | sou bri -- lho do sol,
          | sou bri -- lho da lu -- a.
        }
        \repeat volta 2 {
          \set stanza = "1.B"
          Dou | bri -- lho as es -- tre -- las,
          por -- que | to -- das me~a -- com -- pa -- nham.
        }
      }
    }
    theLyricsTwo = \lyricmode {
      \repeat segno 2 {
        \repeat volta 2 {
          \set stanza = "2.A"
          Eu | sou bri -- lho do mar,
          | eu vi -- vo no ven -- to.
        }
        \repeat volta 2 {
          \set stanza = "2.B"
          Eu | bri -- lho na flo -- res -- ta
          Por -- que | e -- la me per -- ten -- ce.
        }
      }
    }
    theChords = \transpose d c \chordmode {
      \repeat segno 2 {
        \repeat volta 2 {
          s8 | d1 | d2 b4.:m/fis
        }
        \repeat volta 2 {
          s8 | g2 d | a:7 d4.
        }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifchorded%
    \vfill
    \beginverse \noteson % first line of the next hino (in key D, but will be transposed)
      \hfill\tonextsongmark \hfill \[\mn{D}]Eu |\[D]vivo \[\mn{F#}]na \[\mn{A}]flo\[\mnc{D}Bm]res\[\mn{F#}]ta, a\[\mn{B}]pren|\[\mnc{A}A]dendo a \[\mn{E}]me \[\mn{F#}]cu\[\mnc{D}D]rar \ldots
    \endverse
  \fi
\endsong


\beginsong{Eu Vivo na Floresta}[by={Madr. Rita},key={C},gk={C, G--B--(C)}]
  \audio{https://www.nossairmandade.com/hymn/664/EuVivoNaFloresta}
  \newchords{chords_euvivonafloresta_a}\newchords{chords_euvivonafloresta_b}
  \mnbeginchorus\memorize[chords_euvivonafloresta_a]
    \[^\mn{C}]Eu |\[C]vivo \[^\mn{E}]na \[^\mn{G}]flo\[\mnc{C}Am]res\[^\mn{E}]ta, a\[^\mn{A}]pren|\[\mnc{G}G]dendo a \[^\mn{D}]me \[^\mn{E}]cu\[\mnc{C}C]rar
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_euvivonafloresta_b]
    \[^\mn{C}]Eu con|\[\mnc{E}Am]vido os \[^\mn{D}]meus \[^\mn{C}]ir\[\mnc{E}C]mãos, \[^\mn{C}]va\[^\mn{E}]mos |\[\mnc{G}G]todos \[^\mn{D}]se \[^\mn{E}]cui\[\mnc{C}C]dar
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_euvivonafloresta_a]
    Estou |^dentro da ba^talha, sofren|^do mas sou fe^liz
  \endchorus\glueverses\beginchorus\replay[chords_euvivonafloresta_b]
    Nela |^estou apren^dendo, o que eu a|^inda não sa^bia
  \endchorus
  \beginchorus\replay[chords_euvivonafloresta_a]
    Eu |^não vou enga^nar, eu |^vim e vou di^zer
  \endchorus\glueverses\beginchorus\replay[chords_euvivonafloresta_b]
    Quem qui|^ser passar nas ^provas, é come|^çar do AB^C
  \endchorus
  \beginchorus\replay[chords_euvivonafloresta_a]
    Exami|^nar a consci^ência, é a |^primeira li^ção
  \endchorus\glueverses\beginchorus\replay[chords_euvivonafloresta_b]
    Ter fir|^meza e ter a^mor, e a|^mar os seus ir^mãos
  \endchorus
  \beginchorus\replay[chords_euvivonafloresta_a]
    Isto eu |^digo é porque ^sei, pois es|^tou exami^nando
  \endchorus\glueverses\beginchorus\replay[chords_euvivonafloresta_b]
    É o |^tempo do a^puro, do meu |^Senhor São Jo^ão
  \endchorus
  \beginchorus\replay[chords_euvivonafloresta_a]
    Já foi |^dito e lem^brado, todos |^prestem aten^ção
  \endchorus\glueverses\beginchorus\replay[chords_euvivonafloresta_b]
    O co|^meço da his^tória, vem do |^rio de Jor^dão
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        r8\posectionmark "A" c8 | c8 c e g c4 e,8 a8 | g8 g d e c4
      } \break
      \repeat volta 2 {
        c8\sectionmark "B" c8 | e8 e d c e4 c8 e8 | g8 g d e c4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Eu | vi -- vo na flo -- res -- ta~a --
      pren -- | den -- do~a me cu -- rar.
      \set stanza = "1.B"
      Eu con -- | vi -- do~os meus ir -- mãos
      va -- mos | to -- dos se cui -- dar.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 a:m | g c4
      }
      \repeat volta 2 {
        s4 | a2:m c | g c4
      }
    }
    \include "tex/lp-include-tail-lyricsbetween.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I live in the forest, learning to heal myself
    I invite my brothers and sisters, let's take care of ourselves
    \nextverse
    I am within this battle, suffering but I'm happy
    In it I am learning, what I did not yet know
    \nextverse
    I'm not going to deceive, I came and I'm going to say
    Whoever wants to pass the tests, should start with A.B.C.
    \nextverse
    Examine the conscience, is the first lesson
    To be firm and to have love, and to love your brothers and sisters
    \nextverse
    This I say because I know, as I am examining
    It's the time of purification, of my lord Saint John
    \nextverse
    It was already said and remembered, everybody pay attention
    The beginning of the story, comes from the River of Jordan
  \end{translation}
\endsong
