% Santo Daime: Oração
% ===================
%
\audio[title={Nossa Irmandade}]{https://www.nossairmandade.com/hinario/1/Ora\%C3\%A7\%C3\%A3o}
\audio[title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Examine a Consciência}[by={Padr. Sebastião}, key={C}, gk={D, C--E}]
  \audio[]{https://www.nossairmandade.com/hymn/1/ExamineAConsci\%C3\%AAncia}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=18s}
  \mnbeginchorus\memorize
    \[^\mn{G}]E\[^\mn{C}]xa|\[\mnc{E}C]mine a \[\bmc\mn{D}]con\[^\mn{C}]sci|\[\mnc{G}G]ência \altchords{\id[1]{(D)}|D |A}
    \[\bm]E\[^\mn{C}]xa|\[\mnc{E}Am]mine \[\bmc\mn{D}]di\[^\mn{C}]rei|\[\mnc{G}G]ti\[\bm]nho \altchords{|Bm |A}
    \[^\mn{C}]Sou |\[\mnc{E}C]Pai e \[\bmc\mn{D}]não \[^\mn{C}]sou |\[\mnc{G}G]filho \altchords{|D |A}
    \[\bm]Mas \[^\mn{C}]eu |\[\mnc{E}Am]não fa\[\mnc{D}G]ço \[^\mn{E}]as|\[\mnc{C}C]sim\[\bm] \altchords{|Bm A |D}
  \mnendchorus
  \notesoff
  \beginchorus
    Cha|^mo de ^um a |^um
    A ^todos |^eu mos^tro o ca|^mi^nho
    Fa|^zendo ^como eu |^mando
    ^Tudo |^fica ^bem fa|^ci^nho
  \endchorus
  \beginchorus
    Todos |^podem ^se lem|^brar^ \altchords{\id[4]{MK (C)} |C G7 |C}
    Do |^tempo ^de No|^é ^ \altchords{|Am Dm7 |G}
    \noteson \[\mnlow{G}]A \[\mnlow{C}]dou\notesoff|^trina ^do meu |^Pai \altchords{|C G7 |C}
    ^Eu en|^sino ^como |^é ^ \altchords{|Am G7 |C}
  \endchorus
  \beginchorus
    |^Vamos ^meus ir|^mãos
    ^Vamos |^todos se ^humi|^lhar^
    Pe|^dir nos^so per|^dão
    Para ^nosso |^Pai nos ^perdo|^ar ^
  \endchorus
  \beginchorus
    Quem qui|^ser que se ^agu|^ente \altchords{\id[6]{simple (C)} |C G |C}
    ^Não tem |^{a quem} ^se quei|^xar^ \altchords{| - G |C}
    Eu |^bem que ^avi|^sei \altchords{| - G |C}
    ^Que ha|^via ^de che|^gar^ \altchords{| - G |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2023-01
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8( \pomark << \parenthesize g) c >> | e4 e8( e8) d4 c4 | g4.( g8)( g4) c
        | e4 e8( e8) d4 c | g'2( g4) \once\slurUp << \parenthesize g,8( c >> c8)
        | e4. e8 d4 c | g4( g8)( g8) g4 c
        | e4 e d e | c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        E -- xa -- | mi -- ne a con -- ci -- | ên -- cia;
        E -- xa -- | mi -- ne __ _ di -- rei -- | ti -- nho;
        Sou __ _ | Pai e não sou | fil -- _ ho;
        Mas eu | não fa -- ço as -- | sim. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Cha -- _ | mo de __ _ um a | um;
        A to -- dos | eu mos -- _ tro~o ca | mi -- nho;
        Fa -- _ | zen -- do co -- mo~eu | man -- _ do;
        Tu -- do | fi -- ca bem fa -- | ci -- nho.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        To -- dos | po -- dem __ _ se lem -- | brar; __ _ _
        Do | tem -- po __ _ de No -- | é; __ _
        (A) dou -- | tri -- na do meu | Pai; __ _ _
        Eu en -- | si -- no co -- mo | é. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        \skip 1 \skip 1 | Va -- mos __ _ meus ir -- | mãos; __ _
        Va -- mos | to -- dos se hu -- mi -- | lhar; __ _
        Pe -- _ | dir nos -- so per -- | dão;
        Pa -- ra nos -- so | Pai nos per -- do -- | ar. __ _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \repeat volta 2 {
        Quem qui -- | ser que se a -- gu -- | en -- te;
        Não tem | a quem __ _ se quei -- | xar; __ _
        Eu __ _ | bem que a -- vi -- | sei; __ _ _
        Que ha -- | vi -- a de che -- | gar. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | g
        | a:m | g
        | c | g
        | a2:m g | c2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Examine your conscience; Examine it thoroughly
    I‘m the Father, not the son; But I don‘t act that way
    \nextverse
    I call one by one; To all I show the path
    Doing as I order; Everything becomes really easy
    \nextverse
    All can remember; The time of Noah
    The doctrine of my Father; I teach it like it is
    \nextverse
    Let‘s go my brothers and sisters; Let‘s all humble ourselves
    Ask our forgiveness; For our Father to forgive us
    \nextverse
    Those who want it, should endure; They have no one to complain to
    I really warned; That I would come
  \end{translation}
\endsong


\beginsong{A meu Pai Peço Firmeza}[by={Padr. Sebastião}, tags={á capela, perfilado}, key={C}, gk={D, C--E}]
  \audio[]{https://www.nossairmandade.com/hymn/2/AMeuPaiPe\%C3\%A7oFirmeza}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=180s}
  \beginchorus
    \[\mnlow{G}]A meu |\[\mnlow{C}]Pai pe\[\bm]ço \[\mnlow{E}]fir|\[\mnlow{G}]m\[\bm]e\[\mnlow{C}]za
    E não |\[\mnlow{E}]saia \[\mnlow{C}]da \[\bmc\mnlow{A}\mnlow{G}]min\[\mnlow{C}]ha |men\[\bm]te
  \endchorus\glueverses\beginchorus
    \[\mnlow{C}]Dou en|\[\mnlow{E}]sino \[\mnlow{C}]a \[\bmc\mnlow{A}]quem \[\mnlow{G}]não |s\[\bm]abe
    \[\mnlow{C}]E a\[\mnlow{D}]con|selho \[\mnlow{C}]os \[\bmc\mnlow{A}]i\[\mnlow{C}]no|cen\[\bm]tes
  \endchorus
  \notesoff\chordsoff\measureson
  \beginchorus
    Meu |Pai a \[\bm]ti eu |p\[\bm]eço
    E não |saio do \[\bm]meu lu|gar\[\bm]
  \endchorus\glueverses\beginchorus
    Dai-me |força e \[\bm]dai-me a|mor\[\bm]
    Para eu |poder \[\bm]traba|lhar\[\bm]
  \endchorus
  \beginchorus
    Meu |Pai a \[\bm]ti eu |p\[\bm]eço
    E |aos teus \[\bm]pés es|tou\[\bm]
  \endchorus\glueverses\beginchorus
    Ro|gando \[\bm]pelo |p\[\bm]ovo
    Para |ser me\[\bm]rece|dor\[\bm]
  \endchorus
  \beginchorus
    Oh! |Minha \[\bm]Virgem |Mãe\[\bm]
    Oh! |Virgem \[\bm]prote|to\[\bm]ra
  \endchorus\glueverses\beginchorus
    És |Rai\[\bm]nha do |mar\[\bm]
    És |minha \[\bm]profes|so\[\bm]ra
  \endchorus
  \beginchorus
    Oh! |Meu ben\[\bm]dito |Pai\[\bm]
    Oh! |Meu Ju\[\bm]rami|dam\[\bm]
  \endchorus\glueverses\beginchorus
    Cha|ma de \[\bm]um a |um\[\bm]
    Para re|ceber \[\bm]o per|dão\[\bm]
  \endchorus
  \beginchorus
    Se |todos \[\bm]conhe|ces\[\bm]sem
    O po|der que \[\bm]meu Pai |tem\[\bm]
  \endchorus\glueverses\beginchorus
    Dei|xavam a \[\bm]ilu|são\[\bm]
    Que é |coisa que \[\bm]não con|vém\[\bm]
  \endchorus
  \brk
  \beginchorus
    O |mundo está \[\bm]em ba|la\[\bm]nço
    E |tudo vai \[\bm]balan|çar\[\bm]
   \endchorus\glueverses\beginchorus
    Mas |nos pés \[\bm]do meu |Pai\[\bm]
    Todos |têm que \[\bm]se cur|var\[\bm]
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8( \posectionmark "A" g) | c8( c8 c8) c8 c4. e8 | g2~ g8 \parenthesize c,8 c8( c8)
        | e4( e8) c8 \once\slurSolid a8( g4) c8 | c2( c4)
      } \break
      \repeat volta 2 {
        c8( \sectionmark "B" c8) | e4( e8) c8 a4. g8 | g2~ g8 \parenthesize c8 c8 d8
        | d4( d8) c8 a4. c8 | c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        A meu | Pai __ _ _ pe -- ço fir -- | me -- _ za;
        E não | sai -- a da mi -- _ nha | men -- te.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Dou en -- | si -- no a quem não | sa -- _ be;~E
        a -- con -- | se -- _ lho~os i -- no -- | cen -- tes.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Meu __ _ | Pai __ _ _ a ti eu | pe -- _ ço;
        E não | sai -- o do meu __ _ lu -- | gar. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Dai- -- me | for -- ça e dai- me~a -- | mor; __ _
        Pa -- ra eu | po -- _ der tra -- ba -- | lhar. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Meu __ _ | Pai __ _ _ a ti eu | pe -- _ ço;
        E __ _ | aos __ _ teus pés __ _ es -- | tou. __ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Ro -- _ | gan -- _ do pe -- lo | po -- _ vo;
        Pa -- ra | ser __ _ me -- re -- ce -- | dor. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Oh! __ _ | Mi -- _ _ nha Vir -- gem | Mãe; __ _
        \skip 1 Oh! __ _ | Vir -- _ gem pro -- _ te -- | to -- ra.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        És __ _ | Ra -- _ i -- nha do | mar; __ _
        \skip 1 És __ _ | mi -- _ nha pro -- fes -- | so -- ra.
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        Oh! __ _ | Meu __ _ _ ben -- di -- to | Pai; __ _
        \skip 1 Oh! __ _ | Meu __ _ Ju -- ra -- _ mi -- | dam. __ _
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Cha -- _ | ma __ _ de um a | um; __ _
        Pa -- ra re -- | ce -- _ ber o per -- | dão. __ _
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \repeat volta 2 {
        Se __ _ | to -- _ _ dos co -- nhe -- | ces -- _ sem;
        O po -- | der __ _ que meu __ _ Pai | tem. __ _
      }
      \set stanza = "6.B"
      \repeat volta 2 {
        Dei -- _ | xa -- vam a i -- lu -- | são; __ _
        \skip 1 Que é | coi -- sa que não con -- | vém. __ _
      }
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7.A"
      \repeat volta 2 {
        O __ _ | mun -- do es -- tá em ba -- | lan -- _ ço;
        E __ _ | tu -- do vai ba -- _ lan -- | çar. __ _
      }
      \set stanza = "7.B"
      \repeat volta 2 {
        Mas __ _ | nos __ _ pés do meu | Pai; __ _
        \skip 1 To -- dos | têm __ _ que se cur -- | var. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | c1 | c2 f2 | c2.
      }
      \repeat volta 2 {
        s4 | c2 a2:m | g1 | d2:m f2 | c2.
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    From my Father I ask for firmness, and He never leaves my mind
    I teach those who don‘t know, and I advise the innocents
    \nextverse
    My Father, I ask You, and I don't leave my place
    Give me strength and give me love, so that I can work
    \nextverse
    My Father, I ask You, and I am at Your feet
    Praying for the people, for them to be deserving
    \nextverse
    Oh! my Virgin Mother, oh! Virgin Protectress
    You are Queen of the sea, You are my Professor
    \nextverse
    Oh! my Father, oh! my Juramidam
    He calls one by one, to receive forgiveness
    \nextverse
    If all knew the power that my Father has
    They would drop illusion, which is something not worthwhile
    \nextverse
    The world is being shaken, and everything is going to shake
    But at the feet of my Father everyone must bow
  \end{translation}
\endsong


\beginsong{Eu Vivo com meu Mestre}[by={Padr. Sebastião}, key={C}, gk={D, C--F\shrp{}}]
  \audio[]{https://www.nossairmandade.com/hymn/3/EuVivoComMeuMestre}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=454s}
  % Note: This hino might be sometimes sung two times?
  \newchords{chords_euvivocom_a}\newchords{chords_euvivocom_b}
  \mnbeginchorus\memorize[chords_euvivocom_a]
    \[^\mn{G}]Eu |\[\mnc{C}C]vivo \[\mnc{A}Am]com \[^\mn{C}]meu |\[\mnc{G}G]Mes\[\bm]tre \altchords{\id[1]{(D)} |D Bm |A}
    \[^\mn{C}]Eu |\[\mnc{E}Am]vi\[^\mn{C}]vo com \[\mnc{A}F]meus \[^\mn{C}]ir|\[C]mãos\[\bm] \altchords{|Bm G |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_euvivocom_b]
    \[^\mn{C}]Eu |\[\mnc{F}F]vivo \[^\mn{E}]na \[\mnc{D}G]san\[^\mn{E}]ta |\[\mnc{C}C]luz \altchords{|G A |D}
    Estou \[^\mn{B}]no \[\mnc{A}(F)]pé \[^\mn{B}]da |\[\mnc{G}G]cruz com Ju\[\mnc{C}(Am)]ra\[^\mn{E}]mi|\[\mnc{C}C]dam\[\bm] \altchords{ (G) |A (Bm) |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_euvivocom_a]
    |^Eu pe^{ço a} meu |^Pai
    ^O que eu pe|^dir E^le me |^dá^
  \endchorus\glueverses\beginchorus\replay[chords_euvivocom_b]
    Os ini|^migos que vi^erem |^contra
    Eu ^peço |^força para ^derri|^bar^
  \endchorus
  \beginchorus\replay[chords_euvivocom_a]
    Oh! |^Minha ^Virgem |^Mãe^ \altchords{\id[4]{MK (C)}|C Am |C}
    Oh! |^Virgem da ^Concei|^ção^ \altchords{|Am F |C}
  \endchorus\glueverses\beginchorus\replay[chords_euvivocom_b]
    Eu |^peço a ^Jesus |^Cristo \altchords{|F G |Am}
    Pa^ra dar |^força aqui ^{na ses}|^são^ \altchords{F |G Am |C}
  \endchorus
  \brk
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        r8 \posectionmark "A" \parenthesize g4 | c4 c4 a4 c4 | g2( \altcol\grace c8 \altmark "2." g4) \altcol\grace c8 c8( c8) | e4 c8( c8) a4 c4 | c2~8
      } \break
      \repeat volta 2 {
        \parenthesize c8 \sectionmark "B" c8( c8) | f8( f8) f8 e8 d4 e4 | c8( c8) c8 b8 a4 b4 | g8( g8) g8 g8 c4 e4 | c2~8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Eu | vi -- vo com meu | Mes -- tre;
      Eu __ _ | vi -- vo com meus ir -- | mãos. __ _
      \set stanza = "1.B"
      \skip 1 Eu __ _ | vi -- _ vo na san -- ta | luz;
      Es -- tou no pé da | cruz __ _ com Ju -- ra -- mi -- | dam. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \skip 1 | Eu pe -- ço~a meu | Pai;
      \altcol O_que eu pe -- | dir E -- _ le me | dá. __ _
      \set stanza = "2.B"
      Os i -- ni -- | mi -- gos que vi -- e -- rem  | con -- _ tra;
      Eu pe -- ço | for -- ça pa -- ra der -- ri -- | bar. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      Oh! | Mi -- nha Vir -- gem | Mãe; __ _
      Oh! __ _ | Vir -- gem da Con -- cei -- | ção. __ _
      \set stanza = "3.B"
      \skip 1 Eu __ _ | pe -- _ ço a Je -- sus | Cris -- _ to;
      Pa -- ra dar | for -- _ ça~a -- qui na ses -- | são. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 a:m | g1
        | a2:m f | c2~8
      }
      \repeat volta 2 {
        s4. | f2 g | c \parenthesize f
        | g \parenthesize a:m | c2~8
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I live with my Master; I live with my brothers and sisters
    I live in the holy light; I'm at the foot of the cross with Juramidam
    \nextverse
    I ask my Father; what I ask, He gives to me
    The enemies who come against me, I ask for strength to defeat them
    \nextverse
    Oh! My Virgin Mother; Oh! Virgin of Conception
    I ask Jesus Christ to give strength here in the session
  \end{translation}
\endsong


\beginsong{É Pedindo e é Rogando}[by={Padr. Sebastião}, key={C}, gk={D, C--E}]
  \audio[]{https://www.nossairmandade.com/hymn/4/\%C3\%89PedindoE\%C3\%89Rogando}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=620s}
  \newchords{chords_epedindo_a}\newchords{chords_epedindo_b}
  \mnbeginchorus\memorize[chords_epedindo_a]
    \[^\mn{G}]É pe|\[\mnc{C}C]dindo \[Am]{e é} \[^\mn{E}]ro|\[\mnc{G}G]ga\[\bm]n\[^\mn{F}]do \altchords{\id[1]{(D)}|D Bm |A}
    \[^\mn{E}]Que \[^\mn{D}]po|\[\mnc{C}Am]demos \[\mnc{G}G]al\[^\mn{D}]can|\[\mnc{C}C]çar \[\bm] \altchords{|Bm A |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_epedindo_b]
    \[^\mn{C}]Não é |\[\mnc{G}C]fa\[^\mn{C}]lar \[\bm]um do |\[\mnc{E}Am]ou\[\bmadj{-1ex}]\[^\mn{C}]tro \altchords{|D |Bm}
    Queren|\[\mnc{G}G]do ca\[\mnc{C}Am]lu\[^\mn{E}]ni|\[\mnc{C}C]ar \[\bm] \altchords{|A Bm |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_epedindo_a]
    Me apre|^sento ^{a meu} |^Pa^i
    E minha his|^tória eu ^sei con|^tar ^
  \endchorus\glueverses\beginchorus\replay[chords_epedindo_b]
    Peço |^que to^dos se |^u^nam
    E a|^prendam a ^respei|^tar ^
  \endchorus
  \beginchorus\replay[chords_epedindo_a]
    É |^no céu ^{e na} |^te^rra \altchords{\id[4]{MK (C)} |C Am |G}
    E é bei|^rando a ^beira |^mar ^ \altchords{|C G |C}
  \endchorus\glueverses\beginchorus\replay[chords_epedindo_b]
    O meu en|^contro ^com Je|^sus ^ \altchords{|C |Am}
    Só |^eu sei ^destrin|^char ^ \altchords{|C Am |C}
  \endchorus
  \beginchorus\replay[chords_epedindo_a]
    Foi |^aí ^neste |^di^-a
    E foi nas |^águas ^de Jor|^dão ^
  \endchorus\glueverses\beginchorus\replay[chords_epedindo_b]
    Que ambos |^foram ^bati|^za^dos
    E come|^çou su^{a mis}|^são ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize g8\posectionmark "A" g8( g8) | c4 c4 c4 e4 | g2~ g8 f8 e8 d8
        | c4 c8( c8) g4 d'4 | c2~8
      } \break
      \repeat volta 2 {
        \parenthesize c8\sectionmark "B" c8 c8 | g4 c4 c4 c4 | e2~ e8 \parenthesize c8 c8( c8) |
        | g4 g4 c4 e4 | c2~8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        \skip 1 É pe -- | din -- do e~é ro -- | gan -- _ do;
        Que po -- | de -- mos __ _ al -- can -- | çar. __ _
      \set stanza = "1.B"
        \skip 1 Não é | fa -- lar um do | out -- _ ro;
        Que -- ren -- | do ca -- lu -- ni -- | ar. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
        Me a -- pre -- | sen -- to a meu | Pai; __ _
        E mi -- nha~his | tó -- ria eu sei con -- | tar. __ _
      \set stanza = "2.B"
        \skip 1 Pe -- ço | que to -- dos se | u -- _ nam;
        E a -- | pren -- dam~a res -- pei -- | tar. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
        \skip 1 É __ _ | no céu e na | ter -- _ ra;
        E~é bei -- | ran -- do a bei -- ra | mar. __ _
      \set stanza = "3.B"
        O meu en -- | con -- tro com Je -- | sus; __ _
        \skip 1 Só __ _ | eu sei des -- trin -- | char. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
        \skip 1 Foi __ _ | a -- í nes -- te | di -- _ a;~E
        foi nas | á -- guas __ _ de Jor -- | dão. __ _
      \set stanza = "4.B"
        Que am -- bos | fo -- ram ba -- ti -- | za -- _ dos;~E
        co -- me -- | çou su -- a mis -- | são. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 a:m | g1
        | a2:m g | c2~8
      }
      \repeat volta 2 {
        s4. | c1 | a:m
        | g2 a:m | c2~8
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    It's by asking and praying
    That we're able to attain
    It's not by talking about each other
    Wanting to slander
    \nextverse
    I present myself to my Father
    And know how to tell my story
    I ask that all unite
    And learn to be respectful
    \nextverse
    It's in heaven and on the earth
    And long the sea
    My meeting with Jesus
    Only I know how to unravel it
    \nextverse
    It was there on this day
    And in the waters of the Jordan
    That both were baptized
    And began their mission
  \end{translation}
\endsong


\beginsong{Dem Dum}[by={Padr. Sebastião}, key={C}, gk={D, C--E}]
  \audio[]{https://www.nossairmandade.com/hymn/5/DemDum}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=785s}
  \newchords{chords_demdum_a}\newchords{chords_demdum_b}
  \mnbeginchorus\rep{3}
    \ind \[\mn{G}]Dem |\[\mnc{C}C]dum\[\bm], \[\mn{G}]dem |\[\mn{C}]dum\[\bm] \altchords{\id[1]{(D)}|D | \e}
    \ind \[\mn{G}]Dem |\[\mnc{E}Am]dum\[\bm], \[\mn{G}]dem |\[\mnc{C}C]dum\[\bm] \altchords{|Bm |D}
  \mnendchorus
  \mnbeginchorus\memorize[chords_demdum_a]
    \[^\mn{G}]Deus sa|\[\mnc{C}C]be o que es\[\bm]tá \[^\mn{D}]fa|\[\mnc{C}Am]zen\[\bmadj{-1ex}]do \altchords{|D |Bm}
    Sen\[^\mn{D}]ta|\[\mnc{E}C]do \[^\mn{G}]no \[\mnc{D}G]seu \[^\mn{E}]lu|\[\mnc{C}C]gar\[\bm] \altchords{|D A |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_demdum_b]
    \[^\mn{C}]As |\[\mnc{D}Dm]doze \[^\mn{C}]ho\[\mnc{A}F]ras \[^\mn{C}]do |\[\mnc{G}G]di\[\bm]a \altchords{|Em G |A}
    \[^\mn{C}]Nós \[^\mn{D}]pre|\[\mnc{E}Am]ci\[^\mn{G}]sa\[\mnc{D}G]mos \[^\mn{E}]re|\[\mnc{C}C]zar\[\bm] \altchords{|Bm A |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_demdum_a]
    Pai |^nosso que es^tais no |^céu ^
    Rece|^bemos com ^ale|^gri^a
  \endchorus\glueverses\beginchorus\replay[chords_demdum_b]
    Nosso |^Pai e ^nossa |^Mãe^
    A sem|^pre Vir^gem Ma|^ri^a
  \endchorus
  \beginchorus\replay[chords_demdum_a]
    O po|^der de ^Deus é |^gra^nde
    Seja |^feita a vos^sa von|^ta^de
  \endchorus\glueverses\beginchorus\replay[chords_demdum_b]
    É quem |^nos dá ^o per|^dão^
    E é a |^nossa ^majes|^ta^de
  \endchorus
  \beginchorus\replay[chords_demdum_a]
    Todo |^mundo ^pede a |^Deus ^
    Mas não |^sabem se ^expli|^car^
  \endchorus\glueverses\beginchorus\replay[chords_demdum_b]
    Guar|^dai-me, ^defen|^dei^-me
    Livrai-|^me de ^todo |^mal^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \mark \markup {"3x"} \bar ".|:" \repeat volta 3 {
        g4\sectionmark "i" | c2. g4 | c2. g4
        | e'2. g,4 | c2.
      } \break
      \repeat volta 2 {
        g8( \segno \posectionmark "A" g8) | c4 c8( c8) c4 d4 | c2~ c8( c8) c8 d8
        | e4 g8( g8) d4 e4 | c2( c4)
      } \break
      \repeat volta 2 {
        c8( \sectionmark "B" c8) | d4. c8 a4. c8 | g2( g8)( g8) c8 d8
        | e4 g4 d4 e4
      } \alternative {
        { | c2( c4)}
        { | c2( c4) ^\dalsegno \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 3 {
        Dem | dum, dem | dum; Dem | dum, dem | dum.
      }
      << % verses, part A
        {
          \set stanza = "1.A"
          \repeat volta 2 {
            Deus sa -- | be~o que_es -- _ tá fa -- | zen -- _ do;
            Sen -- ta -- | do no __ _ seu lu -- | gar. __ _
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "2.A"
          \repeat volta 2 {
            Pai __ _ | nos -- so que~es -- tais no | céu; __ _ _
            Re -- ce -- | be -- mos com a -- le -- | gri -- a.
          }
        } 
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "3.A"
          \repeat volta 2 {
            O po -- | der de __ _ Deus é | gran -- _ de;
            Se -- ja | fei -- ta~a vos -- sa von -- | ta -- de.
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "4.A"
          \repeat volta 2 {
            To -- do | mun -- do __ _ pe -- de~a | Deus; __ _ _
            Mas não | sa -- bem se ex -- pli -- | car. _
          }
        }
      >>
      << % verses, part B
        {
          \set stanza = "1.B"
          \repeat volta 2 {
            As __ _ | doze ho -- ras do | di -- a; __ _
            Nós pre -- | ci -- sa -- mos re --
          } \alternative {
            { | zar. __ _ }
            { | zar. __ _ }
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "2.B"
          \repeat volta 2 {
            Nos -- so | Pai e nos -- sa | Mãe; __ _ _
            A sem -- | pre Vir -- gem Ma --
          } \alternative {
            { | ri -- a. }
            { | ri -- a. }
          }
        } 
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "3.B"
          \repeat volta 2 {
            É quem | nos dá o per -- | dão; __ _
            E é a | nos -- sa ma -- jes --
          } \alternative {
            { | ta -- de. }
            { | ta -- de. }
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "4.B"
          \repeat volta 2 {
            Guar -- _ | dai -- me, de -- fen -- | dei -- _ me;
            Liv -- rai -- | me de to -- do
          } \alternative {
            { | mal. __ _ }
            { | mal. __ _ }
          }
        }
      >>
    }
    theChords = \chordmode {
      \repeat volta 3 {
        s4 | c1 | c1
        | a:m | c2.
      }
      \repeat volta 2 {
        s4 | c1 | a:m
        | c2 g | c2.
      }
      \repeat volta 2 {
        s4 | d2:m f | g1
        | a2:m g
      } \alternative {
        { | c2. }
        { | c2. }
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    Dem dum, dem dum; Dem dum, dem dum
    \nextverse
    God knows what He's doing; Seated in his place
    Throughout the day's twelve hours; We need to pray
    \nextverse
    Our Father who art in heaven; We receive with joy
    Our Father and our Mother; The Ever Virgin Mary
    \nextverse
    The power of God is great; Thy will be done
    It's He who grants forgiveness; And is our majesty
    \nextverse
    All ask God; But don't know how to explain themselves
    Guard me, defend me; Deliver me from all evil
  \end{translation}
\endsong


\beginsong{Aqui Eu Vou Expor}[by={Padr. Sebastião}, key={D}, gk={D, D--E}]
  \audio[]{https://www.nossairmandade.com/hymn/6/AquiEuVouExpor}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=925s}
  \transpose{2} % C to D
  \mnbeginchorus\memorize
    \[^\mn{G}]A|\[\mnc{C}C]qui eu \[\bm]vou \[^\mn{E}]ex|\[\mnc{G}(G)]po\[\bmc\mn{E}]r \altchords{\id[1]{(C)}|C |(G)}
    \[^\mn{G}]Eu |\[\mnc{F}C7]vim \[^\mn{E}]pa\[\bmc\mn{D}]ra \[^\mn{C}]lem|\[\mnc{F}F]brar\[\bm] \altchords{|C7 |F}
    \[^\mn{A}]O mis|tério da \[\bmc\mn{F}]o\[^\mn{A}]ra|\[\mnc{G}C]ção \altchords{| - |C}
    \[\bmc\mn{C}]Não \[^\mn{D}]é |\[\mnc{E}G7]so\[^\mn{D}]men\[\bmc\mn{A}]te \[^\mn{B}]re|\[\mnc{C}C]zar\[\bm] \altchords{|G7 |C}
  \mnendchorus
  \notesoff
  \beginchorus
    É re|^zar e ^por em |^prática
    ^E en|^trar em ^comu|^nhão^
    Se lem|brar de ^Jesus |^Cristo
    E ^esque|^cer a ^{i}lu|^são^
  \endchorus
  \beginchorus
    A minha |^Mãe sem^pre me |^olha \altchords{\id[4]{alt. (C)} |C (Am) |(G) C}
    ^E meu |^Pai co^migo es|^tá ^ \altchords{|Fmaj7 C |F}
    Me en|trega es^tes en|^sinos \altchords{| - |G}
    ^Para a|^qui eu ^expli|^car ^ \altchords{|Dm F |C}
  \endchorus
  \beginchorus
    Cada |^um cui^da de |^si
    ^Eu tam|^bém cui^do de |^mim ^
    Vou ze|lando es^ta es|^trada
    Es^tou fa|^zendo o ^meu jar|^dim ^
  \endchorus
  \beginchorus
    O que é |^do meu ^Pai é |^meu \altchords{\id[5]{alt. (D)} |D (Bm) |(A) D}
    ^O que é |^dele eu ^posso u|^sar ^ \altchords{|Gmaj7 D |G}
    Só não |uso o que ^é dos |^outros \altchords{| - |A}
    ^Que po|^de me ^derri|^bar ^ \altchords{|Em G |D}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \transpose c d \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize g8 \pomark g8( g8) | c4 c4 c4 e4 | g4.( \parenthesize g16)( \parenthesize g16)( e4) g4
        | f4 e4 d4 c4 | f2. a,8 a8
        | a4( a8) a8 f4 a4 | g4.( g8) c4 d4
        | e4 d4 a4 b4 | c2~8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 A -- _ | qui eu vou ex -- | por; __ _ _ _
        Eu | vim pa -- ra lem -- | brar;
        O mis -- | té -- rio da o -- ra -- | ção; __ _
        Não é | so -- men -- te re -- | zar. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        \skip 1 É re -- | zar e por em | prá -- ti -- ca;
        E en -- | trar em co -- mu -- | nhão;
        Se lem -- | brar __ _ de Je -- sus | Cris -- to;~E
        es -- que -- | cer a i -- lu -- | são. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        A mi -- nha | Mãe sem -- pre me | o -- lha; __ _
        E meu | Pai co -- mi -- go~es -- | tá;
        Me en -- | tre -- ga es -- tes en -- | si -- nos;
        Pa -- ra~a -- | qui eu ex -- pli -- | car. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        \skip 1 Ca -- da | um cui -- da de | si; __ _ _
        Eu tam -- | bém cui -- do de | mim;
        Vou ze -- | lan -- do es -- ta es | tra -- da;~Es --
        tou fa -- | zen -- do~o meu jar -- | dim. __ _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \repeat volta 2 {
        O que é | do meu  Pai é | meu; __ _
        O que é | de -- le~eu  pos -- so~u -- | sar;
        Só não | u -- so~o que é dos | ou -- tros;
        Que po -- | de me der -- ri -- | bar. __ _
      }
    }
    theChords = \transpose c d \chordmode {
      \repeat volta 2 {
        s4. | c1 | \parenthesize g | c:7 | f
        | f | c | g:7 | c2~8
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}\scriptsize % smaller to fit whole song on a spread
    Here I'm going to reveal; I came to recall
    The mystery of the prayer; Is not merely to pray
    \nextverse
    One must pray and put this into practice; And enter into communion
    One must recall Jesus Christ; And to forget the illusion
    \nextverse
    My Mother always watches me; And my Father is with me
    He gives me these teachings; For me to explain them here
    \nextverse
    Each one looks after oneself; I also look after myself
    I'm taking care of this path; I'm making my garden
    \nextverse
    What belongs to my Father is mine; I can use that which is His
    But I don't use what belongs to others; Because that can throw me down
  \end{translation}
\endsong


\beginsong{Eu Vou Rezar}[by={Padr. Sebastião}, key={D}, gk={D, D\shrp{}--G\shrp{}}]
  \audio[]{https://www.nossairmandade.com/hymn/7/EuVouRezar}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1121s}
  \transpose{2}
  \newchords{chords_euvourezar_a}\newchords{chords_euvourezar_b}
  \mnbeginchorus\memorize[chords_euvourezar_a]
    \[^\mn{G}]Eu \[^\mn{E}]vou \[^\mn{G}]re|\[\mnc{C}C]zar que é pa\[^\mn{B}]ra \[\mnc{A}(Am)]to\[^\mn{B}]do \[^\mn{C}]mun\[^\mn{A}]do |\[\mnc{G}G]ver
    Pai \[^\mn{B}]nos\[\bmc\mn{D}]so que estais \[^\mn{B}]no |\[^\mn{G}]céu vós \[^\mn{B}]quei\[\bmc\mn{D}]ra \[^\mn{C}]me \[^\mn{A}]de\[^\mn{B}]fen|\[\mnc{C}C]der \[\up{2}(C7)]
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_euvourezar_b]
    \[^\mn{C}]Pão |\[\mncii{F}{E}F]nos\[\mnc{D}G]so \[^\mn{E}]de \[^\mn{F}]ca\[^\mn{D}]da |\[\mnc{C}C]dia
    Je\[^\mn{A}]sus \[\mnc{C}Am]no alto \[^\mn{A}]da |\[\mnc{G}G]cruz \[^\mn{B}]so\[\bmc\mn{D}]freu \[^\mn{C}]to\[^\mn{A}]da a\[^\mn{B}]go|\[\mnc{C}C]ni\[\up{1}C7]a
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_euvourezar_a]
    \noteson\[\bmc\mn{E}]Eu \[\mn{G}]pe\notesoff|^di ^{e meu} Pai me |^deu \altchords{\id[1]{(C)}|C (Am) |G}
    Para eu ^nunca me esque|cer ^de São Iri|^neu ^ \altchords{| - |C \up{2}(C7)}
    \endchorus\glueverses\beginchorus\replay[chords_euvourezar_b]
    A |^cruz ele ^sempre consa|^grou \altchords{|F G |C}
    ^No céu e na |^terra aqui es^tá o meu a|^mor ^ \altchords{Am |G |C \up{1}C7}
  \endchorus
  \beginchorus\replay[chords_euvourezar_a]
    \noteson\[\mn{G}]A\notesoff|^mei ^{e bem} soube a|^mar
    Meu ^Mestre me cha|mou eu ^vim lhe acompa|^nhar ^
    \endchorus\glueverses\beginchorus\replay[chords_euvourezar_b]
    Je|^sus ele ^tem todo a|^mor
    É a^qui que ele es|^tá e é a^qui que eu es|^tou ^
  \endchorus
  \beginchorus\replay[chords_euvourezar_a]
    Esta men|^sagem ele ^mandou explan|^dir
    Quem não ^quiser escu|tar fa^ça favor ou|^vir ^
    \endchorus\glueverses\beginchorus\replay[chords_euvourezar_b]
    Meu |^Mestre ^ele não se es|^conde
    Eu ^sempre estou a|^tento com o San^tíssimo Sacra|^men^to
  \endchorus
  \beginchorus\replay[chords_euvourezar_a]
    \noteson\[\mn{G}]Não \notesoff|^digas que o Mes^tre não tem sa|^ber \altchords{\id[4]{MK (D)}|D G |A}
    E^le bem ensi|nou e você ^não quis apren|^der ^ \altchords{|A7 |D \up{2}(D7)}
    \endchorus\glueverses\beginchorus\replay[chords_euvourezar_b]
    A|^gora ^é que eu quero |^ver \altchords{|G A |Bm}
    É ^andar direi|^tinho sob ^pena de sof|^rer ^ \altchords{G |A7 |D \up{1}D7}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \transpose c d \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 2
      \repeat volta 2 {
        \afterGrace \parenthesize e4 { \altcol g8 \altmark "1. & 4." \posectionmark "A" } \altcol\grace e8 \afterGrace g4 { \altcol g8 } | c8( c8)( c8) \parenthesize b8 a8 b8 c8 a8 | g8( g8)(g8) b8 d8 d8 d8 b8
        | g8( g8)( g8) \parenthesize b8 d8 c8 a8 b8
      } \alternative {
        { | c2 }
        { | c2. c4\sectionmark "B" }
      }
      \repeat volta 2 {
        | f4( f8)( e8) d8 e8 f8 d8 | c8( c8)( c8) \parenthesize a8 c8 c8 c8 a8
        | g8( g8)( g8)( b8) d8 c8 a8 b8
      } \alternative {
        { | c2( c4) c4 }
        { | c4( c4) \bar "|."}
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 { \set includeGraceNotes = ##t
        \skip 1 \altcol Eu \altcol vou \skip 1 \altcol re --
          | zar que~é pa -- ra to -- do mun -- do | ver;
        Pai __ _ nos -- so que~es -- tais no | céu __ _ vós quei -- ra me de -- fen --
      } \alternative {
        { | der. }
        { | der. \set stanza = "1.B" Pão }
      }
      \repeat volta 2 {
        | nos -- _ _ so de ca -- da | di -- a;
        Je -- sus no al -- to da | cruz __ _ _ so -- freu to -- da~a -- go --
      } \alternative {
        { | ni -- a. Pão }
        { | ni -- a. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Eu pe -- | di __ _ _ \skip 1 e meu Pai me | deu; __ _
        Pa -- ra~eu nun -- ca me~es -- que -- | cer __ _ _ \skip 1 de São I -- ri --
      } \alternative {
        { | neu. }
        { | neu. \set stanza = "2.B" A }
      }
      \repeat volta 2 {
        | cruz e -- le  sem -- pre con -- sa -- | grou; __ _ _ \skip 1
        No céu e na | ter -- ra~a -- qui es -- tá o meu a --
      } \alternative {
        { | mor. __ _ A }
        { | mor. __ _ }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        \skip 1 A -- | mei __ _ _ \skip 1 e bem sou -- be~a -- | mar; __ _ _
        Meu Mes -- tre me cha -- | mou __ _ _ eu vim lhe~a -- com -- pa --
      } \alternative {
        { | nhar. }
        { | nhar. \set stanza = "3.B" Je -- }
      }
      \repeat volta 2 {
        | sus e -- le tem to -- do a -- | mor; __ _ 
        É a -- qui que e le~es -- | tá __ _ e~é a -- qui que eu es --
      } \alternative {
        { | tou. __ _ Je -- }
        { | tou. __ _ }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {  \set includeGraceNotes = ##t
        \skip 1 \altcol Es -- \altcol ta \skip 1 \altcol men --
          | sa -- _ gem~e -- le  man -- dou ex -- plan -- | dir; __ _
        Quem não qui -- ser es -- cu -- | tar __ _ _ fa -- ça fa -- vor ou --
      } \alternative {
        { | vir. }
        { | vir. \set stanza = "4.B" Meu }
      }
      \repeat volta 2 {
        | Mes -- _ tre e -- le não se~es -- | con -- _ de;
        Eu sem -- pre~es -- tou a -- | ten -- to com~o San -- tíssi -- mo Sa -- cra --
      } \alternative {
        { | men -- to. Meu }
        { | men -- to. }
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        \skip 1 Não | di -- gas que~o Mes -- tre não tem sa -- | ber; __ _ _
        E -- le bem en -- si -- | nou e vo -- cê não quis a -- pren --
      } \alternative {
        { | der. }
        { | der. \set stanza = "5.B" A -- }
      }
      \repeat volta 2 {
        | go -- _ ra é que~eu que -- ro | ver; __ _ _
        É an -- dar di -- rei -- | ti -- nho sob __ _ pe -- na de sof --
      } \alternative {
        { | rer. __ _ A -- }
        { | rer. __ _ }
      }
    }
    theChords = \transpose c d \chordmode {
      \repeat volta 2 {
        s2 | c2 \parenthesize a:m | g1 | g
      } \alternative {
        { | c2 }
        { | c2 c2:7 }
      }
      \repeat volta 2 {
        | f2 g | c a:m | g1
      } \alternative {
        { | c2 c2:7 }
        { | c2 }
      }
    }
    \layout { #(layout-set-staff-size 12) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    I'm going to pray for everyone to see
    Our Father who art in heaven please defend me
    Our bread of each day
    Jesus on the height of the cross suffered all agony
    \nextverse
    I asked and my Father gave me
    To never forget Saint Irineu
    The cross he always consecrated
    In heaven and on earth, here is my love
    \nextverse
    I loved and knew how to love well
    My Master called me, I came along with Him
    Jesus, he has all love
    It's here that he is and it's here that I am
    \nextverse
    This message he ordered to spread
    Those who don't want to listen, please hear it
    My Master he does not hide
    I'm always attentive with the Most Holy Sacrament
    \nextverse
    Don't say that the Master has no knowledge
    He taught well and you didn't want to learn
    It is now that I want to see
    One must walk the straight and narrow on pain of suffering
  \end{translation}
\endsong


\beginsong{Para Estar Junto a Este Cruzeiro}[by={Padr. Sebastião}, key={C}, gk={D, C--E}]
  \audio[]{https://www.nossairmandade.com/hymn/8/ParaEstarJuntoAEsteCruzeiro}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1257s}
  \newchords{chords_paraestarjunto_a}\newchords{chords_paraestarjunto_b}
  \mnbeginchorus\memorize[chords_paraestarjunto_a]
    \[^\mn{G}]Para es|\[\mnc{C}C]tar junto a \[\bm]este \[^\mn{E}]cru|\[^\mn{G}]zei\[\bmc\mn{E}]ro \altchords{\id[1]{(D)}|D | \e }
    É \[^\mn{G}]mu|\[\mnc{E}Am]dar \[^\mn{C}]de \[^\mn{A}]o\[\mnc{D}G]pi\[^\mn{E}]ni|\[\mnc{C}C]ão \[\bm] \altchords{|Bm A |D}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_paraestarjunto_b]
    \[^\mn{A}]Quem |\[\mnc{C}C]a\[^\mn{A}]ma a \[\mnc{D}Dm]Je\[^\mn{C}]sus |\[\mnc{G}G]Cris\[\bm]to \altchords{|D Em |A}
    \[^\mn{C}]Não |\[\mnc{E}Am]fa\[^\mn{C}]la \[^\mn{A}]do \[\mnc{D}G]seu \[^\mn{E}]ir|\[\mnc{C}C]mão \[\bm] \altchords{|Bm A |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_paraestarjunto_a]
    O |^Mestre es^tá a|qui ^
    E|^le fala ^bem bai|^xi^nho
    \endchorus\glueverses\beginchorus\replay[chords_paraestarjunto_b]
    En|^sina a ^quem pro|^cu^ra
    Dei|^xando quem não ^quer se|^guir ^
  \endchorus
  \beginchorus\replay[chords_paraestarjunto_a]
    A|^qui es^tou di|zen^do \altchords{\id[4]{alt. (C)}|C Am |G}
    Para os |^meus ir^mãos ou|^vir ^ \altchords{|Am G |C}
    \endchorus\glueverses\beginchorus\replay[chords_paraestarjunto_b]
    Quem for |^filho ^vem che|^gan^do \altchords{|Am Dm |G}
    E quem não |^for vai es^capu|^lir ^ \altchords{|Am G |C}
  \endchorus
  \beginchorus\replay[chords_paraestarjunto_a]
    Não a|^dian^ta ser |gran^de \altchords{\id[5]{MK (C)}|C | \e}
    Sem |^possu^ir no|^bre^za \altchords{|Am G7 |C}
    \endchorus\glueverses\beginchorus\replay[chords_paraestarjunto_b]
    Meu |^Pai e ^minha |^Mãe ^ \altchords{|Am G7 |C}
    Nos |^mostra a su^a be|^le^za \altchords{|Am G7 |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
  % transcribed by larva, updated on 2023-01
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8( \posectionmark "A" g8) | c4( c8) c8 \once\slurDown c4( << c8) \once\override Slur.color = #color-alt \parenthesize e8( \parenthesize\altmark "2." >> e8)
          | g2 e4 << e8 \once\override Slur.color = #color-alt \parenthesize g8( \parenthesize\altmark "2. & 4." >> g8)
        | e4( c8) a8 d4 e4 | c2( c4)
      } \break
      \repeat volta 2 {
        a8( \sectionmark "B" a8) | c4. a8 d4. c8
          | g2( g8) \altcol\parenthesize c8 \altmark "3." c8( c8)
        | e8( e8) c8 a8 d4 e4 | c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Pa -- ra~es -- | tar jun -- to~a es -- te cru -- | zei -- ro;
        É mu -- | dar de o -- pi -- ni -- | ão. __ _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Quem __ _ | a -- ma~a Je -- sus | Cris -- to; \skip 1
        Não __ _ | fa -- _ la do seu ir -- | mão. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        O __ _ | Mes -- tre es -- tá \altcol (a) -- _ | qui; __ _
        \altcol (E) -- _ | le fa -- la bem bai -- | xi -- nho.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        En -- _ | si -- na~a  quem pro -- | cu -- ra; \skip 1
        Dei -- _ | xan -- do quem não quer se -- | guir. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        A -- _ | qui __ _ es -- tou __ _ di -- | zen -- do;
        Pa -- ra~os | meus __ _ ir -- mãos ou -- | vir. __ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Quem for | fi -- lho vem che -- | gan -- do;
        \altcol E quem não | for __ _ vai es -- ca -- pu -- | lir. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Não a -- | di -- _ an -- ta _ ser | gran -- de;
        \altcol (Sem) __ _ | pos -- _ su -- ir no -- | bre -- za.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Meu __ _ | Pai e  mi -- nha | Mãe; __ _ \skip 1
        Nos __ _ | mos -- _ tra~a su -- a be -- | le -- za.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | c1
        | a2:m g | c2.
      }
      \repeat volta 2 {
        s4 | c2 d:m | g1
        | a2:m g | c2.
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    To be next to this Cruzeiro, one must change one's mind
    Those who love Jesus Christ don't talk about their brothers and sisters
    \nextverse
    The Master is here, he speaks very softly
    He teaches those who seek Him, leaving alone those who don't want to follow
    \nextverse
    Here I am saying, for my brothers and sisters to hear me
    Those who are children are arriving, and those who aren't are going to flee
    \nextverse
    It's no use to be great without having nobility
    My Father and my Mother, show us your beauty
  \end{translation}
\endsong


\beginsong{Não Creia nos Mestres que te Aparecem}[by={Padr. Sebastião}, key={C}, gk={D, C--D}]
  \audio[]{https://www.nossairmandade.com/hymn/9/N\%C3\%A3oCreiaNosMestresQueTeAparecem}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1411s}
  \newchords{chords_naocreianosmestres_a}\newchords{chords_naocreianosmestres_b}
  \mnbeginchorus\memorize[chords_naocreianosmestres_a]
    \[^\mn{G}]Não |\[\mnc{C}C]creia nos \[^\mn{D}]mes\[\bm]tres \[^\mn{C}]que \[^\mn{A}]te a\[^\mn{C}]pa|re\[\bm]cem \altchords{\id[1]{(D)}|D | \e}
    E nem \[^\mn{E}]com |\[\mnc{G}G]eles no ca\[F]min\[^\mn{E}]ho \[^\mn{C}]quei\[^\mn{F}]ra an|\[\mnc{E}E]dar\[\bm] \altchords{|A G |F\shrp{}}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_naocreianosmestres_b]
    |\[\mnc{G}G]Creia \[^\mn{E}]so\[\mnc{A}Am]men\[^\mn{G}]te em \[^\mn{F}]seu \[^\mn{E}]Je|\[\mnc{C}C]su\[\mnc{A}(Am)]s \altchords{|A Bm |D (Bm)}
    \[^\mn{E}]Que |\[\mnc{C}F]E\[^\mn{A}]le é \[^\mn{D}]quem \[G7]tem \[^\mn{C}]pa\[^\mn{A}]ra \[^\mn{C}]te |\[C]dar\[\bm] \altchords{|G A7 |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_naocreianosmestres_a]
    Meu |^Mestre a^qui a vós eu |pe^ço
    |^Para ^Vós me gui|^ar ^
    \endchorus\glueverses\beginchorus\replay[chords_naocreianosmestres_b]
    Me |^guie no ca^minho da santa |^luz^
    Não |^deixa nin^guém me ata|^car^
  \endchorus
  \beginchorus\replay[chords_naocreianosmestres_a]
    |^Segue ^sempre o Seu ca|mi^nho \altchords{\id[4]{alt. (C)}|C G |C}
    |^Deixa ^quem quiser fa|^lar^ \altchords{|G F |E}
    \endchorus\glueverses\beginchorus\replay[chords_naocreianosmestres_b]
    Re|^cebe a Su^{a luz} de cris|^tal^ \altchords{|C G |Am}
    Te |^firma e te com^põe em Seu lu|^gar^ \altchords{|F G7 |C}
  \endchorus
  \beginchorus\replay[chords_naocreianosmestres_a]
    Re|^cebe ^todos que che|gar^ \altchords{\id[6]{simples (C)}|C (F) |C}
    |^Faz o que ^eu te man|^dar \altchords{|C |Am}
    \endchorus\glueverses\beginchorus\replay[chords_naocreianosmestres_b]
    Não |^deixa fa^zer o que eles |^que^rem \altchords{|C |Am}
    Es|^pera atá o ^dia que eu che|^gar^ \altchords{|C G |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        \parenthesize g4 \posectionmark "A" | c8( c8)( c8) d8 d8 c8 a8 c8 | c2( c8)( c8 c8) \parenthesize e8
        | g8( g8)( g8) g8 g8( e8) c8 f8 | e2.
      }
      \repeat volta 2 {
        \parenthesize e4\sectionmark "B" | g8( g8) g8 e8 a8 g8 f8 e8 | c2( a4) e'4
        | c8( c8) a8 d8 d8 c8 a8 c8 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Não | crei -- a nos mes -- tres que te~a -- pa -- | re -- cem;
        E nem com | e -- les no ca -- min -- ho quei -- ra~an -- | dar.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        \skip 1 | Crei -- _ a so -- men -- te~em seu Je -- | sus; __ _
        Que E -- _ le~é quem tem pa -- ra te | dar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Meu | Mes -- _ tre a -- qui a vós eu | pe -- ço; __ _ _ \skip 1
        | Pa -- _ _ ra  Vós __ _ me gui -- | ar.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Me | guie _ no ca -- mi -- nho~da san -- ta | luz; __ _
        Não | dei -- _ xa nin -- guém me a -- ta -- | car.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        \skip 1 | Se -- _ _ gue sem -- pre~o Seu ca -- | mi -- nho; __ _ _ \skip 1
        | Dei -- _ _ xa quem qui -- ser fa -- | lar.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Re -- | ce -- be a Su -- a luz de cris -- | tal; __ _
        Te | fir -- ma~e te com -- põe em Seu lu -- | gar.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Re -- | ce -- _ _ be to -- dos que che -- | gar; __ _ _ _ \skip 1
        | Faz __ _ o que eu __ _ te man -- | dar.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Não | dei -- _ xa fa -- zer o que~e -- les | que -- rem;
        Es -- | pe -- ra~a -- tá o di -- a que~eu che -- | gar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | c1
        | g2 f | e2.
      }
      \repeat volta 2 {
        s4 | g2 a2:m | c2 \parenthesize a2:m
        | f2 g2:7 | c2.
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Don't believe in the masters who appear to you; Nor walk on the path with them
    Believe only in your Jesus; For it's He who can give to you
    \nextverse
    My Master, here I ask You; For You to guide me
    Guide me on the path of the holy light; Don't let anyone attack me
    \nextverse
    Always follow Your path; Let whoever wants to talk
    Receive Your crystal light; Be firm and composed in Your place
    \nextverse
    Receive all who arrive; Do as I tell you
    Don't let be done what they want; Wait until the day that I arrive
  \end{translation}
\endsong


\beginsong{Peço que Vós me Ouça}[by={Padr. Sebastião}, tags={valsa}, key={C}, gk={C, C--D}]
  % Also in songs_astral_cura_i.tex
  \audio[]{https://www.nossairmandade.com/hymn/10/Pe\%C3\%A7oQueV\%C3\%B3sMeOu\%C3\%A7a}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1564s}
  % Note: This hino is sometimes sung two times, but not in Oração
  \newchords{chords_pecoquevosmeouca_a}\newchords{chords_pecoquevosmeouca_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_pecoquevosmeouca_a]
    \[^\mn{G}]Meu |\[\mnc{C}C]Pai \[^\mn{F}]pe\[^\mn{E}]ço |\[\mnc{D}G]que \[^\mn{F}]Vós \[^\mn{E}]me |\[\mnc{C}C]ou|\[C7]ça \altchords{\id[1]{(D)}|D |A |D |D7}
    |\[\mnc{A}Fmaj7]Para eu pe|\[\mnc{G}C]dir \[^\mn{C}]o \[^\mn{E}]per|\[\mnc{G}G]dão | \e \altchords{|Gmaj7 |D |A | \e}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_pecoquevosmeouca_b]
    \[^\mn{C}]Eu |\[\mnc{A}F]peço não |\[\mnc{G}G]só \[^\mn{F}]pa\[^\mn{E}]ra |\[\mnc{C}C]mi|\[Am]m \altchords{|G |A |D |Bm}
    \[^\mn{A}]Pa\[^\mn{C}]ra |\[\mnc{E}C]mim \[^\mn{G}]e |\[\mnc{D}G7]os \[^\mn{F}]meus \[^\mn{E}]ir|\[\mnc{C}C]mãos |\[\up{1}C7] \e \altchords{|D |A7 |D |\up{1}D7}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_pecoquevosmeouca_a]
    Meu |^Pai quando |^for perdo|^ar |^ \e
    Per|^{doa co}|^mo lhe con|^vém | \e
    \endchorus\glueverses\beginchorus\replay[chords_pecoquevosmeouca_b]
    Eu |^peço que |^vós nos per|^do|^e
    Como |^perdo|^ou em Be|^lém |^ \e
  \endchorus
  \beginchorus\replay[chords_pecoquevosmeouca_a]
    A |^barca que |^corre no |^mar |^ \e \altchords{\id[4]{MK (C)}|C |G7 |C |C7}
    |^Corre no |^meu cora|^ção | \e \altchords{|Fmaj7 |C |G |\up{1}G7 \up{2}(C)}
    \endchorus\glueverses\beginchorus\replay[chords_pecoquevosmeouca_b]
    A|^quele que |^aqui ba|^ti|^za \altchords{|F |G |Am |F}
    Bati|^zou {\noteson\[\mnlow{G}]no \[\mnlow{F}]ri}|^{o de} Jor|^dão |^ \e \altchords{|C |G7 |C |\up{1}C7}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2023-02
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 4
      \repeat volta 2 {
        g4\posectionmark "A" | c4 f4 e4 | d4 f4 e4 | c2.( | c2)( c4)
        | a'4 a4 a4 | g4 c,4 e4 | g2.~ | g2
      }
      \repeat volta 2 {
        c,4\sectionmark "B" | a'4 a4 a4 | g4 f4 e4 | c2.(
        | c4) a4 c4
        \set melismaBusyProperties = #'() \slurDown
        | e4( << e4) \single\altcol g4\altmark "(3.)" >> << g4 \single\altcol f4 >> | d4 f4 e4 | c2.~ | c2
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Meu | Pai pe -- ço | que Vós me | ou -- | ça; __ _
        | Pa -- ra~eu pe -- | dir o per -- | dão. __ _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Eu | pe -- ço não | só pa -- ra | mim; __ _
        Pa -- ra | mim __ _ e | os meus ir -- | mãos. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Meu | Pai quan -- do | for per -- do -- | ar; __ _
        Per -- | do -- a co -- | mo lhe con -- | vém. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Eu | pe -- ço que | vós nos per -- |do -- | e;
        Co -- mo | per -- __ _ do -- | ou em Be -- | lém. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        A | bar -- ca que | cor -- re no | mar; __ _ _
        | Cor -- re no | meu co -- ra -- | ção. __ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        A -- | que -- le que | a -- qui ba -- | ti -- |za;
        Ba -- ti -- | zou \altcol no \altcol ri -- | o de Jor -- | dão. __ _
      }
    }
    theChords = \chordmode {
     \repeat volta 2 {
       s4 | c2. | g | c | c:7
       | f:maj7 | c | g | g2
     }
     \repeat volta 2 {
       s4 | f2. | g | c | a:m
       | c | g:7 | c | \mark \markup{\hspace #1 \super{"1"}} \parenthesize c2:7
     }
    }
    \layout { #(layout-set-staff-size 13) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    My Father I ask that You hear me, for me to ask for forgiveness
    I ask not only for me, but for me and my brothers and sisters
    \nextverse
    My Father when He forgives, he forgives as it befits Him
    I ask that You forgive us, as You forgave in Bethlehem
    \nextverse
    The boat which sails on the sea sails within my heart
    The one who baptizes here, is baptized in the Jordan River
  \end{translation}
\endsong


\beginsong{O Amor}[by={Padr. Sebastião}, key={D}, gk={D, D--D\shrp{}}]
  \audio[]{https://www.nossairmandade.com/hymn/11/OAmor}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1736s}
  \transpose{2}
  \newchords{chords_oamor_a}\newchords{chords_oamor_b}
  \mnbeginchorus\memorize[chords_oamor_a]
    \[^\mn{C}]O \[^\mn{E}]a|\[\mnc{G}C]mor é para \[\bmc\mn{A}]ser \[^\mn{G}]distri\[^\mn{E}]bu|\[^\mn{G}]ído \altchords{\id[1]{(C)}|C | \e}
    \[^\mn{C}]E \[\bmc\mn{E}]não \[^\mn{C}]amor \[^\mn{A}]fin|\[\mnc{G}G]gido por\[^\mn{B}]que \[\mncii{D}{C}F]ele \[^\mn{A}]cau\[^\mn{C}]sa |\[C]dor\[\bm] \altchords{|G F |C}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_oamor_b]
    \[^\mn{E}]O \[^\mn{G}]a|\[G]mor é o \[^\mn{B}]cam\[\bmc\mn{D}]po \[^\mn{C}]da \[^\mn{A}]for\[^\mn{C}]mo|\[\mnc{E}C]su\[^\mn{C}]ra \altchords{|G |C}
    Onde es\[\bmc\mn{A}]tá \[^\mn{G}]minha i\[^\mn{E}]ma\[^\mn{G}]gem |\[G]pu\[^\mn{C}]ra, \[\mnc{D}F]Deus \[^\mn{C}]foi \[^\mn{A}]quem \[^\mn{C}]cri|\[C]ou\[\bm] \altchords{|G F |C}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_oamor_a]
    O a|^mor é o ^trono da ver|dade \altchords{\id[4]{simples (D)}{|D | \e}}
    Onde es^tá a majes|^tade Cris^to Nosso Se|^nhor^ \altchords{|A |D}
    \endchorus\glueverses\beginchorus\replay[chords_oamor_b]
    O a|^mor de^ve ser bem pro|^fundo \altchords{|A |D}
    Mas não ^é em todo |^mundo, é para ^quem acredi|^tou^ \altchords{|A |D}
  \endchorus
  \beginchorus\replay[chords_oamor_a]
    O a|^mor é o ^trono da harmo|nia \altchords{\id[5]{MK (D)}|D | \e}
    A^onde eu des|^canso e ^rezo todo |^di^a \altchords{Bm |A A7 |D}
    \endchorus\glueverses\beginchorus\replay[chords_oamor_b]
    O a|^mor é da Sem^pre Virgem Ma|^ria \altchords{|A |Bm}
    Jesus ^Cristo Salva|^dor, ^Ele é quem nos |^gui^a \altchords{|A A7 |D}
  \endchorus
  \begin{translation}
    Love is to be shared; Not to be feigned because it causes pain
    Love is the field of beauty; Where my pure image is, it was God who created it
    \nextverse
    Love is the throne of truth; Where the majesty is Christ Our Lord
    Love must be very deep; But it is not in everyone, it's for those who believed
    \nextverse
    Love is the throne of harmony; Where I rest and pray every day
    Love is of the Ever Virgin Mary; Jesus Christ the Savior, it's He who guides me
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \transpose c d \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        c8 \posectionmark "A" e8 | g8.( g16) g8 g8 a8 g8 g8 e8 | g4( g8) c,8 e8 c8 c8 a8
        | g8.( \once\slurDown g16)( g8) b8 d8 c8 a8 c8 | c2( c4)
      } \break
      \repeat volta 2 {
        e,8 \sectionmark "B" g8 | \once\slurDown g8.( g16 g8) b8 d8 c8 a8 c8 | e8 c8 c8 c8 a8 g16( g16) e8 g8
        | g8( g8)( g8) \parenthesize c8 d8 c8 a8 c8 | c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        O a -- | mor é pa -- ra ser di -- stri -- bu -- | í -- do;
        E não a -- mor fin -- | gi -- do por -- que e -- le cau -- sa | dor. __ _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        O a -- | mor é o cam -- po da for -- mo -- | su -- ra;
        On -- de~es -- tá mi -- nha~i -- ma -- gem | pu -- _ _ ra Deus foi quem cri -- | ou. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        O a -- | mor __ _ é o tro -- no da ver -- | da -- de;~On --
        de~es -- tá a ma -- jes -- | ta -- _ de Cris -- to Nos -- so Se -- | nhor. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        O a -- | mor __ _ _ de -- ve ser bem pro -- | fun -- do;
        Mas não é em __ _ to -- do | mun -- do~é pa -- ra  quem a -- cre -- di -- | tou. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        O a -- | mor __ _ é o tro -- no da~har -- mo -- | ni -- _ a;~A --
        on -- de eu des -- | can -- _ _ so~e re -- zo to -- do | di -- a.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        O a -- | mor é da Sem -- pre Vir -- gem Ma -- | ri -- a;
        Je -- sus Cris -- to __ _ Sal -- va -- | dor __ _ _ \skip 1  E -- le~é quem nos | gui -- a.
      }
    }
    theChords = \transpose c d \chordmode {
      \repeat volta 2 {
        s4 | c1 | c1
        | g2 f2 | c2.
      }
      \repeat volta 2 {
        s4 | g1 | c1
        | g2 f2 | c2.
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Eu Não Sou Deus}[by={Padr. Sebastião},tags={perfilado, 2x}, key={D}, gk={D, D\shrp{}--F\shrp{}}]
  \audio[]{https://www.nossairmandade.com/hymn/12/EuN\%C3\%A3oSouDeus}
  \audio[key={F},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1857s}
  \newchords{chords_eunaosoudeus_a}\newchords{chords_eunaosoudeus_b}
  \transpose{2}
  \musicnotefornext{Tocar 2 vezes}
  \mnbeginchorus\memorize[chords_eunaosoudeus_a]
    \[^\mn{C}]Eu \[^\mn{A}]não \[^\mn{C}]sou |\[\mnc{E}C]Deus \altchords{\id[1]{(C)}|C}
    \[^\mn{C}]Mas \[\mnc{A}Am]tenho uma \[^\mn{E}]es\[^\mn{G}]pe|\[G]rança\[\bm] \altchords{Am |G}
    Eu \[^\mn{B}]não \[^\mn{D}]sou |\[\mnc{F}F]Deus \altchords{|F}
    \[^\mn{E}]Mas \[\bm\mn{A}]sou \[^\mn{C}]sua semel|\[C]hança\[\bm] \altchords{G |C}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eunaosoudeus_b]
    \ind \[^\mn{A}]Deus \[^\mn{C}]é |\[\mnc{E}C]fo\[^\mn{C}]go, \altchords{|C}
    \ind Deus é \[\bmc\mn{A}]á\[^\mn{G}]gua, \[^\mn{E}]Deus \[^\mn{G}]é |\[G]tudo \altchords{|G}
    \ind Eu con\[\bm]vido os \[^\mn{B}]meus \[^\mn{D}]ir|\[\mnc{F}F]mãos \altchords{|F}
    \ind Para co\[^\mn{E}]me\[\bm\mn{A}]çar \[^\mn{C}]nossos es|\[C]tudos\[\bm] \altchords{|C}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eunaosoudeus_a]
    Eu não sou |^Deus \altchords{\id[4]{MK (D)}|Bm}
    Mas ^tenho uma espe|^rança^ \altchords{|A}
    Eu não sou |^Deus \altchords{|G}
    Mas ^sou sua seme|^lhança^ \altchords{|D}
  \endchorus\glueverses\beginchorus\replay[chords_eunaosoudeus_b]
    \ind Deus no |^céu, \altchords{|Bm}
    \ind Deus na ^terra, Deus no |^mar \altchords{|A}
    \ind Eu con^vido os meus ir|^mãos \altchords{|G}
    \ind Para fi^car em seu lu|^gar ^ \altchords{|D}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \transpose c d \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        c8\posectionmark "A" a8 c8 | e4. c8 a8 a8 e8 g8 | g4 g4. g8 b8 d8
        | f4. e8 a,8 c8 c8 c8 | c4 c4.
      }
      \repeat volta 2 {
        r8 a8\sectionmark "B" c8 | e8. \altcol \parenthesize c16 \altmark "1." c8 c8 a8 g8 e8 g8 | g8.( g16) g8 g8 g8 g8 b8 d8
        | f8 f16( f16) f8 e8 a,8 c8 c8 c8 | c4( c4.)
      }
    }
    % no repeats in lyrics, as they make a mess when combined with the rest
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Eu não sou | Deus; Mas te -- nho~u -- ma~es -- pe -- | ran -- ça;
        Eu não sou | Deus; Mas sou sua se -- me -- | lhan -- ça. 
      \set stanza = "1.B"
        Deus é | fo -- \altcol go Deus é á -- gua Deus é | tu --  do;
        Eu con -- vi -- do~os meus ir -- | mãos; pa -- ra co -- me -- çar nos -- sos es -- | tu -- dos.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
        Eu não sou | Deus; Mas te -- nho~u -- ma~es -- pe -- | ran -- ça;
        Eu não sou | Deus; Mas sou sua se -- me -- | lhan -- ça.
      \set stanza = "2.B"
        Deus no | céu; \skip 1 Deus na ter -- ra Deus no | mar; __ _
        Eu con -- vi -- do~os meus ir -- | mãos; pa -- _ ra fi -- car em seu lu -- | gar. __ _
    }
    theChords = \transpose c d \chordmode {
      \repeat volta 2 {
        s4. | c2 a:m | g1 | f | c2~8
      }
      \repeat volta 2 {
        s4. | c1 | g | f | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I am not God; But I have a hope
    I am not God; But I am His likeness
    \nextverse
    God is fire; God is water, God is everything
    I invite my brothers and sisters; To begin our studies
    \nextverse
    I am not God; But I have a hope
    I am not God; But I am His likeness
    \nextverse
    God in heaven; God on earth, God in the sea
    I invite my brothers and sisters; To remain in their places
  \end{translation}
\endsong


\beginsong{Eu Pedi e Tive o Toque}[by={Padr. Alfredo}, off={Maria Sebastiana}, key={A}, gk={A, A--B}]
  \audio[]{https://www.nossairmandade.com/hymn/534/EuPediETiveOToque}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=2009s}
  \newchords{chords_eupedietive_a}\newchords{chords_eupedietive_b}
  \transpose{-3}
  \mnbeginchorus\memorize[chords_eupedietive_a]
    \[^\mn{E}]Eu \[^\mn{F}]pe|\[\mnc{G}C]di e \[\bmc\mn{C}]ti\[^\mn{A}]ve o |\[Fmaj7]to\[\bmc]que \altchords{\id[1]{(G)}|G |Cmaj7}
   \[^\mn{D}]Da \[^\mn{E}]Flo|\[\mnc{F}Dm]res\[^\mn{D}]ta e \[\mnc{G}C]do Ast|\[G]ral\[\bmc] \altchords{|Am G |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eupedietive_b]
    \[^\mn{C}]A\[^\mn{D}]qui |\[\mnc{E}C]estou \[\mnc{D}Dm7]a\[^\mn{C}]vi|\[\mnc{G}G]sando \altchords{|G Am7 |D}
    \[\bmc\mn{D}]Que \[^\mn{B}]de|\[^\mn{G}]vemos \[\mnc{D}G7]ser \[^\mn{E}]i|\[\mnc{C}C]gual\[\bmc] \altchords{| - D7 |G}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eupedietive_a]
    Exami|^nando o ^firma|^men^to
    O te|^souro u^niver|^sal ^
    \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Sinto |^profundo ^este |^toque
    ^Deste |Rei Im^peri|^al ^
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    Digo as|^sim es^clare|^cen^do \altchords{\id[4]{O (A)}|A |D}
    E mos|^trando a ^todos |^que ^ \altchords{|Bm |E}
    \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Es|^tá nes^{te ca}|^minho \altchords{|A Bm |E}
    ^Que pro|cure ^compreen|^der ^ \altchords{| - E7 |A}
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    Vou di|^zendo e ^quero |^ver ^
    Esta |^ora^ção vib|^rar ^
    \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    No co|^ração ^{de quem} |^ama
    ^Para |sempre ^confor|^tar ^
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    Digo |^sempre ^com fir|^me^za \altchords{\id[5]{MK (A)}|A |Dmaj7}
    Pois sou |^capaz ^de pro|^var ^ \altchords{|Bm7 |E}
    \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Quem é |^firme ^balan|^ceia \altchords{|A Bm7 |E}
    E ^quem zom|bar po^de tom|^bar ^ \altchords{| - E7 |A}
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    Esta |^força ^balan|^cei^a
    Faz as |^Estre^las bri|^lhar ^
    \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Foge o |^Vento ^das al|^turas
    ^Treme a |Terra e ^geme o |^Mar ^
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    A Meu |^Pai eu ^agra|^de^ço
    Por es|^ta com^preen|^são ^
    \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Todos |^busquem a ^Santa |^Paz
    ^Para |si e ^seus ir|^mãos ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \transpose c a, \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize e8 e8\posectionmark "A" f8 | g4 g4 c4 a8( a8) | a2( a4) d,8 e8
        | f4 d8( d8) g4 g4 | g2~8
      } \break
      \repeat volta 2 {
        r8 c,8\sectionmark "B" d8 | e4 e8( e8) d4 c4 | g'4.( g8) d4 b4
        | g'4. g8 d4 e8( e8) | c2~8
      }
    }
    % No repeats in lyrics, as they are incompatible with the rest starting B
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        \skip 1 Eu pe -- | di e ti -- ve o | to -- que;
        Da Flo -- | res -- ta e do As -- | tral. __ _
      \set stanza = "1.B"
        A -- qui | es -- tou __ _ a -- vi -- | san -- do;
        Que de -- | ve -- mos ser i -- _ | gual. __ _
    }
    %% Rest of the verses are commented out, to fit the whole song on one
    %% spread.
    % theLyricsTwo = \lyricmode {
    %   \set stanza = "2.A"
    %     E -- xa -- mi -- | nan -- do~o fir -- ma -- _ | men -- to;
    %     O te -- | sou -- ro u -- ni -- ver -- | sal. __ _
    %   \set stanza = "2.B"
    %     Sin -- to | pro -- fun -- do es -- te | to -- que;
    %     Des -- te | Rei Im -- pe -- ri -- _ | al. __ _
    % }
    % theLyricsThree = \lyricmode {
    %   \set stanza = "3.A"
    %     \skip 1 Di -- go~as -- | sim es -- cla -- re -- _ | cen -- do;
    %     E mos -- | tran -- do a to -- dos | que. __ _
    %   \set stanza = "3.B"
    %     Es -- _ | tá nes -- _ te ca -- | mi -- nho;
    %     Que pro -- | cu -- re com -- pre -- en -- | der. __ _
    % }
    % theLyricsFour = \lyricmode {
    %   \set stanza = "4.A"
    %     \skip 1 Vou di -- | zen -- do~e que -- ro __ _ | ver; __ _
    %     Es -- ta | o -- ra -- _ ção vib -- | rar. __ _
    %   \set stanza = "4.B"
    %     No co -- | ra -- ção __ _ de quem | a -- ma;
    %     Pa -- ra | sem -- pre con -- for -- _ | tar. __ _
    % }
    % theLyricsFive = \lyricmode {
    %   \set stanza = "5.A"
    %     \skip 1 Di -- go | sem -- pre com fir -- _ | me -- za;
    %     Pois sou | ca -- paz __ _ de pro -- | var. __ _
    %   \set stanza = "5.B"
    %     Quem é | fir -- me __ _ ba -- lan -- | cei -- a;~E
    %     quem zom -- | bar po -- de tom -- _ | bar. __ _
    % }
    % theLyricsSix = \lyricmode {
    %   \set stanza = "6.A"
    %     \skip 1 Es -- ta | for -- ça ba -- lan -- _ | cei -- a;
    %     Faz as | Es -- tre -- _ las bri -- | lhar. __ _
    %   \set stanza = "6.B"
    %     Fo -- ge~o | Ven -- to __ _ das al -- | tu -- ras;
    %     Tre -- me~a | Ter -- ra~e ge -- me o | Mar. __ _
    % }
    % theLyricsSeven = \lyricmode {
    %   \set stanza = "7.A"
    %     \skip 1 A Meu | Pai eu a -- gra -- _ | de -- ço;
    %     Por es -- | ta com -- _  pre -- en -- | são. __ _
    %   \set stanza = "7.B"
    %     To -- dos | bus -- quem a San -- ta | Paz; __ _
    %     Pa -- ra | si e seus ir -- _ | mãos. __ _
    % }
    theChords = \transpose c a, \chordmode {
      \repeat volta 2 {
        s4. | c1 | f:maj7
        | d2:m c | g2~8
      }
      \repeat volta 2 {
        s4. | c2 d2:m7 | g1
        | g2 g:7 | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 14) } % for all verses: 14
    \include "tex/lp-include-tail.ly" % for all verses: -lyricsbelow.ly
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    I asked and received the touch
    Of the forest and the Astral
    Here I am advising
    That we must be equal
    \nextverse
    Examining the firmament
    The universal treasure
    Deep inside I feel this touch
    Of this Imperial King
    \nextverse
    I say this clarifying
    And showing to everyone
    Who is on this path
    Should try to understand
    \nextverse
    I keep saying and I want to see
    This prayer vibrate
    In the heart of those who love
    Forever giving comfort
    \nextverse
    I always say with firmness
    For I am capable of proving
    Who is firm shakes
    And who mocks can fall down
    \nextverse
    This force shakes
    It makes the stars shine
    The wind of the heights flees
    The earth trembles and the sea groans
    \nextverse
    My Father I thank you
    For this comprehension
    Everyone seek the Holy Peace
    For themselves and their brothers and sisters
  \end{translation}
  \noendsongvfill % otherwise the horiz. line signifying song end wouldn't fit
\endsong


\beginsong{A Magia da Oração}[by={Madr. Nonata}, off={Madr. Júlia}, key={C}, gk={D, C--E}]
  \audio[]{https://www.nossairmandade.com/hymn/14/AMagiaDaOra\%C3\%A7\%C3\%A3o}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=2229s}
  \newchords{songs_amagiadaoracao_a}\newchords{songs_amagiadaoracao_b}
  \mnbeginchorus\memorize[songs_amagiadaoracao_a]
    \[^\mn{C}]Meu São \[^\mn{E}]Jo|\[\mnc{G}C]ão\[\bm], \[^\mn{E}]Meu \[^\mn{C}]São \[^\mn{E}]Jo|\[^\mn{G}]ão \[\bm] \altchords{\id[1]{(D)}|D | \e }
    \[^\mn{C}]Foi quem can|\[\mnc{E}Am]tou \[^\mn{C}]es\[\mnc{G}G]ta \[^\mn{D}]can|\[\mnc{C}C]ção \[\bm] \altchords{|Bm A |D}
    \mnendchorus\glueverses\mnbeginchorus\memorize[songs_amagiadaoracao_b]
    \[^\mn{C}]Para |\[\mnc{G}G]mim\[\bm] \[^\mn{C}]{e para} |\[\mnc{E}Em]ti \[\bm] \altchords{|A |F\shrp{}m}
    \[^\mn{G}]Na \[^\mn{C}]ma|\[\mnc{E}Am]gi\[^\mn{C}]{a da} \[\mnc{G}G7]O\[^\mn{D}]ra|\[\mnc{C}C]ção \[\bm] \altchords{|Bm A7 |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[songs_amagiadaoracao_a]
    Exa|^mi^{--ne} a consci|ên^cia
    E a|^calme seu ^cora|^ção ^
    \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    Atra|^vés ^da minha pa|^la^vra
    Refle|^tida na ^Ora|^ção ^
  \endchorus
  \beginchorus\replay[songs_amagiadaoracao_a]
    A meu |^Pa^i peço fir|me^za \altchords{\id[4]{MK (C)}|C | \e}
    E não sai|^o do ^meu lu|^gar ^ \altchords{|Am G7 |C}
    \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    Eu |^vi^{--vo} com meu |^Mes^tre \altchords{|Cmaj7 |Am}
    Na barca |^que cor^re no |^mar ^ \altchords{|C G7 |C}
  \endchorus
  \beginchorus\replay[songs_amagiadaoracao_a]
    É pe|^din^{--do} e ro|gan^do
    Que de|^vemos ^sempre es|^tar ^
    \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    As |^seis^ horas da |^tar^de
    Com a|^mor va^mos can|^tar ^
  \endchorus
  \beginchorus\replay[songs_amagiadaoracao_a]
    \noteson\[\mnlow{E}]Dem\notesoff |^Dum^, Dem Dum Dem |Dum^
    Eu não sou |^Deus mais te^nho espe|^ran^ça
    \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    Eu pe|^di^ e tive o |^toque
    ^Quen rezar com |^Deus nun^ca se |^can^sa
  \endchorus
  \beginchorus\replay[songs_amagiadaoracao_a]
    Estou re|^zan^do e sempre ze|lan^do
    Dentro |^do meu ^cora|^ção ^
    \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    O que o Se|^nhor^ deixou co|^migo
    ^A hora sa|^grada da ^Ora|^ção ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize c8\posectionmark "A" << c8 \parenthesize e8( \genmark "(5.)" >> e8) | g2( g8) e8 c8 e8 | g2( g8) \parenthesize c,8 c8 c8
        | e4 c8( c8) g4 d'4 | c2( c8)
      } \break
      \repeat volta 2 {
        \parenthesize c8\sectionmark "B"
        c8( c8) | g2( g8) c8 c8 c8 | e4.( \parenthesize e8)( \genmark "(5. & 6.)" e8) \parenthesize e8 g,8 c8
        | e4 c8( c8) g4 d'4 | c2( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Meu São Jo -- | ão __ _ Meu São Jo -- | ão; __ _
        Foi quem can -- | tou es -- _ ta can -- | ção; __ _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        \skip 1 Pa -- ra | mim __ _ e pa -- ra | ti; __ _ _ \skip 1
        Na ma -- | gi -- a da O -- ra -- | ção. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        \skip 1 E -- xa -- | mi -- _ ne~a cons -- ci -- | ên -- cia; \skip 1
        E a -- | cal -- me seu co -- ra -- | ção. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 A -- tra -- | vés da mi -- nha pa -- | la -- _ vra; \skip 1
        Re -- fle -- | ti -- da na O -- ra -- | ção. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        \skip 1 A meu | Pai __ _ pe -- ço fir -- | me -- za;
        E não sai -- | o do __ _ meu lu -- | gar. __ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 Eu __ _ | vi -- _ vo com meu | Mes -- _ tre;
        Na bar -- ca | que cor -- _ re no | mar. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        \skip 1 É pe -- | din -- _ do e ro -- | gan -- do;
        \skip 1 Que de -- | ve -- mos __ _ sem -- pre~es -- | tar. __ _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        \skip 1 As __ _ | seis __ _ ho -- ras da | tar -- _ de;
        \skip 1 Com a -- | mor va -- _ mos can -- | tar. __ _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        \skip 1 Dem __ _ | Dum __ _ Dem Dum Dem | Dum; __ _
        Eu não sou | Deus mais te -- nho~es -- pe -- | ran -- ça.
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        \skip 1 Eu pe -- | di __ _ e ti -- ve~o | to -- que;
        Quen re -- zar com | Deus nun -- _ ca se | can -- sa.
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \repeat volta 2 {
        Es -- tou re -- | zan -- do~e sem -- pre ze -- | lan -- do; \skip 1
        Den -- tro | do meu __ _ co -- ra -- | ção. __ _
      }
      \set stanza = "6.B"
      \repeat volta 2 {
        O que~o Se -- | nhor __ _ dei -- xou co -- | mi -- go;
        A ho -- ra sa -- | gra -- da da O -- ra -- | ção. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1 | c1
        | a2:m g | c2~ c8
      }
      \repeat volta 2 {
        s4. | g1 | e:m
        | a2:m g:7 | c2~ c8
      }
    }
    \layout { #(layout-set-staff-size 11) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    My Saint John, My Saint John, was who sang this song
    For me and for you, the magic of the Oração
    \nextverse
    Examine your conscience and calm your heart
    Through my word reflected in the Oração
    \nextverse
    My Father I ask for firmness, and I don't leave my place
    I live with my master, with the boat that sails on the sea
    \nextverse
    I am asking and praying, that we must always be
    At six in the afternoon, with love we will sing
    \nextverse
    Dem Dum, Dem Dum Dem Dum, I am not God but I have hope
    I ask and receive the touch, because God never tires
    \nextverse
    I am praying and always caring for within my heart
    But you Lord left with me, this is the hour of the Oração
  \end{translation}
\endsong


\beginsong{Recebendo}[by={Odemir Raulino da Silva}, off={Francinete Oliveira}, tags={valsa}, key={C}, gk={D, C--E}]
  \audio[key=D]{https://www.nossairmandade.com/hymn/1527/Recebendo}
  \audio[key={C},title={Play for Daime}]{https://www.youtube.com/watch?v=jJItq9efhqM}
  \meter{3}{4}
  \mnbeginchorus\memorize
    \lrep \[^\mn{G}]Rece|\[C]ben\[^\mn{E}]do \[^\mn{D}]no |\[^\mn{C}]meu \[^\mn{B}]co\[^\mn{C}]ra|\[\mncii{D}{A}Dm]ção | \e \altchords{\id[1]{(D)}|D | - |Em | \e}
    \[^\mn{F}]U\[^\mn{D}]ma |\[\mncii{B}{G}G]flor |\[\mnc{F}G7]que \[^\mn{E}]me \[^\mn{D}]con|\[\mnc{C}C]for|te \rrep \altchords{|A |A7 |D | \e}
    \lrep Agra|\[\mnc{A}F]deço por |tudo \[^\mn{B}]de |\[\mncii{C}{G}C]bom |\[A7] \e \altchords{|G | - |D |B7}
    \[^\mn{E}]Deus \[^\mn{D}]nos |\[\mnc{G}Dm]liv\[^\mn{F}]re \[^\mn{D}]do |\[\mnc{G}G7]que \[^\mn{B}]é \[^\mn{D}]a |\[\mnc{C}C]mor|te \rrep \altchords{|Em |A7 |D | \e }
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep Esta |^é uma |mensagem |^boa | \e
    Para |^nós vi|^ver consci|^en|te \rrep
    \lrep Aumen|^tai a nos|sa ale|^gria |^ \e
    E na tris|^teza um fi|^nal para |^sem|pre \rrep
  \endchorus
  \beginchorus
    \lrep É mais |^isto que eu |tenho a di|^zer | \e
    No meu |^ponto e|^spiritu|^al | \e \rrep
    \lrep Deus nos |^cubra com |a vossa |^glória |^ \e
    E nas mal|^dades um |^ponto fi|^nal | \e \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-08
    theMelody = \relative g'' {
      \key c \major \time 3/4 \partial 2
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        g4\posectionmark "A" g4 | g4 e4 d4 | c4 b4 c4 | d4( a2~) | a4
        f'4 d4 | b2( g4) | f'4 e4 d4 | c2.( | c4)
      }
      \repeat volta 2 {
        c4\sectionmark "B" c4 | a4 a4 a4 | a4 a4 b4 | c4( g2~) | g8
        \parenthesize e'8 \genmark "(2. & 3.)" e4 d4 | g4 f4 d4 | g,4 b4 d4 | c2.( | c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Re -- ce -- | ben -- do no | meu co -- ra -- | çã -- o; __ _
        U -- ma | flor __ _ | que me con -- | for -- | te.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        A -- gra -- | de -- ço por | tu -- do de | bom; __ _ _ \skip 1
        Deus nos | liv -- re do | que é a | mor -- | te.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Es -- ta | é u -- ma | men -- sa -- gem | bo -- a; __ _
        Pa -- ra | nós vi -- | ver con -- sci -- | en -- | te.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Au -- men -- | tai a nos -- | sa a -- le | gri -- a; __ _
        E na tris -- | te -- za~um fi -- | nal pa -- ra | sem -- | pre.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        É mais | is -- to que~eu | te -- nho~a di -- | zer; __ _ _
        No meu | pon -- to~e -- | spi -- ri -- tu | al. __ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Deus nos | cub -- ra com | a vos -- sa | gló -- ria; __ _
        E nas mal -- | da -- des um | pon -- to fi -- | nal. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | c2. | c2. | d:m | d:m
        | g | g:7 | c | c4
      }
      \repeat volta 2 {
        s2 | f2. | f | c | a:7
        | d:m | g:7 | c | c4
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Receiving in my heart a flower that comforts me
    I give thanks to all that is good; God free us from that which is death
    \nextverse
    This is a good message for us to live consciously
    Increase our joy, and for sadness an end forever
    \nextverse
    This is more of what I have to say at my spiritual point
    God cover us with your glory, and for wickedness a final ending
  \end{translation}
\endsong
