% Santo Daime: Hinos da Concentração
% ==================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Firmeza}[by={Padr. Sebastião},tags={à capela},key={A},sks={A, B}]
  \audio{https://www.nossairmandade.com/hymn/15/Firmeza}
  \mnbeginchorus
    \[\mn{C#}]Fir|\[\mnc{E}A]me\[\mn{C#}]za, \[\mn{A}]fir|\[\mn{E}]me\[\mn{A}]za \[\mn{B}]no \[\mn{C#}]a|\[\mnc{D}D]mor \altchords{\id[2]{MK (A)}|A |A7 |D}
    \[\mn{E}]Fir|\[\mnc{G#}E]me\[\mn{E}]za, \[\mn{F#}]fir|\[\mn{G#}]me\[\mn{E}]za a\[\mn{F#}]on\[\mn{G#}]de es\up{1}(|\[\mnc{C#}A]tou) \up{2}(\meter{6}{4}|\[\mnc{C#}A]tou) \altchords{|E |E7 |A}
  \mnendchorus\glueverses\mnbeginchorus
    \meter{4}{4}
    \ind \[\mn{A}]Eu \[\mn{B}]es\[\mn{C#}]tou |\[\mnc{D}D]firme com meu Je|sus \altchords{|D |Bm}
    \ind \[\mn{F#}]Eu estou |\[\mnc{A}A]fir\[\mn{A}]me \[E]nes\[\mn{B}]ta |\[\mnc{C#}A]luz \altchords{|A |F\#m \e}
    \ind \[\mn{E}]A\[\mnc{D}E7]on\[\mn{B}]de es|\[\mnc{A}A]tou \altchords{E7 |A}
  \mnendchorus
  \mnbeginchorus
    \[\mn{C#}]Fir|\[\mnc{E}A]me\[\mn{C#}]za, \[\mn{A}]fir|\[\mn{E}]me\[\mn{A}]za \[\mn{B}]no \[\mn{C#}]a|\[\mnc{D}D]mor \altchords{|A |A7 |D}
    \[\mn{E}]Fir|\[\mnc{G#}E]me\[\mn{E}]za, \[\mn{F#}]fir|\[\mn{G#}]me\[\mn{E}]za a\[\mn{F#}]on\[\mn{G#}]de es\up{1}(|\[\mnc{C#}A]tou) \up{2}(\meter{6}{4}|\[\mnc{C#}A]tou) \altchords{|E |E7 |A}
  \mnendchorus\glueverses\mnbeginchorus
    \meter{4}{4}
    \ind \[\mn{A}]O \[\mn{B}]Mes\[\mn{C#}]tre |\[\mnc{D}D]manda eu traba|lhar \altchords{|D |Bm}
    \ind \[\mn{F#}]O Mestre |\[\mnc{A}A]man\[\mn{A}]da eu \[E]me \[\mn{B}]fir|\[\mnc{C#}A]mar \altchords{A |F\#m}
    \ind No \[\mn{D}]lu|\[\mnc{E}E7]gar \[\mn{D}]on\[\mn{B}]de E\[\mn{C#}]le es|\[\mnc{A}A]tá \altchords{|E7 A}
  \mnendchorus
  \begin{translation}
    Firmness, firmness in love
    Firmness, firmness where I am
    I am firm with my Jesus
    I am firm in this light
    Where I am
    \nextverse
    Firmness, firmness in love
    Firmness, firmness where I am
    The Master orders me to work
    The Master orders me to firm myself
    In the place where he is
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lilypond-settings-include.ly"
    \layout { #(layout-set-staff-size 14) } % to fit all on one spread
    theMelody = \relative c'' {
      \key a \major \time 4/4 \partial 4
      \repeat volta 2 {
        cis4 | e2 cis4 a | e' a, b cis | d2.
        d4 | gis2 e4 fis4 | gis e fis gis
      } \alternative { { | cis,2. } { \time 6/4 | cis2. a4 b cis } }
      \time 4/4
      \repeat volta 2 {
        | d4 d8 d d4 d | d4. fis8 fis4 fis
        | a a, a b | cis e d b
      } \alternative { { | a4. a8 b4 cis } { | a2. cis4 } }
      \repeat volta 2 {
        | e2 cis4 a | e' a, b cis | d2. e4
        | gis2 e4 fis | gis e fis gis
      } \alternative { { | cis,2. e4 } { \time 6/4 | cis2. a4 b cis } }
      \time 4/4
      \repeat volta 2 {
        | d4 d8 d d4 d | d4. fis8 fis4 fis
        | a4 a,8 a a4 b | cis2 cis4 d | e d b cis
      } \alternative { { | a4. a8 b4 cis } { | a2.} }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        \set stanza = "1. "
        Fir -- me -- za fir -- me -- za no a -- mor;
        Fir -- me -- za fir -- me -- za_a -- on -- de_es-
      } \alternative { { tou; } { tou. Eu es -- tou } }
      \repeat volta 2 {
        fir -- me com meu Je -- sus;
        Eu es -- tou fir -- me nes -- ta luz;
        Aon -- de es-
      } \alternative { { tou; Eu es -- tou } { tou. \set stanza = "2." Fir- } }
      \repeat volta 2 {
        me -- za fir -- me -- za no a -- mor;
        Fir -- me -- za fir -- me -- za_a -- on -- de_es-
      } \alternative { { tou; Fir- } { tou. O Mes -- tre } }
      \repeat volta 2 {
        man -- da eu tra -- ba -- lhar;
        O Mes -- tre man -- da eu me fir -- mar;
        No lu -- gar on -- de_E le_es-
      } \alternative { { tá; O Mes -- tre } { tá. } }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a1 | a | d
        | e | e
      } \alternative { { | a2. } { | a1. } }
      \repeat volta 2 {
        | d1 | d | a2 e2 | a2 e2:7
      } \alternative { { | a1 } { | a1 } }
      \repeat volta 2 {
        | a1 | a | d
        | e | e
      } \alternative { { | a1 } { | a1. } }
      \repeat volta 2 {
        | d1 | d | a2 e2 | a1 | e2:7 e2:7
      } \alternative { { | a1 } { | a2. \bar "|." } }
    }
    \include "tex/lilypond-score-chords-melody-tabs.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Eu Estou Firme com meu Jesus}[by={Padr. Sebastião},tags={2x},key={D},sks={D, E}]
  \audio{https://www.nossairmandade.com/hymn/16/EuEstouFirmeComMeuJesus}
  \newchords{chords_euestoufirme_a}\newchords{chords_euestoufirme_b}
  \musicnote{Play 2 times}
  \mnbeginchorus\memorize[chords_euestoufirme_a]
    \[^\mn{A}]Eu estou |\[\mnc{D}D]firme \[^\mn{C#}]com \[\mnc{B}Bm]meu \[^\mn{A}]Je|\[\mnc{D}D]sus
    \[^\mn{A}]Foi \[^\bm]Ele \[^\mn{D}]quem \[^\mn{E}]me |\[\mnc{F#}Bm]deu esta \[\mnc{E}A7]San\[^\mn{F#}]ta |\[\mnc{D}D]Luz
  \mnendchorus
  \mnbeginchorus\memorize[chords_euestoufirme_b]
    \ind \[^\mn{A}]Esta |\[\mnc{D}D]luz é da \[^\mn{C#}]Vir\[\mnc{B}Bm]gem \[^\mn{A}]da \[^\mn{F#}]Con\[^\mn{A}]cei|\[\mnc{D}D]ção
    \ind \[^\mn{A}]Foi \[^\bm]Ela \[^\mn{D}]quem \[^\mn{E}]man|\[\mnc{F#}Bm]dou eu me u\[\mnc{E}A7]nir \[^\mn{D}]com \[^\mn{F#}]meus \[^\mn{E}]ir|\[\mnc{D}D]mãos
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_euestoufirme_a]
    Foi \[\bm]Ela quem man|^dou eu me u^nir \noteson\[\mnlow{A}]com \[\mnlow{F#}]meus \[\mnlow{A}]ir \notesoff |^mãos
    Pa\[\bm]ra a reuni|^ão da se^para|^ção
  \endchorus
  \beginchorus\replay[chords_euestoufirme_b]
    \ind Neste |^dia Muita ^gente vai cho|^rar
    \ind Por\[\bm]que tem muitos |^deles que não ^sa\noteson\[\mnlow{E}]bem \[\mnlow{F#}]a\notesoff|^mar
  \endchorus
  \begin{translation}
    I am firm with my Jesus
    It was he who gave me this holy light
    \nextverse
    This light is of the Virgin of Conception
    It was She who sent me to unite with my brothers and sisters
    \nextverse
    It was She who sent me to unite with my brothers and sisters
    For the reunion from the separation
    \nextverse
    On this day many people will cry
    Because there are many who don't know how to love
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lilypond-settings-include.ly"
    \layout { #(layout-set-staff-size 15) } % to fit all on one spread
    theMelody = \relative d'' {
      \key d \major \time 4/4 \partial 1*5/8
      \repeat volta 2 {
         r4  a8 a a | d4 d8 cis b4 a | d4. a8 a a d e | fis4 fis8 fis e4 fis | d4.
      }
      \repeat volta 2 {
        r4. a8 a | d d d cis b a fis a | d4. a8 a a d e | fis fis fis fis e d fis e | d4.
      }
      \repeat volta 2 {
        a8 a a a a | d d d cis b a fis a | d4. a8 a a d e | fis4 fis8 fis e4 fis | d4.
      }
      \repeat volta 2 {
        r4. a8 a | d d d cis b a fis a | d4. a8 a a d e | fis fis fis fis e4 fis | d4.
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
      \set stanza = "1. "
        Eu es -- tou fir -- me com meu Je -- sus;
        Foi E -- le quem me deu es -- ta san -- ta luz.
        Es -- ta luz é da Vir -- gem da Con -- cei -- ção;
        Foi E -- la quem man -- dou eu me u -- nir com meus ir -- mãos.
      }
      \repeat volta 2 {
      \set stanza = "2. "
        Foi E -- la quem man -- dou eu me u -- nir com meus ir -- mãos;
        Pa -- ra a reu -- ni -- ão da se -- pa -- ra -- ção;
        Nes -- te di -- a mui -- ta gen -- te vai cho -- rar;
        Por -- que tem mui -- tos de -- les que não sa -- bem_a -- mar.
      }
    }
    theChords = \chordmode {
      s2 s8 | d2 b:m | d d | b:m a:7 | d d
      | d b:m | d d | b:m a:7 | d d
      | d b:m | d d | b:m a:7 | d d
      | d b:m | d d | b:m a:7 | d4.
    }
    \include "tex/lilypond-score-chords-melody-tabs.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\scleardpage
\beginsong{Eu Vivo Neste Mundo}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio{https://www.nossairmandade.com/hymn/17/EuVivoNesteMundo}
  \mnbeginchorus\memorize
    \[^\mn{G}]Eu |\[\mnc{C}C]vivo nes\[^\mn{E}]te |\[\mnc{G}(G)]mundo
    En\[^\mn{A}]quan|\[\mnc{F}Dm]to \[^\mn{E}]che\[\mnc{D}G7]ga \[^\mn{E}]meu |\[\mnc{C}C]diz
  \mnendchorus\glueverses\mnbeginchorus
    \[\mn{G}]Encos|\[\mnc{C}C]ta\[\mn{G}]do \[\mn{C}]a \[\mn{E}]meu |\[\mnc{G}(G)]Mestre
    E a \[\mn{A}]Sem|\[\mnc{F}Dm]pre \[\mn{E}]Vir\[\mnc{D}G7]gem \[\mn{E}]Ma|\[\mnc{C}C]ria
  \mnendchorus
  \notesoff
  \beginchorus
    Meu |^Mes\noteson\[\mnlow{G}]tre \notesoff é quem me |^guia
    Meu |^Mestre é ^quem me en|^sina
  \endchorus\glueverses\beginchorus
    Foi |^E\noteson\[\mnlow{G}]le \notesoff quem me |^deu
    Es|^ta San^ta Dou|^trina
  \endchorus
  \beginchorus
    Foi |^E\noteson\[\mnlow{G}]le \notesoff quem me |^deu
    Foi |^Ele quem ^me man|^dou
  \endchorus\glueverses\beginchorus
    Can|^tar \noteson\[\mnlow{G}]com os \notesoff meus ir|^mãos
    Ensi|^nar e ^ter a|^mor
  \endchorus
  \beginchorus
    |^Pa\noteson\[\mnlow{G}]ra \notesoff ter o a|^mor
    E sen|^tir no ^cora|^ção
  \endchorus\glueverses\beginchorus
    Ro|^gar \noteson\[\mnlow{G}]ao \notesoff Pai E|^terno
    Para rece|^ber o ^meu per|^dão
  \endchorus
  \brk
  \beginchorus
    |^Pa\noteson\[\mnlow{G}]ra \notesoff ter o per|^dão
    E tra|^balhar ^com a|^mor
  \endchorus\glueverses\beginchorus
    Pres|^tar \noteson\[\mnlow{G}]bem \notesoff aten|^ção
    Os en|^sinos do ^profes|^sor
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lilypond-settings-include.ly"
    \layout { #(layout-set-staff-size 15) } % to fit all on one spread
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4
      #(define afterGraceFraction (cons 1 4))
      \repeat volta 2 {
         g4 | c << g4 \parenthesize c >> c e |
         \set melismaBusyProperties = #'() \slurDown \slurDashed 
         g4.( g8 g4 )
         \unset melismaBusyProperties
         a | f \grace{\parenthesize f8} \afterGrace e4 {\parenthesize e8} d4 e
         \set melismaBusyProperties = #'() \slurDown \slurDashed
         | c2( c4)
         \unset melismaBusyProperties
      } \break
      \repeat volta 2 {
         g4 | c << \parenthesize g4 c >> c e |
         \set melismaBusyProperties = #'() \slurDown \slurDashed
         g4.( g8 g4 )
         \unset melismaBusyProperties
         a | f \grace{\parenthesize f8} \afterGrace e4 {\parenthesize e8} d4 e
         \set melismaBusyProperties = #'() \slurDown \slurDashed
         | c2( c4)
         \unset melismaBusyProperties
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Eu vi -- \parenthesize vo nes -- te mun -- do;
      en -- quan -- to che -- ga meu diz. __ _
      \set stanza = "1.b"
      Encos -- ta -- do a meu Mes -- tre;
      e_a Sem -- pre Vir -- gem Ma -- ri -- a.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Meu Mes -- tre_é quem me gui -- a;
      meu Mes -- tre (é_quem) me en -- si -- na.
      \set stanza = "2.b"
      Foi E -- le quem me deu; __ _ _
      es -- ta San -- ta Dou -- tri -- na.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Foi E -- le quem me deu; __ _ _
      foi E -- (le_quem) me man -- dou. __ _
      \set stanza = "3.b"
      Can -- tar com_os meus ir -- mãos; __ _
      en -- si -- nar e ter a -- mor. __
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 Pa -- ra ter o_a -- mor; __ _
      e sen -- tir no co -- ra -- ção. __ _
      \set stanza = "4.b"
      Ro -- gar ao Pai E -- terno;_pa --
      ra re -- ce -- ber o meu per -- dão. __
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \skip 1 Pa -- ra ter o_per -- dão; __ _
      e tra -- ba -- lhar com a -- mor. __ _
      \set stanza = "5.b"
      Pres -- tar bem a -- ten -- ção; __ _
      os en -- si -- (nos_do) pro -- fes -- sor. __
    }
    theChords = \chordmode {
      s4 | c1 | \parenthesize g | d2:m g:7 | c2.
      s4 | c1 | \parenthesize g | d2:m g:7 | c2.
    }
    \score {
      <<
        \new ChordNames { \theChords }
        \new Staff { \clef "treble" \new Voice = "theVoice" { \theMelody } }
        \new Lyrics = "lyricsOne" \lyricsto "theVoice" \theLyricsOne
        \new Lyrics = "lyricsTwo" \lyricsto "theVoice" \theLyricsTwo
        \new Lyrics = "lyricsThree" \lyricsto "theVoice" \theLyricsThree
        \new Lyrics = "lyricsFour" \lyricsto "theVoice" \theLyricsFour
        \new Lyrics = "lyricsFive" \lyricsto "theVoice" \theLyricsFive
        \new TabStaff { \clef "moderntab" \transpose d'' d \theMelody }
      >>
    }
  \end{lilypond}\end{lilywrap}
  \begin{translation}\scriptsize % to fit on one spread
    I live in this world until my day comes
    Next to my Master and the Ever Virgin Mary
    \nextverse
    It is my Master who guides me, it is my Master who teaches me
    It was he who gave me this Holy Doctrine
    \nextverse
    It was he who gave me, it was he who sent me
    To sing with my brothers and sisters, to teach and to have love
    \nextverse
    To have love and to feel in the heart
    Pray to the Eternal Father to receive my forgiveness
    \nextverse
    To receive forgiveness and to work with love
    Pay attention closely to the teachings of the professor
  \end{translation}
\endsong


\beginsong{Todos Devem}[by={Germano Guilherme},tags={2x},key={Em},sks={F\#m, Em}]
  \audio[key=F\#m]{https://www.nossairmandade.com/hymn/18/TodosDevem}
  \newchords{chords_todosdevem_a}\newchords{chords_todosdevem_b}
  \musicnote{Play 2 times}
  \mnbeginchorus\memorize[chords_todosdevem_a]
    \[^\mn{B}]Todos |\[Em]devem pro\[\mnc{A}(Am)]cu|\[\mncii{C}{B}Em]rar \altchords{\id[1]{(F\#m)} |F\#m (Bm) |F\#m}
    Ter fir|\[Em]meza e ter \[\mnc{A}(Am)]a|\[\mncii{C}{B}Em]mor \altchords{|F\#m (Bm) |F\#m}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_todosdevem_b]
    O que o |\[\mncii{C}{B}B7]Mestre \[^\mn{B&}]nos \[^\mn{B}]en|\[\mncii{G}{F#}Em]sina \altchords{|C\#7 |F\#m}
    \[^\mn{E}]A minha |\[\mnc{D#}B7]Mãe foi \[^\mn{B}]quem \[^\mn{F#}]man|\[\mnc{E}Em]dou \altchords{|C\#7 |F\#m}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_todosdevem_a]
    O |^Mestre, Ele ^en|^sina
    Para |^todos seus ^ir|^mãos
  \endchorus\glueverses\beginchorus\replay[chords_todosdevem_b]
    Bem gra|^var e ter fir|^meza
    Dent|^ro do cora|^ção
  \endchorus
  \beginchorus\replay[chords_todosdevem_a]
    O |^Mestre, Ele ^en|^sina \altchords{\id[2]{MK (Em)}|Em B7 |Em}
    Para |^bem se ter ^a|^mor \altchords{|- B7 |Em}
  \endchorus\glueverses\beginchorus\replay[chords_todosdevem_b]
    Bem gra|^var e ter fir|^meza \altchords{|Am B7 |Em}
    Em nos|^so Pai Cria|^dor \altchords{|B7 |Em}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lilypond-settings-include.ly"
    theMelody = \relative b' {
      \key e \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        r8 b8 b8 | b4 b b a | c4( b2)
        b8 b8 | b4 b b a | c4( b4.)
      }
      \repeat volta 2 {
        \parenthesize b8 b8 b8 | c4 b bes b | g' fis4.
        \parenthesize e8 e e | dis4 dis b fis' | e2~ e8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        To -- dos de -- vem pro -- cu -- rar; __
        Ter fir -- me -- za_e ter a -- mor. __
      }
      \repeat volta 2 {
        O que o Mes -- tre nos en -- si -- na;
        A mi -- nha Mãe foi quem man -- dou. __
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        O __ _ Mes -- tre_E -- le en -- sina; __
        Pa -- ra to -- dos seus ir -- mãos.
      }
      \repeat volta 2 {
        \skip 1 Bem gra -- var e ter fir -- me -- za;
        \skip 1 Den __ -- \skip 1 tro do co -- ra -- ção. __
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        O __ _ Mes -- tre_E -- le en -- sina; __
        Pa -- ra bem se ter a -- mor.
      }
      \repeat volta 2 {
        \skip 1 Bem gra -- var e ter fir -- me -- za;
        \skip 1 Em nos -- so Pai Cri -- a -- dor. __
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | e2.:m \parenthesize a4:m | e1:m
        | e2.:m \parenthesize a4:m | e2:m e8:m
      }
      \repeat volta 2 {
        s4.| b1:7 | e:m
        | b:7 | e2:m e8:m
      }
    }
    \score {
      <<
        \new ChordNames { \theChords }
        \new Staff { \clef "treble" \new Voice = "theVoice" { \theMelody } }
        \new Lyrics = "lyricsOne" \lyricsto "theVoice" \theLyricsOne
        \new Lyrics = "lyricsTwo" \lyricsto "theVoice" \theLyricsTwo
        \new Lyrics = "lyricsThree" \lyricsto "theVoice" \theLyricsThree
        \new TabStaff { \clef "moderntab" \transpose d'' d \theMelody }
      >>
    }
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    All must seek to have firmness and to have love
    What the Master teaches us, my Mother was who sent this
    \nextverse
    The Master He teaches all his brothers
    To engrave well and have firmness within the heart
    \nextverse
    The Master He teaches us to really have love
    Engrave well and have firmness in our Father Creator
  \end{translation}
\endsong


\beginsong{Tábuas de Moisés}[by={Padr. Sebastião}]
  \audio{https://www.nossairmandade.com/hymn/19/T\%C3\%A1buasDeMois\%C3\%A9s}
  \newchords{chords_tabuasdemoises_a}\newchords{chords_tabuasdemoises_b}
  \transpose{2}
  \mnbeginchorus\memorize[chords_tabuasdemoises_a]
    \[^\mn{B}]Meus \[^\mn{D}]ir|\[\mnc{G}G]mãos \[^\mn{F#}]eu \[\mnc{E}D]vou \[^\mn{D}]lem|\[\mnc{G}G]brar
    \[\mnc{B}Em]O \[^\mn{E}]que |\[\mnc{D}D]nin\[^\mn{C}]guém \[^\mn{A}]se \[^\mn{B}]lem|\[\mnc{G}G]brou
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_tabuasdemoises_b]
    \[^\mn{D}]Meu |\[\mnc{A}Am]Pai \[^\mn{C}]e \[\mncii{B}{A}D]minha |\[\mnc{G}G]Mãe
    \[^\mn{B}]Tan\[^\mn{D}]to |\[\mnc{A}Am]que \[^\mn{C}]re\[\mnc{B}D]co\[^\mn{A}]men|\[\mnc{G}G]dou
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_tabuasdemoises_a]
    As |^Tábuas ^de Moi|^sés
    ^Que o |^meu Pai entre|^gou
  \endchorus\glueverses\beginchorus\replay[chords_tabuasdemoises_b]
    Não |^ligar^am impor|^tância
    Não con|^sagra^ram o a|^mor
  \endchorus
  \beginchorus\replay[chords_tabuasdemoises_a]
    Me ve|^jo cont^rari|^ado
    ^Com o |^povo brasi|^leiro
  \endchorus\glueverses\beginchorus\replay[chords_tabuasdemoises_b]
    Querem |^que o ^meu Pai |^faça
    Como |^faz lá ^no estran|^geiro
  \endchorus
  \beginchorus\replay[chords_tabuasdemoises_a]
    Não sei o |^que o ^povo |^pensa
    ^Que de |^tudo se esque|^ceu
  \endchorus\glueverses\beginchorus\replay[chords_tabuasdemoises_b]
    Amam |^mais a ^ilu|^são
    Do que |^meu Pai ^verda|^deiro
  \endchorus
  \begin{translation}
    My brothers and sisters I'm going to remember
    That which nobody remembered
    My Father and my Mother
    Much recommended it
    \nextverse
    The tablets of Moses
    That my Father entrusted to them
    They didn't care
    They didn't consecrate love
    \nextverse
    I am disappointed
    With the Brazilian people
    They want my Father to do
    As is done abroad
    \nextverse
    I don't know what the people think
    For they have forgotten everything
    They love illusion more
    Than my true Father
  \end{translation}
\endsong


\beginsong{O Valor que o Mestre Tem}[by={Padr. Sebastião}]
  \newchords{chords_ovalorqueomestre_a}\newchords{chords_ovalorqueomestre_b}
  \mnbeginchorus\memorize[chords_ovalorqueomestre_a]
    \[^\mn{G}]O va|\[\mnc{C}C]lor \[^\mn{E}]que o \[^\mn{D}]Mest\[^\mn{E}]re |\[^\mn{C}]tem
    \[^\mn{E}]Eu |\[^\mn{G}]vou \[^\mn{E}]es\[\mncii{A}{C}F]clare|\[\mnc{E}C]cer
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_ovalorqueomestre_b]
    \[^\mn{D}]Se ti\[^\mn{E}]ver |\[\mnc{F}Fmaj7]alguém \[^\mn{D}]que \[^\mn{E}]du|\[\mnc{C}C]vide
    \[^\mn{B}]To\[^\mn{A}]me |\[\mnc{G}G]Daime \[^\mn{E}]pa\[^\mn{D}]ra |\[\mnc{C}C]ver
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_ovalorqueomestre_a]
    Meu |^Mestre veio ao |mundo
    Nas|ceu lá ^no estran|^geiro
    \endchorus\glueverses\beginchorus\replay[chords_ovalorqueomestre_b]
    O va|^{lor que} o Mestre |^tem
    Não se |^compra com din|^heiro
  \endchorus
  \beginchorus\replay[chords_ovalorqueomestre_a]
    Meu |^Mestre é for|moso
    É pre|ciso a^credi|^tar
    \endchorus\glueverses\beginchorus\replay[chords_ovalorqueomestre_b]
    Eu con|^{vido os} meus ir|^mãos
    Vamos |^todos acompan|^har
  \endchorus
  \beginchorus\replay[chords_ovalorqueomestre_a]
    Meu |^Mestre a ti eu |peço
    Na |minha con^centra|^ção
    \endchorus\glueverses\beginchorus\replay[chords_ovalorqueomestre_b]
    Para |^{vós me} conso|^lar
    E con|^solar meus ir|^mãos
  \endchorus
  \beginchorus\replay[chords_ovalorqueomestre_a]
    Meu |^Mestre a ti eu |peço
    Faça de |mim o ^que qui|^ser
    \endchorus\glueverses\beginchorus\replay[chords_ovalorqueomestre_b]
    Meu |^Mestre estou a|^qui
    E te pro|^meto ser fi|^el
  \endchorus
  \begin{translation}
    The worth that the Master has
    I am going to clarify
    If someone is doubtful
    Take Daime to see
    \nextverse
    My Master came to the world
    He was born in a foreign land
    The worth that my Master has
    Cannot be bought with money
    \nextverse
    My Master is beautiful
    One must believe
    I invite my brothers and sisters
    Let‘s all accompany Him
    \nextverse
    My Master I ask You
    In my concentration
    For You to console me
    And console my brothers and sisters
    \nextverse
    My Master I ask You
    Do with me as you please
    My Master here I am
    I promise to be loyal
  \end{translation}
\endsong
