% Santo Daime: Hinos de Larva (Unilaiva)
% ======================================
%

\audio{https://soundcloud.com/unilarva/sets/transparencia-hinario}


% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{O Ego}[by={larva}, key={Am}, gk={Am, Gm--G\shrp{}m--(Am)}]
  \audio[key=Am]{https://soundcloud.com/unilarva/o-ego?in=unilarva/sets/transparencia-hinario}
  \mnbeginchorus\memorize
    \[^\mn{E}]Na i|\[\mnc{A}Am]gre\[\bm]ja, o |\[^\mn{C}]e\[^\mn{B}]go \[^\mn{A}]se \[\mnc{G}Am7]re\[^\mn{F}]ve\[^\mn{E}]la |\[\mnc{D}Dm]for\[\bm]te; | \e
    Mas \[\bmc\mn{C}]não \[^\mn{B}]vou \[^\mn{E}]m|\[Am]ais \[\bmc\mn{C}]resis\[^\mn{B}]t|\[E]ir, não \[\bmc\mn{C}]vou \[^\mn{B}]com\[^\mn{A}]pe|\[Am]tir. \[A7]
    Em |\[\mnc{D}Dm]to\[\bm]dos, | ve\[\bmc\mn{E}]jo \[^\mn{F}]a\[^\mn{E}]m|\[Am]{or ---} \[^\mn{C}]um \[\bm]dom da \[^\mn{B}]s|\[E]orte ---
    \[^\mn{A}]No \[\bmc\mn{B}]co\[^\mn{A}]ra\[^\mn{B}]ç|ão, a \[E7]luz \[^\mn{C}]que |\[\mnc{B}Am]vai \[^\mn{A}]brilh\[\bm]ar. |{ }{ }\[\bm]{ }{ }{ } \e
  \mnendchorus
  \notesoff
  \beginchorus
    Não |^que^ro |jogos de ^poder, só |^paz;^ | \e \altchords{\id[1]{(Gm)}|Gm | - Gm7 |Cm | \e}
    A ^conex|^ão ^e o am|^or vou ^priori|^zar. ^ \altchords{|Gm |D |Gm G7}
    Nas |^al^mas, | en^contro a l|^uz que i^lumin|^a; \altchords{|Cm | - |Gm |D}
    E as ^difer|enças ^vão se |^dissip^ar. |{ }{ }^{ }{ }{ } \e \altchords{| - D7 |Gm | \e}
  \endchorus
  \beginchorus
    Na i|^gre^ja e |fora de^{la, vou} o|^lhar:^ | \e
    A ^chama a b|^on^-da|^de que es^tá lá, no |^ser.
    A ^necessi|^da^de | de ^control|^e vai se ^dissip|^ar;
    Na bus^ca do am|or,^ vou |^renasc^er. |{ }{ }^{ }{ }{ } \e
  \endchorus
  \beginchorus
    A compreen|^são ^{ }{ } |nos leva ^{a transcen}|^der;^ | \e
    Os ^problem|^as ^se diss|^ol-^vem no o|^lhar. ^
    Atra|^vés ^ |{ } ^do am|^or, va^mos cresc|^er;
    Na ^paz do \noteson\[\mnlow{B}]San\[\mnlow{A}]to \notesoff|Daime, ^ vou |^medit^ar. |{ }{ }^{ }{ }{ } \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-10
    % \header {
    %   title = "Sou Daime, Sou um espelho"
    %   subtitle = "Transparência #1"
    %   composer = "Lari Natri (2023-10)"
    %   copyright = "CC BY-NC-SA 4.0"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \key a \minor \time 4/4 \partial 4.
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        \parenthesize e8 \pomark e8( e8) | a2(
        a4.) \parenthesize a8 | \tuplet 3/2 2 { c4 b4 a } \tuplet 3/2 2 { g f e } d2( d2)~
        | d4 d4 c b8 e8~ | \once\slurUp e2 \single\altcol ( << \single\altcol e4 \altmark "3." ) c4 >> c8 \single\slurUp\single\altcol ( << \single\altcol c8) \altmark "3." b8( >> | b4) b4 \tuplet 3/2 2 { c4 b4 a4 } | a4.( a8)( a8) \parenthesize a8( a8)( a8)
        | d2( d2)~ | d4 d4 e f8 e8~ | e4 \parenthesize c8 c8 c4 c8 b8~
        | b4 b8 a8 b8( b8) << a8 \altmark "4." \single\altcol b8 >> << \single\altcol a8 b8( >> | b4)( b8)( \parenthesize b8) \parenthesize b4 c4 | b4 a8 a8~ a2~ | a2~ 8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 Na i -- | gre -- ja, o | e -- go se re -- ve -- la | for -- te; | _
        Mas não vou mais __ | _ re -- sis -- tir, __ | _ não vou com -- pe -- | tir. __ _ _
        \skip 1 Em __ _ | to -- dos, | _ ve -- jo a -- mor— | _ \skip 1 um dom da sor | _ -- te—
        No co _ -- ra -- ção, __ | _ _ a luz que | vai bri -- lhar. _ | _ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        \skip 1 Não __ _ | que -- ro \skip 1 | jo -- gos de po -- der, só | paz; __ _ | _
        A co -- ne -- xão __ | _ e o~a -- mor __ | _ vou pri -- o -- ri -- | zar. __ _ _
        \skip 1 Nas __ _ | al -- mas, | _ en -- con -- tro~a luz | _ \skip 1 que~i -- lu -- mi -- na; | _
        E as di _ -- fe -- ren | _ _ -- ças vão se | dis -- si -- par. _ | _ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        \skip 1 Na i -- | gre -- ja e | fo -- ra de -- la, vou o -- | lhar: __ _ | _
        A cha -- ma~a bon -- | _ _ \altcol da _ -- | de que~es -- tá lá, no | ser.
        A ne -- ces _ -- si -- | da -- de | _ de con -- tro -- le | _ vai se dis -- si -- par; | _
        Na bus -- ca __ _ do~a -- mor, __ | _ _ \skip 1 \skip 1 vou | re -- nas -- cer. _ | _ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        A com -- preen -- | são __ _ \skip 1 | nos le -- va a trans -- cen -- | der; __ _ | _
        Os pro -- ble -- mas __ | _ se dis -- sol | _ _ -- vem no o -- | lhar. __ _ _
        \skip 1 A -- tra -- | vés __ _ | _ _ do a -- mor, |  _ \skip 1 va -- mos cres -- cer; | _
        \skip 1 Na paz do \altcol San -- \altcol to | Dai -- me, __ _ \skip 1 vou | me -- di -- tar. _ | _ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4.
        | a1:m | a2:m a2:m7 | d1:m | d1:m | a1:m
        | e1 | a2:m a2:7 | d1:m | d1:m | a1:m
        | e1 | e2 e2:7 | a1:m | a2:m~ 8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    In the church, the ego reveals its might;
    But I won't resist no more, I won't compete.
    In everyone, I see love --- a gift (of luck) ---
    In the heart, a light that shines.
    \nextverse
    I don't want power games, just peace;
    I'll prioritize connection and love.
    In every soul, a light that illuminates;
    And differences will fade.
    \nextverse
    In the church and out, I will see:
    The flame of kindness that is there, in existence.
    The need to control will dissipate;
    In the quest for love, I'll be born again.
    \nextverse
    Understanding leads us to transcendence;
    Problems dissolve in it's gaze.
    Through love we will grow;
    In the peace of Santo Daime, I'll meditate.
  \end{translation}
\endsong


\beginsong{Sou Daime, Sou um Espelho}[by={larva}, key={Am}, gk={Bm, (Bm)--(Cm)}]
  \audio[key=Am]{https://soundcloud.com/unilarva/sou-daime-sou-um-espelho?in=unilarva/sets/transparencia-hinario}
  \mnbeginchorus\memorize
    |\[\mnc{A}Am]Sou \[A\up{sus2}]{}\[^\mn{B}]Dai|\[\mnc{D}A\up{sus4}]me, \[Am]{}\[^\mn{C}]{} |\[\mnc{B}A\up{sus2}]sou \[Am]{}\[^\mn{C}]um es|\[\mncii{B}{A}A\up{sus2}]{pe}lho \[Am]
    \[^\mn{E}]Pa|\[\mnc{A}Am]ra \[A\up{sus2}]{}\[^\mn{B}]{te mos}|\[\mnc{D}A\up{sus4}]trar \[Am]{}\[^\mn{C}]{} |\[\mnc{B}A\up{sus2}]a \[Am]{}\[^\mn{C}]ti |\[\mncii{B}{A}A\up{sus2}]{mes}mo \[Am]
    Se esti|\[\mnc{D}Dm]ve\[\bm]res | dis\[\mnc{E}D\up{sus2}]pos\[^\mn{F}]{to a} |\[\mncii{A}{E}Am]ver \[A\up{sus2}] |\[Am] \[A\up{sus2}]{} \e
    Se esti|\[\mnc{B}Em]ve\[\bm]res | dis\[\mnc{D}E7]pos\[^\mn{C}\mn{B}]{to a} |\[\mnc{A}Am]ver \[A\up{sus2}] |\[Am] \[A\up{sus2}]{} \e
  \mnendchorus
  \notesoff
  \beginchorus
    |^Sou ^ Dai|^me, ^ |^sou ^ um por|^tal ^
    Pa|^ra ^ mun|^dos ^ re|^ais ^ e imagi|^nados ^
    Deves jul|^gar ^ |{ }{ } ^qual é |^qual ^ |^ ^ \e
    Deves jul|^gar ^ |{ }{ } ^qual é |^qual ^ |^ ^ \e
  \endchorus
  \beginchorus
    |^Sou ^ Dai|^me, ^ |^sou ^ A|^mor ^
    |^E ^ tam|^bém ^ |^és ^ |^tu ^
    A|^mor ^ | per^meia |^tu^do |^ ^ \e
    A|^mor ^ | per^meia |^tu^do |^ ^ \e
  \endchorus
  \beginchorus
    |^Sou ^ Dai|^me, ^ con|^fi ^{-} a em |^mim, ^
    No |^U ^{-} ni|^ver ^{-} |^so, ^ em ti |^mesmo ^
    E se|^rás ^ | a^benço|^a^do |^ ^ \e
    E se|^rás ^ | a^benço|^a^do |^ ^ \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2024-01
    % \header {
    %   title = "Sou Daime, Sou um espelho"
    %   subtitle = "Transparência #2"
    %   composer = "Lari Natri (2024-01)"
    %   copyright = "CC BY-NC-SA 4.0"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative e' {
      \key a \minor \slurDashed
      \set melismaBusyProperties = #'()
      \tempo 4 = 116
      \time 4/4
      \repeat volta 2 {
        | a2. \pomark b4 | d2.( c4) | b2. c8( c8) | \once\slurSolid b8( a8)( a2)
        %\break
        \parenthesize e4 | a2. b8( b8) | d2.( c4) | b2~ b8( \altcol \parenthesize c8 \altmark "2." c8)( c8) | \once\slurSolid b8( a8)( a4.)
        %\break
        \parenthesize a8 a8( a8) | d2( d2~) | d4( d4) e4 f4 | \once\slurSolid a4.( e8)( e2~) | e2~ e8
        %\break
        \parenthesize e8[ e8( e8)] | b2( b2~) | b4( b4) d4 c8( b8) | a2( a2~) | a1
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        | Sou Dai -- | me, __ _ | sou um es -- | pe -- _ lho;
        Pa -- | ra te mos -- | trar __ _ | a _ \skip 1 ti __ _ | mes -- _ mo;
        Se es -- ti -- | ve -- res __ | _ dis -- pos -- to~a | ver; __ _ _ | _ _
        Se es -- ti -- | ve -- res __ | _ dis -- pos -- to a | ver. __ _ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        | Sou Dai -- | me, __ _ | sou um por -- | tal; __ _ _
        Pa -- | ra mun -- _ | dos re -- | ais _ \altcol e~i -- ma -- gi -- | na -- _ dos;
        De -- ves jul -- | gar __ _ | _ _ qual é | qual; __ _ _ | _ _
        De -- ves jul -- | gar __ _ | _ _ qual é __ _ | qual. __ _ | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        | Sou Dai -- | me, __ _ | sou A -- _ | mor; __ _ _
        \skip 1 | E tam -- _ | bém __ _ | és __ _ _ _ _ | tu; __ _ _
        \skip 1 A -- _ | mor __ _ | _ per -- mei -- a | tu -- _ do; | _ _
        \skip 1 A -- _ | mor __ _ | _ per -- mei -- a __ _ | tu -- do. | _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        | Sou Dai -- | me, con -- | fi -- a em | mim, __ _ _
        No | U -- ni -- _ | ver -- _ | so, _ \skip 1 em ti | mes -- _ mo;
        \skip 1 E se -- | rás __ _ | _ a -- ben -- ço -- | a -- _ do; | _ _
        \skip 1 E se -- | rás __ _ | _ a -- ben -- ço -- _ | a -- do. | _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        | a2:m a:sus2 | a:sus4 a:m | a:sus2 a:m | a:sus2 a:m
        | a:m a:sus2 | a:sus4 a:m | a:sus2 a:m | a:sus2 a:m
        | d:m d:m | d:m d:sus2 | a:m a:sus2 | a:m a:sus2
        | e:m e:m | e:m e:7 | a:m a:sus2 | a:m a:sus2
      }
    }
   % \layout { #(layout-set-staff-size 15) } % for better fit
   \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I am Daime; I am a mirror to show you yourself,
    If you're willing to see, if you're willing to see.
    \nextverse
    I am Daime; I am a portal to worlds real and imagined.
    You must judge which is which, you must judge which is which.
    \nextverse
    I am Daime; I am Love, and so are you.
    Love permeates everything, love permeates everything.
    \nextverse
    I am Daime; trust me, the Universe, yourself,
    And you will be blessed, and you will be blessed.
  \end{translation}
\endsong


\beginsong{O Espírito de Tudo}[by={larva}, key={Gm}, gk={Gm}, tags={2x}]
  \newchords{chords_o_espirito_de_tudo_a}\newchords{chords_o_espirito_de_tudo_b}
  \textnotefornext{Tocar 2 vezes. / Sing twice.}
  \mnbeginchorus\memorize[chords_o_espirito_de_tudo_a]
    \[\bmc\mn{D}]O \[^\mn{E&}\mn{F#}]es|\[\mnc{G}Gm]pírito \[\bm]de \[^\mn{B&}]tu\[^\mn{A}]do \[^\mn{G}]{se en}|\[\mnc{F#}D]con\[^\mn{D}]tra
    \[\bmc\mn{E&}]quan\[^\mn{D}]do \[^\mn{C#}]es\[^\mn{D}]que|\[\mnc{B&}B&]cemos de \[\bm]ser \[^\mn{A}]es\[^\mn{B&}]piri\[^\mn{C#}]tu|\[\mnc{D}D]al
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_o_espirito_de_tudo_b]
    \[\bmc\mn{D}]O \[^\mn{E&}]a|\[\mnc{C#}F\shrp{}m/C\shrp{}]{mor en} \[\bm]toda \[^\mn{E&}]cria|\[\mnc{D}Gm]ção
    na \[\bm]vul\[^\mn{C#}]nera\[^\mn{B&}]bi\[^\mn{C#}]li|\[\mnc{A}D]da de \[\bm]se \[^\mn{D}]re|\[\mnc{G}Gm]vela
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_o_espirito_de_tudo_a]
    ^Sagrados es|^tamos ^quando exis|^timos
    ^sem esconder |^nossos a^bismos nem vergo|^nhas
    \endchorus\glueverses\beginchorus\replay[chords_o_espirito_de_tudo_b]
    ^Apren|^demos aos ^poucos a ver|^dade ver
    ^ser mais reais |^é o que há ^de vi|^ver
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2024-01
    \include "tex/lp-include-head.ly"
    % \header {
    %   title = "O Espírito de Tudo"
    %   composer = "Lari Natri"
    % }
    theMelody = \relative d'' {
      \key g \minor \slurDashed
      \set melismaBusyProperties = #'()
      \tempo 4 = 108
      \time 4/4 \partial 2
      \repeat segno 2 {
        \sectionLabel "A"
        \repeat volta 2 {
          d8( \pomark d8) es8( fis8)
          | g4( g8) g8 g8 bes a g | fis4. d8 es8 d cis d
          | bes4 bes8 bes8 bes a16( a) bes16( bes) cis8 | d2
        }
        \sectionLabel "B"
        \repeat volta 2 {
          d4 es4
          | cis4( cis8) cis8 cis8 cis8 es8 es8 | d4( d8) d8 d8 cis16( cis16) bes8 cis
          | a8( \parenthesize a8 \parenthesize a8) a8 a4 d | g,4( g4)
        }
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      O __ _ es -- _ | pí -- ri -- to de tu -- do se~en -- | con -- tra,
      quan -- do es -- que -- | ce -- mos de ser es -- _ pi -- ri -- tu -- | al.
      \set stanza = "1.B"
      O a --  | mor __ _ en to -- da cri -- a -- | ção, __ _
      na vul -- ne -- ra -- bi -- li -- | da -- _ _ de se re -- | ve -- la.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Sa -- gra -- dos es -- | ta -- _ mos quan -- do e -- xis -- | ti -- mos
      sem es -- con -- der | nos -- sos a -- bis -- mos nem ver -- _ go -- | nhas.
      \set stanza = "2.B"
      A -- pren -- | de -- mos aos pou -- cos a ver -- | da -- de ver,
      ser mais __ _ re -- ais | é o que há de vi -- | ver. __ _
    }
    theChords = \chordmode {
      \repeat segno 2 {
        \repeat volta 2 {
          s2 | g1:m | d | bes | d2
        }
        \repeat volta 2 {
          s2 | fis1:m/cis | g:m | d | g2:m
        }
      }
    }
%     \layout { #(layout-set-staff-size 15) } % for better fit
   \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    The spirit of everything is found when we forget to be spiritual.
    Love in all creation, in vulnerability it is revealed.
    \nextverse
    We are sacred when we exist without hiding our abysses or shames.
    We gradually learn to see the truth, being more real is what there is to live.
  \end{translation}
\endsong

