% Santo Daime: closing for São Miguel & Mesa Branca works
% =======================================================
%


% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Em Pé Firme na Floresta}[by={Padr. Alfredo}, tags={perfilado, 3x, mazurca}, off={Tratorista}, key={Am}, sks={Am, G\shrp{}m--(Am)}]
  \audio{https://www.nossairmandade.com/hymn/551/EmP\%C3\%A9FirmeNaFloresta}
  \newchords{chords_empefirme_a}\newchords{chords_empefirme_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_empefirme_a]
    \[^\mn{E}]Em pé |\[\mnc{A}Am]fir\[^\mn{E}]me \[^\mn{C}]na \[^\mn{B}]Flo\[\bmc\mn{A}]res\[^\mn{E}]ta
    \[^\mn{C}]Re\[^\mn{A}]ce|\[\mnc{C}E7]ben\[^\mn{B}]do a \[^\mn{A}]san\[^\mn{G#}]ta \[\mnc{A}Am]Luz
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_empefirme_b]
    \[^\mn{A}]Sou \[^\mn{B}]hu|\[\mnc{C}Am]mil\[^\mn{E}]de, \[^\mn{D}]sou \[^\mn{C}]hu\[Fmaj7]mil\[^\mn{B}]de
    \[^\mn{G#}]Sou \[^\mn{B}]hu|\[\mnc{E}E7]mil\[^\mn{D}]de \[^\mn{C}]de \[^\mn{B}]Je\[\mnc{A}Am]sus
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_empefirme_a]
    O im|^pério destas ^matas
    Não e|^xiste força mai^or
    \endchorus\glueverses\beginchorus\replay[chords_empefirme_b]
    Agora a|^qui peço fir^meza
    As Es|^trelas, a Lua e ao ^Sol
  \endchorus
  \beginchorus\replay[chords_empefirme_a]
    To|^quei a minha cor^neta
    Já é a |última cha^mada
    \endchorus\glueverses\beginchorus\replay[chords_empefirme_b]
    Se per|^filem coman^dantes
    Para |^vencer a jor^nada
  \endchorus
  \beginchorus\replay[chords_empefirme_a]
    Esta |^força verda^deira
    É o |^reinado do ^Sol
    \endchorus\glueverses\beginchorus\replay[chords_empefirme_b]
    Em |^cima vivem os ^astros
    E em|^baixo vivem os ^paus
  \endchorus
  \beginchorus\replay[chords_empefirme_a]
    Oh! Meu |^Pai onipo^tente
    Que me dá |^força e me se^gura
    \endchorus\glueverses\beginchorus\replay[chords_empefirme_b]
    Para |^eu ser Vosso ^filho
    E me li|^vrar das amar^guras
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 6/4 \partial 4.
      \repeat volta 2 {
        r8 \posectionmark "A" e8( e)
        | a4 e8( e) c'8 b  a4 e8( e) c8 a
        | c4 b8( b) a gis  a4( a8)
      }
      \repeat volta 2 {
        \parenthesize a8 \sectionmark "B" a( b)
        | c4 e d8 c  c4 b8( b) gis b
        | e8( e) d( d) c b  a4( a8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Em pé | fir -- me __ _ na Flo -- res -- ta; __ _
        Re -- ce -- | ben -- do a san -- ta Luz. __ _
      \set stanza = "1.B"
        \skip 1 Sou hu -- | mil -- de, sou hu -- mil -- de; __ _
        Sou hu -- | mil -- _ de _ de Je -- sus. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
        O im -- | pé -- rio __ _ des -- tas ma -- tas; __ _
        Não e -- | xis -- te for -- ça mai -- or. __ _
      \set stanza = "2.B"
        A -- go -- ra~a -- | qui pe -- ço fir -- me -- za; __ _
        As Es -- | tre -- las, a Lu -- a~e ao Sol. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
        To -- _ | quei a mi -- nha cor -- ne -- ta; __ _
        Já é~a | úl -- ti -- _ ma cha -- ma -- da.
      \set stanza = "3.B"
        \skip 1 Se per -- | fi -- lem co -- man -- dan -- tes; __ _
        Pa -- ra | ven -- _ cer __ _ a jor -- na -- da.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
        Es -- ta | for -- ça __ _ ver -- da -- dei -- ra; __ _
        É o | rei -- na -- _ do do Sol. __ _
      \set stanza = "4.B"
        \skip 1 Em __ _ | ci -- ma vi -- vem~os as -- tros; __ _
        E em -- | bai -- _ xo __ _ vi -- vem~os paus. __ _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
        Oh! Meu | Pai o -- _ ni -- po -- ten -- te;
        Que me dá | for -- ça e me se -- gu -- ra.
      \set stanza = "5.B"
        \skip 1 Pa -- ra | eu ser Vos -- so fi -- lho
        E me li -- | vrar __ _ das __ _ a -- mar -- gu -- ras.
      }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a2.:m a:m | e:7 a4.:m
      }
      \repeat volta 2 {
        s4. | a2.:m f:maj7 | e:7 a4.:m
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Standing firm in the forest, receiving the Holy Light
    I am huble, I am huble, I am humble of Jesus
    \nextverse
    The Empire of these forests; no force is greater than this
    Now here I ask for firmness; from the stars, the Moon and the Sun
    \nextverse
    I sounded my trumpt; it's already th last call
    Stand up straight, commanders, in order to overcome the journey
    \nextverse
    This true force is the kingdom of the Sun
    In the heights dwell the heavenly bodies, and down here dwell the logs
    \nextverse
    Oh! My Omnipotent Father who gives me strength and secures me
    For me to be Your son, and to deliver me from bitterness
  \end{translation}
\endsong
