% Santo Daime: Hinos Diversos da Concentração
% ===========================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Firmado em Concentração}[by={Padr. Alfredo},tags={valsa}, key={Am}, gk={Am, G\shrp{}m--Am}]
  \audio{https://www.nossairmandade.com/hymn/538/FirmadoEmConcentra\%C3\%A7\%C3\%A3o}
  \meter{3}{4}
  \mnbeginchorus\memorize
    |\[\mncii{C}{A}Am]Firmad\[^\mn{E}]{o em} |\[^\mn{C}]con\[^\mn{A}]cen\[^\mn{C}]tra|\[^\mn{E}]ção | \e
    |\[^\mn{C}]Na \[^\mn{A}]Vir\[^\mn{E}]gem |\[\mnc{C#}A7]Mãe ver\[^\mn{E}]da|\[\mnc{D}Dm]dei|ra
    \lrep \[^\mn{A}]Eu |\[\mnc{D}Dm]vou ol|\[^\mn{F}]hand\[^\mn{E}]{o e} dou |\[\mnc{C}Am]chan\[^\mn{A}]ce
    A |\[^\mn{E}]quem ol|\[\mnc{B}E7]har pa\[^\mn{D}]ra |\[^\mn{G#}]esta \[^\mn{B}]ban|\[\mnc{A}Am]dei|\[\up{1}A7]ra \rrep
  \mnendchorus
  \notesoff
  \beginchorus\replay
    |^Vou publi|car umas pa|la|vras
    |Que nos traz |^pura lem|^bran|ça
    \lrep Das |^cores |desta ban|^deira
    Do |Pai verda|^deiro, ver|de azul e |^bran|^ca \rrep
  \endchorus
  \beginchorus\replay
    |^Firmado |no verde |lin|do
    |Sou eu, re|^presento a |^Ter|ra
    \lrep Por |^isto a|qui eu es|^tou
    Com a |paz do Se|^nhor, acal|mando a |^guer|^ra \rrep
  \endchorus
  \beginchorus\replay
    |^Firmado |neste a|zul | \e
    Es|ta imen|^sidão ce|^les|te
    \lrep Faz |^calmar o |meu cora|^ção
    E |dos meus ir|^mãos, os |que não es|^que|^cem \rrep
  \endchorus
  \beginchorus\replay
    |^Lembranças |vivas de |Deus | \e
    |Nos traz o |^branco do As|^tral | \e
    \lrep Com |^todos |seres do |^alto
    Que |nos ilu|^mina jun|tamente ao |^Sol |^ \e \rrep
  \endchorus
  \beginchorus\replay
    |^Completei |esta li|ção | \e \altchords{\id[4]{MK (Am)} |Am | |E | \e}
    |Com justi|^ça e leal|^da|de \altchords{|Am |A7 |Dm | \e}
    \lrep Para |^todos |se reu|^nir \altchords{|Dm | |Am}
    Pro|vando a|^qui sua |capaci|^da|^de \rrep \altchords{| - |Bm7\flt{}5 |E7 |Am |\up{1}A}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, latest update on 2024-03
    theMelody = \relative c''' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4
        \sectionLabel "A"
        | c4 \pomark a e | c a c | e2.( | e2)( e4)
        | c'4 a e | cis cis e | d2.( | d4)
      \repeat volta 2 {
        \sectionLabel "B"
        \altcol \parenthesize a4 a4 | d4( d4) d4 | f e e
        | c \parenthesize a \genmark "(1., 2., 5.)" a | e'4( e4) e4
        | b( b) d | gis, gis b | a2.(
      } \alternative {
        { | a4) }
        { | a2. \repeatTie \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      | Fir -- ma -- do~em | con -- cen -- tra -- | ção; __ _ _
      | Na Vir -- gem | Mãe ver -- da -- | dei -- ra.
      \repeat volta 2 {
        \set stanza = "1.B"
        \skip 1 Eu | vou __ _ o -- | lhan -- do~e dou | chan -- ce;
        A | quem __ _ o -- | lhar pa -- ra | es -- ta ban -- | dei --
      } \alternative {
        { | ra. }
        { | ra. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      | Vou pu -- bli -- | car~u -- mas pa -- | la -- | vras; __ _
      | Que nos traz | pu -- ra lem -- | bran -- | ça.
      \repeat volta 2 {
        \set stanza = "2.B"
        \skip 1 Das | co -- _ res | des -- ta ban -- | dei -- ra;
        Do | Pai ver -- da -- | dei -- ro, ver -- | de~a -- zul e | bran --
      } \alternative {
        { | ca. }
        { | ca. }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      | Fir -- ma -- do | no ver -- de | lin -- | do; __ _
      | Sou eu, re -- | pre -- sen -- to~a | Ter -- | ra.
      \repeat volta 2 {
        \set stanza = "3.B"
        \skip 1 Por | is -- to a -- | qui eu es -- | tou; \skip 1
        Com~a | paz do Se -- | nhor, a -- cal -- | man -- do a | guer --
      } \alternative {
        { | ra. }
        { | ra. }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      | Fir -- ma -- do | nes -- te a -- | zul; __ _
      Es -- | ta i -- men -- | si -- dão ce -- | les -- | te.
      \repeat volta 2 {
        \set stanza = "4.B"
        \skip 1 Faz | cal -- mar o | meu co -- ra -- | ção; \skip 1
        E | dos meus ir -- | mãos, __ _ os | que não es -- | que --
      } \alternative {
        { | cem. }
        { | cem. }
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      | Lem -- bran -- ças | vi -- vas de | Deus; __ | _ _
      | Nos traz o | bran -- co do~As -- | tral. __ | _
      \repeat volta 2 {
        \set stanza = "5.B"
        \skip 1 Com | to -- _ dos | se -- res do | al -- to;
        Que | nos i -- lu -- | mi -- na jun -- | ta -- men -- te~ao | Sol.
      } \alternative {
        { | \skip 1 }
        { | \skip 1 }
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      | Com -- ple -- tei | es -- ta li -- | ção; __ | _ _
      | Com jus -- ti -- | ça~e le -- al -- | da -- | de.
      \repeat volta 2 {
        \set stanza = "6.B"
        \altcol Pa -- ra | to -- _ dos | se re -- u -- | nir; \skip 1
        Pro -- | van -- do a -- | qui su -- a | ca -- pa -- ci -- | da --
      } \alternative {
        { | de. }
        { | de. }
      }
    }
    theChords = \chordmode {
      | a2.:m | a:m | a:m | a:m
      | a:m | a:7 | d:m | d4:m
      \repeat volta 2  {
        \set chordChanges = ##f
        s2 | d2.:m
        \set chordChanges = ##t
        | d:m | a:m | a:m
        | e:7 | e:7 | a:m
      } \alternative {
        { | a4:7 }
        { | a2.:m }
      }
    }
    \layout { #(layout-set-staff-size 12) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    Firmed in concentration, in the true Virgin Mother
    I keep looking and I give opportunity to those who look for this banner
    \nextverse
    I will announce some words that bring us pure remembrance
    Of the colors of this banner of the true Father, green, blue and white
    \nextverse
    Firmed in the beautiful green, I represent the Earth
    For this I am here, with the peace of the Lord calming the war
    \nextverse
    Firmed in this blue, this celestial immensity
    Calms my heart and of my brothers, those who don‘t forget
    \nextverse
    Living memories of God bring us the white of the Astral
    With all Beings of the heights who illuminate us together with the Sun
    \nextverse
    I completed this lesson with justice and loyalty
    For everyone to be reunited, proving thus their capacity
  \end{translation}
\endsong


\beginsong{Firmeza}[by={Padr. Valdete}, key={F}, gk={F, C--B}]
  \audio{https://www.nossairmandade.com/hymn/148/Firmeza}
  \mnbeginchorus\memorize
    \[^\mn{C}]Fir|\[\mnc{F}F]meza, bem fir\[\bmc\mnc{C}C]meza peço |\[\mnc{F}F]em concentra\[\bmc\mnc{C}C]ção \altchords{\id[1]{(G)}|G D |G D}
    \[^\mn{F}]Fir|\[F]me\[^\mn{C}]za, \[C]bem \[^\mn{F}]fir\[\bmc{}F]me\[^\mn{C}]za \[C]na cor|\[\mnc{F}F]rente da ses\[\bmc]são \altchords{|G D G D |G}
  \mnendchorus
  \notesoff
  \beginchorus
    Fir|^meza, bem fir^meza, peço ao |^Rei Jurami^dam
    Fir|^meza, ^bem fir^meza, ^para eu |^sempre ser seu ^fã
  \endchorus
  \beginchorus
    Fir|^meza, bem fir^meza, peço |^a Virgem Ma^ria \altchords{\id[2]{(E)}|E B |E B}
    Fir|^meza, ^bem fir^meza, ^que Vós |^seja minha ^Guia \altchords{|E B E B |E}
  \endchorus
  \beginchorus
    Fir|^meza, bem fir^meza, peço ao |^Senhor São Jo^ão
    Fir|^meza, ^bem fir^meza, ^para eu |^seguir na mis^são
  \endchorus
  \beginchorus
    Fir|^meza, bem fir^meza, peço ao |^Pai da Cria^ção
    Vós me |^dê Paz ^e A^mor, e ^apla|^nai meu cora^ção
  \endchorus
  \beginchorus
    Apla|^nai meu cora^ção, para |^eu poder a^mar
    E as o|^fenças ^dos ir^mãos, ^ eu |^saber perdo^ar
  \endchorus
  \beginchorus
    Sa|^bendo perdo^ar, se|^guindo nesta ^Luz
    Pa|^ra po^der di^zer, ^que es|^tou com meu Je^sus
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, latest update on 2024-03
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key f \major \time 4/4 \partial 8
      \repeat volta 2 {
        \grace \parenthesize c8 \genmark "6." c8 \pomark | f8. f16 f8. f16 c8.( c16)( c8.) c16 | f8. f16 f8. f16 c4( c8) f8
        | f8. c16 c8. f16 f8. c16 c8. c16 | f8. f16 f8. f16 f4( f8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
        Fir -- | me -- za bem fir -- me -- za pe -- ço | em con -- cen -- tra -- ção; __ _
        Fir -- | me -- za bem fir -- me -- za na cor -- | ren -- te da ses -- são. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
        Fir -- | me -- za, bem fir -- me -- za, pe -- ço~ao | Rei Ju -- ra -- mi -- dam; __ _
        Fir -- | me -- za, bem fir -- me -- za, pa -- ra~eu | sem -- pre ser seu fã. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
        Fir -- | me -- za, bem fir -- me -- za, pe -- ço | a Vir -- gem Ma -- ri -- a;
        Fir -- | me -- za, bem fir -- me -- za, que Vós | se -- ja mi -- nha Gui -- a.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
        Fir -- | me -- za, bem fir -- me -- za, pe -- ço~ao | Se -- nhor São Jo -- ão; __ _
        Fir -- | me -- za, bem fir -- me -- za, pa -- ra~eu | se -- guir na mis -- são. __ _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
        Fir -- | me -- za, bem fir -- me -- za, pe -- ço~ao | Pai da Cri -- a -- ção;
        Vós me | dê Paz e A -- mor, e a -- pla -- | nai meu co -- ra -- ção. __ _
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      \set includeGraceNotes = ##f
        (A)pla -- | nai meu co -- ra -- ção, __ _ pa -- ra | eu po -- der a -- mar;
        E~as o -- | fen -- ças dos ir -- mãos, \skip 1 \skip 1 eu | sa -- ber per -- do -- ar. __ _
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7."
        Sa -- | ben -- do per -- do -- ar, __ _ _ se -- | guin -- do nes -- ta Luz; __ _
        Pa -- | ra po -- der di -- zer, \skip 1 que es -- | tou com meu Je -- sus. __ _
    }
    theChords = \chordmode {
      % No repeat here nor in the lyrics, as it would leave the grace note outside
        s8 | f2 c | f c
        | f4 c f c | f2.~ f8
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Firmness, great firmness, I ask in concentration
    Firmness, great firmness, in the current of the session
    \nextverse
    Firmness, great firmness, I ask of King Juramidam
    Firmenss, great firmness, always to be your devotee
    \nextverse
    Firmness, great firmness, I ask the Virgin Mary
    Firmness, great firmness, that you may be my guide
    \nextverse
    Firmness, great firmness, I ask Lord Saint John
    Firmness, great firmness, to follow in the mission
    \nextverse
    Firmness, great firmness, I ask the Father of Creation
    That You give me peace and love, and smooth my heart
    \nextverse
    Smooth my heart, so I am able to love
    And the offenses of the brothers and sisters, I know how to forgive
    \nextverse
    Knowing to forgive, following in this light
    So I can say, that I am with my Jesus
  \end{translation}
\endsong


\beginsong{Eu Te Dei uma Casa}[by={Padr. Sebastião}, key={C}, gk={C, B\flt{}--C}]
  % Also in songs_astral_cura_i.tex
  \audio{https://www.nossairmandade.com/hymn/63/EuTeDeiUmaCasa}
  \mnbeginchorus\memorize
    \[^\mn{C}]Eu |\[\mnc{F}F]peço \[\bmc\mn{A}]a \[^\mn{C}]meu |\[^\mn{A}]Pai\[\bm], \[^\mn{C}]sei que |\[\mnc{E}C]Vós \[^\mn{C}]tem \[\bmc\mn{E}]o \[^\mn{G}]po|\[\mnc{E}(Em)]der \[\bm]
    \[^\mn{C}]Per\[^\mn{B}]do|\[\mnc{A}Am]ai \[^\mn{C}]as \[\bmc\mnc{E}(A7)]min\[^\mn{G}]has |\[\mnc{D}Dm]cul\[\bm]pas, \[^\mn{C}]se \[^\mn{B}]de |\[\mnc{A}Am]Vós \[^\mn{C}]eu \[\bm]me\[^\mn{E}]re|\[\mnc{C}C]cer\[\bm]
  \mnendchorus
  \notesoff
  \beginchorus
    Eu |^te dei ^uma |ca^sa que |^não fal^ta nin|^guém ^\altchords{\id[1]{(B\flt{})}|E\flt{} | - |B\flt{} |(Dm) }
    Pa|^{ra tu} ^esco|^lher ^aque|^les que ^te con|^vém^\altchords{|Gm (G7) |Cm |Gm |B\flt{}}
  \endchorus
  \beginchorus
    A es|^trada eu ^dou a |to^dos, para |^todos ^via|^jar ^
    |^Ver e ^compreen|^der, ^e fi|^car em ^seu lu|^gar^
  \endchorus
  \beginchorus
    |^Eu es^tou com |Deus^, |^Deus es^tá em |^mim ^
    Eu |^estan^{do com} |^Deus^, |^Deus é o ^meu ca|^mi^nho
  \endchorus
  \beginchorus
    |^Deus ^é a |gló^ria, |^Deus a ^glória |^é ^
    Quem |^{é meu} ^Salva|^dor ^é Je|^sus de ^Naza|^ré ^
  \endchorus
  \beginchorus
    Eu |^vivo ^neste |mun^do na |^minha ^dire|^ção ^
    \noteson\[\mnd{E}]Ol\[\mnd{C}]han\notesoff|^do as coi^sas de |^Deus e ^prestan|^do bem ^aten|^ção^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, latest update on 2024-03
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
         c4\pomark |f f a c |a2( a4) c,8( c8) |e4 c e g |e2( e4) c8( b8)
         |a4 c e g |d2 d4 c8( b8) |a4 c c e |c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Eu  |pe -- ço a meu | Pai, __ _
      sei que | Vós tem o po -- | der; __ _
      Per -- do -- | ai as mi -- nhas | cul -- pas,
      se de | Vós eu me -- re -- | cer. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Eu | te dei u -- ma | ca -- sa
      que __ _ | não fal -- ta nin -- | guém; __ _
      Pa -- _ | ra tu es -- co -- | lher
      a -- que -- _ | les que te con -- | vém. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      A~es -- | tra -- da~eu dou a | to -- dos
      pa -- ra | to -- dos vi -- a -- jar; _ \skip 1 \skip 1
      Ver e com -- preen -- der
      e fi -- _ car em seu lu -- gar. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 Eu es -- tou com Deus, _
      \skip 1 \skip 1 Deus es -- tá em mim; __ _
      Eu __ _ es -- tan -- do com Deus,
      \skip 1 \skip 1 \skip 1 Deus é~o meu ca -- mi -- nho.
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \skip 1 | Deus __ _ é a | gló -- ria,
      \skip 1 \skip 1 | deus a gló -- ria | é; __ _
      Quem __ _ | é meu Sal -- va -- | dor
      é Je -- _ | sus de Na -- za -- | ré. __ _
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      Eu | vi -- vo nes -- te | mun -- do;
      na __ _ | mi -- nha di -- re -- | ção;
      O -- lhan -- _ | do~as coi -- sas de | Deus~e
      pres -- tan -- _ | do bem a -- ten -- | ção. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 |f1 |f1 |c1 |\parenthesize e:m
        |a2:m \parenthesize a:7 |d1:m |a:m |c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I ask my Father, I know that You have the power
    Forgive my guilt, if I am deserving
    \nextverse
    I gave you a house in which no one is missing
    For you to choose those whom you find worthy
    \nextverse
    I give the path to all, for everyone to travel
    To see and understand, and to stay in your place
    \nextverse
    I am with God, God is within me
    Being with God, God is my path
    \nextverse
    God is the glory, God the glory is
    He who is my Savior is Jesus of Nazareth
    \nextverse
    I live in this world following my direction
    Looking at the things of God and paying close attention
  \end{translation}
\endsong


\beginsong{São João na Terra}[by={Padr. Sebastião}, tags={2x}, key={C}, gk={C, C--D}]
  % Also in songs_astral_cura_i.tex
  \audio[]{https://www.nossairmandade.com/hymn/64/S\%C3\%A3oJo\%C3\%A3oNaTerra}
  \newchords{chords_saojoaonaterra_a}\newchords{chords_saojoaonaterra_b}
  \mnbeginchorus\memorize[chords_saojoaonaterra_a]
    \[^\mn{G}]Quando ou\[\bmc\mn{C}]vir \[^\mn{E}]fa|\[\mnc{G}C]lar de São \[^\mn{E}]Jo\[\bmc\mn{A}]ão \[^\mn{G}]na |\[\mncii{E}{C}Am]terra \altchords{\id[1]{(D)}|D |Bm}
    É \[^\mn{A}]si\[\mnc{C}C]nal \[^\mn{E}]de |\[\mnc{D}Dm]guerra em \[^\mn{C}]to\[\mnc{A}F]do \[^\mn{C}]lu|\[C]gar \altchords{D |Em G |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_saojoaonaterra_b]
    \ind \[^\mn{C}]É |\[\mnc{D}Dm]fora \[^\mn{C}]de \[\bmc\mn{A}]con\[^\mn{C}]fu|\[\mnc{E}C]são \altchords{|Em |D}
    \ind \[^\mn{A}]Che\[\bmc\mn{C}]gou \[^\mn{E}]São |\[\mnc{D}Dm]Pedro com \[^\mn{C}]seus \[\mnc{A}F]dois \[^\mn{C}]ir|\[C]mãos \altchords{|Em G |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_saojoaonaterra_a]
    Os an^jinhos do |^céu é quem ^vem co|^lher \altchords{\id[4]{MK (C)}|C |Am}
    Para ^ajun|^tar em um ^{só lu}|^gar \altchords{|G F |C}
  \endchorus\glueverses\beginchorus\replay[chords_saojoaonaterra_b]
    \ind Lou|^var a meu ^Pai E|^terno \altchords{|G F |Am}
    \ind Fel^iz da|^quele que bem ^traba|^lhar \altchords{|G F |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, latest update on 2024-03
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 2.
      \repeat volta 2 {
        \sectionLabel "A"
        g8 \pomark g c4 e | g8( g) g e a4 g
        | e8( c) c a c4 e | d8( d) d c a4 c
      } \alternative {
        { | c4 }
        { | c2. }
      }
      \repeat volta 2 {
        \sectionLabel "B"
        c4 | d d8 c a4 c | e4( e8) a,8 c4 e4
        | d8 d d c a4 c4
      } \alternative {
        { | c2. }
        { | c4 }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Quan -- do~ou -- vir fa -- | lar de São Jo -- ão na | ter -- ra;
        É si -- nal de | guer -- ra em to -- do lu --
      } \alternative {
        { | gar; }
        { | gar. }
      }
      \repeat volta 2 {
        É | fo -- ra de con -- fu -- | são; _
        Che -- gou São | Pe -- dro com seus dois ir --
      } \alternative {
        { | mãos; }
        { | mãos. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Os an -- jinhos do | céu _ é quem vem co -- | lher; _
        Pa -- ra a -- jun -- | tar _ em um só lu --
      } \alternative {
        { | gar; }
        { | gar. }
      }
      \repeat volta 2 {
        Lou -- | var a meu Pai E -- | ter -- no;
        Fe -- liz da -- | que -- le que bem tra -- ba --
      } \alternative {
        { | lhar; }
        { | lhar. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2. | c1 | a2:m c | d:m f
      } \alternative {
        { | c4 }
        { | c2. }
      }
      \repeat volta 2 {
        s4 | d1:m | c | d2:m f
      } \alternative {
        { | c2. }
        { | c4 \bar "|." }
      }
    }
    \include "tex/lp-include-tail-lyricsbetween.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    When you hear it said that St. John is on the earth
    It‘s a sign of war everywhere
    \nextverse
    Apart from the confusion
    St. Peter arrived with his two brothers
    \nextverse
    The little angels of heaven are the ones who come to gather
    To bring together in one single place
    \nextverse
    Praise to my Eternal Father
    Happy is he who works well
  \end{translation}
\endsong


\beginsong{Conforto}[by={Padr. Alfredo}, key={Bm}, gk={Cm, Bm--Cm--(Dm)}]
  \audio[]{https://www.nossairmandade.com/hymn/478/Conforto}
  \transpose{-3}
  \beginchorus\memorize
    \[^\mn{A}]Eu |\[\mnc{F}Dm]pe\[^\mn{D}]ço \[^\mn{F}]con\[\mnc{E}A7]for\[^\mn{C#}]to \[^\mn{E}]aos |\[\mnc{D}Dm]Reis \[\bm]{} \altchords{\id[1]{(Dm)}|Dm A7 |Dm}
    \[^\mn{D}]Do |\[^\mn{A}]Céu, \[^\mn{F}]da \[^\mn{D}]Flo\[\mnc{A}D7]rest\[^\mn{F}]{a e} \[^\mn{D}]do |\[\mnc{G}Gm]Mar \[\bm]{} \altchords{| - D7 |Gm}
    |\[^\mn{B&}]Pe\[^\mn{G}]ço \[^\mn{E}]con\[\mnc{C#}A7]fort\[^\mn{A}]{o as} \[^\mn{E}]Ra|\[\mnc{D}Dm]i\[\bm]nhas \altchords{| - A7 |Dm}
    Para |\[\mnc{A}A]nos \[\mnciii{E}{F}{E}A7]ilumi|\[\mnc{D}Dm]nar \[\bm]{} \altchords{|A A7 |Dm}
  \endchorus
  \notesoff
  \beginchorus
    Eu |^peço con^forto aos |^Prínci^pes
    Do |Céu, da Flo^resta e do |^Mar ^
    |Peço con^forto as Prin|^ce^sas
    Para |^nos ^ilumi|^nar ^
  \endchorus
  \beginchorus
    Eu |^peço con^forto aos |^An^jos
    Do |Céu, da Flo^resta e do |^Mar ^
    |Peço con^forto aos |^San^tos
    Para |^nos ^ilumi|^nar ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, latest update on 2024-03
    theMelody = \transpose d b, \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4
      \repeat volta 2 {
        a4 \pomark | f'4 d8 f8 e4 cis8 e8 | d4.( d8)( d4)
        d'4 | a4 f8 d' a4 f8 d | g1 \break
        | bes4 g8 e cis8. cis16 a8 e' | d2 d4
        d8 d8 | a'2 e4 f8 e | d2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu | pe -- ço con -- for -- to aos | Reis; __ _ _
        Do | Céu, da Flo -- res -- ta~e do | Mar;
        | Pe -- ço con -- for -- to as Ra -- | i -- nhas;
        Pa -- ra | nos i -- lu -- mi -- | nar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Eu | pe -- ço con -- for -- to aos | Prín -- ci -- pes;
        Do | Céu, da Flo -- res -- ta~e do | Mar;
        | Pe -- ço con -- for -- to as Prin -- | ce -- sas;
        Pa -- ra | nos i -- lu -- mi -- | nar.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Eu | pe -- ço con -- for -- to aos | An -- _ jos;
        Do | Céu, da Flo -- res -- ta~e do | Mar;
        | Pe -- ço con -- for -- to a -- os | San -- tos;
        Pa -- ra | nos i -- lu -- mi -- | nar.
      }
    }
    theChords = \transpose d b, \chordmode {
      \repeat volta 2 {
        s4 | d2:m a:7 | d1:m
        | d2:m d:7 | g1:m
        | g2:m a:7 | d1:m
        | a2 a:7 | d2.:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I ask comfort from the Kings
    Of Heaven, of the Forest and of the Sea
    I ask comfort from the Queens
    To illuminate us
    \nextverse
    I ask comfort from the Princes
    Of Heaven, the Forest and the Sea
    I ask comfort from the Princesses
    To illuminate us
    \nextverse
    I ask comfort from the Angels
    Of Heaven, the Forest and the Sea
    I ask comfort from the Saints
    To illuminate us
  \end{translation}
\endsong


\beginsong{Chamo o Tempo}[by={Mestre Irineu Serra}, key={A}, gk={A, G--A}]
  \audio[]{https://www.nossairmandade.com/hymn/23/ChamoOTempo}
  \transpose{2}
  \mnbeginchorus\memorize
    \[^\mn{B}]Cha\[^\mn{A}]mo o |\[\mnc{G}G]Tempo, eu \[\mnc{A}D]cha\[^\mn{G}]{mo o} |\[\mnc{D}G]Tempo\[\bm]{} \altchords{\id[1]{(G)}|G D |G}
    \[^\mn{B}]Para e\[^\mn{A}]le |\[^\mn{G}]vir me \[\mncii{A}{G}D]ensi|\[\mnc{D}G]nar\[G7]{} \altchords{| - D |G G7}
    \lrep \[^\mn{D}]Apren|\[\mnc{E}C]der com \[\mnc{F#}D]per\[^\mn{A}]fei|\[\mnc{G}G]ção\[\bm]{} \altchords{|C D |G}
    \[^\mn{G}]Pa\[^\mn{A}]ra |\[^\mn{B}]po\[^\mn{A}]der \[\mncii{D}{B}D]ensi|\[\mnc{G}G]nar\[\up{1}G7]{} \rrep \altchords{| - D |G \up{1}G7}
  \mnendchorus
  \notesoff
  \beginchorus
    Os que |^forem o^bedi|^entes^
    Tra|tar de ^apren|^der^
    \lrep Para |^ser e^terna|^men^te
    Para |Deus lhe ^aten|^der^ \rrep
  \endchorus
  \beginchorus
    De|^pois que o ^Tempo |^chega^ \altchords{\id[4]{alt. (A)}|A E |A E}
    Nin|guém quis ^apren|^der^ \altchords{|A E |A A7}
    \lrep De|^pois que ^refle|^tir^ \altchords{|D E |A F\shrp{}m}
    É que |vai se ar^repen|^der^ \rrep \altchords{|Bm E |A A7}
  \endchorus
  \beginchorus
    Fir|^meza no ^pensa|^mento^
    Para |seguir ^no ca|^minho^
    \lrep Embora |^que não a^prenda |^mui^to
    Aprenda |sempre um ^boca|^di^nho \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, latest update on 2024-03
    theMelody = \transpose g a \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 4
        \sectionLabel "A"
        b8 \pomark ( a) | g4 g8 g8 a4 g4
        | d'4 d4. \parenthesize b8 \genmark "(1.)" b8( a8)
        | g4 g a g |d'4( d4.)
      \repeat volta 2 {
        \sectionLabel "B"
        \parenthesize d8 \genmark "(4.)" d8( d8) | e4 e fis a
        | \slurDown g2( g8) \parenthesize g,8 \genmark "(4.)" g8 a8
        | b4. a8 d4. b8
      } \alternative {
        { | g2( g8) }
        { | g2( g4) \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Cha -- mo~o | Tem -- po, eu cha -- mo~o | Tem -- po;
      Pa -- ra~e -- le | vir me en -- si -- | nar. __ _
      \repeat volta 2 {
        \set stanza = "1.B"
        \skip 1 A -- pren -- | der com per -- fei -- | ção; __ _
        \skip 1 Pa -- ra | po -- der en -- si --
      } \alternative {
        { | nar. __ _ }
        { | nar. __ _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Os que | fo -- rem o -- be -- di -- | en -- tes; _
      Tra -- _ | tar de a -- pren -- | der. __ _
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 Pa -- ra | ser e -- ter -- na -- | men -- te; __
        \skip 1 Pa -- ra | Deus lhe a -- ten --
      } \alternative {
        { | der. __ _ }
        { | der. __ _ }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      De -- _ | pois que o Tem -- po | che -- ga;
      \skip 1 Nin -- _ | guém quis a -- pren -- | der. __ _
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 De -- _ | pois que re -- fle -- | tir; __ _
        \skip 1 É que | vai se~ar -- re -- pen --
      } \alternative {
        { | der. __ _ }
        { | der. __ _ }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      Fir -- _ | me -- za no pen -- sa -- | men -- to;
      \skip 1 Pa -- ra | se -- guir no ca -- | mi -- nho.
      \set stanza = "4.B"
      \repeat volta 2 {
        Em -- bo -- ra | que não~a -- pren -- da | mui -- to;
        A -- pren -- da | sem -- pre~um bo -- ca --
      } \alternative {
        { | di -- nho. }
        { | di -- nho. }
      }
    }
    theChords = \transpose g a \chordmode {
      s4 | g2 d | g1
      | g2 d2 | g g8:7
      \repeat volta 2 {
        s4. | c2 d | g1
        | g2 d
      } \alternative {
        % NOTE: this was used earlier insead of alternative endings:
        % \mark\markup{\hspace #-1.7 \super{"1"}} \parenthesize g8:7
        { g2 g8:7 }
        { g2. }
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I call the time, I call the time, for it to come to teach me
    To learn with perfection, so that I can teach
    \nextverse
    Those who are obedient try to learn
    To be eternally, for God to help you
    \nextverse
    After the time arrives, nobody wanted to learn
    After reflecting is when one will repent
    \nextverse
    Firmness in the mind to continue on the path
    Even if you don‘t learn much, always learn a little bit
  \end{translation}
\endsong


\beginsong{Chamo a Força}[by={Mestre Irineu Serra}, key={Am}, gk={Am, Gm--Bm}]
  \audio{https://www.nossairmandade.com/hymn/270/ChamoAFor\%C3\%A7a}
  \mnbeginchorus\memorize
    \[^\mn{C}]Cha\[^\mn{B}]{mo a} |\[\mnc{A}Am]força, eu \[\mnc{C}(C)]cha\[^\mn{E}]{mo a} |\[\mnc{A}Am]força\[\bm]{} \altchords{\id[1]{(Bm)}|Bm (D) |Bm}
    \[^\mn{G}]A força |\[G]vem \[^\mn{E}]nos \[\mncii{C}{A}C]amos|\[\mnciii{C}{B}{A}Am]trar \[\bm]{} \altchords{|A D |Bm}
  \mnendchorus\glueverses\notesoff\mnbeginchorus
    Treme a |^terra e ^balan|^ceia^ \altchords{|Bm (D) |Bm}
    E vós não |^sai do ^seu lu|^gar ^ \altchords{|A D |Bm}
  \mnendchorus
  \beginchorus
    Treme a |^terra, ^treme a |^terra^
    Treme a |^terra e ^geme o |^mar ^
  \endchorus\glueverses\beginchorus
    Ainda tem |^gente ^que du|^vida^
    Do po|^der que ^vós me |^dá ^
  \endchorus
  \beginchorus
    Aqui |^dentro ^da ver|^dade^ \altchords{\id[2]{(Gm)}|Gm (B\flt{}) |Gm}
    Tem uns |^certos ^menti|^ro^sos \altchords{|F B\flt{} |Gm}
  \endchorus\glueverses\beginchorus
    Que calu|^niam os ^seus ir|^mãos \altchords{|Gm (B\flt{}) |Gm}
    ^Para se tor|^nar mui^to vi|^ço^sos \altchords{|F B\flt{} |Gm}
  \endchorus
  \brk
  \beginchorus
    Mas |^ninguém ^não se |^lembra^
    Chamou o |^Mestre ^menti|^ro^so
  \endchorus\glueverses\beginchorus
    Devaga|^rinho ^vai che|^gando^
    E quem cha|^mou é que ^vai fi|^can^do
  \endchorus
  \brk
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, latest update on 2024-03
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        \sectionLabel "A"
        r8 \pomark c8( b) | a4 a c e | a a4. \parenthesize g8 g g
        | g4 e c a | c4.( b8)( a8)
      }
      \repeat volta 2 {
        \sectionLabel "B"
        \parenthesize c8 c b | a4 a c e | a a4 \parenthesize g8 \parenthesize g8 g g
        | g4 e c a | c4.( b8)( a8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Cha -- mo~a | for -- ça~eu cha -- mo~a | for -- ça;
        A for -- ça | vem nos a -- mos -- | trar. __ _ _
      \set stanza = "1.B"
        \skip 1 Tre -- me~a | ter -- ra~e ba -- lan -- | cei -- a;
        \skip 1 E vós não | sai do seu lu -- | gar. __ _ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
        Tre -- me~a | ter -- ra tre -- me~a | ter -- ra;
        Tre -- me a | ter -- ra~e ge -- me~o | mar. __ _ _
      \set stanza = "2.B"
        Ain -- da tem | gen -- te que du -- | vi -- da;
        \skip 1 \skip 1 Do po -- | der que vós me | dá. __ _ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
        A -- qui | den -- tro da ver -- | da -- de;
        \skip 1 Tem uns | cer -- tos men -- ti -- | ro -- _ sos.
      \set stanza = "3.B"
        Que ca -- lu -- | ni -- am os seus~ir -- | mã -- os;
        Pa -- ra se tor -- | nar mui -- to vi -- | ço -- _ sos.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
        Mas __ _ | nin -- guém não se | lem -- bra;
        Cha -- mou o | Mes -- tre men -- ti -- | ro -- _ so.
      \set stanza = "4.B"
        De -- va -- ga -- | ri -- nho vai che -- | gan -- do;
        \skip 1 E quem cha -- | mou~é que vai fi -- | can -- _ do.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a2:m \parenthesize c | a1:m | g2 c | a:m~ a8:m
      }
      \repeat volta 2 {
        s4. | a2:m \parenthesize c | a1:m | g2 c | a:m~ a8:m
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]\scriptsize % to fit on one spread
    I call the Force, I call the Force; the Force comes to show us
    The earth shakes and quakes, but Thou don't move
    \nextverse
    The earth shakes, the earth shakes, the earth shakes and the sea moans
    Yet, there are people who still doubt the power that Thou give me
    \nextverse
    Here in the Truth there are some liars
    Who slander their brothers and sisters so that they can look good
    \nextverse
    But no one remembers that he called the Master a liar
    Slowly he's going to arrive and who called is who stays behind
  \end{translation}
\endsong


\beginsong{Eu Peço a Deus\\Vi Deus no Sol, na Lua e nas Estrelas}[by={Francisco Corrente}, tags={2x}, key={C}, gk={C, C--D}]
  \audio[]{https://www.nossairmandade.com/hymn/26/EuPe\%C3\%A7oADeus}
  \newchords{chords_eupecoadeus_a}\newchords{chords_eupecoadeus_b}
  \mnbeginchorus\memorize[chords_eupecoadeus_a]
    \[^\mn{C}]Eu pe\[^\mn{E}]{ço a} |\[\mnc{G}C]Deus que per\[\mnc{A}Am]doe os meus \[^\mn{E}]pe|\[\mnc{G}F]ca\[^\mn{F}]dos\[^\bm]{} \altchords{\id[1]{(D)}|D Bm |G}
    Perdoe \[^\mn{G}]a |\[\mnc{A}Dm]mim e per\[^\bm]doe \[^\mn{F}]{a meus} \[^\mn{A}]ir|\[\mnc{G}G]mã\[^\bm]os \altchords{|Em |A}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eupecoadeus_b]
    \[^\mn{/}]Eu peço a |\[\up{1}C \up{2}(Am)]{Deus que} me \[^\bm]dê \[^\mn{A}]a San\[^\mn{/}]ta |\[\mnc{/}G]Luz\[^\bm]{} \altchords{|\up{1}D \up{2}(Bm) |A}
    \[^\mn{D}]Para eu a|\[G7]mar Vós no \[^\bmc\mn{E}]meu co\[^\mn{C}]ra|\[C]ção\[^\bm]{} \altchords{|A7 |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eupecoadeus_a]
    Vi Deus no |^sol Deus na ^lua e nas es|^trelas\[\bm]
    Vi Deus no |^vento Deus na \[\bm]terra Deus no |^mar\[\bm]
  \endchorus\glueverses\beginchorus\replay[chords_eupecoadeus_b]
    Todos |^{sabem que} \[\bm]Deus esta em |^todo\[\bm]
    Todos se |^firmam, se com\[\bm]ponham em seu lu|^gar\[\bm]
  \endchorus
  \beginchorus\replay[chords_eupecoadeus_a]
    Eu digo a |^todos com a^mor no cora|^ção\[\bm]
    |^Deus é quem nos \[\bm]da a Santa |^Luz\[\bm]
  \endchorus\glueverses\beginchorus\replay[chords_eupecoadeus_b]
    |^{Deus é quem} da \[\bm]o nosso des|^tino\[\bm]
    Pra nos sa|^ir deste \[\bm]mundo de ilu|^são\[\bm]
  \endchorus
  \vfill
  \textnotefornext{This hino can be sung when someone is going through a
                   \emph{passage} in a concentration work.}
  \textnoteforprev{Este hino pode ser cantado quando alguém está passando por
                   uma \emph{passagem} em um trabalho de concentração.}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, latest update on 2024-03
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        \sectionLabel "A"
        c8 \pomark c e | g8( g8) g8 g8 a8 a8 a8 e8 | g4 f4.( \parenthesize f8 \parenthesize f8) \parenthesize g8
        | a8( a8) a8 a8 a8 f8 f8 a8 | g2( g8)
      } \break
      \sectionLabel "B:I"
      \parenthesize c,8 \parenthesize c8 \parenthesize c8 | c8( c8) c8 c8 c8 a8 a8 c8 | b4( b4.) d8 d8 d8
      | d8( d8) d8 d8 e8( e8) e8 c8 |  c2~ c8 \sectionLabel "B:II" \parenthesize a8 \parenthesize a8 \parenthesize a8
      | a8( a8) a8 a8 a8 a8 a8 a8 | a4( g4.) d'8 d8 d8
      | d8( d8) d8 d8 e8( e8) e8 c8 | c2~ c8 \bar "|."
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu pe -- ço~a | Deus __ _ que per -- doe Os meus pe -- | ca -- dos;
        Per -- do e~a | mim __ _ e per -- doe a meus ir -- | mã -- os.
      }
      \set stanza = "1.B"
      Eu pe -- ço~a | Deus __ _ que me dê a San -- ta | Luz; __ _
      Pa -- ra eu_a -- | mar __ _ Vós no meu __ _ co -- ra -- | ção. __ _
      Eu pe -- ço~a | Deus __ _ que me dê a San -- ta | Luz; __ _
      Pa -- ra eu_a -- | mar __ _ Vós no meu __ _ co -- ra -- | ção. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Vi Deus no | sol __ _ Deus na lu -- a~e nas es -- | tre -- las;
        Vi Deus no | ven -- to Deus na ter -- ra Deus no | mar. __ _
      }
      \set stanza = "2.B"
      \skip 1 To -- dos | sa -- _ bem que Deus es -- ta em | to -- do;
      To -- dos se | fir -- mam se com -- po -- nham~em seu lu -- | gar. __ _
      \skip 1 To -- dos | sa -- _ bem que Deus es -- ta em | to -- do;
      To -- dos se | fir -- mam se com -- po -- nham~em seu lu -- | gar. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Eu di -- go~a | to -- dos com a -- mor no co -- ra -- | çã -- o;
        \skip 1 \skip 1 \skip 1 | Deus é quem nos da a San -- ta | Luz. __ _
      }
      \set stanza = "3.B"
      \skip 1 \skip 1 \skip 1 | Deus é quem da o nos -- so des -- | ti -- no;
      Pra nos sa -- | ir __ _ des -- te mun -- do de~i -- lu -- | são. __ _
      \skip 1 \skip 1 \skip 1 | Deus é quem da o nos -- so des -- | ti -- no;
      Pra nos sa -- | ir __ _ des -- te mun -- do de~i -- lu -- | são. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 a:m | f1
        | d1:m | g2~8
      }
      s4. | c1 | g1
      | g1:7 | c1
      | a1:m | g1
      | g1:7 | c2~8
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    I ask God to forgive my sins
    Forgive me and forgive my brothers and sisters
    I ask God to give me the Holy Light
    So that I can love You in my heart
    \nextverse
    I saw God in the Sun, I saw God in the Moon and in the Stars
    I saw God in the Wind, God in the Earth, God in the Sea
    Everyone knows that God is in everything
    Everyone is firming themselves and cmoposing themselves in their place
    \nextverse
    I say to everyone with love in my heart
    It is God who gives us the Holy Light
    It is God who gives us our destiny
    So we can leave this world of illusion
  \end{translation}
\endsong
