% Santo Daime: Hinos do Daime
% ===========================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Aqui eu Recebi}[by={Padr. Sebastião},key={A},sks={A, B, C}]
  \audio[key=C]{https://www.nossairmandade.com/hymn/35/AquiEuRecebi}
  \transpose{-3}
  \musicnote{4º verso tem uma melodia diferente.}
  \mnbeginchorus\memorize
    \[^\mn{G}]A|\[\mnc{E}C]qui eu \[\mncii{D}{C}(G7)]rece|\[\mnc{G}C]bi, \[^\mn{E}]pa\[^\mn{G}]ra |\[^\mn{E}]mim dis\[\mnc{D}C7]tri\[^\mn{C}]bu|\[\mnc{A}F]ir
    |\[^\mn{A}]É \[^\mn{B}]o \[^\mn{C}]San\[^\mn{A}]to |\[\mnc{G}C]Daime, \[^\mn{E}]pa\[^\mn{C}]ra |\[^\mn{E}]com meu \[\mnc{D}G7]Pai se|\[\mnc{C}C]guir
  \mnendchorus
  \notesoff
  \beginchorus
    Se |^meus ir^mãos sou|^bessem, o que |é que ^vem fa|^zer
    Sa|íam bem lim|^pinhos, pois o |meu Pai ^tem po|^der
  \endchorus
  \beginchorus
    Es|^te é ^{o po}|^der, es|ta é ^{a ver}|^dade
    Quem não |ama com fir|^meza, sempre |carre^{ga a} mal|^dade
  \endchorus
  \beginchorus
    Eu |^gosto ^{de di}|^zer, também |gosto ^de mos|^trar
    \noteson |\[\mnlow{A}]Tá.\[\mnlow{F}].. |\[C\mnlow{E}]tum, |veja aon\[G7]de es|\[C]tá \notesoff
  \endchorus
  \notesoff
  \beginchorus
    Quem não |^souber ^{o que} |^é, puxe |pela ^consci|^ência
    Quem |ama com leal|^dade, sempre |rende o^bedi|^ência
  \endchorus
  \begin{translation}\footnotesize % to fit
    Here I received, for me to distribute
    It's the Holy Daime, for me to follow with my Father
    \nextverse
    If my brothers and sisters knew what they are coming to do
    They would leave well cleansed, because my Father has power
    \nextverse
    This is the power, this is the truth
    Who doesn't love with firmness always carries wickedness
    \nextverse
    I like to say and also like to show
    Tá\ldots tum, Behold it where it is
    \nextverse
    Whoever doesn't know what it is, pull on your conscience
    Whoever loves with loyalty always renders obedience
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose c' a \relative c''' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \mark \markup {"6x"} \bar ".|:" \repeat volta 6 {
        g4\sectionmark "1.-3." | e4 e d c | g'2( g4) e8 g8 | e4 e d c | a'2( a4 a8 a8)
        | a4 b c a | g4. g8 e4 c4 | e e d d | c2( c4)
      }
      \slurSolid
      \repeat volta 2 {
        g'4\sectionmark "4." | e4 e d c | g'2. e8 g8 | e4 e d c | a'1
        | a2.( f4) | e1  | e4 e d d | c2.
      }
      \repeat volta 2 {
        g'8\posectionmark "5." g8 | e4 e d c | g'2. e8 g8 | e4 e d c | a'2 a4 a4
        | a4 b8 b8 c4 a | g4. g8 e4 c4 | e e d d | c2 c4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      A -- | qui eu re -- ce -- | bi __ _
      pa -- ra | mim dis -- tri -- bu -- | ir; __ _ _ _
      É o San -- to | Dai -- me
      pa -- ra | com meu Pai se -- | guir. __ _
      \set stanza = "4."
      Eu | gos -- to de di -- | zer
      tam -- bém | gos -- to de mos -- | trar;
      | Tá _ | tum
      | ve -- ja~a -- on -- de~es -- | tá.
      \set stanza = "5."
      Quem não | sou -- ber o que | é
      pu -- xe | pe -- la cons -- ci -- | ên -- cia; Quem
      | a -- ma com -- le -- al -- | da -- de
      Sem -- pre | ren -- de~o -- be -- di -- | ên -- cia.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Se | meus ir -- mãos sou -- | bes -- sem
      O que | é que vem fa -- | zer _ Sa -- _
      | í -- am bem lim -- | pi -- nhos
      Pois o | meu Pai tem po -- | der. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Es -- | te é o po -- | der __ _
      Es -- _ | ta é a ver -- | da -- de Quem não
      | a -- ma com fir -- | me -- za
      Sem -- pre | car -- re -- ga~a mal -- | da -- de.
    }
    theChords = \transpose c' a \chordmode {
      \repeat volta 6 {
        s4 | c2 \parenthesize g:7 | c1
        | c2 \parenthesize c:7 | f1
        | f | c
        | c2 g:7 | c2.
      }
      \repeat volta 2 {
        s4 | c2 \parenthesize g:7 | c1
        | c2 \parenthesize c:7 | f1
        | f | c
        | c2 g:7 | c2.
      }
      \repeat volta 2 {
        s4 | c2 \parenthesize g:7 | c1
        | c2 \parenthesize c:7 | f1
        | f | c
        | c2 g:7 | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\scleardpage
\beginsong{O Daime, é o Daime}[by={Padr. Alfredo},tags={mazurka},key={C},sks={C}]
  \audio{https://www.nossairmandade.com/hymn/536/ODaime\%C3\%89ODaime}
  \newchords{chords_odaime_a}\newchords{chords_odaime_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_odaime_a]
    \[^\mn{E}]O |\[\mnc{G}C]Daime \[^\mn{E}]é \[^\mn{F}]o \[\bm\mn{G}]Daime
    Eu |\[^\mn{C}]es\[^\mn{G}]tou \[^\mn{E}\mn{G}]afir\[(G)]mando
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_odaime_b]
    \[^\mn{C}]É o Di|\[C]vi\[^\mn{G}]no \[^\mn{C}]Pai \[^\mn{E}]E\[(Am/E)]terno
    \[^\mn{C}]E a Ra|\[G]in\[^\mn{G}]ha \[^\mn{B}]So\[^\mn{D}]be\[\mnc{C}C]rana
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_odaime_a]
    O |^Daime é o ^Daime
    O profes|sor dos profes^sores
  \endchorus\glueverses\beginchorus\replay[chords_odaime_b]
    É o Di|^vino Pai E^terno
    E seu |^Filho Reden^tor
  \endchorus
  \beginchorus\replay[chords_odaime_a]
    O |^Daime é o ^Daime
    O Mestre |de todos en^sinos
  \endchorus\glueverses\beginchorus\replay[chords_odaime_b]
    É o Di|^vino Pai E^terno
    E to|^dos seres di^vinos
  \endchorus
  \beginchorus\replay[chords_odaime_a]
    O |^Daime é o ^Daime
    Eu agra|deço com a^mor
  \endchorus\glueverses\beginchorus\replay[chords_odaime_b]
    É quem me |^dá a minha sa^úde
    E revi|^gora o meu a^mor
  \endchorus\brk
  \beginchorus\replay[chords_odaime_a]
    Agra|^deço ao Santo ^Daime
    Agrade|cendo a todos ^seres
  \endchorus\glueverses\beginchorus\replay[chords_odaime_b]
    E quem me |^manda agrade^cer
    É o |^meu Pai verda^deiro
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 6/4 \partial 4.
      \repeat volta 2 {
        r8\posectionmark "A" e4 | g g e8 f8 g4 g8( g) g( g) | c4 g e8 g8 g4 g8
      }
      \repeat volta 2 {
        c,8\sectionmark "B" c c | c4 g c8 e8 e4 e8 c c c | c4 g4 b8 d8 c4( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      O | Dai -- me é o Dai -- me; __ _
      Eu __ _ | es -- tou a -- fir -- man -- do;
      \set stanza = "1.B"
      É o Di -- | vi -- no Pai E -- ter -- no;
      E a Ra -- | i -- nha So -- be -- ra -- na.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
        O | Dai -- me é o Dai -- me;
        O pro -- fes -- | sor dos pro -- fes -- so -- res;
        \set stanza = "2.B"
        É o Di -- | vi -- no Pai E -- ter -- no; __ _
        E seu | Fi -- lho Re -- den -- tor. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      O | Dai -- me é o Dai -- me;
      O Mes -- tre | de to -- dos en -- si -- nos;
      \set stanza = "3.B"
      É o Di -- | vi -- no Pai E -- ter -- no; __ _
      E to -- | dos se -- res di -- vi -- nos.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      O | Dai -- me é o Dai -- me;
      Eu a -- gra -- | de -- ço com a -- mor; __ _
      \set stanza = "4.B"
      É quem me | dá a~mi -- nha sa -- ú -- de;
      E re -- vi -- | go -- ra~o meu a -- mor. __ _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      Agra | de -- ço~ao San -- to Dai -- me;
      A -- gra -- de -- | cen -- do~a to -- dos se -- res;
      \set stanza = "5.B"
      E quem me | man -- da~a -- gra -- de -- cer; __ _
      \skip 1 É o | meu Pai ver -- da -- dei -- ro.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2. c | c \parenthesize g4~ g8
      }
      \repeat volta 2 {
        s4. | c2. \parenthesize a:m/e | g c4~ c8
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    The Daime is the Daime, I am affirming
    It is the divine Eternal Father, and the Sovereign Queen
    \nextverse
    The Daime is the Daime, the Teacher of all teachers
    It is the Divine Eternal Father, and his son the redeemer
    \nextverse
    The Daime is the Daime, the master of all teachings
    It is the Divine Eternal Father, and all Divine Beings
    \nextverse
    The Daime is the Daime, I thank with love
    It is he who gives my health, and renews my faith
    \nextverse
    I thank the holy Daime, thanking all beings
    And who orders me to give thanks, is my truthful Father
  \end{translation}
\endsong


\beginsong{Graças a Deus}[by={Madr. Maria Brilhante},key={G},sks={A, G}]
  \audio{https://www.nossairmandade.com/hymn/28/Gra\%C3\%A7asADeus}
  \newchords{chords_gracasadeus_a}\newchords{chords_gracasadeus_b}
  \mnbeginchorus\memorize[chords_gracasadeus_a]
    \[^\mn{D}]Graças \[^\mn{E}]a |\[\mnc{D}D]Deus aon\[^\mn{E}]de \[\mnc{D}(D7)]eu \[^\mn{C}]es\[^\mn{B}]tou \[^\mn{A}]tem |\[\mnc{G}G]Dai\[\bm]me
    Gra\[^\mn{B}]ças \[^\mn{D}]a |\[\mnc{G}Em]Deus Dai\[^\mn{F#}]me \[\mnc{A}(Am7)]nun\[^\mn{G}]ca \[^\mn{F#}]me \[^\mn{E}]fal|\[\mnc{D}D]tou\[\bm]
  \mnendchorus
  \mnbeginchorus\memorize[chords_gracasadeus_b]
    \ind \[^\mn{/}]Sou \[^\mn{B}]u\[^\mn{D}]ma |\[\mnc{G}G]árvore ro\[^\mn{F#}]si\[\mnc{A}Am7]an\[^\mn{G}]te em \[^\mn{F#}]u\[^\mn{E}]ma |\[\mnc{D}D]flor\[bm]
    \ind Graças \[^\mn{E}]a |\[^\mn{D}]Deus aon\[^\mn{E}]de o \[\mnc{D}D7]Dai\[^\mn{C}]me es\[^\mn{B}]tá \[^\mn{A}]es|\[\mnc{G}G]tou\[bm]
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_gracasadeus_a]
    \[\mnlow{/}]Louvar \[\mnlow{/}]a |^Deus e \[\mnlow{/}]a^\[\mnlow{/}]mar \[\mnlow{/}]com \[\mnlow{/}]to\[\mnlow{D}]do a|^mor^
    São João Ba|^tista é o ^nosso Prote|^tor^
  \endchorus
  \beginchorus\replay[chords_gracasadeus_b]
    \ind São João Ba|^tista e a sem^pre Virgem Ma|^ri^a
    \ind É quem nos |guia neste ^caminho com a|^mor^
  \endchorus
  \begin{translation}
    Thanks to God, where I am I have Daime
    Thanks to God, the Daime has never failed me
    \nextverse
    I am a tree shining in a Flower
    Thanks to God I am where the Daime is
    \nextverse
    To praise God and love with all love
    Saint John the Baptist is our protector
    \nextverse
    Saint John the Baptist and the Ever Virgin Mary
    Are who Guide us in this path with love
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \key g \major \time 4/4 \partial 4.
      d8\sectionmark "1." d e
      \repeat volta 2 {
        | d d d e d c b a | g2 g8 g b d | g4 g8 fis a g fis e
      } \alternative {
        { | d2~ d8 d d e }
        { | d2~ d8 b\sectionmark "2." b d }
      }
      \repeat volta 2 {
        g8 g16 g16 g8 fis a g fis e | d2~ d8 d d e | d d d e d c b a
      } \alternative {
        { | g2~ g8 g b d }
        { | g,2~ g8\posectionmark "3." g g b | d4 d8 d b b a a }
      }
      \repeat volta 2 {
        | g2~ g8 g b d | g g g fis a g fis e
      } \alternative {
        { | d2~ d8 d d e | d4 d8 e d c b a }
        { | d2~ d8 b\sectionmark "4." b d }
      }
      \repeat volta 2 {
        | g8 g g fis a g fis e | d2 d8 d d e | d d d e d c16 c16 b8 a
      } \alternative {
        { | g2~ g8 g b d }
        { | g,2~ g8 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Gra -- ças a
      \repeat volta 2 {
        | Deus a -- on -- de eu es -- tou tem | Dai -- me
        Gra -- ças a | Deus
        Dai -- me nun -- ca me fal --
      } \alternative {
        { | tou. Gra -- ças a }
        { | tou. \set stanza = "2." Sou u -- ma }
      }
      \repeat volta 2 {
        | ár -- vo -- re
        Ro -- si -- an -- te~em u -- ma | flor
        Gra -- ças a | Deus
        A -- on -- de~o Dai -- me~es -- tá es -- 
      } \alternative {
        { | tou. Sou u -- ma }
        { | tou. \set stanza = "3." Lou -- var a | Deus e a -- mar com to -- do~a -- }
      }
      \repeat volta 2 {
         | mor
        São João Ba -- | tis -- ta
        É o nos -- so Pro -- te -- 
      } \alternative {
        { | tor. Lou -- var a | Deus e a -- mar com to -- do~a -- }
        { | tor. \set stanza = "4." São João Ba -- }
      }
      \repeat volta 2 {
        | tis -- ta
        E~a sem -- pre Vir -- gem Ma -- | ri -- a
        É quem nos | gui -- a
        Nes -- te ca -- mi -- nho com a --
      } \alternative {
        { | mor. São João Ba -- }
        { | mor. }
      }
    }
    theChords = \chordmode {
      s4.
      \repeat volta 2 {
        | d2 \parenthesize d:7 | g1 | e2:m \parenthesize a:m7 
      } \alternative {
        { | d1  }
        { | d1 }
      }
      \repeat volta 2 {
        | g2 a:m7 | d1 | d2 d:7
      } \alternative {
        { | g1 }
        { | g1 | d2 d:7 }
      }
      \repeat volta 2 {
        | g1 | e2:m \parenthesize a:m7
      } \alternative {
        { | d1 | d2 d:7 }
        { | d1 }
      }
      \repeat volta 2 {
        | g2 a:m7 | d1 | d2 d:7
      } \alternative {
        { | g1 }
        { | g2~ g8 }
      }
    }
    \layout { #(layout-set-staff-size 13) } % to fit on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Tomo Daime}[by={Tetéo},key={C},sks={D, C}]
  \newchords{chords_tomodaime_a}\newchords{chords_tomodaime_b}
  \mnbeginchorus\memorize[chords_tomodaime_a]
    \[^\mn{/}]Eu |\[\mnc{C}C]tomo \[\bm]Dai\[^\mn{A}]me eu |\[^\mn{C}]tomo \[\bm]Daime \altchords{\id[1]{D}|D | \e}
    |\[\mnc{E}Am]Não tenho \[\bm]me\[^\mn{D}]do |\[\mnc{F}F]de \[^\mn{D}]to\[\bmc\mnc{B}G]mar \altchords{|Bm |G A}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_tomodaime_b]
    |\[\mnc{E}C]Eu es\[\bm]tan\[^\mn{D}]do |\[\mnc{F}F]com \[^\mn{D}]meu \[\mnc{B}G]Mestre \altchords{|D |G A}
    |\[\mnc{A}Am]Ne\[^\mn{C}]le eu \[\bm]pos\[^\mn{A}]so |\[\mnc{C}C]me fir\[\bm]mar \altchords{|Bm |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_tomodaime_a]
    Eu |^tomo ^Daime eu |tomo ^Daime
    |^Tomo ^para |^via^jar
  \endchorus\glueverses\beginchorus\replay[chords_tomodaime_b]
    |^Ouvir ^muito e |^falar ^pouco
    |^Pra co^nhecer |^meus ca^boclos
  \endchorus
  \beginchorus\replay[chords_tomodaime_a]
    Eu |^tomo ^Daime eu |tomo ^Daime \altchords{\id[2]{MK (C/Am)}|Am | \e}
    |^Porque ^acho |^bom to^mar \altchords{|C |Dm E}
  \endchorus\glueverses\beginchorus\replay[chords_tomodaime_b]
    Não |^exis^te na|^da di^fícil \altchords{|Am |Dm E}
    |^Se com o ^Mestre |^se fir^mar \altchords{|Am | \e}
  \endchorus
  \beginchorus\replay[chords_tomodaime_a]
    |^Eu a^qui vou |via^jando
    |^Por a^qui tenho |^que se^guir
  \endchorus\glueverses\beginchorus\replay[chords_tomodaime_b]
    Es|^tou con^vidan|^do sor^rindo
    E |^comi^go nin|^guém quer ^ir
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 8
      a8\posectionmark "A"
      \repeat volta 2 {
        | c4 c c4. a8 | c4 c c4. c8
        | e4 e8( e8) e4 d8( d8)
      } \alternative {
        { | f4 d4 b4. \parenthesize b8 }
        { | f'4 d4 b4. \parenthesize b8 \sectionmark "B" }
      }
      \repeat volta 2 {
        | e4 e e d | f d b4. b8
        | a4 c c a
      } \alternative {
        { | c4 c c4. \parenthesize c8 }
        { | c4 c c4. \parenthesize a8 }
      }
      \bar "|."
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Eu
      \repeat volta 2 {
        | to -- mo Dai -- me~eu | to -- mo Dai -- me;
        | Não te -- nho me -- do __ _
      } \alternative {
        { | de to -- mar. Eu}
        { | de to -- mar. __ _ }
      }
      \repeat volta 2 {
        \set stanza = "1.B"
        | Eu es -- tan -- do | com meu Mes -- tre;
        | Ne -- le~eu pos -- so
      } \alternative {
        { | me fir -- mar. __ _ }
        { | me fir -- mar. \set stanza = "2." Eu }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \skip 1
      \repeat volta 2 {
        | to -- mo Dai -- me~eu | to -- mo Dai -- me;
        | To -- mo __ _ pa -- ra __ _
      } \alternative {
        { | vi -- a -- jar. Eu }
        { | vi -- a -- jar. __ _ }
      }
      \repeat volta 2 {
        \set stanza = "2.B"
        | Ou -- vir mui -- to~e | fa -- lar pou -- co;
        | Pra co -- nhe -- cer
      } \alternative {
        { | meus ca -- boclos. __ _ }
        { | meus ca -- boclos. \set stanza = "3." Eu}
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1
      \repeat volta 2 {
        | to -- mo Dai -- me~eu | to -- mo Dai -- me;
        | Por -- que __ _ a -- cho __ _
      } \alternative {
        { | bom to -- mar. Eu }
        { | bom to -- mar. \set stanza = "3.B" Não }
      }
      \repeat volta 2 {
        | e -- xis -- te na -- | da di -- fí -- cil
        | Se com~o Mes -- tre
      } \alternative {
        { | se fir -- mar. Não}
        { | se fir -- mar. \skip 1 }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1
      \repeat volta 2 {
        | Eu a -- qui vou | vi -- a -- jan -- do;
        | Por a -- _ qui te -- nho
      } \alternative {
        { | que se -- guir. \skip 1 }
        { | que se -- guir. \set stanza = "4.B" Es -- }
      }
      \repeat volta 2 {
        | tou con -- vi -- dan -- | do sor -- rin -- do;~E
        | co -- mi -- go nin --
      } \alternative {
        { | guém quer ir. Es}
        { | guém quer ir. }
      }
    }
    theChords = \chordmode {
      s8
      \repeat volta 2 {
        | c1 | c1
        | a1:m
      } \alternative {
        { | f2 g2 }
        { | f2 g2 }
      }
      \repeat volta 2 {
        | c1 | f2 g2
        | a1:m
      } \alternative {
        { | c1 }
        { | c1 }
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I drink Daime, I drink Daime, I'm not afraid of drinking it
    Being with myu Master, in him I can firm myself
    \nextverse
    I drink Daime, I drink Daime, I drink it to travel
    Listen a lot and speak little, to know my caboclos
    \nextverse
    I drink Daime I drink Daime, because I think it's good to drink
    There isn't anything difficult, if with the Master we firm ourselves
    \nextverse
    Through this way I go traveling, through here I must follow
    I am inviting smiling, and with me no one wants to go
  \end{translation}
\endsong


\setcounter{songnum}{9}
\beginsong{O Lindo Daime}[by={Luis Mendes},key={Am},sks={Cm, Bm, Am}]
  \audio{https://www.nossairmandade.com/hymn/34/OLindoDaime}
  \mnbeginchorus\memorize
    |\[\mnc{A}Am]O \[^\mn{C}]lin\[^\mn{A}]do |\[\mnc{E}(E)]Daime
    |\[\mncii{A}{B}Am]Veja \[^\mn{C}]co\[^\mn{A}]mo |\[\mnc{E}(E)]é
    \lrep |\[\mnc{A}Am]É \[^\mn{C}]ma\[^\mn{A}]ra|\[\mnc{E}E]vilha
    Pa\[^\mn{D}]ra |\[\mnc{C}(C)]to\[^\mn{B}]dos \[\mnc{E}E7]ten\[^\mn{C}]do |\[\mnc{A}Am]fé \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    |^Eu peço a meu |^Mestre
    |^No meu cora|^ção
    \lrep |^A santa |^luz
    Da vir|^gem da ^Concei|^ção \rrep
  \endchorus
  \beginchorus
    |^Te afirma em |^Deus
    |^Em concentra|^ção
    \lrep |^Que tu te|^rás
    A |^san^ta ben|^ção \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4
      | a4._\posectionmark "A" \parenthesize b8 c4 a4 | e'2( e4 e4) | a,4. b8 c4 a4 | e'1
      \repeat volta 2 {
        | a,2_\sectionmark "B" c4 a4 | e'4.( e8 e4) d4 | c4( b4) e4 c4 | a1
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      | O __ _ lin -- do | Dai -- _ me;
      | Ve -- ja co -- mo | é.
      \repeat volta 2 {
        | É ma -- ra -- | vi -- lha;
        Pa -- ra | to -- dos ten -- do | fé.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      | Eu pe -- ço~a meu | Mes -- tre; __ _
      | No meu co -- ra -- | ção.
      \repeat volta 2 {
        | A san -- ta | luz; __ _
        Da vir -- | gem da Con -- cei -- | ção.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      | Te a -- fir -- ma~em | Deus; __ _ _
      | Em con -- cen -- tra -- | ção.
      \repeat volta 2 {
        | Que tu te -- | rás; __ _ _
        A | san -- _ ta ben -- | ção.
      }
    }
    theChords = \chordmode {
      | a1:m | \parenthesize e | a:m | \parenthesize e
      \repeat volta 2 {
        | a1:m | e | \parenthesize c2 e2:7 | a1:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    The beautiful Daime
    See how it is
    It is wonderful
    For everyone who has faith
    \nextverse
    I ask my Master
    In my heart
    The holy light
    Of the Virgin of Conception
    \nextverse
    Affirm yourself in God
    In concentration
    That you will have
    The holy blessing
  \end{translation}
\endsong
