% Santo Daime: Nova Dimensão (Padr. Alfredo)
% ==========================================
%
\audio[title={Nossa Irmandade}]{https://www.nossairmandade.com/hinario/1/Ora\%C3\%A7\%C3\%A3o}
\audio[title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\setcounter{songnum}{15}
\beginsong{Vida}[by={Pard. Alfredo},key={Am},sks={Am}]
  \audio[key={Am}]{https://www.youtube.com/watch?v=Xboe1-JfM_Y}
  \mnbeginchorus\memorize
    \[^\mn{A}]Vida \[^\mn{C}]São |\[\mnc{E}Am]João, vida \[\mnc{D}(Dm)]meu \[^\mn{E}]Je|\[\mnc{A}Am]su\[^\bm]s
    A \[^\mn{C}]lu\[^\mn{E}]a |\[\mnc{A}A7]cheia, seu bri\[^\bm\mn{G}]lho \[^\mn{A}]re|\[\mnc{D}Dm]lu\[^\bm]z
    \lrep \[^\mn{A}]É tão bo|\[\mnc{B}Bm7b5]ni\[^\mn{A}]to, o poder \[\mnc{F}(Dm/F)]da \[^\mn{D}]fo\[^\mn{F}]gue|\[Am]i\[^\mn{E}]ra
    Queima a \[\mnc{C}C]noit\[^\mn{A}]e in\[^\mn{E}]te|\[E7]i\[^\mn{D}]ra, mis\[^\mn{C}]té\[^\bm\mn{B}]rio \[^\mn{C}]da |\[\mnc{A}Am]Cruz \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    Esta lem|^brança é da e^terni|^da\[\bm]de
    Esta ver|^dade nos e\[\bm]leva as|^si\[\bm]m
    \lrep Lembrando |^sempre a Luz ^deste di|^{'a}
    Oh Vir^gem Mari|^{'a}, vós lem\[\bm]brai de |^mim \rrep
  \endchorus
  \beginchorus
    Aqui na |^Terra a vida é ^como |^é
    Domina|^dor da vida é \[\bm]São Jo|^sé\[\bm]
    \lrep Oh Patri|^arca, nos as^cenda Lu|^z
    Vida ^meu Jesu|^s, Espe\[\bm]rança e |^Fé \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-08
    theMelody = \relative a' {
      \key a \minor \time 4/4 \partial 4.
      a8 a c | e8 e8 e8 e8 d4 e |
      \set melismaBusyProperties = #'()
      \slurDown
        a,2~ a8
      \unset melismaBusyProperties
      a8 c e | a8 a8 a8 a8 g4 a4 | d,2~ d8
      \repeat volta 2 {
        a'8 a a | b a a a f4 d8 f8~ | f8 e8 e8 e8 c4 a8 e'8~
        | e8 d d c8 b4 c4 | a2~ a8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
        Vi -- da São | Jo -- ão
        Vi -- da meu Je -- | sus; __ _
        A lu -- a | chei -- a
        seu bri -- lho re -- | luz. __
      \repeat volta 2 {
        É tão bo -- | ni -- to_o po -- der da fo -- guei -- ra;
        Quei -- ma_a noi -- te_in -- tei -- ra
        mis -- té -- rio da | Cruz. __
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Es -- ta lem -- | bran -- ça_é
      da e -- ter -- ni -- | da -- de;
      Es -- ta ver -- | da -- de
      nos e -- le -- va_as -- | sim. __
      \repeat volta 2 {
        Lem -- bran -- do | sem -- pre
        a Luz des -- te di -- a;
        Oh Vir -- gem Ma -- ri -- a
        Vós lem -- brai de | mim. __
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      A -- qui na | Ter -- ra_a
      vi -- da_é co -- mo | é; __ _
      Do -- mi -- na -- | dor da vi -- da_é
      São Jo -- | sé. __
      \repeat volta 2 {
        Oh Pat -- ri -- | ar -- ca
        nos a -- scen -- da Luz; __
        \skip 1 Vi -- da meu Je -- sus __
        Es __ -- \skip 1 pe -- ran -- ça_e | Fé. __
      }
    }
    theChords = \chordmode {
      s4. | a2:m \parenthesize d2:m| a1:m | a:7 | d2:m~ d8:m
      \repeat volta 2 {
         d4.:m | b2:m7.5- \parenthesize d2:m/f | a2:m c | e1:7 | a2:m~ a8:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % to fit all on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}\scriptsize % to fit on one spread
    Life Saint John, life my Jesus
    The full moon, its glow shines
    It's so beautiful, the power of the fire
    Burn all night, mystery of the Cross
    \nextverse
    This memory is from eternity
    This truth lifts us like this
    Always remembering the Light of this day
    Oh Virgin Mary, you remember me
    \nextverse
    Here on Earth, life is what it is
    Dominant of life is St. John
    Oh Patriarch, ascend us to Light
    Life my Jesus, Hope and Faith
  \end{translation}
\endsong
