% Santo Daime: closing for São Miguel & Mesa Branca works
% =======================================================
%

{ % Put everything in this file in a block to not bleed settings

% use Roman numerals for song (prayer) numbering:
\renewcommand{\thesongnum}{\Roman{songnum}}
\setcounter{songnum}{1}


\beginsong{Em Pé Firme na Floresta}[by={Padr. Alfredo}, tags={perfilado, mazurca, 3x}, off={Tratorista}, key={Am}, gk={Am, G\shrp{}m--(Am)}]
  \audio{https://www.nossairmandade.com/hymn/551/EmP\%C3\%A9FirmeNaFloresta}
  \newchords{chords_empefirme_a}\newchords{chords_empefirme_b}
  \meter{6}{4}
  \mnbeginverse
    \beginrep\memorize[chords_empefirme_a]
    \[^\mn{E}]Em pé |\[\mnc{A}Am]fir\[^\mn{E}]me \[^\mn{C}]na \[^\mn{B}]Flo\[\bmc\mn{A}]res\[^\mn{E}]ta
    \[^\mn{C}]Re\[^\mn{A}]ce|\[\mnc{C}E7]ben\[^\mn{B}]do a \[^\mn{A}]san\[^\mn{G#}]ta \[\mnc{A}Am]Luz
      \endrep
  \mnendverse\glueverses\mnbeginverse
    \beginrep\memorize[chords_empefirme_b]
    \[^\mn{A}]Sou \[^\mn{B}]hu|\[\mnc{C}Am]mil\[^\mn{E}]de, \[^\mn{D}]sou \[^\mn{C}]hu\[Fmaj7]mil\[^\mn{B}]de
    \[^\mn{G#}]Sou \[^\mn{B}]hu|\[\mnc{E}E7]mil\[^\mn{D}]de \[^\mn{C}]de \[^\mn{B}]Je\[\mnc{A}Am]sus
    \endrep
  \mnendverse
  \notesoff
  \beginverse\replay[chords_empefirme_a]
    \beginrep
    O im|^pério destas ^matas
    Não e|^xiste força mai^or
      \endrep
  \endverse\glueverses\beginverse\replay[chords_empefirme_b]
    \beginrep
    Agora a|^qui peço fir^meza
    As Es|^trelas, a Lua e ao ^Sol
    \endrep
  \endverse
  \beginverse\replay[chords_empefirme_a]
    \beginrep
    To|^quei a minha cor^neta
    Já é a |^última cha^mada
      \endrep
  \endverse\glueverses\beginverse\replay[chords_empefirme_b]
    \beginrep
    Se per|^filem coman^dantes
    Para |^vencer a jor^nada
    \endrep
  \endverse
  \beginverse\replay[chords_empefirme_a]
    \beginrep
    Esta |^força verda^deira
    É o |^reinado do ^Sol
      \endrep
  \endverse\glueverses\beginverse\replay[chords_empefirme_b]
    \beginrep
    Em |^cima vivem os ^astros
    E em|^baixo vivem os ^paus
    \endrep
  \endverse
  \beginverse\replay[chords_empefirme_a]
    \beginrep
    Oh! Meu |^Pai onipo^tente
    Que me dá |^força e me se^gura
      \endrep
  \endverse\glueverses\beginverse\replay[chords_empefirme_b]
    \beginrep
    Para |^eu ser Vosso ^filho
    E me li|^vrar das amar^guras
    \endrep
  \endverse
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 6/4 \partial 4.
      \repeat volta 2 {
        r8 \posectionmark "A" e8( e)
        | a4 e8( e) c'8 b  a4 e8( e) c8 a
        | c4 b8( b) a gis  a4( a8)
      }
      \repeat volta 2 {
        \parenthesize a8 \sectionmark "B" a( b)
        | c4 e d8 c  c4 b8( b) gis b
        | e8( e) d( d) c b  a4( a8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Em pé | fir -- me __ _ na Flo -- res -- ta; __ _
        Re -- ce -- | ben -- do a san -- ta Luz. __ _
      \set stanza = "1.B"
        \skip 1 Sou hu -- | mil -- de, sou hu -- mil -- de; __ _
        Sou hu -- | mil -- _ de _ de Je -- sus. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
        O im -- | pé -- rio __ _ des -- tas ma -- tas; __ _
        Não e -- | xis -- te for -- ça mai -- or. __ _
      \set stanza = "2.B"
        A -- go -- ra~a -- | qui pe -- ço fir -- me -- za; __ _
        As Es -- | tre -- las, a Lu -- a~e ao Sol. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
        To -- _ | quei a mi -- nha cor -- ne -- ta; __ _
        Já é~a | úl -- ti -- _ ma cha -- ma -- da.
      \set stanza = "3.B"
        \skip 1 Se per -- | fi -- lem co -- man -- dan -- tes; __ _
        Pa -- ra | ven -- _ cer __ _ a jor -- na -- da.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
        Es -- ta | for -- ça __ _ ver -- da -- dei -- ra; __ _
        É o | rei -- na -- _ do do Sol. __ _
      \set stanza = "4.B"
        \skip 1 Em __ _ | ci -- ma vi -- vem~os as -- tros; __ _
        E em -- | bai -- _ xo __ _ vi -- vem~os paus. __ _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
        Oh! Meu | Pai o -- _ ni -- po -- ten -- te;
        Que me dá | for -- ça e me se -- gu -- ra.
      \set stanza = "5.B"
        \skip 1 Pa -- ra | eu ser Vos -- so fi -- lho
        E me li -- | vrar __ _ das __ _ a -- mar -- gu -- ras.
      }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a2.:m a:m | e:7 a4.:m
      }
      \repeat volta 2 {
        s4. | a2.:m f:maj7 | e:7 a4.:m
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Standing firm in the forest, receiving the Holy Light
    I am humble, I am humble, I am humble of Jesus
    \nextverse
    The Empire of these forests; no force is greater than this
    Now here I ask for firmness; from the stars, the Moon and the Sun
    \nextverse
    I sounded my trumpet; it's already th last call
    Stand up straight, commanders, in order to overcome the journey
    \nextverse
    This true force is the kingdom of the Sun
    In the heights dwell the heavenly bodies, and down here dwell the logs
    \nextverse
    Oh! My Omnipotent Father who gives me strength and secures me
    For me to be Your son, and to deliver me from bitterness
  \end{translation}
\endsong


\beginsong{Devo Amar Aquela Luz}[by={Mestre Irineu Serra}, tags={perfilado, 2x}, key={Am}, gk={Am, (G\shrp{}m)--(Cm)}]
  \audio{https://www.nossairmandade.com/hymn/220/DevoAmarAquelaLuz}
  \meter{2}{4}
  \mnbeginverse
    \[\mn{A}]De\[\mn{B}]vo a|\[\mnc{C}Am]mar |\[\mnc{B}E7]a\[\mn{A}]que\[\mn{G#}]la |\[\mnc{A}Am]luz | \e
    \[\mn{C}]O \[\mn{E}]Di|\[\mn{A}]vi|\[\mnc{G}A7]no a\[\mn{E}]on\[\mn{C}]de es|\[\mnc{D}Dm]tá | \e
    Pa\[\mn{F}]ra |\[\mn{A}]ser |\[\mn{G}]um \[\mn{F}]fi\[\mn{E}]lho |\[\mn{D}]seu
    \[\mn{C}]No |\[Am]cora|\[\mnc{B}E7]ção \[\mn{D}]eu |\[\mn{B}]de\[\mn{C}]vo a|\[\mnc{A}Am]mar
    \[\mn{E}]No |\[\mn{A}]co\[\mn{B}]ra|\[\mnc{C}C]ção \[\mn{D}]eu |\[\mnc{E}E7]de\[\mn{F}]vo a|\[\mn{E}]mar \[\mn{C}]a |\[\mnc{A}Am]luz | \e
  \mnendverse
  \mnbeginverse\memorize
    \ind \[^\mn{A}]A \[^\mn{C}]Vir\[^\mn{E}]gem |\[\mnc{A}Am]Mãe |\[\mnc{G}A7]foi \[^\mn{E}]quem \[^\mn{C}]me |\[\mnc{D}Dm]deu | \e
    \ind Para en\[^\mn{F}]si|\[^\mn{A}]nar |\[^\mn{G}]os \[^\mn{F}]meus \[^\mn{E}]ir|\[^\mn{D}]mãos
    \ind |\[\mnc{C}Am]Para |\[\mnc{B}E7]ser \[^\mn{D}]um |\[^\mn{B}]fi\[^\mn{C}]lho |\[\mnc{A}Am]seu
    \ind |\[^\mn{A}]Pa\[^\mn{B}]ra |\[\mnc{C}C]ser \[^\mn{D}]um |\[\mnc{E}E7]fi\[^\mn{F}]lho |\[^\mn{E}]seu \[^\mn{C}]de a|\[\mnc{A}Am]mor | \e
  \mnendverse
  \notesoff
  \beginverse
    \ind No cora|^ção |^este pri|^mor | \e
    \ind Conhe|cer |esta ver|dade
    \ind |^Deus do |^Céu foi |quem man|^dou
    \ind |Deus do |^Céu foi |^quem man|dou a |^luz | \e
  \endverse
  \begin{translation}[EN]
    I must love this light, the Divine wherever it is, to be a son of Yours
    In the heart I must love, in the heart I must love the light
    \nextverse
    The Virgin Mother who gave me to teach my brothers and sisters
    To be a son of Yours, to be a son of Yours of love
    \nextverse
    In the heart this splendor, to know this truth
    God in Heaven is the one who sent, God in Heaven is the one who sent the light
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 2/4 \partial 4.
      r8 \posectionmark "1." a8 b
      | c2 | b4 a8 gis8 | a2~ | a4 c8 e | a2 | g4 e8 c8
      | d2~ | d4 d8 f8 | a2 | g4 f8 e | d4. c8 | c4 c | b d
      | b c | a4. e8 a4 b | c d | e f | e4. c8 | a2~ | a8
      \repeat volta 2 {
        a8 \sectionmark "2., 3." c e
        | a2 | g4 e8 c | d2~ | d8( \parenthesize d) d f | a2
        | g4 f8 e | d4.( d8) | c4 c | b d | b c | a2
        | a4 b | c d | e f | e4. c8 | a2~ | a8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      De -- vo~a -- | mar | a -- que -- la | luz; | _
      O Di -- | vi -- | no~a -- on -- de~es -- | tá; | _
      Pa -- ra | ser | um fi -- lho | seu;
      No | co -- ra -- | ção eu | de -- vo~a -- | mar;
      No | co -- ra -- | ção eu | de -- vo~a -- | mar a | luz. | _
      <<
        {
          \set stanza = "2."
          A Vir -- gem | Mãe | foi quem me | deu; | _
          Para en -- si -- | nar | os meus ir -- | mãos; __ _
          | Pa -- ra | ser um | fi -- lho | seu;
          | Pa -- ra | ser um | fi -- lho | seu de~a -- | mor. | _
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "3."
          No co -- ra -- | ção | es -- te pri -- | mor; | _ _
          Co -- nhe -- | cer | es -- ta ver -- | da -- de;
          | Deus do | Céu foi | quem man -- | dou;
          | Deus do | Céu foi | quem man -- | dou a | luz. | _
        }
      >>
    }
    theChords = \chordmode {
      s4. | a2:m | e:7 | a:m | a:m | a:m | a:7
      | d:m | d:m | d:m | d:m | d:m | a:m | e:7
      | e:7 | a:m | a:m | c | e:7 | e:7 | a:m | a8:m
      \repeat volta 2 {
        s4. | a2:m | a:7 | d:m | d:m | d:m
        | d:m | d:m | a:m | e:7 | e:7 | a:m
        | a:m | c | e:7 | e:7 | a:m | a8:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Prece para o Encerramento da Reunião}[by={Allan Kardec}]
  \begin{passage}[PT]{}
    Agradecemos aos bons espíritos que anuíram em vir
    comunicar-se conosco e lhjes pedimos que nos
    ajudem a por em prática as instruções que nos
    deram e façam com que ao sairmos daqui cada um de
    nós se sinta fortalecido na prática do bem e do
    amor ao próximo.
    \par
    Desejamos igualmente que as instruções que recebemos
    sejam proveitosas aos espíritos sofredores,
    ignorantes ou viciosos, que hajam assistido à nossa
    reunião, espíritos esses para os quais imploramos
    misericórdia de Deus.
  \end{passage}
  \begin{passage}[EN]{Prayer to Close the Meeting}
    We give thanks to the good spirits who have come
    to communicate with us, and ask them to help us put
    the advice they've given us into practice. We also
    ask that, when we leave this gathering, they help
    us to feel strengthened in the practice of goodness
    and love toward our fellow human beings.
    \par
    We hope that today's teachings are healing to all
    suffering, unaware of misguided spirits who have
    been present at this meeting. For them we implore
    God's mercy.
  \end{passage}
\endsong


\vfill
\begin{intersong}
  \vspace{1ex}
  \textbf{Finalmente:}
  \begin{itemize}
    \item 3 x Pai Nosso \& Ave Maria
    \item Credo
    \item Salve Rainha
    \item Encerramento por Juramidam
    \item Sinal da Cruz
  \end{itemize}
\end{intersong}


}
