% Santo Daime: Hinos Diversões do Mestre
% ======================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\audio{https://www.youtube.com/watch?v=NObHfoO_1d8}

\beginsong{Pra Pilar}[by={Mestre Irineu Serra}, key={Bm}, gk={Bm, Am--Cm}]
  \newchords{chords_prapilar_a}\newchords{chords_prapilar_b}
  \mnbeginverse\memorize[chords_prapilar_a]
    \[^\mn{D}]Dessa es\[\bm]trada de on\[^\mn{F#}]de eu |\[\mnc{A}A]venho, \[\bmc\mn{F#}]pra \[^\mn{D}]pi|\[\mnc{B}Bm]lar \altchords{\id[1]{(Dm)}|C |Dm}
    \[^\mn{D}]Venho da \[\bm]terra do ci|\[\mnc{F#}F#7]gano, \[\bmc\mn{E}]pra \[^\mn{D}]pi|\[\mnc{B}Bm]lar \altchords{|A7 |Dm}
    \[^\mn{D}]A Ra\[\bm]inha me \[^\mn{F#}]man|\[\mnc{A}A]dou, \[\bmc\mn{F#}]pra \[^\mn{D}]pi|\[\mnc{B}Bm]lar \altchords{|C |Dm}
    \[^\mn{D}]Eu pas\[\bm]sar aqui can|\[\mnc{F#}F#7]tando, \[\bmc\mn{E}]pra \[^\mn{D}]pi|\[\mnc{B}Bm]lar \altchords{|A7 |Dm}
  \mnendverse\glueverses\mnbeginchorus\memorize[chords_prapilar_b]
    \[^\mn{D}]É pra pi\[\bm]lar \[^\mn{E}]es\[^\mn{F#}]tou \[^\mn{D}]pi|\[\mnc{E}A]lando \altchords{|C}
    Estou \[^\mn{D}]pi\[\bmc\mn{E}]lando é pra \[^\mn{D}]pi|\[\mnc{B}Bm]lar \altchords{|Dm}
  \mnendchorus
  \notesoff
  \beginverse\replay[chords_prapilar_a]
    Passan^do por entre as |^flores, ^pra pi|^lar
    Vejo um ^retrato or|^nado, ^pra pi|^lar
    Me pa^rece ser um |^rei, ^pra pi|^lar
    Que esta^rá ali encan|^tado, ^pra pi|^lar
  \endverse\glueverses\beginchorus\replay[chords_prapilar_b]
    É pra pi^lar estou pi|^lando
    Estou pi^lando é pra pi|^lar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative f'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key b \minor \time 4/4 \partial 2.
      d8 \posectionmark "A" d8 d8 d8 d8 fis8 | a4. a8 fis4. d8 | b4 d8 d8 d8 d8 d8 d8 | fis4. fis8 e4. d8
      | b4 d8 d8 d8 d8 d8 fis8 | a2 fis4. d8 | b4 d8 d8 d8 d8 d8 d8 | fis4. fis8 e4. d8
      | b8
      \repeat volta 2 {
        d8 \sectionmark "B" d8 d8 d8 e8 fis8 d8 | e8 e8 e8 d8 e8 e8 e8 d8
      } \alternative {
        { | b8 }
        { | b4 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Des -- sa~es -- tra -- da de~on -- de~eu | ve -- nho, pra pi -- | lar;
      Ve -- nho~da ter -- ra do ci -- | ga -- no, pra pi -- | lar;
      A Ra -- i -- nha me man -- | dou, pra pi -- | lar;
      Eu pas -- sar a -- qui can -- | tan -- do, pra pi -- | lar.
      \repeat volta 2 {
        \set stanza = "1.B"
        É pra pi -- lar es -- tou pi -- | lan -- do;~Es
        tou pi -- lan -- do~é pra pi --
      } \alternative {
        { | lar. }
        { | lar. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Pas -- san -- do por en -- tre~as | flo -- res, pra pi -- | lar;
      Ve -- jo~um re -- tra -- to or -- | na -- do, pra pi -- | lar;
      Me pa -- re -- ce ser um | rei, pra pi -- | lar;
      Que~es -- ta -- rá~a -- li en -- can -- | ta -- do, pra pi -- | lar.
      \repeat volta 2 {
        \set stanza = "2.B"
        É pra pi -- lar es -- tou pi -- | lan -- do;~Es
        tou pi -- lan -- do~é pra pi --
      } \alternative {
        { | lar. }
        { | lar. }
      }
    }
    theChords = \chordmode {
      s2. | a1 | b:m | fis:7 | b:m | a | b:m | fis:7 | b8:m
      \repeat volta 2 {
        s2.~s8 | a1
      } \alternative {
        { | b8:m }
        { | b4:m }
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    This path from where I come, to pound; I come from the lands of the gypsies, to pound
    The Queen ordered me, to pound; for me to pass here singing, to pound
    \nextverse
    It is to pound, I am pounding, I am pounding, it is to pound
    \nextverse
    Passing between the flowers, to pound; I see a ornate portrait, to pound
    I look like I am a king, to pound; that will be enchanted, to pound
    \nextverse
    It is to pound, I am pounding, I am pounding, it is to pound
  \end{translation}
\endsong


\beginsong{Cachiado}[by={Mestre Irineu Serra}, key={Bm}, gk={Bm, G\shrp{}m--Bm}, tags={3x}]
  \musicnote{Tocar 3 vezes}
  \mnbeginchorus
    \[\mn{B}]Ca\[\mn{C#}]che|\[\mnc{D}D]a\[\mn{B}]do \[\bmc\mn{D}]ve\[\mn{C#}]nha |\[\mnc{B}Bm]cá \altchords{\id[1]{(Am)}|C |Am}
    \[\bm]Car\[\mn{C#}]ra|\[\mnc{D}D]cá \[\mn{C#}]car\[\mnc{B}F#7]ra \[\mn{A#}]cá |\[\mnc{B}Bm]cá \altchords{|C E7 |Am}
  \mnendchorus\glueverses\mnbeginchorus
    \[\bmc\mn{B}]Carra|\[\mnc{E}Em]cá car\[\bmc\mn{G}]ra cá |\[\mnc{B}Bm]cá \altchords{|Dm |Am}
    \[\bmc\mn{F#}]Car\[\mn{G}]ra|\[\mnc{F#}F#7]cá \[\mn{E}]car\[\bmc\mn{D}]ra \[\mn{C#}]cá |\[\mnc{/}Bm]cá \altchords{|E7 |Am}
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key b \minor \time 4/4 \partial 2
      \repeat volta 2 {
        b4 \posectionmark "A" cis | d4. b8 d4 cis | b2 b4 cis
        | d cis b ais | b2
      }
      \repeat volta 2 {
        b4 \sectionmark "B" b | e e g g | b2 fis4 g
        | fis e d cis
      } \alternative {
        { | d2 }
        { | b2 \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        Ca -- che -- | a -- do ve -- nha | cá;
        Car -- ra -- | cá car -- ra cá | cá.
      }
      \repeat volta 2 {
        Car -- ra -- | cá car -- ra cá | cá;
        Car -- ra -- | cá car -- ra cá | cá.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | d1 | b:m | d2 fis2:7 | b2:m
      }
      \repeat volta 2 {
        s2 | e1:m | b:m | fis:7
      } \alternative {
        { | b2:m }
        { | b2:m }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Cacheado come here, Carracá carra cá cá
    Carracá carra cá cá, Carracá carra cá cá
  \end{translation}
\endsong

