% Santo Daime: Cruzeirinho (Mestre Irineu)
% ========================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{117}

\beginsong{Dou Viva a Deus nas Alturas}[by={Mestre Irineu Serra},tags={valsa},key={C},sks={C, D}]
  \audio{https://www.nossairmandade.com/hymn/85/DouVivaADeusNasAlturas}
  \newchords{chords_douvivaadeus_a}\newchords{chords_douvivaadeus_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_douvivaadeus_a]
    \[^\mn{G}]Dou |\[\mnc{C}C]viva a |Deus nas \[^\mn{E}]al|\[\mnc{G}G]turas \altchords{\id[1]{(D)}|D | |A}
    \[^\mn{E}]E a |\[\mnc{A}Am]Vir\[^\mn{G}]gem |\[\mnc{F}F]Mãe \[^\mn{A}]nos\[^\mn{B}]so a|\[\mnc{C}C]mor \altchords{|Bm |G |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_douvivaadeus_b]
    |\[\mnc{C}C]Vi\[^\mn{B}]va \[^\mn{A}]to|\[\mnc{C}Am]do \[^\mn{B}]Ser \[^\mn{A}]Di|\[\mnc{D}Dm]vino \altchords{|D |Bm |Em}
    E Je|\[\mnc{G}G]sus Cris|\[\mnc{E}C/E]to \[^\mn{C}]Reden|\[C]tor \altchords{|A |D/F\# |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_douvivaadeus_a]
    Eu |^peço a |Deus nas al|^turas
    Pa|^ra Vós |^me ilumi|^nar
    \endchorus\glueverses\beginchorus\replay[chords_douvivaadeus_b]
    Bo|^tai-me |^no bom ca|^minho
    E li|^vrai-me |^de todo |^mal
  \endchorus
  \beginchorus\replay[chords_douvivaadeus_a]
    Eu |^vivo a|qui neste |^mundo \altchords{\id[2]{ED (C)}|C |Am |Em}
    Encos|^tado a |^este Cru|^zeiro \altchords{|F |G |C}
    \endchorus\glueverses\beginchorus\replay[chords_douvivaadeus_b]
    Ve|^jo tan|^ta ilumi|^nária \altchords{|C |Am |Dm}
    Do |^nosso |^Deus Verda|^deiro \altchords{|G |G7 |C}
  \endchorus
  \beginchorus\replay[chords_douvivaadeus_a]
    Es|^ta ilumi|nária que eu |^vejo \altchords{\id[3]{MK (C)}|C |Am |C}
    A|^legra o |^meu cora|^ção \altchords{|Dm7 |G7 |C}
    \endchorus\glueverses\beginchorus\replay[chords_douvivaadeus_b]
    Es|^tas flores |^que rece|^bemos \altchords{|Am |Am7 |Dm}
    Pa|^ra nos|^sa Salva|^ção \altchords{|G |Fmaj7 |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 4
      \repeat volta 2 {
        g4\posectionmark "A" | c4. c8 c4 | c4 c4 e4 
        | g4 g4 e4 | a2 g4 | f4 a,4 b4 | c4( c4)
      } \break
      \repeat volta 2 {
        \parenthesize g4\sectionmark "B" | c4 b4 a4 | c4 b4 a4
        | d4 d8 d8 d4 | g2 g4 | e4 c4 c4 | c4( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Dou | vi -- va a | Deus nas al -- | tu -- ras;
        E~a | Vir -- gem | Mãe nos -- so~a -- | mor. __ _
      }
      \repeat volta 2 {
        \skip 1 | Vi -- va to -- | do Ser Di -- | vi -- no;
        E Je -- | sus Cris -- | to Re -- den -- | tor. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Eu | pe -- ço a | Deus nas al -- | tu -- ras;
        Pa -- | ra Vós | me~i -- lu -- mi -- | nar. __ _
      }
      \repeat volta 2 {
        Bo -- | tai -- _ me no bom ca -- | mi -- nho;
        E li -- | vrai -- me | de to -- do | mal. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Eu | vi -- vo a -- | qui nes -- te | mun -- do;~En
        cos -- | ta -- do~a | es -- te Cru -- | zei -- ro.
      }
      \repeat volta 2 {
        Ve -- | jo __ _ tan -- | ta~i -- lu -- mi -- | ná -- ri -- a;
        Do | nos -- so | Deus Ver -- da -- | dei -- ro.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Es -- | ta~i -- lu -- mi -- | ná -- ria que~eu | ve -- jo;
        A -- | le -- gra~o | meu co -- ra -- | ção. __ _
      }
      \repeat volta 2 {
        Es -- | tas flo -- res | que re -- ce -- | be -- mos; __ _
        Pa -- | ra nos -- | sa Sal -- va -- | ção. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2. | c | g
        | a:m | f | c2
      }
      \repeat volta 2 {
        \set chordChanges = ##f
        s4 | c2. | a:m | d:m
        | g | c:/e | c2
        \set chordChanges = ##t
      }
    }
    \layout { #(layout-set-staff-size 15) }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I give viva to God in the Heights, and to the Virgin Mary, our love
    I give viva to every Divine Being, and Jesus Christ the Redeemer
    \nextverse
    I ask the God in the Heights, for Thou to illuminate me
    Put me on the right path and deliver me from all evil
    \nextverse
    I live here in this world, next to this Cross
    I see so much Light from our true God
    \nextverse
    This brightness that I see gladdens my heart
    These flowers that we receive for our salvation
  \end{translation}
\endsong

\beginsong{Todos Querem Ser Irmão}[by={Mestre Irineu Serra},key={Am},sks={Am}]
  \audio{https://www.nossairmandade.com/hymn/86/TodosQueremSerIrm\%C3\%A3o}
  \newchords{chords_todosquerem_a}\newchords{chords_todosquerem_b}
  \mnbeginchorus\memorize[chords_todosquerem_a]
    \[^\mn{E}]Todos |\[\mnc{A}Am]que\[^\mn{E}]rem \[\bmc\mn{C}]ser \[^\mn{A}]ir|\[\mnc{B}E/B]mã\[^\mn{A}]os
    \[\mnc{E}E]Mas \[^\mn{G}]não |\[G]têm a \[\mnc{D}Dm]leal|\[\mnc{C}C]da\[^\mn{A}]de\[Am]
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_todosquerem_b]
    \[^\mn{E}]Para \[^\mn{G}]se|\[G]guir \[^\mn{D}]na \[Dm]Vida \[^\mn{G}]E|\[\mnc{A}Am]spírita
    Que \[\bmc\mn{A}]é \[^\mn{C}]o |\[\mnc{E}E]Rei\[^\mn{D}]no \[\mnc{B}E7/B]da \[^\mn{C}]Ver|\[\mnc{A}Am]dade
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_todosquerem_a]
    É o |^Reino ^da Ver|^dade \altchords{\id[2]{ED}|Am |F}
    É ^a Es|^trada ^do A|^mor^ \altchords{|G |Am}
    \endchorus\glueverses\beginchorus\replay[chords_todosquerem_b]
    É todos |^prestar ^aten|^ção \altchords{|G |F}
    ^Os en|^sinos do ^profes|^sor \altchords{|E E7 |Am}
  \endchorus
  \beginchorus\replay[chords_todosquerem_a]
    Os en|^sinos do ^profes|^sor \altchords{\id[3]{MK}|Am | \e}
    É ^quem nos |^traz be^las li|^ções^ \altchords{|G Dm |Am}
    \endchorus\glueverses\beginchorus\replay[chords_todosquerem_b]
    Para |^todos ^se u|^nir \altchords{|G Dm |Am}
    E ^respei|^tar os ^seus ir|^mãos \altchords{|C G |Am}
  \endchorus
  \beginchorus\replay[chords_todosquerem_a]
    Respei|^tar os ^seus ir|^mãos
    Com ^ale|^gria e ^com a|^mor^
    \endchorus\glueverses\beginchorus\replay[chords_todosquerem_b]
    Para |^todos ^conhe|^cer
    E ^saber |^dar o ^seu va|^lor
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        r8\posectionmark "A" e8 e8 | a4. e8 c'4. a8 | b4 a4 e4. g8
        | g4. g8 d4. d8 | c4( a4.)
      }
      \repeat volta 2 {
        \parenthesize e'8\sectionmark "B" e8 g8 | g4. d8 d4 d8( \parenthesize g8) | a8( a a a) a,4. c8
        | e4( e8) d8 b4. c8 | a2( a8)
      }
    }
    theLyricsOne = \lyricmode { % no repeats 'coz begin with a rest
      \set stanza = "1."
      To -- dos | que -- rem ser ir -- | mã -- os;
      Mas não | têm a le -- al -- | da -- de.
      \set stanza = "1.B"
      Pa -- ra se -- | guir na Vi -- da E -- | spí -- ri -- ta;
      Que é o | Rei -- _ no da Ver -- | da -- de.
  }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      É o | Rei -- no da Ver -- | da -- de;~É
      a Es -- | tra -- da do A -- | mor. __ _
      \set stanza = "2.B"
      É to -- dos | pres -- tar a -- ten -- _ | ção; __ _ _ _
      Os en -- | si -- nos  do pro -- fes -- | sor. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Os en -- | sinos do pro -- fes -- | sor;
      é quem nos | traz be -- las li -- | çõ -- es.
      \set stanza = "3.B"
      \skip 1 Pa -- ra | to -- dos se u -- _ | nir; __ _ _
      E res -- pei -- | tar __ _ os seus ir -- | mã -- os.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      Res -- pei -- | tar os seus ir -- | mãos;
      Com a -- le -- | gria e com a -- | mor. __ _
      \set stanza = "4.B"
      \skip 1 Pa -- ra | to -- dos co -- nhe -- _ | cer; __ _ _
      E sa -- ber | dar __ _ o seu va -- | lor. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1:m | e2/b e
        | g2 d:m | c a8:m
      }
      \repeat volta 2 {
        s4. | g2 d:m | a:m a:m
        | e e:7/b | a2:m~ a8:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    All want to be brothers
    But don't have loyalty
    To follow the Spiritual Life
    Which is the Kingdom of Truth
    \nextverse
    It's the Kingdom of Truth
    It's the path of Love
    And everybody must pay attention
    To the teachings of the professor
    \nextverse
    The teachings of the professor
    Bring us beautiful lessons
    For everybody to come together
    And respect one's brothers and sisters
    \nextverse
    To respect one's brothers and sisters
    With happiness and with love
    For everybody to know
    And learn to appreciate one another
  \end{translation}
\endsong


\beginsong{Confia}[by={Mestre Irineu Serra},key={Dm},sks={Dm, Em, Cm}]
  \audio{https://www.nossairmandade.com/hymn/87/Confia}
  \mnbeginchorus\memorize
    \[^\mn{A}]Con|\[Dm]fia, con\[\bm]fia, con|\[^\mn{A}]fia no \[^\mn{F}]Po\[\mnc{G}Gm]der \altchords{\id[1]{(Em)}|Em | - Am}
    \[^\mn{E}]Con|\[^\mn{G}]fia no \[^\mn{E}]sa\[\mnc{F}F]ber \altchords{| - G}
    \[^\mn{D}]Con|\[^\mn{F}]fia \[^\mn{G}]na \[\mnc{A}A7]for\[^\mn{G}]ça \altchords{| - B7}
    A|\[^\mn{F}]on\[^\mn{E}]de \[^\mn{D}]po\[^\mn{C#}]de \[\mnc{D}Dm]ser \altchords{| - Em}
  \mnendchorus
  \notesoff
  \beginchorus
    |^ Esta ^força |é muito ^simples
    |Todo mundo ^vê
    Mas |passa por ^ela
    E não pro|cura compreen^der
  \endchorus
  \beginchorus
    |^ Es^tamos |todos reu^nidos \altchords{\id[2]{ED (Dm)}|Dm |D7/F\# Gm}
    Com a nos|sa chave na ^mão \altchords{|C7 F}
    A lim|par mentali^dade \altchords{|Bbmaj7 A7sus4}
    Para en|trar neste sa^lão \altchords{|A7/G Dm}
  \endchorus
  \beginchorus
    |^{\up{2}(ros)} Este ^é |o Salão Dou^rado \altchords{\id[3]{MK (Dm)}|Dm |- Gm}
    Do nos|so Pai Verda^deiro \altchords{|A7 Dm}
    Todos |nós somos ^filhos \altchords{| - A7}
    E todos |nós somos her^dei- \altchords{| - Dm}
  \endchorus
  \beginchorus
    |^{\up{1}(ros)} Nós ^to|dos somos ^filhos
    E é pre|ciso traba^lhar
    A|mar o Pai E^terno
    É quem |tem para nos ^dar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 8
      \repeat volta 2 {
        \parenthesize a8\pomark | << \parenthesize d4 a4 >> a8( a8) a4( a8)( a8) | a'8( a8) a8 f8 g4. e8
        | g8 g8 g8 e8 f4. d8 | f4 f8 g8 a4. g8 | f8 e8 d8 cis8 d4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Con -- | fi -- a, con -- fi -- a, con -- | fi -- a no Po -- der;
      Con -- | fi -- a no sa -- ber;
      Con -- | fi -- a na for -- ça;~A --
      | on -- de po -- de ser.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \skip 1 | \skip 1
      Es -- ta for -- _ ça | é __ _ mui -- to sim -- ples;
      | To -- do mun -- do vê;
      Mas | pas -- sa por ela;~E~não pro -- | cu -- ra com -- preen -- der.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1 | \skip 1
      Es -- _ ta -- _ mos | to -- dos re -- u -- nidos;~Com~a
      nos -- | sa cha -- ve na mão;~A
      lim -- | par~men -- ta -- li -- dade;~Pa -- ra~en -- | trar nes -- te sa -- lão.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 | \markup{\super{"2"}\parenthesize ros.}
      Es -- te é __ _ _ | o Sa -- lão Dou -- rado;~Do
      nos -- | so Pai Ver -- da -- deiro;~To --
      dos | nós so -- mos filhos;~E~to --
      dos | nós so -- mos her -- dei-
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \skip 1 | \markup{\super{"1"}\parenthesize ros.}
      Nós __ _ to -- _ _ | dos __ _ so -- mos filhos;~E~é
      pre -- | ci -- so tra -- ba -- lhar;
      A -- | mar~o Pai E -- terno;~é
      quem | tem pa -- ra nos dar.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | d1:m | d2:m g2:m
        | g2:m f2
        | f2 a2:7
        | a2:7 d4.:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Trust, trust, trust the power, trust the knowledge
    Trust the force where it is
    \nextverse
    This force is very simple, everyone can see it
    But they pass by and don't try to understand it
    \nextverse
    We are all together with our key in hand
    Cleaning our mentality to enter this temple
    \nextverse
    This is the Golden Temple of our true Father
    We are all children and we are all heirs
    \nextverse
    We are all children and we need to work
    To love our Eternal Father who has what we need
  \end{translation}
  \noendsongvfill % otherwise the horiz. line signifying song end wouldn't fit
\endsong


\beginsong{Eu Peço}[by={Mestre Irineu Serra},key={C},sks={D, C}]
  \audio{https://www.nossairmandade.com/hymn/88/EuPe\%C3\%A7o}
  \ifshowlilypond%
    \vspace*{-.5ex} % an ugly hack to fit the whole song on one spread
  \fi
  \mnbeginchorus
    \ind \[\mn{E}]Eu |\[\mnc{C}C]pe\[\mnc{G}(G)]ço, \[\mn{E}]eu |\[\mnc{C}C]pe\[\mnc{G}(G)]ço \altchords{\id[1]{(D)}|D (A) |D (A)}
    \ind \[\mn{E}]Eu |\[\mnc{C}C]pe\[\mn{G}]ço ao \[\mn{C}]Pai \[\mn{E}]Di|\[\mnc{D}Dm]vino \altchords{|D |Em}
    \ind Que me |dê a Santa |\[\mnc{G}G7]Luz \altchords{| |A7}
    \ind Para ilu\[\mn{F}]mi|\[\mnc{E}(Em)]nar \[\mn{D}]o \[\mnc{C}G7]meu \[\mn{B}]ca|\[\mnc{C}C]minho \altchords{|(F\#m) A7 |D}
  \mnendchorus
  \mnbeginchorus\memorize
    \[^\mn{E}]Eu |\[\mnc{C}C]pe\[^\mn{G}]ço à \[^\mn{C}]Vir\[^\mn{E}]gem |\[^\mn{C}]Mãe
    \[^\mn{G}]E a \[^\mn{C}]Je\[^\mn{E}]sus |\[^\mn{C}]Cris\[^\mn{G}]to \[^\mn{C}]Re\[^\mn{E}]den|\[\mnc{D}Dm]tor
    Ilumi|nai o meu ca|\[\mnc{G}G7]minho
    Nes\[^\mn{F}]sa Es|\[\mnc{E}(Em)]tra\[^\mn{D}]da \[\mnc{C}G7]do \[^\mn{B}]A|\[\mnc{C}C]mor
  \mnendchorus
  \notesoff
  \beginchorus
    Essa Es|^trada do A|mor \altchords{\id[2]{ED (C)}|C G |C}
    Dentro |do meu cora|^ção \altchords{|Am |Dm}
    Eu |peço a Jesus |^Cristo \altchords{|F |C}
    Que nos |^dê a ^Salva|^ção \altchords{|G7 |C}
  \endchorus
  \beginchorus
    Eu |^peço a Salva|ção \altchords{\id[3]{MK (C)}|C | \e}
    Que só |Vós pode nos |^dar \altchords{| |G}
    Perdo|ai-nos neste |^mundo \altchords{|Dm |G}
    E na vi|^da es^piritu|^al \altchords{|G7 |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'()
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        r8 e4\sectionmark "1." | c2 g4 e'4 | c2 g4 e'4 | c4. g8 c4 e4 | d2 d4 d8 d8
        | d4. d8 d4 d4 | g4 g8 g8 g4 f4 | e4 d4 c4 b4 | c2 c8~
      }
      \repeat volta 2 {
        c8 e4\sectionmark "2." | c4. g8 c4 e4 | c4. g8 c4 e4 | c4 g4 c4 e4 | d2~ d8 d8 d8 d8
        | d4. d8 d4 d4 | g4. g8 g4 f8 f8 | e4 d4 c4 b4 | c2~ c8
      }
      \repeat volta 2 {
        c8\sectionmark "3." c8 e8 | c4. g8 c4 e4 | c2 c4 e4 | c4 g4 c4 e4 | d2. d4
        | d4. d8 d4 d4 | g4. g8 g4 f4 | e4 d4 c4 b4 | c2~ c8~
      }
      \repeat volta 2 {
        c8 e4\posectionmark "4." | c4. g8 c4 e4 | c2 c4 e4 | c4 g4 c4 e4 | d2. d8 d8
        | d4. d8 d4 d4 | g4. g8 g4 f4 | e4 d4 c8 c8 b4 | c2~ c8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Eu | pe -- ço, eu | pe -- ço;
      Eu | pe -- ço~ao Pai Di -- | vi -- no;
      Que me | dê a San -- ta | Luz;
      Pa -- ra ilu -- mi -- | nar o meu ca -- | mi -- nho. __
      \set stanza = "2."
      \skip 1 Eu | pe -- ço~à Vir -- gem | Mãe;
      E~a Je -- sus | Cris -- to Re -- den -- | tor; __ _
      I -- lu -- mi -- | nai o meu ca -- | mi -- nho;
      Nes -- sa Es -- | tra -- da do A -- | mor. __ _
      \set stanza = "3."
      Es -- sa Es -- | tra -- da do A -- | mor;
      Den -- tro | do meu co -- ra -- | ção;
      Eu | pe -- ço~a Je -- sus | Cris -- to;
      Que nos | dê a Sal -- va -- | ção. __ _
      \set stanza = "4."
      \skip 1 Eu | pe -- ço~a Sal -- va -- | ção;
      Que só | Vós po -- de nos | dar;
      Per -- do -- | ai -- nos nes -- te | mun -- do;~E
      na vi -- | da es -- pi -- ri -- tu -- | al. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 \parenthesize g2 | c2 \parenthesize g2
        | c1 | d1:m
        | d1:m | g1:7
        | \parenthesize e2:m \parenthesize g2:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c1 | c1
        | c1 | d1:m
        | d1:m | g1:7
        | \parenthesize e2:m g2:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c1 | c1
        | c1 | d1:m
        | d1:m | g1:7
        | \parenthesize e2:m g2:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c1 | c1
        | c1 | d1:m
        | d1:m | g1:7
        | \parenthesize e2:m g2:7 | c2~ c8
      }
    }
    \layout { #(layout-set-staff-size 15) } % to fit on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I ask, I ask, I ask the Divine Father
    To give me the Holy Light, to illuminate my path
    \nextverse
    I ask the Virgin Mother and Jesus Christ the Redeemer
    To illuminate my way on that Path of Love
    \nextverse
    This path of Love inside my heart
    I ask Jesus Christ to give us salvation
    \nextverse
    I ask for salvation which only You can give us
    Forgive us in this world and in the Spiritual Life
  \end{translation}
\endsong


\beginsong{Está Força}[by={Mestre Irineu Serra},tags={2x, valsa}, key={C},sks={D, C}]
  \audio{https://www.nossairmandade.com/hymn/89/EstaFor\%C3\%A7a}
  \meter{3}{4}
  \newchords{chords_estaforca_a}\newchords{chords_estaforca_b}
  \musicnote{Tocar 2 vezes}
  \mnbeginchorus\memorize[chords_estaforca_a]
    \[^\mn{E}]Es\[^\mn{A}]ta |\[\mnc{G}C]For\[^\mn{F}]ça, |\[\mnc{A}Am]es\[^\mn{B}]te \[^\mn{C}]Po|\[\mnc{G}G]der \altchords{\id[1]{(D)}|D |Bm |A}
    |Eu de\[^\mn{C}]vo a|\[\mnc{A}Am]mar \[^\mn{C}]no |\[\mnc{B}G/B]meu \[^\mn{C}]co\[^\mn{D}]ra|\[\mnc{G}G]ção | \e \altchords{| |Bm |A/C\# |A | \e}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_estaforca_b]
    \[^\mn{E}]Tra\[^\mn{A}]ba|\[\mncii{G}{F}C]lhar |\[\mnc{A}Am]no \[^\mn{B}]mun\[^\mn{C}]do |\[\mnc{G}G]Terra \altchords{|D |Bm |A}
    |A be\[^\mn{C}]ne|\[\mnc{A}Am]fí\[^\mn{C}]cio |\[\mnc{B}G7/B]dos \[^\mn{C}]meus \[^\mn{D}]ir|\[\mnc{C}C]maõs | \e \altchords{| |Bm |A7/C\# |D | \e}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_estaforca_a]
    Estou a|^qui, |^neste lu|^gar \altchords{\id[2]{ED (C)}|C |Am |G}
    |Foi minha |^Mãe |^que me man|^dou | \e \altchords{|C7 |F | |G | \e}
  \endchorus\glueverses\beginchorus\replay[chords_estaforca_b]
    Estamos |^den|^tro desta |^casa \altchords{C7 |F | |C}
    |Onde afir|^mamos a |^{fé e} o a|^mor | \e \altchords{|C7 |F |G7 |C | \e}
  \endchorus
  \begin{translation}
    This force, this power
    I must love in my heart
    I work on Earth
    For the benefit of my brothers and sisters
    \nextverse
    I am here in this place
    It was my Mother who ordered me
    We are here in this house
    Where we affirm faith and love
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 1*5/8
      \repeat volta 2 {
         \parenthesize e8\posectionmark "A" e4 a4 | g2( f4) | a, b c | g2. | g4 g c
        | a2( c4) | b c d | g,2.~ | g8
      } \break
      \repeat volta 2 {
        \parenthesize e'8\sectionmark "B" e4 a | g2( f4) | a, b c | g2 g4 | g4 g c
        | a4( a4) c4 | b c d | c2.~ | c8
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        \set stanza = "1."
        \skip 1 Es -- ta | For -- ça, | es -- te Po -- | der;
        | Eu de -- vo~a -- | mar no | meu co -- ra -- | ção. __ | _
      }
      \repeat volta 2 {
        \set stanza = "1.B"
        \skip 1 Tra -- ba -- | lhar __ _ | no mun -- do | Ter -- ra;
        | A be -- ne -- | fí -- _ cio | dos meus ir -- | maõs. __ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \repeat volta 2 {
        \set stanza = "2."
        Es -- tou a -- | qui, __ _ | nes -- te lu -- | gar;
        | Foi mi -- nha | Mãe __ _ | que me man -- | dou. __ _
      }
      \repeat volta 2 {
        \set stanza = "2.B"
        Es -- ta -- mos | den -- _ | tro des -- ta | ca -- sa;
        On -- de~a -- fir -- | ma -- mos a | fé~e o a -- | mor. __ _
      }
    }
    theChords =  \chordmode {
      \repeat volta 2 {
        s2~ s8 | c2. | a:m | g | g
        | a:m | g/b | g | g8
      }
      \repeat volta 2 {
        s2~ s8 | c2. | a:m | g | g
        | a:m | g:7/b | c | c8
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Quem Procurar Esta Casa}[by={Mestre Irineu Serra},ph={I},key={Am},sks={Am, Gm}]
  \audio{https://www.nossairmandade.com/hymn/90/QuemProcurarEstaCasa}
  \mnbeginchorus\memorize
    |\[\mnc{A}Am]Quem pro\[^\mn{B}]cu\[^\mn{C}]rar \[^\mn{B}]es\[^\mn{A}]ta |\[\mnc{F}Dm/F]ca\[\mnc{D}Dm]sa \altchords{\id{(Em)}|Em |Am/C Am}
    |\[\mnc{A}F]Que a\[^\mn{B}]qui \[\mnc{C}(Bm7&5)]ne\[^\mn{B}]la \[^\mn{A}]che|\[\mnc{E}E]gar \[(E7)] \altchords{|C (F\#m7b5) |B (B7)}
    \lrep En|\[\mnc{A}Am]contra \[^\mn{B}]{com a} \[\mnc{C}C]Vir\[^\mn{B}]gem \[^\mn{A}]Ma|\[\mncii{D}{F}Dm]ri\[\mnc{A}(F)]a \altchords{|Em G |Am (C)}
    |\[\mnc{E}Am]Su\[^\mn{F}]a \[^\mn{E}]sa\[\mnc{D}E7]úde \[^\mn{C}]E\[^\mn{B}]la |\[\mnc{A}Am]dá \rrep \altchords{|Em B7 |Em}
  \mnendchorus
  \notesoff
  \beginchorus
    Mi|^nha Sempre Virgem Ma|^ri^a \altchords{\id[2]{AP (Am)}|Am C |F Dm}
    |^Perdoai ^{os filhos} |^seus ^ \altchords{|Am C |E}
    \lrep |^Vós como ^Mãe sobe|^ra^na \altchords{|Am C |Dm F}
    |^A Divi^na Mãe de |^Deus \rrep \altchords{|E Dm |Am}
  \endchorus
  \beginchorus
    |^Eu peço a vós, bem con|^tri^to \altchords{\id[3]{O (Am)}|Am |Dm}
    Fa|^zendo as mi^{nhas ora}|^ções ^ \altchords{| |E}
    \lrep |^Peço a vós ^a Santa |^Lu^z \altchords{|Am |Dm}
    |^Para ilumi^nar o meu per|^dão \rrep \altchords{|E |Am}
  \endchorus
  \beginchorus
    |^Aqui dentro desta |^ca^sa
    |^Tem tudo ^{que procu}|^rar ^
    \lrep |^Seguindo ^o bom ca|^mi^nho
    |^Fazer bem, ^não fazer |^mal \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \parenthesize e4\posectionmark "A" | a4 a8 b8 c4 b8 a8 | f2 d4( d4)
      | a'4 a8 b8 c4 b8 a8 | e2.
      \repeat volta 2 {
        \parenthesize e4\sectionmark "B" | a,4 a8 b8 c4 b8 a8 | \slurSolid d4.( f8) a2
        \slurDashed
        | e8( e8) f8 e8 d8( d8) c8 b8 | a2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 | Quem pro -- cu -- rar es -- ta | ca -- sa; __ _
      | Que a -- qui ne -- la che -- | gar;
      \repeat volta 2 {
        \parenthesize En -- | con -- tra com~a Vir -- gem Ma -- | ri __ _ -- a;
        | Su -- _ a sa -- ú -- de E -- la | dá.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \parenthesize Mi -- | nha Sem -- pre Vir -- gem Ma -- | ri  -- a; __ _
      | Per -- do -- ai os fi -- lhos | seus.
      \repeat volta 2 {
        \skip 1 | Vós co -- mo Mãe so -- be -- | ra __ _ -- na;
        | A __ _ Di -- vi -- na __ _ Mãe de | Deus.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
        \skip 1 Eu pe -- ço~a vós bem con -- | tri -- to;
        Fa -- | zen -- do as mi -- nhas ora -- | ções.
      \repeat volta 2 {
        \skip 1 | Pe -- ço~a vós a San -- ta | Luz; __ _ _
        | Pa -- ra~i -- lu -- mi -- nar o meu per -- | dão.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 | A -- qui den -- tro des -- ta ca -- sa; __ _
      | Tem tu -- do que pro -- cu -- | rar.
      \repeat volta 2 {
        \skip 1 | Se -- guin -- do o bom ca -- | mi __ _ -- nho;
        | Fa -- _ zer bem não __ _ fa -- zer | mal.
      }
    }
    theChords = \chordmode {
      s4 | a1:m | d2:m/f d:m
      | f2 \parenthesize b:m7.5- | e \parenthesize e4:7
      \repeat volta 2 {
        s4 | a2:m c | d:m \parenthesize f
        | a:m e:7 | a2.:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}\footnotesize % to fit whole song on one spread
    Whoever arrives at this house and comes into it here
    Encounters the Virgin Mary, she is who gives you your well being
    \nextverse
    My Always Virgin Mary, forgive Your children
    You as Sovereign Mother, the Divine Mother of God
    \nextverse
    I beg You so contritely doing my prayers
    I ask Your Holy Light to illuminate my release
    \nextverse
    Here in this house there is everything to find
    Following the right path, doing the right and not the wrong
  \end{translation}
\endsong


\beginsong{Eu Andei na Casa Santa}[by={Mestre Irineu Serra},key={Dm},sks={Dm, Cm}]
  \audio{https://www.nossairmandade.com/hymn/91/EuAndeiNaCasaSanta}
  \meter{3}{4}
  \mnbeginchorus\memorize
    |\[\mnc{D}Dm]Eu \[^\mn{F}]an\[^\mn{E}]dei |\[^\mn{A}]na \[^\mn{F}]Ca\[^\mn{D}]sa |\[\mnc{A}(A)]San|\[\mnc{F}F]ta
    |\[\mnc{D}Dm]Trou\[^\mn{F}]xe \[^\mn{E}]mui|\[^\mn{D}]tas \[^\mn{B&}]coi\[^\mn{A}]sas |\[\mnc{G}Gm]bo|\[\mnc{E}A/E]as
    |\[\mnc{A}A]Tu\[^\mn{C#}]do \[^\mn{E}]vi|\[^\mn{G}]ve \[^\mn{F}]nes\[^\mn{E}]te |\[\mnc{G}Gm]mun|\[\mnc{E}A/E]do
    |\[\mnc{A}A]Pa\[^\mn{G}]re\[^\mn{F}]ce u|\[\mnc{E}A7]ma \[^\mn{D}]coi\[^\mn{C#}]sa-à-|\[\mnc{D}Dm]toa
  \mnendchorus
  \notesoff
  \beginchorus
    |^Pedi li|cença ao Di|^vi|^no \altchords{\id[2]{ED (Dm)}|Dm | |F | \e}
    Para |^estas pa|lavras eu nar|^ra|^{'r} \altchords{|Dm | |A7 | \e}
    |^Perante |os meus ir|^mã|^'os \altchords{| | |Gm6 | \e}
    |^Para to|^dos escu|^tar \altchords{|A7 | |Dm}
  \endchorus
  \beginchorus
    |^Depois que |todos escu|^ta|^rem
    |^É que vão |reconhe|^ce|^{'r}
    |^Tudo vi|ve neste |^mun|^do
    |^Muito lon|^ge do Po|^der
  \endchorus
  \beginchorus
    |^Para estar |junto ao Po|^de|^{'r} \altchords{\id[3]{simples (Dm)}|Dm | | | \e}
    |^Da Virgem |da Concei|^çã|^o \altchords{| | |A7 | \e}
    |^É ter fé |e ter a|^mo|^{'r} \altchords{| | | | \e}
    |^Dar valor |^aos seus ir|^mãos \altchords{| | |Dm}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 3/4
      \repeat volta 2 {
        | d8(_\pomark d8) f4 e | d8( d8) f4 d | a'2. | f2( f8 f8)
        | d4 f e | d8( d8) bes'4 a | g2.( | e2.)
        | a,4 cis e | g f e | g2. | e2.
        | a4 g f | e d cis | d2.
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        \set stanza = "1."
        | Eu __ _ an -- dei | na __ _ Ca -- sa | San -- | ta; __ _ _
        | Trou -- xe mui -- | tas __ _ coi -- sas | bo -- | as;
        | Tu -- do vi -- | ve nes -- te | mun -- | do;
        | Pa -- re -- ce~u -- | ma coi- -- sa-à | toa.
      }
    }
    theLyricsTwo = \lyricmode {
      \repeat volta 2 {
      \set stanza = "2."
        | Pe -- _ di li -- | cen -- ça ao Di -- | vi -- | no;
        Pa -- ra | es -- tas pa -- | la -- vras eu nar -- | rar; __ | _
        | Pe -- ran -- te | os meus ir -- | mã -- | ãos;
        | Pa -- ra to -- | dos es -- cu -- | tar.
      }
    }
    theLyricsThree = \lyricmode {
      \repeat volta 3 {
      \set stanza = "2."
        | De -- _ pois que | to -- dos es -- cu -- | ta -- | rem; __ _ _
        | É que vão | re -- _ co -- nhe -- | cer; __ | _
        | Tu -- do vi -- | ve nes -- te | mun -- | do;
        | Mui -- to lon -- | ge do Po -- | der.
      }
    }
    theLyricsFour = \lyricmode {
      \repeat volta 2 {
      \set stanza = "4."
        | Pa -- ra es -- tar | jun -- to ao Po -- | der; __ | _ _ _
        | Da Vir -- gem | da __ _ Con -- cei -- | ção; __ | _
        | É ter fé | e ter a -- | mor; __ | _
        | Dar va -- lor | aos seus ir -- | mãos.
      }
    }
    theChords =  \chordmode {
      \repeat volta 2 {
        | d2.:m | d:m | \parenthesize a | f
        | d:m | d:m | g:m | a/e
        | a | a | g:m | a/e
        | a | a:7 | d:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I went to the Holy House, I brought a lot of good things
    All live in this world of seemingly worthless things
    \nextverse
    I asked permission from the Divine to narrate these words
    In front of my brothers and sisters, for all to listen
    \nextverse
    After they all have listened then they will recognize
    That all live in this world far away from the power
    \nextverse
    To be next to the power of the Virgin of Conception
    One must have faith and have love and recognize his brothers' worth
  \end{translation}
\endsong


\beginsong{Eu Tomo Esta Bebida}[by={Mestre Irineu Serra},key={Gm},sks={Gm, F\#m}]
  \audio{https://www.nossairmandade.com/hymn/92/EuTomoEstaBebida}
  \transpose{3}\preferflats
  \mnbeginchorus\memorize
    \[^\mn{B}]Eu |\[\mnc{E}Em]tomo esta \[^\mn{G}]be|\[^\mn{B}]bida \altchords{\id[1]{(Em)}|Em | \e}
    Que tem \[^\mn{G}]po|\[\mnc{E}E7]der ina\[^\mn{B}]cre\[^\mn{D}]di|\[\mnc{A}Am]tável \altchords{|E7 |Am}
    \lrep \[^\mn{/}]Ela |\[\mnc{A}Am]mostra a \[^\mn{C}]to\[^\mn{E}]dos |\[\mnc{G}Em]nós \altchords{| |Em}
    A\[^\mn{B}]qui \[^\mn{E}]den|\[\mnc{F#}B7]tro \[^\mn{A}]des\[^\mn{C}]ta \[^\mn{B}]ver|\[\mnc{E}\up{1}E7\up{2}(Em)]dade \rrep \altchords{|B7 |Em}
  \mnendchorus
  \notesoff
  \beginchorus
    Su|^bi, subi, su|bi
    Su|^bi foi com ale|^gria
    \lrep Quando eu |^chequei nas al|^turas
    Encontrei |^com a Virgem Ma|^ria \rrep
  \endchorus
  \beginchorus
    Su|^bi, subi, su|bi
    Su|^bi foi com a|^mor
    \lrep Encon|^trei com o Pai E|^terno
    E Jesus |^Cristo Reden|^tor \rrep
  \endchorus
  \beginchorus
    Su|^bi, subi, su|bi
    Con|^forme os meus en|^sinos
    \lrep |^Viva o Pai E|^terno
    E viva |^todo Ser Di|^vino \rrep
    % or "...todos Seres Divinos"?
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose e g \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key e \minor \time 4/4 \partial 4
      \repeat volta 2 {
        b4\posectionmark "A" | e4 e8( e8) e4 g4 | b4( b8 b8 b4) g4
        | e4 e8 e8 b4 d4 | a2 a4 \parenthesize a8\sectionmark "B:I" \parenthesize a8
        % repeated section:
        | a4 a4 c4 e4 | g,4( g8) g8 b4 e4
        | fis,4 a4 c4 b4 | e,2( e4) \parenthesize b'8\sectionmark "B:II" \parenthesize b8
        | a4 a4 c4 e4 | g,4( g8) g8 b4 e4
        | fis,4 a4 c4 b4 | e,2( e4)
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        \set stanza = "1."
        Eu | to -- mo es -- ta be -- | bi -- da;
        Que tem po -- | der in -- a -- cre -- di -- | tá -- vel.
        \set stanza = "1.B-I"
        E -- la | mos -- tra~a to -- dos | nós; __ _
        A -- qui den -- | tro des -- ta ver -- | da -- de.
        \set stanza = "1.B-II"
        E -- la | mos -- tra~a to -- dos | nós; __ _
        A -- qui den -- | tro des -- ta ver -- | da -- de.
      }
    }
    theLyricsTwo = \lyricmode {
      \repeat volta 2 {
        \set stanza = "2."
        Su -- | bi, su -- _ bi, su -- | bi; __ _ _ _
        Su -- | bi foi com a -- le -- | gri -- a.
        \set stanza = "2.B-I"
        Quan -- do~eu | che -- quei nas al -- | tu -- ras;
        En -- con -- trei | com~a Vir -- gem Ma -- | ri -- a.
        \set stanza = "2.B-II"
        Quan -- do~eu | che -- quei nas al -- | tu -- ras;
        En -- con -- trei | com~a Vir -- gem Ma -- | ri -- a.
      }
    }
    theLyricsThree = \lyricmode {
      \repeat volta 2 {
        \set stanza = "3."
        Su -- | bi, su -- _ bi, su -- | bi; __ _ _ _
        Su -- | bi foi __ _ com a -- | mor. __ _
        \set stanza = "3.B-I"
        En -- con -- | trei com~o Pai E -- | ter -- no;
        E Je -- sus | Cris -- to Re -- den -- | tor. __ _
        \set stanza = "3.B-II"
        En -- con -- | trei com~o Pai E -- | ter -- no;
        E Je -- sus | Cris -- to Re -- den -- | tor. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \repeat volta 2 {
        \set stanza = "4."
        Su -- | bi, su -- _ bi, su -- | bi; __ _ _ _
        Con -- | for -- me os meus en -- | si -- nos.
        \set stanza = "4.B-I"
        \skip 1 \skip 1 | Vi -- va~o Pai E -- | ter -- no;
        E vi -- va | to -- dos Seres Di -- | vi -- nos.
        \set stanza = "4.B-II"
        \skip 1 \skip 1 | Vi -- va~o Pai E -- | ter -- no;
        E vi -- va | to -- do Ser Di -- | vi -- no.
        % or "...todos Seres Divinos"?
      }
    }
    theChords = \transpose e g \chordmode {
      \repeat volta 2 {
        s4 | e1:m | e:m
        | e:7 | a:m
        | \once \set chordChanges = ##f a:m | e:m
        | b:7 | e:7
        | \once \set chordChanges = ##f a:m | e:m
        | b:7 | e2.:m
      }
    }
    % Custom score block to force guitar tabs to fret 3 and above
    \score {
      <<
        \new ChordNames { \theChords }
        \new Staff { \clef "treble" \new Voice = "theVoice" { \theMelody } }
        \new TabStaff { \clef "moderntab" \set minimumFret = #3 \set restrainOpenStrings = ##t \transpose c'' c \theMelody }
        \new Lyrics \lyricsto "theVoice" { \theLyricsOne }
        \new Lyrics \lyricsto "theVoice" { \theLyricsTwo }
        \new Lyrics \lyricsto "theVoice" { \theLyricsThree }
        \new Lyrics \lyricsto "theVoice" { \theLyricsFour }
      >>
      \layout { }
    }
    \include "tex/lp-internal-midi-score.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I take this drink which has an incredible Power
    It shows all of us here in this Truth
    \nextverse
    I went up, I went up, I went up, I went up with hapiness
    When I arrived in the Heights, I met with the Virgin Mary
    \nextverse
    I went up, I went up, I went up, I went up with love
    I met the Eternal Father and Jesus Christ the Redeemer
    \nextverse
    I went up, I went up, I went up, following my teachings
    Viva my Eternal Father and viva to all the Divine Beings
  \end{translation}
\endsong


\beginsong{Aqui Estou Dizendo}[by={Mestre Irineu Serra},key={Am},sks={Am, Bm}]
  \audio{https://www.nossairmandade.com/hymn/93/AquiEstouDizendo}
  \mnbeginchorus\memorize
    \[^\mn{E}]A|\[\mnc{A}Am]qui \[^\mn{G}]es\[^\mn{F}]tou \[^\mn{E}]di|\[\mnc{G}Dm]zen\[^\mn{F}]do\[(Dm/F)] \altchords{\id[1]{(Bm)}|Bm |Em (Em/G)}
    \[^\mn{D}]A|\[\mnc{G}G]qui \[^\mn{F}]es\[^\mn{E}]tou \[^\mn{D}]can|\[\mnc{F}F]tan\[^\mn{E}]do\[E7] \altchords{|A |G F\#7}
    \lrep \[^\mn{C}]Eu |\[\mnc{A}Am]digo \[\mnc{C}(C)]pa\[^\mn{E}]ra |\[\mnc{D}Dm]todos \altchords{|Bm (D) |Em}
    \[^\mn{E}]E \[^\mn{F}]os |\[\mnc{E}E7]hinos \[^\mn{D}]estão \[\bmc\mn{C}]en\[^\mn{B}]si|\[\mnc{A}Am]nando \rrep \altchords{|F\#7 |Bm}
  \mnendchorus
  \notesoff
  \beginchorus
    Aque|^les que compreen|^derem^
    Os que qui|^ser seguir co|^migo^
    \lrep \noteson\[\mnlow{C}]Ten\[\mnlow{B}]do \notesoff|^fé e ^tendo a|^mor
    Não de|^vem enca^rar pe|^rigo \rrep
  \endchorus
  \beginchorus
    Si|^go os meus passos em |^frente^
    Com ale|^gria e com a|^mor^
    \lrep \noteson\[\mnlow{C}]Por\[\mnlow{B}]que \notesoff|^Deus é ^Sobe|^rano
    E nesta |^firme^za es|^tou \rrep
  \endchorus
  \beginchorus
    A Virgem |^Mãe é Sobe|^rana^
    Foi |^Ela quem me ensi|^nou^
    \lrep \noteson\[\mnlow{C}]E\[\mnlow{B}]la \notesoff|^me man^dou pra |^cá
    Para |^ser um ^Profes|^sor \rrep
  \endchorus
  \beginchorus
    Vamos se|^quir, vamos se\noteson|^guir
    \[\mnlow{F}]Va^\[\mnlow{D}]mos \[\mnlow{B}]se\notesoff|^guir, vamos em|^bora^
    \lrep \noteson\[\mnlow{C}]Que \[\mnlow{B}]nós \notesoff|^somos ^Filhos E|^ternos
    Filhos |^de Nos^sa Se|^nhora \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \parenthesize e8\sectionmark "1.-4.A" e8( e8) | a2~ a8 g f e | g4 f4. \parenthesize d8 d8( d8)
      | g4( g4.) f8 e d | f4( e4.)
      \repeat volta 2 {
         r8\sectionmark "1.-4.B" c8( << c8) \parenthesize b8 >> | a4. a8 c4 e4 | d4.( d8) e4 f4
         | e8( e8) d8( d8) c4 b4 | a2( a8)
      } \break
      e'8\posectionmark "5.A" e8( e8) | a2~ a8 g f e | g4 f4 d4 b4
      | g'2~ g8 f8 e d | f4 e4.
      \repeat volta 2 {
         r8\sectionmark "5.B" c8 b8 | a4. a8 c8 c8 e4 | d4. d8 e4 f4
         | e4 d c4 b4 | a2 a8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 A -- _ | qui __ _ es -- tou di -- | zen -- do; _
      A -- _ |qui __ _ es -- tou can -- | tan -- do.
        Eu __ _ | di -- go pa -- ra | to -- dos;
        E os | hi -- nos es -- tão en -- si -- | nan -- do.
      \set stanza = "5."
      Va -- mos se -- | quir __ _ va -- mos se -- | guir;
      Va -- mos se -- | guir __ _ va -- mos em -- | bo -- ra.
        Que nós | so -- mos Fi -- lhos E -- | ter -- nos;
        Fi -- lhos | de Nos -- sa Se -- | nho -- ra.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \skip 1 A -- que -- | les __ _ que com -- preen -- | de -- rem;
      Os que qui -- | ser __ _ se -- guir co -- | mi -- go.
        Ten -- do | fé e ten -- do~a -- | mor; __ _
        Não de -- | vem en -- ca -- _ rar  pe -- | ri -- go.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1 Si -- _ | go~os __ _ meus pas -- sos~em | fren -- te;
      Com a -- le -- | gri -- a e com a -- | mor. __ _
        Por -- que | Deus é So -- be -- | ra -- no;~E
        nes -- ta | fir -- _ me -- _ za es -- | tou. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      A Vir -- gem | Mãe __ _ é So -- be -- | ra -- na;
      \skip 1 Foi __ _ | E -- la quem me~en -- si -- | nou. __ _
        E -- la | me man -- dou pra | cá; __ _
        Pa -- ra | ser __ _ um __ _ Pro -- fes -- | sor. __ _
    }
    theChords =  \chordmode {
      s4. | a1:m | d2:m \parenthesize d:m/f
      | g1 | f2 e8:7
      \repeat volta 2 {
        s4. | a2:m \parenthesize c | d1:m
        | e:7 | a2:m~ a8:m
      }
      % for verse 5 (same chords):
      s4. | \once \set chordChanges = ##f a1:m | d2:m f
      | g1 | f2 e8:7
      \repeat volta 2 {
        s4. | a2:m \parenthesize c | d1:m
        | e:7 | a2:m~ a8:m
      }
    }
     \layout { #(layout-set-staff-size 13) } % to fit on one spread
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Here I am saying, here I am singing
    I tell everybody the hymns are teaching us
    \nextverse
    Those who understand, who want to follow with me
    Having Faith, having Love, must not go through danger
    \nextverse
    I keep going forward with joy and with love
    Because God is Supreme and I am in this firmness
    \nextverse
    The Holy Mary is Supreme, it was She who taught me
    She sent me here to be a teacher
    \nextverse
    Let's follow, let's follow, let's follow, let's go
    We are all eternal children, sons and daughters of Our Lady
  \end{translation}
\endsong


\beginsong{Flor das Águas}[by={Mestre Irineu Serra},tags={2x},key={Am},sks={Cm, Am, Dm}]
  \audio{https://www.nossairmandade.com/hymn/94/FlorDas\%C3\%81guas}
  \beginchorus
    |\[\mnc{E}Am]Flor \[\mn{C}]das |\[\mnc{D}Dm]águas \altchords{\id[1]{(Dm)}|Dm |Gm}
    \[\mn{C}]Da \[\mn{D}]on\[\mn{F}]de |\[\mnc{E}E]vens, para \[\mnc{D}(E7/D)]on\[\mn{E}]de |\[\mnc{C}Am]vais \altchords{|A A7/G |Dm}
    Vou \[\mn{B}]fa|\[\mn{A}]zer a mi\[\mnc{C}C]nha \[\mn{D}]lim|\[\mnc{E}E]peza \altchords{| - F |A}
    No \[\mnc{D}(E7/D)]cora|\[\mnc{C}C]ção \[\mn{B}]es\[\mnc{G#}E]tá \[\mn{B}]meu |\[\mnc{A}Am]Pai \altchords{ A7/G |F A |Dm}
  \endchorus
  \mnbeginchorus\memorize
    \ind \[^\mn{A}]A \[^\mn{C}]mo|\[\mnc{E}Am]rada \[\mnc{G}G]do meu |\[\mncii{C}{B}Am]Pai
    \ind \[^\mn{A}]É \[^\mn{C}]no |\[\mnc{E}C]cora\[^\mn{D}]ção \[^\mn{E}]do |\[\mnc{D}Dm]mundo
    \ind Aonde e|xiste \[\mnc{C}C]to\[^\mn{B}]do a|\[\mnc{E}E]mor
    \ind E \[\mnc{D}(E7/D)]{tem um} |\[\mnc{C}C]se\[^\mn{B}]gre\[\mnc{G#}E7]do \[^\mn{B}]pro|\[\mnc{A}Am]fundo
  \mnendchorus
  \notesoff
  \beginchorus
    \ind Este |^segre^do pro|^fundo
    \ind Está em |^toda humani|^dade
    \ind Se to|dos se ^conhe|^cerem
    \ind ^Aqui |^dentro ^da ver|^dade
  \endchorus
  \begin{translation}
    Flower of the waters, from where do you come, where do you go?
    I will do my cleansing, my Father is in my heart
    \nextverse
    The House of my Father is in the heart of the world
    Where all Love exists, and there is a profound secret
    \nextverse
    This profound secret is in all of humanity
    If everyone knew themselves here within the Truth
  \end{translation}
  \begin{explanation}\tiny % to fit
    It is said that after \emph{Flor das Águas} was presented at a
    concentration work, Mestre asked everyone attending: ``Where is the heart of
    the world?'' Nobody answered. He asked again and still got no response. Then
    he said: ``The heart of the world is the sea!''
  \end{explanation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \key a \minor \time 4/4 \partial 4
      \mark \markup \with-color #darkgreen \italic "Final: toque tudo sem repetições"
      \repeat volta 2 {
        r4\posectionmark "1." | e2. c4 | d4 d8 c8 d4 f4 | e4 e8 e8 d4 e4 | c2. c8 b8
        | a4 a8 a8 c4 d4 | e4 e8 e8 d4 d4 | c4 b4 gis4 b4 | a2.
      } \break
      \repeat volta 2 {
        a8\sectionmark "2." c8 | e4 e4 d4 e4 | c4.( b8) a4 c4 | e4 e4 d4 e4 | d2 d8. d16 d8 d8
        | d4 d4 c4 b4 | e4. e8 d4 d4 | c4 b4 gis4 b4 | a2 a4
      } \break
      \repeat volta 2 {
        a8\sectionmark "3." c8 | e4 e4 d4 e4 | c4 c8 b8 a4 c4 | e4 e8 e8 d4 e4 | d2 d4 d8 d8
        | d4 d4 c4 b4 | e4. e8 d4 d4 | c4 b4 gis4 b4 | a2 a4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      | Flor das | á -- guas;
      da on -- de | vens, pa -- ra on -- de | vais;
      Vou fa -- | zer a mi -- nha lim -- | pe -- za;
      No co -- ra -- | ção es -- tá meu | Pai.
      \set stanza = "2."
      A mo -- | ra -- da do meu | Pai; __
      É no | co -- ra -- ção do | mun -- do;
      A -- on -- de~e -- | xis -- te to -- do~a -- | mor;
      E tem um | se -- gre -- do pro -- | fun -- do.
      \set stanza = "3."
      Es -- te | se -- gre -- do pro -- | fun -- do;
      Es -- tá em | to -- da hu -- ma -- ni -- | da -- de;
      Se to -- | dos se co -- nhe -- | ce -- rem;
      A -- qui | den -- tro da ver -- | da -- de.
    }
    theChords =  \chordmode {
      \repeat volta 2 {
        s4 | a1:m | d:m | e2 \parenthesize e:7/d | a1:m
        | a2:m c | e2 \parenthesize e:7/d | c2 e | a2.:m
      }
      \repeat volta 2 {
        s4 | a2:m g | a1:m | c | d:m
        | d2:m c | e2 \parenthesize e:7/d | c2 e:7 | a2.:m
      }
      \repeat volta 2 {
        s4 | a2:m g | a1:m | c | d:m
        | d2:m c | e2 \parenthesize e:7/d | c2 e:7 | a2.:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % to fit on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Marchinha \emph{(instrumental)}}[by={Mestre Irineu Serra},key={D}]
  \audio{https://www.nossairmandade.com/hymn/3291}
  \meter{2}{4}
  \beginchorus
    |\[D] | |\[A] |\[D] | |\[D7] | |\[G] \altchords{\id[1]{(C)}|C | |G |C | |C7 | |F}
    | |\[Em7] | |\[A] |\[D] |\[A] |\[D] |\[A7] |\[D] \altchords{| |Dm7 | |G |C |G |C |G7 |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative d' {
      \key d \major \time 2/4
      \repeat volta 2 {
        | d8 d fis a | d d fis cis | e2 | d4. d,8
        | d8 d fis a | c c a fis | d d e fis | g2~
        | g8 d e fis | g4 g4 | g8 b b b | a4 a4
        | a8 fis fis g | a4 a4 | a8 fis' fis cis | e4 e8 e
        | d2
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        | d2 | d | a | d | d | d:7 | d:7 | g | g
        | e:m7 | e:m7 | a | d | a | d | a:7 | d
      }
    }
    % Use custom score to get high and low staff
    \layout {
      \context {
        \Score {
          \override StaffGrouper.staff-staff-spacing.padding = #2
        }
      }
    }
    \score {
      <<
        \new ChordNames { \theChords }
        \new StaffGroup \with {
          \override StaffGrouper.staffgroup-staff-spacing.padding = #5
        } <<
          \new Staff { \clef "treble" \new Voice = "theVoice" { \theMelody } }
          \new TabStaff { \clef "moderntab" \transpose c' c \theMelody }
          \new TabStaff { \tabFullNotation \stemDown \clef "moderntab" \set minimumFret = #10  \theMelody }
        >>
      >>
      \layout { }
    }
    \include "tex/lp-internal-midi-score.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Eu Pedi}[by={Mestre Irineu Serra},key={G},sks={G, A}]
  \audio{https://www.nossairmandade.com/hymn/95/EuPedi}
  \mnbeginchorus\memorize
    \[^\mn{D}]Eu pe|\[\mnc{G}G]di, \[^\mn{D}]eu pe\[^\mn{G}]di, \[^\mn{D}]eu pe|\[^\mn{G}]di \altchords{\id[1]{(A)}|A | \e}
    \[^\mn{B}]Eu \[^\mn{D}]pe|\[^\mn{G}]di Ma\[^\mn{A}]mãe \[^\mn{G}]me |\[\mnc{E}C]deu \altchords{| |D}
    \[^\mn{A}]Para |\[Am]mim \[^\mn{C}]a\[\mnc{B}(D)]pre\[^\mn{A}]sen|\[\mncii{B}{G}G]tar \[(Em)]\altchords{|Bm (E) |A (F\#m)}
    \[^\mn{B}]Ao \[^\mn{E}]Di|\[\mnc{D}D7]vi\[^\mn{C}]no \[\mnc{A}(Am)]Se\[^\mn{B}]nhor |\[\mnc{G}G]Deus\altchords{|E7 (Bm) |A}
  \mnendchorus
  \notesoff
  \beginchorus
    Meu Di|^vino Senhor \noteson|\[\mnlow{G}]De\[\mnlow{D}]us \notesoff
    É Pai |de todo a|^mor
    Perdo|^{ai os} ^Vossos |^filho^s
    Neste |^mundo ^peca|^dor
  \endchorus
  \beginchorus
    Jesus |^Cristo Reden\noteson|\[\mnlow{G}\mnlow{D}]tor \notesoff
    Senhor |do meu cora|^ção
    Defen|^dei os ^Vossos |^filho^s
    Neste |^mundo ^{de ilu}|^são \tonextsongmark
  \endchorus
  \begin{translation}
    I asked, I asked, I asked, I asked, Mother allow me
    To present myself to the Divine Lord God
    \nextverse
    My Divine Lord God is the Father of all Love
    Forgive Your children in this sinful world
    \nextverse
    Jesus Christ the Redeemer, Lord of my heart
    Defend Your children in this world of illusion
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \key g \major \time 4/4 \partial 4
      \repeat volta 2 {
        d8\sectionmark "1." d8 | g4 d8 d8 g4 d8 d8 | g2. b,8 d8 | g4 g4 a4 g4 | e2. a8 a8
        | a4 c4 b4 a4 | b4( g2) b,8 e8 | d4 c4 a4 b4 | g2.
      } \break
      \repeat volta 2 {
        d'8\sectionmark "2." d8 | g4 d4 g4 d4 | g4( d2) b8 d8 | g4 g4 a4 g4 | e2. a8 a8
        | a4 c4 b4 a4 | b4 g2 b,8 e8 | d4 c4 a4 b4 | g2.
      } \break
      \repeat volta 2 {
        d'8\posectionmark "3." d8 | g4 d4 g4 d4 | g4( d2) b8 d8 | g4 g4 a4 g4 | e2. a8 a8
        | a4 c4 b4 a4 | b4 g2 b,8 e8 | d4 c4 a4 b4 | g2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Eu pe -- | di, eu pe -- di, eu pe -- | di;
      Eu pe -- | di Ma -- mãe me | deu;
      Pa -- ra | mim a -- pre -- sen -- | tar; __
      Ao Di -- | vi -- no Se -- nhor | Deus.
      \set stanza = "2."
      Meu Di -- | vi -- no Se -- nhor | Deus;
      É Pai | de to -- do a -- | mor;
      Per -- do -- | ai os Vos -- sos | fi -- lhos;
      Nes -- te | mun -- do pe -- ca -- | dor.
      \set stanza = "3."
      Je -- sus | Cris -- to Re -- den -- | tor; __
      Se -- nhor | do meu co -- ra -- | ção;
      De -- fen -- | dei os Vos -- sos | fi -- lhos;
      Nes -- te | mun -- do de ilu -- | são.
    }
    theChords = \chordmode {
      \repeat volta 2 { % verse 1
        s4 | g1 | g | g | c
        | a2:m \parenthesize d | g \parenthesize e:m | d2:7 \parenthesize a:m | g2.
      }
      \repeat volta 2 { % verse 2
        \once \set chordChanges = ##f
        s4 | g1 | g c | g | c
        | a2:m \parenthesize d | g \parenthesize e:m | d2:7 \parenthesize a:m | g2.      }
      \repeat volta 2 { % verse 3
        \once \set chordChanges = ##f
        s4 | g1 | g c | g | c
        | a2:m \parenthesize d | g \parenthesize e:m | d2:7 \parenthesize a:m | g2.      }
    }
    \layout { #(layout-set-staff-size 15) } % to fit on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Eu Cheguei Nesta Casa}[by={Mestre Irineu Serra},key={G},sks={G, A}]
  \audio{https://www.nossairmandade.com/hymn/96/EuChegueiNestaCasa}
  \newchords{chords_eucheguei_a}\newchords{chords_eucheguei_b}
  \mnbeginchorus\memorize[chords_eucheguei_a]
    \[^\mn{B}]Eu |\[\mnc{D}G]cheguei \[\mnc{B}(Em/B)]nes\[^\mn{E}]ta |\[\mncii{D}{G}G]casa \altchords{\id[1]{(A)}|A (F\#m/C\#) |A}
    \[\bm]Eu \[^\mn{F#}]en|\[\mnc{A}D7]trei \[^\mn{F#}]por \[\bmc\mn{D}]es\[^\mn{C}]ta |\[\mnc{B}G]por\[^\mn{G}]ta \[\bm] \altchords{|E7 |A}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eucheguei_b]
    \[^\mn{G}]Eu ve\[^\mn{F#}]nho |\[\mnc{A}D7]dar os a\[^\mn{F#}]gra\[\bmc\mn{D}]de\[^\mn{C}]ci|\[\mnc{B}G]mentos \altchords{|E7 |A}
    \[^\mn{G}]A \[\mnc{B}(Em/B)]quem \[^\mn{E}]ro|\[\mnc{D}D7]gou \[^\mn{C}]por \[\bmc\mn{A}]mi\[^\mn{B}]nha |\[\mnc{G}G]volta \[\bm] \altchords{|(F\#m/C\#) |A}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eucheguei_a]
    Eu estou |^dentro ^desta |^casa
    A^qui no |^meio des^te sa|^lão ^
  \endchorus\glueverses\beginchorus\replay[chords_eucheguei_b]
    Estou a|^legre e ^satis|^feito
    ^Junto a|^qui com os ^meus ir|^mãos ^
  \endchorus
  \beginchorus\replay[chords_eucheguei_a]
    Ia fa|^zendo u^{ma vi}|^agem
    ^Ia pen|^sando em ^não vol|^tar ^
  \endchorus\glueverses\beginchorus\replay[chords_eucheguei_b]
    Os pe|^didos ^foram |^tantos
    ^{Me man}|^daram ^eu vol|^tar ^
  \endchorus
  \brk
  \beginchorus\replay[chords_eucheguei_a]
    Me man|^daram ^{eu vol}|^tar
    Eu ^estou |^firme, vou ^traba|^lhar ^
  \endchorus\glueverses\beginchorus\replay[chords_eucheguei_b]
    Ensi|^nar os ^meus ir|^mãos
    A^queles |^{que me} ^escu|^tar ^
  \endchorus
  \brk
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize b8\posectionmark "A" b8( << b8) \parenthesize c8 >> |
        | d4. d8 b4 e4 | d4. g8 g4 fis4
        | a4( a8) fis8 d4 c4 | b4( g4.)
      } \break
      \repeat volta 2 {
        \parenthesize g'8\sectionmark "B" g8 fis8 | a8( a8 a8) fis8 d4 c4 | b4( b8) g8 b4 e4
        | d4( d8) c8 a4 b4 | g2( g8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 Eu __ _ | che -- guei nes -- ta | ca -- sa;
      Eu en -- | trei __ _ por es -- ta | por -- ta.
      \set stanza = "1.B"
      Eu ve -- nho | dar os a -- gra -- de -- ci -- | men -- tos;
      A quem ro -- | gou __ _ por mi -- nha | vol -- ta.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Eu es -- tou | den -- tro des -- ta | ca -- sa;~
      Aqui no | mei -- o des -- te sa -- | lão. __ _
      \set stanza = "2.B"
      Es -- tou a -- | le -- _ _ gre~e sa -- tis -- | fei -- _ to;
      Jun -- to~a -- | qui com os meus ir -- | mãos. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1 Ia fa -- | zen -- do~u -- ma vi -- | a -- gem;
      Ia pen -- | san -- do em não vol -- | tar. __ _
      \set stanza = "3.B"
      \skip 1 Os pe -- | di -- _ _ dos fo -- ram | tan -- _ tos;
      Me man -- | da -- _ ram eu vol -- | tar. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 Me man -- | da -- ram eu vol -- | tar;
      Eu es -- tou | fir -- me, vou tra -- ba -- | lhar. __ _
      \set stanza = "4.B"
      \skip 1 En -- si -- | nar __ _ _ os meus ir -- | mã -- os;
      A -- que -- les | que __ _ me es -- cu -- | tar. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | g2 \parenthesize e2:m/b | g1 | d:7 | g2~ g8
      }
      \repeat volta 2 {
        s4. | d1:7 | g2 \parenthesize e2:m/b |  d1:7 | g2~ g8
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I arrived in this House, I entered through this door
    I came to give thanks to those who prayed for my return
    \nextverse
    I am in this House, here in this temple
    I am happy and satisfied here with my brothers and sisters
    \nextverse
    I was about to travel, I was thinking of not coming back
    There were so many, they ordered me to return
    \nextverse
    They ordered me to return, I am firm, I will work
    Teaching my brothers and sisters, those who will listen to me
  \end{translation}
\endsong


\beginsong{Pisei na Terra Fria}[by={Mestre Irineu Serra},key={Am},sks={Am, Bm, Cm}]
  \audio{https://www.nossairmandade.com/hymn/310/PiseiNaTerraFria}
  \mnbeginchorus\memorize
    \[^\mn{E}]Pi|\[\mnc{A}Am]sei \[\bm] \[^\mn{A}]na ter\[^\mn{B}]ra |\[\mnc{C}(C)]fri\[^\mn{A}]a \altchords{\id[1]{(Bm)}|Bm |(D)}
    \[\bmc\mn{C}]Ne\[^\mn{E}]la |\[\mnc{G}G]eu \[^\mn{D}]sen\[\bm]ti ca|\[Dm]lor \[\bm] \altchords{|A |Em}
    Ela é |quem \[^\mn{A}]me \[\bm]dá o |\[\mnc{E}Am]pão \altchords{| |Bm}
    \[^\mn{C}]A \[\bmc\mn{A}]mi\[^\mn{C}]nha |\[\mnc{E}E7]Mãe\[\bm] \[^\mn{A}]que nos cri|\[Am]ou \[\bm] \altchords{|F\#7 |Bm}
  \mnendchorus
  \notesoff
  \beginchorus
    A minha |^Mãe ^ que nos cri|^ou
    ^E me |^dá to^dos en|^si^nos
    A ma|téria eu en^trego a |^Ela
    E ^o meu e|^spí^-rito ao Di|^vi^no
  \endchorus
  \beginchorus
    Do |^san^gue das minhas |^veias
    ^Eu fiz |^minha as^sina|^tu^ra
    O meu e|spírito, eu en^trego a |^Deus
    E ^o meu |^cor^po, à sepul|^tu^ra
  \endchorus
  \beginchorus
    Meu |^cor^po na sepul|^tura
    ^Despre|^zado ^no re|^len^to
    Alguém |fala ^em meu |^nome
    Al^guma |^vez^ em pensa|^men^to
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize e8\pomark e8( e8) | a2( a8) a,8 a8 b8 | c4( a) c e | g d d d | d2( d8)( d8) d8 d8
        | d8( d8) a'8( a8) a4 a | e4. c8 a4 c8( c8) | e2( e8) a a a | a2( a8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 Pi -- _ | sei __ _ na ter -- ra | fri -- a;
      Ne -- la | eu sen -- ti ca -- | lor; __ _ _
      E -- la~é | quem __ _ me __ _ dá o | pão;
      A mi -- nha __ _ | Mãe __ _ que nos cri -- | ou. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      A mi -- nha | Mãe __ _ que nos cri -- | ou; __ _
      E me | dá to -- dos en -- | si -- nos; __ _
      A ma -- | té -- _ ria~eu en -- tre -- go~a | E -- la;~E
      o meu es -- | pí -- _ ri -- to~ao Di -- | vi -- no.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1 Do __ _ | san -- gue das mi -- nhas | vei -- as;
      Eu fiz | mi -- nha~as -- si -- na -- | tu -- ra;
      O meu e -- | spí -- ri -- to~eu en -- tre -- go~a | Deus;
      E o meu __ _ | cor -- po à se -- pul -- | tu -- ra.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 Meu __ _ | cor -- po na se -- pul -- | tu -- ra;
      Des -- pre -- | za -- do no re -- | len -- to; __ _
      Al -- guém | fa -- _ la __ _ em meu | no -- me;~Al --
      gu -- ma __ _ | vez __ _ em pen -- sa -- | men -- to.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1:m | \parenthesize c | g | d:m
        | d:m | a:m | e:7 | a2:m~ a8:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I stepped on the cold earth; on her, I felt warmth
    She is the one who gives me bread, my Mother who created us
    \nextverse
    My Mother who created us and gives me all the teachings
    My body, I deliver to her; and my spirit to the Divine
    \nextverse
    With the blood of my veins, I signed my name
    I deliver my spirit to God; and my body to the grave
    \nextverse
    My body to the grave, neglected in the night air
    Someone speaks of me, sometimes, in thought
  \end{translation}
\endsong
