% Santo Daime: Hinos Diversos de Cura
% ===================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Com Fé em Deus}[by={Madr. Júlia}, key={C}, gk={D, C--E}]
  \audio{https://www.nossairmandade.com/hymn/690/ComF\%C3\%A9EmDeus}
  \newchords{chords_comfeemdeus_a}\newchords{chords_comfeemdeus_b}
  \mnbeginchorus\memorize[chords_comfeemdeus_a]
    \[^\mn{G}]Com fé \[^\mn{C}]em |\[\mncii{E}{C}C]Deus, eu \[\mnc{E}G7]vou me \[^\mn{D}]levan|\[\mnc{C}C]tar\[\bm]{} \altchords{\id[1]{(D)}|D A7 |D}
    Com fé \[^\mn{E}]em |\[^\mn{G}\mn{E}]Deus, E\[\mnc{G}G7]le vai me a\[^\mn{F}]ju|\[\mnc{E}C]dar\[\bm]{} \altchords{| - A7 |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_comfeemdeus_b]
    \[^\mn{C}]Com fé \[^\mn{E}]em |\[\mnc{G}C]Deus \[^\mn{C}]e na Vir\[\bmc\mn{G}]gem da Concei|\[^\mn{C}]ção\[\bm]{} \altchords{|D | \e}
    \[^\mn{G}]Esta \[^\mn{C}]ba|\[\mnc{E}Am]ta\[^\mn{C}]lha nós te\[\mnc{E}G7]mos que a\[^\mn{D}]traves|\[\mnc{C}C]sar\[\bm]{} \altchords{|Bm A7 |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_comfeemdeus_a]
    Vamos se|^guir, meus ir^mãos, vamos se|^guir^
    No ca|minho da Sem^pre Virgem Ma|^ri^a
  \endchorus\glueverses\beginchorus\replay[chords_comfeemdeus_b]
    Que |^Ela é a ^nossa prote|to^ra
    E nos |^guia no ca^minho da salva|^ção^
  \endchorus
  \beginchorus\replay[chords_comfeemdeus_a]
    Eu devo a|^mar minha ^Mãe lá nas al|^tu^ras
    Que me en|sina eu sa^ir das amar|^gu^ras
  \endchorus\glueverses\beginchorus\replay[chords_comfeemdeus_b]
    Estou a|^qui, vim cum^prir minha mis|são^
    Com fé em |^Deus e na Vir^gem da Concei|^ção^
  \endchorus
  \begin{translation}[EN]
    With faith in God, I'm going to stand up; with faith in God, He's going to help me
    With faith in God and in the Virgin of Conception, this battle we've to go through
    \nextverse
    Let's follow, my brothers, let's follow, in the path of the Ever Virgin Mary
    For She is our Protector, and who guides us in the path of salvation
    \nextverse
    I have to love my Mother up in the heights, who teaches me how to leave the sorrows
    I am here, I came to fulfill my mission, with faith in God and in the Virgin of Conception
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4.
        \repeat volta 2 {
          g8\sectionmark "1.A" g c | e4( c8) c e e d d | c2~ c8 c c e | g4( e8) e g g g f | e2~ e8
        } \break
        \repeat volta 2 {
          c8\sectionmark "1.B" c e | g8. c,16 c8 c g' g g g | c,2~ c8 g g c | e8. c16 c8 c e e d d | c2~ c8
        } \break
        \repeat volta 2 {
          g8\sectionmark "2.A" g c | e4 c8 c e e d d | c2. c8 e | g8. e16 e8 e g g g f | e2 e8
        } \break
        \repeat volta 2 {
          r8\sectionmark "2.B" e4 | g8. c,16 c8 c g' g g g | c,2 c4 g8 c | e8. c16 c8 c e e d d | c2~ c8
        } \break
        \repeat volta 2 {
          g8\posectionmark "3.A" g c | e4 c8 c e e d d | c2 c8 c c e | g8. e16 e8 e g g g f | e2 e8
        } \break
        \repeat volta 2 {
          c8\sectionmark "3.B" c e | g4 c,8 c g' g g g | c,2~ c8 g g c | e8. c16 c8 c e e d d | c2~ c8
        }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Com fé em | Deus __ eu vou me le -- van -- | tar; __
      Com fé em | Deus __ E -- le vai me~a -- ju -- | dar. __
      \set stanza = "1.B"
      Com fé em | Deus e na Vir -- gem da Con -- cei -- | ção; __
      Es -- ta ba -- | ta -- lha nós te -- mos que~a -- tra -- ves -- | sar. __
      \set stanza = "2."
      Va -- mos se -- | guir meus ir -- mãos va -- mos se -- | guir;
      No ca -- | mi -- nho da Sem -- pre Vir -- gem Ma -- | ri -- a.
      \set stanza = "2.B"
      Que | E -- la é a nos -- sa pro -- te -- | to -- ra;
      E nos | gui -- a no ca -- mi -- nho~da sal -- va -- | ção. __
      \set stanza = "3."
      Eu de -- vo~a -- | mar mi -- nha Mãe lá nas al -- | tu -- ras;
      Que me en -- | si -- na eu sa -- ir das a -- mar -- | gu -- ras.
      \set stanza = "3.B"
      Es -- tou a -- | qui vim cum -- prir mi -- nha mis -- | são; __
      Com fé em | Deus e na Vir -- gem da Con -- cei -- | ção. __
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 g:7 | c1 | c2 g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c1 | c1 | a2:m g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c2 g:7 | c1 | c2 g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c1 | c1 | a2:m g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c2 g:7 | c1 | c2 g:7 | c2~ c8
      }
      \repeat volta 2 {
        s4. | c1 | c1 | a2:m g:7 | c2~ c8
      }
    }
    \layout { #(layout-set-staff-size 12) } % to fit on one spread
    \include "tex/lp-include-tail-lyricsbetween.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{A Cura \\ Eu Venho Acrescentar}[by={Padr. Alfredo}, off={Liza}, key={A}, gk={A, A\flt{}--A}]
  % Also in songs_astral_novaera.tex
  \audio{https://www.nossairmandade.com/hymn/105/EuVenhoAcrescentar}
  \audio[key=A]{https://soundcloud.com/canaljagube/03-eu-venho-acrescentar?in=canaljagube/sets/hinario-nova-era_oficial}
  \mnbeginchorus\memorize
    \[^\mn{E}]Eu |\[\mnciii{C#}{B}{C#}A]venho \[\mnc{D}E7]a\[^\mn{G#}]cres\[^\mn{B}]cen|\[\mnc{A}A]tar\[\bm]{} \altchords{\id[1]{(B)}|B F\shrp{}7 |B}
    \[^\mn{C#}]A\[^\mn{E}]qui |\[\mnc{A}(F#m)]dentro \[\mnc{B}(Bm)]des\[^\mn{F#}]te po|\[D]der\[\bm]{} \altchords{|(G\shrp{}m) (C\shrp{}m) |E}
    A |\[\mnc{D}(Bm)]cu\[^\mn{F#}]ra \[\mnc{A}D]Deus é quem |\[\mnc{E}A]dá\[\bmc\mn{C#}]{} \altchords{|(C\shrp{}m) E |B}
    \[^\mn{E}]E |\[\mncii{C#}{B}(F#m)]é \[^\mn{C#}]se \[\mnc{D}E7]bem \[^\mn{G#}]me\[^\mn{B}]re|\[\mnc{A}A]cer\[\bm]{} \altchords{|(G\shrp{}m) F\shrp{}7 |B}
  \mnendchorus
  \notesoff
  \beginchorus
    E |^é se ^bem mere|^cer^
    Da ver|^dade ^{e do a}|^mor^
    |^Deus e ^a Virgem |^Mãe^
    E |^Je^sus Reden|^tor^
  \endchorus
  \beginchorus
    Patri|^ar^ca São Jo|^sé^ \altchords{\id[2]{(C)}|C G7 |C}
    E |^todos ^seres di|^vi^nos \altchords{|(Am) (Dm) |F}
    Nos |^dão a ^graça da |^vi^da \altchords{|(Dm) F |C}
    São |^João é o ^nosso ca|^mi^nho \altchords{|(Am) G7 |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-08
    % \header {
    %   title = "A Cura"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative e' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4
      \repeat volta 2 {
        e8(\pomark e8) | \once\slurSolid cis'4( b8)( cis8) d4 gis,8 b8 | a2. cis8 e8
        | a4. a8 b4 fis8 fis8 | fis2( fis4)( fis4)
        | d4. fis8 a4 a8 a8 | e2( cis4) e4
        | cis4( b8)( cis8) d4 gis,8 b8 | a2( a4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu __ _ | ve -- _ nho a -- cres -- cen -- | tar;
        A -- qui | den -- tro des -- te po -- | der; __ _
        A | cu -- ra Deus é quem | dá; __ _
        E | é __ _ se bem me -- re -- | cer. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        E  __ _ | é __ _ se bem me -- re -- | cer;
        Da ver -- | da -- de e do a -- | mor; __ _ _
        | Deus e a Vir -- gem | Mãe; __ _
        E | Je -- _ _ sus Re -- den -- | tor. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Pa -- tri -- | ar -- _ _ ca São Jo -- | sé;
        E __ _ | to -- dos se -- res di -- | vi -- nos;
        Nos | dão a gra -- ça da | vi -- da;
        São | Jo -- ão é~o nos -- so ca -- | mi -- nho.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a2 e2:7 | a1 | \parenthesize fis2:m \parenthesize b2:m | d1
        | \parenthesize b2:m d2 | a1 | \parenthesize fis2:m e:7 | a2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I come to add here within this power
    Healing, God is who gives it and if one really deserves it
    \nextverse
    And if one really deserves it, of truth and of love
    God and the Virgin Mother and Jesus the Redeemer
    \nextverse
    The Patriarch Saint Joseph and all divine beings
    Give us the grace of life, Saint John is our path
  \end{translation}
\endsong


\beginsong{Peço a Vós Minha Firmeza \\ Meu Deus}[by={Padr. Valdete},key={Am},gk={Am, Am--(Bm)},tags={2x}]
  \audio{https://www.nossairmandade.com/hymn/154/MeuDeus}
  \audio[key=A]{https://soundcloud.com/canaljagube/03-eu-venho-acrescentar?in=canaljagube/sets/hinario-nova-era_oficial}
  \newchords{chords_pecoavos_a}\newchords{chords_pecoavos_b}
  \mnbeginchorus\memorize[chords_pecoavos_a]
    \[^\mn{E}]Meu |\[\mnc{A}Am]Deus,\[\bm]{} \[^\mn{B}]meu |\[\mncii{G#}{E}E]Pai,\[\bm]{} minha |\[\mncii{D}{B}E7/D]Mãe \[\bm]{} \altchords{\id[1]{(Bm)}|Bm |F\shrp{} |F\shrp{}7/E}
    Eu pe|\[\mnc{E}E7]ço \[^\mn{D}]que \[\mnc{C}(C)]Vós \[^\mn{B}]me |\[Am]cu\[^\mn{A}]re \[\bm]{} \altchords{|F\shrp{}7 (D) |Bm}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_pecoavos_b]
    \[^\mn{A}]A \[^\mn{C}]ma|\[\mncii{E}{D}Am/E]téria \[\mnc{B}(Bm7&5)]das \[^\mn{A}]do|\[\mnc{G#}E]en\[^\mn{E}]ças\[\bm]{} \altchords{|Bm/F\shrp{} (C\shrp{}m7\flt{}5) |F\shrp{}}
    E \[^\mn{G#}]o \[^\mn{B}]es|\[\mnc{E}E7]píri\[^\mn{D}]to \[\bmc\mn{B}]do \[^\mn{G#}]es|\[\mnc{A}Am]cu\[\bm]ro \altchords{|F\shrp{}7 |Bm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_pecoavos_a]
    Meu |^Deus,^ meu |^Pai,^ minha |^Mãe ^
    Eu peço |^para Vós ^me cu|^rar ^
  \endchorus\glueverses\beginchorus\replay[chords_pecoavos_b]
    A ma|^téria ^{das do}|^enças ^
    O es|^pírito um ^bom lu|^gar ^
  \endchorus
  \beginchorus\replay[chords_pecoavos_a]
    Meu |^Deus,^ meu |^Pai,^ minha |^Mãe ^
    Eu sei que |^Vós já ^me cu|^rou ^
  \endchorus\glueverses\beginchorus\replay[chords_pecoavos_b]
    Peço a |^Vós mi^{nha fir}|^meza ^
    Para |^sempre eu ^dar va|^lor ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \repeat volta 2 {
        e4\posectionmark "A" | a2. b4 | \once\slurSolid gis4( e2) e8 e8
        | \once\slurSolid d4( b4.)( b8) b8 b8 | e4( e8) d8 c4. b8 | b4( a2)
      }
      \repeat volta 2 {
        a8\sectionmark "B" c8 | e4. d8 b4. a8 | gis4 e4.( e8) gis8 b8
        | e4 e8 d8 b4. gis8 | a2( a4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Meu | Deus, meu | Pai, __ _ mi -- nha | Mãe; __ _ _
        Eu pe -- | ço __ _ que Vós me | cu -- re.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        A ma -- | té -- ria das do -- | en -- ças;
        E o es -- | pí -- ri -- to do es -- | cu -- ro.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Meu | Deus, meu | Pai, __ _ mi -- nha | Mãe; __ _
        Eu pe -- ço | pa -- ra Vós me cu -- | rar. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        A ma -- | té -- ria das do -- | en -- ças; __ _
        O es -- | pí -- ri -- to~um bom lu -- | gar. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Meu | Deus, meu | Pai, __ _ mi -- nha | Mãe; __ _
        Eu sei que | Vós __ _ já me cu -- | rou. __ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Pe -- ço~a | Vós mi -- nha fir -- | me -- za; __ _
        Pa -- ra | sem -- pre eu dar va -- | lor. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a1:m | e | e:7/d | e2:7 \parenthesize c2 | a2.:m
      }
      \repeat volta 2 {
        s4 | a2:m/e \parenthesize b2:m7.5- | e1 | e:7 | a2.:m
      }
    }
    \include "tex/lp-include-tail-lyricsbetween.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    My God, My Father, My Mother, I ask that you cure me
    The body of illness, and the spirit of darkness
    \nextverse
    My God, My Father, My Mother, I ask for you to heal me
    The body of sickness, (and to give my) spirit a good place
    \nextverse
    My God, My Father, My Mother, I know that you've already healed me
    I ask you for my firmness, so that I always give worth
  \end{translation}
\endsong


\beginsong{Espada de São Miguel \\ Da Terra Ao Astral}[by={Baixinha}, key={Dm}, gk={Dm, Cm--Em}]
  % Also in: songs_astral_saomiguel.tex
  \audio{https://www.nossairmandade.com/hymn/2399/DaTerraAoAstral}
  \mnbeginchorus\memorize
    \[^\mn{A}]Da \[\bmc\mn{D}]Terra \[^\mn{F}]ao as|\[\mnc{A}Dm]tral \[\bm]{} | \e \altchords{\id[1]{(Em)}|Em | \e}
    Os i\[^\mn{F}]ni\[\bm]mi\[^\mn{D}]gos a\[^\mn{B&}]ta|\[\mnc{A}A]car \[\bm]{} | \e \altchords{|B | \e}
    Na es\[\bmc\mn{C#}]pada de \[^\mn{E}]São Mi|\[\mnc{G}Gm]guel \[\bm]{} |\[A7]{} \e \altchords{|Am |B7}
    \[^\mn{E}]Todos \[\bmc\mn{F}]vão se \[^\mn{E}]transfor|\[\mnc{D}Dm]mar \[\bm]{} | \e \altchords{|Em | \e}
  \mnendchorus
  \notesoff
  \beginchorus
    As ^estrelas do |^Céu ^ | \e
    Brilham ^pra quem tem a|^mor ^ | \e
    Nas ^matas do meu |^Pai ^ |^ \e
    Corre ^água e nasce |^flor ^ | \e
  \endchorus
  \beginchorus
    As ^curas estão a|^ber^-|'tas \altchords{\id[2]{(Cm)}|Cm | \e}
    Aos ^bons de cora|^ção ^ | \e \altchords{|G | \e }
    Quem ^recebe me|^re^|^ce \altchords{|Fm |G7}
    Agra^dece, nunca es|^que^-|ce \altchords{|Cm | \e}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-09
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 1*5/8
      \repeat volta 4 {
        a8\pomark d16( d16) d8 f f | a1~ | a8( a8) a8 f f d d bes | a1~
        a4( a8) a cis cis e e | g1( | g4) e8 e f f e e | d1( | d4.)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Da Ter -- _ ra ao as -- | tral; __ | _
        Os i -- ni -- mi -- gos a -- ta -- | car; __ | _
        Na es -- pa -- da~de São Mi -- | guel; __ | _
        To -- dos vão se trans -- for -- | mar. __ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        As es -- _ tre -- las do | Céu; __ | _
        \skip 1 Bri -- lham pra quem tem a -- | mor; __ | _
        \skip 1 Nas ma -- tas do meu | Pai; __ | _
        Cor -- re á -- gua~e nas -- ce | flor. __ | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        As cu -- ras es -- tão a -- | ber -- | _ _ tas;
        Aos bons de co -- ra -- | ção; __ | _ _
        Quem re -- ce -- be me -- | re -- | ce;
        A -- gra -- de -- ce, nun -- ca~es -- | que -- | ce.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2~ s8 | d1:m | d:m | a
        | a | g:m | a:7 | d:m | d4.:m
      }
    }
    \include "tex/lp-include-tail-lyricsbetween.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    On Earth and in the Astral, the enemies attack
    On the sword of Saint Michael all will be transformed
    \nextverse
    The stars of heaven shine for who has love
    In the forests of my Father runs water and flower births
    \nextverse
    The healings are open for those who are goodhearted
    Who receives, deserves, gives thanks, never forgets
  \end{translation}
\endsong


\beginsong{Jesus}[by={Lúcio Mortimer}, key={C}, gk={D, C--E}, tags={valsa}]
  % Also in: songs_astral_unilaiva_tios_queridos.tex
  \audio{https://www.nossairmandade.com/hymn/1423/Jesus}
  \meter{3}{4}
  \mnbeginchorus
    \[\mn{E}]Je|\[\mnc{C}C]sus, |\[\mnc{E}Am]ten\[\mn{D}]de \[\mn{C}]pie|\[\mnc{B}G7]da\[\mn{A}]de \[\mn{G}]de |\[\mnc{E}C]mim | \e \altchords{\id[1]{(D)}|D |Bm |A7 |D | \e}
    |\[Am]Eu \[\mn{D}]vou \[\mn{C}]pe|\[\mnc{B}G7]din\[\mn{A}]do \[\mn{G}]as|\[\mnc{G}C]sim \altchords{|Bm |A7 |D}
    \lrep \[\mn{G}]E |\[C]Vós, Se|nhor \altchords{|D | \e}
    Per|\[G]do\[\mn{F}]a \[\mn{E}]a |\[\mnc{D}G7]nós \[\mn{E}]pe\[\mn{D}]ca|\[\mnc{C}C]dor \rrep \altchords{|A |A7 |D}
  \mnendchorus
  \mnbeginchorus
    \[\mn{E}]Meu |\[\mnc{C}C]Pai \[\mn{E}]que |\[Am]tan\[\mn{D}]to \[\mn{C}]já |\[\mncii{B}{G}G7]ofen|\[\mnc{E}C]di | \e \altchords{|D |Bm |A7 |D | \e}
    E |\[Am]Vós \[\mn{D}]me \[\mn{C}]trou|\[\mnc{B}G7]xes\[\mn{G}]{te a}|\[\mnc{G}C]qui \altchords{|Bm |A7 |D}
    \lrep \[\mn{G}]No |\[C]cora|ção \altchords{|D | \e}
    Eu |\[G]re\[\mn{F}]ce\[\mn{E}]ber |\[\mnc{D}G7]meu \[\mn{E}]per|\[\mnc{C}C]dão \rrep \altchords{|A |A7 |D}
  \mnendchorus
  \mnbeginchorus
    \[\mn{E}]Que |\[\mnc{C}C]bom \[\mn{E}]estar |sem\[\mn{D}]pre \[\mn{C}]com |\[\mn{E}]Deus | \e \altchords{|D | | | \e}
    Tri|\[Am]lhar \[\mn{D}]os \[\mn{C}]ca|\[\mncii{B}{A}G7]mi\[\mn{G}]nhos |\[\mnc{G}C]seus | \e \altchords{|Bm |A7 |D | \e}
    \lrep \[\mn{G}]Com a|\[C]mor \altchords{|D}
    Na |\[G]mis\[\mn{F}]são \[\mn{E}]do |\[\mnc{D}G7]Re\[\mn{E}]den|\[\mnc{C}C]tor \rrep \altchords{|A |A7 |D}
  \mnendchorus
  \begin{translation}[EN]
    Jesus, have mercy on me; I'm asking like this
    And You, Lord, forgive us sinner
    \nextverse
    My Father that I have offended so much, and you brought me here
    In the heart I receive my forgiveness
    \nextverse
    It's good to always be with God; walk your paths
    With love on the Redeemer's Mission
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \key c \major \time 3/4 \partial 4
      \repeat volta 2 {
        e4\sectionmark "1." | c2. | e4 d c | b a g | e'2.~ | e2.
        | e4 d c | b a g | g'2
          g4\sectionmark "1.B:I" | g2 g4 | g2 g4 | g f e | d e d | c2
          g'4\sectionmark "1.B:II" | g2 g4 | g2 g4 | g f e | d e d | c2
      } \break
      \repeat volta 2 {
        e4\sectionmark "2." | c2 e4 | e4 d c | b2 g4 | e'2.~ | e2 e4
        | e4 d c | b2 g4 | g'2
          g4\sectionmark "2.B:I" | g2 g4 | g2 g4 | g4 f e | d2 e4 | c2
          g'4\sectionmark "2.B:II" | g2 g4 | g2 g4 | g4 f e | d2 e4 | c2
      } \break
      \repeat volta 2 {
        e4\posectionmark "3." | c e e | e d c | e2.~ | e2 e4 | e d c | b( a) g | g'2.~ | g4
          g4\sectionmark "3.B:I" g4 | g2 g4 | g f e | d2 e4 | c4
          g'4\sectionmark "3.B:II" g4 | g2 g4 | g f e | d2 e4 | c2
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        \set stanza = "1."
        Je -- | sus, | ten -- de pie -- | da -- de de | mim; __ |
        | Eu vou pe -- | din -- do as -- | sim.
          E | Vós, Se -- | nhor;
          Per -- | do -- a a | nós pe -- ca -- | dor.
          E | Vós, Se -- | nhor;
          Per -- | do -- a a | nós pe -- ca -- | dor.
      }
      \repeat volta 2 {
        \set stanza = "2."
        Meu | Pai que | tan -- to já | o -- fen -- | di;
        E | Vós me trou -- | xes -- te~a -- | qui.
          No | co -- ra -- | ção;
          Eu | re -- ce -- ber | meu per -- | dão.
          No | co -- ra -- | ção;
          Eu | re -- ce -- ber | meu per -- | dão.
      }
      \repeat volta 2 {
        \set stanza = "3."
        Que | bom es -- tar | sem -- pre com | Deus; __
        Tri -- | lhar os ca -- | mi -- nhos | seus.
          Com a -- | mor;
          Na | mis -- são do | Re -- den -- | tor.
          Com a -- | mor;
          Na | mis -- são do | Re -- den -- | tor.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2. | a:m | g:7 | c | c
        | a:m | g:7 | c
        | c | c | g | g:7 | c
        | c | c | g | g:7 | c2
      }
      \repeat volta 2 {
        s4 \once \set chordChanges = ##f | c2.| a:m | g:7 | c | c
        | a:m | g:7 | c
        | c | c | g | g:7 | c
        | c | c | g | g:7 | c2
      }
      \repeat volta 2 {
        s4 \once \set chordChanges = ##f | c2. | c | c | c
        | a:m | g:7 | c | c
        | c | g | g:7 | c
        | c | g | g:7 | c2
      }
    }
    \layout { #(layout-set-staff-size 14) } % to fit on one spread
    \include "tex/lp-include-tail-lyricsbetween.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Se Afrouxar}[by={Lúcio Mortimer}, key={C}, gk={C, B\flt{}--D}]
  \audio{https://www.nossairmandade.com/hymn/39/SeAfrouxar}
  \newchords{chords_seafrouxar_a}\newchords{chords_seafrouxar_b}
  \mnbeginverse\memorize[chords_seafrouxar_a]
    \[^\mn{A}]Se a\[^\mn{C}]frou|\[\mnc{E}C]xa\[\bm]r \[^\mn{C}]o \[^\mn{D}]Dai\[^\mn{C}]me |\[\mnc{A}Am]cura\[\bm], se a\[^\mn{C}]frou|\[\mnc{E}C]xa\[\bm]r \[^\mn{C}]o \[^\mn{D}]Dai\[^\mn{C}]me a|\[\mnc{A}Am]juda\[\bm]
  \mnendverse\glueverses\mnbeginchorus\memorize[chords_seafrouxar_b]
    \[^\mn{E}]Se \[^\mn{A}]af\[^\mn{E}]rou|\[\mnc{G}G]xa\[\bm]r \[^\mn{E}]o \[^\mn{A}]Dai\[^\mn{E}]me |\[^\mn{G}]salva\[\bm], \[^\mn{C}]se afrou|\[\mnc{E}Am]xa\[\mncadj{0.8em}{D}G7]{r o Dai}\[^\mn{C}]me |\[C]toma\[\bm]
  \mnendchorus
  \notesoff
  \beginverse\replay[chords_seafrouxar_a]
    Quem qui|^se^r saúde es|^cute^; tem que lim|^pa^r seu cora|^ção^
  \endverse\glueverses\beginchorus\replay[chords_seafrouxar_b]
    Não adi|^anta^ querer sa|ra^r e em se|^guida ^{ir pra} ilu|^são^
  \endchorus
  \beginverse\replay[chords_seafrouxar_a]
    Se afrou|^xa^r o Daime |^cura^, se afrou|^xa^r o Daime a|^juda^
  \endverse\glueverses\beginchorus\replay[chords_seafrouxar_b]
    Se afrou|^xa^r o Daime |salva^, se afrou|^xa^{r o} Daime |^toma^
  \endchorus
  \beginverse\replay[chords_seafrouxar_a]
    O sofri|^mento^ está na |^Terra^; é um re|^curso^ para apu|^rar ^
  \endverse\glueverses\beginchorus\replay[chords_seafrouxar_b]
    Aos que pre|^cisam^ chegar mais |perto^ do Pai E|^terno ^{e da} perfei|^ção^
  \endchorus
  \beginverse\replay[chords_seafrouxar_a]
    Se afrou|^xa^r o Daime |^cura^, se afrou|^xa^r o Daime a|^juda^
  \endverse\glueverses\beginchorus\replay[chords_seafrouxar_b]
    Se afrou|^xa^r o Daime |salva^, se afrou|^xa^{r o} Daime |^toma^
  \endchorus
  \beginverse\replay[chords_seafrouxar_a]
    Vão enten|^der^, vamos cu|^rar;^ todos têm |^do^m de se sal|^var ^
  \endverse\glueverses\beginchorus\replay[chords_seafrouxar_b]
    Saúde |^boa é^ a do es|pírito ^que se humi|^lho^{u a} nosso |^Deus
  \endchorus
  \brk
  \beginverse\replay[chords_seafrouxar_a]
    Se afrou|^xa^r o Daime |^cura^, se afrou|^xa^r o Daime a|^juda^
  \endverse\glueverses\beginchorus\replay[chords_seafrouxar_b]
    Se afrou|^xa^r o Daime |salva^, se afrou|^xa^{r o} Daime |^toma^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \parenthesize a8\posectionmark "A" a c | e4( \parenthesize e4 \parenthesize e8) c d c | a4( \parenthesize a4.) a8 a c
      | e4( \parenthesize e4 \parenthesize e8) c d c | a4( \parenthesize a4.)
      \repeat volta 2 {
        e'8\sectionmark "B" a e | g4( \parenthesize g4 \parenthesize g8) e a e | g8( \parenthesize g8 \parenthesize g4 \parenthesize g8) c,8 c c
        | e4( \parenthesize e4 \parenthesize e8) d d c | c4( \parenthesize c4.)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1. & 3. & 5. & 7."
      Se a -- frou -- | xar __ _ _ o Dai -- me | cu -- ra;
      Se a -- frou -- | xar __ _ _ o Dai -- me~a -- | ju -- da.
      \repeat volta 2 {
        Se a -- frou -- | xar __ _ _ o Dai -- me | sal -- _ va; __ _
        Se a -- frou -- | xar __ _ _ o Dai -- me | to -- ma.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \skip 1 Quem qui -- | ser __ _ _ saú -- de es -- | cu -- te;
      Tem que lim -- | par __ _ _ seu co -- ra -- | ção. __ _
      \repeat volta 2 {
        \set stanza = "2.B"
        Não a -- di -- | an -- ta __ _ que -- rer sa -- | rar; __ _ _ _
        E em se -- | gui -- da ir pra i -- lu -- | são. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      O so -- fri -- | men -- to __ _ es -- tá na | Ter -- ra;
      É um re -- | cur -- so __ _ pa -- ra~a -- pu -- | rar. __ _
      \repeat volta 2 {
        \set stanza = "4.B"
        Aos que pre -- | ci -- sam __ _ che -- gar mais | per -- _ to; __ _
        Do Pai E -- | ter -- no e da per -- fei -- | ção. __ _
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      Vão en -- ten -- | der, __ _ _ va -- mos cu -- | rar; __ _
      To -- dos têm | dom __ _ _ de se sal -- | var. __ _
      \repeat volta 2 {
        \set stanza = "6.B"
        Sa -- ú -- de | bo -- a~é __ _ a do es -- | pí -- ri -- to;
        Que se hu -- mi -- | lhou __ _ _ a nos -- so | Deus. __ _
      }
    }
    theChords = \chordmode {
      s4. | c1 | a:m | c | a2:m~ a8:m
      \repeat volta 2 {
        s4. | g1 | g | a2:m g2:7 | c2~ c8
      }
    }
    \layout { #(layout-set-staff-size 13) } % to fit on one spread
    % Custom score block to put the first verse in between staffs, and the
    % rest below.
    \score {
      <<
        \new ChordNames { \theChords }
        \new Staff { \clef "treble" \new Voice = "theVoice" { \theMelody } }
        \new Lyrics \lyricsto "theVoice" { \theLyricsOne }
        \include "tex/lp-internal-tabstaff.ly"
        \new Lyrics \lyricsto "theVoice" { \theLyricsTwo }
        \new Lyrics \lyricsto "theVoice" { \theLyricsFour }
        \new Lyrics \lyricsto "theVoice" { \theLyricsSix }
      >>
      \layout { }
    }
    \include "tex/lp-internal-midi-score.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]\iflyriconly\scriptsize\fi% to fit on one page in lyrics-only book
    If you relax the Daime cures, if you relax the Daime helps
    If you relax the Daime saves, if your relax the Daime takes
    \nextverse
    Whoever wants health, listen; one must clean one's heart
    It's not worthwhile to want to heal and later go back to the illusion
    \nextverse
    If you relax the Daime cures, if you relax the Daime helps
    If you relax the Daime saves, if your relax the Daime takes
    \nextverse
    Suffering is on Earth; it's a resource to purify
    Those who need to be closer to the eternal father and the perfection
    \nextverse
    If you relax the Daime cures, if you relax the Daime helps
    If you relax the Daime saves, if your relax the Daime takes
    \nextverse
    Go understand, let's heal; everyone has the gift of saving oneself
    Good health is of the spirit who is humbled before our God
    \nextverse
    If you relax the Daime cures, if you relax the Daime helps
    If you relax the Daime saves, if your relax the Daime takes
  \end{translation}
\endsong


\beginsong{Força de Cura}[by={Lúcio Mortimer}, key={C}, gk={C, G\shrp{}--D}, tags={marcha e meia valsa}]
  \audio{https://www.nossairmandade.com/hymn/1437/For\%C3\%A7aDeCura}
  \audio{https://www.youtube.com/watch?v=-b4u-O4VUJI}
  \mnbeginchorus\memorize
    \lrep \[\bm]{} \[^\mn{C}]Chamei \[^\mn{E}]a |\[\mnc{G}C]for\[^\mn{E}]ça \[\bm]
    \[^\mn{G}]E\[^\mn{A}]la é \[^\mn{G}]de |\[\mnc{F}G7]cu\[^\mn{D}]ra \rrep
    \lrep \[\bmc\mnc{C}C]Sempre pedindo \[^\mn{E}]ao |\[^\mn{G}]Mes\[^\mn{C}]tre
    No plano \[^\mn{E}]ter\[\bmc\mnc{G}G7]res\[^\mn{C}]tre
    Ele é \[^\mn{D}]quem \[^\mn{B}]nos se|\[\mnc{C}C]gura \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep ^ Nesta ses|^são ^
    Só tem bon|^dade \rrep
    \lrep ^Vamos rezar pro do|ente
    Que é dever da ^gente
    Ter a cari|^dade \rrep
  \endchorus
  \beginchorus
    \lrep ^ Jesus a|^tende ^
    Quem Lhe pro|^cura \rrep
    \lrep ^Peço firmeza na |mente
    Fechar a cor^rente
    Que a força é de |^cura \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \key c \major \time 4/4 \partial 2
      \repeat volta 2 {
        r8 c8\posectionmark "A" c e | g4 e4. g8 a g | f4 d4
      }
      \repeat volta 2 {
        \tuplet 3/2 4 { c8\sectionmark "B" c c c c e | g c, c c c e g c, c d b b }
      } \alternative {
        { | c4 c4 }
        { | c4 c4^\dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Cha -- mei a | for -- ça;
      E -- la~é de | cu -- ra.
      \set stanza = "1.B"
      Sem -- pre pe -- din -- do ao | Mes -- tre;
      No pla -- no ter -- res -- tre;~E
      le~é quem nos se -- | gu -- ra.
         | gu -- ra.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Nes -- ta ses -- | sã -- o;
      Só tem bon -- | da -- de.
      \set stanza = "2.B"
      Va -- mos re -- zar pro do -- | en -- te;
      Que~é de -- ver da gen -- te;
      Ter a ca -- ri -- | da -- de.
         | da -- de.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      Je -- sus a -- | ten -- de;
      Quem Lhe pro -- | cu -- ra.
      \set stanza = "3.B"
      Pe -- ço fir -- me -- za na | men -- te;
      Fe -- char a cor -- ren -- te;
      Que~a for -- ça~é de | cu -- ra.
         | cu -- ra.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | c1 | g2:7
      }
      \repeat volta 2 {
        c2 | c2 g2:7
      } \alternative {
        { | c2 }
        { | c2 }
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I called the force, it's a healing force
    Always asking the Master
    In the terrestrial plane
    It's Him who secures us
    \nextverse
    In this session there's only goodness
    Let's pray for the sick
    For it's our duty
    To do charity
    \nextverse
    Jesus answers those who search for Him
    I ask firmness in the mind
    Close the current
    For the force is a healing force
  \end{translation}
\endsong


\beginsong{Vim Pedir o Meu Perdão}[by={Gercila}, off={Geraldine}, key={Em}, gk={Em, Cm--Em}]
  \audio[key=Em]{https://www.youtube.com/watch?v=c9BhGV-wuNs}
  \mnbeginchorus\memorize
    \[^\mn{E}]Mi\[^\mn{F#}]nha |\[\mnc{G}Em]Mãe es\[\bmc\mn{F#}]tou \[^\mn{E}]a|\[\mnc{C}C]qui\[\bm]{} \altchords{\id[1]{(Dm)}|Dm |B\flt{} }
    \[^\mn{E}]Eu vim \[^\mn{F#}]pe|\[\mnc{G}Am7]{dir o} \[\bmc\mn{F#}]meu \[^\mn{E}]per|\[\mnc{B}B7]dão\[\bm]{} \altchords{|Gm7 |A7 }
    \lrep \[^\mn{A}]Eu sei que |\[Am]Vós \[\mnc{B}Asus2]tem po|\[\mnc{E}Em]der \altchords{|Gm Gsus2 |Dm }
    E \[\bmc\mn{G}]me dê |\[\mnc{F#}B7]se \[^\mn{G}]eu \[\bm\mn{A}]me\[^\mn{G}]re|\[\mnc{E}Em]cer\[\bm]{} \rrep \altchords{|A7 |Dm }
  \mnendchorus
  \notesoff
  \beginchorus
    Estou pas|^sando um ^julga|^men^to
    Aqui no |^meio da es^curi|^dão^
    \lrep Eu peço a |^Vós um en^tendi|^mento
    ^Que é pa|^ra meu ^segui|^men^to \rrep
  \endchorus
  \beginchorus
    Estou pas|^sando as ^amar|^gu^ras
    Aqui em|^baixo ^neste |^chão^
    \lrep Mas sei que |^Vós a^{i de} |^cima
    ^Me es|^tende as ^vossas |^mãos^ \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2022-07
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key e \minor \time 4/4 \partial 4.
      \parenthesize e8 \posectionmark "A" e8 fis8 | g4 g4 fis4 e4 | c2( 8)
      e8 e8 fis8 | g4 g4 fis4 e4 | b2~8
      \repeat volta 2 {
        a'8 \sectionmark "B" a8 a8 | a4.( a8) b4. b8 | e,4. e8 g4. g8
        | fis4. g8 a4. g8
      } \alternative {
        { | e2( 8) }
        { | e2( 8) \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 Mi -- nha | Mãe es -- tou a -- | qui; __ _
      Eu vim pe -- | dir o meu per -- | dão. __ _
      \repeat volta 2 {
        Eu sei que | Vós __ _ tem po -- | der;
        E me dê | se eu me -- re --
      } \alternative {
        { | cer. __ _ }
        { | cer. __ _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Es -- tou pas -- | san -- do~um jul -- ga -- | men -- to;
      A -- qui no | meio da~es -- cu -- ri -- | dão. __ _
      \repeat volta 2 {
        Eu pe -- ço~a | Vós um~en -- ten -- di -- | men -- to;
        Que~é pa -- | ra meu se -- gui --
      } \alternative {
        { | men -- to. }
        { | men -- to. }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Es -- tou pas -- | san -- do~as a -- mar -- | gu -- ras;
      A -- qui em -- | bai -- xo nes -- te | chão. __ _
      \repeat volta 2 {
        Mas sei que | Vós a -- i de | ci -- ma;
        Me es -- | ten -- de~as vos -- sas
      } \alternative {
        { | mãos. __ _ }
        { | mãos. __ _ }
      }
    }
    theChords = \chordmode {
      s4. | e1:m | c1 | a1:m7 | b2:7~8
      \repeat volta 2 {
        s4. | a2:m a2:sus2 | e1:m | b1:7
      } \alternative {
        { | e2:m~8 }
        { | e2:m~8 }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    My mother I'm here, I came to ask for my forgiveness
    I know you have power and give it to me if I deserve it
    \nextverse
    I'm passing a trial here in the middle of the darkness
    I ask you for an understanding which is for my follow-up
    \nextverse
    I'm passing the bitterness down here on this floor
    But I know that you from above extend your hands to me
  \end{translation}
\endsong


\beginsong{Pequenininho}[by={Saturnito Brito}, off={Ana Emilly}, key={B}, gk={B}]
  \audio{https://nossairmandade.com/hymn/2979/Pequenininho}
  \mnbeginchorus
    \[\mn{B}]Pe\[\mn{C#}]que\[\mn{D#}]ni|\[\mnc{E}E]ni\[\bm]nho, \[\mn{C#}]peque\[\mn{B}]ni|\[B]ni\[\bm]nho \altchords{\id[1]{(C)}|F |C}
    \[\mn{G#}]Peque\[\mn{F#}]ni|\[F#]ni\[\mn{E}]nho pa\[\mn{D#}]ra \[\bm]se\[\mn{C#}]guir no \[\mn{B}]ca|\[\mnc{/}B]minho \altchords{|G |C}
    \mnendchorus\glueverses\mnbeginchorus
    \[\bmc\mn{B}]Grande na ale|\[B]gri\[\mn{A#}]a, \[\bmc\mn{G#}]gran\[\mn{F#}]de \[\mn{G#}]na \[\mn{B}]ver|\[\mnc{A#}F#]dade \altchords{|C |G}
    \[\bmc\mn{C#}]Grande na harmo|\[\mn{F#}]ni\[\mn{E}]a, \[\bm]gran\[\mn{D#}]de na hu\[\mn{C#}]mil|\[\mnc{B}B]dade \altchords{| - |C}
  \mnendchorus
  \beginchorus
    Pequeni|\[E]ni\[\bm]nho, pequeni|\[B]ni\[\bm]nho
    Pequeni|\[F#]ninho para \[\bm]seguir no ca|\[B]minho
    \endchorus\glueverses\beginchorus
    \[\bm]Grande na fir|\[B]meza, \[\bm]grande no a|\[F#]mor
    \[\bm]Grande na cer|teza, do nos\[\bm]so Pai Cria|\[B]dor
  \endchorus
  \dacapo
  \beginchorus
    Pequeni|\[E]ni\[\bm]nho, pequeni|\[B]ni\[\bm]nho
    Pequeni|\[F#]ninho para \[\bm]seguir no ca|\[B]mi\[\bm]nho
  \endchorus
  \begin{translation}[EN]
    Tiny, tiny, small to follow on the way
    \nextverse
    Big on joy, really big
    Big on harmony, great in humility
    \nextverse
    Tiny, tiny, small to follow on the way
    \nextverse
    Big in firmness, big in love
    Great for sure, from our Creator Father
    \nextverse
    Tiny, tiny, small to follow on the way
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2023-03
    theMelody = \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key b \major \time 4/4 \partial 4.
      \repeat volta 2 {
        b8 \sectionmark "1.A" cis dis | e2 e8 cis'8 cis8 b | b2 b8 gis8 gis8 fis8
        | fis8 e8 e8 dis8 dis8 cis8 cis8 b8
      } \alternative {
        { | dis2 dis8 }
        { | b4. b8 }
      }
      \repeat volta 2 {
        b8 \sectionmark "1.B" b8 b8 b8 | b4. ais8 gis8 fis8 gis8 b8 | ais4. ais8 cis8 cis8 cis8 cis8
        | fis4. e8 e8 dis8 dis8 cis8
      } \alternative {
        { | b4.( b8) }
        { | b2( b8) }
      }
      \repeat volta 2 {
        b8 \sectionmark "2.A" cis dis | e2 e8 cis'8 cis8 b | b2 b8 gis8 gis8 fis8
        | fis8 e8 e8 dis8 dis8 cis8 cis8 b8
      } \alternative {
        { | dis2 dis8 }
        { | b4. b8 }
      }
      \repeat volta 2 {
        b8 \posectionmark "2.B" b8 b8 b8 | b4. ais8 gis8 fis8 gis8 b8 | ais2 cis8 cis8 cis8 cis8
        | fis8 fis8 fis8 e8 e8 dis8 dis8 cis8
      } \alternative {
        { | b4.( b8) }
        { | b2( b8) \dacapo }
      }
      \repeat volta 2 {
        b8 \sectionmark "final" cis dis | e2 e8 cis'8 cis8 b | b2 b8 gis8 gis8 fis8
        | fis8 e8 e8 dis8 dis8 cis8 cis8 b8
      } \alternative {
        { | dis2 dis8 }
        { | b4. b8 }
      }
      \bar "|."
    }
    lyricsPequenininho = \lyricmode {
      \repeat volta 2 {
        Pe -- que -- ni -- | ni -- nho, pe -- que -- ni -- | ni -- nho;
        Pe -- que -- ni -- | ni -- nho pa -- ra se -- guir no ca --
      } \alternative {
        { | mi -- nho. }
        { | mi -- nho. }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \lyricsPequenininho
      \set stanza = "1.B"
      \repeat volta 2 {
        Gran -- de na~a -- le -- | gri -- a;
        Gran -- de na ver -- | da -- de;
        Gran -- de na~har -- mo -- | ni -- a;
        Gran -- de na~hu -- mil --
      } \alternative {
        { | da -- de. }
        { | da -- de. }
      }
      \set stanza = "2.A"
      \lyricsPequenininho
      \set stanza = "2.B"
      \repeat volta 2 {
        Gran -- de na -- fir -- | me -- za;
        Gran -- de no a -- | mor;
        Gran -- de na cer -- | te -- za;
        Do nos -- so Pai Cri -- a --
      } \alternative {
        { | dor. __ _ }
        { | dor. __ _ }
      }
      \set stanza = "X."
      \lyricsPequenininho
    }
    chordsPequenininho = \chordmode {
      \repeat volta 2 {
        s4. | e1 | b | fis
      } \alternative {
        { | b2~8 }
        { | b2 }
      }
    }
    chordsGrande = \chordmode {
      \repeat volta 2 {
        s2 | b1 | fis1 | fis1
      } \alternative {
        { | b2 }
        { | b2~8 }
      }
    }
    theChords = \chordmode {
      \chordsPequenininho
      \chordsGrande
      \chordsPequenininho
      \chordsGrande
      % final
      \chordsPequenininho
    }
    \layout { #(layout-set-staff-size 13) } % for better fit
    \include "tex/lp-include-tail-lyricsbetween.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Vigiai}[by={Saturnito Brito}, tags={valsa, 2x}, key={C}, gk={C, B--C}]
  \audio{https://www.nossairmandade.com/hymn/2985/Vigiai}
  \newchords{chords_vigiai_a}\newchords{chords_vigiai_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_vigiai_a]
    \[^\mn{G}]Fecha |\[\mnc{C}C]bem \[^\mn{D}]a |\[^\mn{E}]tu\[^\mn{D}]a |\[^\mn{C}]por|ta \altchords{\id[1]{A}|A | - | - | \e}
    Vigi|\[\mnc{F}F]ai \[^\mn{A}]e |\[^\mn{C}]vi\[^\mn{A}]gi|\[\mnc{G}C]ai | \e \altchords{|D | - |A | \e}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_vigiai_b]
    \[^\mn{C}]Faz en|\[\mnc{F}F]trar \[^\mn{A}]as |\[^\mn{C}]coi\[^\mn{A}]sas |\[\mnc{G}C]bo|\[G]as \altchords{|D | - |A |E}
    \[^\mn{B}]Do \[^\mn{A}]Di|\[^\mn{G}]vino, |\[\mnc{F}Dm]nos\[^\mn{D}]so |\[\mnc{C}C]Pai | \e \altchords{| - |Bm |A | \e}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_vigiai_a]
    Fecha |^bem a |tua |por|ta
    Vigi|^ai e |vigi|^ai | \e
    \endchorus\glueverses\beginchorus\replay[chords_vigiai_b]
    Pra não en|^trar a |coisa à |^to|^a
    Que desa|grada o |^nosso |^Pai | \e
  \endchorus
  \beginchorus\replay[chords_vigiai_a]
    Fecha |^bem a |tua |por|ta
    Vigi|^ai e |vigi|^ai | \e
    \endchorus\glueverses\beginchorus\replay[chords_vigiai_b]
    Para |^ser um |apa|^re|^lho
    Do Di|vino |^nosso |^Pai | \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 1*5/8
      \repeat volta 2 {
        r8 \posectionmark "A" g4 g4 | c2 d4 | e2 d4 | c2. | c4
        c4 c4 | f2 a4 | c2 a4 | g2.~ | g8
      }
      \repeat volta 2 {
        \altcol\parenthesize c,8 \altmark "2." \sectionmark "B" c4 c4 | f2 a4 | c2 a4 | g2. | g8( \altcol g8) \altmark "2."
        b4 a4 | g2 g4 | f2 d4 | c2.~ | c8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Fe -- cha | bem a | tu -- a | por -- | ta;
      Vi -- gi -- | ai e | vi -- gi -- | ai. __ | _
      \set stanza = "1.B"
      \skip 1 Faz en -- | trar as | coi -- sas | bo -- | as; __ _
      Do Di -- | vi -- no, | nos -- so | Pai. __ | _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Fe -- cha | bem a | tu -- a | por -- | ta;
      Vi -- gi -- | ai e | vi -- gi -- | ai. __ | _
      \set stanza = "2.B"
      \altcol Pra não en -- | trar a | coi -- sa~à | to -- | a;
      \altcol Que de -- sa -- | gra -- da~o | nos -- so | Pai. __ | _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      Fe -- cha | bem a | tu -- a | por -- | ta;
      Vi -- gi -- | ai e | vi -- gi -- | ai. __ | _
      \set stanza = "3.B"
      \skip 1 Pa -- ra | ser um | a -- pa -- | re -- | lho; __ _
      Do Di -- | vi -- no | nos -- so | Pai. __ | _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2~s8 | c2. | c2. | c2. | c2.
        | f2. | f2. | c2. | c8
      }
      \repeat volta 2 {
        s2~s8 | f2. | f2. | c2. | g2. | g2. | d2.:m | c2. | c8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Close your door well, watch and watch
    Bring in the good things from the Divine, our Father
    \nextverse
    Close your door well, watch and watch
    To not enter the random thing that displeases our Father
    \nextverse
    Close your door well, watch and watch
    To be an instrument of the Divine, our Father
  \end{translation}
\endsong


\beginsong{Eu Tenho Fé}[by={Luiz Mendes}, tags={3x}, key={Gm}, gk={Gm, Gm--Bm}]
  \audio{https://www.nossairmandade.com/hymn/3067/EuTenhoF\%C3\%A9}
  \audio[key=Gm]{https://www.youtube.com/watch?v=SsAOIC1enuA}
  \mnbeginchorus
      \[\mn{D}]Eu \[\mn{E&}]te\[\mn{D}]nho |\[\mnc{G}Gm]fé \[\mn{D}]em \[\mn{E&}]meu \[\mn{D}]Je|\[\mn{G}]sus \altchords{\id[1]{(Am)}|Am | \e}
      \[\mn{D}]Que \[\mn{E&}]E\[\mn{D}]le |\[\mnc{A}D7]há \[\mn{C}]de \[\mn{D}]me \[\mn{B&}]cu|\[\mnc{G}Gm]rar \altchords{|E7 |Am}
  \mnendchorus
  \mnbeginchorus
      \[\mn{A}]É \[\mn{B&}]cu\[\mn{E&}]ra|\[\mnc{D}Gm]dor, \[\mn{A}]é \[\mn{B&}]cu\[\mn{E&}]ra|\[\mn{D}]dor \altchords{|Am | \e}
      \[\mn{A}]E ao \[\mn{B&}]meu \[\mn{E&}]Je|\[\mnc{D}D7]sus \[\mn{C}]eu \[\mn{B&}]dou \[\mn{A}]lou|\[\mnc{G}Gm]vor \altchords{|E7 |Am}
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \minor \time 4/4 \partial 1*5/8
      \repeat volta 2 {
        d8 \posectionmark "A" es4 d4 | g4 d4 es4 d4 | g4 d4
        es4 d4 | a4 c4 d4 bes4 | g4.
      }
      \repeat volta 2 {
        a8 \sectionmark "B" bes4 es4 | d4 a4 bes4 es4 | d4. a8
        bes4 es4 | d4 c4 bes4 a4 | g4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "A."
        Eu te -- nho | fé em meu Je -- | sus;
        Que E -- le | há de me cu -- | rar.
      \set stanza = "B."
        É cu -- ra -- | dor, é cu -- ra -- | dor;
        E~ao meu Je -- | sus eu dou lou -- | vor.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2~s8 | g1:m | g1:m | d1:7 | g4.:m
      }
      \repeat volta 2 {
        s2~s8 | g1:m | g1:m | d1:7 | g4.:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I have faith in my Jesus, that he will heal me
    \nextverse
    Is a healer, is a healer, and to my Jesus I give praise
  \end{translation}
\endsong


\beginsong{Lá Vem Mestre Irineu}[by={Maria de Conceição}, off={Saturnino Brito}, key={D}, gk={D, C--E}]
  \audio[key=D]{https://www.youtube.com/watch?v=izMUkIAXZZs}
  \normalsize % make smaller to fit all verses on one spread
  \mnbeginchorus\memorize
    \[^\mn{F#}]Lá |\[\mnc{E}A7]vem \[^\mn{G}]Mes\[^\mn{F#}]tre I\[^\mn{E}]ri|\[\mnc{D}D]neu \altchords{\id[1]{(C)}|G7 |C}
    \[^\mn{F#}]Com seu |\[\mnc{E}A7]ca\[^\mn{G}]ja\[^\mn{F#}]do \[^\mn{E}]na |\[\mnc{D}D]mão \altchords{|G7 |C}
    \[^\mn{F#}]Aben|\[\mnc{E}A7]ço\[^\mn{G}]an\[^\mn{F#}]do \[^\mn{E}]a |\[\mnc{D}D]todo \altchords{|G7 |C}
    \[^\mn{B}]Que es|\[Bm]tão neste \[^\mn{A}]sa|\[\mnc{E}Em]lão \altchords{|Am |Dm}
    \[^\mn{G}]Nosso |\[G]Mestre vem \[^\mn{F#}]fe|\[\mnc{E}Em]liz \altchords{|A |Dm}
    \[^\mn{G}]Ale|\[G]grar a nos\[^\mn{F#}]sa |\[\mnc{E}Em]festa \altchords{|A |Dm}
    \[^\mn{G}]Traz a |\[G]força das \[^\mn{F#}]fa|\[\mnc{A}A7]lan\[^\mn{G}]ges \altchords{|A |G7}
    Dos \[^\mn{F#}]ca|bo\[^\mn{E}]clos da \[^\mn{D}]flo|\[D]resta \altchords{| - |C}
  \mnendchorus
  \notesoff
  \beginchorus
    Nosso |^grande compa|^nheiro \altchords{\id[2]{(E)}|B7 |E}
    Foi Mes|^tre na disci|^plina \altchords{|B7 |E}
    Quando |^implantou na |^Terra \altchords{|B7 |E}
    Esta |^Divina Dou|^trina \altchords{|C\shrp{}m |F\shrp{}m}
    Conti|^nua no es|^paço \altchords{|A |F\shrp{}m}
    Do as|^tral superi|^or \altchords{|A |F\shrp{}m}
    Zelan|^do pelo Dou|^trina \altchords{|A |B7}
    Aumen|tando o seu va|^lor \altchords{| - |E}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2022-08
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 2
      \repeat volta 2 {
        \parenthesize fis4 \pomark fis4 | e4 g fis e | d4.( d8)
        fis4 fis4 | e4 g fis e | d4.( d8)
        fis4 fis4 | e4 g fis e | d4. d8
        b4 b4 | b4 b4 b4 a4 | e'4.( e8)
        g4 g4 | g g g fis | e4.( e8)
        g4 g4 | g g g fis | e4.( e8)
        g4 g4 | g g g fis | a4. g8
        g4 fis | fis e e d | d4.( d8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 Lá | vem Mes -- tre~I -- ri -- | neu; __ _
      Com seu | ca -- ja -- do na | mão; __ _
      A -- ben -- | ço -- an -- do a | to -- do;
      Que es -- | tão nes -- te sa -- | lão; __ _
      Nos -- so | Mes -- tre vem fe -- | liz; __ _
      A -- le -- | grar a nos -- sa | fes -- ta;
      Traz a | for -- ça das fa -- | lan -- ges;
      Dos ca -- | bo -- clos da flo -- | res -- ta.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Nos -- so | gran -- de com -- pa -- | nhei -- ro;
      Foi Mes -- | tre na dis -- ci -- | pli -- na;
      Quan -- do | im -- plan -- tou na | Ter -- ra;
      Es -- ta | Di -- vi -- na Dou -- | tri -- na;
      Con -- ti -- | nu -- a no es -- | pa -- ço;
      Do as -- | tral su -- pe -- ri -- | or __ _
      Ze -- lan -- | do pe -- lo Dou -- | tri -- na;
      Au -- men -- | tan -- do~o seu va -- | lor. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | a1:7 | d
        | a:7 | d
        | a:7 | d
        | b,:m | e:m
        | g | e:m
        | g | e:m
        | g | a:7
        | a:7 | d2
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Here comes Mestre Irineu with his staff in hand
    Blessing all who are in this hall
    Our Master comes happy cheering up our party
    Brings the strength of the phalaxes from the caboclos of the forest
    \nextverse
    Our great companion, Master in discipline
    When he was implanted on Earth, this Divine Doctrine
    Continues in space, from the superior astral
    Watching over the Doctrine, Increasing its value
  \end{translation}
\endsong
