% Santo Daime: Cura II
% ====================
%
\audio[title={Nossa Irmandade}]{https://www.nossairmandade.com/hinario/3/CuraII}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Eu Vivo na Floresta}[by={Padr. Sebastião},key={C},sks={C, A, B, D}]
  \audio{https://www.nossairmandade.com/hymn/66/EuVivoNaFloresta}
  \newchords{chords_cura_euvivonafloresta_a}\newchords{chords_cura_euvivonafloresta_b}
  \mnbeginchorus\memorize[chords_cura_euvivonafloresta_a]
    \[^\mn{C}]Eu |\[C]vivo \[\bm]na flo|\[\mnc{A}F]res\[\bmc\mn{F}]ta, \[^\mn{A}]eu |te\[^\mn{G}]nho os \[\bmc\mn{C}]meus \[^\mn{E}]en|\[\mnc{G}G]si\[\bm]nos
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_cura_euvivonafloresta_b]
    \[^\mn{G}]Eu |\[\mnc{E}C]não \[^\mn{C}]me \[\bmc\mn{D}]cha\[^\mn{C}]mo |\[\mnc{A}Am]Dai\[\bmc\mn{C}]me, \[^\mn{E}]eu |\[\mnc{G}G]sou \[^\mn{E}]é um \[\bmc\mnc{F}G7]ser \[^\mn{D}]di|\[\mnc{C}C]vi\[\bm]no
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    Eu |^sou um ^ser di|^vino, eu ^venho a|qui para ^te ensi|^nar ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    \noteson\[\mnlow{E}]Quan\[\mnlow{G}]to \notesoff|^mais pu^xar por |^mim, ^mais eu |^tenho ^que te |^dar ^
  \endchorus
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    Muito eu |^tenho ^que te |^dar, e ^também |tenho para ^te di|^zer ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    Quem |^tem dois ^olhos en|^xerga, ^mas os |^cegos ^também |^vêem ^
  \endchorus
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    Os en|^sinos ^da Ra|^inha, ^todos e|les são ^divi|^nal ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    E|^les são ^das cor|^tinas, ^lá do |^alto ^do as|^tral ^
  \endchorus
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    Eu te en|^trego es^tes en|^sinos, ^como |que seja ^uma |^flor ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    Gra|^vai bem ^no teu |^pei^to, es|^te tão ^grande a|^mor ^
  \endchorus
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    Es|^te tão ^grande a|^mor, é ^para |todos os ^meus ir|^mãos ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    \noteson\[\mnlow{E}]Os \[\mnlow{G}]en\notesoff|^sinos ^da Ra|^inha, e ^do Mes|^tre Ju^rami|^dam ^
  \endchorus
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    Meus a|^migos e ^meus ir|^mãos, ^todos |vão gos^tar de |^ver ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    \noteson\[\mnlow{E}]Que \[\mnlow{G}]a\notesoff|^qui nes^te sa|^lão, ^tem mui|^to que se ^apren|^der ^
  \endchorus
  \brk
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    Aquele |^que não ^apren|^der, é ^porque |não pres^ta aten|^ção ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    \noteson\[\mnlow{E}]Mui\[\mnlow{G}]to \notesoff|^terá ^que so|^frer, ^aqui |^na re^uni|^ão ^
  \endchorus
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    O |^Mestre ^e a Ra|^inha, ^eles |têm um ^grande a|^mor ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    \noteson\[\mnlow{E}]Eles \[\mnlow{G}]es\notesoff|^tão fa^zendo |^paz, ^como |^Cristo ^Reden|^tor ^
  \endchorus
  \beginchorus\replay[chords_cura_euvivonafloresta_a]
    Jesus |^Cristo ^veio ao |^mundo, ^e so|freu a^té mor|^rer ^
    \endchorus\glueverses\beginchorus\replay[chords_cura_euvivonafloresta_b]
    \noteson\[\mnlow{E}]Mas \[\mnlow{G}]dei\notesoff|^xou os ^seus en|^sinos, pa^ra quem |^quiser ^apren|^der ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \altcol c8 \altmark "8." c8\posectionmark "A" ( c8) | c4 c c c | a'4( a8) \parenthesize f8 f4 a | a g8( g8) c4 e, | g2( g8)
      } \break
      \repeat volta 2 {
        \altcol e8 \altmark "9." << e8 \parenthesize g8( \sectionmark "B" >> g8)
        | e4 c d c | a( a8)( a8) c4 e | g e8( e8) f4 d | c2( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        \skip 1 Eu __ _ | vi -- vo na flo -- | res -- _ _ ta,
        eu | te -- nho os meus en -- | si -- nos.
      \set stanza = "1.B"
        \skip 1 \parenthesize Eu __ _ | não me cha -- mo | Dai -- _ _ me,
        eu | sou é um ser di -- | vi -- no.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
        \skip 1 Eu __ _ | sou um ser di -- | vi -- no,
        eu ve -- nho~a -- | qui pa -- ra te~en -- si -- | nar. __ _
      \set stanza = "2.B"
        \skip 1 Quan -- to | mais pu -- xar por | mim, __ _ _
        mais eu | te -- nho __ _ que te | dar. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \skip 1 Mui -- to~eu | te -- nho que te | dar, __ _
      e tam -- bém | tenho pa -- ra te di -- | zer. __ _
      \set stanza = "3.B"
      \skip 1 \parenthesize Quem __ _ | tem dois olhos en -- | xer -- _ ga,
      mas os | ce -- gos __ _ tam -- bém | vêem. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \skip 1 Os en -- | si -- nos da Ra -- | i -- _ nha,
      to -- dos~e -- | les são __ _ di -- vi -- | nal. __ _
      \set stanza = "4.B"
      \skip 1 \parenthesize E -- __ _ | les são das cor -- | ti -- _ nas,
      lá do | al -- to __ _ do as -- | tral. __ _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \skip 1 Eu te~en -- | tre -- go~es -- tes en -- | si -- _ nos,
      co -- mo | que se -- ja u -- ma | flor. __ _
      \set stanza = "5.B"
      \skip 1 \parenthesize Gra -- __ _ | vai bem no teu | pei -- _ _ to,
      es -- | te tão __ _ gran -- de~a -- | mor. __ _
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \skip 1 Es -- _ | te tão gran -- de~a -- | mor, __ _
      é pa -- ra | to -- dos os meus ir -- | mãos. __ _
      \set stanza = "6.B"
      \skip 1 Os en -- | si -- nos da Ra -- | i -- nha,
      e do Mes -- | tre Ju -- _ ra -- mi -- | dam. __ _
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7.A"
      \skip 1 Meus a -- | mi -- gos~e meus ir -- | mã -- _ os,
      to -- dos | vão gos -- _ tar de | ver. __ _
      \set stanza = "7.B"
      \skip 1 Que a -- | qui nes -- te sa -- | lão, __ _ _
      tem mui -- | to que se a -- pren -- | der. __ _
    }
    theLyricsEight = \lyricmode {
      \set stanza = "8.A"
      \altcol A -- que -- le | que não a -- pren -- | der, __ _
      é por -- que | não pres -- _ ta~a -- ten -- | ção. __ _
      \set stanza = "8.B"
      \skip 1 Mui -- to | te -- rá que so -- | frer, __ _ _
      a -- qui | na re -- _ u -- ni -- | ão. __ _
    }
    theLyricsNine = \lyricmode {
      \set stanza = "9.A"
      \skip 1 O __ _ | Mes -- tre e~a Ra -- | i -- _ nha,
      e -- les | têm um __ _ gran -- de~a -- | mor. __ _
      \set stanza = "9.B"
      \altcol E -- les es -- | tão fa -- zen -- do | paz, __ _ _
      co -- mo | Cris -- to __ _ Re -- den -- | tor. __ _
    }
    theLyricsTen = \lyricmode {
      \set stanza = "10.A"
      \skip 1 Je -- sus | Cris -- to veio ao | mun -- _ do,
      e so -- | freu a -- _ té mor -- | rer. __ _
      \set stanza = "10.B"
      \skip 1 Mas dei -- | xou os seus en -- | si -- nos,
      pa -- ra quem | qui -- ser __ _ a -- pren -- | der. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1 | f | f | g2~ g8
      }
      \repeat volta 2 {
        s4. | c1 | a:m | g2 \parenthesize g2:7 | c2~ c8
      }
    }
    \layout { #(layout-set-staff-size 13) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I live in the forest, I have my teachings
    I don't call myself Daime, I am a Divine Being
    \nextverse
    I am a Divine Being, I come here to teach you
    The more you ask of me, the more I have to give you
    \nextverse
    Much I have to give you, and also to say to you
    Who has two eyes sees, but the blind also see
    \nextverse
    The teachings of the Queen, all of them are divine
    They are from the curtains of the height of the astral
    \nextverse
    I give you these teachings as if they were a flower
    Engrave well in your heart this great love
    \nextverse
    This great love is for all of my brothers and sisters
    The teachings of the Queen and of the Master Juramidam
    \nextverse
    My friends and my brothers and sisters will all be glad to see
    That here inside this room there is much to be learned
    \nextverse
    He who doesn't learn, it's because he doesn't pay attention
    He will suffer a great deal here in the reunion
    \nextverse
    The Master and the Queen, they have a great love
    They are bringing peace as did Christ the Redeemer
    \nextverse
    Jesus Christ came to the world, and he suffered until he died
    But He left His teachings for those who want to learn
  \end{translation}
\endsong


\beginsong{Princesa Janaína}[by={Padr. Sebastião},key={G},sks={A, G, B}]
  \audio{https://www.nossairmandade.com/hymn/67/PrincesaJana\%C3\%ADna}
  \newchords{chords_princesajanaina_a}\newchords{chords_princesajanaina_b}
  \mnbeginchorus\memorize[chords_princesajanaina_a]
    \[^\mn{B}]Je\[^\mn{C}]sus |\[\mnc{D}G]Cristo \[^\mn{B}]es\[\bmc\mn{G}]tá \[^\mn{B}]no |\[^\mn{D}]céu \altchords{\id[1]{(A)}|A | \e}
    \[^\mn{B}]Es\[\bmc\mn{G}]tá \[^\mn{B}]na |\[^\mn{D}]terra \[^\mn{B}]es\[\bmc\mn{G}]tá \[^\mn{B}]no |\[^\mn{D}]mar \[\bm] \altchords{| - | \e}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_princesajanaina_b]
    \[^\mn{G}]A Prin|\[\mnc{C}C]ce\[^\mn{B}]sa \[\mnc{A}Am]Ja\[^\mn{C}]na|\[\mnc{B}G]í\[^\mn{G}]na \altchords{|D Bm |A }
    \[(Em)]E\[^\mn{B}]la |\[\mnc{D}D]veio pa\[^\mn{C}]ra \[\bmc\mn{A}]me en\[^\mn{B}]si|\[\mnc{G}G]nar \[\bm] \altchords{(F\#m) |E |A}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_princesajanaina_a]
    Os en|^sinos ^da prin|cesa
    ^Todos |eles ^têm va|lor ^
    \endchorus\glueverses\beginchorus\replay[chords_princesajanaina_b]
    Vamos lou|^var ao ^Pai E|^terno
    E a ^Jesus |^Cristo ^Reden|^tor ^
  \endchorus
  \beginchorus\replay[chords_princesajanaina_a]
    Jesus |^Cristo foi o ^maior |Rei
    Que ^neste |mundo ^habi|tou ^
    \endchorus\glueverses\beginchorus\replay[chords_princesajanaina_b]
    Jesus |^Cristo es^tá em |^mim
    ^Ele |^é meu ^prote|^tor ^
  \endchorus
  \beginchorus\replay[chords_princesajanaina_a]
    Jesus |^Cristo Fi^lho de |Deus \altchords{\id[3]{O (G)}|G |D}
    ^Ele |é bom ^cura|dor ^ \altchords{G |D G | \e}
    \endchorus\glueverses\beginchorus\replay[chords_princesajanaina_b]
    Ele |^cura ^todo |^mundo \altchords{|C Am |G}
    ^Que sou|^ber dar o ^seu va|^lor ^ \altchords{Em |Am7 D |G }
  \endchorus
  \beginchorus\replay[chords_princesajanaina_a]
    Estou a|^qui nes^te sa|lão
    Eu ^vim a|qui para ^me cu|rar ^
    \endchorus\glueverses\beginchorus\replay[chords_princesajanaina_b]
    Peço |^força ao ^Pai E|^terno
    E^le é quem |^tem pa^ra nos |^dar ^
  \endchorus
  \beginchorus\replay[chords_princesajanaina_a]
    A Prin|^cesa ^Jana|ína
    ^Ela |tem to^do pri|mor ^
    \endchorus\glueverses\beginchorus\replay[chords_princesajanaina_b]
    Ela |^ama ao ^Pai E|^terno
    E a ^Jesus |^Cristo ^Salva|^dor ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize \altcol b8 \altmark "5." b8 \posectionmark "A" c8 | d8( d8)( d8) b8 g'4. b,8 | d4. b8 g'4. b,8 | d4( d8) b8 g'4. b,8 | d2~ d8
      }
      \repeat volta 2 {
        \parenthesize \altcol g,8 \altmark "2." g8 \sectionmark "B" g8 | c4( c8) b8 a4. c8 | b4. g8 g4. b8 | d8( d8 d8) c8 a4( a8) b8 | g2~ g8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \skip 1 Je -- sus | Cris -- _ to es -- tá no | céu;
      Es -- tá na | ter -- ra es -- tá no | mar. _
      \set stanza = "1.B"
      \skip 1 A Prin -- | ce -- _ sa Ja -- na -- | í -- na;
      E -- la | vei -- o pa -- ra me en -- si -- | nar.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \skip 1 Os en -- | si -- _ _ nos da prin -- | ce -- sa;
      To -- dos | e -- _ les têm va -- | lor. _
      \set stanza = "2.B"
      Va -- mos lou -- | var __ _ ao Pai E -- | ter -- no;~E~a
      Je -- sus | Cris -- _ _ to Re -- _ den -- | tor. _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \skip 1 Je -- sus Cris -- to foi o mai -- or Rei;
      Que nes -- te mun -- _ do ha -- bi -- tou. _
      \set stanza = "3.B"
      \skip 1 Je -- sus | Cris -- to es -- tá em | mim;
      \skip 1 E -- le | é __ _ _ meu pro -- _ te -- | tor. _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \skip 1 Je -- sus | Cris -- _ to Fi -- lho de | Deus;
      \skip 1 E -- le | é __ _ bom cu -- ra -- | dor. _
      \set stanza = "4.B"
      \skip 1 E -- le | cu -- _ ra to -- do | mun -- do;
      Que sou -- | ber __ _ dar o seu __ _ va -- | lor. _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      Es -- tou a -- | qui __ _ _ nes -- te sa -- | lão;
      Eu vim a -- | qui pa -- ra me cu -- | rar. _
      \set stanza = "5.B"
      \skip 1 Pe -- ço | for -- ça ao Pai E -- | ter -- no;~E --
      le~é quem | tem __ _ _ pa -- ra __ _ nos | dar. _
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \skip 1 A Prin -- | ce -- _ _ sa Ja -- na -- | í -- na;
      E -- la | tem __ _ to -- do pri -- | mor. _
      \set stanza = "6.B"
      \skip 1 E -- la | a -- ma ao Pai E -- | ter -- no;~E~a
      Je -- sus | Cris -- _ _ to Sal -- _ va -- | dor. _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | g1 | g1 | g1 | g2~ g8
      }
      \repeat volta 2 {
        s4. | c2 a2:m | | g2 \parenthesize e2:m | d1 | g2~ g8
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Jesus Christ is in Heaven, is on the earth, is in the sea
    The Princess Janaina, she comes to teach me
    \nextverse
    The teachings of the princess, all of them have value
    Let's praise the Eternal Father and Jesus Christ the Redeemer
    \nextverse
    Jesus Christ was the greatest king that ever lived in this world
    Jesus Christ is within me, he is my protector
    \nextverse
    Jesus Christ, Son of God, he's a good healer
    He cures everyone who know how to value him
    \nextverse
    I am inside this room, I came here to heal myself
    I ask the Eternal Father for strength, it is He who can give it to us
    \nextverse
    The Princess Janaina, it is she who has all perfection
    She loves the Eternal Father and Jesus Christ the Savior
  \end{translation}
\endsong


\beginsong{Quando Tu Estiver Doente}[by={Padr. Sebastião},key={D},sks={D, C, E}]
  \audio{https://www.nossairmandade.com/hymn/68/QuandoTuEstiverDoente}
  \newchords{chords_quandotuestiver_a}\newchords{chords_quandotuestiver_b}
  \mnbeginchorus\memorize[chords_quandotuestiver_a]
    \[^\mn{A}]Quando |\[\mnc{D}D]tu es\[^\mn{B}]ti\[\mnc{E}A7]ver \[^\mn{D}]do|\[D]e\[\bm]nte \altchords{\id[1]{(C)}|C G7 |C}
    Que \[^\mn{E}]o |\[^\mn{F#}]Dai\[^\mn{D}]me \[\mnc{G}A7]for \[^\mn{E}]to|\[\mnc{F#}D]mar \[\bm] \altchords{| - G7 |C}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_quandotuestiver_b]
    \[^\mn{F#}]Te |\[\mnc{G}G]lembran\[^\mn{B}]do \[\bmc\mn{E}]ser \[^\mn{G}]di|\[\mnc{F#}D]vino \altchords{|A |C}
    \[^\mn{A}]Que \[\bmc\mn{D}]tu \[^\mn{F#}]to|\[\mnc{E}A7]mou pa\[^\mn{D}]ra \[\bmc\mn{F#}]te \[^\mn{E}]cu|\[\mnc{D}D]rar \[\bm] \altchords{|G7 |C}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_quandotuestiver_a]
    Te lem|^brando do ^ser di|^v^ino
    O uni|verso es^treme|^ceu ^
    \endchorus\glueverses\beginchorus\replay[chords_quandotuestiver_b]
    A flo|^resta se ^emba|^lou
    ^Porque |^tudo a^qui é |^meu ^
  \endchorus
  \beginchorus\replay[chords_quandotuestiver_a]
    Eu |^já te ^entre|gue^i \altchords{\id[2]{MK (D)}|Bm A7 |D}
    Agora |vou re^ali|^zar ^ \altchords{|Bm A7 |D}
    \endchorus\glueverses\beginchorus\replay[chords_quandotuestiver_b]
    Se fi|^zeres co^mo eu te |^mando \altchords{|Em |Bm}
    ^Nunca |^hás de ^fracas|^sar ^ \altchords{|A7 |D}
  \endchorus
  \beginchorus\replay[chords_quandotuestiver_a]
    Tu |^já vis^te o meu |^br^ilho
    E já |sabes ^quem eu |^sou ^
    \endchorus\glueverses\beginchorus\replay[chords_quandotuestiver_b]
    A|^gora eu ^te con|^vido
    ^Para |^ires a^onde es|^tou ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 4
      \repeat volta 2 {
        a8( \posectionmark "A" a8) | d4( d8) b8 e4. d8 | d2~ d8 d8 d8 e8 | fis4. d8 g4. e8 | fis2.
      }
      \repeat volta 2 {
        fis8( \sectionmark "B" fis8) | g4 g8 b,8 e4. g8 | fis4( fis8) a,8 d4. fis8 | e4( e8) a,8 cis4. e8 | d2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Quan -- do | tu es -- ti -- ver do -- | en -- _ te;
      Que o | Dai -- me for to -- | mar.
      \set stanza = "1.B"
      Te __ _ | lem -- bran -- do ser di -- | vi -- no;
      Que tu to -- | mou pa -- ra te cu -- | rar.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Te lem -- | bran -- do do ser di -- | vi -- _ no;~O
      u -- ni -- | ver -- so~es -- tre -- me -- | ceu.
      \set stanza = "2.B"
      A flo -- | res -- ta se em -- ba -- | lou;  _
      \skip 1 Por -- que | tu -- do a -- qui é | meu.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      Eu __ _ | já __ _ te en -- tre -- | guei; __ _
      A -- go -- ra | vou re -- a -- li -- | zar.
      \set stanza = "3.B"
      Se fi -- | ze -- res co -- mo~eu te | man -- _ do;
      Nun -- ca | hás __ _ de fra -- cas -- | sar.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      Tu __ _ | já __ _ vis -- te~o meu | bri -- _ lho;
      E já | sa -- bes quem eu | sou.
      \set stanza = "4.B"
      A -- _ | go -- ra eu te con -- | vi -- _ do;
      Pa -- ra | i -- res a -- on -- de~es -- | tou.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d2 a2:7 | d1 | d2 a2:7 | d2.
      }
      \repeat volta 2 {
        s4 | g1 | d1 | a1:7 | d2.
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Whenever you are sing and you're going to take the Daime
    Remember the Divine Being that you took to heal yourself
    \nextverse
    Remembering the Divine Being, the universe did shake
    The forest did sway, because everything here is mine
    \nextverse
    I already gave to you, now I'm going to manifest it
    If you do as I tell you, then you will never fail
    \nextverse
    You have seen my brilliance and you know who I am
    Now I invite you to go where I am
  \end{translation}
\endsong


\beginsong{Peço Força}[by={Padr. Sebastião},key={D},sks={D, C, E}]
  \audio{https://www.nossairmandade.com/hymn/69/Pe\%C3\%A7oFor\%C3\%A7a}
  \mnbeginchorus\memorize
    \[^\mn{A}]Peço |\[\mnc{D}D]for\[^\mn{A}]ça\[\bm], \[^\mn{D}]lá vem |\[\mnc{F#}(Bm)]for\[^\mn{D}]ça \[\bm] \altchords{\id[1]{(C)}|C |(Am)}
    Deus \[^\mn{E}]do |\[\mnc{F#}D]céu \[^\mn{A}]foi \[\mnc{E}A]quem \[^\mn{F#}]man|\[\mncii{E}{D}D]dou \[\bm] \altchords{|C G |C}
  \mnendchorus
  \notesoff
  \beginchorus
    Jesus |^Cristo^ está co|^migo ^
    Ele |^é meu ^prote|^tor ^
  \endchorus
  \beginchorus
    Jesus |^Cristo^ está na |^terra ^
    Ele |^é bom ^cura|^dor ^
  \endchorus
  \beginchorus
    Ele |^cura^ quem lhe pro|^cura ^
    Pois Ele |^é o tri^unfa|^dor ^
  \endchorus
  \beginchorus
    Ele |^cura^ quem lhe pro|^cura ^ \altchords{\id[2]{(E)}|E |(C\#m)}
    Conforme |^o seu ^mere|^cer ^ \altchords{|E B |E}
  \endchorus
  \beginchorus
    Que nem |^todos^ estão nas |^graças ^
    Para as |^curas ^rece|^ber ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 4
      \repeat volta 2 {
        a8 \pomark a8 | d4 a4. \altcol\parenthesize d8 \altmark "2. – 6." d8 d8 | fis4 d4.( \altcol\parenthesize d8) \altmark "4. & 5." d8 e8
        | fis4 a4 e4 fis4 | \once\slurSolid e4( d2)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Pe -- ço | for -- ça, \skip 1 lá vem | for -- ça; __ _
      Deus do | céu foi quem man -- | dou. _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2"
      Je -- sus | Cris -- to \altcol es -- tá co -- | mi -- go; __ _
      E -- le | é meu pro -- te -- | tor. _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Je -- sus | Cris -- to \altcol es -- tá na | ter -- ra; __ _
      E -- le | é bom cu -- ra -- | dor. _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      E -- le | cu -- ra \altcol quem lhe pro -- | cu -- ra;
      \altcol Pois E -- le | é~o tri -- un -- fa -- | dor. _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      E -- le | cu -- ra \altcol quem lhe pro -- | cu -- ra;
      \altcol Con -- for -- me | o seu me -- re -- | cer. _
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      Que nem | to -- dos \altcol es -- tão nas | gra -- ças; __ _
      Pa -- ra~as | cu -- ras re -- ce -- | ber. _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d1 | \parenthesize b1:m | d2 a2 | d2.
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I ask for strength, strength comes; God in heaven sent it
    \nextverse
    Jesus Christ is with me, he is my protector
    \nextverse
    Jesus Christ is on the earth, he is a good healer
    \nextverse
    He cures who seeks Him, for He is the triumphant
    \nextverse
    He cures who seeks Him according to their merit
    \nextverse
    For not everyone is in the grace to receive the healings
  \end{translation}
\endsong


\beginsong{Beija-Flor}[by={Padr. Sebastião},key={A},sks={A, G, B}]
  \audio{https://www.nossairmandade.com/hymn/70/Beija-Flor}
  \newchords{chords_beijaflor_a}\newchords{chords_beijaflor_b}
  \mnbeginchorus\memorize[chords_beijaflor_a]
    \[^\mn{C#}]É |\[\mnc{E}A]Bei\[^\mn{C#}]ja é \[\mnc{F#}F#m]Beija-|\[\mncii{D}{B}Bm]Flor \altchords{\id[1]{(G)}|G Em |Am}
    \[\bmc\mn{B}]Que mi|\[\mnc{G#}E]nha \[^\mn{E}]Mãe \[\bmc\mn{F#}]me en\[^\mn{E}]tre|\[\mncii{C#}{A}A]gou\[\bm] \altchords{|D |G}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_beijaflor_b]
    \[^\mn{C#}]Pa\[^\mn{D}]ra a|\[\mnc{E}A]fas\[^\mn{C#}]tar \[\mnc{F#}F#]as do|\[\mnc{D}Bm]en\[^\mn{B}]ças \altchords{|G Em |Am}
    \[\bmc\mn{D}]De \[^\mn{F#}]quem |\[\mnc{E}E]for \[^\mn{D}]me\[\mnc{C#}E7]re\[^\mn{B}]ce|\[\mnc{A}A]dor\[\bm] \altchords{|D D7 |G}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_beijaflor_a]
    Meu |^Mestre es^{tá co}|^migo
    ^Pois e|^le é ^meu a|^mor^
    \endchorus\glueverses\beginchorus\replay[chords_beijaflor_b]
    É |^no céu ^e na |^terra
    ^Jesus |^Cristo ^Salva|^dor^
  \endchorus
  \beginchorus\replay[chords_beijaflor_a]
    Oh |^meu Ju^rami|^dam \altchords{\id[2]{(B)}|B G\#m |C\#m}
    ^Foi E|^le quem ^me man|^dou^ \altchords{|F\# |B}
    \endchorus\glueverses\beginchorus\replay[chords_beijaflor_b]
    Para |^relem^brar lem|^branças \altchords{|B G\#m |C\#m}
    ^Da sal|^vação ^do a|^mor^ \altchords{|F\# F\#7 |B}
  \endchorus
  \beginchorus\replay[chords_beijaflor_a]
    Meu |^Mestre es^tá co|^migo
    ^Mesmo a|^qui a^onde es|^tou^
    \endchorus\glueverses\beginchorus\replay[chords_beijaflor_b]
    É a |^glória ^do meu |^Pai
    ^Jesus |^Cristo ^Reden|^tor^
  \endchorus
  \brk
  \beginchorus\replay[chords_beijaflor_a]
    Eu digo |^tá, eu ^digo |^tá
    Eu ^digo |^tá e a^qui es|^tou^
    \endchorus\glueverses\beginchorus\replay[chords_beijaflor_b]
    Eu não me es|^queço eu ^só me |^lembro
    ^Do meu |^Mestre En^sina|^dor^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative cis'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \altcol \parenthesize cis8 \altmark "5." \posectionmark "A" cis8( cis8)  | e4. cis8 fis4 fis4 | d4( b4) b'4 b4
        | gis4 e4 fis4 e4 | \once\slurSolid cis4( a4.)
      }
      \repeat volta 2 {
        \altcol \parenthesize cis8 \altmark "5."  \once\slurDown cis8( \sectionmark "B" << \parenthesize cis8) d8 >> | e4. cis8 fis4 fis4 | d4.( b8) d4 fis4
        | e4. d8 cis4 b4 | a2~ a8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        \skip 1 É __ _ | Bei -- ja~é Bei -- ja -- | Flor; __ _
        Que mi -- | nha Mãe me~en -- tre -- | gou. _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        \skip 1 Pa -- ra~a -- | fas -- tar as do -- | en -- ças;
        De quem | for me -- re -- ce -- | dor. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        \skip 1 Meu __ _ | Mes -- tre~es -- tá co -- | mi -- go;
        Pois e -- | le é meu a -- | mor. _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 É __ _ | no céu e na | ter -- ra;
        Je -- sus | Cris -- to Sal -- va -- | dor. _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        \skip 1 Oh __ _ | meu Ju -- ra -- mi -- | dam; __ _
        Foi E -- | le quem me man -- | dou. _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 Pa -- ra | re -- lem -- brar lem -- | bran -- ças;
        Da sal -- | va -- ção do a -- | mor. _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        \skip 1 Meu __ _ | Mes -- tre~es -- tá co -- | mi -- go;
        Mes -- mo~a -- | qui a -- on -- de~es -- | tou. _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        \skip 1 É a | gló -- ria do meu | Pai; __ _
        Je -- sus | Cris -- to Re -- den -- | tor. _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        Eu di -- go | tá, eu di -- go | tá;
        Eu di -- go | tá e~a -- qui es -- | tou. _
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Eu não me~es -- | que -- ço~eu só me | lem -- bro;
        Do meu | Mes -- tre~En -- si -- na -- | dor. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a2 fis:m | b1:m | e | a2~a8
      }
      \repeat volta 2 {
        s4. | a2 fis:m | b1:m | e2 e2:7 | a2~a8
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  %\translationoff
  \begin{translation}
    It's the humming-, hummingbird that my Mother gave me
    To remove all the sickness of the ones who are deserving
    \nextverse
    My Master is with me, for He is my love
    It's in heaven and on earth, Jesus Christ the Savior
    \nextverse
    Oh! My Juramidam; it was he who sent me here
    To remember memories of the salvation of love
    \nextverse
    My Master is with me right here where I am
    He's the glory of my Father, Jesus Christ the Redeemer
    \nextverse
    I say yes, I say yes, I say yes and here I am
    I don't forget and only remebr my Master who is the teacher
  \end{translation}
\endsong


\beginsong{Deus É Para Todos}[by={Padr. Sebastião},key={C},sks={D, C, E}]
  \audio{https://www.nossairmandade.com/hymn/71/Deus\%C3\%89ParaTodos}
  \mnbeginchorus\memorize
    \[^\mn{E}]Eu |\[\mnc{G}C]vim pa\[\mnc{A}(F)]ra \[^\mn{G}]lem|\[\mnc{E}C]brar \[\bm] \altchords{\id[1]{(D)}|D (G) |D}
    \[^\mn{C}]Eu |\[\mnc{B}G]te\[^\mn{D}]nho \[\mnc{A}(Am)]que \[^\mn{B}]di|\[\mnc{G}G]zer \[\bm] \altchords{|A (Bm) |A}
    |\[\mnc{C}C]Deus é \[\bm]para |\[\mnc{E}(Am/E)]to\[\bm]dos \altchords{|D |(Bm/F\#)}
    \[^\mn{C}]Não |\[\mnc{B}G]se \[^\mn{D}]po\[\mnc{A}(F)]de es\[^\mn{B}]co|\[\mnc{C}C]lher \[\bm] \altchords{|A (G) |D}
  \mnendchorus
  \notesoff
  \beginchorus
    Do |^que vi^ve o E|^terno
    ^É do |^Vosso ^grande a|^mor
    ^E da |^onde ^vem a |^luz
    ^É do |^nosso ^Salva|^dor ^
  \endchorus
  \beginchorus
    Meu |^Pai e ^minha |^Mãe ^ \altchords{\id[2]{(E)}|E (A) |E}
    |^Todo ^mundo |^vê ^ \altchords{|B (C\#m) |B}
    |^Vêem ^mas não |^sa-^ {bem} \altchords{|E |(C\#m/G\#)}
    |^Ficam ^por sa|^ber ^ \altchords{|B (A) |E}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        e4 \pomark | g g a g | e4.( e8 e4)( c4) | b d a b | g2( g4 g4)
        | c4 c c c | e2( e4) c | b d a b | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu | vim pa -- ra lem -- | brar; __ _ _
        Eu | te -- nho que di -- | zer; __ _ _
        | Deus é pa -- ra | to -- dos;
        Não | se po -- de~es -- co -- | lher.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Do | que vi -- ve~o E -- | ter -- no;
        É do | Vos -- so gran -- de~a -- | mor;
        E da | on -- de vem a | luz;
        É do | nos -- so Sal -- va -- | dor.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Meu | Pai e mi -- nha | Mãe; __ _ _ _
        | To -- do mun -- do | vê; __ _ _
        | Vê -- em mas não | sa -- _ bem;
        | Fi -- cam por sa -- | ber.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 \parenthesize f | c1 | g2 \parenthesize a:m | g1
        | c | \parenthesize a:m/e | g2 \parenthesize f | c2.
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I came to remember; I have to say:
    God is for everyone, this cannot be hidden
    \nextverse
    What sustains the eternal is Your great love
    And from where comes the light, it's from our Savior
    \nextverse
    My Father and my Mother, everyone sees them
    They see but don't know, will remain without knowing
  \end{translation}
\endsong


\beginsong{Eu Invoco Meu Mestre}[by={Padr. Sebastião},key={D},sks={D, E, F}]
  \audio{https://www.nossairmandade.com/hymn/72/EuInvocoMeuMestre}
  \mnbeginchorus\memorize
    \[^\mn{A}]Eu |\[\mnc{D}D]in\[^\mn{F#}]vo\[\mnc{E}A]co o \[^\mn{D}]meu |\[D]Mestre \altchords{\id[1]{(F)}|F C |F}
    \[\bmc\mn{F#}]Quan\[^\mn{A}]do |\[\bmc\mn{D}]me \[^\mn{F#}]a\[\mnc{E}(Bm)]cho \[^\mn{D}]do|\[\mnc{A}A]en\[\bm]te\altchords{| - (Dm) |C}
    \[^\mn{A}]Re|\[\mnc{D}D]cebo a \[^\mn{F#}]mi\[\mnc{E}A]nha \[^\mn{D}]sa|\[D]ú\[^\mn{A}]de\altchords{|F C |F}
    \[\bmc\mn{F#}]É \[^\mn{A}]de |\[\mnc{D}(Bm)]Deus \[^\mn{F#}]O\[\mnc{E}A7]ni\[^\mn{D}]po|\[D]tente\[\bm]\altchords{|(Dm) C7 |F}
  \mnendchorus
  \notesoff
  \beginchorus
    Le|^van\noteson\[\mn{D}]{to a} \[\mn{F#}]mi\notesoff^nha ban|^dei^ra
    Mos|^trando o ^meu va|^lor ^
    An|^dando por ^minha es|^tra^da
    Por |^onde o ^Mestre an|^dou ^
  \endchorus
  \beginchorus
    Quem qui|^ser po^de cor|^rer
    ^Mas eu |^vim tes^temu|^nhar ^
    Me |^chamam de ^menti|^roso
    ^Mas meu |^{Pai e} minha ^Mãe lá es|^tá ^
  \endchorus
  \beginchorus
    Sou |^filho ^da ver|^dade
    ^Mas não |^querem me ^escu|^tar ^
    O |^mun\noteson\[\mnlow{F#}]do \notesoff^de ilu|^são
    ^Como |^{é que} ^vai fi|^car ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 4
      \repeat volta 2 {
        a8( \pomark a8) | d4 << \parenthesize d8 \once\slurUp fis8( >> fis8) e4 d | d4.( d8) fis,4 a | d fis e d | a'2( a4) a,
        | d4 << d8 \once\slurUp \parenthesize fis8( >> fis8) e4 d | d4. \parenthesize a8 fis4 a | d fis e d | d2( d4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu __ _ | in -- vo -- _ co~o meu | Mes -- tre;
        Quan -- do | me a -- cho do -- | en -- te;
        Re -- | ce -- bo~a mi -- nha sa -- | ú -- de;
        É de | Deus O -- ni -- po -- | ten -- te.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Le -- _ | van -- \parenthesize to~a mi -- nha ban -- | dei -- _ ra;
        Mos -- | tran -- do~o meu va -- | lor; __ _
        An -- | dan -- do por mi -- nha~es -- | tra -- \skip 1 da;
        Por | on -- de~o Mes -- tre~an -- | dou. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Quem qui -- | ser po -- _ de cor -- | rer; __ _
        Mas eu | vim tes -- te -- mu -- | nhar; __ _
        Me | cha -- mam de men -- ti -- | ro -- so;
        Mas meu | Pai~e minha Mãe lá~es -- | tá. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Sou __ _ | fi -- lho __ _ da ver -- | da -- de;
        Mas não | que -- rem~me es -- cu -- | tar; __ _
        O | mun -- \parenthesize do __ _ de~i -- lu -- | são; \skip 1
        Co -- mo | é que vai fi -- | car. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d2 a2 | d1 | d2 \parenthesize b2:m | a1
        | d2 a2 | d1 | \parenthesize b2:m a2:7 | d2.
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I invoke my Master when I feel sick
    I receive my health from God omnipotent
    \nextverse
    I lift my flag, showing my worth
    Walking along my path where the Master walked
    \nextverse
    Whoever wants can run, but I came to testify
    They call me a liar, but my Father and Mother are there
    \nextverse
    I am a son of truth, but they don't want to listen to me
    The wolrd of illusion, what's going to happen to it?
  \end{translation}
\endsong


\beginsong{Cuidado no Julgamento}[by={Padr. Sebastião},key={C},sks={D, C--F\#}]
  \audio{https://www.nossairmandade.com/hymn/73/CuidadoNoJulgamento}
  \newchords{chords_cuidadonoj_a}\newchords{chords_cuidadonoj_b}
  \mnbeginchorus\memorize[chords_cuidadonoj_a]
    \[^\mn{G}]Eu |\[\mnc{C}C]chamo os \[\mnc{A}Am7]meus \[^\mn{C}]ir|\[\mnc{G}G7]mã\[\bm]os \altchords{\id[1]{(D)}|D Bm7 |A7}
    |\[^\mn{B}]Para \[^\mn{D}]jus\[\mnc{A}F]ti\[^\mn{C}]fi|\[C]car \[\bm] \altchords{| - G |D}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_cuidadonoj_b]
    \[^\mn{C}]Cui|\[\mnc{F}F]dado \[^\mn{E}]no \[\mnc{D}G7]jul\[^\mn{E}]ga|\[\mnc{C}C]mento \altchords{|G A7 |D}
    Pa\[^\mn{B}]ra \[\mnc{A}Am]ser \[^\mn{C}]jul|\[\mnc{G}G7]gado e \[^\mn{B}]fi\[^\mn{D}]car (em) \[\bmc\mn{A}]seu \[^\mn{C}]lu|\[C]gar \[\bm] \altchords{Bm |A7 |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_cuidadonoj_a]
    Não |^fale de ^coisas |^sé^rias \altchords{\id[2]{(E)}|E C\#m7 |B7}
    Não |sejas blas^fema|^dor ^ \altchords{| - A |E}
    \endchorus\glueverses\beginchorus\replay[chords_cuidadonoj_b]
    Di|^zendo que es^tão com |^Cristo \altchords{|A B7 |E}
    ^Estão |^longe do ^Salva|^dor ^ \altchords{C\#m |B7 |E}
  \endchorus
  \beginchorus\replay[chords_cuidadonoj_a]
    |^Eu a^mo a meu |^Pai
    A|qui eu ^vou cha|^mar ^
    \endchorus\glueverses\beginchorus\replay[chords_cuidadonoj_b]
    Quem  |^ama ^coisa à-|^toa
    Peran^te a ver|^dade vem se en^vergo|^nhar ^
  \endchorus
  \beginchorus\replay[chords_cuidadonoj_a]
    Não |^quero mal ^a nin|^guém^
    A |todos eu ^tenho a|^mor ^
    \endchorus\glueverses\beginchorus\replay[chords_cuidadonoj_b]
    Eu |^amo a ^Jesus |^Cristo
    O ^nosso |^Mestre Im^pera|^dor ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g4\posectionmark "A" | c c8( c8) a4 c | g2( g4) \altcol\parenthesize c4 \altmark "2., 3., 4."
        | b4 \once\slurDown b8( << \parenthesize b8) \altmark "(3.)" d8 >> a4 c4 | c2.
      } \break
      \repeat volta 2 {
        c4\sectionmark "B" | f8( f8) \parenthesize f8 e8 d4 e4 | c8( c c) b a4 c4
        | g8( g) b d a4 c4 | c2.
      } \break
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu | cha -- mo os meus ir -- | mã -- os;
        \skip 1 | Pa -- ra jus -- ti -- fi -- | car.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Cui -- | da -- _ do no jul -- ga -- | men -- to;
        Pa -- ra ser jul -- | ga -- do~e fi -- car~em seu lu -- | gar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Não | fa -- le de coi -- sas | sé -- rias;
        Não | se -- jas blas -- fe -- ma -- | dor.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Di -- | zen -- do que es -- tão com | Cris -- _ _ to;
        Es -- tão | lon -- _ ge do Sal -- va -- | dor.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        \skip 1 | Eu a -- _ mo~a meu | Pai; __ _
        A -- | qui eu __ _ vou cha -- | mar.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Quem  | a -- _ _ ma coi -- sa~à -- | to -- a;
        Pe -- ran -- te~a ver -- | da -- de vem se~en -- ver -- go -- | nhar.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Não | que -- ro mal a nin -- | guém; __ _
        A | to -- dos eu te -- nho~a -- | mor.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Eu | a -- _ mo a Je -- sus | Cris -- _ _ to;~O
        nos -- so | Mes -- _ tre Im -- pe -- ra -- | dor.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 a2:m7 | g1:7 | g2:7 f2: | c2.
      }
      \repeat volta 2 {
        s4 | f2 g2:7 | c2 a2:m | g1:7 | c2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I call my brothers and sisters to justify
    Be careful in the judgement, to be judged and remain in your place
    \nextverse
    Don't talk about serious things, don't be a blasphemer
    Saying that you're with Christ, you're far from the Savior
    \nextverse
    I love my Father, here I'm going to call
    He who loves worthless things before the truth is going to feel ashamed
    \nextverse
    I don't wish harm to anyone, for everyone I have love
    I love Jesus Christ, our Master the Emperor
  \end{translation}
\endsong


\beginsong{Sou Luz}[by={Padr. Sebastião}, key={C}, sks={D, C--E}, tags={de pé}]
  \audio{https://www.nossairmandade.com/hymn/74/SouLuz}
  \newchords{chords_souluz_a}\newchords{chords_souluz_b}
  \mnbeginchorus\memorize[chords_souluz_a]
    \[^\mn{E}]Sou |\[\mnc{G}C]Luz\[\bm], \[^\mn{E}]dou |\[\mncii{D}{C}Am]Luz\[\bm] \altchords{\id[1]{(D)}|D |Bm}
    \[^\mn{A}]E \[^\mn{B}]fa\[^\mn{C}]ço |\[\mnc{D}Dm]tudo i\[\mnc{G}G7]lu\[^\mn{E}]mi|\[\mncii{D}{C}C]nar\[\bm] \altchords{|Em A7 |D}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_souluz_b]
    \[^\mn{C}]Vejo |\[\mnc{E}Am]meu \[^\mn{C}]Pai \[\bm]nas \[^\mn{B}]al|\[\mnc{G}G]tu\[\bm]ras \altchords{|Bm |A}
    \[^\mn{D}]E o Po|\[Dm]der a\[\mnc{G}G7]on\[^\mn{E}]de es|\[\mncii{D}{C}C]tá\[\bm] \altchords{|Em A7 |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_souluz_a]
    \ind A |^for^ça está co|^migo^
    \ind Falo |^peran^te o Po|^der^
    \endchorus\glueverses\beginchorus\replay[chords_souluz_b]
    \ind Fa|^{ço o} que ^Tu me |^pe^des
    \ind Eu quero |^ver es^treme|^cer^
  \endchorus
  \beginchorus\replay[chords_souluz_a]
    O a|^mor^ e|^terno^ \altchords{\id[2]{simple (C)}|C | \e}
    Gra|^vei no ^cora|^ção^ \altchords{|G |C}
    \endchorus\glueverses\beginchorus\replay[chords_souluz_b]
    De Vós eu |^rece^bo os en|^si^nos \altchords{|C |G \e}
    Para explan|^dir para os ^meus ir|^mãos^ \altchords{| - |C}
  \endchorus
  \beginchorus\replay[chords_souluz_a]
    \ind As|^sim ^é que meu Pai |^quer^
    \ind Pe|^rante es^te Po|^der^
    \endchorus\glueverses\beginchorus\replay[chords_souluz_b]
    \ind Não |^fazem o que ^Ele |^pe^de
    \ind E todos |^querem ^mere|^cer^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        r8\sectionmark "1. & 3." e8( e8) | g2. e4 | d4( c4.)
        \parenthesize a8 b8( c8) | d4( d8) d8 g4. e8 | \once\slurSolid d4( c4.)
      } \break
      \repeat volta 2 {
        \parenthesize c8 c8 c8 | e4 c4 c4 b4 | g2 g8
        d'16( d16) d8 d8 | d4( d8) d8 g4. e8 | d4( c4.)
      } \break
      \repeat volta 2 {
        r8\posectionmark "2. & 4." e4 | g2( g8) e8 f8 e8 | d4( c2)
        b8( c8) | d4. d8 g4. e8 | \once\slurSolid d4( c4.)
      } \break
      \repeat volta 2 {
        r8 c4 | e4 c8( c8) c4 b4 | g2 g8
        d'8 d8 d8 | d4. d8 g4. e8 | \once\slurSolid d4( c4.)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Sou _ | Luz, dou | Luz; __ _
        E fa -- ço | tu -- do i -- lu -- mi -- | nar. _
      \set stanza = "1.B"
        \skip 1 Ve -- jo | meu Pai nas al -- | tu -- ras;
        E __ _ o Po -- | der __ _ a -- on -- de~es -- | tá. __ _
      \set stanza = "2.A"
        A | for -- _ ça~es -- tá co -- | mi -- go;
        Fa -- lo | pe -- ran -- te~o Po -- | der. _
      \set stanza = "2.B"
        Fa -- | ço~o que __ _ Tu me | pe -- des;
        Eu que -- ro | ver es -- tre -- me -- | cer. _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "3.A"
        O a -- | mor e -- | ter -- no; \skip 1
        Gra -- _ | vei __ _ no co -- ra -- | ção. _
      \set stanza = "3.B"
        De Vós eu | re -- ce -- bo~os en -- | si -- nos;
        Pa -- ra ex -- plan -- | dir pa -- ra~os meus ir -- | mã -- os.
      \set stanza = "4.A"
        As -- | sim é que meu Pai | quer; __ _
        Pe -- _ | ran -- te~es -- te Po -- | der. _
      \set stanza = "4.B"
        Não | fa -- zem~o que E -- le | pe -- de;
        E to -- dos | que -- rem me -- re -- | cer.
    }
    verseChords = \chordmode {
      \set chordChanges = ##f % this is needed 'cos verses paired
      \repeat volta 2 {
        s4. | c1 | a:m | d2:m g2:7 | \set chordChanges = ##t c2~8
      }
      \repeat volta 2 {
        s4. | a1:m | g | d2:m g2:7 | \set chordChanges = ##t c2~8
      }
    }
    theChords = { \verseChords \verseChords }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I am Light, I give Light, and illuminate everything
    I see my Father in the Heights, and the power where it is
    \nextverse
    The force is with me, I speak in the presence of the power
    I do whatever You ask of me, I want to see everything shake
    \nextverse
    The eternal love I inscribed upon my heart
    From You I receive the teachings to spread to my brothers and sisters
    \nextverse
    This is how my Father wants it, in the presence of this power
    They don't do what He asks, yet they all want to deserve
  \end{translation}
\endsong


\beginsong{Tão Bonito é meu Pai}[by={Padr. Sebastião}, key={G}, sks={A, G--B}]
  \audio{https://www.nossairmandade.com/hymn/75/T\%C3\%A3oBonito\%C3\%89MeuPai}
  \newchords{chords_taobonitoemeupai_a}\newchords{chords_taobonitoemeupai_b}
  \mnbeginchorus\memorize[chords_taobonitoemeupai_a]
    \[^\mn{G}]Tão bo|\[\mnc{B}G]ni\[^\mn{G}]to \[(Em)]é \[^\mn{B}]meu |\[\mnc{D}D]Pai\[\bm] \altchords{\id[1]{(A)}|A (F\#m) |E}
    \[^\mn{G}]É \[^\mn{F#}]meu |\[\mnc{E}Em]Mes\[^\mn{D}]tre en\[\mncii{B}{G}G]si\[^\mn{B}]na|\[\mnc{D}D]dor\[\bm] \altchords{|F\#m A |E}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_taobonitoemeupai_b]
    \[^\mn{G}]Va\[^\mn{F#}]mos |\[\mnc{E}Em]re\[^\mn{D}]ce\[\mncii{B}{G}G]ber \[^\mn{B}]a |\[\mnc{D}D]gló\[\bm]ria \altchords{|F\#m A |E}
    \[^\mn{G}]Do nosso |\[\mnc{B}Bm]Mes\[^\mn{G}]tre \[\mnc{A}D]cu\[^\mn{B}]ra|\[\mnc{G}G]dor\[\bm] \altchords{|C\#m E |A}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_taobonitoemeupai_a]
    A |^força ^do meu |^Pai^
    Quem du|^vida é o ^peca|^dor^
    \endchorus\glueverses\beginchorus\replay[chords_taobonitoemeupai_b]
    Não se |^lembram do ^que fi|^ze^ram
    Assassi|^naram o ^Salva|^dor^
  \endchorus
  \beginchorus\replay[chords_taobonitoemeupai_a]
    Le|^varam Ele ^para a |^fren^te \altchords{\id[3]{simple (G)}|G |D}
    Sem ter |^dó, sem ^ter a|^mor^ \altchords{|G |D}
    \endchorus\glueverses\beginchorus\replay[chords_taobonitoemeupai_b]
    Procu|^rando os ^seus dis|^cípu^los \altchords{|G |D}
    E Todos |^se a^fugen|^tou^ \altchords{|G D |G}
  \endchorus
  \beginchorus\replay[chords_taobonitoemeupai_a]
    A|^qui eu ^vim lem|^brar^
    Tudo o |^que já ^se pas|^sou^
    \endchorus\glueverses\beginchorus\replay[chords_taobonitoemeupai_b]
    Peço |^que nin^guém se es|^que^ça
    Do nosso |^Mestre ^zela|^dor^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8( \posectionmark "A" g8) | b8( b8) g8( g8) g4 b4 | d2( d4)
        g8 fis8 | e4 d8( d8) \once\slurSolid b8( g8) b4 | d2.
      } \break
      \repeat volta 2 {
        g8 \sectionmark "B" fis8 | e4 d8( d8) \once\slurSolid b8( g8) b4 | d4.(d8) d8
        g,8 g8 g8 | b4 g4 a4 b4 | g2.
      } \break

    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Tão bo -- | ni -- _ to __ _ é meu | Pai; __ _
        É meu | Mes -- tre en -- si -- _ na -- | dor.
      \set stanza = "1.B"
        Va -- mos | re -- ce -- _ ber __ _ a | gló -- _ ria;
        Do nos -- so | Mes -- tre cu -- ra -- | dor.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
        A __ _ | for -- _ ça __ _ do meu | Pai; __ _
        Quem du -- | vi -- da é~o pe -- _ ca -- | dor.
      \set stanza = "2.B"
        Não se | lem -- bram do que __ _ fi -- | ze -- _ ram;
        As -- sas -- si -- | na -- ram~o Sal -- va -- | dor.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
        Le -- _ | va -- ram E -- le pa -- ra~a | fren -- te;
        Sem ter | dó, sem __ _ ter __ _ a -- | mor.
      \set stanza = "3.B"
        Pro -- cu -- | ran -- do os seus __ _ dis -- | cí -- pu -- los;
        E To -- dos | se a -- fu -- gen -- | tou.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
        A -- _  | qui __ _ eu __ _ vim lem -- | brar; __ _
        Tu -- do~o | que já __ _ se __ _ pas -- | sou.
      \set stanza = "4.B"
        Pe -- ço | que nin -- _ guém __ _ se~es -- | que -- _ ça;
        Do nos -- so | Mes -- tre ze -- la -- | dor.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | g2 \parenthesize e2:m | d1
        | e2:m g2 | d2.
      }
      \repeat volta 2 {
        s4 | e2:m g2 | d1
        | b2:m d2 | g2.
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    How beautiful is my Father, he is my Master teacher
    Let us all receive the glory of our Master, the healer
    \nextverse
    The force of my Father, who doubts it is a sinner
    They don't remember what they did, they killed the Savior
    \nextverse
    They took Him to the front without pity, without love
    Seeking his disciples, and all of them fled
    \nextverse
    Here I came to remember everything that already happened
    I ask that no one forget our Master who cares for us
  \end{translation}
\endsong






