% Santo Daime: Hinos do Daime
% ===========================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Aqui eu Recebi}[by={Padr. Sebastião},key={A},gk={A, G--B--(C)}]
  \audio[key=C]{https://www.nossairmandade.com/hymn/35/AquiEuRecebi}
  \transpose{-3}
  \mnbeginchorus\memorize
    \[^\mn{G}]A|\[\mnc{E}C]qui eu \[\mncii{D}{C}(G7)]rece|\[\mnc{G}C]bi\[\bm], \[^\mn{E}]pa\[^\mn{G}]ra |\[^\mn{E}]mim dis\[\mnc{D}C7]tri\[^\mn{C}]bu|\[\mnc{A}F]ir \[\bm] \altchords{\id[1]{(C)}|C (G7) |C | - |F}
    |\[^\mn{A}]É \[^\mn{B}]o \[\bmc\mn{C}]San\[^\mn{A}]to |\[\mnc{G}C]Daime, \[\bmc\mn{E}]pa\[^\mn{C}]ra |\[^\mn{E}]com meu \[\mnc{D}G7]Pai se|\[\mnc{C}C]guir\[\bm] \altchords{| - |C | - G7 |C}
  \mnendchorus
  \notesoff
  \beginchorus
    Se |^meus ir^mãos sou|^bes^sem, o que |é que ^vem fa|^zer ^
    Sa|íam ^bem lim|^pinhos, ^pois o |meu Pai ^tem po|^der ^
  \endchorus
  \beginchorus
    Es|^te é ^{o po}|^der^, es|ta é ^{a ver}|^da^de
    Quem não |ama ^com fir|^meza, ^sempre |carre^{ga a} mal|^da^de
  \endchorus
  \beginchorus
    Eu |^gosto ^{de di}|^zer^, também |gosto ^de mos|^trar ^
    \noteson |\[\mnlow{A}]Tá\[\bm] \[\mnlow{F}] |\[C\mnlow{E}]tum\[\bm], |veja aon\[G7]de es|\[C]tá \notesoff
  \endchorus
  \notesoff
  \beginchorus
    Quem não |^souber ^{o que} |^é,^ puxe |pela ^consci|^ên^cia
    Quem |ama com ^leal|^dade, ^sempre |rende o^bedi|^ên^cia
  \endchorus
  \begin{translation}\footnotesize % to fit
    Here I received, for me to distribute
    It's the Holy Daime, for me to follow with my Father
    \nextverse
    If my brothers and sisters knew what they are coming to do
    They would leave well cleansed, because my Father has power
    \nextverse
    This is the power, this is the truth
    Who doesn't love with firmness always carries wickedness
    \nextverse
    I like to say and also like to show
    Tá\ldots tum, Behold it where it is
    \nextverse
    Whoever doesn't know what it is, pull on your conscience
    Whoever loves with loyalty always renders obedience
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose c' a \relative c''' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \mark \markup {"6x"} \bar ".|:" \repeat volta 6 {
        g4\sectionmark "1.-3." | e4 e d c | g'2( g4) e8 g8 | e4 e d c | a'2( a4 a8 a8)
        | a4 b c a | g4. g8 e4 c4 | e e d d | c2( c4)
      }
      \slurSolid
      \repeat volta 2 {
        g'4\sectionmark "4." | e4 e d c | g'2. e8 g8 | e4 e d c | a'1
        | a2.( f4) | e1  | e4 e d d | c2.
      }
      \repeat volta 2 {
        g'8\posectionmark "5." g8 | e4 e d c | g'2. e8 g8 | e4 e d c | a'2 a4 a4
        | a4 b8 b8 c4 a | g4. g8 e4 c4 | e e d d | c2 c4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      A -- | qui eu re -- ce -- | bi __ _
      pa -- ra | mim dis -- tri -- bu -- | ir; __ _ _ _
      É o San -- to | Dai -- me
      pa -- ra | com meu Pai se -- | guir. __ _
      \set stanza = "4."
      Eu | gos -- to de di -- | zer
      tam -- bém | gos -- to de mos -- | trar;
      | Tá _ | tum
      | ve -- ja~a -- on -- de~es -- | tá.
      \set stanza = "5."
      Quem não | sou -- ber o que | é
      pu -- xe | pe -- la cons -- ci -- | ên -- cia; Quem
      | a -- ma com -- le -- al -- | da -- de
      Sem -- pre | ren -- de~o -- be -- di -- | ên -- cia.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Se | meus ir -- mãos sou -- | bes -- sem
      O que | é que vem fa -- | zer __ _ Sa -- _
      | í -- am bem lim -- | pi -- nhos
      Pois o | meu Pai tem po -- | der. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Es -- | te é o po -- | der __ _
      Es -- _ | ta é a ver -- | da -- de Quem não
      | a -- ma com fir -- | me -- za
      Sem -- pre | car -- re -- ga~a mal -- | da -- de.
    }
    theChords = \transpose c' a \chordmode {
      \repeat volta 6 {
        s4 | c2 \parenthesize g:7 | c1
        | c2 \parenthesize c:7 | f1
        | f | c
        | c2 g:7 | c2.
      }
      \repeat volta 2 {
        s4 | c2 \parenthesize g:7 | c1
        | c2 \parenthesize c:7 | f1
        | f | c
        | c2 g:7 | c2.
      }
      \repeat volta 2 {
        s4 | c2 \parenthesize g:7 | c1
        | c2 \parenthesize c:7 | f1
        | f | c
        | c2 g:7 | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{O Daime, é o Daime}[by={Padr. Alfredo}, off={José Teixeira}, tags={mazurka}, key={C}, gk={C, (B)--(C)}]
  % Also in Cura II
  \audio{https://www.nossairmandade.com/hymn/536/ODaime\%C3\%89ODaime}
  \newchords{chords_odaime_a}\newchords{chords_odaime_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_odaime_a]
    \[^\mn{E}]O |\[\mnc{G}C]Daime \[^\mn{E}]é \[^\mn{F}]o \[\bmc\mn{G}]Daime
    Eu |\[^\mn{C}]es\[^\mn{G}]tou \[^\mn{E}\mn{G}]afir\[(G)]mando
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_odaime_b]
    \[^\mn{C}]É o Di|\[C]vi\[^\mn{G}]no \[^\mn{C}]Pai \[^\mn{E}]E\[(Am/E)]terno
    \[^\mn{C}]E a Ra|\[G]in\[^\mn{G}]ha \[^\mn{B}]So\[^\mn{D}]be\[\mnc{C}C]rana
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_odaime_a]
    O |^Daime é o ^Daime
    O profes|sor dos profes^sores
  \endchorus\glueverses\beginchorus\replay[chords_odaime_b]
    É o Di|^vino Pai E^terno
    E seu |^Filho Reden^tor
  \endchorus
  \beginchorus\replay[chords_odaime_a]
    O |^Daime é o ^Daime
    O Mestre |de todos en^sinos
  \endchorus\glueverses\beginchorus\replay[chords_odaime_b]
    É o Di|^vino Pai E^terno
    E to|^dos seres di^vinos
  \endchorus
  \beginchorus\replay[chords_odaime_a]
    O |^Daime é o ^Daime
    Eu agra|deço com a^mor
  \endchorus\glueverses\beginchorus\replay[chords_odaime_b]
    É quem me |^dá a minha sa^úde
    E revi|^gora o meu a^mor
  \endchorus\brk
  \beginchorus\replay[chords_odaime_a]
    Agra|^deço ao Santo ^Daime
    Agrade|cendo a todos ^seres
  \endchorus\glueverses\beginchorus\replay[chords_odaime_b]
    E quem me |^manda agrade^cer
    É o |^meu Pai verda^deiro
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 6/4 \partial 4.
      \repeat volta 2 {
        r8\posectionmark "A" e4 | g g e8 f8 g4 g8( g) g( g) | c4 g e8 g8 g4 g8
      }
      \repeat volta 2 {
        c,8\sectionmark "B" c c | c4 g c8 e8 e4 e8 c c c | c4 g4 b8 d8 c4( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      O | Dai -- me é o Dai -- me; __ _
      Eu __ _ | es -- tou a -- fir -- man -- do;
      \set stanza = "1.B"
      É o Di -- | vi -- no Pai E -- ter -- no;
      E a Ra -- | i -- nha So -- be -- ra -- na.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
        O | Dai -- me é o Dai -- me;
        O pro -- fes -- | sor dos pro -- fes -- so -- res;
        \set stanza = "2.B"
        É o Di -- | vi -- no Pai E -- ter -- no; __ _
        E seu | Fi -- lho Re -- den -- tor. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      O | Dai -- me é o Dai -- me;
      O Mes -- tre | de to -- dos en -- si -- nos;
      \set stanza = "3.B"
      É o Di -- | vi -- no Pai E -- ter -- no; __ _
      E to -- | dos se -- res di -- vi -- nos.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      O | Dai -- me é o Dai -- me;
      Eu a -- gra -- | de -- ço com a -- mor; __ _
      \set stanza = "4.B"
      É quem me | dá a~mi -- nha sa -- ú -- de;
      E re -- vi -- | go -- ra~o meu a -- mor. __ _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      Agra | de -- ço~ao San -- to Dai -- me;
      A -- gra -- de -- | cen -- do~a to -- dos se -- res;
      \set stanza = "5.B"
      E quem me | man -- da~a -- gra -- de -- cer; __ _
      \skip 1 É o | meu Pai ver -- da -- dei -- ro.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2. c | c \parenthesize g4~ g8
      }
      \repeat volta 2 {
        s4. | c2. \parenthesize a:m/e | g c4~ c8
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    The Daime is the Daime, I am affirming
    It is the divine Eternal Father, and the Sovereign Queen
    \nextverse
    The Daime is the Daime, the Teacher of all teachers
    It is the Divine Eternal Father, and his son the redeemer
    \nextverse
    The Daime is the Daime, the master of all teachings
    It is the Divine Eternal Father, and all Divine Beings
    \nextverse
    The Daime is the Daime, I thank with love
    It is he who gives my health, and renews my faith
    \nextverse
    I thank the holy Daime, thanking all beings
    And who orders me to give thanks, is my truthful Father
  \end{translation}
\endsong


\beginsong{Graças a Deus}[by={Madr. Maria Brilhante},key={G},gk={A, G--A}]
  \audio{https://www.nossairmandade.com/hymn/28/Gra\%C3\%A7asADeus}
  \newchords{chords_gracasadeus_a}\newchords{chords_gracasadeus_b}
  \mnbeginchorus\memorize[chords_gracasadeus_a]
    \[^\mn{D}]Graças \[^\mn{E}]a |\[\mnc{D}D]Deus aon\[^\mn{E}]de \[\mnc{D}(D7)]eu \[^\mn{C}]es\[^\mn{B}]tou \[^\mn{A}]tem |\[\mnc{G}G]Dai\[\bm]me \altchords{\id[1]{(A)}|E (E7) |A}
    Gra\[^\mn{B}]ças \[^\mn{D}]a |\[\mnc{G}Em]Deus Dai\[^\mn{F#}]me \[\mnc{A}(Am7)]nun\[^\mn{G}]ca \[^\mn{F#}]me \[^\mn{E}]fal|\[\mnc{D}D]tou\[\bm] \altchords{|F\shrp{}m (Bm7) |E}
  \mnendchorus
  \mnbeginchorus\memorize[chords_gracasadeus_b]
    \ind \[^\mn{/}]Sou \[^\mn{B}]u\[^\mn{D}]ma |\[\mnc{G}G]árvore ro\[^\mn{F#}]si\[\mnc{A}Am7]an\[^\mn{G}]te em \[^\mn{F#}]u\[^\mn{E}]ma |\[\mnc{D}D]flor\[\bm] \altchords{|A Bm7 |E}
    \ind Graças \[^\mn{E}]a |\[^\mn{D}]Deus aon\[^\mn{E}]de o \[\mnc{D}D7]Dai\[^\mn{C}]me es\[^\mn{B}]tá \[^\mn{A}]es|\[\mnc{G}G]tou\[\bm] \altchords{| - E7 |A}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_gracasadeus_a]
    \[\mnlow{/}]Louvar \[\mnlow{/}]a |^Deus e \[\mnlow{/}]a^\[\mnlow{/}]mar \[\mnlow{/}]com \[\mnlow{/}]to\[\mnlow{D}]do a|^mor^
    São João Ba|^tista é o ^nosso Prote|^tor^
  \endchorus
  \beginchorus\replay[chords_gracasadeus_b]
    \ind São João Ba|^tista e a sem^{pre Virgem} Ma|^ri^a
    \ind É quem nos |guia neste ^caminho com a|^mor^
  \endchorus
  \begin{translation}
    Thanks to God, where I am I have Daime
    Thanks to God, the Daime has never failed me
    \nextverse
    I am a tree shining in a Flower
    Thanks to God I am where the Daime is
    \nextverse
    To praise God and love with all love
    Saint John the Baptist is our protector
    \nextverse
    Saint John the Baptist and the Ever Virgin Mary
    Are who Guide us in this path with love
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \key g \major \time 4/4 \partial 4.
      d8\sectionmark "1." d e
      \repeat volta 2 {
        | d d d e d c b a | g2 g8 g b d | g4 g8 fis a g fis e
      } \alternative {
        { | d2~ d8 d d e }
        { | d2~ d8 b\sectionmark "2." b d }
      }
      \repeat volta 2 {
        g8 g16 g16 g8 fis a g fis e | d2~ d8 d d e | d d d e d c b a
      } \alternative {
        { | g2~ g8 g b d }
        { | g,2~ g8\posectionmark "3." g g b | d4 d8 d b b a a }
      }
      \repeat volta 2 {
        | g2~ g8 g b d | g g g fis a g fis e
      } \alternative {
        { | d2~ d8 d d e | d4 d8 e d c b a }
        { | d2~ d8 b\sectionmark "4." b d }
      }
      \repeat volta 2 {
        | g8 g g fis a g fis e | d2 d8 d d e | d d d e d c16 c16 b8 a
      } \alternative {
        { | g2~ g8 g b d }
        { | g,2~ g8 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Gra -- ças a
      \repeat volta 2 {
        | Deus a -- on -- de eu es -- tou tem | Dai -- me
        Gra -- ças a | Deus
        Dai -- me nun -- ca me fal --
      } \alternative {
        { | tou. Gra -- ças a }
        { | tou. \set stanza = "2." Sou u -- ma }
      }
      \repeat volta 2 {
        | ár -- vo -- re
        Ro -- si -- an -- te~em u -- ma | flor
        Gra -- ças a | Deus
        A -- on -- de~o Dai -- me~es -- tá es -- 
      } \alternative {
        { | tou. Sou u -- ma }
        { | tou. \set stanza = "3." Lou -- var a | Deus e a -- mar com to -- do~a -- }
      }
      \repeat volta 2 {
         | mor
        São João Ba -- | tis -- ta
        É o nos -- so Pro -- te -- 
      } \alternative {
        { | tor. Lou -- var a | Deus e a -- mar com to -- do~a -- }
        { | tor. \set stanza = "4." São João Ba -- }
      }
      \repeat volta 2 {
        | tis -- ta
        E~a sem -- pre Vir -- gem Ma -- | ri -- a
        É quem nos | gui -- a
        Nes -- te ca -- mi -- nho com a --
      } \alternative {
        { | mor. São João Ba -- }
        { | mor. }
      }
    }
    theChords = \chordmode {
      s4.
      \repeat volta 2 {
        | d2 \parenthesize d:7 | g1 | e2:m \parenthesize a:m7 
      } \alternative {
        { | d1  }
        { | d1 }
      }
      \repeat volta 2 {
        | g2 a:m7 | d1 | d2 d:7
      } \alternative {
        { | g1 }
        { | g1 | d2 d:7 }
      }
      \repeat volta 2 {
        | g1 | e2:m \parenthesize a:m7
      } \alternative {
        { | d1 | d2 d:7 }
        { | d1 }
      }
      \repeat volta 2 {
        | g2 a:m7 | d1 | d2 d:7
      } \alternative {
        { | g1 }
        { | g2~ g8 }
      }
    }
    \layout { #(layout-set-staff-size 13) } % to fit on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Tomo Daime}[by={Tetéo}, key={C}, gk={D, B\flt{}--F\shrp{}}]
  \audio[key=D]{https://www.nossairmandade.com/hymn/1065/TomoDaime}
  \newchords{chords_tomodaime_a}\newchords{chords_tomodaime_b}
  \mnbeginchorus\memorize[chords_tomodaime_a]
    \[^\mn{/}]Eu |\[\mnc{C}C]tomo \[\bm]Dai\[^\mn{A}]me eu |\[^\mn{C}]tomo \[\bm]Daime \altchords{\id[1]{D}|D | \e}
    |\[\mnc{E}Am]Não tenho \[\bm]me\[^\mn{D}]do |\[\mnc{F}F]de \[^\mn{D}]to\[\bmc\mnc{B}G]mar \altchords{|Bm |G A}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_tomodaime_b]
    |\[\mnc{E}C]Eu es\[\bm]tan\[^\mn{D}]do |\[\mnc{F}F]com \[^\mn{D}]meu \[\mnc{B}G]Mestre \altchords{|D |G A}
    |\[\mnc{A}Am]Ne\[^\mn{C}]le eu \[\bm]pos\[^\mn{A}]so |\[\mnc{C}C]me fir\[\bm]mar \altchords{|Bm |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_tomodaime_a]
    Eu |^tomo ^Daime eu |tomo ^Daime
    |^Tomo ^para |^via^jar
  \endchorus\glueverses\beginchorus\replay[chords_tomodaime_b]
    |^Ouvir ^muito e |^falar ^pouco
    |^Pra co^nhecer |^meus ca^boclos
  \endchorus
  \beginchorus\replay[chords_tomodaime_a]
    Eu |^tomo ^Daime eu |tomo ^Daime \altchords{\id[2]{MK (C/Am)}|Am | \e}
    |^Porque ^acho |^bom to^mar \altchords{|C |Dm E}
  \endchorus\glueverses\beginchorus\replay[chords_tomodaime_b]
    Não |^exis^te na|^da di^fícil \altchords{|Am |Dm E}
    |^Se com o ^Mestre |^se fir^mar \altchords{|Am | \e}
  \endchorus
  \beginchorus\replay[chords_tomodaime_a]
    |^Eu a^qui vou |via^jando
    |^Por a^qui tenho |^que se^guir
  \endchorus\glueverses\beginchorus\replay[chords_tomodaime_b]
    Es|^tou con^vidan|^do sor^rindo
    E |^comi^go nin|^guém quer ^ir \tonextsongmark
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 8
      a8\posectionmark "A"
      \repeat volta 2 {
        | c4 c c4. a8 | c4 c c4. c8
        | e4 e8( e8) e4 d8( d8)
      } \alternative {
        { | f4 d4 b4. \parenthesize b8 }
        { | f'4 d4 b4. \parenthesize b8 \sectionmark "B" }
      }
      \repeat volta 2 {
        | e4 e e d | f d b4. b8
        | a4 c c a
      } \alternative {
        { | c4 c c4. \parenthesize c8 }
        { | c4 c c4. \parenthesize a8 }
      }
      \bar "|."
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Eu
      \repeat volta 2 {
        | to -- mo Dai -- me~eu | to -- mo Dai -- me;
        | Não te -- nho me -- do __ _
      } \alternative {
        { | de to -- mar. Eu}
        { | de to -- mar. \skip 1 }
      }
      \repeat volta 2 {
        \set stanza = "1.B"
        | Eu es -- tan -- do | com meu Mes -- tre;
        | Ne -- le~eu pos -- so
      } \alternative {
        { | me fir -- mar. \skip 1  }
        { | me fir -- mar. \set stanza = "2." Eu }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \skip 1
      \repeat volta 2 {
        | to -- mo Dai -- me~eu | to -- mo Dai -- me;
        | To -- mo __ _ pa -- ra __ _
      } \alternative {
        { | vi -- a -- jar. Eu }
        { | vi -- a -- jar. \skip 1 }
      }
      \repeat volta 2 {
        \set stanza = "2.B"
        | Ou -- vir mui -- to~e | fa -- lar pou -- co;
        | Pra co -- nhe -- cer
      } \alternative {
        { | meus ca -- boclos. \skip 1 }
        { | meus ca -- boclos. \set stanza = "3." Eu}
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1
      \repeat volta 2 {
        | to -- mo Dai -- me~eu | to -- mo Dai -- me;
        | Por -- que __ _ a -- cho __ _
      } \alternative {
        { | bom to -- mar. Eu }
        { | bom to -- mar. \set stanza = "3.B" Não }
      }
      \repeat volta 2 {
        | e -- xis -- te na -- | da di -- fí -- cil
        | Se com~o Mes -- tre
      } \alternative {
        { | se fir -- mar. Não}
        { | se fir -- mar. \skip 1 }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1
      \repeat volta 2 {
        | Eu a -- qui vou | vi -- a -- jan -- do;
        | Por a -- _ qui te -- nho
      } \alternative {
        { | que se -- guir. \skip 1 }
        { | que se -- guir. \set stanza = "4.B" Es -- }
      }
      \repeat volta 2 {
        | tou con -- vi -- dan -- | do sor -- rin -- do;~E
        | co -- mi -- go nin --
      } \alternative {
        { | guém quer ir. Es}
        { | guém quer ir. }
      }
    }
    theChords = \chordmode {
      s8
      \repeat volta 2 {
        | c1 | c1
        | a1:m
      } \alternative {
        { | f2 g2 }
        { | f2 g2 }
      }
      \repeat volta 2 {
        | c1 | f2 g2
        | a1:m
      } \alternative {
        { | c1 }
        { | c1 }
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I drink Daime, I drink Daime, I'm not afraid of drinking it
    Being with myu Master, in him I can firm myself
    \nextverse
    I drink Daime, I drink Daime, I drink it to travel
    Listen a lot and speak little, to know my caboclos
    \nextverse
    I drink Daime I drink Daime, because I think it's good to drink
    There isn't anything difficult, if with the Master we firm ourselves
    \nextverse
    Through this way I go traveling, through here I must follow
    I am inviting smiling, and with me no one wants to go
  \end{translation}
\endsong


\beginsong{O Daime me Balanção}[by={Tetéo},key={C},gk={C, (B)--(C)}]
  \audio{https://www.nossairmandade.com/hymn/1066/ODaimeMeBalan\%C3\%A7ou}
  \newchords{chords_odaimemebalancao_a}\newchords{chords_odaimemebalancao_b}
  \mnbeginchorus\memorize[chords_odaimemebalancao_a]
    |\[\mnc{G}C]O Dai\[\bmc\mn{C}]me \[^\mn{G}]me |ba\[^\mn{E}]lan\[\bmc\mn{G}]çou
    |\[^\mn{C}]O Dai\[\bmc\mn{E}]me \[^\mn{C}]me |\[\mnc{A}F]se\[^\mn{G}]gu\[G]rou
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_odaimemebalancao_b]
    |\[\mnc{C}C]O po\[\bmc\mn{E}]der \[^\mn{C}]que o |\[\mnc{A}F]Mes\[^\mn{G}]tre \[G]tem
    \[^\mn{C}]O |\[C]mesmo \[\bmc\mn{E}]Dai\[^\mn{C}]me |\[\mnc{D}G7]me \[^\mn{B}]mos\[\mnc{C}C]trou
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_odaimemebalancao_a]
    Me |^concen^trei no |Presi^den|te
    E lo^go E|^le che^gou
  \endchorus\glueverses\beginchorus\replay[chords_odaimemebalancao_b]
    Fi|^quei a^legre e |^satis^feito
    Em |^conhe^cer o |^seu va^lor
  \endchorus
  \beginchorus\replay[chords_odaimemebalancao_a]
    Fi|^quei a^legre e |satis^feito
    Em |conhe^cer o |^seu va^lor
  \endchorus\glueverses\beginchorus\replay[chords_odaimemebalancao_b]
    |^Os que es^tive|^rem com ^Ele
    Es|^tão com o ^Mestre En|^sina^dor
  \endchorus
  \beginchorus\replay[chords_odaimemebalancao_a]
    |^Pedi ^confor|to a meu ^Mestre \altchords{\id[4]{MK (C)}|C | \e}
    E |a Vir^gem que |^me le^vou \altchords{|Am | - G}
  \endchorus\glueverses\beginchorus\replay[chords_odaimemebalancao_b]
    |^Para ^mim po|^der che^gar \altchords{|C |Am G}
    |^No lu^gar a|^onde es^tou \altchords{|C |G7 C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 8
      \repeat volta 2 {
        \parenthesize g8\sectionmark "A"
        | g4_\pomark g c g | g e g4. \parenthesize c,8
        | c4 c e c | a g g4.
      } \break
      \repeat volta 2 {
        \parenthesize c8 \sectionmark "B"
        | c4 c4 e4 c4 | a4 g g4. \parenthesize c8
        | c4 c4 e4 c4 | d4 b c4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 | O Dai -- me me | ba -- lan -- çou;
        \skip 1 | O Dai -- me me | se -- gu -- rou.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        \skip 1 | O po -- der que~o | Mes -- tre tem;
        O | mes -- mo Dai -- me | me mos -- trou.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Me | con -- cen -- trei no | Pre -- si -- den -- \skip 1 | te;~E
        lo -- go E -- | le che -- gou.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Fi -- | quei a -- le -- gre~e | sa -- tis -- fei -- to;~Em
        | co -- nhe -- cer o | seu va -- lor.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Fi -- | quei a -- le -- gre~e | sa -- tis -- fei -- to;~Em
        | co -- nhe -- cer o | seu va -- lor.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 | Os que~es -- ti -- ve -- | rem com E -- le;~Es
        | tão com~o Mes -- tre~En -- | si -- na -- dor.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        \skip 1 | Pe -- di con -- for -- | to~a meu Mes -- tre;~E
        | a Vir -- gem que | me le -- vou.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        \skip 1 | Pa -- ra mim po -- | der che -- gar;
        \skip 1 | No lu -- gar a -- | on -- de~es -- tou.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | c1 | c | c | f2 g4.
      }
      \repeat volta 2 {
        s8 | c1 | f2 g | c1 | g2:7 c4.
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    The Daime shook me, the Daime held me
    The power that the Master has, the same Daime showed me
    \nextverse
    I Concentrated myself in the President, and soon he arrived
    I became joyful and satisfied in knowing his value
    \nextverse
    I became joyful and satisfied in knowing his value
    Those who are with Him, are with the Teaching Master
    \nextverse
    I asked for comfort to my Master, and to the Virgin who took me
    So that I could arrive in the place where i am
  \end{translation}
\endsong


\beginsong{Mesa de Centro}[by={Tetéo},key={D},gk={D, (D)--(E\flt{})},tags={2x}]
  \audio{https://www.nossairmandade.com/hymn/1081/MesaDeCentro}
  \newchords{chords_mesadecentro_a}\newchords{chords_mesadecentro_b}
  \mnbeginchorus\memorize[chords_mesadecentro_a]
    \[^\mn{A}]Eu \[^\mn{D}]to\[^\mn{F#}]mei |\[\mnc{A}D]Dai\[^\mn{F#}]me \[^\mn{A}]com \[\mnc{B}(Bm)]meu \[^\mn{A}]Pre\[^\mn{F#}]si|\[\mnc{D}D]den\[\bmc\mn{B}]te \altchords{\id[1]{(C)}|C (Am) |C}
    |\[\mnc{D}Bm]Den\[^\mn{C#}]tro \[^\mn{D}]de um \[\mnc{E}Em]lin\[^\mn{C#}]do \[^\mn{B}]sa|\[\mnc{A}A7]lão\[\bm] \altchords{|Am Dm |G7}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_mesadecentro_b]
    \[^\mn{A}]Em |\[\mnc{D}D]u\[^\mn{C#}]ma \[\mnc{E}Em]Me\[^\mn{C#}]sa \[^\mn{B}]de |\[\mnc{A}A]Cen\[\bm]tro \altchords{|C Dm |G}
    Da |\[\mnc{D}D]Vir\[^\mn{C#}]gem \[\mnc{E}A7]da \[^\mn{D}]Con\[^\mn{C#}]cei|\[\mnc{D}D]ção\[\bm] \altchords{|C G7 |C}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_mesadecentro_a]
    Esta |^Mesa ^é bem or|^na^da
    De |^flores ^bem enfei|^ta^das
    \endchorus\glueverses\beginchorus\replay[chords_mesadecentro_b]
    De |^luzes de ^diversas |^co^res
    Aonde es|^tá o ^nosso Je|^sus^
  \endchorus
  \beginchorus\replay[chords_mesadecentro_a]
    Aonde es|^tá o ^nosso Je|^sus^
    Com a|^mor ^à Santa |^Cruz^
    \endchorus\glueverses\beginchorus\replay[chords_mesadecentro_b]
    Nos |^dando ^a Santa |^Luz^
    E nos mos|^trando os ^nossos de|^fei^tos
  \endchorus
  \beginchorus\replay[chords_mesadecentro_a]
    Nos mos|^trando os ^nossos de|^fei^tos
    Quem |^quiser tra^balhe e apro|^vei^te
    \endchorus\glueverses\beginchorus\replay[chords_mesadecentro_b]
    Que o |^tempo ^está fin|^da^do
    E pra de|^pois ^não tem mais |^jei^to
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      % Note that the \breaks are where they are to fit on one page and
      % to have clear fist and last verse.
      \key d \major \time 4/4 \partial 4.
      % verse 1
      \repeat volta 2 {
        a8\sectionmark "1.A" d8 fis8 | a4 fis8 a8 b4 a8 fis8 | d2. b4 | d4 cis8 d8 e4 cis8 b8 | a2~ a8
      }
      \repeat volta 2 {
        r8\sectionmark "1.B" a4 | d4. cis8 e4 cis8 b8 | a2 a4 a4 | d4. cis8 e4 d8 cis8 | d2~ d8
      } \break
      % verse 2
      \repeat volta 2 {
        r8\sectionmark "2.A" d8 fis8 | a4. fis8 b4 a8 fis8 | d2 d4 b4 | d4( cis8) d8 e4 cis8 b8 | a2 a8
      }
      \repeat volta 2 {
        r8\sectionmark "2.B" a4 | d4. cis8 e4 cis8 b8 | a2 a8 a8 fis8 a8 | d4. cis8 e4 d8 cis8 | d2~ d8
      }
      % verse 3
      \repeat volta 2 {
        a8\sectionmark "3.A" d8 fis8 | a4. fis8 b4 a8 fis8 | d2. b8 b8 | d4.( cis8) e4 cis8 b8 | a2~ a8
      }
      \repeat volta 2 {
        r8\sectionmark "3.B" a4 | d4. cis8 e4 cis8 b8 | a2~a8 a8 fis8 a8 | d4. cis8 e4 d8 cis8 | d2 d8
      } \break
      % verse 4
      \repeat volta 2 {
        r8\posectionmark "4.A" d8 fis8 | a4. fis8 b4 a8 fis8 | d2 d4 b4 | d4 cis8 d8 e4 cis8 b8 | a2 a8
      }
      \repeat volta 2 {
        r8\sectionmark "4.B" a4 | d4. cis8 e4 cis8 b8 | a2 a8 a8 fis8 a8 | d4.( cis8) e4 d8 cis8 | d2 d8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Eu to -- mei | Dai -- me com meu Pre -- si -- | den -- te;
      | Den -- tro de~um lin -- do sa -- | lão.
      \set stanza = "1.B"
      Em | u -- ma Me -- sa de | Cen -- tro;
      Da | Vir -- gem da Con -- cei -- | ção.
      \set stanza = "2.A"
      Es -- ta | Me -- sa é bem or -- | na -- da;
      De | flo -- res bem en -- fei -- | ta -- das.
      \set stanza = "2.B"
      De | lu -- zes~de di -- ver -- sas | co -- res;
      A -- on -- de~es -- | tá o nos -- so Je -- | sus.
      \set stanza = "3.A"
      A -- on -- de~es -- | tá o nos -- so Je -- | sus;
      Com a -- | mor à San -- ta | Cruz.
      \set stanza = "3.B"
      Nos | dan -- do a San -- ta | Luz;
      E nos mos -- | tran -- do~os nos -- sos de -- | fei -- tos.
      \set stanza = "4.A"
      Nos mos -- | tran -- do~os nos -- sos de -- | fei -- tos;
      Quem | qui -- ser tra -- ba -- lhe~e~a -- pro -- | vei -- te.
      \set stanza = "4.B"
      Que~o | tem -- po es -- tá fin -- | da -- do;
      E pra de -- | pois não tem mais | jei -- to.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | \once \set chordChanges = ##f d2 \parenthesize b:m | d1 | b2:m e2:m | a2:7~ a8:7
      }
      \repeat volta 2 {
        s4. | d2 e2:m | a1 | d2 a:7 | d2~ d8
      }
      % verse 2, copied from verse 1
      \repeat volta 2 {
        s4. | \once \set chordChanges = ##f d2 \parenthesize b:m | d1 | b2:m e2:m | a2:7~ a8:7
      }
      \repeat volta 2 {
        s4. | d2 e2:m | a1 | d2 a:7 | d2~ d8
      }
      % verse 3, copied from verse 1
      \repeat volta 2 {
        s4. | \once \set chordChanges = ##f d2 \parenthesize b:m | d1 | b2:m e2:m | a2:7~ a8:7
      }
      \repeat volta 2 {
        s4. | d2 e2:m | a1 | d2 a:7 | d2~ d8
      }
      % verse 4, copied from verse 1
      \repeat volta 2 {
        s4. | \once \set chordChanges = ##f d2 \parenthesize b:m | d1 | b2:m e2:m | a2:7~ a8:7
      }
      \repeat volta 2 {
        s4. | d2 e2:m | a1 | d2 a:7 | d2~ d8
      }
    }
    \layout { #(layout-set-staff-size 11) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    I drank Daime withg my president in a beautiful room
    At a table in the center of the Virgin of Conception
    \nextverse
    This table is well ornated, with flowers, well decorated
    With lights of various colours, where our Jesus is
    \nextcolor
    Where our Jesus is, with love for the Holy Cross
    Giving us the Holy Light and showing us our defects
    \nextverse
    Showing us our defects; who wants can work and profit
    Because the time is coming to an end, for after there is no more use
  \end{translation}
\endsong


\beginsong{O Daime é o Nosso Pai}[by={Tetéo},key={G},gk={A, G--B}]
  \audio{https://www.nossairmandade.com/hymn/1120/Daime\%C3\%89ONossoPai}
  \newchords{chords_odaimeeonossopai_a}\newchords{chords_odaimeeonossopai_b}
  \mnbeginchorus\memorize[chords_odaimeeonossopai_a]
    \[^\mn{G}]O |\[\mnc{B}G]Daime é o \[\mnc{A}D]nosso |\[\mnc{G}G]Pai \altchords{\id[1]{(A)}|A E |A}
    É \[\bmc\mn{B}]nos\[^\mn{D}]so ir|\[\mnc{G}C]mão \[^\mn{E}]e \[\bmc\mn{G}]com\[^\mn{E}]pa|\[\mnc{G}G]nhei\[\bm]ro \altchords{|D |A}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_odaimeeonossopai_b]
    \[^\mn{D}]É |\[\mnc{G}C]E\[^\mn{E}]le é \[\bmc\mn{G}]quem \[^\mn{E}]nos |\[\mnc{G}G]cura \altchords{|D |A}
    E \[\mnc{F#}(D)]nos \[^\mn{E}]li|\[\mnc{B}G]vra \[^\mn{D}]de \[\mnc{A}D7]to\[^\mn{B}]do |\[\mnc{G}G]mal\[\bm] \altchords{(E) |A E7 |A}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_odaimeeonossopai_a]
    O |^Daime é o ^nosso ir|^mão
    Não ^se escu|^sando ^de to|^mar^
    \endchorus\glueverses\beginchorus\replay[chords_odaimeeonossopai_b]
    Den|^tro De^le tem |^tudo
    ^Que o a|^migo ^procu|^rar^
  \endchorus
  \beginchorus\replay[chords_odaimeeonossopai_a]
    Vamos |^todos ^meus ir|^mãos
    ^Traba|^lhar e ^se fir|^mar
    \endchorus\glueverses\beginchorus\replay[chords_odaimeeonossopai_b]
    \noteson\[\bmc\mnlow{B}]Va\[\mnlow{D}]mos \notesoff |^crer em ^Jesus |^Cristo
    O ^Nosso |^Mestre En^sina|^dor
  \endchorus
  \begin{translation}
    The Daime is our Father, our brother and companion
    It's him who heals and saves us from all evil
    \nextverse
    The Daime is our brother, no apologizing for taking
    Inside of it there is everything that the friend is searching for
    \nextverse
    Let's all go, my brothers, and work and firm ourselves
    Let us believe in Jesus Christ, our Master Teacher
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 4
      \repeat volta 2 {
        g4_\sectionmark "1-2.A" | b4 b8 b8 a4 a4 | g4. g8 b4 d4 | g4 e4 g4 e4 | g2( g4)
      }
      \repeat volta 2 {
        d4_\sectionmark "1-2.B" | g4 e8( e8) g4 e4 | g4. g8 fis4 e4 | b4 d4 a4 b4
      } \alternative {
        { | g2. }
        { | g2. _\dacapo }
      }
      \repeat volta 2 {
        g8_\posectionmark "3.A" g8 | b4 b4 a4 a4 | g2 b4 d4 | g4 e4 g4 e4
      } \alternative {
        { | g2. }
        { | g2 }
      }
      \repeat volta 2 {
        b,4_\sectionmark "3.B" d4 | g4 e4 g4 e4 | g4. g8 fis4 e4 | b4 d4 a4 b4 | g2
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        O | Dai -- me~é o nos -- so | Pai;
        É nos -- so~ir -- | mão e com -- pa -- | nhei -- ro.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        É | E -- le é quem nos | cu -- ra;~E
        nos li -- | vra de to -- do
      } \alternative {
        { | mal. }
        { | mal. }
      }
      \set stanza = "3.A"
      \repeat volta 2 {
        Va -- mos | to -- dos meus ir -- | mãos;
        Tra -- ba -- | lhar e se fir --
      } \alternative {
        { | mar. }
        { | mar. }
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Va -- mos | crer em Je -- sus | Cris -- to;~O
        Nos -- so | Mes -- tre~En -- si -- na -- | dor.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        O | Dai -- me~é o nos -- so~ir -- | mão;
        Não se~es -- cu -- | san -- do de to -- | mar. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Den -- | tro De -- _ le tem | tu -- do;
        Que~o a -- | mi -- go pro -- cu --
      } \alternative {
        { | rar. }
        { | rar. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | g2 d2 | g1 | c | g2.
      }
      \repeat volta 2 {
        s4 | c1 | g2 \parenthesize d | g2 d2:7
      } \alternative {
        { | g2. }
        { | g2. }
      }
      % verse 3, same chords as above but with alt. ending after part A
      \repeat volta 2 {
        s4 | g2 d2 | g1 | c
      } \alternative {
        { | g2. }
        { | g2 }
      }
      \repeat volta 2 {
        s2 | c1 | g2 \parenthesize d | g2 d2:7 | g2
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Um, Dois e Três}[by={Tetéo},key={C},gk={D, C, E}]
  \audio{https://www.nossairmandade.com/hymn/1130/Um,DoisETr\%C3\%AAs}
  \newchords{chords_umdoisetres_a}\newchords{chords_umdoisetres_b}
  \mnbeginchorus\memorize[chords_umdoisetres_a]
    \[^\mn{G}]É |\[\mnc{C}C]um, \[^\mn{G}]é \[\bmc\mn{C}]dois, \[^\mn{G}]é |\[^\mn{C}]trê\[\bm]s
    É |\[\mnc{F}F]qua\[^\mn{D}]tro, é \[\bmc\mn{E}]cin\[^\mn{C}]co, é |\[C]seis\[\bm]
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_umdoisetres_b]
    \[^\mn{C}]Quem não esti|\[\mnc{F}F]ver \[^\mn{D}]com\[\bmc\mn{E}]pre\[^\mn{D}]en|\[\mnc{C}C]den\[\bm]do
    \[^\mn{B}]To\[^\mn{A}]me |\[\mnc{G}G]Daime \[\mnc{C}F]ou\[^\mn{G}]tra |\[\mnc{C}C]vez\[\bm]
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_umdoisetres_a]
    Eu es|^tando ^com meu |Mes^tre
    Estou com |^o meu ^Presi|^den^te
    \endchorus\glueverses\beginchorus\replay[chords_umdoisetres_b]
    Estou com |^todos se^res di|^vi^nos
    Aqui es|^tá o ^meu pre|^sen^te
  \endchorus
  \beginchorus\replay[chords_umdoisetres_a]
    Vou mos|^trar pra ^meus ir|mã^os
    O va|^lor des^te pre|^sen^te
    \endchorus\glueverses\beginchorus\replay[chords_umdoisetres_b]
    Quem não esti|^ver a^credi|^tan^do
    Tome |^Daime e ^vamos em |^fren^te
  \endchorus
  \begin{translation}
    It's one, it's two, it's three, it's four, it's five, it's six.
    Who is not understanding, dring Daime one more time
    \nextverse
    Being with my Master, I am with my President
    I am with all the Divine Beings here in my present
    \nextverse
    I will show to my brothers and sisters the value of this present
    Who is not believing, drink Daime and let's go ahead
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        r8 g8(\posectionmark "A" g8) | c4. g8 c4. g8 | c2( c8 c8) c8( c8) | f4. d8 e4. c8 | c2( c8)
      }
      \repeat volta 2 {
        c8\sectionmark "B" c8 c8 | f4( f8) d8 e4. d8 | c2 c8( c8) b8 a8 | g4. g8 c4( c8) g8 | c2( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      É __ _ | um é dois é | três; __ _ _
      É __ _ | qua -- tro~é cin -- co~é | seis. __ _
      \set stanza = "1.B"
      Quem não~es -- ti -- | ver __ _ com -- pre -- en -- | den -- do; __ _
      To -- me | Dai -- me ou -- _ tra | vez. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Eu es -- | tan -- do com meu | Mes -- tre;
      Es -- tou com | o meu Pre -- si -- | den -- te.
      \set stanza = "2.B"
      Es -- tou com | to -- dos se -- res di -- | vi -- nos;
      A -- qui es -- | tá o meu __ _ pre -- | sen -- te.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      Vou mos -- | trar pra meus ir -- | mãos; __ _ _
      O va -- | lor des -- te pre -- | sen -- te.
      \set stanza = "3.B"
      Quem não~es -- ti -- | ver __ _ a -- cre -- di -- | tan -- do; __ _
      To -- me | Dai -- me~e va -- mos em | fren -- te.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1 | c1 | f1 | c2~ c8
      }
      \repeat volta 2 {
        s4. | f1 | c1 | g2 f2 | c2~ c8
      }

    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{O Lindo Daime}[by={Luiz Mendes},key={Am},gk={Cm, Bm, Am}]
  \audio{https://www.nossairmandade.com/hymn/34/OLindoDaime}
  \mnbeginchorus\memorize
    |\[\mnc{A}Am]O \[^\mn{C}]lin\[^\mn{A}]do |\[\mnc{E}(E)]Daime
    |\[\mncii{A}{B}Am]Veja \[^\mn{C}]co\[^\mn{A}]mo |\[\mnc{E}(E)]é
    \lrep |\[\mnc{A}Am]É \[^\mn{C}]ma\[^\mn{A}]ra|\[\mnc{E}E]vilha
    Pa\[^\mn{D}]ra |\[\mnc{C}(C)]to\[^\mn{B}]dos \[\mnc{E}E7]ten\[^\mn{C}]do |\[\mnc{A}Am]fé \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    |^Eu peço a meu |^Mestre
    |^No meu cora|^ção
    \lrep |^A santa |^luz
    Da vir|^gem da ^Concei|^ção \rrep
  \endchorus
  \beginchorus
    |^Te afirma em |^Deus
    |^Em concentra|^ção
    \lrep |^Que tu te|^rás
    A |^san^ta ben|^ção \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4
      | a4._\posectionmark "A" \parenthesize b8 c4 a4 | e'2( e4 e4) | a,4. b8 c4 a4 | e'1
      \repeat volta 2 {
        | a,2_\sectionmark "B" c4 a4 | e'4.( e8 e4) d4 | c4( b4) e4 c4 | a1
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      | O __ _ lin -- do | Dai -- _ me;
      | Ve -- ja co -- mo | é.
      \repeat volta 2 {
        | É ma -- ra -- | vi -- lha;
        Pa -- ra | to -- dos ten -- do | fé.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      | Eu pe -- ço~a meu | Mes -- tre; __ _
      | No meu co -- ra -- | ção.
      \repeat volta 2 {
        | A san -- ta | luz; __ _
        Da vir -- | gem da Con -- cei -- | ção.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      | Te a -- fir -- ma~em | Deus; __ _ _
      | Em con -- cen -- tra -- | ção.
      \repeat volta 2 {
        | Que tu te -- | rás; __ _ _
        A | san -- _ ta ben -- | ção.
      }
    }
    theChords = \chordmode {
      | a1:m | \parenthesize e | a:m | \parenthesize e
      \repeat volta 2 {
        | a1:m | e | \parenthesize c2 e2:7 | a1:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    The beautiful Daime
    See how it is
    It is wonderful
    For everyone who has faith
    \nextverse
    I ask my Master
    In my heart
    The holy light
    Of the Virgin of Conception
    \nextverse
    Affirm yourself in God
    In concentration
    That you will have
    The holy blessing
  \end{translation}
\endsong


\beginsong{Convite}[by={Luiz Mendes},key={Am},gk={Am, Gm, Bm},tags={mazurca}]
  \audio{https://www.youtube.com/watch?v=4kLsE-ujOYQ}
  \newchords{chords_convite_a}\newchords{chords_convite_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_convite_a]
    \[^\mn{E}]O \[^\mn{C}]meu |\[\mnc{A}Am]Mestre \[^\mn{E}]con\[^\mn{C}]vi\[\bmc\mn{A}]dou-me \altchords{\id[1]{(Gm)}|Gm}
    \[^\mn{E}\mn{C}]E |\[^\mn{A}]eu \[^\mn{C}]o\[\mncii{G}{F}(Am7)]bede\[\bmc\mnc{E}E]ci \altchords{| - (Gm7) D}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_convite_b]
    \[^\mn{E}]To|\[\mnc{A}Fmaj7]{mei o} San\[^\mn{B}]to \[\bmc\mnc{C}Am]Dai\[^\mn{B}]me \altchords{|E\flt{}maj7 Gm}
    \[^\mn{A}]E |\[\mnc{E}E]eu me corri\[\bmc\mnc{A}Am]gi \altchords{|D Gm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_convite_a]
    Eu corri|^gi meu pensa^mento
    Entrei |na mi^{nha pes}^soa
    \endchorus\glueverses\beginchorus\replay[chords_convite_b]
    Fiz |^{um bonito} es^tudo
    Eu já |^vi que é coisa ^boa
  \endchorus
  \beginchorus\replay[chords_convite_a]
    As |^veias são os ^rios
    E o co|ração ^{é o} ^mar
    \endchorus\glueverses\beginchorus\replay[chords_convite_b]
    A |^carne é a ^Terra
    Como é |^bom se estu^dar
  \endchorus
  \beginchorus\replay[chords_convite_a]
    Aqui |^dentro temos ^tudo
    Nesta |fonte ^{de va}^lor
    \endchorus\glueverses\beginchorus\replay[chords_convite_b]
    O meu |^Mestre me aju^dando
    Se |^Deus quiser eu ^vou
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-11
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 6/4 \partial 4.
      \repeat volta 2 {
        \altcol \parenthesize e8 \altmark "2." e8 \posectionmark "A" c8 | a4 a4 e'8 c8  a4 a4 e'8( c8) | a4 c4 g'8 f8  e4( e8)
      }
      \repeat volta 2 {
        r8 \sectionmark "B" e8( e8) | a4 a4 a8 b8  c4 b4 a8( a8) | e4 e4 e8 e8  a,4( a8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 O meu | Mes -- tre con -- vi --  dou -- -me;
      E __ _ | eu o -- be -- de --  ci. __ _
      \set stanza = "1.B"
      To -- _ | mei o San -- to  Dai -- me;
      E __ _ | eu me cor -- ri --  gi. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \altcol Eu cor -- ri -- | gi meu pen -- sa --  men -- to;
      En -- trei | na mi -- nha pes --  so -- a.
      \set stanza = "2.B"
      Fiz __ _ | um bo -- ni -- to~es --  tu -- do;
      Eu já | vi que~é coi -- sa  bo -- a.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1 As __ _ | vei -- as são os  ri -- os;
      E~o co -- | ra -- ção é o  mar. __ _
      \set stanza = "3.B"
      A __ _ | car -- ne é a  Ter -- ra;
      Co -- mo~é | bom se es -- tu --  dar. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 A -- qui | den -- tro te -- mos  tu -- do;
      Nes -- ta | fon -- te de va --  lor. __ _
      \set stanza = "4.B"
      O meu | Mes -- tre me~a -- ju --  dan -- do;
      Se __ _ | Deus qui -- ser eu  vou. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a2.:m  a:m | a2:m \parenthesize a4:m7  e4.
      }
      \repeat volta 2 {
        s4. | f2.:maj7  a:m | e  a4.:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    My Master invited me and I obeyed
    I drank Santo Daime and corrected myself
    \nextverse
    I corrected my thought, I entered my person
    I made a beautiful study, I've seen that it is a good thing
    \nextverse
    The veins are the rivers, the earth is the sea
    The flesh is the earth, how good to study oneself
    \nextverse
    Here inside we have everything, in this fountain of value
    My Master helping me, God willing I shall go
  \end{translation}
\endsong


\beginsong{Eu Tomo Daime}[by={Vera Gall},key={Bm},gk={Cm, Bm, Am, Dm}]
  \audio{https://www.youtube.com/watch?v=yZR3eKULn_M}
  \audio{https://www.youtube.com/watch?v=bUR-OVaVTto}
  \mnbeginchorus\memorize
    \lrep \[^\mn{B}]Eu \[^\mn{D}]to\[^\mn{B}]mo |\[\mnc{D}Bm]Daime \altchords{\id[1]{(Am)}|Am}
    \[^\mn{B}]Que é \[\bmc\mn{D}]pa\[^\mn{B}]ra \[^\mn{D}]co\[^\mn{B}]nhe|\[\mnc{C#}F#m]cer \[\bm] \rrep \altchords{|Em}
    \lrep \[^\mn{A}]Conhe|\[\mnc{B&}Gm]cer a be\[\bmc\mnc{D}]leza de \[^\mn{E}]vi|\[\mncii{F}{D}Dm]ver \altchords{|Fm |Cm}
    \[\bmc\mn{A}]Dentro \[^\mn{B&}]desta |\[\mnc{A}A7]luz \altchords{|G7}
    Do meu \[\bmc\mn{F}]eu su\[^\mn{E}]pe\[^\mn{F}]ri|\[\mncii{E}{D}Dm]or \[\bm] \rrep \altchords{|Cm}
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep Eu tomo |^Daime
    Que é ^para apren|^der ^ \rrep
    \lrep Apren|^der a ter a^mor no cora|^ção
    Andar pe^la estrada da |^vida
    Com ^toda a liber|^dade ^ \rrep
  \endchorus
  \beginchorus
    \lrep Eu tomo |^Daime
    É ^para renas|^cer ^ \rrep
    \lrep Renas|^cer no ca^minho da ver|^dade
    Para ^encontrar a |^paz
    Vos me ^livre dos en|^ganos ^ \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose a b \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        a8 \posectionmark "A" c8 a8 | c4 c8 a8 c8 a8 c8 a8 | b2~ b8
      } \break
      \repeat volta 2 {
        \key c \minor
        r8 \sectionmark "B" g8 g8 | aes8( aes8) aes8 aes8 c8 c8 c8 d8 | \once\slurSolid es8( c8)( c8) \altcol \parenthesize g8 \altmark "2., 3." g8 g8 aes8 aes8
        | g4 g8 g8 es'8 es8 d8 es8
      } \alternative {
        { | \once\slurSolid d8( c8)~ c4.}
        { | \once\slurSolid d8( c8)~ c4. ^\dacapo }
      }
      \bar "|."
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Eu to -- mo | Dai -- me;
      Que~é pa -- ra co -- nhe -- | cer. __ _
      \set stanza = "1.B"
      Co -- nhe -- | cer __ _ a be -- le -- za de vi -- | ver; __ _ _
      \skip 1 Den -- tro des -- ta | luz;
      Do meu eu su -- pe -- ri -- | or. __ _ _ | or. __ _ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Eu to -- mo | Dai -- me;
      Que~é pa -- ra a -- pren -- | der. __ _
      \set stanza = "2.B"
      A -- pren -- | der a ter a -- mor no co -- ra -- | ção;
      An -- dar \altcol pe -- la~es -- tra -- da da | vi -- da;
      Com to -- da~a li -- ber -- | da -- _ de. | da -- _ de.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      Eu to -- mo | Dai -- me;
      É pa -- ra re -- nas -- | cer. __ _
      \set stanza = "3.B"
      Re -- nas -- | cer __ _ no ca -- mi -- nho da ver -- | da -- de; 
      Pa -- \altcol ra en -- con -- trar a | paz;
      Vos me li -- vre dos en -- | ga -- _ nos. | ga -- _ nos.
    }
    theChords = \transpose a b \chordmode {
      \repeat volta 2 {
        s4. | a1:m | e2:m~ e8:m
      }
      \repeat volta 2 {
        s4. | f1:m | c:m | g:7 
      } \alternative {
        { | c2:m~ c8:m }
        { | c2:m~ c8:m }
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I drink Daime to get to know
    To know the beauty of living
    Inside this light of my superior I
    \nextverse
    I drink Daime to get to learn
    To learn to have love in the heart
    To walk on the road of life with total freedom
    \nextverse
    I drink Daime to get to be reborn
    To be reborn on the way of truth
    To find the peace; You deliver me from deceit
  \end{translation}
\endsong


\beginsong{É com Deus}[by={Baixinha},key={C},gk={C, A-D}]
  \audio{https://www.nossairmandade.com/hymn/2516/\%C3\%89ComDeusQueEuTomoDaime}
  \mnbeginchorus
     \lrep \[\mn{E}]É com |\[C]Deus \[\mn{D}]que eu \[G]to\[\mn{C}]mo |\[C]Dai\[\bm]me \altchords{\id[1]{(A)}|A E |A}
     \[\mn{A}]E com |\[Am]Deus \[\mn{G}]eu \[G]che\[\mn{F}]go |\[F]lá \[\bm] \rrep \altchords{|F\shrp{}m E |D}
     \lrep \[\mn{A}]Porque |\[F]Deus \[\mn{G}]é \[\bm]quem m\[\mn{F}]e en|\[\mnc{E}C]si\[\mn{C}]na\[\bm] \altchords{|D |A}
     \[\mn{E}]Tudo |\[Am]que eu \[\mn{D}]te(nho) \[G7]que \[\mn{C}]sa|\[C]ber \[\bm] \rrep \altchords{|F\shrp{}m E7 |A}
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
         e8 \posectionmark "A" e8 | e4. d8 d4. c8 | c2 c4 a'8 a8 | a4. g8 g4. f8 | f2.
      }
      \repeat volta 2 {
        a8 \sectionmark "B" a8 | a4. g8 g4. f8 | e4 c2 e8 e8 | e4. d8 d4. c8
      } \alternative {
        { | c2. }
        { | c2. ^\dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        É com | Deus que~eu to -- mo | Dai -- me;
        E com | Deus eu che -- go | lá.
      }
      \repeat volta 2 {
        Por -- que | Deus é quem me~en -- | si -- na;
        Tu -- do | que~eu te(nho) que sa --
      } \alternative {
        { | ber. }
        { | ber. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 g2 | c1 | a2:m g2 | f2.
      }
      \repeat volta 2 {
        s4 | \once\set chordChanges = ##f f1 | c1 | a2:m g2:7
      } \alternative {
        { | c2. }
        { | c2. }
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    It is with God that I take Daime
    And with God I get there
    \nextverse
    Because God is who teaches me
    All that I have to know
  \end{translation}
\endsong


\beginsong{Ser Divino}[by={Odemir Raulino Da Silva},key={A},gk={A, B, C, G}]
  \audio{https://www.nossairmandade.com/hymn/1540/SerDivino}
  \mnbeginchorus\memorize
    \[^\mn{A}]Quem \[\bm]não \[^\mn{C#}]pro|\[\mnc{E}A]vou \[\bm] | \e \altchords{\id[1]{(G)}|G | \e}
    \[^\mn{C#}]Ve\[\bmc\mn{A}]nha \[^\mn{C#}]pro|\[\mnc{B}Bm]var \[\bm] | \e \altchords{|Am | \e}
    \[^\mn{D}]Des\[\bmc\mn{F#}]ta \[^\mn{D}]be|\[\mnc{F#}D]bi\[\bm]da | \e \altchords{|C | \e}
    \[^\mn{/}]Que a\[\bmc\up{2}(E7)]qui es|\[\up{1}E\up{2}(A)]tá \[\bm] |\[\up{1}E7\up{2}(A)] \e \altchords{\up{2}(D7) |\up{1}D\up{2}(G) |\up{1}D7\up{2}(G)}
  \mnendchorus
  \notesoff
  \beginchorus
    Um ^Ser Di|^vi^no | \e
    Transfor^mado em |^líqui^do | \e
    Vem ^acor|^dar ^ | \e
    O ^nosso es|^píri^to |^ \e
  \endchorus
  \beginchorus
    Se ^acor|^da^dos | \e
    Po^demos |^ver ^ | \e
    O ^Mestre en|^si^na | \e
    Vamos ^apren|^der ^ |^ \e
  \endchorus
  \begin{translation}
    Who has not proved, come taste
    This drink that is here
    \nextverse
    A Divine Being transformed into liquid
    Come wake our spirit
    \nextverse
    If it's agreed, we can see
    The Master teaches, let's learn
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 2.
      a4\posectionmark "I" a4 cis4 | e2( e2)~ | e4 cis8( cis8) a4 cis4 | b4.( b8 b2)~
      | b4 d4 fis4 d8( d8) | fis2( fis2)~
      | fis4 d8( d8) fis4 fis8( fis8) | e4.( e8 e2)~ \bar "||" | e4
      % repeat (different melody in the last three bars)
      a,4\sectionmark "II" a4 cis4 | e2( e2)~ | e4 cis8( cis8) a4 cis4 | b4.( b8 b2)~
      | b4 d4 fis4 d8( d8) | fis2( fis2)~
      | fis4 a8( a8) gis4 e8( e8) | a4.( a8 a2)~ | a4 \bar "|."
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Quem não pro -- | vou; __ _ | _
      Ve -- _  nha pro -- | var; __ _ _ | _
      Des -- ta be -- _ | bi -- da; __ | _
      Que a -- qui es -- _ | tá. __ _ _ | _
      % repeat
      Quem não pro -- | vou; __ _ _
      Ve -- _  nha pro -- | var; __ _ _ | _
      Des -- ta be -- _ | bi -- da; __ | _
      Que a -- qui es -- _ | tá. __ _ _ | _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Um Ser Di -- | vi -- no; __ | _
      Trans -- for -- ma -- do~em lí -- qui -- do; __ | _
      Vem a -- cor -- _ | dar; __ _ | _
      O __ _ nos -- so es -- pí -- ri -- to. __ | _
      % repeat
      Um Ser Di -- | vi -- no; __ | _
      Trans -- for -- ma -- do~em lí -- qui -- do; __ | _
      Vem a -- cor -- _ | dar; __ _ | _
      O __ _ nos -- so es -- pí -- ri -- to. __ | _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Se a -- cor -- | da -- dos; __ | _
      Po -- _ de -- mos | ver; __ _ _ | _
      O Mes -- tre en -- | si -- na; __ | _
      Va -- mos a -- pren -- _ | der. __ _ _ | _
      % repeat
      Se a -- cor -- | da -- dos; __ | _
      Po -- _ de -- mos | ver; __ _ _ | _
      O Mes -- tre en -- | si -- na; __ | _
      Va -- mos a -- pren -- _ | der. __ _ _ | _
    }
    theChords = \chordmode {
      s2. | a1 | a | b:m | b:m | d | d | e
      | e:7 | a1 | a | b:m | b:m | d | d2 e2:7 | a1 | a4
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Balanço de São João}[by={Odemir Raulino Da Silva},key={C},gk={C, A-F}]
  \audio{https://www.nossairmandade.com/hymn/1548/Balan\%C3\%A7oDeS\%C3\%A3oJo\%C3\%A3o}
  \mnbeginchorus
    \lrep \[\mn{G}]Eu es|\[C]tando \[\mn{E}]com o \[\bmc\mn{C}]Daime, eu |\[Am]nun\[\mn{E}]ca \[\mn{C}]me \[\bmc\mnc{D}G]can\[\mn{G}]so
    Eu es|tando com \[\bm]e\[\mn{F}]le
    Eu \[\mn{E}]en\up{1}(|\[\mnc{D}G7]tro \[\mn{E}]no \[\mn{D}]ba\[\bmc\mnc{C}C]lanço) \up{2}(|\[\mnc{D}G7]tro \[\mn{E}]no \[\mn{D}]ba\[\bmc\mnc{C}C]lan|ço)\rrep
    \lrep \[\mn{E}]E eu \[\mn{D}]ba\[\bmc\mn{C}]lan|ço \[\mn{G}]e eu ba\[\bmc G]lan|ço
    Nesta |força Di\[\bm]vi\[\mn{F}]na
    \[\mn{E}]Eu \up{1}(|\[\mnc{D}G7]nun\[\mn{E}]ca \[\mn{D}]me \[\bmc\mnc{C}C]can|so) \up{2}(|\[\mnc{D}G7]nun\[\mn{E}]ca \[\mn{D}]me \[\bmc\mnc{C}C]canso) \rrep
  \mnendchorus
  \mnbeginchorus
    \ind \lrep \[\mn{G}]Venho |\[C]dizer a \[\mn{E}]meu \[\bmc\mn{C}]Mestre, que eu es|\[Am]tou \[\mn{E}]sa\[\mn{C}]tis\[\bmc\mnc{D}G]feito
    \ind \[\mn{G}]Pelo |meu cora\[\bm]ção há |quarenta \[\bm]a\[\mn{F}]nos
    \ind \[\mn{E}]Ba\up{1}(|\[\mnc{D}G7]ten\[\mn{E}]do em \[\mn{D}]meu \[\bmc\mnc{C}C]peito) \up{2}(|\[\mnc{D}G7]ten\[\mn{E}]do em \[\mn{D}]meu \[\bmc\mnc{C}C]pei|to) \rrep
    \ind \lrep \[\mn{E}]E eu \[\mn{D}]ba\[\bmc\mn{C}]lanço, cora|ção \[\mn{G}]segue ba\[\bmc G]tendo
    \ind Com |meu São Jo\[\bm]ão
    \ind \[\mn{F}]Vou \[\mn{E}]a\up{1}(|\[\mnc{D}G7]le\[\mn{E}]gre \[\mn{D}]vi\[\bmc\mnc{C}C]ven|do) \up{2}(|\[\mnc{D}G7]le\[\mn{E}]gre \[\mn{D}]vi\[\bmc\mnc{C}]vendo) \rrep
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8\sectionmark "1.A" g8 | g4 g8 e8 c4 c8 c8 | c4 e8 c8 d4 g8 g8
        | g4 g8 g8 g4 f8 e8
      } \alternative {
        { | d4 e8 d8 c8. c16 }
        { | d4 e8 d8 c2 | c8 }
      }
      \repeat volta 2 {
        e8\sectionmark "1.B" e8 d8 c2 | c8 g'8 g8 g8 g4 g8 g8 | g4 g8 g8
        g4 f8 e8
      } \alternative {
        { | d4 e8 d8 c2 | c8 }
        { | d4 e8 d8 c8. c16 ^\dacapo \break }
      }
      \repeat volta 2 {
        g'8\segno g8\posectionmark "2.A" | g8 g8 g8 e8 c4 c8 c8 | c4 e8 c8 d4 g8 g8
        | g4 g8 g8 g4. g8 | g4 g8 g8 g4 f8 e8
      } \alternative {
        { | d4 e8 d8 c8. c16 }
        { | d4 e8 d8 c2 | c8 }
      }
      \repeat volta 2 {
        e8\sectionmark "2.B" e8 d8 c8 c8 c8 c8 | c8 g'8 g8 g8 g4 g8 g8 | g4 g8 g8 g4 f8 e8
      } \alternative {
        { | d4 e8 d8 c2 c8 }
        { | d4 e8 d8 c8. c16 ^\dalsegno \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu es -- | tan -- do com~o Dai -- me,
        eu | nun -- ca me can -- so;~Eu
        es -- | tan -- do com e -- le;~Eu en --
      } \alternative {
        { | tro no ba -- lan -- ço. }
        { | tro no ba -- lan -- | ço. }
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        E eu ba -- lan -- | ço,
        e eu ba -- lanço;
        Nes -- ta | for -- ça Di -- vi -- na; Eu
      } \alternative {
        { | nun -- ca me can -- | so. }
        { | nun -- ca me can -- so. }
      }
      \set stanza = "2.A"
      \repeat volta 2 {
        Ve -- nho | di -- zer a meu Mestre,
        que~eu es -- | tou sa -- tis -- feito;
        Pe -- lo | meu co -- ra -- ção há | qua -- ren -- ta a -- nos; Ba --
      } \alternative {
        { | ten -- do~em meu pei -- to. }
        { | ten -- do~em meu pei -- | to. }
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        E eu ba -- lan -- ço,
        co -- ra -- | ção se -- gue ba -- ten -- do;
        Com | meu São Jo -- ão; Vou a --
      } \alternative {
        { | le -- gre vi -- ven -- | do. }
        { | le -- gre vi -- ven -- do. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | a2:m g | g1
      } \alternative {
        { | g2:7 c4 }
        { | g2:7 c2 | c8~ }
      }
      \repeat volta 2 {
        c4.~ c2 | c2 g2 | g1
      } \alternative {
        { | g2:7 c2 | s8 }
        { | g2:7 c4 }
      }
      \repeat volta 2 {
        s4 | c1 | a2:m g2 | g1 g1
      } \alternative {
        { | g2:7 c4 }
        { | g2:7 c2 | c8~ }
      }
      \repeat volta 2 {
        c4.~ c2 | c2 g2 | g1
      } \alternative {
        { | g2:7 c2 | s8 }
        { | g2:7 c4 }
      }
    }
    \layout { #(layout-set-staff-size 13) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    Being with the Daime I never get tired
    Being with Him I start shaking
    And I shake, and I shake
    In this Divine Force and I never get tired
    \nextverse
    I come to tell my Master that I am satisfied
    With my heart, since forty years beating in my chest
    And I shake and the heart goes on beating
    And with my Saint John, joyful I go on living
  \end{translation}
\endsong


\beginsong{Professor de Estrela}[by={Odemir Raulino Da Silva},key={Dm},gk={Dm, Cm, Em}]
  \ifshowlilypond%
    \vspace*{-.75ex} % an ugly hack to fit the whole song on one spread
  \fi
  \audio{https://www.nossairmandade.com/hymn/1557/ProfessorDeEstrela}
  \mnbeginchorus
    |\[A] \[\mn{A}]O Daime é \[\bm]meu profes|\[\mnc{A}Dm]sor \[\bm] \altchords{\id[1]{(Cm)}|G |Cm}
    |\hspace{0.5em} Ele \[\bm]es\[\mn{B&}]tá \[\mn{A}]de |\[\mnc{G}Gm]o\[\bmc\mn{E}]lho \altchords{| - |Fm}
    |\hspace{0.5em} \[\mn{G}]Ele \[\bm]es\[\mn{A}]tá \[\mn{G}]de |\[\mnc{F}Dm]o\[\bmc\mn{D}]lho \altchords{| - |Cm}
    |\hspace{0.5em} \[\mn{F}]Ele \[\bm]es\[\mn{G}]tá \[\mn{F}]de |\[\mnc{E}A]o\[\bm]lho \altchords{| - |G}
    |\hspace{0.5em} Na \[\bm]mi\[\mn{D}]nha \[\mn{C#}]mu|\[\mnc{B&}B&]dan\[\mnc{A}A]ça \altchords{| - |A\flt{} G}
  \mnendchorus
  \mnbeginchorus
    |\[A] \[\mn{A}]Daime é \[\bm]meu profes|\[\mnc{A}Dm]sor \[\bm] \altchords{|G |Cm}
    |\hspace{0.5em} Sempre \[\bm]es\[\mn{B&}]tá \[\mn{A}]de |\[\mnc{G}Gm]o\[\bmc\mn{E}]lho \altchords{| - |Fm}
    |\hspace{0.5em} \[\mn{G}]Sempre \[\bm]es\[\mn{A}]tá \[\mn{G}]de |\[\mnc{F}Dm]o\[\bmc\mn{D}]lho \altchords{| - |Cm}
    |\hspace{0.5em} \[\mn{F}]Sempre \[\bm]es\[\mn{G}]tá \[\mn{F}]de |\[\mnc{E}A]o\[\bm]lho \altchords{| - |G}
    |\hspace{0.5em} Na \[\bm]mi\[\mn{D}]nha es\[\mn{C#}]pe|\[\mnc{E}A7]ran\[\mnc{D}Dm]ça \altchords{| - |G7 Cm}
  \mnendchorus
  \mnbeginchorus
    \ind |\[Dm] \[\mn{D}]És gran\[\bm]de profes|\[\mnc{B&}B&]sor\[\bm] \altchords{|Cm |A\flt{}}
    \ind |\hspace{0.5em} \[\mn{D}]De pa\[\bm]lavra \[\mn{E}]ver\[\mn{D}]da|\[\mnc{A}A]dei\[\bm]ra \altchords{| - |G}
    \ind |\hspace{0.5em} \[\mn{A}]Obri\[\bm]ga\[\mn{B&}]do \[\mn{A}]Se|\[\mncii{G}{E}Gm]nhor \altchords{| - |Fm}
    \ind |\[A] Profes\[\bm]sor \[\mn{D}]de \[\mn{C#}]es|\[\mnc{E}A7]tre\[\mnc{D}Dm]la \altchords{|G |G7 Cm}
  \mnendchorus
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    Daime is my teacher, he is watching, he is watching,
    he is watching over my change (transformation)
    \nextverse
    Daime is my teacher, he is always watching, he is always watching,
    he is always watching over my hope (expectation)
    \nextverse
    He is a great teacher of the truthful word
    Thank you Lord, teacher of stars
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva on 2021-08
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() % \slurDashed
      \key d \minor \time 4/4
      \repeat volta 2 {
        | r8 a8\sectionmark "1." 8 8 4 8 8 | a'1~ | a4
        a8 a8 a4 bes8 a8 | g2 e2~ | e4
        g8 g8 g4 a8 g8 | f2 d2~ | d4
        f8 f8 f4 g8 f8 | e2 e2~ | e4.
        e8 e4 d8 cis8 | bes2 a2
      } \break
      \repeat volta 2 {
        | r4 a8\once\tweak X-offset #.8 \posectionmark "2." 8 4 8 8 | a'1~ | a4
        a8 a8 a4 bes8 a8 | g2 e2~ | e4
        g8 g8 g4 a8 g8 | f2 d2~ | d4
        f8 f8 f4 g8 f8 | e2 e2~ | e4.
        e8 e4 d8 cis8 | e2 d2
      } \break
      \repeat volta 2 {
        | r4 d8\once\tweak X-offset #1 \sectionmark "3." d8 d4 d8 d8 | bes1~ | bes4 d8 d d d e d
        | a2 a2~ | a4
        a'8 a8 a4 bes8 a8 | g2( e2)~ | e4
        e8 e8 e4 d8 cis8 | e2 d2~
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      O Dai -- me~é meu pro -- fes -- | sor; __
      | _ E -- le es -- tá de | o -- lho; __
      | _ E -- le es -- tá de | o -- lho; __
      | _ E -- le es -- tá de | o -- lho; __
      | _ Na mi -- nha mu -- | dan -- ça.
      \set stanza = "2."
      Dai -- me meu pro -- fes -- | sor; __
      | _ Sem -- pre es -- tá de | o -- lho; __
      | _ Sem -- pre es -- tá de | o -- lho; __
      | _ Sem -- pre es -- tá de | o -- lho; __
      | _ Na mi -- nha~es -- pe -- | ran -- ça.
      \set stanza = "3."
      És gran -- de pro -- fes -- | sor; __
      | _ De pa -- la -- vra ver -- da -- | dei -- ra; __
      | _ O -- bri -- ga -- do Se -- | nhor; __ _
      | _ Pro -- fes -- sor de es -- | tre -- la.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        | a1 | d1:m | d1:m | g:m | g:m
        | d:m | d:m | a | a1 | bes2 a2
      }
      \repeat volta 2 {
        | a1 | d1:m | d1:m | g:m | g:m
        | d:m | d:m | a | a1 | a2:7 d2:m
      }
      \repeat volta 2 {
        | d1:m | bes1 | bes1 | a1 | a1
        | g1:m | a1 | a2:7 d2:m
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Em Minha Memória}[by={Padr. Valdete},key={Am},gk={Cm, Bm, Am}]
  \audio{https://www.nossairmandade.com/hymn/141/EmMinhaMem\%C3\%B3ria}
  \mnbeginchorus
    \[\mn{A}]Eu to\[\mn{C}]mo |\[\mnc{E}Am]Daime para \[\bmc\mn{C}]ver os \[\mn{B}]meus de|\[\mn{A}]feitos\[\bm] \altchords{\id[1]{(Cm)}|Cm | \e }
    \[\mn{A}]Eu to\[\mn{C}]mo |\[\mn{E}]Daime para \[\bmc\mn{C}]eu \[\mn{A}]me cor\[\mn{C}]ri|\[\mnc{E}E]gir \[\bm] \altchords{| - |G}
    \mnendchorus\glueverses\mnbeginchorus
    \[\mn{A}]Não to\[\mn{C}]mo |\[\mnc{E}Am]Daime para \[\bmc\mn{C}]me en\[\mn{B}]grande|\[\mn{A}]cer\[\bm] \altchords{|Cm | \e}
    Porque \[\mn{B}]o |\[\mnc{C}F]grande é Je\[\bmc\mnc{B}E7]sus, es\[\mn{E}]tá a|\[\mnc{A}Am]quí \[\bm] \altchords{|A\flt{} G7 |Cm}
  \mnendchorus
  \mnbeginchorus
    \[\mn{A}]Eu to\[\mn{C}]mo |\[\mnc{E}Am]Daime é para a\[\bmc\mn{C}]cender \[\mn{B}]minha |\[\mn{A}]Luz\[\bm]
    E es\[\mn{B}]ta |\[\mn{C}]Luz meu Je\[\bmc\mn{B}]sus \[\mn{A}]é quem \[\mn{C}]me |\[\mnc{E}E]dá \[\bm]
    \mnendchorus\glueverses\mnbeginchorus
    \[\mn{A}]Por is\[\mn{C}]so eu |\[\mnc{E}Am]devo consa\[\bmc\mn{C}]grar no \[\mn{B}]cora|\[\mn{A}]ção\[\bm]
    \[\mn{A}]Que tam\[\mn{B}]bém |\[\mnc{C}F]é da Vir\[\bmc\mnc{B}E7]gem da \[\mn{E}]Concei|\[\mnc{A}Am]ção \[\bm]
  \mnendchorus
  \mnbeginchorus
    \[\mn{A}]Eu to\[\mn{C}]mo |\[\mnc{E}Am]Daime e consi\[\bmc\mn{C}]dero \[\mn{B}]este |\[\mn{A}]vinho\[\bm]
    O mes\[\mn{B}]mo |\[\mn{C}]vinho que Je\[\bmc\mn{B}]sus \[\mn{A}]deu pra \[\mn{C}]to|\[\mnc{E}E]mar \[\bm]
    \mnendchorus\glueverses\mnbeginchorus
    \[\mn{A}]Aos Seus \[\mn{C}]a|\[\mnc{E}Am]póstoles dis\[\bm]se: em \[\mn{C}]minha \[\mn{B}]me|mó\[\mn{A}]ria\[\bm]
    \[\mn{A}]Que é pa\[\mn{B}]ra |\[\mnc{C}F]sempre esta \[\bmc\mnc{B}E7]Luz nun\[\mn{E}]ca fal|\[\mnc{A}Am]tar \[\bm]
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        a8\sectionmark "1.A" a c | e e e e c c b b | a4 a4. a8 a8 c8
        | e8 e e e c a a c | e2~ e8
      } \break
      \repeat volta 2 {
        a,8\sectionmark "1.B" a c | e e e e c c b b | a2~ a8 a a b
        | c8. c16 c8 c8 b8 b8 e8 e8 | a,2~ a8
      } \break
      \repeat volta 2 {
        a8\sectionmark "2.A" a c | e e e e c c b b | a2~ a8 a a b
        | c4 c8 c b a a c | e2~ e8
      } \break
      \repeat volta 2 {
        a,8\sectionmark "2.B" a c | e e e e c c b b | a2~ a8 a a b
        | c4 c8 c b b e e | a,2~ a8
      } \break
      \repeat volta 2 {
        a8\posectionmark "3.A" a c | e e e e c c b b | a4 a4. a8 a b
        | c c c c b a a c | e2~ e8
      } \break
      \repeat volta 2 {
        a,8\sectionmark "3.B" a c | e e e e e c c b | b4 a4. a8 a b
        | c8. c16 c8 c b b e e | a,2~ a8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Eu to -- mo | Dai -- me pa -- ra ver os meus de -- | fei -- tos;
      Eu to -- mo | Dai -- me pa -- ra eu me cor -- ri -- | gir.
      \set stanza = "1.B"
      Não to -- mo | Dai -- me pa -- ra me en -- gran -- de -- | cer;
      Por -- que o | gran -- de é Je -- sus, es -- tá a -- | quí.
      \set stanza = "2.A"
      Eu to -- mo | Dai -- me~é pa -- ra~a -- cen -- der mi -- nha | Luz;
      E es -- ta | Luz meu Je -- sus é quem me | dá.
      \set stanza = "2.B"
      Por is -- so~eu | de -- vo con -- sa -- grar no co -- ra -- | ção;
      Que tam -- bém | é da Vir -- gem da Con -- cei -- | ção.
      \set stanza = "3.A"
      Eu to -- mo | Dai -- me~e con -- si -- de -- ro es -- te | vi -- nho;
      O mes -- mo | vi -- nho que Je -- sus deu pra to -- | mar.
      \set stanza = "3.B"
      Aos Seus a -- | pós -- to -- les dis -- se:~em mi -- nha me -- | mó -- ria;
      Que~é pa -- ra | sem -- pre es -- ta Luz nun -- ca fal -- | tar.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1:m | a1:m | a1:m | e2~ 8
      }
      \repeat volta 2 {
        s4. | a1:m | a1:m | f2 e2:7 | a2:m~ 8
      }
      \repeat volta 2 {
        s4. | a1:m | a1:m | a1:m | e2~ 8
      }
      \repeat volta 2 {
        s4. | a1:m | a1:m | f2 e2:7 | a2:m~ 8
      }
      \repeat volta 2 {
        s4. | a1:m | a1:m | a1:m | e2~ 8
      }
      \repeat volta 2 {
        s4. | a1:m | a1:m | f2 e2:7 | a2:m~ 8
      }
    }
    \layout { #(layout-set-staff-size 11) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}
    I drink Daime to see my flaws
    I drink Daime to correct myself
    I don't drink Daime to exalt myself
    Because the Great is Jesus and He's here
    \nextverse
    I drink Daime to light my flame
    And this light, Jesus gives it to me
    I must consecrate in my heart
    For it belongs to the Virgin of Conception
    \nextverse
    I drink Daime and consider this wine
    The same wine Jesus offered his apostle4s
    To His apostles he said: ''in my memory''
    So that forever you will have this light
  \end{translation}
\endsong


\beginsong{Daime Ele é a Vida}[by={Maria Brilhante},key={C},gk={D, C}]
  \audio{https://www.nossairmandade.com/hymn/37/DaimeEle\%C3\%89AVida}
  \mnbeginchorus
    |\[\mnc{C}C]Daime ele é a \[\bm]vi\[\mn{G}]da \altchords{\id[1]{(D)}|D}
    |\[\mnc{E}Am]Daime ele é \[\mn{D}]o a\[\bmc\mn{E}]mor \altchords{|Bm}
    |\[\mnc{G}C]Daime ele é Je\[\bm]sus \altchords{|D}
    \[\mn{C}]O nos|\[\mnc{E}G7]so Pai \[\mn{D}]cria\[\bmc\mnc{C}C]dor \altchords{|A7 D}
  \mnendchorus
  \mnbeginchorus\memorize
    \ind \[^\mn{G}]Da|\[\mnc{C}C]qui estou te \[\bm]ven\[^\mn{G}]do \altchords{|D}
    \ind \[^\mn{E}]Daqui |\[Am]es\[^\mn{D}]tou \[^\mn{F}]te \[^\mn{E}]o\[\bmc\mnc{D}G]lhando \altchords{|Bm A}
    \ind \[^\mn{G}]Esta|mos \[^\mn{F}]nu\[^\mn{E}]ma \[^\mn{D}]ba\[\bmc\mnc{C}C]talha \altchords{| - D}
    \ind \[^\mn{G}]Da Vir|\[\mnc{C}F]gem \[^\mn{B}]Mãe \[^\mn{A}]So\[^\mn{B}]be\[\bmc\mnc{C}C]rana \altchords{|G D}
  \mnendchorus
  \notesoff
  \beginchorus
    \ind Eu |^peço a Jesus ^Cristo \altchords{|D}
    \ind E ao meu |^Senhor São Jo^ão \altchords{|Bm A}
    \ind A mi|nha Senhora ^Mãe \altchords{| - D}
    \ind Segu|^rai a minha ^mão \altchords{|G D}
  \endchorus
  \begin{translation}
    Daime He’s the life, Daime He’s the love
    Daime He is Jesus, our Father Creator
    \nextverse
    From here I see you, from here I look at you
    We are in a battle of the Virgin Sovereign Mother
    \nextverse
    I ask of Jesus Christ and my Lord Saint John
    My Lady Mother, hold my hand
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \key c \major \time 4/4 \partial 8
      \repeat volta 2 {
        r8\sectionmark "1." | c8 c c c c4 g4 | e'8 e e d e2
        | g8 g g g g4 c,8 c | e8 e d d c4.
      } \break
      \repeat volta 2 {
        g8\sectionmark "2." | c8 c c c c g e' e | e d f e d d g g
        | g f e d c c g g | c b a b c4 c8
      } \break
      \repeat volta 2 {
        g8\posectionmark "3." | c8 c c c c g e' e | e d f e d4 g8 g
        | g f e d c4 g8 g | c b a b c4 c8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      | Dai -- me~e -- le~é a vi -- da;
      | Dai -- me~e -- le~é o~a -- mor;
      | Dai -- me~e -- le~é Je -- sus;
      O nos -- | so Pai cri -- a -- dor.
      \set stanza = "2."
      Da -- | qui es -- tou te ven -- do;
      Da -- qui | es -- tou te o -- lhan -- do;
      Es -- ta -- | mos nu -- ma ba -- ta -- lha;
      Da Vir -- | gem Mãe So -- be -- ra -- na.
      \set stanza = "3."
      Eu | pe -- ço~a Je -- sus Cris -- to;
      E~ao meu | Se -- nhor São Jo -- ão;
      A mi -- | nha Se -- nho -- ra Mãe;
      Se -- gu -- | rai a mi -- nha mã -- o.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | c1 | a:m | c | g2:7 c4.
      }
      \repeat volta 2 {
        s8 | c1 | a2:m g2 | g2 c | f c4.
      }
      \repeat volta 2 {
        s8 | c1 | a2:m g2 | g2 c | f c4.
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{O Santo Daime Está Aí}[by={Francisco Grangeiro},key={Am},gk={Gm, Am}]
  \audio{https://www.youtube.com/watch?v=tVT77jI-jzw}
  \newchords{chords_osantodaimeestaai_a}\newchords{chords_osantodaimeestaai_b}
  \mnbeginchorus\memorize[chords_osantodaimeestaai_a]
    \[^\mn{E}]O Santo |\[Am]Daime es\[\bm]tá a|\[\mnc{C}F]í \altchords{\id[1]{(Gm)}|Gm |E\flt{}}
    É \[\bm]pa\[^\mn{A}]ra |\[\mnc{E}E]todos \[\bmc\mn{C}]nós \[^\mn{B}]to|\[\mnc{A}Am]mar \[\bm] \altchords{|D |Gm}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_osantodaimeestaai_b]
    \[^\mn{A}]O San\[^\mn{C}]to |\[\mnc{E}Am]Daime é \[\bmc\mn{D}]um \[^\mn{C}]pri|\[\mnc{B}E]mor \altchords{|Gm |D}
    Pa\[\bm]ra \[^\mn{F}]quem |\[\mnc{E}E7]sa\[^\mn{D}]be a\[\bmc\mn{C}]pre\[^\mn{B}]ci|\[\mnc{A}Am]ar \[\bm] \altchords{|D7 |Gm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_osantodaimeestaai_a]
    Não sa|^bendo a^preci|^ar
    Qua^se não a|^dian^ta to|^mar ^
    \endchorus\glueverses\beginchorus\replay[chords_osantodaimeestaai_b]
    Passa |^por ci^ma de |^tudo
    ^E na|^da po^de alcan|^çar ^
  \endchorus
  \beginchorus\replay[chords_osantodaimeestaai_a]
    Antigui|^dade não ^é ri|^queza \altchords{\id[2]{(Em)}|Em |C}
    An^tigui|^dade não ^é sa|^ber ^ \altchords{|B |Em}
    \endchorus\glueverses\beginchorus\replay[chords_osantodaimeestaai_b]
    De que |^serve a an^tigui|^da^de \altchords{|Em |B}
    Não |^saber ^compreen|^der ^ \altchords{|B7 |Em}
  \endchorus
  \beginchorus\replay[chords_osantodaimeestaai_a]
    A fir|^meza é ^muito |^boa
    ^Sem fir|^meza ^não se |^vai ^
    \endchorus\glueverses\beginchorus\replay[chords_osantodaimeestaai_b]
    Se |^não ti^ver fir|^meza
    ^Daqui |^da ter^ra não |^sai ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-08
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize e8\posectionmark "A" e e | e4 e8 e8 e4 e | c'4. 8 c4 a
        | e4 e c b | a2~ 8
      }
      \repeat volta 2 {
        \parenthesize a8\posectionmark "B" a( c) | e4 e8( e) d4 c | b4.( b8) b4 f'4
        | e d c b | a2~ 8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        O San -- to | Dai -- me es -- tá a -- | í;
        É pa -- ra | to -- dos nós to -- | mar. __ _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        O San -- to | Dai -- me é um pri -- | mor;
        Pa -- ra quem | sa -- be~a -- pre -- ci -- | ar. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        \skip 1 Não sa -- | ben -- do a -- pre -- ci -- | ar;
        Qua -- se não~a -- | di -- an -- ta to -- | mar. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 Pas -- sa | por ci -- _ ma de | tu -- do;
        E na -- | da po -- de~al -- can -- | çar. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        An -- ti -- gui -- | da -- de não é ri -- | que -- za~An --
        ti -- gui -- | da -- de~não é sa -- | ber. __ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 De que | ser -- ve a~an -- ti -- gui -- | da -- _ de;
        Não | sa -- ber com -- preen -- | der. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        \skip 1 A fir -- | me -- za é mui -- to | bo -- a;
        Sem fir -- | me -- za não se | vai. __ _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        \skip 1 Se __ _ | não ti -- _ ver fir -- | me -- za;
        Da -- qui | da ter -- ra não | sai. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1:m | f1 | e1 | a2:m~ 8
      }
      \repeat volta 2 {
        s4. | a1:m | e1 | e1:7 | a2:m~ 8
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Santo Daime is there, it is for all to take
    Santo Daime is a perfection for those who know how to appreciate
    \nextverse
    Not knowing how to appreciate, it hardly advantages one to take it
    One passes over everything and obtains nothing
    \nextverse
    Antique is not wealth, antique is not knowledge
    What good for is antiquity and not to know how to understand
    \nextverse
    Firmness is verygood, without firmness one doesn't go
    If you don't have firmness, you can't get out from this earth
  \end{translation}
\endsong

