% Santo Daime: Cura I
% ===================
%
\audio[title={Nossa Irmandade}]{https://www.nossairmandade.com/hinario/2/CuraI}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Pai Nosso}[by={Padr. Sebastião},key={Am},sks={Bm, Cm, Dm}]
  \audio{https://www.nossairmandade.com/hymn/53/PaiNosso}
  \newchords{chords_painosso_a}\newchords{chords_painosso_b}
  \mnbeginchorus\memorize[chords_painosso_a]
    \[^\mn{A}]Pai |\[\mnc{C}C]Nosso que es\[\bmc\mn{D}]tá \[^\mn{C}]no |\[\mnc{A}Am]céu \altchords{\id[1]{(Bm)}|D |Bm}
    San\[\bmc\mn{C}]ti\[^\mn{E}]fi|\[\mnc{C}C]cado é \[^\mn{B}]nos\[\mnc{A}Am]so \[^\mn{C}]Se|\[\mnc{E}Em]nhor\[\bm] \altchords{|D Bm |F\#m}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_painosso_b]
    \[^\mn{D}]Aprovei|\[Dm]tando a o\[\bm]ca\[^\mn{C}]si|\[\mnc{A}Am]ão \altchords{|Em |Bm}
    Meu \[\bmc\mn{C}]Mes\[^\mn{E}]tre é |\[\mnc{C}C]Rei s\[^\mn{B}]u\[\mnc{A}Am]pe\[^\mn{C}]ri|\[C]or \[\bm] \altchords{|D Bm |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_painosso_a]
    Oh |^minha ^Virgem |^Mãe
    As ^suas |^lágrimas ^derra|^mou ^
  \mnendchorus\glueverses\mnbeginchorus\replay[chords_painosso_b]
    A|^queles ^que não |^amam
    ^Vão sen|^tir a ^mesma |^dor ^
  \endchorus
  \beginchorus\replay[chords_painosso_a]
    Meu |^Mestre es^tá co|^migo
    E^le é |^Mestre en^sina|^dor ^
  \mnendchorus\glueverses\mnbeginchorus\replay[chords_painosso_b]
    Jun|^{to com} a ^Virgem |^Mãe
    O ^nosso |^Pai foi ^quem man|^dou ^
  \endchorus
  \beginchorus\replay[chords_painosso_a]
    Nin|^guém sa^be o que |^diz
    E ^nem sa|^bem o que es^tão di|^zen^do
  \mnendchorus\glueverses\mnbeginchorus\replay[chords_painosso_b]
    Com o po|^der do ^nosso |^Pai
    O ^relho a|^gora es^{tá co}|^men^do
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        r8\posectionmark "A" a4 | c4 c8( c8) d4 c | a4. a8 c4 e | c c8 b a4 c | e2~ e8
      }
      \repeat volta 2 {
        \parenthesize d8\sectionmark "B" d( d) | d4 d8( d8) d4 c4 | a4. a8 c4 e | c4 c8( b8) a4 c4 | c2~ c8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Pai | Nos -- so que~es -- tá no | céu;
      San -- ti -- fi -- | ca -- do~é nos -- so Se -- | nhor. __ _
      \set stanza = "1.B"
      A -- pro -- vei -- | tan -- do~a o -- ca -- si -- | ão;
      Meu Mes -- tre~é | Rei su -- _ pe -- ri -- | or. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Oh | mi -- nha __ _ Vir -- gem | Mãe;
      As su -- as | lá -- gri -- mas der -- ra -- | mou. __ _
      \set stanza = "2.B"
      \skip 1 A -- _ | que -- les __ _ que não | a -- mam;
      Vão sen -- | tir a __ _ mes -- ma | dor. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Meu | Mes -- tre es -- tá co -- | mi -- go;
      Ele é | Mes -- tre en -- si -- na -- | dor. __ _
      \set stanza = "3.B"
      \skip 1 Jun -- _ | to com a Vir -- gem | Mãe;
      O nos -- so | Pai foi __ _ quem man -- | dou. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      Nin -- | guém sa -- _ be~o que | diz;
      E nem sa -- | bem o que~es -- tão di -- | zen -- do.
      \set stanza = "4.B"
      Com o po -- | der do __ _ nos -- so | Pai;
      O re -- lho~a -- | go -- ra es -- tá co -- | men -- do.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1 | a:m | c2 a2:m | e2:m~ e8:m
      }
      \repeat volta 2 {
        s4. | d1:m | a:m | c2 a:m | c2~ c8
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better division
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Our father who art in heaven, hallowed is our Lord
    Using the occasion, my Master is superior King
    \nextverse
    Oh! My Virgin Mother, your tears were shed
    Those who do not love are going to feel the same pain
    \nextverse
    My Master is with me, he is the Master teacher
    Together with the Virgin Mother, it was ordered by our father
    \nextverse
    No one knows what they say, nor do they know what they're saying
    With the power of our Father, now the whip is in full swing
  \end{translation}
\endsong


\beginsong{Eu Chamei Meu Mestre}[by={Padr. Sebastião},key={C},sks={D, C, E}]
  \audio{https://www.nossairmandade.com/hymn/54/EuChameiMeuMestre}
  \newchords{chords_euchameimeumestre_a}\newchords{chords_euchameimeumestre_b}
  \mnbeginchorus\memorize[chords_euchameimeumestre_a]
    |\[\mnc{C}C]Eu \[^\mn{A}]cha\[\mnc{D}G]mei \[^\mn{C}]meu |\[C]Mes\[\bm]tre \[^\mn{G}]em |\[\mncii{E}{C}Am]no\[^\mn{E}]me \[\mnc{D}Dm]da \[^\mn{C}]ver|\[\mnc{E}Em]da\[\bm]de
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_euchameimeumestre_b]
    \[^\mn{G}]Que |\[\mnc{E}Am]a \[^\mn{C}]ver\[\mnc{D}Dm]da\[^\mn{C}]de é |\[\mnc{G}G]Deus\[\bm], \[^\mn{E}]o |\[\mnc{C}C]rei \[^\mn{A}]da \[\mnc{D}G]ca\[^\mn{C}]ri|\[C]da\[\bm]de
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_euchameimeumestre_a]
    |^Eu pe^ço a meu |^Mes^tre de |^todo meu ^cora|^ção ^
    \endchorus\glueverses\beginchorus\replay[chords_euchameimeumestre_b]
    Meu |^Mestre tenha ^pie|^da^de, |^abra nos^sa ses|^são ^
  \endchorus
  \beginchorus\replay[chords_euchameimeumestre_a]
    As|^sim está a^conte|^cen^do, dei|^xa ficar ^como es|^tá ^
    \endchorus\glueverses\beginchorus\replay[chords_euchameimeumestre_b]
    Que é |^para ^conhe|^ce^rem, sa|^berem me ^respei|^tar ^
  \endchorus
  \beginchorus\replay[chords_euchameimeumestre_a]
    Já |^disse e tor^no a di|^zer^, não |^querem a^credi|^tar ^
    \endchorus\glueverses\beginchorus\replay[chords_euchameimeumestre_b]
    Le|^vanto a mi^nha ses|^são ^ para o |^reino ce^lesti|^al ^
  \endchorus
  \beginchorus\replay[chords_euchameimeumestre_a]
    Meus ir|^mãos va^mos o|^rar^, ro|^gar e va^mos pe|^dir ^
    \endchorus\glueverses\beginchorus\replay[chords_euchameimeumestre_b]
    Para le|^varmos es^ta ver|^da^de que o |^Mestre dei^xou a|^qui ^
  \endchorus
  \beginchorus\replay[chords_euchameimeumestre_a]
    Todos |^querem ^ser fe|^liz^, cada |^um só ^quer pra |^si ^
    \endchorus\glueverses\beginchorus\replay[chords_euchameimeumestre_b]
    Di|^zendo que es^tão co|^mi^go, es|^tão lon^ge de |^mim ^
  \endchorus
  \beginchorus\replay[chords_euchameimeumestre_a]
    Eu |^não dei^xei as|^sim^, dei|^xei foi pa^ra ajun|^tar ^
    \endchorus\glueverses\beginchorus\replay[chords_euchameimeumestre_b]
    Não fi|^zeram ^como eu |^dis^se, fi|^zeram foi ^espa|^lhar ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        \parenthesize e8( \posectionmark "A" \parenthesize e8) | c8( c c) a8 d4. c8 | c2( c4) g'8( g) | e8( c4) e8 d4. c8 | e2( e4)
      }
      \repeat volta 2 {
        \grace{\altcol\parenthesize g8\altmark "5." } g8( \sectionmark "B" g) | e8( e e) c d4. c8 | g2( g4) e'8( e) | c4( c8) a8 d4. c8 | c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 \skip 1 | Eu __ _ _ cha -- mei meu | Mes -- tre
        em __ _ | no -- _ me da ver -- | da -- de.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        \skip 1 Que __ _ | a __ _ _ ver -- da -- de~é | Deus, __ _
        o __ _ | rei __ _ da ca -- ri -- | da -- de.
      }
    }
    theLyricsTwo = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "2."
      \repeat volta 2 {
        \skip 1 \skip 1 | Eu __ _ _ pe -- ço~a meu | Mes -- tre
        de __ _ | to -- do meu co -- ra -- | ção. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 Meu __ _ | Mes -- tre te -- nha pi -- e -- | da -- de, \skip 1 \skip 1
        | a -- bra nos -- sa ses -- | são. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "3."
      \repeat volta 2 {
        As -- _ | sim es -- tá a -- con -- te -- | cen -- do,
        dei -- _ | xa fi -- car co -- mo~es -- | tá. __ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 Que é | pa -- _ _ ra co -- nhe -- | ce -- rem,
        sa -- _ | be -- rem me res -- pei -- | tar. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "4."
      \repeat volta 2 {
        Já __ _ | dis -- se e tor -- no~a di -- | zer, __ _
        não __ _ | que -- rem a -- cre -- di -- | tar. __ _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        \skip 1 Le -- _ | van -- _ to~a mi -- nha ses -- | são __ _
        pa -- ra~o | rei -- no ce -- les -- ti -- | al. __ _
      }
    }
    theLyricsFive = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "5."
      \repeat volta 2 {
        Meus ir -- | mã -- _ os va -- mos o -- | rar, __ _
        ro -- _ | gar e va -- mos pe -- | dir. __ _
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        \altcol Pa -- ra le -- | var -- _ mos es -- ta ver -- | da -- de
        que o | Mes -- tre dei -- xou a -- | qui. __ _
      }
    }
    theLyricsSix = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "6."
      \repeat volta 2 {
        To -- dos | que -- _ _ rem ser fe -- | liz, __ _
        ca -- da | um __ _ só quer pra | si. __ _
      }
      \set stanza = "6.B"
      \repeat volta 2 {
        \skip 1 Di -- _ | zen -- do que es -- tão co -- | mi -- go,
        es -- _ | tão __ _ lon -- ge de | mim. __ _
      }
    }
    theLyricsSeven = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "7."
      \repeat volta 2 {
        Eu __ _ | não __ _ _ dei -- xei as -- | sim, __ _
        dei -- _ | xei foi pa -- ra~a -- jun -- | tar. __ _
      }
      \set stanza = "7.B"
      \repeat volta 2 {
        \skip 1 Não fi -- | ze -- _ _ ram co -- mo~eu | dis -- se,
        fi -- _ | ze -- ram foi es -- pa -- | lhar. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 g | c1
        | a2:m d:m | e2.:m
      }
      \repeat volta 2 {
        \grace s8 s4 | a2:m d:m | g1
        | c2 g | c2.
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better division
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I called my Master in the name of the truth
    Because the truth is God, the King of charity
    \nextverse
    I ask my Master with all of my heart
    My Master have mercy, open our session
    \nextverse
    This is how it's happening, leave it as it is
    So that all know, know how to respect me
    \nextverse
    I have said and I say it again: you don't want to believe
    I raise up my session to the Celestial Kingdom
    \nextverse
    My brothers and sisters, let's pray; implore, and let's ask
    For us to take this truth that the Master left here
    \nextverse
    Everyone wants to be happy, each one only wants this for oneself
    Saying that they are with me they are far from me
    \nextverse
    I didn't leave things this way, I left things so they could gather.
    They didn't do as I said, what they did was scatter.
  \end{translation}
\endsong


\beginsong{Chamei o Mestre Juramidam}[by={Padr. Sebastião},key={C},sks={D, C, E}]
  \audio{https://www.nossairmandade.com/hymn/55/ChameiOMestreJuramidam}
  \mnbeginchorus\memorize
    \[^\mn{G}]Chamei o |\[\mnc{C}C]Mes\[^\mn{G}]tre \[^\mn{C}]Jurami|\[\mnc{E}Am]dam \altchords{\id[1]{(D)}|D |Bm}
    \[^\mn{C}]Pa\[^\mn{E}]ra o |\[\mnc{G}G]meu \[^\mn{C}]Mes\[\mnc{E}Em]tre \[^\mn{G}]vir |\[\mnc{C}C]cá \altchords{|A F\#m |D}
  \mnendchorus
  \notesoff
  \beginchorus
    Com su|^a força di|^vina
    Para |^vir me ^liber|^tar
  \endchorus
  \beginchorus
    Dai-me |^força, dai-me a|^mor
    Para eu |^poder ^domi|^nar
  \endchorus
  \beginchorus
    Meu |^Mestre em sua |^corte
    Em seu |^trono ^divi|^nal
  \endchorus
  \beginchorus
    Tudo |^tem, tudo |^dá
    Com su|^a luz ^de cris|^tal
  \endchorus
  \beginchorus
    Sou pe|^queno, sou pe|^queno
    É a |^quem eu ^devo pe|^dir
  \endchorus
  \beginchorus
    Todos |^têm, todos |^têm
    Todos |^têm, po^dem se|^guir
  \endchorus
  \beginchorus
    Aqui |^eu vou decla|^rar
    A quem o |^Mestre ^entre|^gou
  \endchorus
  \beginchorus
    Quem |^ama e sabe a|^mar
    Segue |^na estrada ^do a|^mor
  \endchorus
  \beginchorus
    Meu |^Mestre me de|^clare
    Como |^é que ^vai fi|^car
  \endchorus
  \beginchorus
    Preste aten|^ção no que eu já |^disse
    Quem ven|^cer é que ^vai bri|^lhar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize g8\pomark g g | c2 \parenthesize g8 c c c | e2( e4) \grace \parenthesize c8 c8 e | g4. c,8 e4. g,8 | c2~ c8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Cha -- mei o | Mes -- tre Ju -- ra -- mi -- | dam; __ _
        Pa -- ra~o | meu Mes -- tre vir | cá. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        \skip 1 Com su -- | a \skip 1 for -- ça di -- | vi -- na;
        Pa -- ra | vir me li -- ber -- | tar. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        \skip 1 Dai -- me | for -- ça, dai -- me a -- | mor; __ _
        Pa -- ra~eu | po -- der do -- mi -- | nar. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        \skip 1 Meu __ _ | Mes -- tre em su -- a | cor -- te;
        Em seu | tro -- no di -- vi -- | nal. __ _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \repeat volta 2 {
        \skip 1 Tu -- do | tem, \skip 1 \skip 1 tu -- do | dá; __ _
        Com su -- | a luz de cris -- | tal. __ _
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      \repeat volta 2 {
        \skip 1 Sou pe -- | que -- no, \skip 1 sou pe -- | que -- no;
        É a | quem eu devo pe -- | dir. __ _
      }
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7."
      \repeat volta 2 {
        \skip 1 To -- dos | têm, \skip 1 \skip 1 to -- dos | têm; __ _
        To -- dos | têm, po -- dem se -- | guir. __ _
      }
    }
    theLyricsEight = \lyricmode {
      \set stanza = "8."
      \set includeGraceNotes = ##t
      \repeat volta 2 {
        \skip 1 A -- qui | eu \skip 1 vou de -- cla -- | rar; __ _
        \parenthesize A quem o | Mes -- tre en -- tre -- | gou. __ _
      }
      \set includeGraceNotes = ##f
    }
    theLyricsNine = \lyricmode {
      \set stanza = "9."
      \repeat volta 2 {
        \skip 1 Quem __ _ | a -- ma e sa -- be~a -- | mar; __ _
        Se -- gue | na~estra -- da do a -- | mor. __ _
      }
    }
    theLyricsTen = \lyricmode {
      \set stanza = "10."
      \repeat volta 2 {
        \skip 1 Meu __ _ | Mes -- tre \skip 1 me de -- | cla -- re;
        Co -- mo | é que vai fi -- | car. __ _
      }
    }
    theLyricsEleven = \lyricmode {
      \set stanza = "11."
      \repeat volta 2 {
        Pres -- te~a -- ten -- | ção no que eu já | dis -- se;
        Quem ven -- | cer é~que vai bri -- | lhar. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1 | a:m | g2 e:m | c2~ c8
      }
    }
    \layout { #(layout-set-staff-size 13) } % to fit on one staff
    \score { % custom score to show all the 11 verses
      <<
        \new ChordNames { \theChords }
        \new Staff { \clef "treble" \new Voice = "theVoice" { \theMelody } }
        \new TabStaff { \clef "moderntab" \transpose c' c, \theMelody }
        \new Lyrics \lyricsto "theVoice" { \theLyricsOne }
        \new Lyrics \lyricsto "theVoice" { \theLyricsTwo }
        \new Lyrics \lyricsto "theVoice" { \theLyricsThree }
        \new Lyrics \lyricsto "theVoice" { \theLyricsFour }
        \new Lyrics \lyricsto "theVoice" { \theLyricsFive }
        \new Lyrics \lyricsto "theVoice" { \theLyricsSix }
        \new Lyrics \lyricsto "theVoice" { \theLyricsSeven }
        \new Lyrics \lyricsto "theVoice" { \theLyricsEight }
        \new Lyrics \lyricsto "theVoice" { \theLyricsNine }
        \new Lyrics \lyricsto "theVoice" { \theLyricsTen }
        \new Lyrics \lyricsto "theVoice" { \theLyricsEleven }
      >>
      \layout { }
    }
    \include "tex/lp-internal-midi-score.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I called the Master Juramidam, for my Master to come here
    \nextverse
    With his divine force to come and liberate me
    \nextverse
    Give me strength, give me love, for me to be able to dominate
    \nextverse
    My Master in His court, on His divine throne
    \nextverse
    He has and gives everything with His crystal light
    \nextverse
    I am small, I am small, it's he whom I should ask
    \nextverse
    Everyone has, everyone has, everyone has, you can follow
    \nextverse
    Here I'm going to declare to whom the Master entrusted it
    \nextverse
    He who loves and knows how to love, follows the path of love
    \nextverse
    My Master declares to me how things are going to be
    \nextverse
    Pay attention to what I've already said; he who overcomes is going to shine
  \end{translation}
\endsong


\beginsong{As Estrelas}[by={Mestre Irineu Serra},key={A},sks={A, B, G}]
  \audio{https://www.nossairmandade.com/hymn/265/AsEstrelas}
  \mnbeginchorus\memorize
    \[^\mn{C#}]As \[^\mn{E}]es|\[\mnc{A}A]trelas \[\bmc\mn{C#}]já \[^\mn{E}]che|\[^\mn{A}]garam \altchords{\id[1]{(G)}|G | \e}
    \[\bmc\mn{A}]Para \[^\mn{G#}]di|\[\mnc{F#}F#m]zer \[^\mn{E}]o \[(A)]no\[^\mn{C#}]me |\[\mnc{E}E]seu \[\bm] \altchords{|Em (G) |D}
    \[^\mn{E}]Sou |\[\mnc{A}A]eu, sou \[\bmc\mn{C#}]eu, \[^\mn{E}]sou |\[(E)]eu \altchords{|G |(D)}
    \[\mnc{A}A]Sou \[^\mn{G#}]eu |\[\mnc{F#}F#m]um \[^\mn{E}]fi\[E]lho \[^\mn{C#}]de |\[\mnc{D}D]Deus \[\bm] \altchords{G |Em D |C}
  \mnendchorus
  \notesoff
  \beginchorus
    As es|^trelas ^me le|varam
    ^Para cor|^rer o ^mundo in|^tei^ro
    \noteson\[\mnlow{C#}]Pra co\[\mnlow{E}]nhe\notesoff|^cer es^ta ver|^dade
    ^Para po|^der ser ^verda|^dei^ro
  \endchorus
  \beginchorus
    Eu su|^bi ser^ra de es|pinhos \altchords{\id[2]{(B)}|B | \e}
    ^Pisan|^do em pon^tas a|^gu^das \altchords{|G\#m (B) |F\#}
    \noteson\[\mnlow{C#}]As \[\mnlow{E}]es\notesoff|^trelas ^me dis|^seram \altchords{|B |(F\#)}
    ^No mun|^do se ^cura |^tu^do \altchords{B |G\#m F\# |E}
  \endchorus
  \beginchorus
    As es|^trelas ^me dis|seram
    ^Ouve |^muito e ^fala |^pou^co
    \noteson\[\mnlow{C#}]Pa\[\mnlow{E}]ra \notesoff|^poder ^compreen|^der
    E ^conver|^sar com ^meus ca|^bo^clos
  \endchorus
  \beginchorus
    Os ca|^boclos ^já che|garam
    De ^braços |^nus e ^pés no |^chão ^
    \noteson\[\mnlow{C#}]E\[\mnlow{E}]les \notesoff|^trazem re^médios |^bons
    ^Para |^curar ^os cris|^tã^os
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4
      \repeat volta 2 {
        cis8\pomark e | a,4 a cis e | a, a a'4( a8) gis8
        | fis4. e8 e4. cis8 | e2( e8) \parenthesize cis8 \parenthesize cis8 \altcol\grace e4\altmark "1." e8
        | a,4 a8( a8) cis4 e | e4.( e8) a4( a8) gis8
        | fis4. e8 e4. cis8 | d2( d4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \set includeGraceNotes = ##t
        As es -- | tre -- las já che -- | ga -- ram;
        Pa -- ra di -- | zer o no -- me | seu; __ _ \skip 1 \skip 1
        \altcol Sou __ _  | eu, sou __ _ eu, sou | eu; __ _
        Sou __ _ eu | um fi -- lho de | Deus. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        As es -- | tre -- las me le -- | va -- ram;
        Pa -- ra cor -- | rer o mun -- do~in -- | tei -- ro;
        Pra co -- nhe -- | cer es -- _ ta ver -- | da -- de;
        Pa -- ra po -- | der ser ver -- da -- | dei -- ro.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Eu su -- | bi ser -- ra de~es -- | pi -- nhos;
        Pi -- _ san -- | do~em pon -- tas a -- | gu -- das; \skip 1
        As es -- | tre -- las __ _ me dis -- | se -- ram;
        No __ _ mun -- | do se cu -- ra | tu -- do.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        As es -- | tre -- las me dis -- | se -- ram;
        Ou -- _ ve | mui -- to~e fa -- la | pou -- co; \skip 1
        Pa -- ra | po -- der __ _ com -- preen -- | der;
        E con -- _ ver -- | sar com meus ca -- | bo -- clos.
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \repeat volta 2 {
        Os ca -- | bo -- clos já che -- | ga -- ram;~De
        bra -- _ ços | nus e pés no | chão; __ \skip 1 \skip 1
        E -- les | tra -- zem re -- mé -- dios | bons; __ _
        Pa -- _ ra | cu -- rar os cris -- | tã -- os.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a1 | a1 | fis2:m \parenthesize a2 | e1
        | a | \parenthesize e2 a2 | fis2:m e2 | d2.
      }
    }
    \layout { #(layout-set-staff-size 13) } % to fit translation, too
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    The Stars already arrived to say their name
    I am, I am, I am, I am a son of God
    \nextverse
    The Stars took me to go through the entire world
    For me to know this Truth, to be able to be true
    \nextverse
    I climbed a hill of thorns, stepping on sharp points
    The Stars told me: in the world everything can be healed
    \nextverse
    The Stars told me: listen much and speak little
    So that I can understand and speak with my caboclos
    \nextverse
    Thge caboclos already arrived with naked arms and feet on the ground
    They bring good remedies to heal the Christians
  \end{translation}
\endsong


\beginsong{Os Espíritos Estão Chegando}[by={Alex Polari},key={C},sks={C},tags={mazurca}]
  \audio{https://www.nossairmandade.com/hymn/948/OsEsp\%C3\%ADritosEst\%C3\%A3oChegando}
  \newchords{chords_osespiritosestao_a}\newchords{chords_osespiritosestao_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_osespiritosestao_a]
    \[^\mn{C}]Pe|\[C]rante este mo\[\bmc\mnc{G}G]mento \[^\mn{A}]eu |\[^\mn{G}]que\[^\mn{E}]ro \[^\mn{C}]de\[^\mn{A}]cla\[\bmc\mnc{C}C]rar \altchords{\id[1]{(D)}|D A | - D}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_osespiritosestao_b]
    \[^\mn{G}]U|\[\mnc{C}C]mas pou\[^\mn{E}]cas \[^\mn{D}]pa\[\bmc\mn{C}]lavras \[^\mn{G}]que |\[\mnc{B}G]eu ouvi \[^\mn{A}]pub\[^\mn{B}]li\[\bmc\mnc{C}C]car \altchords{|D |A D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_osespiritosestao_a]
    Os es|^píritos estão che^gando pela |linha deva^gar
    \endchorus\glueverses\beginchorus\replay[chords_osespiritosestao_b]
    Se pre|^parem apa^relhos para ou|^vir e ensi^nar
  \endchorus
  \beginchorus\replay[chords_osespiritosestao_a]
    Eles es|^tão vin do do ^Céu, tam|bém virão do ^Mar
    \endchorus\glueverses\beginchorus\replay[chords_osespiritosestao_b]
    Da |^Terra e das Mon^tanhas para |^todos doutri^nar
  \endchorus
  \beginchorus\replay[chords_osespiritosestao_a]
    Esta es|^tra da é do ^Mestre, foi |ele quem a^briu
    \endchorus\glueverses\beginchorus\replay[chords_osespiritosestao_b]
    Replan|^tando a Santa Dou^trina para a|^quele que se^guir
  \endchorus
  \beginchorus\replay[chords_osespiritosestao_a]
    Santo |^Dai me, Santa Ma^ria, con|sola e dá a^lívio
    \endchorus\glueverses\beginchorus\replay[chords_osespiritosestao_b]
    Eu |^digo aos meus ca^boclos que a|^qui o centro é ^livre
  \endchorus
  \beginchorus\replay[chords_osespiritosestao_a]
    Todos |^são filhos de ^Deus, só |basta ele que^rer
    \endchorus\glueverses\beginchorus\replay[chords_osespiritosestao_b]
    Sa|^údo a prote^ção do Vo|^vô O mungue^lê
  \endchorus
  \beginchorus\replay[chords_osespiritosestao_a]
    No |^meio da minha vi^agem ele co|migo veio ^ter
    \endchorus\glueverses\beginchorus\replay[chords_osespiritosestao_b]
    Disse |^que já fora es^cravo e cultu|^ava o mesmo po^der
  \endchorus
  \brk
  \beginchorus\replay[chords_osespiritosestao_a]
    Meu Im|^pério Jurami^dam, que |glória vos perten^cer
    \endchorus\glueverses\beginchorus\replay[chords_osespiritosestao_b]
    Basta |^ser sempre fi^el que |^tudo eu posso ^ser
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c''' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 6/4 \partial 4.
      \repeat volta 2 {
        \parenthesize c8\posectionmark "A" c8( c8) | c8( c8) c8( c8) c c  g4( g) a8( a8)
        | g4 e c8 a8  c4( c8)
      }
      \repeat volta 2 {
        r8\sectionmark "B" g8( g8) | c4( c8)( c8) e8 d8  c4( c) g8( g8)
        | b4 b8( b8) a8 b8  c4( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
        \skip 1 Pe -- _ | ran -- _ te es -- te mo -- men -- to
        Eu __ _ | que -- ro de -- cla -- rar. __ _
      \set stanza = "1.B"
        U -- _ | mas pou -- _ cas pa -- la -- vras
        Que __ _ | eu ou -- vi pu -- bli -- car. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
        \skip 1 Os es -- | pí -- ri -- tos es -- tão che -- gan -- do
        Pe -- la | li -- nha de -- va -- gar. __ _
      \set stanza = "2.B"
        Se pre -- | pa -- rem __ _ a -- pa -- re -- lhos
        Pa -- ra~ou -- | vir e __ _ en -- si -- nar. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
        E -- les es -- | tão __ _ vin -- _ do do Céu __ _
        Tam -- _ | bém vi -- rão do Mar. __ _
      \set stanza = "3.B"
        Da __ _ | Ter -- ra e das Mon -- ta -- nhas
        Pa -- ra | to -- dos __ _ dou -- tri -- nar. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
        Es -- ta es -- | tra -- _ da __ _ é do Mes -- tre
        Foi __ _ | e -- le quem a -- bri -- u.
      \set stanza = "4.B"
        Re -- plan | tan -- do~a San -- ta Dou -- tri -- na
        Pa -- ra~a -- | que -- le __ _ que se -- guir. __ _
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
        \skip 1 San -- to | Dai -- _ me, San -- ta Ma -- ri -- a
        Con -- _ | so -- la~e dá a -- lí -- vio.
      \set stanza = "5.B"
        Eu __ _ | di -- go aos meus ca -- bo -- clos
        Que a -- | qui o __ _ cen -- tro~é li -- vre.
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
        \skip 1 To -- dos | são __ _ fi -- _ lhos de Deus __ _
        Só __ _ | bas -- ta~e -- le que -- rer. __ _
      \set stanza = "6.B"
        Sa -- _ | ú -- do a pro -- te -- ção __ _
        Do  Vo -- | vô O -- _ mun -- gue -- lê. __ _
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7."
        \skip 1 No __ _ | mei -- o da mi -- nha vi -- a -- gem~e --
        le co -- | mi -- go vei -- o ter. __ _
      \set stanza = "7.B"
        Dis -- se | que já fo -- ra es -- cra -- vo~E
        cul -- tu -- | ava o mes -- mo po -- der. __ _
    }
    theLyricsEight = \lyricmode {
      \set stanza = "8."
        \skip 1 Meu Im -- | pé -- _ rio Ju -- ra -- mi -- dam __ _
        Que __ _ | gló -- ria~vos per -- ten -- cer. __ _
      \set stanza = "8.B"
        Bas -- ta | ser __ _ sem -- pre fi -- el __ _
        Que __ _ | tu -- do eu pos -- so ser. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2. g
        | g c4.
      }
      \repeat volta 2 {
        s4. | c2. c
        | g c4.
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better division
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    In this very moment I want to declare
    A few words which I heard being announced
    \nextverse
    The Spirits are arriving along the line slowly
    Prepare yourselves to listen and teach
    \nextverse
    They are coming from the Sky, they will also come from the Sea
    The Earth and the mountains to indocrinate everyone
    \nextverse
    This road is the Master's, it was he who opened it
    Replanting the Holy Doctrines for those who followed
    \nextverse
    Holy Daime and Holy Mary who console and give relief
    I tell my caboclos that the center here is free
    \nextverse
    All are children of God, it is sufficient that He wills it
    I praise the protection of grandfather Omunguelê
    \nextverse
    In the middle of my journey he come to meet me
    Told me that he had been slave and cultivated the same power
    \nextverse
    My Emperor Juramidam, what a glory to belong to You
    I need only to be forever faithful to be everything I can be
  \end{translation}
\endsong


\beginsong{Linha do Arroxim}[by={Vera Fróes},key={C},sks={D, C}]
  \audio{https://www.nossairmandade.com/hymn/58/LinhaDeArrochim}
  \audio[key={C}]{https://www.youtube.com/watch?v=6L4aBI5EWzo}
  \newchords{chords_linhadoarroxim_a}\newchords{chords_linhadoarroxim_b}
  \mnbeginchorus\memorize[chords_linhadoarroxim_a]
    \[^\mn{G}]Harmo|\[\mnc{C}C]nia, Ver\[\bm]dade e \[^\mn{E}]Per|\[\mnc{G}(G)]dão \[\bm] \altchords{\id[1]{(D)}|D |(A)}
    São \[^\mn{A}]os \[^\mn{G}]três |\[\mnc{E}C]pon\[^\mn{C}]tos que se\[\mnc{A}Am]gu\[^\mn{B}]ram es\[^\mn{C}]ta u\[^\mn{A}]ni|\[\mnc{G}G]ão \[\bm] \altchords{|D Bm |A}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_linhadoarroxim_b]
    \[^\mn{C}]Eu |\[\mnc{A}Am]peço \[^\mn{C}]meus ir\[C]mãos: prestem aten|\[\mnc{G}G]ção \altchords{|Bm D |A}
    Que o \[\mnc{C}C]Mestre do as|\[\mnc{E}(Em)]tral está \[^\mn{C}]ol\[\mnc{D}G]hando a \[^\mn{B}]ses|\[\mnc{C}C]são \[\bm] \altchords{D |(F\#m) A |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_linhadoarroxim_a]
    As do|^enças ^que apare|^cer ^
    É disci|^plina pra quem ^faz por mere|^cer ^
    \endchorus\glueverses\beginchorus\replay[chords_linhadoarroxim_b]
    Pe|^dir aos es^píritos cura|^dores
    da li^nha de Arro|^xim a Jesus ^Cristo Reden|^tor ^
  \endchorus
  \beginchorus\replay[chords_linhadoarroxim_a]
    Ter |^fé e espe^rança no pe|^di^do
    Pensar em |^Deus e na ^nossa Virgem |^Mãe ^
    \endchorus\glueverses\beginchorus\replay[chords_linhadoarroxim_b]
    Não |^ter ^medo de mor|^rer
    ^E se sair cor|^rendo é pi^or para vo|^cê ^
  \endchorus
  \beginchorus\replay[chords_linhadoarroxim_a]
    Com |^calma ^e tranqüili|^da^de
    O seu ca|^minho ^vai se ilumi|^nar ^
    \endchorus\glueverses\beginchorus\replay[chords_linhadoarroxim_b]
    Te |^lembra do ve^lho Jurami|^dam
    Ele es^tá sempre pre|^sente e se^gura a tua |^mão
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8(\posectionmark "A" g8) | c4( c8) c c c c e | g2( g8) g a g
        | e( c8 c) c a b c a | g2.
      } \break
      \repeat volta 2 {
        c4\sectionmark "B" | a8( a)( c8 c) c c16( c16) c8 c | g4( g8 g8) c c c c
        | e e e c d d d b | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Har -- mo -- | ni -- a, Ver -- da -- de e Per -- | dão; __ _
        São os três | pon -- tos que se -- gu -- ram~es -- ta~u -- ni -- | ão.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Eu | pe -- ço meus ir -- mãos:
        pres -- tem a -- ten -- | ção;
        Que o Mes -- tre do as -- | tral
        es -- tá ol -- han -- do a ses -- | são.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        As do -- | en -- _ ças que a -- pa -- re -- | cer; __ _
        É dis -- ci -- | pli -- na Pra quem faz por me -- re -- | cer.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Pe -- | dir __ _ aos es -- pí -- ri -- tos cu -- ra -- | dores;
        da li -- nha de Ar -- ro -- | xim
        A Je -- sus Cris -- to Re -- den -- | tor.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Ter __ _ | fé~e es -- pe -- ran -- ça no pe -- | di -- do;
        Pen -- sar em | Deus __ _ e na nos -- sa Vir -- gem | Mãe.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Não | ter __ _ _ _ me -- do __ _ de mor -- | rer; __ _ _
        E se sair cor -- | ren -- do é pi -- or pa -- ra vo -- | cê.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Com __ _ | cal -- _ ma e tran -- qüi -- li -- | da -- de;
        O seu ca -- | mi -- _ _ nho vai se~i -- lu -- mi -- | nar.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Te | lem -- bra do ve -- lho Ju -- _ ra -- mi -- | dam;
        Ele es -- tá sem -- pre pre -- | sen -- te e se -- gu -- ra~a tu -- a | mão.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | \parenthesize g1 | c2 a2:m | g2.
      }
      \repeat volta 2 {
        s4 | a2:m c2 | g2 c2 | \parenthesize e2:m g2 | c2.
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Harmony, truth and forgiveness
    Are the three points that secure this union.
    I ask my brothers and sisters: pay attention
    For the Master in the Astral is watching this session
    \nextverse
    The sicknesses that appear
    The discipline for those who try to be deserving.
    It's to ask the spiris of healing
    from the Arroxim line and Jesus Christ the Redeemer
    \nextverse
    To have faith and hope in the request
    To think of God and of our Virgin Mother.
    To not be afraid of dying
    And if you take off running, it's worse for you.
    \nextverse
    With calmness and tranquility
    Your path is going to be illuminated.
    Remember the old Juramidam
    He is always present and holds your hand.
  \end{translation}
\endsong


\beginsong{Linha do Tucum}[by={Mestre Irineu Serra},tags={marcha/valsa, 2x},key={Dm},sks={Dm, Cm -- Gm}]
  \audio{https://www.nossairmandade.com/hymn/59/LinhaDoTucum}
  \newchords{chords_linhadotucum_a}\newchords{chords_linhadotucum_b}
  \mnbeginchorus\memorize[chords_linhadotucum_a]
    \[^\mn{A}]Eu |\[\mnc{D}Dm]canto \[^\mn{C#}]a\[\bmc\mn{D}]qui \[^\mn{E}]na |\[^\mn{F}]ter\[^\mn{D}]ra \[\bm] \altchords{\id[1]{(Em)}|Em | \e}
    O \[^\mn{F}]a|\[\mnc{E}A7]mor \[^\mn{D}]que \[\bmc\mn{C#}]Deus \[^\mn{E}]me |\[\mnc{D}Dm]dá \[\bm] \altchords{|B7 |Em}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_linhadotucum_b]
    \[^\mn{A}]Pa\[^\mn{C}]ra |\[C]sempre\[\bm] \[^\mn{B&}]pa\[^\mn{A}]ra |\[\mnc{B&}F]sem\[^\mn{A}]pre \[\bm]\altchords{|D |G}
    Para |\[A7]sempre\[\bm] para |\[\mnc{D}Dm]sempre \[\bm]\altchords{|B7 |Em}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_linhadotucum_a]
    A minha |^Mãe que ^vem co|migo ^
    Que me |^deu es^ta li|^ção ^
    \endchorus\glueverses\beginchorus\replay[chords_linhadotucum_b]
    Para |^sempre^ para |^sempre^
    Para |^sempre eu ^ser ir|^mão ^
  \mnendchorus
  \beginchorus\replay[chords_linhadotucum_a]
    Enxo|^tando os ^malfa|zejos ^
    Que não |^querem ^me ou|^vir ^
    \endchorus\glueverses\beginchorus\replay[chords_linhadotucum_b]
    Que escu|^recem ^o pensa|^mento^
    E nunca |^podem ^ser fe|^liz
  \mnendchorus
  \beginchorus\replay[chords_linhadotucum_a]
    Esta é a |^Linha ^do Tu|cum ^
    Que traz |^toda ^leal|^da^de
    \endchorus\glueverses\beginchorus\replay[chords_linhadotucum_b]
    Casti|^gando^ os menti|^rosos^
    Aqui den|^tro des^ta ver|^da^de
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        r8\sectionmark "1.A" a4 | d4 d8 cis8 d4 e | f d2 d8 f8
        | e4 d4 cis4 e4 | d2~ d8
      } \break
      \repeat volta 2 {
        r8\sectionmark "1.B" a8 c8 | c4 c2 bes8 a8 | bes4 a2 a8 a8 | a4 a2 a8 a8 | d4 d4.
      } \break
      \repeat volta 2 {
        a8\posectionmark "2-4.A"\segno a8 a8 | d4 cis4 d4 e | f( d2) d8 f8
        | e4 d4 cis4 e4 | d2( d8)
      } \break
      \repeat volta 2 {
        a8\sectionmark "2-4.B" a8 c8 | c4 c4.( bes8) bes8 a8 | bes4 a4.( a8) a8 a8 | a4 a8 a8 cis4 e4 | d2( d8)
        \dalsegno
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Eu | can -- to a -- qui na | ter -- ra;
        O a -- | mor que Deus me | dá. __ _
      \set stanza = "1.B"
        Pa -- ra | sem -- pre pa -- ra | sem -- pre;
        Pa -- ra | sem -- pre pa -- ra | sem -- pre.
      <<
        \new Lyrics {
          \set associatedVoice = "theMelody"
          \set stanza = "2.A"
            A mi -- nha | Mãe que vem co -- | mi -- go;
            Que me | deu es -- ta li -- | ção. _
          \set stanza = "2.B"
            _ Pa -- ra | sem -- pre __ _ pa -- ra | sem -- pre; __ _
            Pa -- ra | sem -- pre eu ser ir -- | mão. _
        }
        \new Lyrics {
          \set stanza = "3.A"
            _ En -- xo -- | tan -- do~os mal -- fa -- | ze -- jos;
            Que não | que -- rem me ou -- | vir. __ _
          \set stanza = "3.B"
            Que es -- cu -- | re -- cem o pen -- sa -- | men -- to;
            E nun -- ca | po -- dem __ _ ser fe -- | liz. _
        }
        \new Lyrics {
          \set stanza = "4.A"
            Es -- ta é~a | Li -- nha do Tu -- | cum __ _
            Que traz | to -- da le -- al -- | da -- de
          \set stanza = "4.B"
            _ Cas -- ti -- | gan -- do os men -- ti -- | ro -- sos;
            A -- qui den -- | tro des -- _ ta ver -- | da -- de.
        }
      >>
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | d1:m | d:m | a:7 | d2:m~ d8:m
      }
      \repeat volta 2 {
        s4. | c1 | f1 | a:7 | d2:m~ d8:m
      }
      \repeat volta 2 {
        s4. | d1:m | d:m | a:7 | d2:m~ d8:m
      }
      \repeat volta 2 {
        s4. | c1 | f1 | a:7 | d2:m~ d8:m
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I sing here on earth, the love that God gives me
    Forever, forever, forever, forever
    \nextverse
    My Mother that comes with me, who gave me this lesson
    Forever, forever, forever to be a brother
    \nextverse
    Driving away those who do evil, who don't want to listen to me
    Who darken their minds and can never be happy
    \nextverse
    This is the line of Tucum that brings all loyalty
    Punishing the liars here in this truth
  \end{translation}
\endsong
