% Santo Daime: Nova Dimensão (Padr. Alfredo)
% ==========================================
%
\audio[title={santodaime.org}]{https://hinos.santodaime.org/acervo/padrinho-alfredo/nova-dimensao}
\audio[title={Nossa Irmandade}]{https://nossairmandade.com/hinario/116/NovaDimens\%C3\%A3o}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Brilhantes Pedras Finas}[by={Padr. Alfredo}, key={A}, gk={A, (A)--(B\flt{})}, tags={marcha e valsa}, off={Angelina}]
  \audio{https://nossairmandade.com/hymn/3240/BrilhantesPedrasFinas}
  \audio[key=A]{https://soundcloud.com/violeiro-daime/brilhantes-pedras-finas}
  \audio[key=A]{https://soundcloud.com/canaljagube/01-brilhantes-pedras-finas?in=canaljagube/sets/hinario-nova-dimensao-1}
  \newchords{chords_brilhantes_pedras_a}\newchords{chords_brilhantes_pedras_b}
  \mnbeginchorus\memorize[chords_brilhantes_pedras_a]
    \[^\mn{A}]Ao pai e\meter{4}{4}|\[A]ter\[^\mn{E}]no nunca \[\bmc\mn{F#}]dei\[^\mn{E}]xo de pe|\[^\mn{A}]dir\[\bm]
    \[^\mn{A}]Na minha |\[A7]mãe \[^\mn{E}]eu nunca \[\bm]pa\[^\mn{C#}]ro \[^\mn{D}]de \[^\mn{E}]fa|\[\mnc{F#}D]lar\[\bm]
    \[^\mn{B}]Je\[^\mn{C#}]sus |\[^\mn{D}]Cristo nos\[^\mn{F#}]so \[\bmc\mn{B}]gui\[^\mn{A}]a eterna|\[\mnc{E}A]men\[^\mn{C#}]te\[\bm]
    \[^\mn{E}]E me dá |\[E]forças \[^\mn{B}]pa\[^\mn{C#}]ra \[\bmc\mn{D}]eu e\[^\mn{A}]xe\[^\mn{B}]cu|\[\mnc{C#}A]tar\[A7]
    \[^\mn{A}]Es\[^\mn{B}]ta \[^\mn{C#}]mis|\[\mnc{D}D]são edu\[^\mn{F#}]ca\[\bmc\mn{B}]ção \[^\mn{A}]em nossa |\[\mnc{E}A]men\[^\mn{C#}]te\[\bm]
    \[^\mn{E}]Eterna|\[E]mente \[^\mn{B}]pa\[^\mn{C#}]ra \[\bmc\mn{D}]todos \[^\mn{C#}]nós \[^\mn{B}]can\up{1}(|\[\mnc{A}A]tar\[\bm]{} ) \up{2}(\meter{3}{4}|\[\mnc{A}A]tar)
  \mnendchorus
  \mnbeginchorus\memorize[chords_brilhantes_pedras_b]
    \ind \[^\mn{A}]Se\meter{3}{4}|\[A7]guin\[^\mn{B}]do es\[^\mn{C#}]ta |\[\mnc{D}D]rosa \[^\mn{F#}]de |\[^\mn{B}]luz \[^\mn{A}]e \[^\mn{C#}]ca|\[\mnc{E}E]lor
    \ind \[^\mn{F#}]Que |\[^\mn{E}]no \[^\mn{C#}]meu \[^\mn{A}]jar|\[^\mn{B}]dim fez nas|cer \[^\mn{A}]es\[^\mn{C#}]ta |\[A]flor
    \ind Es|\[\mnc{A}A7]ta \[^\mn{B}]flor \[^\mn{C#}]me|\[\mnc{D}D]nina, \[^\mn{F#}]di|\[^\mn{B}]vi\[^\mn{A}]na es\[^\mn{C#}]ta |\[\mnc{E}E]flor
    \ind \[^\mn{F#}]Jar|\[^\mn{E}]dim \[^\mn{C#}]da \[^\mn{A}]in|\[^\mn{B}]fância \[^\mn{A}]Jar|\[^\mn{C#}]dim \[^\mn{A}]do \[^\mn{F#}]a\up{1}(|\[\mnc{A}A]mor) \up{2}(\meter{4}{4}|\[\mnc{A}A]mor\[\bm]{} )
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_brilhantes_pedras_a]
    Vem das es\meter{4}{4}|^trelas o vi^gor desta mis|são^
    São nossos |^guias que vem ^para nos cu|^rar^
    Passando o |visto o ser di^vino Santo |^Daime^
    Nos traz o |^dom e o po^der de transfor|^mar^
    Aqui na |^terra de bri^lhantes pedras |^finas^
    O nosso |^mestre tem po^der de nos sal\up{1}(|^var^ ) \up{2}(\meter{3}{4}|^var)
    \endchorus
  \beginchorus\replay[chords_brilhantes_pedras_b]
    \ind No \meter{3}{4}|^jardim lou|^vando a |nossa mãe|^zinha
    \ind Que |foi quem nos |deu es|ta pedra |^fina
    \ind Es|^te dia|^mante de i|lumina|^ção
    \ind E|leva o es|tudo No|va Dimen\up{1}(|^são) \up{2}(\meter{4}{4}|^são^ )
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2023-04
    theMelody = \relative a'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4.
      \repeat volta 2 {
        a8 \posectionmark "A" a a | a e e e fis e e e | a,2~8 a' a a
        | a e e e e cis d e | fis2~8 \parenthesize b,8 b cis
        | d d d fis b a a a | e4 cis4. e8 e e
        | e e b cis d d a b | cis2~8 a b cis
        | d d d fis b a a a | e4 cis4. e8 e e
        | e e b cis d d cis b
      } \alternative {
        { | a2~8 }
        { \time 3/4 | a2 \once \override Score.TimeSignature.stencil = ##f }
      } \break
      \repeat volta 2 { \time 3/4 \partial 4
        a4 \sectionmark "B" | a b cis | d d fis | b a cis, | e( e) fis
        | e cis a | b( b) b | b a cis | cis( cis) cis
        | a b cis | d d fis | b a cis, | e2 fis4
        | e cis a | b b a | cis a fis
      } \alternative {
        { a2 }
        { \time 4/4 a2~8 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 2 {
        \set stanza = "1.A"
        Ao pai e -- | ter -- no nun -- ca dei -- xo de pe -- | dir; _
        Na mi -- nha | mãe eu nun -- ca pa -- ro de fa -- | lar; _
        \skip 1 Je -- sus | Cris -- to nos -- so gui -- a~e -- ter -- na -- | men -- te;
        E me dá | for -- ças pa -- ra eu e -- xe -- cu -- | tar; _
        Es -- ta mis -- | são e -- du -- ca -- ção em nos -- sa | men -- te;
        E -- ter -- na -- | men -- te pa -- ra to -- dos nós can --
      } \alternative {
        { | tar. _ }
        { | tar. }
      }
      \repeat volta 2 {
        \set stanza = "1.B"
        Se -- | guin -- do~es -- ta | ro -- sa de | luz e ca -- | lor; __ _
        Que | no meu jar -- | dim fez nas -- | cer es -- ta | flor; __ _
        Es -- | ta flor me -- | ni -- na, di -- | vi -- na~es -- ta | flor;
        Jar -- | dim da in -- | fân -- cia, jar -- | dim do a --
      } \alternative {
        { | mor. }
        { | mor. _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \repeat volta 2 {
        \set stanza = "2.A"
        Vem das es -- | tre -- las o vi -- gor des -- ta mis -- | são; _
        São nos -- sos | gui -- as que vem pa -- ra nos cu -- | rar; _
        Pas -- san -- do~o | vis -- to~o ser di -- vi -- no San -- to | Dai -- me;
        Nos traz o | dom e o po -- der de trans -- for -- | mar; _
        A -- qui na | ter -- ra de bri -- lhan -- tes pe -- dras | fi -- nas;
        O nos -- so | mes -- tre tem po -- der de nos sal --
      } \alternative {
        { | var. _ }
        { | var. }
      }
      \repeat volta 2 {
        \set stanza = "2.B"
        No | jar -- dim lou -- | van -- do a | nos -- sa mãe -- | zi -- nha;
        Que | foi quem nos | deu __ _ es -- | ta pe -- dra | fi -- na;
        Es -- | te di -- a -- | man -- te de~i -- | lu -- mi -- na -- | ção;
        E -- | le -- va~o es -- | tu -- do No -- | va Di -- men --
      } \alternative {
        { | são. }
        { | são. _ }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1 | a | a:7 | d
        | d | a | e | a2 a2:7
        | d1 | a | e
      } \alternative {
        { | a2~8 }
        { | a2 }
      }
      \repeat volta 2 {
        s4 | a2.:7 | d | d | e
        | e | e | e | a
        | a:7 | d | d | e
        | e | e | e
      } \alternative {
        { | a2 }
        { | a2~8 }
      }
    }
    \layout { #(layout-set-staff-size 10.3) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi
  \begin{translation}[EN]
    Of the Eternal Father I never cease to ask, I never stop speaking about my Mother
    Jesus Christ our guide forever, and gives me strength to perform
    This mission education in our mind, forever for all of us to sing
    \nextverse
    \ind Following this rose of light and warmth, that in my garden gave birth to this flower
    \ind This little girl flower, this flower divine, garden of childhood, garden of love
    \nextverse
    The vigor of this mission comes from the stars, it is our guides who come to heal us
    The divine being of Santo Daime grading our work, which brings the gift and the power to transform
    Here in the land of shining precious stones, our master has power to save us
    \nextverse
    \ind In the garden praising our Mother, who was the one who gave us this fine stone
    \ind This diamond of illumination elevates the study of the New Dimension
  \end{translation}
\endsong


\beginsong{Ciranda do Amor \\ Ciranda do Santo Daime}[by={Padr. Alfredo}, key={Am}, gk={Bm, (Am)--(Cm)}, tags={marcha e meia valsa}, off={April, Lemoni e Grace}]
  \audio{https://nossairmandade.com/hymn/3237/CirandaDoSantoDaime}
  \audio[key=Am]{https://soundcloud.com/violeiro-daime/ciranda-do-santo-daime?in=violeiro-daime/sets/hinario-nova-dimensao}
  \newchords{chords_cirandadoamor_a}\newchords{chords_cirandadoamor_b}
  \mnbeginchorus\memorize[chords_cirandadoamor_a]
    \ind \[^\mn{E}]O |\[\mnc{A}Am]que Pa\[\bm]pai \[^\mn{B}]me |\[^\mn{A}]de\[\mnc{G}Am7]{-u} \altchords{\id[1]{(Bm)}|Bm | - Bm7}
    \ind |\[Em]Ma\[^\mn{F#}]mãe \[\bmc\mn{G}]con\[^\mn{A}]sa|\[\mnc{E}E]grou \[E7]{} \altchords{|F\shrp{}m |F\shrp{} F\shrp{}7}
  \mnendchorus
  \mnbeginchorus\memorize[chords_cirandadoamor_b]
    \[^\mn{A}]Gira, |\[Am]gira, \[^\mn{E}]crian\[\bmc\mn{C}]ci\[^\mn{A}]nha, |\[^\mn{C}]gi\[^\mn{A}]ra \altchords{|Bm | \e}
    \[\bm]Na ci|\[\mnc{E}E]randa \[\bmc\mn{A}]do a|\[\mnc{C}C]mor \[\bm]{} \altchords{|F\shrp{} |D}
    \[^\mn{A}]Gira, |\[Am]gira, \[^\mn{E}]crian\[\bmc\mn{C}]ci\[^\mn{A}]nha, |\[^\mn{C}]gi\[^\mn{A}]ra \altchords{|Bm | \e}
    \[\bm]Que a |\[\mnc{E}E]Virgem \[\bmc\mn{C}]Mãe \[^\mn{B}]man|\[\mnc{A}Am]dou \[\bm]{} \altchords{|F\shrp{} |Bm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_cirandadoamor_a]
    \ind O |^que Ma^mãe me |dis^se \altchords{\id[4]{alt. (Am)}|Am | - G}
    \ind |^Papai ^confir|^mou ^ \altchords{| - |E7}
  \endchorus
  \beginchorus\replay[chords_cirandadoamor_b]
    Gira, |^gira, cabo^clinha, |gira \altchords{|Am C | - Am}
    ^Gira |^na gi^ra do a|^mor ^ \altchords{|E7 Am |C}
    Gira, |^gira, cabo^clinha, |gira \altchords{|Am C | - Am}
    ^Na gi|^ra que ^Deus man|^dou ^ \altchords{|E7 C |Am}
  \endchorus
  \beginchorus\replay[chords_cirandadoamor_a]
    \ind O |^velho ^tempo |pas^sa \altchords{\id[5]{alt. (Bm)}|Bm | - A}
    \ind No|^vo tem^po che|^gou ^ \altchords{| - |F\shrp{}7}
  \endchorus
  \beginchorus\replay[chords_cirandadoamor_b]
    Novo |^mundo, novo ^povo, nova |era, \altchords{|Bm D | - Bm}
    ^E um |^novo ^profes|^sor ^ \altchords{|F\shrp{}7 Bm |D}
    Novo |^mundo, novo ^povo, nova |era \altchords{|Bm D | - Bm}
    ^E um |^novo ^profes|^sor ^ \altchords{|F\shrp{}7 D |Bm}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2024-05
    theMelody = \relative a'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \repeat volta 2 {
        e4 \posectionmark "A" | a a a b | a2( g4)( g) | g fis g a | e2.
      }
      \repeat volta 2 {
        a8 \sectionmark "B" a | a a e e c8( c8) a8( a8) | c4 a4 a4 a4 | e4 e a a | c2.
        a'8 a | a a e e c8( c8) a8( a8) | c4 a4 a4 a4 | e4 e c' b | a2.
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        O | que Pa -- pai me | deu; __ _ _
        | Ma -- mãe con -- sa -- | grou.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Gi -- ra, | gi -- ra, cri -- an -- ci -- _ nha, __ _ | gi -- ra
        Na ci -- | ran -- da do a -- | mor;
        Gi -- ra, | gi -- ra, cri -- an -- ci -- _ nha, __ _ | gi -- ra
        Que a | Vir -- gem Mãe man -- | dou.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        O | que Ma -- mãe me | dis -- se; __ _
        | Pa -- pai con -- fir -- | mou.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Gi -- ra, | gi -- ra, ca -- bo -- cli -- _ nha, __ _ | gi -- ra
        Gi -- ra | na gi -- ra do~a -- | mor;
        Gi -- ra, | gi -- ra, ca -- bo -- cli -- _ nha, __ _ | gi -- ra
        Na gi -- | ra que Deus man -- | dou.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        O | ve -- lho tem -- po | pas -- sa;
        No -- | vo tem -- po che -- | gou.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        No -- vo | mun -- do, no -- vo po -- vo, no -- va | e -- ra,
        E um | no -- vo pro -- fes -- | sor;
        No -- vo | mun -- do, no -- vo po -- vo, no -- va | e -- ra
        E um | no -- vo pro -- fes -- | sor.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a1:m | a2:m a2:m7 | e1:m | e2 e4:7
      }
      \repeat volta 2 {
        s4 | a1:m  | a:m | e1 | c1
        | a1:m | a:m | e1 | a2.:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi
  \begin{translation}[EN]
    That which Daddy gave to me, Mommy consecrated it
    Go around, go around, little child, go around in the ciranda of love
    Go around, go around, little child, go around because the Virgin Mother ordered it
    \nextverse
    What Mommy told me, Daddy confirmed it.
    Go around, go around, little cabocla, go around
    Go around, go around, little cabocla, go around in the ring, because God ordered it
    \nextverse
    The old time passes, the new time has arrived
    New world, new people, new age, and a new teacher
    New world, new people, new age, and a new teacher
  \end{translation}
\endsong


\beginsong{Luzeiro do Meu Hinário}[by={Padr. Alfredo}, key={Dm}, gk={Dm, Cm--Em}, off={Rosália}]
  \audio{https://nossairmandade.com/hymn/3257/LuaCheia}
  \audio[key=Am]{https://soundcloud.com/violeiro-daime/lua-cheia?in=violeiro-daime/sets/hinario-nova-dimensao}
  \newchords{chords_luzeirodomeuhinario_a}\newchords{chords_luzeirodomeuhinario_b}
  \mnbeginchorus\memorize[chords_luzeirodomeuhinario_a]
    \[^\mn{F}]A\[^\mn{D}]com|\[\mnc{A}A]panho \[\bm]es\[^\mn{F}]ta |\[^\mn{E}]Luz \[\bm]{} \altchords{\id[1]{(Am) \capo{5}}|E | \e}
    Cla\[^\mn{C#}]re|\[^\mn{A}]ando o \[\bm]nos\[^\mn{E}]so |\[\mnc{D}Dm]chão \[\bm]{} \altchords{| - | Am}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_luzeirodomeuhinario_b]
    \[^\mn{F}]Da mi\[^\mn{E}]nha |\[\mnc{D}Dm]Mãe lá \[\mnc{F}(F)]no \[^\mn{D}]As|\[\mnc{G}Gm]tral \[\bmadj{-.5ex}] \altchords{|Am (C) |Dm }
    \[^\mn{E}]{É que} me |\[\mnc{A}A]vem \[^\mn{G}]es\[\mnc{C#}A7]te \[^\mn{E}]cla|\[\mnc{D}Dm]rão \[\bm]{} \altchords{|E E7 |Am}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_luzeirodomeuhinario_a]
    Oh! Luz |^que cla^reia a |noi^te
    Lu|zeiro do ^meu hi|^ná^rio
    \endchorus\glueverses\beginchorus\replay[chords_luzeirodomeuhinario_b]
    Sua |^força es^tá em |^tu^{'do}
    Meu Di|^vino ^calen|^dá^rio
  \endchorus
  \beginchorus\replay[chords_luzeirodomeuhinario_a]
    Está na |^grande^za dos |as^tros \altchords{\id[2]{(Em)}|B | \e}
    O re|médio ^para |^tu^do \altchords{| - |Em}
    \endchorus\glueverses\beginchorus\replay[chords_luzeirodomeuhinario_b]
    Na Dou|^trina ^eu a|^pren^{'do} \altchords{|Em (G) |Am}
    E na Dou|^trina ^eu me |^cu^ro \altchords{|B B7 |Em}
  \endchorus
  \beginchorus\replay[chords_luzeirodomeuhinario_a]
    Também não |^é só ^tomar |Dai^me
    Sem pres|tar bem ^aten|^ção ^
    \endchorus\glueverses\beginchorus\replay[chords_luzeirodomeuhinario_b]
    Nos diz |^Padrinho ^Iri|^neu ^
    E Pa|^pai Se^basti|^ão ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize f8 \posectionmark "A" f8 d | a4. a8 a4. f'8 | e2( e4) \once\slurUp e8 \single\altcol ( << \single\altcol e) \altmark "2." cis >> | a4( a8) a8 a4. e'8 | d2( 8)
      }
      \repeat volta 2 {
        \parenthesize f8 \sectionmark "B" f e | d4 ( d8 ) d8 f4. d8 | g2~ g8 \parenthesize e e e | a4. g8 cis,4. e8 | d2( 8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        "" A -- com -- | pa -- nho es -- ta | Luz; __ _
        Cla -- re -- | an -- _ do~o nos -- so | chão. __ _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Da mi -- nha | Mãe __ _ lá no As -- | tral; _
        É que me | vem es -- te cla -- | rão. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        "" Oh! Luz | que cla -- rei -- a~a | noi -- te;
        Lu -- _ | zei -- ro do meu hi -- | ná -- rio.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        "" Su -- a | for -- ça es -- tá em | tu -- _ do;
        Meu Di -- | vi -- no ca -- len -- | dá -- rio.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Es -- tá na | gran -- de -- za dos | as -- tros;
        O re -- | mé -- _ dio pa -- ra | tu -- do.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        "" Na Dou -- | tri -- _ na eu a -- | pren -- _ do;~E
        na Dou -- | tri -- na eu me | cu -- ro.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Tam -- bém não | é só to -- mar | Dai -- me;
        Sem pres -- | tar __ _ bem a -- ten -- | ção. __ _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        "" Nos diz | Pa -- dri -- nho I -- ri -- | neu; _
        "" E Pa -- | pai Se -- bas -- ti -- | ão. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1 | a | a | d2:m~ 8
      }
      \repeat volta 2 {
        s4. | d2:m \parenthesize f2 | g1:m | a2 a2:7 | d2:m~ 8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I follow the Light, clearing our ground
    It is from my mother there in the Astral, where this clarity comes
    \nextverse
    Oh! Light that clears the night, beacon of my hinário
    Your strength is in everything, my Divine calendar
    \nextverse
    It is the greatness of the stars, the remedy for everything
    I learn in the Doctrine, and in the Doctrine I heal myself
    \nextverse
    Also is it not just taking Daime without paying close attention
    Padrinho Irineu tells us, and Papa Sebastião
  \end{translation}
\endsong


\beginsong{Salmo}[by={Padr. Alfredo}, key={Dm}, gk={Dm}, off={Alexandre}, tags={valsa}]
  \audio{https://nossairmandade.com/hymn/3800/Salmo}
  \audio[key=Dm]{https://soundcloud.com/violeiro-daime/nova-dimensao?in=violeiro-daime/sets/hinario-nova-dimensao}
  \newchords{chords_salmo_a}\newchords{chords_salmo_b}\newchords{chords_salmo_c}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_salmo_a]
    \[^\mn{A}]Eu |\[\mnc{D}Dm]vou \[^\mn{E}]re|\[\mnc{D}A]zan\[^\mn{C#}]do, \[^\mn{A}]pa|\[\mnc{D}Dm]pai \[^\mn{E}]do |\[\mncii{D}{C#}A]Céu
    \[^\mn{A}]ma|\[\mnc{C#}A7]mãe \[^\mn{E}]do |\[\mnc{D}Dm]Céu, ma|\[\mnc{C#}A7]mãe \[^\mn{E}]do |\[\mnc{D}Dm]Céu |\[\up{2}(D7)]\e
    \mnendchorus\glueverses\mnbeginverse\memorize[chords_salmo_b]
    \[^\mn{D}]Eu |\[\mnc{G}Gm]vou can|\[\mnc{B&}(B&)]tan\[^\mn{A}]do, e este |\[\mnc{F}Dm]sal\[^\mn{D}]mo bai|\[\mnc{F}(F)]lan\[^\mn{E}]do
    \[^\mn{A}]es|\[\mnc{B&}B&]te \[^\mn{G}]do\[^\mn{B&}]ce |\[\mnc{A}A]mel |\[A7]{} \e
    \mnendverse\glueverses\mnbeginchorus\memorize[chords_salmo_c]
    \[^\mn{D}]Vou |\[\mnc{G}Gm]implo|\[\mnc{B&}(B&)]ran\[^\mn{A}]do, pe|\[\mnc{F}Dm]din\[^\mn{D}]do e ro|\[\mnc{F}(F)]gan\[^\mn{E}]do
    \[^\mn{D}]Ao |\[\mnc{C#}A7]meu São \[^\mn{E}]Mi|\[\mnc{D}Dm]guel, |\[\mnc{C#}A7]meu São \[^\mn{E}]Mi|\[\mnc{D}Dm]guel |\[\up{1}D7]\e
  \mnendchorus
  \notesoff
  \vspace{2ex}
  \beginchorus\replay[chords_salmo_a]
    Vou |^medi|^tando, na |^minha dou|^trina
    a |^cami|^nhar, |^cami|^nhar |^ \e
    \endchorus\glueverses\beginverse\replay[chords_salmo_b]
    Fir|^mando os en|^sinos, do cri|^ador di|^vino
    nos |^faz enxer|^gar |^ \e
    \endverse\glueverses\beginchorus\replay[chords_salmo_c]
    O |^nosso sis|^tema: Sol, |^Lua, es|^trelas
    ter|^ra, vento e |^mar, ter|^ra, vento e |^mar |^ \e
  \endchorus
  \begin{translation}[EN]
    I am praying, father of Heaven, mother of Heaven, mother of Heaven
    I am singing, and this psalm dancing, this sweet honey
    I am imploring, asking and praying, to my Saint Michael, my Saint Michael
    \nextverse
    I meditate in my doctrine, in walking, to walk
    Firming the teachings of the divine creator, makes us see
    Our system: Sun, Moon, stars, Earth, wind and sea, Earth, wind and sea
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 3/4 \partial 4
      \repeat volta 2 {
        \mark \markup \with-color #darkgreen \italic "Final: toque tudo, mas parte A sem repetição"
        a4 \posectionmark "A" | d2 e4 | d cis a | d4( d4) e4 | d( cis) a | cis2 e4
        | d2 d4 | cis2 e4
      } \alternative {
        { | d2.~ | d2 }
        { | d2.~ | d2 }
      }
      d4 \sectionmark "B" | g4 (g4) g4 | bes4 a4 a8 a8 | f4 d d | f e a, | bes g bes | a2.~ | a2
      \repeat volta 2 {
        d4 \sectionmark "C" | g4( g4) g4 | bes a a | f d d | f e d | cis cis e
        | d2( d4) | cis4 cis e
      } \alternative {
        { | d2.~ | d2 }
        { | d2.~ | d2 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu | vou re -- | zan -- do
        pa -- | pai __ _ do | céu; __ _
        ma -- | mãe do | céu
        ma -- | mãe do
      } \alternative {
        { | céu. | _ }
        { | céu. | _ }
      }
      \set stanza = "1.B"
        Eu | vou __ _ can -- | tan -- do~E
        es -- te | sal -- mo bai -- | lan -- do;
        es -- | te do -- ce | mel. | _
      \set stanza = "1.C"
      \repeat volta 2 {
        Vou | im -- _ plo -- | ran -- do
        Pe -- | din -- do~e ro -- | gan -- do;
        Ao | meu São Mi -- | guel __ _
        | meu São Mi --
      } \alternative {
        { | guel. | _ }
        { | guel. | _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Vou | me -- di -- | tan -- do
        na | mi -- nha dou -- | tri -- na;
        a | ca -- mi -- | nhar
        \skip 1 | ca -- mi --
      } \alternative {
        { | nhar. | _ }
        { | nhar. | _ }
      }
      \set stanza = "2.B"
        Fir -- | man -- do~os en -- | si -- nos
        do cri -- | a -- dor di -- | vi -- no;
        nos | faz en -- xer -- | gar. | _
      \set stanza = "2.C"
      \repeat volta 2 {
        O | nos -- so sis -- | te -- ma:
        Sol, | Lu -- a, es -- | tre -- las;
        ter -- | ra, ven -- to~e | mar
        ter -- | ra, ven -- to~e
      } \alternative {
        { | mar. | _ }
        { | mar. | _ }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d2.:m | a | d:m | a | a:7
        | d:m | a:7
      } \alternative {
        { | d2.:m | d2:m }
        { | d2.:m | d2:7 }
      }
      s4 | g2.:m | \parenthesize bes | d:m | \parenthesize f | bes | a | a2:7
      \repeat volta 2 {
        s4 | g2.:m | \parenthesize bes | d:m | \parenthesize f | a:7
        | d:m | a:7
      } \alternative {
        { | d2.:m | d2:7 }
        { | d2.:m | d2:m }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Rei da Ciência}[by={Padr. Alfredo}, key={Am}, gk={Am, Gm--G\shrp{}m--(Am)}, off={Lúcio \& Cristiane}, tags={mazurca}]
  \audio{https://nossairmandade.com/hymn/3801/ReiDaCi\%C3\%AAncia}
  \audio[key=Am]{https://soundcloud.com/violeiro-daime/mundo-novo?in=violeiro-daime/sets/hinario-nova-dimensao}
  \newchords{chords_reidaciencia_a}\newchords{chords_reidaciencia_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_reidaciencia_a]
    \[^\mn{A}]Pesqui|\[\mnc{C}Am]san\[^\mn{A}]do a \[^\mn{C}]Na\[^\mn{E}]tu\[\bmc\mn{A}]reza \altchords{\id[1]{(Gm)}|Gm}
    Não \[^\mn{B}]se |\[^\mn{C}]tem \[^\mn{A}]na\[^\mn{E}]da \[^\mn{D}]mai\[\mnc{C}C]or \altchords{| - B\flt{}}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_reidaciencia_b]
    \[^\mn{A}]To\[^\mn{C}]da |\[\mnc{E}E]vida \[^\mn{F}]vai \[^\mn{E}]ao \[^\mn{D}]a\[\mncii{C}{A}Am]lém \altchords{|D Gm}
    Toda \[^\mn{B}]ma|\[\mnc{C}E]téria \[^\mn{D}]fi\[^\mn{B}]ca \[^\mn{C}]no \[\mnc{A}Am]pó \altchords{|D Gm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_reidaciencia_a]
    Estu|^dando a Mãe da ^Vida
    O pla|neta do A^mor
    \endchorus\glueverses\beginchorus\replay[chords_reidaciencia_b]
    Salve as |^águas e salve a ^Terra
    Onde Je|^sus Cristo pi^sou
  \endchorus
  \beginchorus\replay[chords_reidaciencia_a]
    Vamos |^todos meus ir^mãos
    Constru|ir um mundo ^novo
    \endchorus\glueverses\beginchorus\replay[chords_reidaciencia_b]
    O ver|^de Paz da flo^resta
    O ver|^melho, justiça do ^fogo
  \endchorus
  \beginchorus\replay[chords_reidaciencia_a]
    Aqui |^com a juven^tude
    Rezo |esta ora^ção
    \endchorus\glueverses\beginchorus\replay[chords_reidaciencia_b]
    Me lem|^brar do Pai E^terno
    O dono |^Rei Jurami^dam
  \endchorus
  \beginchorus\replay[chords_reidaciencia_a]
    Feito a|^qui este con^vite
    Em ple|no dois mil e ^doze
    \endchorus\glueverses\beginchorus\replay[chords_reidaciencia_b]
    Lembran|^do o Rei da Ci^ência
    Mais ma|^duro e mais i^doso
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 6/4 \partial 4
      \repeat volta 2 {
        a8 \posectionmark "A" a8
        | c4 a8( a) c e  a4( a) a8 b
        | c4 a e8 d  c4( c)
      }
      \repeat volta 2 {
        a8 \sectionmark "B" c8
        | e4 << e8 \once\slurUp \single\altcol f \altmark "3., 4., 5." \single\altcol ( >> f) e d  \once\slurUp c4( a8)( a) a b
        | c8( c) << c8 \once\slurUp \single\altcol d \altmark "2., 4." \single\altcol ( >> d) b c  a4( a)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Pes -- qui -- | san -- do a Na -- tu -- re -- za;
        Não se | tem na -- da mai -- or. __ _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        To -- da | vi -- da vai ao a -- lém; __ _
        To -- da ma -- | té -- _ ria fi -- ca no pó. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Es -- tu -- | dan -- do a Mãe da Vi -- da;
        O pla -- | ne -- ta do A -- mor. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Sal -- ve~as | á -- guas e sal -- ve~a Ter -- ra;
        On -- de Je -- | sus __ _ \altcol Cris -- _ to pi -- sou. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Va -- mos | to -- dos __ _ meus ir -- mãos; __ _
        Cons -- tru -- | ir um mun -- do no -- vo.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        O ver -- | de \altcol Paz __ _ da flo -- res -- ta; __ _
        O ver -- | me -- lho, jus -- ti -- ça do fo -- go.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        A -- qui | com a __ _ ju -- ven -- tu -- de;
        Re -- zo | es -- ta o -- ra -- ção. __ _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Me lem -- | brar \altcol do __ _ Pai E -- ter -- no; __
        O do -- no | Rei __ _ \altcol Ju -- _ ra -- mi -- dam. __ _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        Fei -- to~a -- | qui es -- _ te con -- vi -- te;
        Em ple -- | no dois mil e do -- ze.
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Lem -- bran -- | do~o \altcol Rei __ _ da Ci -- ên -- cia; __ _
        Mais ma -- | du -- _ ro e mais i -- do -- so.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a2.:m a:m | a:m c2
      }
      \repeat volta 2 {
        s4 | e2. a:m | e a2:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]\iflyriconly\scriptsize\fi % to fit on one page in lyrics-only book
    Searching for Nature, there has been no greater way
    All life goes to the beyond, all matter remains in dust
    \nextverse
    Studying the Mother of Life, the planet of Love
    Hail the water and hail the Earth where Jesus Christ stepped
    \nextverse
    Let's all go my brothers and sisters to construct a new world
    The green, Peace of the forest; the red, justice of the fire
    \nextverse
    Here with the youth I pray this prayer
    I remember the Eternal Father, the owner, King Juramidam
    \nextverse
    Made here, this invitation, in the middle of two thousand and twelve
    Remembering the King of Science, more mature and older
  \end{translation}
\endsong


\beginsong{In, in \\ In Agradecimento}[by={Padr. Alfredo}, key={C}, gk={C, B\flt{}--E}, off={José Bento}]
  \audio{https://nossairmandade.com/hymn/3804/InAgradecimento}
  \audio[key=D]{https://soundcloud.com/violeiro-daime/in-agradecimento?in=violeiro-daime/sets/hinario-nova-dimensao}
  \newchords{chords_inin_a}\newchords{chords_inin_b}
  \mnbeginchorus\memorize[chords_inin_a]
    \[^\mn{E}]Meu |\[\mnc{D}Dm]Pai, \[^\mn{A}]Vos \[\mnc{C}Fmaj7]a\[^\mn{E}]gra|\[\mnc{C}C]de\[\bmc\mn{A}]ço \altchords{\id[1]{(D)}|Em Gmaj7 |D}
    O \[^\mn{E}]que o Se|\[\mnc{D}Dm]nhor \[^\mn{A}]con\[\mnc{C}Fmaj7]ce\[^\mn{E}]de a |\[\mnc{C}C]mim \[\bm]{} \altchords{|Em Gmaj7 |D}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_inin_b]
    \[^\mn{C}]Com \[^\mn{B}]pa|\[\mnc{A}F]lavras, Vos \[\bmc\mn{C}]a\[^\mn{E}]gra|\[\mnc{G}C]de\[^\mn{E}]ço \[\bm]{} \altchords{|G |D}
    Santís\[^\mn{G}]si|\[^\mn{E}]ma \[^\mn{C}]flor \[\mnc{A}F]de \[^\mn{C}]Jas|\[C]mim \[\bm]{} \altchords{| - G |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_inin_a]
    \noteson\[\mn{C}]Mamãe \[\mn{E}]Di\notesoff|^vina ^Natu|^re^za
    Para |^sempre a^grade|^cer ^
    \endchorus\glueverses\beginchorus\replay[chords_inin_b]
    O ali|^mento ^do es|^pírito^
    E na ma|téria, ^conhe|^cer ^
  \endchorus
  \beginchorus\replay[chords_inin_a]
    \noteson\[\mn{C}]Jura\[\mn{E}]mi\notesoff|^dam, Vos ^agra|^de^ço
    Me ensi|^nou can^{tar as}|^sim ^
    \endchorus\glueverses\beginchorus\replay[chords_inin_b]
    Sem pa|^lavras, Vos ^agra|^deço^
    In, |in, in, ^in, in, |^in ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize c8 \posectionmark "A" << c \once\slurUp \single\altcol e \altmark "1." \single\altcol ( >> e )
        | d4. a8 c4. e8 | c2 a4 e'8 e
        | d4. a8 c4. e8 | c2~ 8
      }
      \repeat volta 2 {
        \parenthesize c8 \sectionmark "B" c8 b
        | a4( a8) a8 c4. e8 | g8( g8) e4. \parenthesize e8 \parenthesize e8 g8
        | e4. c8 a4. c8 | c2~ 8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        \skip 1 \altcol Meu __ _ | Pai, Vos a -- gra -- | de -- ço;~O
        que~o Se -- | nhor con -- ce -- de~a | mim. _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        \skip 1 Com pa -- | la -- vras, Vos a -- gra -- | de -- _ ço;
        San -- tís -- si -- | ma flor de Jas -- | mim. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Ma -- mãe Di -- | vi -- na Na -- tu -- | re -- za;
        Pa -- ra | sem -- pre~a -- gra -- de -- | cer. _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        O a -- li -- | men -- _ to do es -- | pí -- ri -- to;
        E na ma -- | té -- ria, co -- nhe -- | cer. _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Ju -- ra -- mi -- | dam, Vos a -- gra -- | de -- ço;
        Me~en -- si -- | nou can -- tar as -- | sim. _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 Sem pa -- | la -- vras, Vos a -- gra -- | de -- _ ço;
        \skip 1 \skip 1 In, | in, in, in, in, | in. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | d2:m f:maj7 | c1 | d2:m f:maj7 | c2~8
      }
      \repeat volta 2 {
        s4. | f1 | c | c2 f | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    My Father, I thank You, for what the Lord grants me
    With words, I thank You, most Holy Jasmine Flower
    \nextverse
    Divine Mother Nature, forever I thank you
    The nourishment of the spirit, and in the matter, knowing
    \nextverse
    Juramidam, I thank You, You taught me to sing like this
    Without words, I thank You, in, in, in, in, in, in
  \end{translation}
\endsong


\beginsong{Porto Seguro}[by={Padr. Alfredo}, key={A}, gk={A, G--B}, off={Isabella, Sophia Sterling e família}]
  \audio{https://nossairmandade.com/hymn/4002/PortoSeguro}
  \audio[key=A]{https://soundcloud.com/violeiro-daime/porto-seguro?in=violeiro-daime/sets/hinario-nova-dimensao}
  \newchords{chords_portoseguro_a}\newchords{chords_portoseguro_b}
  \mnbeginchorus\memorize[chords_portoseguro_a]
    \[^\mn{C#}]Meu |\[\mnc{E}A]Deus\[\bm]{} | \e \altchords{\id[1]{(G)}|G | \e}
    Desde \[\bmc\mn{A}]o infi|ni\[^\mn{E}]to\[\bm]{} | \e \altchords{| - | \e}
    \[^\mn{C#}]Escu\[\bmc\mn{E}]tai o meu |\[E]gri\[^\mn{B}]to\[\bm]{} | \e \altchords{|D | \e}
    Minha o\[\bm]ra\[^\mn{A}]ção \[^\mn{C#}]de a|\[A]mor\[\bm]{} |\[\up{2}(A7)] \[\bm]{} \altchords{|G |\up{2}(G7)}
  \mnendchorus
  \mnbeginchorus\memorize[chords_portoseguro_b]
    \ind \[^\mn{A}]Por|\[\mnc{D}D]que\[\bm]{} | \e \altchords{|C | \e}
    \ind Sois \[^\mn{F#}]meu \[\bmc\mn{A}]porto se|\[A]gu\[^\mn{E}]ro\[\bm]{} | \e \altchords{|G | \e}
    \ind \[^\mn{C#}]Só com \[\bmc\mn{E}]Vós eu me |\[E]cu\[^\mn{B}]ro\[\bm]{} | \e \altchords{|D | \e}
    \ind E só \[\bm]com \[^\mn{A}]Vós, \[^\mn{C#}]eu |\[\mnc{A}A]sou\[\bm]{} |\[\up{1}A7]{} \[\bm]{} \altchords{|G |\up{1}G7}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_portoseguro_a]
    Sois |^luz^ | \e
    Brilha em ^todo uni|verso^ | \e
    Meu Pai, ^a Vós eu |^peço^ | \e
    O ^Vosso vi|^gor^ |^ ^
  \endchorus
  \beginchorus\replay[chords_portoseguro_b]
    \ind Can|^tar^ | \e
    \ind E sa^ir do es|^curo^ | \e
    \ind Só com ^Vós me se|^guro^ | \e
    \ind Meu Di^vino Se|^nhor^ |^ ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \major \time 4/4 \partial 4
      \repeat volta 2 {
        cis4 \posectionmark "A"
        | e1~ | e4 e8 e a4 a8 a | a4 e2.~ | e4 cis8 cis e4 e8 e
        | e4 b2.~ | b4 \parenthesize b8 b b4 a8 cis
      } \alternative {
        { | cis1~ | cis2. }
        { | cis1~ | cis2. }
      }
      \repeat volta 2 {
        a4 \sectionmark "B"
        | d1~ | d4 d8 fis a4 a8 a | a4 e2.~ | e4 cis8 cis e4 e8 e
        | e4 b2.~ | b4 b8 b b4 a8 cis
      } \alternative {
        { | a1~ | a2. }
        { | a1~ | a2. \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Meu | Deus | _
        Des -- de o in -- fi -- | ni -- to | _
        Es -- cu -- tai o meu | gri -- to | _
        Mi -- nha~o -- ra -- ção de~a --
      } \alternative {
        { | mor. | _ }
        { | mor. | _ }
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Por -- | que | _
        Sois meu por -- to se -- | gu -- ro | _
        Só com Vós eu me | cu -- ro | _
        E só com Vós, eu
      } \alternative {
        { | sou. | _ }
        { | sou. | _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Sois | luz; | _
        Bri -- lha~em to -- do~u -- ni -- | ver -- so; | _
        Meu Pai, a Vós eu | pe -- ço; | _
        \skip 1 O Vos -- so vi --
      } \alternative {
        { | gor. | _ }
        { | gor. | _ }
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Can -- | tar; | _
        E sa -- ir do es -- | cu -- ro; | _
        Só com Vós me se -- | gu -- ro; | _
        Meu Di -- vi -- no Se --
      } \alternative {
        { | nhor. | _ }
        { | nhor. | _ }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a1 | a | a | a | e | e
      } \alternative {
        { | a1 | a2. }
        { | a1 | a2.:7 }
      }
      \repeat volta 2 {
        s4 | d1 | d | a | a | e | e
      } \alternative {
        { | a1 | a2.:7 }
        { | a1 | a2. }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Oh my God, from the infinite
    Hear my cry, my prayer of love
    \nextverse
    Because You are my safe harbor
    Only with You do I heal, and only with You, I am
    \nextverse
    You are light, shining throughout the universe
    My Father, I ask of You, Your vigor
    \nextverse
    To sing, and to leave the darkness
    Only with You am I safe, my Divine Lord
  \end{translation}
\endsong


\beginsong{Mamãe Maria}[by={Padr. Alfredo}, key={C}, gk={C, (B\flt{})--(C)}, off={Gabriela Shore}]
  \mnbeginchorus\memorize
    \[^\mn{G}]Firmo |\[\mnc{C}C]lá na al\[\bm]tu\[^\mn{G}]ra
    E no |\[^\mn{E}]fundo \[^\mn{D}]do \[\bmc\mn{C}]mar
    Vem |\[\mnc{D}Dm]Mamãe Ma\[\bm]ria \[^\mn{A}]e Ma|\[\mnc{C}C]mãe Ieman\[\bm]já
    \[^\mn{A}]Vem |\[Am]Mamãe Ma\[\bm]ria \[^\mn{G}]e Ma|\[\mnc{C}C]mãe Ieman\[\bm]já
    \[^\mn{A}]Vem |\[Am]Mamãe Ma\[\bm]ria \[^\mn{G}]e Ma|\[\mnc{C}C]mãe Ieman\[\bm]já
  \mnendchorus
  \notesoff
  \beginchorus
    Na |^força das ^ondas
    Lá |do alto ^mar
    O|^gum Rei Guer^reiro
    |^Vem doutri^nar
    |^Neste ter^reiro |^ilumi^nar
    |^Neste ter^reiro |^ilumi^nar
  \endchorus
  \beginchorus
    Viva a |^força das ^mães
    E as prin|cesas do ^mar
    Os pri|^mores das ^águas
    No |^seu balan^çar
    |^Salve o en^canto dos |^seres do ^mar
    |^Salve o en^canto dos |^seres do ^mar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g'8( \pomark g)
        | c4 c8 c c8( c8) g8 g | e8( e8)( e8) d c4 \parenthesize c8 c8
        | d8 d4 d8 d8.( d16) \parenthesize a8 a | c4 c8 c c4. \parenthesize a8
        | a8( a8)( a8) a8 a8.( a16) \parenthesize g8 g | c4 c8 c c4. \parenthesize a8
        | a8( a8)( a8) a8 a8.( a16) \parenthesize g8 g | c4 c8 c8 c4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Fir -- mo | lá na al -- tu -- _ ra;~E
        no | fun -- _ do do mar; \skip 1
        Vem | Ma -- mãe Ma -- ri -- a e Ma -- | mãe Ie -- man -- já;
        Vem | Ma -- mãe __ _ Ma -- ri -- a e Ma -- | mãe Ie -- man -- já;
        Vem | Ma -- mãe __ _ Ma -- ri -- a e Ma -- | mãe Ie -- man -- já.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Na __ _ | for -- ça das on -- _ das;
        Lá | do al -- _ to mar; \skip 1
        O -- | gum Rei Guer -- rei -- _ \skip 1 ro;
        | Vem dou -- tri -- nar;
        \skip 1 | Nes -- _ te ter -- rei -- _ \skip 1 ro | i -- lu -- mi -- nar;
        \skip 1 | Nes -- _ te ter -- rei -- _ \skip 1 ro | i -- lu -- mi -- nar.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Vi -- va~a | for -- ça das mães;
        E as prin -- | ce -- _ sas do mar;
        Os pri -- | mo -- res das á -- _ guas;
        No | seu ba -- lan -- çar;
        \skip 1 | Sal -- _ ve~o en -- can -- _ to dos | se -- res do mar;
        \skip 1 | Sal -- _ ve~o en -- can -- _ to dos | se -- res do mar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | c | d:m | c
        | a:m | c | a:m | c2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I am firm there in the heights
    And in the depths of the sea
    Coming are Mother Mary and Mother Iemanjá
    Coming are Mother Mary and Mother Iemanjá
    Coming are Mother Mary and Mother Iemanjá
    \nextverse
    In the force of the waves
    There from the high seas
    Ogun Warrior King
    Comes to indoctrinate
    To illuminate in this land
    To illuminate in this land
    \nextverse
    Viva the force of the Mothers
    And the princesses of the sea
    The splendors of the waters
    In its shaking
    Hail the enchantment of the beings of the sea
    Hail the enchantment of the beings of the sea
  \end{translation}
\endsong


\beginsong{Eu Sou Flor das Águas}[by={Padr. Alfredo}, key={Am}, gk={Bm, G\shrp{}m--Bm}, off={Mariana, Mikael}, tags={valsa, 2x}]
  \audio{https://nossairmandade.com/hymn/4282/EuSouFlorDas\%C3\%81guas}
  \newchords{chords_eusouflordasaguas_a}\newchords{chords_eusouflordasaguas_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_eusouflordasaguas_a]
    \[^\mn{E}]Eu |\[Am]sou \[^\mn{F}]flor \[^\mn{E}]das |\[^\mn{C}]á\[^\mn{A}]guas \altchords{\id[1]{(Bm)}|Bm | \e}
    E |\[^\mn{C}]te\[^\mn{A}]nho \[^\mn{C}]po|\[\mnc{B}E]der \altchords{| - |F\shrp{}}
    \[^\mn{D}]Eu |\[E7/D]sa\[^\mn{E}]cio \[^\mn{D}]a |\[\mnc{B}E]se\[^\mn{G#}]de \altchords{|F\shrp{}7/E |F\shrp{}}
    \[^\mn{B}]De |\[\mnc{D}Dm]quem \[^\mn{E}]me\[^\mn{F}]re|\[\mnc{E}E]cer \altchords{|Em |F\shrp{}}
  \mnendchorus
  \mnbeginchorus\memorize[chords_eusouflordasaguas_b]
    \ind |\[^\mn{E}]Da \[^\mn{F}]on\[^\mn{E}]de |\[\mnc{D}Dm]vens \altchords{| - |Em}
    \ind Pa|\[^\mn{F}]ra on\[^\mn{A}]de |\[\mnc{E}E]vais \altchords{| - |F\shrp{}}
    \ind Eu |sou \[^\mn{F}]flor \[^\mn{E}]das |\[\mnc{D}Dm]á\[^\mn{B}]guas \altchords{| - |Em}
    \ind \[^\mn{C}]Somos |\[\mnc{D}E7]e \[^\mn{G#}]de\[^\mn{B}]ve |\[\mnc{A}Am]ser \altchords{|F\shrp{}7 |Bm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eusouflordasaguas_a]
    Fa|^zer a lim|peza
    No |meu cora|^ção
    Dou |^{viva a} Je|^sus
    Dou |^{viva a} São Jo|^ão
  \endchorus
  \beginchorus\replay[chords_eusouflordasaguas_b]
    \ind E |Nossa Se|^nhora
    \ind |Da Concei|^ção
    \ind Na |Santa Dou|^trina
    \ind Nos |^dá a ben|^ção
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2024-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 4
      \repeat volta 2 {
        \sectionLabel "A"
        e4 \pomark
        | e f e | c a a | c a c | b2 d4
        | d e d | b( gis) b | d e f8( f8)
      } \alternative {
        { | e2 }
        { | e2 \sectionLabel "B" \parenthesize e4 | e f e }
      }
      \repeat volta 2 { 
        | d2 d4 | f f a | e2 e4
        | e f e | d b c8( c8) | d4 gis, b
      } \alternative {
        { | a2 \parenthesize e'4 | e f e  }
        { | a2 }
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu | sou flor das | á -- guas;
        E | te -- nho po -- | der;
        Eu | sa -- cio a | se -- de;
        De | quem me -- re _ --
      } \alternative {
        { | cer. }
        { | cer. \set stanza = "1.B" \skip 1 | Da on -- de  }
      }
      \repeat volta 2 {
        | vens;
        Pa -- | ra on -- de | vais;
        Eu | sou flor das | á -- guas;
        So -- mos | e de -- ve
      } \alternative {
        { | ser. \skip 1 | Da on -- de }
        { | ser. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Fa -- | zer a lim -- | pe -- za;
        No | meu co -- ra -- | ção;
        Dou | vi -- va~a Je -- | sus; __ _
        Dou | vi -- va~a São Jo --
      } \alternative {
        { | ão. }
        { | ão. \set stanza = "2.B" E | Nos -- sa Se -- }
      }
      \repeat volta 2 {
        | nho -- ra;
        | Da Con -- cei -- | ção;
        Na | San -- ta Dou -- | tri -- na;
        Nos __ _ | dá a ben --
      } \alternative {
        { | ção. E | Nos -- sa Se -- }
        { | ção. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4
        | a2.:m | a:m | a:m | e
        | e:7/d | e | d:m
      } \alternative {
        { | e2 }
        { | e2. | e2. }
      }
      \repeat volta 2 {
        | d:m | d:m | e | e
        | d:m | e:7
      } \alternative {
        { | a2.:m | a2.:m }
        { | a2:m }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I am the flower of the waters, and I have power
    I quench the thirst of those who merit it
    \nextverse
    From where you come, where you go
    I am the flower of the waters, we are and we must be
    \nextverse
    To do a cleansing in my heart
    I give viva to Jesus, I give viva to St. John
    \nextverse
    And Our Lady of Conception
    In the Holy Doctrine gives us the blessing
  \end{translation}
\endsong


\beginsong{Excelência}[by={Padr. Alfredo}, key={Am}, gk={Am, Gm--Bm}, off={Kelly Cristina}, tags={3x}]
  \mnbeginchorus\memorize
    \[^\mn{A}]Meu São \[^\mn{B}]Jo|\[\mnc{C}C]ão,\[\bm]{} meu São \[^\mn{B}]Jo|\[\mnc{A}Am]ão \[\bm]
    Vos\[^\mn{C}]sa ex\[^\mn{E}]ce|\[^\mn{A}]lência e Jesus \[\bm]Cristo Reden|\[\mnc{D}Dm]tor \[\bm]
    São quem \[^\mn{C}]me en|\[\mnc{B}E]sinam nesta es\[\bm]cola \[^\mn{C}]do \[^\mn{D}]a|\[\mnc{E}Am]mor \[\bm]
    \[^\mn{A}]A Vir\[^\mn{C}]gem |\[\mnc{E}E]Mãe e o \[^\mn{D}]nosso \[\bmc\mn{C}]Mestre En\[^\mn{B}]sina|\[\mnc{A}Am]dor \[\bm]
  \mnendchorus
  \notesoff
  \beginchorus
    Santo Cru|^zei^ro, Santa Dou|^tri^na
    O Santo |Daime, esta ^luz que nos en|^si^na
    Para |^sempre só nos ^resta agrade|^cer ^
    Para |^sempre com a^mor hei de ven|^cer ^
  \endchorus
  \begin{translation}[EN]
    My Saint John, my Saint John
    Your Excellency and Jesus Christ the Redeemer
    They are who teach me in this school of love
    The Virgin Mother and our Master Teacher
    \nextverse
    Holy Cross, Holy Doctrine
    The Santo Daime, this light that teaches us
    Forever all that remains is for us to be thankful
    Forever with love I will overcome
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        a8 \pomark a b
        | c2( 8) c8 c b | a2( 8) a8 c e | a a a a a a a a | d,2( 8)( d8) d c
        | b b b b b b c d | e2~ 8 \parenthesize a,8 a c | e e d d c c b b | a2~ 8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Meu São Jo -- | ão, __ _ meu São Jo -- | ão; __ _
        Vos -- sa~ex -- ce -- | lên -- cia~e Je -- sus Cris -- to Re -- den -- | tor; __ _
        São quem me~en -- | si -- nam nes -- ta~es -- co -- la do a -- | mor; _
        A Vir -- gem | Mãe e~o nos -- so Mes -- tre~En -- si -- na -- | dor. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        San -- to Cru -- | zei -- ro, San -- ta Dou -- | tri -- na;
        O San -- to | Dai -- me, es -- ta luz que nos en -- | si -- na; __ _
        Pa -- ra | sem -- pre só nos res -- ta~a -- gra -- de -- | cer; _
        \skip 1 Pa -- ra | sem -- pre com a -- mor hei de ven -- | cer. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4.
        | c1 | a:m | a:m | d:m | e | a:m | e | a2:m~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Louvar o Criador}[by={Padr. Alfredo}, key={C}, gk={C, B\flt{}--B--(C)}, off={Kayke}]
  \audio{https://nossairmandade.com/hymn/4369/Tucum}
  \newchords{chords_louvarocriador_a}\newchords{chords_louvarocriador_b}\newchords{chords_louvarocriador_c}
  \mnbeginchorus\memorize[chords_louvarocriador_a]
    \[^\mn{C}]Lou|\[\mnc{G}C]var\[\bmc\mn{E}], \[^\mn{A}]lou|\[^\mn{E}]van\[\bmc\mn{C}]do \altchords{\id[1]{(A) \capo{3}}|A | \e}
    \[^\mn{D}]Lou|\[G]var \[^\mn{C}]o \[\mnc{A}F]Cri\[^\mn{C}]a|\[C]dor \[\bm]{} \altchords{|E D |A}
  \mnendchorus
  \mnbeginchorus\memorize[chords_louvarocriador_b]
    \ind \[^\mn{C}]Por tu\[^\mn{B}]do o |\[\mnc{A}F]que já \[\bmc\mn{C}]es\[^\mn{E}]tá |\[\mnc{G}C]fei\[\mnc{E}(Am)]to \altchords{|D |A (F\shrp{}m)}
    \ind \[^\mn{A}]E tudo o |\[\mnc{E}C]que \[^\mn{C}]nos \[\mnc{A}F]en\[^\mn{C}]si|\[C]nou \[\bm]{} \altchords{|A D |A}
  \mnendchorus
  \mnbeginchorus\memorize[chords_louvarocriador_c]
    \ind[2] \[^\mn{A}]Lou|\[\mnc{D}G]var, \[^\mn{A}]lou\[\mnc{C}F]var lou|\[C]van\[\mnc{A}(Am)]do \altchords{|E D |A (F\shrp{}m)}
    \ind[2] Lou|\[\mnc{D}G]var \[^\mn{A}]o \[\mnc{C}F]Cria|\[C]dor \[\bm]{} \altchords{|E D |A}
  \mnendchorus
  \notesoff
  % verse two
  \beginchorus\replay[chords_louvarocriador_a]
    Di|^vi^no san|tíssi^mo
    Cora|^ção do ^Santo A|^mor ^
  \endchorus
  \beginchorus\replay[chords_louvarocriador_b]
    \ind A Ra|^inha ^da flo|^res^ta
    \ind Mãe do |^mestre en^sina|^dor ^
  \endchorus
  \beginchorus\replay[chords_louvarocriador_c]
    \ind[2] Pa|^pai, Ma^mãe tam|^bém
    \ind[2] ^Filho Es|^pírito ^Santo a|^mém ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative c''' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
        \mark \markup \with-color #darkgreen \italic "Final: toque tudo, mas parte A sem repetição"
      \repeat volta 2 {
        r8 \posectionmark "A" c4
        | g2( e4) a4 | e4.( e8) c4 d8( d)
        | d4 c4 a4 c4 | c2~ 8
      }
      \repeat volta 2 {
        \parenthesize c8 \sectionmark "B" c b
        | a4 a c e | g2 e8 \parenthesize a a a
        | e4 c a c | c2~ 8
      }
      \repeat volta 2 {
        r8 \sectionmark "C" a4
        | d4. a8 c4 c4 | c2 a4 a4
        | d4( d8) a8 c4 c4 | c2~ 8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Lou -- | var, __ _ lou -- | van -- _ do;
        Lou -- _ | var o Cri -- a -- | dor. _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Por tu -- do~o | que já es -- tá | fei -- to;
        E tu -- do~o | que nos en -- si -- | nou. _
      }
      \set stanza = "1.C"
      \repeat volta 2 {
        Lou -- | var, lou -- var lou -- | van -- do;
        Lou -- | var __ _ o Cri -- a -- | dor. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Di -- | vi -- no san -- | tís -- si -- mo;
        Co -- ra -- | ção do San -- to~A -- | mor. _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 A Ra -- | i -- nha da flo -- | res -- ta; __ _
        Mãe do | mes -- tre~en -- si -- na -- | dor. _
      }
      \set stanza = "2.C"
      \repeat volta 2 {
        Pa -- | pai, Ma -- mãe tam -- | bém;
        Fi -- lho~Es -- | pí -- ri -- to San -- to~a -- | mém. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1 | c | g2 f2 | c2~8
      }
      \repeat volta 2 {
        s4. | f1 | c2 \parenthesize a2:m | c2 f2 | c2~8
      }
      \repeat volta 2 {
        s4. | g2 f2 | c2 \parenthesize a2:m | g2 f2 | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    To praise, praising, to praise the Creator
    \nextverse
    \ind For all that is already been done, and all that taught us
    \nextverse
    \ind[2] To praise, praising, to praise the Creator
    \nextverse
    Holy Divine, heart of Holy Love
    \nextverse
    \ind The Queen of the forest, mother of the Master Teacher
    \nextverse
    \ind[2] Papa, Mama also, Son Holy Spirit Amen
  \end{translation}
\endsong


\beginsong{Tucum}[by={Padr. Alfredo}, key={C}, gk={C, (B)--(C)}, off={Samara Melo}]
  \audio{https://nossairmandade.com/hymn/4369/Tucum}
  \audio[key=C]{https://soundcloud.com/violeiro-daime/12-tucum?in=violeiro-daime/sets/hinario-nova-dimensao}
  \mnbeginchorus\memorize
    \[^\mn{G}]Eu |\[\mnc{C}C]me \[^\mn{G}]santi\[\bmc\mn{E}]fi\[^\mn{C}]co e |\[\mnc{D}G]minhas \[^\mn{E}]pa\[\mnc{C}C]la\[^\mn{A}]vras
    E |\[Am]guardo a \[\mnc{D}G]fé em |\[\mnc{E}C]mi\[^\mn{C}]nha me\[\bm]mória
    \lrep \[^\mn{C}]E |\[C]quando eu or\[\mnc{A}(Am7)]de\[^\mn{G}]no esse |\[\mnc{C}C]mal vai em\[\bmc\mn{E}]bora
    É em |\[^\mn{C}]nome \[^\mn{E}]de \[\mnc{G}G]Deus \[^\mn{D}]e de |\[G7]Nos\[^\mn{C}]sa Se\[C]nhora
    É em |nome \[^\mn{E}]de \[\mnc{G}G]Deus \[^\mn{D}]e de |\[G7]Nos\[^\mn{C}]sa Se\[C]nhora \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    E |^na minha ^linha ver|^dadeira e ^reta
    Li|^nha do Tu^cum A|^mor da Flo^resta
    \lrep Enxo|^tando os ^maus que não |^querem ou^vir
    A Jus|tiça do ^Mestre pa|^ra ser fe^liz
    A Jus|tiça do ^Mestre pa|^ra ser fe^liz \rrep
  \endchorus
  \begin{translation}[EN]
    I sanctify myself and my words
    And keep the faith in my memory
    \nextverse
    And when I give the order this evil goes away
    It's in the name of God and of Our Lady
    \nextverse
    And in my line true and straight
    Line of Tucum, Love of the Forest
    \nextverse
    Expelling the wicked that do not want to hear
    The Justice of the Master, in order to be happy
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative g'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 8
        g8 \posectionmark "A"
        | c4 g8 g8 e4 c8 c8 | d4 d8 e8 c4 a8 a8
        | a4 a8 a8 d4. d8 | e4 c8 c8 c4 c8
      \repeat volta 2 {
        c8 \sectionmark "B"
        | c4 c8 c8 a4 g8 g8 | c4 c8 c8 e4 e8 e8
        | c4 c8 e8 g4 d8 d8 | d4 c8 c8 c4 c8 c8
        | c4 c8 e8 g4 d8 d8
      } \alternative {
        { | d4 c8 c8 c4 c8 }
        { | d4 c8 c8 c4( c8) \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Eu | me san -- ti -- fi -- co e | mi -- nhas pa -- la -- vras;
      E | guar -- do a fé em | mi -- nha me -- mó -- ria.
      \set stanza = "1.B"
      \repeat volta 2 {
        E | quan -- do~eu or -- de -- no~es -- se | mal vai em -- bo -- ra;
        É~em | no -- me de Deus e de | Nos -- sa Se -- nho -- ra;
        É~em | no -- me de Deus e de
      } \alternative {
        { | Nos -- sa Se -- nho -- ra. }
        { | Nos -- sa Se -- nho -- ra. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      E | na mi -- nha li -- nha ver -- | da -- dei -- ra~e re -- ta;
      Li -- | nha do Tu -- cum A -- | mor da Flo -- res -- ta.~En
      \set stanza = "2.B"
      \repeat volta 2 {
        xo -- | tan -- do os maus que não | que -- rem ou -- vir;
        A Jus -- | ti -- ça do Mes -- tre pa -- | ra ser fe -- liz;
        A Jus -- | ti -- ça do Mes -- tre pa --
      } \alternative {
        { | ra ser fe -- liz. En }
        { | ra ser fe -- liz. __ _ }
      }
    }
    theChords = \chordmode {
      s8 | c1 | g2 c2 | a2:m g2 | c2.~8
      \repeat volta 2 {
        s8 | c2 \parenthesize a2:m7 | c1 | c2 g2 | g2:7 c2 | c2 g2
      } \alternative {
        { | g2:7 c4. }
        { | g2:7 c4. }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Só por Amor}[by={Padr. Alfredo},key={C},gk={C, (B)--(C)},off={Cecila Pineiros}]
  \audio{https://nossairmandade.com/hymn/4370/S\%C3\%B3PorAmor}
  \audio[key=C]{https://www.youtube.com/watch?v=U617-3tsLTI}
  \audio[key=C]{https://www.youtube.com/watch?v=0b2v8vsdTJQ}
  \newchords{chords_soporamor_a}\newchords{chords_soporamor_b}
  \meter{2}{4}
    \mnbeginchorus\memorize[chords_soporamor_a]
      |\[\mnc{C}C]Só \[^\mn{A}]por \[^\mn{B}]a|\[^\mn{G}]mor|\[^\mn{E}]{ } \e
      \[^\mn{A}]Mui\[^\mn{G}]to a|\[^\mn{C}]mor | \e
      É |\[\mnc{D}Dm]que es|\[\mnc{E}Am/E]pando esta |\[\mnc{C}C]luz | \e
    \mnendchorus
    \mnbeginchorus\memorize[chords_soporamor_b]
      \ind \[^\mn{C}]Essa |\[\mnc{F}F]trilha que |estou \[^\mn{G}]an|\[^\mn{A}]dan|do
      \ind É \[^\mn{G}]a |\[\mnc{E}C]mesma que |an\[^\mn{G}]dou Je|\[G]sus | \e
      \ind \lrep \[^\mn{B}]Es\[^\mn{C}]te |\[\mnc{D}Dm]mes\[^\mn{C}]tre \[^\mn{B}]a|\[^\mn{D}]qui \[^\mn{C}]en\[^\mn{B}]si|\[\mnc{A}G]nan\[^\mn{G}]do | \e
      \ind \[^\mn{C}]Com \[^\mn{D}]o |\[\mnc{E}Am]simbo\[^\mn{G}]lo |\[\mnc{D}G]da San\[^\mn{E}]ta |\[\mnc{C}C]Cruz | \e \rrep
    \mnendchorus
    \notesoff
    \beginchorus\replay[chords_soporamor_a]
      |^Fitando a |lu|a
      Ao lu|ar | \e
      Domi|^nando |^{em harmo}|^ni|a
    \endchorus
    \beginchorus\replay[chords_soporamor_b]
      \ind O a|^mor de |Deus coman|dan|do
      \ind O as|^tral com |toda ale|^gri|a
      \ind \lrep Viva |^nós e o |nosso pla|^neta | \e
      \ind Dando |^viva a |^Virgem Ma|^ri|a \rrep
    \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative c''' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 2/4 \partial 4
      \repeat volta 2 {
        r4 \posectionmark "A"
        | c4 a8 b8 | g2( | e4) a8 g | c,2~ | c4 c8( c)
        | d4. d8 | e4 e8 e | c2( | c4)
      }
      \repeat volta 2 {
        c8 \sectionmark "B:a" c | f4 \parenthesize f8 f8 | f4 f8 g8 | a2 | a4 a8 g8
        | e4 \parenthesize e8 e8 | e4 g8 g8 | g2~ | g4 \break
        b,8 \sectionmark "B:b:i" c8
        | d4 c8 b8 | d4 c8 b8 | a4 g4~ | g4 c8 d8
        | e4 e8 g8 | d4 d8 e8 | c2~ | c4 \break
        b8 \sectionmark "B:b:ii" c8
        | d4 c8 b8 | d4 c8 b8 | a4 g4~ | g4 c8 d8
        | e4 e8 g8 | d4 d8 e8 | c2~ | c4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        | Só por a -- | mor; __ | _
        Mui -- to~a -- | mor; | _
        É __ _ | que es -- | pan -- do~es -- ta | luz. | _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Es -- sa | tri -- lha que | es -- tou an -- | dan -- | do;
        É a | mes -- ma que | an -- dou Je -- | sus. | _
        Es -- te | mes -- tre a -- | qui en -- si -- | nan -- do; | _
        Com o | sim -- bo -- lo | da San -- ta | Cruz. __ | _
        Es -- te | mes -- tre a -- | qui en -- si -- | nan -- do; | _
        Com o | sim -- bo -- lo | da San -- ta | Cruz. __ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        | Fi -- tan -- do~a | lu -- | a;
        Ao lu -- | ar; | _
        Do -- mi -- | nan -- do | em har -- mo -- | ni -- | a.
      }
      \set stanza = "2.B"
      \repeat volta 2  {
        O a -- | mor \skip 1 de | Deus co -- man -- | dan -- | do;
        O as -- | tral \skip 1 com | to -- da~a -- le -- | gri -- | a.
        Vi -- va | nós e o | nos -- so pla -- | ne -- ta; | _
        Dan -- do | vi -- va a | Vir -- gem Ma -- | ri -- | a.
        Vi -- va | nós e o | nos -- so pla -- | ne -- ta; | _
        Dan -- do | vi -- va a | Vir -- gem Ma -- | ri -- | a.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4
        | c2 | c | c | c | c
        | d:m | a:m/e | c | c4
      }
      \repeat volta 2 {
        s4
        | f2 | f | f | f | c | c | g | g
        | d:m | d:m | g | g | a:m | g | c | c
        | d:m | d:m | g | g | a:m | g | c | c4
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Only through love, much love
    Is this light expanding
    \nextverse
    This path that I am walking is the same as Jesus walked
    This master here teaching with the symbol of the Holy Cross
    \nextverse
    Gazing at the moon, at the moonlight
    Orchestrating in harmony
    \nextverse
    The love of God commanding the astral with total joy
    Viva us and our planet, giving Viva to the Virgin Mary
  \end{translation}
\endsong


\beginsong{Bastão}[by={Padr. Alfredo},key={C},gk={C, B\flt{}--D},off={Vicente e o povo do Japão}]
  \audio[key=C]{https://www.youtube.com/watch?v=Bxypv25DNsE}
  \audio{https://nossairmandade.com/hymn/4417/Bast\%C3\%A3o}
  \mnbeginchorus\memorize
    \[^\mn{C}]É se|\[\mnc{D}Dm]guir o \[^\mn{A}]nos\[^\mn{B}]so \[\mnc{C}C]mestre \altchords{\id[1]{(D)}|Em D}
    Den\[^\mn{E}]tro |\[^\mn{G}]da vossa ins\[^\mn{E}]tru\[\bmc\mn{G}]ção \altchords{| \e}
    E po|\[\mnc{A}Dm]der \[^\mn{G}]se \[^\mn{F}]le\[^\mn{E}]van\[\mnc{C}F]tar \altchords{|Em G}
    Com a \[^\mn{E}]su|\[\mnc{D}G7]a ca\[^\mn{A}]du\[^\mn{B}]ca\[\mnc{C}C]ção \altchords{|A7 D}
  \mnendchorus
  \notesoff
  \beginchorus
    É se|^guindo a instru^ção
    Papai |velho e mamãe ^velha
    Mamãe |^velha sempre ^dá
    E pa|^pai acari^nhar
  \endchorus
  \beginchorus
    Sou eu |^nasci em Na^tal
    Vós me |dê o meu bas^tão
    Sou |^eu sou, eu sou ^eu
    Com a mi|^nha caduca^ção
  \endchorus
  \beginchorus
    Viva os |^mestres desta es^cola
    Atra|vés dos nossos ^hinos
    Viva o |^nosso Cria^dor
    E to|^dos Seres Di^vinos
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        c8 \pomark c8 | d8 d8 a8 b8 c8( c8) c8 e8
        | g8 g8 g8 e8 g8( g8 g8) g8
        | a8 g8 f8 e8 c8( c8) c8 e8
        | d8 d8 a8 b8 c8( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        É se -- | guir o nos -- so mes -- tre;
        Den -- tro | da vos -- sa~ins -- tru -- ção; __ _
        E po -- | der se le -- van -- tar;
        Com a su -- | a ca -- du -- ca -- ção. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        É se -- | guin -- do~a ins -- tru -- ção; __ _
        Pa -- pai | ve -- lho~e ma -- mãe ve -- lha;
        Ma -- mãe | ve -- lha sem -- pre dá; __ _
        E pa -- | pai a -- ca -- ri -- nhar. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Sou eu | nas -- ci em Na -- tal; __ _
        Vós me | dê o meu bas -- tão; __ _ _
        Sou | eu sou, eu sou eu;
        Com a mi -- | nha ca -- du -- ca -- ção. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Vi -- va~os | mes -- tres des -- ta~es -- co -- la;
        A -- tra -- | vés dos nos -- sos hi -- nos;
        Vi -- va~o | nos -- so Cri -- a -- dor; __ _
        E to -- | dos Se -- res Di -- vi -- nos.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d2:m c | c c | d:m f | g:7 c4
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    It is following our master within your instruction
    And being able to stand up with your aging
    \nextverse
    It is following the instruction, elder papa and elder mama
    Elder mama always gives, and papa cares
    \nextverse
    I was bor on Christmas, you give me my staff
    It's me, it's me, it's me, with my aging
    \nextverse
    Long live the masters of this school, through our hymns
    Long live our Creator and all Divine Beings
  \end{translation}
\endsong


\beginsong{Vida}[by={Padr. Alfredo},key={Am},gk={Am},off={Ramaiam, Ana Rita, Igor}]
  \audio[key={Am}]{https://www.youtube.com/watch?v=Xboe1-JfM_Y}
  \mnbeginchorus\memorize
    \[^\mn{A}]Vida \[^\mn{C}]São |\[\mnc{E}Am]João, vida \[\mnc{D}(E7/D)]meu \[^\mn{E}]Je|\[\mnc{A}Am]sus \[^\bm]
    A \[^\mn{C}]lu\[^\mn{E}]a |\[^\mn{A}]cheia, seu bri\[\mnc{G}{A7}]lho \[^\mn{A}]re|\[\mnc{D}Dm]luz \[^\bm]
    \lrep \[^\mn{A}]É tão bo|\[\mnc{B}Bm7&5]ni\[^\mn{A}]to, o poder \[\mnc{F}(Dm/F)]da \[^\mn{D}]fo\[^\mn{F}]gue|\[Am]i\[^\mn{E}]ra
    Queima a \[\mnc{C}(C)]noit\[^\mn{A}]e in\[^\mn{E}]te|\[E7]i\[^\mn{D}]ra, mis\[^\mn{C}]té\[^\bm\mn{B}]rio \[^\mn{C}]da |\[\mnc{A}Am]Cruz \[^\bm]{} \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    Esta lem|^brança é da e^terni|^da\[\bm]de
    Esta ver|dade nos e^leva as|^sim \[\bm]
    \lrep Lembrando |^sempre a Luz ^deste di|^{'a}
    Oh Vir^gem Mari|^{'a}, vós lem\[\bm]brai de |^mim \[\bm]{} \rrep
  \endchorus
  \beginchorus
    Aqui na |^Terra a vida é ^como |^é
    Domina|dor da vida é ^São Jo|^sé \[\bm]
    \lrep Oh Patri|^arca, nos as^cenda Lu|^z
    Vida ^meu Jesu|^s, Espe\[\bm]rança e |^Fé \[\bm]{} \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-08
    theMelody = \relative a' {
            \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      a8\posectionmark "A" a c | e8 e8 e8 e8 d4 e | a,2( a8) a8 c e
      | a8 a8 a8 a8 g4 a4 | d,2~ d8
      \repeat volta 2 {
        a'8\sectionmark "B" a a | b a a a f4 d8 f8~ | f8 e8 e8 e8 c4 a8 e'8~
        | e8 d( d) c8 b4 c4 | a2~ a8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
        Vi -- da São | Jo -- ão
        Vi -- da meu Je -- | sus; __ _
        A lu -- a | chei -- a
        seu bri -- lho re -- | luz. __ _
      \repeat volta 2 {
        É tão bo -- | ni -- to~o po -- der da fo -- guei -- _ ra;
        Quei -- ma~a noi -- te~in -- tei -- _ ra
        mis -- té -- rio da | Cruz. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Es -- ta lem -- | bran -- ça~é
      da e -- ter -- ni -- | da -- de;
      Es -- ta ver -- | da -- de
      nos e -- le -- va~as -- | sim. __ _
      \repeat volta 2 {
        Lem -- bran -- do | sem -- pre
        a Luz des -- te di -- _ a;
        Oh Vir -- gem Ma -- ri -- _ a
        Vós lem -- brai de | mim. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      A -- qui na | Ter -- ra~a
      vi -- da~é co -- mo | é; __ _
      Do -- mi -- na -- | dor da vi -- da~é
      São Jo -- | sé. __ _
      \repeat volta 2 {
        Oh Pat -- ri -- | ar -- ca
        nos a -- scen -- da Luz; __ _
        \skip 1 Vi -- da meu Je -- sus __ _
        Es  -- _ pe -- ran -- ça~e | Fé. __ _
      }
    }
    theChords = \chordmode {
      s4. | a2:m \parenthesize e:7/d | a1:m | a2:m a:7 | d2:m~ d8:m
      \repeat volta 2 {
         s4. | b2:m7.5- \parenthesize d:m/f | a2:m \parenthesize c | e1:7 | a2:m~ a8:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % to fit all on one spread
    \include "tex/lp-include-tail-lyricsbetween.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]\iflyriconly\else\scriptsize\fi % to fit on one spread in chorded book
    Life (of) Saint John, life (of) my Jesus
    The full moon, its glow shines
    It's so beautiful, the power of the fire
    Burn all night, mystery of the Cross
    \nextverse
    This memory is from eternity
    This truth lifts us like this
    Always remembering the Light of this day
    Oh Virgin Mary, you remember me
    \nextverse
    Here on Earth, life is what it is
    Ruler of life is St. Joseph
    Oh Patriarch, ascend us to Light
    Life my Jesus, Hope and Faith
  \end{translation}
\endsong


\beginsong{O Rigor das Profecias}[by={Padr. Alfredo},key={C},gk={C, B\flt{}--B--(C)},off={Vinícius Antonelli e Família}]
  \audio[key=C]{https://www.youtube.com/watch?v=ChkGIAhjlEs}
  \mnbeginchorus\memorize
    \[^\mn{G}]Todo |\[\mnc{C}C]di\[^\mn{G}]a eu \[^\mn{F}]ob\[\bmc\mn{E}]ser\[^\mn{C}]vo
    O \[^\mn{E}]rig|\[\mnc{D}G]or \[^\mn{E}]das \[^\mn{D}]pro\[^\mn{C}]fe\[\mnc{E}C]ci\[^\mn{C}]as
    Oh \[^\mn{E}]mi|\[\mnc{G}Am]nhas \[^\mn{A}]Santas Ma\[\mnc{E}C]ri\[^\mn{G}]as
    Nos es|\[\mnc{D}G]tendam as vos\[^\mn{C}]sas \[\mnc{E}C]mãos
    \lrep | \[^\mn{C}]Nos \[^\mn{D}]dê \[^\mn{C}]a \[\mnc{A}Am]cura
    \[^\mn{C}]Cura |\[\mnc{D}Dm]da \[^\mn{C}]nos\[^\mn{D}]sa \[^\mn{C}]Dou\[\mnc{E}C]tri\[^\mn{C}]na
    De \[^\mn{E}]bri|\[\mnc{G}Am]lhan\[^\mn{A}]tes pedras \[\bmc\mn{E}]finas
    \[^\mn{G}]Jesus |\[\mnc{D}G7]Cristo e \[^\mn{E}]São \[^\mn{C}]Jo\[C]ão \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    Novo |^mundo, novo ^povo
    Anunci|^ado por Je^sus
    Que mos|^trou na Santa ^Cruz
    O Misté|^rio da Salva^ção
    \lrep | Agrade^cer esta |^escola di^vina
    E aos Mes|^tres que nos en^sinam
    Jesus |^Cristo e São Jo^ão \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative g'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
       g8 \posectionmark "A" g8
       | c8 g8 g8 f8 e8 c8 c8 e8 | d8 e8 d8 c8 \once\slurUp e8( << e8) \single\altcol c8 \altmark "1." >> c8 e8
       | g8 a8 a8 a8 e8 g8 g8 g8 | d8 d8 d8 c8 e2
      \repeat volta 2 {
        | r8 \sectionmark "B" c8 d8 c8 a8( a8) c8 c8 | d8 c8 d8 c8 e8 c8 c8 e8
        |  g8 a8 a8 a8 e8 e8 g8 g8
      } \alternative {
        { | d8 d8 e8 c8 c2 }
        { | d8 d8 e8 c8 c4 \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      To -- do | di -- a eu ob -- ser -- vo;
      O rig -- | or das pro -- fe -- ci -- as;
      Oh mi -- | nhas San -- tas Ma -- ri -- as;
      Nos es -- | ten -- dam~as vos -- sas mãos.
      \set stanza = "1.B"
      \repeat volta 2 { %|
        Nos dê a cu -- ra
        Cu -- ra | da nos -- sa Dou -- tri -- na;
        De bri -- | lhan -- tes pe -- dras fi -- nas;
        Je -- sus
      } \alternative {
        { | Cris -- to~e São Jo -- ão. }
        { | Cris -- to~e São Jo -- ão. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      No -- vo | mun -- do, no -- vo po -- vo;~A
      nun -- ci -- | a -- do por Je -- sus; __ _
      Que mos -- | trou na San -- ta Cruz;
      O Mis -- té -- | rio da Sal -- va -- ção.
      \set stanza = "2.B"
      \repeat volta 2 { %|
        A -- gra -- de -- cer __ _ es -- ta | es -- co -- la di -- vi -- na;~E
        aos Mes -- | tres que nos en -- si -- nam;
        Je -- sus
      } \alternative {
        { | Cris -- to~e São Jo -- ão. }
        { | Cris -- to~e São Jo -- ão. }
      }
    }
    theChords = \chordmode {
      s4 | c1 | g2 c | a:m c | g c
      \repeat volta 2 {
        | c2 a2:m | d2:m c | a:m a:m
      } \alternative {
        { | g:7 c }
        { | g:7 c4 }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Every day I observe the rigor of the prophecies
    Oh my Holy Marys, extend your hands to us
    Give us the healing, healing of our Doctrine
    Of shining precious stones, Jesus Christ and Saint John
    \nextverse
    New world, new people, announced by Jesus
    That showed on the Holy Cross, the Mystery of Salvation
    Thanks to this divine school, and to the Masters who teach us
    Jesus Christ and Saint John
  \end{translation}
\endsong


\beginsong{Santa Cura}[by={Padr. Alfredo},key={C},gk={C, C--D}]
  \newchords{chords_santacura_a}\newchords{chords_santacura_b}
  \mnbeginchorus\memorize[chords_santacura_a]
    \[^\mn{G}]Santa |\[\mnc{C}C]cura \[\bm]san\[^\mn{E}]ta |\[^\mn{G}]cura \altchords{\id[1]{(D)}|D | \e}
    \[\bm]San\[^\mn{A}]ta |\[^\mn{E}]cu\[^\mn{G}]ra \[\mnc{D}G]do \[^\mn{C}]a|\[\mnc{E}C]mor \[\bm] \altchords{| - A |D}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_santacura_b]
    \[^\mn{A}]Para |\[F]nun\[^\mn{G}]ca \[Am7]{se es}que|\[\mnc{D}Dm]cer \altchords{|G Bm7 |Em}
    \[\bmc\mn{F}]Do \[^\mn{E}]di|\[\mnc{G}Dsus4]vi\[^\mn{F}]no \[\mnc{E}Dsus2]cu\[^\mn{D}]ra|\[\mnc{G}G]dor \[\bm] \altchords{|Esus4 Esus2 |A}
    \[^\mn{A}]Para |\[F]sem\[^\mn{G}]pre \[Am7]{se lem}|\[\mnc{D}Dm]brar \altchords{|G Bm7 |Em}
    \[\bmc\mn{F}]Do \[^\mn{E}]e|\[\mnc{G}G]ter\[^\mn{F}]no \[\mnc{E}G7]cri\[^\mn{D}]a|\[\mnc{C}C]dor \[\bm] \altchords{|A A7 |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_santacura_a]
    Estudo |^fino es^tudo |fino
    ^É pre|ciso ^compreen|^der ^
    \endchorus\glueverses\beginchorus\replay[chords_santacura_b]
    Disse o |^nosso a^migo |^velho
    ^Somos |^somos e ^deve |^ser ^
    Para |^sempre A^mém Je|^sus
    ^Pronto |^para ^nos va|^ler ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-12
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize g8 \posectionmark "A" g8 g
        | c4 c c e | g4. g8 g4 a4
        | e g d c | e2~8
      } \break
      \repeat volta 2 {
        r8 a8 \sectionmark "B" a
        | a4 g g g | d4.( d8) f4. e8
        | g4 f8( f8) e4 d | g2. \break
        a8 a
        | a4 g g g | d2 f4. e8
        | g4 f e d | c2~8
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        \skip 1 San -- ta | cu -- ra san -- ta | cu -- ra;
        San -- ta | cu -- ra do a -- | mor. _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Pa -- ra | nun -- ca se~es -- que -- | cer; __ _
        Do di -- | vi -- no __ _ cu -- ra -- | dor;
        Pa -- ra | sem -- pre se lem -- | brar;
        Do e -- | ter -- no cri -- a -- | dor. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Es -- tu -- do | fi -- no~es -- tu -- do | fi -- no;
        É pre -- | ci -- so com -- preen -- | der. _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Dis -- se~o | nos -- so~a -- mi -- go | ve -- lho;
        So -- mos | so -- mos e de -- ve | ser;
        Pa -- ra | sem -- pre~A -- mém Je -- | sus;
        Pron -- to | pa -- ra nos va -- | ler. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1 | c | c2 g2 | c2~8
      }
      \repeat volta 2 {
        s4. | f2 a2:m7 | d1:m | d2:sus4 d2:sus2 | g2~8
        s4. | f2 a2:m7 | d1:m | g2 g2:7 | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Holy healing, holy healing, holy healing of love
    Never to forget the divine healer
    Forever to remember the eternal creator
    \nextverse
    Fine study, fine study; it is necessary to understand
    Said our old friend; we are, we are, and it must be
    Forever, Amen, Jesus, ready to help us
  \end{translation}
\endsong


\beginsong{Renascer}[by={Padr. Alfredo},key={C},gk={C, G\shrp{}--B--(C)}]
  \audio[key=C]{https://www.youtube.com/watch?v=XyyjCz_9CII}
  \mnbeginchorus\memorize
    \[^\mn{E}]Fa|\[C]la\[\bmc\mn{C}]ram, \[^\mn{E}]dis|se\[^\mn{C}]ram, \[\bm]en\[^\mn{E}]si|\[\mnc{F}Fmaj7]na\[^\mn{E}]ram \[\bmc\mn{D}]com \[^\mn{C}]a|\[\mnc{B}G]mor \[\bm]
    No |Rio \[\bm]de \[^\mn{C}]Jor|\[\mnc{D}Dm]dão o \[\bm]Bati|\[G]zado \[\bmc\mn{E}]se \[^\mn{F}]Tra|\[\mnc{E}C]çou
    \lrep \[^\bmc\mnvii{E}{C}]Aqui |\[\mnc{C}C]na nos\[\bm]sa mis|\[\mnc{F}F]são o \[\bm]nosso |\[\mnc{A}Am]Mestre \[\bm]Re\[^\mn{G}]plan|\[\mnc{C}C]tou
    \[\bmc\mn{G}]Doutri|\[\mnc{A}G]na \[^\mn{G}]de \[\bm]Jesus |\[\mnc{D}Dm]Cristo \[\bm]do nos|\[\mnc{G}G]so Pai \[\bmc\mn{D}]Cri\[^\mn{E}]a|\[\mnc{C}C]dor. \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    É |^nos^sa Es|cola, ^é o |^nosso ^Profes|^sor ^
    O |nosso ^Tempo\jw é |^este, ^vamos |^todos ^dar lou|^vor \[\bm]
    \lrep Pe|^dir a ^nossa |^Mãe, a ^vossa |^Chama ^do a|^mor
    I^lumi|^nar\jw o nos^so per|^dão e ^se fir|^mar no ^Cria|^dor. \[\bm] \rrep
  \endchorus
  \beginchorus
    Con|^fi^a, con|fi^a, con|^fia ^no po|^der ^ \altchords{\id[1]{(A)}|A | |Dmaj7 |E}
    O |nosso ^Mestre |^diz:^ con|^fia ^no sa|^ber \[\bm] \altchords{| |Bm |E |A}
    \lrep Lem|^brar Ju^rami|^dam, ^vê o |^{dia\jw A}^manhe|^cer ^ \altchords{|A |D |F\shrp{}m |A}
    Na |^luz do ^Santo |^Daime, ^vamos |^todos ^Renas|^cer. \[\bm] \rrep \altchords{|E |Bm |E |A}
  \endchorus
  \begin{translation}[EN]
    They spoke, they said, they taught with love
    In the Jordan River the Baptism was drawn out
    Here in our mission our Master replanted
    Doctrine of Jesus Christ from our Creator Father
    \nextverse
    It is our School, it is our Teacher
    This is our Time, let us all give praise
    Ask for our Mother, your flame of love
    To illuminate our pardon and be established on the Creator
    \nextverse
    Trust, trust, trust in power
    Our Master says: trust in knowledge
    Remember Juramidam, see the dawn breaking
    In the light of Santo Daime, let us all Reborn
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2024-11
    % \header {
    %   title = "Renascer (Nova Dimensão #18)"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \tempo 4 = 155
      \key a \minor \time 4/4 \partial 2
      \set melismaBusyProperties = #'() \slurDashed
      \repeat segno 2 {
        \slurUp
        \sectionLabel "A"
        r4 \pomark e4 | e2 c4 e4 | e4. \altmark "3." \single\altcol ( << \single\altcol e8 ) \parenthesize c8 >> c4 e4 | f e d c | b2. \slurNeutral
        b4 | b b b c | d4.( d8 d4) d | d d e f | e2
        \repeat volta 2 {
          \sectionLabel "B"
          \parenthesize << \parenthesize e4 \parenthesize \single\altcol c \altmark "ii" >> << e \single\altcol c >> | c c c c | f4.( f8) f4 f | a a a g | c4.( c8)
          g4 g | a g g g | d4. d8 d4 d | g g d e | c2
        }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat segno 2 {
        Fa -- | la -- ram, dis -- | se -- ram, en -- si -- | na -- ram com a -- | mor;
        No | Ri -- o de Jor -- | dão o Ba -- ti -- | za -- do se Tra -- | çou;
        \repeat volta 2 {
          A -- qui | na nos -- sa mis -- | são o nos -- so | Mes -- tre Re -- plan -- | tou; __ _
          Dou -- tri -- | na de Je -- sus | Cris -- to do nos -- | so Pai Cri -- a -- | dor.
        }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat segno 2 {
        É | nos -- sa Es -- | co -- la é o | nos -- so Pro -- fes -- | sor;
        O | nos -- so Tem -- po~é | es -- te, va -- mos | to -- dos dar lou -- | vor;
        \repeat volta 2 {
          "" Pe -- | dir a nos -- sa | Mãe, a vos -- sa | Cha -- ma do a -- | mor;
          I -- lu -- mi -- | nar~o nos -- so per -- | dão e se fir -- | mar no Cri -- a -- | dor.
        }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat segno 2 {
        Con -- | fi -- a, con -- | \altcol fi _ -- a, con -- | fi -- a no po -- | der;
        O | nos -- so Mes -- tre | diz: __ _ _ con -- | fi -- a no sa -- | ber;
        \repeat volta 2 {
          "" Lem -- | brar Ju -- ra -- mi -- | dam, __ _ vê o | di -- a~A -- ma -- nhe -- | cer; __ _
          "" Na | luz do San -- to | Dai -- me, va -- mos | to -- dos Re -- nas -- | cer.
        }
      }
    }
    theChords = \chordmode {
      \repeat segno 2 {
        s2 | c1 | c | f:maj7 | g
        | g | d:m | g | c2 % original sounds like e2:m here
        \repeat volta 2 {
          s2 | c1 | f | a:m | c
          | g1 | d:m | g | c2
        }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Infinitum}[by={Padr. Alfredo},key={C},gk={C, (B)--(C)}]
  \audio[key=C]{https://www.youtube.com/watch?v=W_n68txBRiM}
  \audio[key=C]{https://soundcloud.com/hinos-santo-daime/19-infinitum}
  \mnbeginchorus\memorize
    \[^\mn{G}]Infi\[^\mnc{C}]ni|\[\mnc{G}C]tum, \[\bmc\mn{E}]estou \[^\mn{D}]na \[^\mn{E}]flo|\[^\mn{D}]res\[^\mn{C}]ta \[Am]
    \[^\mn{A}]{E nesta} |\[\mnc{D}Dm]festa \[G] eu sou \[^\mn{E}]mais |\[\mnc{C}C]um \[\bm]
    \lrep \[^\mn{C}]Toda\jw a flo|\[\mnc{A}Am]res\[^\mn{G}]ta,\[\bm] \[^\mn{C}]está em |\[\mnc{E}C]festa \[G7]
    \[^\mn{D}]Infini|\[\mnc{C}C]tum \[\bm] \rrep
  \mnendchorus
  \notesoff
  \beginchorus\replay
    E nesta |^casa^ da Virgem |Mãe
    ^Para nós can|^tar, ^ com todo\jw a|^mor ^
    \lrep O nosso |^Mestre^ é Jesus |^Cristo^
    Nosso Se|^nhor ^ \rrep
  \endchorus
  \beginchorus\replay
    Essa es|^cola^ é da Ra|inha^
    E Jesus |^Cristo^ Renden|^tor ^
    \lrep Para lou|^var,^ o Pai E|^terno^
    Rei Cria|^dor ^ \rrep
  \endchorus
  \beginchorus\replay
    Cante|^mos,^ manos can|temos^
    Nossa Dou|^trina,^ é só lou|^var ^
    \lrep A Divin|^dade,^ desta flo|^resta^
    Deste Lu|^gar ^ \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2024-11
    % \header {
    %   title = "Infinitum (Nova Dimensão #19)"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative g'' {
      \tempo 4 = 119
      \key c \major \time 4/4 \partial 4.
      \set melismaBusyProperties = #'() \slurDashed
      \repeat segno 2 {
        \sectionLabel "A"
        g8 \pomark g8 c8 | g4( g4) \parenthesize e8 e d e | d4( c4)
        \parenthesize a8 a a a | d4( d4.) \parenthesize d8 d e | c2~8
        \repeat volta 2 {
          \sectionLabel "B"
          c8 c c | a4( g4.) c8 c c | e4 e4.
          d8 d d | c2~8
        }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat segno 2 {
        In -- fi -- ni -- | tum, __ _ es -- tou na flo -- | res -- ta;
        "" E nes -- ta | fes -- ta eu sou mais | um. _
        \repeat volta 2 {
          \set stanza = "1.B"
          To -- da~a flo -- | res -- ta, es -- tá em | fes -- ta;
          In -- fi -- ni -- | tum. _
        }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat segno 2 {
        E nes -- ta | ca -- sa "" da Vir -- gem | Mãe; __ _
        Pa -- ra nós can -- | tar, __ _ com to -- do~a -- | mor. _
        \repeat volta 2 {
          \set stanza = "2.B"
          O nos -- so | Mes -- tre é Je -- sus | Cris -- to;
          Nos -- so Se -- | nhor. _
        }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat segno 2 {
        Es -- sa es -- | co -- la "" é da Ra -- | i -- nha;
        "" E Je -- sus | Cris -- to "" Ren -- den -- | tor. _
        \repeat volta 2 {
          \set stanza = "3.B"
          Pa -- ra lou -- | var, __ _ o Pai E -- | ter -- no;
          Rei Cri -- a -- | dor. _
        }
      }
    }
    theLyricsFour  = \lyricmode {
      \set stanza = "4."
      \repeat segno 2 {
        "" Can -- te -- | mos, __ _ "" ma -- nos can -- | te -- mos;
        "" Nos -- sa Dou -- | tri -- na, é só lou -- | var. _
        \repeat volta 2 {
          \set stanza = "4.B"
          A Di -- vin -- | da -- de, des -- ta flo -- | res -- ta;
          Des -- te Lu -- | gar. _
        }
      }
    }
    theChords = \chordmode {
      \repeat segno 2 {
        s4. | c1 | c2 a:m
        | d2:m g | c2~8
        \repeat volta 2 {
          s4. | a1:m | c2 g:7 | c2~8
        }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    \emph{Infinitum}, I'm in the forest; and at this party, I'm just another one
    The whole forest is celebrating, \emph{Infinitum}
    \nextverse
    And in the Virgin Mother's house we sing with all our love
    Our Master is Jesus Christ, our Lord
    \nextverse
    This school is of the Queen and Jesus Christ, the Redeemer
    To praise the Eternal Father, Creator King
    \nextverse
    Let's sing, let's sing, our Doctrine is only to praise
    The Divinity of this forest, of this place
  \end{translation}
\endsong


\beginsong{Centenário Integração}[by={Padr. Alfredo},key={G},gk={G, G--A}]
  \audio[key=G]{https://nossairmandade.com/hymn/4798/Centen\%C3\%A1rioIntegra\%C3\%A7\%C3\%A30}
  \audio[key=G]{https://www.youtube.com/watch?v=sYeyJCaThsA}
  \audio[key=G]{https://www.youtube.com/watch?v=7OjNdTDPVo0}
  % verse 1
  \mnbeginchorus\memorize
    \[^\mn{G}]A\[^\mn{B}]qui \[^\mn{D}]eu |\[\mnc{G}G]volto a lem\[\bm]brar \[^\mn{F#}]os \[^\mn{A}]meus \[^\mn{E}]ir|\[C]mãos \[\bm] \altchords{|A |D}
    \[^\mn{C}]De \[^\mn{D}]Je\[^\mn{E}]sus |\[\mnc{F#}D]Cristo\jw e do meu \[\bm]Se\[^\mn{E}]nhor \[^\mn{G}]São \[^\mn{F#}]Jo|\[\mnc{D}G]ão \[\bm] \altchords{|E |A}
    \lrep \[^\mn{D}]Bati|\[\mnc{C}C]zando lá no \[\mnc{D}D]Rio de Jor|\[\mnc{B}Bm]dão \[\bm] \altchords{|D E |Am}
    \[^\mn{D}]Ilumi|\[\mnc{A}Am]nando com a \[\mnc{B}Bm]cura do per|\[\mnc{G}G]dão \[\bm] \rrep \altchords{|Bm |C\shrp{}m |A}
  \mnendchorus
  \notesoff
  % verse 2
  \beginchorus
    Aqui na |^mata feste^jamos São Jo|^ão ^
    Todos |^Santos e\jw a Vir^gem da Concei|^ção ^
    \lrep O cente|^nário da nos^sa Senhora |^Mãe ^
    Eterna |^força, dessa ^grande\jw integra|^ção ^ \rrep
  \endchorus
  % verse 3
  \beginchorus
    Toda\jw irman|^dade dessa ^nossa expan|^são ^
    Rogar a |^Deus com a^mor no cora|^ção ^
    \lrep Ter nossa |^Mãe, fé e ^considera|^ção ^
    O Pai e|^terno é Rei ^da integra|^ção ^ \rrep
  \endchorus
  % verse 4
  \beginchorus
    Sabedo|^ria\jw é do Se^nhor Rei Salo|^mão ^
    Força\jw e Po|^der ele traz ^na palma da |^mão ^
    \lrep O nosso |^Mestre ensi^nando\jw os seus ir|^mãos ^
    Cantando\jw hi|^nário, afir^mando\jw a uni|^ão ^ \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2025-12
    % \header {
    %   title = "Centenário Integração (Nova Dimensão #20)"
    %   composer = "Padr. Alfredo"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key g \major \slurDashed
      \set melismaBusyProperties = #'()
      \time 4/4 \partial 4.
      \sectionLabel "A"
      \repeat segno 2 {
        g8 \pomark b d | g g g g g fis a e | e2~8
        \parenthesize c8 d e | fis( fis) fis fis fis e g fis | d2~8
        \break
        \sectionLabel "B"
        \repeat volta 2 {
          \parenthesize d8 d d | c( c) c c d d d d | b2~8
          d8 d d | a a a a b b b b | g2~8
        }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat segno 2 {
        A -- qui eu | vol -- to a lem -- brar os meus ir -- | mãos; _
        De Je -- sus | Cris -- to~e do meu Se -- nhor São Jo -- | ão. _
        \repeat volta 2 {
          \set stanza = "1.B"
          "" Ba -- ti -- | zan -- do lá no Ri -- o de Jor -- | dão; _
          I -- lu -- mi -- | nan -- do com a cu -- ra do per -- | dão. _
        }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat segno 2 {
        A -- qui na | ma -- ta fes -- te -- ja -- mos São Jo -- | ão; _
        "" To -- dos | San -- tos e~a Vir -- gem da Con -- cei -- | ção. _
        \repeat volta 2 {
          \set stanza = "2.B"
          O cen -- te -- | ná -- rio da nos -- sa Se -- nho -- ra | Mãe; _
          E -- ter -- na | for -- ça, des -- sa gran -- de~in -- te -- gra -- | ção. _
        }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat segno 2 {
        To -- da~ir -- man -- | da -- de des -- sa nos -- sa ex -- pan -- | são; _
        Ro -- gar a | Deus __ _ com a -- mor no co -- ra -- | ção. _
        \repeat volta 2 {
          \set stanza = "3.B"
          Ter nos -- sa | Mãe, __ _ fé e con -- si -- de -- ra -- | ção; _
          O Pai e -- | ter -- no é Rei da in -- te -- gra -- | ção. _
        }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat segno 2 {
        Sa -- be -- do -- | ri -- a~é do Se -- nhor Rei Sa -- lo -- | mão; _
        For -- ça~e Po -- | der e -- le traz na pal -- ma da | mão. _
        \repeat volta 2 {
          \set stanza = "4.B"
          O nos -- so | Mes -- tre en -- si -- nan -- do~os seus ir -- | mãos; _
          Can -- tan -- do~hi -- | ná -- rio, a -- fir -- man -- do~a u -- ni -- | ão. _
        }
      }
    }
    theChords = \chordmode {
      \repeat segno 2 {
        s4. | g1 | c | d | g2~8
        \repeat volta 2 {
          s4. | c2 d2 | b,1:m | a2:m b,:m | g,2~8
        }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    Here I return to remind my brothers and sisters of Jesus Christ and of my Lord Saint John
    Baptizing there in the River Jordan, illuminating with the healing of forgiveness
    \nextverse
    Here in the forest we celebrate Saint John, all the Saints and the Virgin of the Conception
    The Centenary of Our Lady Mother, eternal strength of this great integration
    \nextverse
    All the brotherhood of this our expansion prays to God with love in the heart
    To have our Mother, faith and consideration; the eternal Father is King of integration
    \nextverse
    Wisdom belongs to the Lord King Solomon; strength and Power he carries in the palm of his hand
    Our Master teaching his brothers and sisters, singing the hymnal, affirming the union
  \end{translation}
\endsong
