% Santo Daime: Hinos Diversos da Concentração
% ===========================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Firmado em Concentração}[by={Padr. Alfredo},tags={valsa},key={Am},sks={Am}]
  \audio{https://www.nossairmandade.com/hymn/538/FirmadoEmConcentra\%C3\%A7\%C3\%A3o}
  \meter{3}{4}
  \mnbeginchorus\memorize
    |\[\mncii{C}{A}Am]Firmad\[^\mn{E}]{o em} |\[^\mn{C}]con\[^\mn{A}]cen\[^\mn{C}]tra|\[^\mn{E}]ção | \e
    |\[^\mn{C}]Na \[^\mn{A}]Vir\[^\mn{E}]gem |\[\mnc{C#}A7]Mãe ver\[^\mn{E}]da|\[\mnc{D}Dm]dei|ra
    \lrep \[^\mn{A}]Eu |\[\mnc{D}Dm]vou ol|\[^\mn{F}]hand\[^\mn{E}]{o e} dou |\[\mnc{C}Am]chan\[^\mn{A}]ce
    A |\[^\mn{E}]quem ol|\[\mnc{B}E7]har pa\[^\mn{D}]ra |\[^\mn{G#}]esta \[^\mn{B}]ban|\[\mnc{A}Am]dei|\[\up{1}A7]ra \rrep
  \mnendchorus
  \notesoff
  \beginchorus\replay
    |^Vou publi|car umas pa|lav|ras \altchords{\id[2]{MK (Am)} |Am | | |E}
    |Que nos traz |^pura lem|^bran|ça \altchords{|Am |A7 |Dm |-}
    \lrep Das |^cores |desta ban|^deira \altchords{|Dm | |Am}
    Do |Pai verda|^deiro, ver|de azul e |^bran|^ca \rrep \altchords{|Am |Bm7b5 |E7 |Am |\up{1}(A)}
  \endchorus
  \beginchorus\replay
    |^Firmado |no verde |lin|do
    |Sou eu, re|^presento a |^Ter|ra
    \lrep Por |^isto a|qui eu es|^tou
    Com a |paz do Se|^nhor, acal|mando a |^guer|^ra \rrep
  \endchorus
  \beginchorus\replay
    |^Firmado |neste a|zul | \e
    Es|ta imen|^sidão ce|^les|te
    \lrep Faz |^calmar o |meu cora|^ção
    E |dos meus ir|^mãos, os |que não es|^que|^cem \rrep
  \endchorus
  \beginchorus\replay
    |^Lembranças |vivas de |De|us
    |Nos traz o |^branco do Ast|^ral | \e
    \lrep Com |^todos os |seres do |^alto
    Que |nos ilu|^mina jun|tamente ao |^Sol |^ \e \rrep
  \endchorus
  \beginchorus\replay
    |^Completei |esta li|ção | \e
    |Com justi|^ça e leal|^da|de
    \lrep Para |^todos |se reu|^nir
    Pro|vando a|^qui sua |capaci|^da|^de \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c''' {
      \key a \minor \time 3/4
        | c4 a e | c a c | e2.~ | e2.
        | c'4 a e | cis cis e | d2. | d2
      \break
      \repeat volta 2 {
        a4 | d2 d4 | f e e | c a a | e'2 e4
        | b b d | gis, gis b | a2. | a2
      }
    }
    theLyricsOne = \lyricmode {
      Fir -- ma -- do_em con -- cen -- tra -- ção; __
      Na Vir -- gem Mãe ver -- da -- dei -- ra.
      Eu vou o -- lhan -- do_e dou chan -- ce;
      A quem o -- lhar pa -- ra es -- ta ban -- dei -- ra.
    }
    theChords = \chordmode {
      | a2.:m | a:m | a:m | a:m
      | a:m | a:7 | d:m | d:m
      \set chordChanges = ##f
      | d:m
      \set chordChanges = ##t
      | d:m | a:m | a:m
      | e:7 | e:7 | a:m | \mark \markup{\hspace #.5 \super{"1"}} \parenthesize a2:7
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Firmed in concentration, in the true Virgin Mother
    I keep looking and I give opportunity to those who look for this banner
    \nextverse
    I will announce some words that bring us pure remembrance
    Of the colors of this banner of the true Father, green, blue and white
    \nextverse
    Firmed in the beautiful green, I represent the Earth
    For this I am here, with the peace of the Lord calming the war
    \nextverse
    Firmed in this blue, this celestial immensity
    Calms my heart and of my brothers, those who don‘t forget
    \nextverse
    Living memories of God bring us the white of the Astral
    With all Beings of the heights who illuminate us together with the Sun
    \nextverse
    I completed this lesson with justice and loyalty
    For everyone to be reunited, proving thus their capacity
  \end{translation}
\endsong


\beginsong{Firmeza}[by={Padr. Valdete},key={F},sks={F, E, G}]
  \audio{https://www.nossairmandade.com/hymn/148/Firmeza}
  \mnbeginchorus\memorize
    \[^\mn{C}]Fir|\[\mnc{F}F]meza, bem fir\[\mnc{C}C]meza peço |\[\mnc{F}F]em concentra\[\mnc{C}C]ção
    \[^\mn{F}]Fir|\[F]me\[^\mn{C}]za, \[C]bem \[^\mn{F}]fir\[F]me\[^\mn{C}]za \[C]na cor|\[\mnc{F}F]rente da sessão
  \mnendchorus
  \notesoff
  \beginchorus
    Fir|^meza, bem fir^meza, peço ao |^Rei Jurami^dam
    Fir|^meza, ^bem fir^meza, ^para eu |^sempre ser seu fã
  \endchorus
  \beginchorus
    Fir|^meza, bem fir^meza, peço |^a Virgem Ma^ria
    Fir|^meza, ^bem fir^meza, ^que Vós |^seja minha Guia
  \endchorus
  \beginchorus
    Fir|^meza, bem fir^meza, peço ao |^Senhor São Jo^ão
    Fir|^meza, ^bem fir^meza, ^para eu |^seguir na missão
  \endchorus
  \beginchorus
    Fir|^meza, bem fir^meza, peço ao |^Pai da Cria^ção
    Vós me |^dê Paz ^e A^mor, ^e apla|^nai meu coração
  \endchorus
  \beginchorus
    Apla|^nai meu cora^ção, para |^eu poder a^mar
    E as o|^fenças ^dos ir^mãos, ^eu |^saber perdoar
  \endchorus
  \beginchorus
    Sa|^bendo perdo^ar, se|^guindo nesta ^Luz
    Pa|^ra po^der di^zer, ^que es|^tou com meu Jesus
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
      theMelody = \relative c'' {
      \key f \major \time 4/4 \partial 8
      \repeat volta 2 {
        c8 | f8. f16 f8. f16 c8. c16 c8. c16 | f8. f16 f8. f16 c4. f8
        | f8. c16 c8. f16 f8. c16 c8. c16 | f8. f16 f8. f16 f4.
      }

    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Fir -- me -- za bem fir -- me -- za pe -- ço em con -- cen -- tra -- ção;
        Fir -- me -- za bem fir -- me -- za na cor -- ren -- te da ses -- são.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | f2 c | f c
        | f4 c f c | f2.~ f8
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Firmness, great firmness, I ask in concentration
    Firmness, great firmness, in the current of the session
    \nextverse
    Firmness, great firmness, I ask of King Juramidam
    Firmenss, great firmness, always to be your devotee
    \nextverse
    Firmness, great firmness, I ask the Virgin Mary
    Firmness, great firmness, that you may be my guide
    \nextverse
    Firmness, great firmness, I ask Lord Saint John
    Firmness, great firmness, to follow in the mission
    \nextverse
    Firmness, great firmness, I ask the Father of Creation
    That You give me peace and love, and smooth my heart
    \nextverse
    Smooth my heart, so I am able to love
    And the offenses of the brothers and sisters, I know how to forgive
    \nextverse
    Knowing to forgive, following in this light
    So I can say, that I am with my Jesus
  \end{translation}
\endsong


\beginsong{Eu te Dei uma Casa}[by={Padr. Sebastião},key={C},sks={C}]
  \audio{https://www.nossairmandade.com/hymn/63/EuTeDeiUmaCasa}
  \mnbeginchorus\memorize
    \[^\mn{C}]Eu |\[\mnc{F}F]peço \[^\mn{A}]a \[^\mn{C}]meu |\[^\mn{A}]Pai, \[^\mn{C}]sei que |\[\mnc{E}C]ós \[^\mn{C}]tem \[^\mn{E}]o \[^\mn{G}]po|\[\mnc{E}(Em)]der
    \[^\mn{C}]Per\[^\mn{B}]do|\[\mnc{A}Am]ai \[^\mn{C}]as \[\mnc{E}(A7)]min\[^\mn{G}]has |\[\mnc{D}Dm]culpas, \[^\mn{C}]se \[^\mn{B}]de |\[\mnc{A}Am]Vós \[^\mn{C}]eu me\[^\mn{E}]re|\[\mnc{C}C]cer
  \mnendchorus
  \notesoff
  \beginchorus
    Eu |^te dei uma |casa que |^não falta nin|^guém
    Pa|^{ra tu} ^escol|^her aque|^les que te con|^vém
  \endchorus
  \beginchorus
    A es|^trada eu dou a |todos, para |^todos via|^jar
    |^Ver e ^compreen|^der, e fi|^car em seu lu|^gar
  \endchorus
  \beginchorus
    |^Eu estou com |Deus, |^Deus está em |^mim
    Eu |^estan^{do com} |^Deus, |^Deus é o meu ca|^minho
  \endchorus
  \beginchorus
    |^Deus é a |glória, |^Deus a glória |^é
    Quem |^{é meu} ^Salva|^dor é Je|^sus de Naza|^ré
  \endchorus
  \beginchorus\large
    Eu |^vivo neste |mundo na |^minha dire|^ção
    \noteson\[\mnlow{E}]Ol\[\mnlow{C}]han\notesoff|^do as coi^sas de |^Deus e prestan|^do bem aten|^ção
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
         c4 |f f a c |a2( a4) c,8( c8) |e4 c e g |e2( e4) c8( b8)
         |a4 c e g |d2 d4 c8( b8) |a4 c c e |c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Eu |pe -- ço a meu |Pai; __ _
      Sei que |Vós tem o po -- |der; __ _
      Per -- do -- |ai as mi -- nhas |cul -- pas;
      Se de |Vós eu me -- re -- |cer. __ _
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Eu |te dei u -- ma |ca -- sa;
      Que __ _ |não fal -- ta nin -- |guém; __ _
      Pa -- _ |ra tu es -- co -- |lher;
      A -- que -- _ |les que te con -- |vém. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      A_es -- |tra -- da_eu dou a |to -- dos;
      Pa -- ra |to -- dos vi -- a -- jar; _ \skip 1 \skip 1
      Ver e com -- preen -- der;
      E fi -- _ car em seu lu -- gar. __ _
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \skip 1 Eu es -- tou com Deus; _
      \skip 1 \skip 1 Deus es -- tá em mim; __ _
      Eu __ _ es -- tan -- do com Deus;
      \skip 1 \skip 1 \skip 1 Deus é~o meu ca -- mi -- nho.
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \skip 1 |Deus __ _ é a |gló -- ria;
      \skip 1 \skip 1 |Deus a gló -- ria |é __ _
      Quem __ _ |é meu Sal -- va -- |dor
      É Je -- _ |sus de Na -- za -- |ré. __ _
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      Eu |vi -- vo nes -- te |mun -- do;
      Na __ _ |mi -- nha di -- re -- |ção;
      O -- lhan -- _ |do~as coi -- sas de |Deus;_E
      pres -- tan -- _ |do bem a -- ten -- |ção. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 |f1 |f1 |c1 |\parenthesize e:m
        |a2:m \parenthesize a:7 |d1:m |a:m |c2.
      }
    }
    %\layout { #(layout-set-staff-size 15) }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  %\translationoff
  \begin{translation}\footnotesize
    I ask my Father, I know that You have the power
    Forgive my guilt, if I am deserving
    \nextverse
    I gave you a house in which no one is missing
    For you to choose those whom you find worthy
    \nextverse
    I give the path to all, for everyone to travel
    To see and understand, and to stay in your place
    \nextverse
    I am with God, God is within me
    Being with God, God is my path
    \nextverse
    God is the glory, God the glory is
    He who is my Savior is Jesus of Nazareth
    \nextverse
    I live in this world following my direction
    Looking at the things of God and paying close attention
  \end{translation}
\endsong


\beginsong{São João na Terra}[by={Padr. Sebastião},tags={2x},key={C},sks={C, D}]
  \audio[key=D]{https://www.nossairmandade.com/hymn/64/S\%C3\%A3oJo\%C3\%A3oNaTerra}
  \newchords{chords_saojoaonaterra_a}\newchords{chords_saojoaonaterra_b}
  \musicnote{Tocar 2 vezes}
  \mnbeginchorus\memorize[chords_saojoaonaterra_a]
    \[^\mn{G}]Quando ou\[^\bm\mn{C}]vir \[^\mn{E}]fa|\[\mnc{G}C]lar de São \[^\mn{E}]Jo\[^\bm\mn{A}]ão \[^\mn{G}]na |\[\mncii{E}{C}Am]terra \altchords{\id[1]{(D)}|D |Bm}
    É \[^\mn{A}]si\[\mnc{C}C]nal \[^\mn{E}]de |\[\mnc{D}Dm]guerra em \[^\mn{C}]to\[\mnc{A}F]do \[^\mn{C}]lu|\[C]gar \altchords{D |Em G |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_saojoaonaterra_b]
    \ind \[^\mn{C}]É |\[\mnc{D}Dm]fora \[^\mn{C}]de \[^\bm\mn{A}]con\[^\mn{C}]fu|\[\mnc{E}C]são \altchords{|Em |D}
    \ind \[^\mn{A}]Che\[^\bm\mn{C}]gou \[^\mn{E}]São |\[\mnc{D}Dm]Pedro com \[^\mn{C}]seus \[\mnc{A}F]dois \[^\mn{C}]ir|\[C]mãos \altchords{|Em G |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_saojoaonaterra_a]
    Os an\[\bm]jinhos do |^céu é quem \[\bm]vem col|^her \altchords{\id[2]{MK (C)}|C |Am}
    Para ^ajun|^tar em um ^{só lu}|^gar \altchords{|G F |C}
  \endchorus\glueverses\beginchorus\replay[chords_saojoaonaterra_b]
    \ind Lou|^var a meu \[\bm]Pai E|^terno \altchords{|G F |Am}
    \ind Fel\[\bm]iz da|^quele que bem ^traba|^lhar \altchords{|G F |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 2.
      \repeat volta 2 {
         g8 g c4 e |g8( g) g e a4 g
         |e8( c) c a c4 e |d8( d) d c a4 c
      } \alternative {
        { | c4 }
        { | c2. }
      }
      \repeat volta 2 {
         c4 |d d8 c a4 c |e4( e8) a,8 c4 e4
         |d8 d d c a4 c4
      } \alternative {
        { | c2. }
        { | c4 }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Quan -- do~ou -- vir fa -- lar de São Jo -- ão na ter -- ra;
        É si -- nal de guer -- ra em to -- do lu --
      } \alternative {
        { gar. }
        { gar. }
      }
      \repeat volta 2 {
        É fo -- ra de con -- fu -- são; _
        Che -- gou São Pe -- dro com seus dois ir --
      } \alternative {
        { mãos. }
        { mãos. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Os an -- jinhos do céu _ é quem vem co -- lher; _
        Pa -- ra a -- jun -- tar _ em um só lu --
      } \alternative {
        { gar. }
        { gar. }
      }
      \repeat volta 2 {
        Lou -- var a meu Pai E -- ter -- no;
        Fe -- liz da -- que -- le que bem tra -- ba --
      } \alternative {
        { lhar. }
        { lhar. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2. |c1 |a2:m c |d:m f
      } \alternative {
        { c4 }
        { c2. }
      }
      \repeat volta 2 {
        s4 | d1:m | c | d2:m f
      } \alternative {
        { c2. }
        { c4 }
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    When you hear it said that St. John is on the earth
    It‘s a sign of war everywhere
    \nextverse
    Apart from the confusion
    St. Peter arrived with his two brothers
    \nextverse
    The little angels of heaven are the ones who come to gather
    To bring together in one single place
    \nextverse
    Praise to my Eternal Father
    Happy is he who works well
  \end{translation}
\endsong


\beginsong{Conforto}[by={Padr. Alfredo},key={Dm},sks={Dm, Cm}]
  \audio[key=Dm]{https://www.nossairmandade.com/hymn/478/Conforto}
  \beginchorus\memorize
    \[^\mn{A}]Eu |\[\mnc{F}Dm]pe\[^\mn{D}]ço \[^\mn{F}]con\[\mnc{E}A7]for\[^\mn{C#}]to \[^\mn{E}]aos |\[\mnc{D}Dm]Reis
    \[^\mn{D}]Do |\[^\mn{A}]Céu, \[^\mn{F}]da \[^\mn{D}]Flo\[\mnc{A}D7]rest\[^\mn{F}]{a e} \[^\mn{D}]do |\[\mnc{G}Gm]Mar
    |\[^\mn{B&}]Pe\[^\mn{G}]ço \[^\mn{E}]con\[\mnc{C#}A7]fort\[^\mn{A}]{o as} \[^\mn{E}]Ra|\[\mnc{D}Dm]inhas
    Para |\[\mnc{A}A]nos \[\mnciii{E}{F}{E}A7]ilumi|\[\mnc{D}Dm]nar
  \endchorus
  \notesoff
  \beginchorus
    Eu |^peço con^forto aos |^Príncipes
    Do |Céu, da Flo^resta e do |^Mar
    |Peço con^forto as Prin|^cesas
    Para |^nos ^ilumi|^nar
  \endchorus
  \beginchorus
    Eu |^peço con^forto aos |^Anjos
    Do |Céu, da Flo^resta e do |^Mar
    |Peço con^forto aos |^Santos
    Para |^nos ^ilumi|^nar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-08
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4
      \repeat volta 2 {
        a4 | f'4 d8 f8 e4 cis8 e8 | d4.( d8 d4)
        d'4 | a4 f8 d' a4 f8 d |g1 \break
        |bes4 g8 e cis8. cis16 a8 e' | d2 d4
        d8 d8 | a'2 e4 f8 e | d2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu pe -- ço con -- for -- to aos Reis; __ _ _
        Do Céu, da Flo -- res -- ta~e do Mar;
        Pe -- ço con -- for -- to as Ra -- i -- nhas;
        Pa -- ra nos i -- lu -- mi -- nar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Eu pe -- ço con -- for -- to aos Prín -- ci -- pes;
        Do Céu, da Flo -- res -- ta~e do Mar;
        Pe -- ço con -- for -- to as Prin -- ce -- sas;
        Pa -- ra nos i -- lu -- mi -- nar.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Eu pe -- ço con -- for -- to aos An -- _ jos;
        Do Céu, da Flo -- res -- ta~e do Mar;
        Pe -- ço con -- for -- to a -- os San -- tos;
        Pa -- ra nos i -- lu -- mi -- nar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 |d2:m a:7 |d1:m
        |d2:m d:7 |g1:m
        |g2:m a:7 |d1:m
        |a2 a:7 |d2.:m
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I ask comfort from the Kings
    Of Heaven, of the Forest and of the Sea
    I ask comfort from the Queens
    To illuminate us
    \nextverse
    I ask comfort from the Princes
    Of Heaven, the Forest and the Sea
    I ask comfort from the Princesses
    To illuminate us
    \nextverse
    I ask comfort from the Angels
    Of Heaven, the Forest and the Sea
    I ask comfort from the Saints
    To illuminate us
  \end{translation}
\endsong


\beginsong{Chamo o Tempo}[by={Mestre Irineu Serra}]
  \audio[key=A]{https://www.nossairmandade.com/hymn/23/ChamoOTempo}
  \transpose{2}
  \mnbeginchorus\memorize
    \[^\mn{B}]Cha\[^\mn{A}]mo o |\[\mnc{G}G]Tempo, eu \[\mnc{A}D]cha\[^\mn{G}]{mo o} |\[\mnc{D}G]Temp\[(D)]o
    \[^\mn{B}]Para e\[^\mn{A}]le |\[\mnc{G}G]vir me \[\mncii{A}{G}D]ensi|\[\mnc{D}G]na\[G7]r
    \lrep Apren|\[\mnc{E}C]der com \[\mnc{F#}D]per\[^\mn{A}]fei|\[\mnc{G}G]çã\[Em]o
    \[^\mn{G}]Pa\[^\mn{A}]ra |\[\mnc{B}Am]po\[^\mn{A}]der \[\mncii{D}{B}D7]ensi|\[\mnc{G}G]na\[\up{1}G7]r \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    Os que |^forem o^bedi|^ente^s
    Tra|^tar de ^apren|^de^r
    \lrep Para |^ser e^terna|^ment^e
    Para |^Deus lhe ^aten|^de^r \rrep
  \endchorus
  \beginchorus
    De|^pois que o ^Tempo |^cheg^a
    Nin|^guém quis ^apren|^de^r
    \lrep De|^pois que ^refle|^ti^r
    É que |^vai se a^rrepen|^de^r \rrep
  \endchorus
  \beginchorus
    Fir|^meza no ^pensa|^ment^o
    Para |^seguir ^no ca|^minh^o
    \lrep Embora |^que não a^prenda |^muit^o
    Aprenda |^sempre um ^boca|^dinh^o \rrep
  \endchorus
  \begin{translation}
    I call the time, I call the time
    For it to come to teach me
    To learn with perfection
    So that I can teach
    \nextverse
    Those who are obedient
    Try to learn
    To be eternally
    For God to help you
    \nextverse
    After the time arrives
    Nobody wanted to learn
    After reflecting
    Is when one will repent
    \nextverse
    Firmness in the mind
    To continue on the path
    Even if you don‘t learn much
    Always learn a little bit
  \end{translation}
\endsong


\beginsong{Chamo a Força}[by={Mestre Irineu Serra}]
  \audio{https://www.nossairmandade.com/hymn/270/ChamoAFor\%C3\%A7a}
  \mnbeginchorus\memorize
    \[^\mn{C}]Cha\[^\mn{B}]{mo a} |\[\mnc{A}Am]força, eu \[\mnc{C}C]cha\[^\mn{E}]{mo a} |\[\mnc{A}Am]força\[G]
    \[^\mn{G}]A força |\[Am]vem \[^\mn{E}]nos \[\mncii{C}{A}C]amos|\[\mnciii{C}{B}{A}Am]trar
  \mnendchorus\glueverses\notesoff\mnbeginchorus
    Treme a |^terra e ^balan|^ceia^
    E vós não |^sai do ^seu lu|^gar
  \mnendchorus
  \beginchorus
    Treme a |^terra, ^treme a |^terra^
    Treme a |^terra e ^geme o |^mar
  \endchorus\glueverses\beginchorus
    Ainda tem |^gente ^que du|^vida^
    Do po|^der que ^vós me |^dá
  \endchorus
  \beginchorus
    Aqui |^dentro ^da ver|^dade^
    Tem uns |^certos ^menti|^rosos
  \endchorus\glueverses\beginchorus
    Que calu|^niam os ^seus ir|^mãos^
    Para se tor|^nar mui^to vi|^çosos
  \endchorus
  \beginchorus
    Mas |^ninguém ^não se |^lembra^
    Chamou o |^Mestre ^menti|^roso
  \endchorus\glueverses\beginchorus
    Devaga|^rinho ^vai che|^gando^
    E quem cha|^mou é que ^vai fi|^cando
  \endchorus
  \begin{translation}
    I call the Force, I call the Force
    The Force comes to show us
    The earth shakes and quakes
    But Thou don‘t move
    \nextverse
    The earth shakes, the earth shakes
    The earth shakes and the sea moans
    Yet, there are people who still doubt
    The power that Thou give me
    \nextverse
    Here in the Truth
    There are some liars
    Who slander their brothers and sisters
    So that they can look good
    \nextverse
    But no one remembers
    That he called the Master a liar
    Slowly he‘s going to arrive
    And who called is who stays behind
  \end{translation}
\endsong


\beginsong{Eu Peco a Deus\\Vi Deus no Sol, na Lua e nas Estrelas}[by={Francisco Corrente},tags={2x}]
  \audio[key=C]{https://www.nossairmandade.com/hymn/26/EuPe\%C3\%A7oADeus}
  \newchords{chords_eupecoadeus_a}\newchords{chords_eupecoadeus_b}
  \musicnote{Tocar 2 vezes}
  \mnbeginchorus\memorize[chords_eupecoadeus_a]
    \[^\mn{C}]Eu pe\[^\mn{E}]{co a} |\[\mnc{G}C]Deus que per\[\mnc{A}Am]doe os meus \[^\mn{E}]pe|\[\mncii{G}{F}F]cados
    Perdoe \[^\mn{G}]a |\[\mnc{A}Dm]mim e perdoe \[^\mn{F}]{a meus} \[^\mn{A}]ir|\[\mnc{G}G]maos\[C]
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eupecoadeus_b]
    \[^\mn{/}]Eu peco a |Deus que me \[\up{1}Am\up{2}(F)]{dê a Santa} |\[G]Luz
    \[^\mn{D}]Para eu a|mar Vós no \[\mnc{E}G7]meu co\[^\mn{C}]ra|\[C]ção\[\up{1}Am]
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eupecoadeus_a]
    Vi Deus no |^sol Deus na ^lua e nas es|^trelas
    Vi Deus no |^vento Deus na terra Deus no |^mar^
  \endchorus\glueverses\beginchorus\replay[chords_eupecoadeus_b]
    Todos |sabem que ^Deus esta em |^todo
    Todos se |firmam, se com^ponham em seu lu|^gar^
  \endchorus
  \beginchorus\replay[chords_eupecoadeus_a]
    Eu digo a |^todos com a^mor no cora|^ção
    |^Deus é quem nos da a Santa |^Luz^
  \endchorus\glueverses\beginchorus\replay[chords_eupecoadeus_b]
    |Deus é quem da ^{o nosso} des|^tino
    Pra nos sa|ir deste ^mundo de ilu|^são^
  \endchorus
  \vfill
  \textnote{This hino can be sung when someone is going through a passage
            in a concentration work.}
  \begin{translation}
    I ask God to forgive my sins
    Forgive me and forgive my brothers and sisters
    I ask God to give me the Holy Light
    So that I can love You in my heart
    \nextverse
    I saw God in the Sun, I saw God in the Moon and in the Stars
    I saw God in the Wind, God in the Earth, God in the Sea
    Everyone knows that God is in everything
    Everyone is firming themselves and cmoposing themselves in their place
    \nextverse
    I say to everyone with love in my heart
    It is God who gives us the Holy Light
    It is God who gives us our destiny
    So we can leave this world of illusion
  \end{translation}
\endsong
