% Santo Daime: Hinos Diversos
% ===========================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Graduação}[by={Alfredo}, off={Pedro Mota}, key={C}, gk={C, B\flt{}--D}]
  \mnbeginverse
    \beginrep\memorize
    \[^\mn{E}]No |\[\mnc{G}C]ponto em que \[^\mn{E}]es\[\bmc\mn{G}]tou com \[^\mn{E}]meu |\[^\mn{A}]Pai \[^\mn{G}]e mi\[^\mn{E}]nha \[\bmc\mn{C}]Mãe
    To\[^\mn{A}]da |\[\mnc{C}Am]es\[^\mn{A}]trela que \[\mnc{D}G]dou \[^\mn{E}]é \[^\mn{C}]u|\[\mnc{B}G7]ma \[^\mn{A}]gra\[^\mn{C}]dua\[C]ção
    Nes\[^\mn{A}]te |\[\mnc{C}Am]ca\[^\mn{A}]minho que \[\mnc{D}G]vou, \[^\mn{E}]u\[^\mn{C}]ma |\[\mnc{B}G7]gran\[^\mn{A}]de \[^\mn{C}]devo\[C]ção
    \endrep
  \mnendverse
  \notesoff
  \beginverse
    \beginrep
    Escu|^tai que eu ^vou destrin|chando este ca^minho
    Todo |^ser que agra^do lhe a|^proximo de ^mim
    Todos |^têm que obede^cer e se com|^por neste jar^dim
    \endrep
  \endverse
  \beginverse
    \beginrep
    So|^bre todas as ^coisas deve|mos amar a ^Deus \altchords{\id[1]{(D)}|D | \e}
    E a |^todos seus ir^mãos como |^{se ama} a si ^mesmo \altchords{|Bm A |A7 D}
    Se|^guir sua mis^são e entrar |^na guerra sem ^medo \altchords{|Bm A |A7 D}
    \endrep
  \endverse
  \beginverse
    \beginrep
    Toda |^calma e muito a^mor e sa|tisfação na ^fé
    Ben|^dito é nosso ^Mestre que en|^sina como ^é
    Vamos |^seguir meus ir^mãos seja |^{o que} Deus qui^ser
    \endrep
  \endverse
  \begin{lilywrap}\begin{lilypond}[] \include "ulsbs-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        e8( \pomark e8) | g8 g8 g8 e8 g8( g8) g8 e8 | a8 g8 g8 e8 c8( c8)( c8) a8 | c8 a8 a8 a8 d8( d8) e8 c8
        | b8 a8 c8 c8 c4 c8 a8 | c8 a8 a8 a8 d8( d8) e8 c8 | b8 a8 c8 c8 c8( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        No __ _ | pon -- to~em que es -- tou __ _
        com meu | Pai e mi -- nha Mãe; __ _
        To -- da | es -- tre -- la que dou __ _
        é u -- | ma gra -- du -- a -- ção;
        Nes -- te | ca -- mi -- nho que vou __ _
        u -- ma | gran -- de de -- vo -- ção. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Es -- cu -- | ta -- i que eu vou __ _
        des -- trin -- | chan -- do~es -- te ca -- mi -- nho;
        To -- do | ser que a -- gra -- do __ _
        lhe a -- | pro -- xi -- mo de mim;
        To -- dos | têm que~o -- be -- de -- cer
        e se com -- | por nes -- te jar -- dim. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        So -- _ | bre to -- das as coi -- sas
        de -- ve -- | mos a -- mar a Deus; __ _
        E a | to -- dos seus ir -- mãos __ _
        co -- mo | se a -- ma~a si mes -- mo;
        Se -- | guir su -- a mis -- são;
        e en -- trar | na guer -- ra sem me -- do.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        To -- da | cal -- ma~e mui -- to~a -- mor __ _
        e sa -- | tis -- fa -- ção na fé; __ _ _
        Ben -- | di -- to~é nos -- so Mes -- tre
        que en -- | si -- na co -- mo é;
        Va -- mos | se -- guir meus ir -- mãos __ _
        se -- ja | o que Deus qui -- ser. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | c1 | a2:m g2 | g2:7 c2 | a2:m g2 | g2:7 c4
      }
    }
    \setStaffSize #15 % for better fit
    \include "ulsbs-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    At the point where I am with my Father and my Mother
    Each and every star that I give is a graduation
    On this path that I go on, a great devotion
    \nextverse
    Listen then how I keep unraveling this path
    Every being that I'm pleased with I bring close to me
    Everyone has to obey and compose oneself in this garden
    \nextverse
    Above all things, we must love God
    And all your brothers and sisters, as you love yourself
    To follow your mission and to enter the war without fear
    \nextverse
    All calmness and much love and satisfaction in faith
    Blessed is our Master who teaches how it is
    Let's follow my brothers however God wills
  \end{translation}
\endsong


\beginsong{Bendito da Sexta-Feira Santa}[by={trazida tão Santo Daime por Dona Francisca Nascimento}, ex={canção folclórica}, key={C}, gk={D, B\flt{}--G}]
  \meter{2}{4}
  % verse 1:
  \mnbeginverse
    \[^\mn{A}]Na quar\[^\mn{B}]ta-|\[\mnc{C}Am]fei\[^\mn{B}]ra, \[^\mn{A}]Je|\[\mnc{B}Em]sus com \[^\mn{A}]seus \[^\mn{B}]dis|\[\mnc{C}Am]cí|pulos
    \[^\mn{A}]Foi à\jw O\[^\mn{C}]li|\[^\mn{E}]vei\[^\mn{C}]ra, \[^\mn{D}]foi |\[Dm]à \[^\mn{A}]Jeru\[^\mn{C}]sa|\[\mnc{E}C]lém | \e
    \[^\mn{A}]Foi \[^\mn{C}]à |\[^\mn{E}]Pás\[^\mn{C}]coa, meu \[^\mn{E}]Je|sus com \[^\mn{D}]seus \[^\mn{C}]dis|\[\mncii{D}{C}G]cí|\[\mnc{A}Am]pulos
    |\[\mnc{C}F]Que \[^\mn{E}]pade|\[^\mn{C}]ceu \[^\mn{B}]a \[^\mn{A}]fa|\[\mnc{B}G]vor do \[^\mn{A}]nos\[^\mn{B}]so |\[\mnc{C}C]bem | \e
  \mnendverse
  \notesoff
  % verse 2:
  \beginverse
    Na quinta-|^feira, Je|^sus banhou os |^pés | \e
    Com grande |gosto, prazer |^{e con}tenta|^men|to
    Depois da |ceia, meu Je|sus restitu|^iu-|^se
    |^Com grande |gosto, meu San|^tíssimo Sacra|^men|to
  \endverse
  % verse 3:
  \beginverse
    Na sexta-|^feira, Je|^sus subiu ao |^hor|to \altchords{\id[1]{(D)}|Bm |F\shrp{}m |Bm | \e}
    Foi re|zar três ho|^ras de ora|^ção | \e \altchords{| - |Em |D | \e}
    Encontrou |Judas na |frente de\jw uma |^tro|^pa \altchords{| - | - |A |Bm}
    |^Já vinha |ele, de al|^feres, capi|^tão | \e \altchords{|G | - |A |D | \e}
  \endverse
  % verse 4:
  \beginverse
    |^Judas, pe|^{lo lado} di|^rei|to
    Com falsi|dade lhe bei|^jou devida|^men|te
    Jesus |disse: eu co|nheço\jw a falsi|^da|^de
    |^Com esse |beijo que tu |^agora me |^des|tes
  \endverse
  % verse 5:
  \beginverse
    De|^pois de Je|^sus Cristo\jw arras|^ta|do
    Cobriram |Ele em |^trono peque|^ni|no
    Lhe bo|taram\jw uma co|roa na ca|^be|^ça
    |^Era te|cida com se|^tenta\jw e dois es|^pi|nhos
  \endverse
  % verse 6:
  \beginverse
    Daí sa|^íram com Je|^sus na rua\jw es|^trei|ta
    Certa|mente\jw a ru|^{a de} amar|^gu|ra
    Encon|trou-se com\jw a Sem|pre Virgem Ma|^ri|^a
    |^Era\jw a sua |mãe que cho|^rava com ter|^nu|ra
  \endverse
  % verse 7:
  \beginverse
    Neste |^dia, Nossa |^Senhora che|^gou | \e \altchords{|Bm |F\shrp{}m |Bm | \e}
    Às oito |horas, Sexta-|^feira da Pai|^xão | \e \altchords{| - |Em |D | \e}
    Encon|trou-se com\jw o |seu filhinho |^pre|^so \altchords{| - | - |A |Bm}
    \noteson \[\mn{E}]Mada|\[\mnc{C}F]lena, \[\mn{B}]Oh! \[\mn{A}]Que |\[\mnc{B}G]dor no \[\mn{A}]co\[\mn{B}]ra|\[\mnc{C}C]ção | \e \altchords{|G |A |D | \e}
  \endverse
  % verse 8:
  \beginverse\iflyriconly\else\normalsize\renewcommand{\ulChordFont}{\sffamily\bfseries\small\color{chordcolor}}\fi
    Oh! Minha |^Mãe que por |^mim tanto cho|^ra|va
    Sendo |Ela, Ma|ria\jw e Mada|^le|^na
    Quando\jw eu |cuido que |vinha\jw a meu so|^cor|^ro
    |^Cada vez |mais redo|^brava\jw a minha |^pe|na
  \endverse
  % verse 9:
  \beginverse\iflyriconly\else\normalsize\renewcommand{\ulChordFont}{\sffamily\bfseries\small\color{chordcolor}}\fi
    Chegou Lon|^guinho com a |^lança e cra|^vou | \e
    No peito\jw es|querdo, em ci|^{ma do} cora|^ção | \e
    Quando\jw o |sangue lhe ba|tia pelo |^ros|^to
    |^Se ajoe|lhou, a meu |^Deus pediu per|^dão | \e
  \endverse
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2026-03
    % \header {
    %   title = "Bendito da Sexta-Feira Santa"
    %   composer = "canção folclórica"
    % }
    \include "ulsbs-include-head.ly"
    theMelody =  \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major
      \time 2/4 \partial 4.
      \sectionLabel "1.-6."
      \repeat volta 6 {
        \mark \markup {"6x"}
        \parenthesize a8 \parenthesize a8 \parenthesize b8 | c8( c8) b8 a | b b a b | c2 | \parenthesize c8
        \parenthesize a8 a8 c | e8.( e16) c8 d | d a a c | e2 | \parenthesize e8
        \parenthesize a,8 a8 c8 | e8.( c16) c8 e8 | e8 e8 d8 c8 | \once\slurSolid d4.( c8) | a2
        | c8( c8) e8 e8 | c8( c8) b8 a | b b a b | c2 | \parenthesize c8
      }
      \break
      \slurSolid
      \sectionLabel "7." % Verse 7 is one measure shorter
      r8 a8 b8 | c8 c8 b8 a | b b a b | c2 | r8
      a8 a8 c | e8. e16 c8 d | d a a c | e2 | r4
      a,8 c8 | e8.( c16) c8 e8 | e8 e8 d8 c8 | d4.( c8) | a4 \altcol e'8 \altcol e8
      | c8 c8 b8 a | b b a b | c2 | r8
      \break
      \slurDashed
      \sectionLabel "8.-9."
      \repeat volta 2 {
        \mark \markup {"2x"}
        a8 \pomark a8 b8 | c8( c8) b8 a | b b a b | c2 | \parenthesize c8
        \parenthesize a8 a8 c | e8.( e16) c8 d | d a a c | e2 | \parenthesize e8
        r8 a,8 c8 | e8.( c16) c8 e8 | e8 e8 d8 c8 | \once\slurSolid d4.( c8) | a2
        | c8( c8) e8 e8 | c4 b8 a | b b a b | c2 | \parenthesize c8
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \repeat volta 6 {
        <<
          {
            \set stanza = "1."
            Na quar -- ta -- | fei _ -- ra, Je -- | sus com seus dis -- | cí -- | pulos;
            Foi à~O -- li -- | vei _ -- ra, foi | à Je -- ru -- sa -- | lém; | ""
            "" Foi à | Pás -- coa, meu Je -- | sus com seus dis -- | cí _ -- | pulos;
            | Que __ _ pa -- de -- | ceu __ _ a fa -- | vor do nos -- so | bem. | ""
          }
          \new Lyrics { \set associatedVoice = "theMelody"
            \set stanza = "2."
            Na quin -- ta -- | fei _ -- ra, Je -- | sus ba -- nhou os | pés;
            | "" Com gran -- de | gos -- to, pra -- zer | e con -- ten -- ta -- | men -- | to;
            De -- pois da | cei -- a, meu Je -- | sus res -- ti -- tu -- | iu _ -- | se;
            | Com __ _ gran -- de | gos -- to, meu San -- | tíssi -- mo Sa -- cra -- | men -- | to.
          }
          \new Lyrics { \set associatedVoice = "theMelody"
            \set stanza = "3."
            Na sex -- ta -- | fei _ -- ra, Je -- | sus su -- biu ao | hor -- | to;
            "" Foi re -- | zar __ _ três ho -- | ras de o -- ra -- | ção; | ""
            En -- con -- trou | Ju _ -- das na | fren -- te de~u -- ma | tro _ -- | pa;
            | Já __ _ vi -- nha | e -- le, de al -- | fe -- res, ca -- pi -- | tão. | ""
          }
          \new Lyrics { \set associatedVoice = "theMelody"
            \set stanza = "4."
            "" "" "" | Ju _ -- das, pe -- | lo la -- do di -- | rei -- | to;
            Com fal -- si -- | da -- de lhe bei -- | jou de -- vi -- da -- | men -- | te;
            "" Je -- sus | dis -- se: eu co -- | nhe -- ço~a fal -- si -- | da -- _ | de;
            | Com __ _ es -- se | bei -- jo que tu | a -- go -- ra me | des -- | tes.

          }
          \new Lyrics { \set associatedVoice = "theMelody"
            \set stanza = "5."
            "" De _ -- | pois __ _ de Je -- | sus Cris -- to~ar -- ras -- | ta -- | do;
            Co -- bri -- ram | E _ -- le em | tro -- no pe -- que -- | ni -- | no;
            "" Lhe bo -- | ta -- ram~u -- ma co -- | ro -- a na ca -- | be _ -- | ça;
            | E _ -- ra te -- | ci -- da com se -- | ten -- ta~e dois es -- | pi -- | nhos.
          }
          \new Lyrics { \set associatedVoice = "theMelody"
            \set stanza = "6."
            Da -- í sa -- | í -- ram com Je -- | sus na ru -- a~es -- | trei -- | ta;
            "" Cer -- ta -- | men _ -- te~a ru -- | a de a -- mar -- | gu -- | ra;
            "" En -- con -- | trou -- se com~a Sem -- | pre Vir -- gem Ma -- | ri _ -- | a;
            | E _ -- ra~a sua | mãe __ _ que cho -- | ra -- va com ter -- | nu -- | ra.
          }
        >>
      }
      % Verse 7 is one measure shorter; also this verse is sometimes sung after v4 (incorrect order)
      \set stanza = "7."
      Nes -- te | di -- a, Nos -- sa | Se -- nho -- ra che -- | gou; % |
      Às oi -- to | ho -- ras, Sex -- ta -- | fei -- ra da Pai -- | xão; % |
      En -- con -- | trou- _ -- se com~o | seu fi -- lhi -- nho | pre _ -- | so;
      \altcol Ma -- \altcol da -- | le -- na, Oh! Que | dor no co -- ra -- | ção. %|
      % Verse 8 and 9 have the same melody as 1-6
      \repeat volta 2 {
        <<
          {
            \set stanza = "8."
            Oh! Mi -- nha | Mãe __ _ que por | mim tan -- to cho -- | ra -- | va;
            "" Sen -- do | E _ -- la, Ma -- | ri -- a~e Ma -- da -- | le -- | na;
            Quan -- do~eu | cui _ -- do que | vi -- nha~a meu so -- | cor _ -- | ro;
            | Ca _ -- da vez | mais re -- do -- | bra -- va~a mi -- nha | pe -- | na.
          }
          \new Lyrics { \set associatedVoice = "theMelody"
            \set stanza = "9."
            Che -- gou Lon -- | gui -- nho com a | lan -- ça e cra -- | vou;
            | "" No pei -- to~es -- | quer -- do, em ci -- | ma do co -- ra -- | ção; | ""
            Quan -- do~o | san -- gue lhe ba -- | ti -- a pe -- lo | ros _ -- | to;
            | Se a -- jo -- e -- | lhou, a meu | Deus pe -- diu per -- | dão. | ""
          }
        >>
      }
    }
    theChords = \chordmode {
      % v1-6
      \repeat volta 6 {
        s4. | a2:m | e:m | a:m | a:m
        | a:m | d:m | c | c
        | c | c | g | a:m
        | f | f | g | c | c8
      }
      % v7
      s4. | a2:m | e:m | a:m | a:m
      | a:m | d:m | c | c
      | c | c | g | a:m
      | f | g | c | c8
      % v8-v9 (same as 1-6)
      \repeat volta 2 {
        s4. | a2:m | e:m | a:m | a:m
        | a:m | d:m | c | c
        | c | c | g | a:m
        | f | f | g | c | c8
      }
    }
    \setStaffSize #14 % for better fit
    \include "ulsbs-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    On Wednesday, Jesus with his disciples went to the Mount of Olives, went to Jerusalem.
    He went to the Passover, my Jesus with his disciples, who suffered for the sake of our good.
    \nextverse
    On Thursday, Jesus washed the feet with great joy, pleasure and contentment.
    After the supper, my Jesus instituted with great joy, the Most Holy Sacrament.
    \nextverse
    On Friday, Jesus went up to the garden to pray three hours in prayer.
    He found Judas at the head of a troop --- there he came, like an officer, a captain.
    \nextverse
    Judas, on the right side, with falsehood gave him a proper kiss.
    Jesus said: ``I know your treachery, by this kiss that you have just given me.''
    \nextverse
    After Jesus Christ was dragged away, they seated Him on a little throne.
    They placed a crown upon His head, woven with seventy-two thorns.
    \nextverse
    Then they went out with Jesus through the narrow street, surely the street of bitterness.
    He met the Ever-Virgin Mary --- It was His mother, who wept tenderly.
    \nextverse
    On that day Our Lady arrived, at eight o'clock, on Good Friday.
    She met her little son imprisoned --- Magdalene: Oh! what pain in the heart.
    \nextverse
    ``Oh my Mother who wept so much for me, she being Mary and Magdalene.
    When I thought help was coming to me, my suffering only doubled.''
    \nextverse
    Then Longinus came with the spear and thrust it into the left side above the heart.
    When the blood struck his face, he knelt down and asked my God for forgiveness.
  \end{translation}
\endsong
