% Santo Daime: Oração
% ===================
%
\audio[title={Nossa Irmandade}]{https://www.nossairmandade.com/hinario/1/Ora\%C3\%A7\%C3\%A3o}
\audio[title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}


\beginsong{Examine a Consciência}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/1/ExamineAConsci\%C3\%AAncia}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=18s}
  \mnbeginchorus\memorize
    \[^\mn{G}]E\[^\mn{C}]xa|\[\mnc{E}C]mine a \[^\mn{D}]con\[^\mn{C}]sci|\[\mnc{G}G]ência
    E\[^\mn{C}]xa|\[\mnc{E}Am]mine \[^\mn{D}]di\[^\mn{C}]rei|\[\mnc{G}G]tinho
    \[^\mn{C}]Sou |\[\mnc{E}C]Pai e \[^\mn{D}]não \[^\mn{C}]sou |\[\mnc{G}G]filho
    Mas \[^\mn{C}]eu |\[\mnc{E}Am]não fa\[\mnc{D}G]ço \[^\mn{E}]as|\[\mnc{C}C]sim
  \mnendchorus
  \notesoff
  \beginchorus
    Cha|^mo de um a |^um \altchords{\id[2]{MK (C)} |C G7 |C}
    A todos |^eu mostro o ca|^minho \altchords{|Am Dm7 |G}
    Fa|^zendo como eu |^mando \altchords{|C G7 |C}
    Tudo |^fica ^bem fa|^cinho \altchords{|Am G7 |C}
  \endchorus
  \beginchorus
    Todos |^podem se lem|^brar
    Do |^tempo de No|^é
    A dou|^trina do meu |^Pai
    Eu en|^sino ^como |^é
  \endchorus
  \beginchorus
    |^Vamos meus ir|^mãos
    Vamos |^todos se humi|^lhar
    Pe|^dir nosso per|^dão
    Para nosso |^Pai nos ^perdo|^ar
  \endchorus
  \beginchorus
    Quem qui|^ser que se agu|^ente
    Não tem |^{a quem} se quei|^xar
    Eu |^bem que avi|^sei
    Que ha|^via ^de che|^gar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8 c | e4 e8 e8 d4 c4 | g4. g8 g4 c
        | e4 e d c | g'2 g4 c,
        | e4. e8 d4 c | g4. g8 g4 c
        | e4 e d e | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        E -- xa -- | mi -- ne a con -- ci -- | ên -- cia;
        E -- xa -- | mi -- ne di -- rei -- | tin -- ho;
        Sou | Pai e não sou | fil -- ho;
        Mas eu | não fa -- ço as -- | sim.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | g
        | a:m | g
        | c | g
        | a2:m g | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Examine your conscience; Examine it thoroughly
    I‘m the Father, not the son; But I don‘t act that way
    \nextverse
    I call one by one; To all I show the path
    Doing as I order; Everything becomes really easy
    \nextverse
    All can remember; The time of Noah
    The doctrine of my Father; I teach it like it is
    \nextverse
    Let‘s go my brothers and sisters; Let‘s all humble ourselves
    Ask our forgiveness; For our Father to forgive us
    \nextverse
    Those who want it, should endure; They have no one to complain to
    I really warned; That I would come
  \end{translation}
\endsong


\beginsong{A meu Pai Peço Firmeza}[by={Padr. Sebastião},tags={á capela, de pé},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/2/AMeuPaiPe\%C3\%A7oFirmeza}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=180s}
  \beginchorus
    \[\mnlow{G}]A meu |\[\mnlow{C}]Pai peço \[\mnlow{E}]fir|\[\mnlow{G}]me\[\mnlow{C}]za
    E não |\[\mnlow{E}]saia \[\mnlow{C}]da \[\mnlow{A}\mnlow{G}]min\[\mnlow{C}]ha |mente
  \endchorus\glueverses\beginchorus
    \[\mnlow{C}]Dou en|\[\mnlow{E}]sino \[\mnlow{C}]a \[\mnlow{A}]quem \[\mnlow{G}]não |sabe
    \[\mnlow{C}]E a\[\mnlow{D}]con|selho \[\mnlow{C}]os \[\mnlow{A}]i\[\mnlow{C}]no|centes
  \endchorus
  \notesoff\chordsoff\measureson
  \beginchorus
    Meu |Pai a ti eu |peço
    E não |saio do meu lu|gar
  \endchorus\glueverses\beginchorus
    Dai-me |força e dai-me a|mor
    Para eu |poder traba|lhar
  \endchorus
  \beginchorus
    Meu |Pai a ti eu |peço
    E |aos teus pés es|tou
  \endchorus\glueverses\beginchorus
    Ro|gando pelo |povo
    Para |ser merece|dor
  \endchorus
  \beginchorus
    Oh! |Minha Virgem |Mãe
    Oh! |Virgem prote|tora
  \endchorus\glueverses\beginchorus
    És |Rainha do |mar
    És |minha profes|sora
  \endchorus
  \beginchorus
    Oh! |Meu bendito |Pai
    Oh! |Meu Jurami|dam
  \endchorus\glueverses\beginchorus
    Cha|ma de um a |um
    Para re|ceber o per|dão
  \endchorus
  \beginchorus
    Se |todos conhe|cessem
    O po|der que meu Pai |tem
  \endchorus\glueverses\beginchorus
    Dei|xavam a ilu|são
    Que é |coisa que não con|vém
  \endchorus
  \brk
  \beginchorus
    O |mundo está em ba|lanço
    E |tudo vai balan|çar
   \endchorus\glueverses\beginchorus
    Mas |nos pés do meu |Pai
    Todos |têm que se cur|var
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8 g | c4. c8 c4. e8 | g2~ g8 c,8 c8 c8
        | e4 e8 c8 a8( g4) c8 | c2 c4
      } \break
      \repeat volta 2 {
        c8 c8 | e4 e8 c8 a4. g8 | g2~ g8 c8 c8 d8
        | d4. c8 a4. c8 | c2 c4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        A meu | Pai pe -- ço fir -- | me -- za;
        E não | sai -- a da min -- ha | men -- te;
      }
      \repeat volta 2 {
        Dou en -- | si -- no a quem não | sa -- be;
        E~a -- con -- | selho os i -- no -- | cen -- tes.
      }
    }
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    From my Father I ask for firmness
    And He never leaves my mind
    I teach those who don‘t know
    And I advise the innocents
    \nextverse
    My Father, I ask You
    And I don‘t leave my place
    Give me strength and give me love
    So that I can work
    \nextverse
    My Father, I ask You
    And I am at Your feet
    Praying for the people
    For them to be deserving
    \nextverse
    Oh! My Virgin Mother
    Oh! Virgin Protectress
    You are Queen of the sea
    You are my Professor
  \end{translation}
\endsong


\beginsong{Eu Vivo com meu Mestre}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/3/EuVivoComMeuMestre}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=454s}
  % Note: This hino might be sometimes sung two times?
  \newchords{chords_euvivocom_a}\newchords{chords_euvivocom_b}
  \mnbeginchorus\memorize[chords_euvivocom_a]
    \[^\mn{G}]Eu |\[\mnc{C}C]vivo \[\mnc{A}Am]com \[^\mn{C}]meu |\[\mnc{G}G]Mestre
    \[^\mn{C}]Eu |\[\mnc{E}Am]vi\[^\mn{C}]vo com \[\mnc{A}F]meus \[^\mn{C}]ir|\[C]mãos
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_euvivocom_b]
    \[^\mn{C}]Eu |\[\mnc{F}F]vivo \[^\mn{E}]na \[\mnc{D}G]san\[^\mn{E}]ta |\[\mnc{C}C]luz
    Estou \[^\mn{B}]no \[\mnc{A}(F)]pé \[^\mn{B}]da |\[\mnc{G}G]cruz com Ju\[\mnc{C}(Am)]ra\[^\mn{E}]mi|\[\mnc{C}C]dam
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_euvivocom_a]
    |^Eu pe^{ço a} meu |^Pai \altchords{\id[2]{MK (C)}|C Am |C}
    O que eu pe|^dir E^le me |^dá \altchords{|Am F |C}
  \endchorus\glueverses\beginchorus\replay[chords_euvivocom_b]
    Os ini|^migos que vi^erem |^contra \altchords{|F G |Am}
    Eu ^peço |^força para ^derri|^bar \altchords{F |G Am |C}
  \endchorus
  \beginchorus\replay[chords_euvivocom_a]
    Oh! |^Minha ^Virgem |^Mãe
    Oh! |^Virgem da ^Concei|^ção
  \endchorus\glueverses\beginchorus\replay[chords_euvivocom_b]
    Eu |^peço a ^Jesus |^Cristo
    Pa^ra dar |^força aqui ^{na ses}|^são
  \endchorus
  \brk
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g4 | c4 c4 a4 c4 | g2 g4 c4 | e4 c8 c8 a4 c4 | c2.
      } \break
      \repeat volta 2 {
        c4 | f4 f8 e8 d4 e4 | c8 c8 c8 b8 a4 b4 | g4 g8 g8 c4 e4 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu | vi -- vo com meu | Mes -- tre;
        Eu | vi -- vo com meus ir -- | mãos;
      }
      \repeat volta 2 {
        Eu | vi -- vo na san -- ta | luz;
        Es -- tou no pé da | cruz com Ju -- ra -- mi -- | dam.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 a:m | g1
        | a2:m f | c2.
      }
      \repeat volta 2 {
        s4 | f2 g | c f
        | g a:m | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I live with my Master
    I live with my brothers and sisters
    I live in the holy light
    I‘m at the foot of the cross with Juramidam
    \nextverse
    I ask my Father
    What I ask, He gives to me
    The enemies who come against me
    I ask for strength to defeat them
    \nextverse
    Oh! My Virgin Mother
    Oh! Virgin of Conception
    I ask Jesus Christ
    To give strength here in the session
  \end{translation}
\endsong


\beginsong{É Pedindo e é Rogando}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/4/\%C3\%89PedindoE\%C3\%89Rogando}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=620s}
  \newchords{chords_epedindo_a}\newchords{chords_epedindo_b}
  \mnbeginchorus\memorize[chords_epedindo_a]
    \[^\mn{G}]É pe|\[\mnc{C}C]dindo \[Am]{e é} \[^\mn{E}]ro|\[\mnc{G}G]gan\[^\mn{F}]do
    \[^\mn{E}]Que \[^\mn{D}]po|\[\mnc{C}Am]demos \[\mnc{G}G]al\[^\mn{D}]can|\[\mnc{C}C]çar
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_epedindo_b]
    \[^\mn{C}]Não é |\[\mnc{G}C]fa\[^\mn{C}]lar um do |\[\mnc{E}Am]ou\[^\mn{C}]tro
    Queren|\[\mnc{G}G]do ca\[\mnc{C}Am]lu\[^\mn{E}]ni|\[\mnc{C}C]ar
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_epedindo_a]
    Me apre|^sento ^{a meu} |^Pai \altchords{\id[2]{MK (C)} |C Am |G}
    E minha |^história eu ^sei con|^tar \altchords{|C G |C}
  \endchorus\glueverses\beginchorus\replay[chords_epedindo_b]
    Peço |^que todos se |^unam \altchords{|C |Am}
    E a|^prendam a ^respei|^tar \altchords{|C Am |C}
  \endchorus
  \beginchorus\replay[chords_epedindo_a]
    É |^no céu ^{e na} |^terra
    E é bei|^rando a ^beira |^mar
  \endchorus\glueverses\beginchorus\replay[chords_epedindo_b]
    O meu en|^contro com Je|^sus
    Só |^eu sei ^destrin|^char
  \endchorus
  \beginchorus\replay[chords_epedindo_a]
    Foi |^aí ^neste |^dia
    E foi nas |^águas ^de Jor|^dão
  \endchorus\glueverses\beginchorus\replay[chords_epedindo_b]
    Que ambos |^foram bati|^zados
    E come|^çou su^{a mis}|^são
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8 g8 | c4 c4 c4 e4 | g2~ g8 f8 e8 d8
        | c4 c4 g4 d'4 | c2.
      } \break
      \repeat volta 2 {
        c8 c8 | g4 c4 c4 c4 | e2~ e8 c8 c8 c8 |
        | g4 g4 c4 e4 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        É pe -- | din -- do e~é ro -- | gan -- do;
        Que po -- | de -- mos al -- can -- | çar;
      }
      \repeat volta 2 {
        Não é | fa -- lar um do | out -- ro;
        Que -- ren -- | do ca -- lu -- ni -- | ar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
      s4 | c2 a:m | g1
      | a2:m g | c2.
      }
      \repeat volta 2 {
      s4 | c1 | a:m
      | g2 a:m | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    It's by asking and praying
    That we're able to attain
    It's not by talking about each other
    Wanting to slander
    \nextverse
    I present myself to my Father
    And know how to tell my story
    I ask that all unite
    And learn to be respectful
    \nextverse
    It's in heaven and on the earth
    And long the sea
    My meeting with Jesus
    Only I know how to unravel it
    \nextverse
    It was there on this day
    And in the waters of the Jordan
    That both were baptized
    And began their mission
  \end{translation}
\endsong


\beginsong{Dem Dum}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/5/DemDum}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=785s}
  \newchords{chords_demdum_a}\newchords{chords_demdum_b}
  \mnbeginchorus\rep{3}
    \ind \[\mnc{G}(G)]Dem |\[\mnc{C}C]dum, \[\mnc{G}(G)]dem |\[\mnc{C}C]dum
    \ind \[\mnc{G}(G)]Dem |\[\mnc{E}Am]dum, \[\mnc{G}(G)]dem |\[\mnc{C}C]dum
  \mnendchorus
  \mnbeginchorus\memorize[chords_demdum_a]
    \[^\mn{G}]Deus sa|\[\mnc{C}C]be o que está \[^\mn{D}]fa|\[\mnc{C}Am]zendo
    Sen\[^\mn{D}]ta|\[\mnc{E}C]do \[^\mn{G}]no \[\mnc{D}G]seu \[^\mn{E}]lu|\[\mnc{C}C]gar
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_demdum_b]
    \[^\mn{C}]As |\[\mnc{D}Dm]doze \[^\mn{C}]ho\[\mnc{A}F]ras \[^\mn{C}]do |\[\mnc{G}G]dia
    \[^\mn{C}]Nós \[^\mn{D}]pre|\[\mnc{E}Am]ci\[^\mn{G}]sa\[\mnc{D}G]mos \[^\mn{E}]re|\[\mnc{C}C]zar
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_demdum_a]
    Pai |^nosso que estais no |^céu
    Rece|^bemos com ^ale|^gria
  \endchorus\glueverses\beginchorus\replay[chords_demdum_b]
    Nosso |^Pai e ^nossa |^Mãe
    A sem|^pre Vir^gem Ma|^ria
  \endchorus
  \beginchorus\replay[chords_demdum_a]
    O po|^der de Deus é |^grande
    Seja |^feita a vos^sa von|^tade
  \endchorus\glueverses\beginchorus\replay[chords_demdum_b]
    É quem |^nos dá ^o per|^dão
    E é a |^nossa ^majes|^tade
  \endchorus
  \beginchorus\replay[chords_demdum_a]
    Todo |^mundo pede a |^Deus
    Mas não |^sabem se ^expli|^car
  \endchorus\glueverses\beginchorus\replay[chords_demdum_b]
    Guar|^dai-me, ^defen|^dei-me
    Livrai-|^me de ^todo |^mal
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4
      \mark \markup {"3x"} \bar ".|:" \repeat volta 3 {
        g4 | c2. g4 | c2. g4
        | e'2. g,4 | c2.
      } \break
      \repeat volta 2 {
        g8 g8 | c4 c4 c4 d4 | c2~ c8 c8 c8 d8
        | e4 g4 d4 e4 | c2.
      } \break
      \repeat volta 2 {
        c4 | d4. c8 a4. c8 | g2 g4 c8 d8
        | e4 g4 d4 e4 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \repeat volta 3 {
        Dem | dum, dem | dum; Dem | dum, dem | dum.
      }
      \repeat volta 2 {
        Deus sa -- | be~o que~es -- tá fa -- | zen -- do;
        Sen -- ta -- | do no seu lu -- | gar;
      }
      \repeat volta 2 {
        As | doze ho -- ras do | di -- a;
        Nós pre -- | ci -- sa -- mos re -- | zar.
      }
    }
    theChords = \chordmode {
      \repeat volta 3 {
        s4 | c1 | c1
        | a:m | c2.
      }
      \repeat volta 2 {
        s4 | c1 | a:m
        | c2 g | c2.
      }
      \repeat volta 2 {
        s4 | d2:m f | g1
        | a2:m g | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}\footnotesize % to fit whole song on one spread
    Dem dum, dem dum; Dem dum, dem dum
    \nextverse
    God knows what He's doing; Seated in his place
    Throughout the day's twelve hours; We need to pray
    \nextverse
    Our Father who art in heaven; We receive with joy
    Our Father and our Mother; The Ever Virgin Mary
    \nextverse
    The power of God is great; Thy will be done
    It's He who grants forgiveness; And is our majesty
    \nextverse
    All ask God; But don't know how to explain themselves
    Guard me, defend me; Deliver me from all evil
  \end{translation}
\endsong


\beginsong{Aqui Eu Vou Expor}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/6/AquiEuVouExpor}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=925s}
  \mnbeginchorus\memorize
    \[^\mn{G}]A|\[\mnc{C}C]qui eu \[(Am)]vou \[^\mn{E}]ex|\[\mnc{G}(G)]po\[\mnc{E}C]r
    \[^\mn{G}]Eu |\[\mnc{F}Fmaj7]vim \[^\mn{E}]pa\[\mnc{D}C]ra \[^\mn{C}]lemb|\[\mnc{F}F]rar
    \[^\mn{A}]O mis|tério da \[^\mn{F}]o\[^\mn{A}]ra|\[\mnc{G}G]ção
    \[^\mn{C}]Não \[^\mn{D}]é |\[\mnc{E}Dm]so\[^\mn{D}]men\[\mnc{A}F]te \[^\mn{B}]re|\[\mnc{C}C]zar
  \mnendchorus
  \notesoff
  \beginchorus
    É re|^zar e ^por em |^prática \altchords{\id[2]{MK (C)} |C | \e}
    ^E en|^trar em ^comu|^nhão \altchords{|C7 |F}
    Se lem|brar de Jesus |^Cristo \altchords{| |C}
    E esque|^cer a ^ilu|^são \altchords{|G7 |C}
  \endchorus
  \beginchorus
    A minha |^Mãe sem^pre me |^olha
    ^E meu |^Pai co^migo es|^tá
    Me en|trega estes en|^sinos
    Para a|^qui eu ^expli|^car
  \endchorus
  \beginchorus
    Cada |^um cui^da de |^si
    ^Eu tam|^bém cui^do de |^mim
    Vou ze|lando esta es|^trada
    Estou fa|^zendo o ^meu jar|^dim
  \endchorus
  \beginchorus
    O que é |^do meu ^Pai é |^meu
    ^O que é |^dele eu ^posso u|^sar
    Só não |uso o que é dos |^outros
    Que po|^de me ^derri|^bar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g4 | c4 c4 c4 e4 | g2( e4) g4
        | f4 e4 d4 c4 | f2. a,8 a8
        | a8. a16 a8 a8 f4 a4 | g2 c4 d4
        | e4 d4 a4 b4 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        A -- | qui eu vou ex -- | por; __
        Eu | vim pa -- ra lem -- | brar;
        O mis -- | té -- ri -- o da o -- ra -- | ção;
        Não é | so -- men -- te re -- | zar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 a:m | g c
        | f:maj7 c | f1
        | f | g
        | d2:m f | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Here I'm going to reveal; I came to recall
    The mystery of the prayer; Is not merely to pray
    \nextverse
    One must pray and put this into practice; And enter into communion
    One must recall Jesus Christ; And to forget the illusion
    \nextverse
    My Mother always watches me; And my Father is with me
    He gives me these teachings; For me to explain them here
    \nextverse
    Each one looks after oneself; I also look after myself
    I'm taking care of this path; I'm making my garden
    \nextverse
    What belongs to my Father is mine; I can use that which is His
    But I don't use what belongs to others; Because that can throw me down
  \end{translation}
\endsong


\scleardpage
\beginsong{Eu Vou Rezar}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/7/EuVouRezar}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1121s}
  \newchords{chords_euvourezar_a}\newchords{chords_euvourezar_b}
  \mnbeginchorus\memorize[chords_euvourezar_a]
    \[^\mn{G}]Eu vou re|\[\mnc{C}C]zar que é pa\[^\mn{B}]ra \[\mnc{A}(Am)]to\[^\mn{B}]do \[^\mn{C}]mun\[^\mn{A}]do |\[\mnc{G}G]ver
    Pai \[^\mn{B}]nos\[^\mn{D}]so que estais \[^\mn{B}]no |\[^\mn{G}]céu vós \[^\mn{B}]quei\[^\mn{D}]ra \[^\mn{C}]me \[^\mn{A}]de\[^\mn{B}]fen|\[\mnc{C}C]der \[\up{2}(C7)]
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_euvourezar_b]
    \[^\mn{C}]Pão |\[\mncii{F}{E}F]nos\[\mnc{D}G]so \[^\mn{E}]de \[^\mn{F}]ca\[^\mn{D}]da |\[\mnc{C}C]dia
    Je\[^\mn{A}]sus \[\mnc{C}Am]no alto \[^\mn{A}]da |\[\mnc{G}G]cruz \[^\mn{B}]so\[^\mn{D}]freu \[^\mn{C}]to\[^\mn{A}]da a\[^\mn{B}]go|\[\mnc{C}C]nia \[\up{1}C7]
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_euvourezar_a]
    Eu pe|^di ^{e meu} Pai me |^deu  \altchords{\id[2]{MK (C)}|C F |G}
    Para eu nunca me esque|cer de São Iri|^neu ^ \altchords{|G7 |C \up{2}(C7)}
  \endchorus\glueverses\beginchorus\replay[chords_euvourezar_b]
    A |^cruz ele ^sempre consa|^grou \altchords{|F G |Am}
    ^No céu e na |^terra aqui está o meu a|^mor ^ \altchords{F |G7 |C \up{1}C7}
  \endchorus
  \beginchorus\replay[chords_euvourezar_a]
    A|^mei ^{e bem} soube a|^mar
    Meu Mestre me cha|mou eu vim lhe acompa|^nhar ^
  \endchorus\glueverses\beginchorus\replay[chords_euvourezar_b]
    Je|^sus ele ^tem todo a|^mor
    É a^qui que ele es|^tá e é aqui que eu es|^tou ^
  \endchorus
  \beginchorus\replay[chords_euvourezar_a]
    Esta men|^sagem ele ^mandou explan|^dir
    Quem não quiser escu|tar faça favor ou|^vir ^
  \endchorus\glueverses\beginchorus\replay[chords_euvourezar_b]
    Meu |^Mestre e^le não se es|^conde
    Eu ^sempre estou a|^tento com o Santíssimo Sacra|^mento ^
  \endchorus
  \beginchorus\replay[chords_euvourezar_a]
    Não |^digas que o Mes^tre não tem sa|^ber
    Ele bem ensi|nou e você não quis apren|^der ^
  \endchorus\glueverses\beginchorus\replay[chords_euvourezar_b]
    A|^gora ^é que eu quero |^ver
    É ^andar direi|^tinho sob pena de sof|^rer ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        g8 g8 g8 | c8 c8 c8 b8 a8 b8 c8 a8 | g4 g8 b8 d8 d8 d8 b8
        | g4 g8 b8 d8 c8 a8 b8
      } \alternative {
        { | c2~ c8 }
        { | c2. c4\sectionmark "B" }
      }
      \repeat volta 2 {
         | f4.( e8) d8 e8 f8 d8 | c8 c8 c8 a8 c8 c8 c8 a8
        | g4. b8 d8 c8 a8 b8
      } \alternative {
        { | c2 c4 c4 }
        { | c4 c4 \bar "|."}
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu vou re -- | zar que~é pa -- ra to -- do mun -- do | ver;
        Pai nos -- so que~es -- tais no | céu vós quei -- ra me de -- fen --
      } \alternative {
        { | der; __ }
        { | der; Pão }
      }
      \repeat volta 2 {
        |nos -- so de ca -- da | di -- a;
        Je -- sus no al -- to da | cruz so -- freu to -- da~a -- go --
      } \alternative {
        { | ni -- a. Pão }
        { | ni -- a. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 \parenthesize a:m | g1
        | g
      } \alternative {
        { | c2~ c8 }
        { | c2 c2:7 }
      }
      \repeat volta 2 {
        | f2 g | c a:m
        | g1
      } \alternative {
        { | c2 c2:7 }
        { | c2 }
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I'm going to pray for everyone to see
    Our Father who art in heaven please defend me
    Our bread of each day
    Jesus on the height of the cross suffered all agony
    \nextverse
    I asked and my Father gave me
    To never forget Saint Irineu
    The cross he always consecrated
    In heaven and on earth, here is my love
    \nextverse
    I loved and knew how to love well
    My Master called me, I came along with Him
    Jesus, he has all love
    It's here that he is and it's here that I am
    \nextverse
    This message he ordered to spread
    Those who don't want to listen, please hear it
    My Master he does not hide
    I'm always attentive with the Most Holy Sacrament
    \nextverse
    Don't say that the Master has no knowledge
    He taught well and you didn't want to learn
    It is now that I want to see
    One must walk the straight and narrow on pain of suffering
  \end{translation}
\endsong


\beginsong{Para Estar Junto a Este Cruzeiro}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/8/ParaEstarJuntoAEsteCruzeiro}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1257s}
  \newchords{chords_paraestarjunto_a}\newchords{chords_paraestarjunto_b}
  \mnbeginchorus\memorize[chords_paraestarjunto_a]
    \[^\mn{G}]Para es|\[\mnc{C}C]tar junto a \[Am]este \[^\mn{E}]cru|\[\mnc{G}G]zei\[^\mn{E}]ro
    É \[^\mn{G}]mu|\[\mnc{E}Am]dar \[^\mn{C}]de \[^\mn{A}]o\[\mnc{D}G]pi\[^\mn{E}]ni|\[\mnc{C}C]ão
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_paraestarjunto_b]
    \[^\mn{A}]Quem |\[\mnc{C}Am]a\[^\mn{A}]ma a \[\mnc{D}Dm]Je\[^\mn{C}]sus |\[\mnc{G}G]Cristo
    \[^\mn{C}]Não |\[\mnc{E}Am]fa\[^\mn{C}]la \[^\mn{A}]do \[\mnc{D}G]seu \[^\mn{E}]ir|\[\mnc{C}C]mão
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_paraestarjunto_a]
    O |^Mestre es^tá a|^qui \altchords{\id[2]{MK (C)}|C | \e}
    E|^le fala ^bem bai|^xinho \altchords{|Am G7 |C}
  \endchorus\glueverses\beginchorus\replay[chords_paraestarjunto_b]
    En|^sina a ^quem pro|^cura \altchords{|Am G7 |C}
    Dei|^xando quem não ^quer se|^guir \altchords{|Am G7 |C}
  \endchorus
  \beginchorus\replay[chords_paraestarjunto_a]
    A|^qui es^tou di|^zendo
    Para os |^meus ir^mãos ou|^vir
  \endchorus\glueverses\beginchorus\replay[chords_paraestarjunto_b]
    Quem for |^filho ^vem che|^gando
    E quem não |^for vai es^capu|^lir
  \endchorus
  \beginchorus\replay[chords_paraestarjunto_a]
    Não a|^dian^ta ser |^grande
    Sem |^possu^ir no|^breza
  \endchorus\glueverses\beginchorus\replay[chords_paraestarjunto_b]
    Meu |^Pai e ^minha |^Mãe
    Nos mos|^tra a su^a be|^leza
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8 g8 | c4 c8 c8 c4 c8 e8 | g2 e4 e8 g8
        | e4 c8 a8 d4 e4 | c2.
      } \break
      \repeat volta 2 {
        a4 | c4. a8 d4. c8 | g2 g4 c4
        | e8 c4 a8 d4 e4 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Para es -- | tar jun -- to~a es -- te cru -- | zei -- ro;
        É mu -- | dar de o -- pi -- ni -- | ão;
      }
      \repeat volta 2 {
        Quem | a -- ma~a Je -- sus Cris -- to;
        Não | fa -- la do seu ir -- | mão.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 a:m | g1
        | a2:m g | c2.
      }
      \repeat volta 2 {
        s4 | a2:m d:m | g1
        | a2:m g | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    To be next to this Cruzeiro
    One must change one's mind
    Those who love Jesus Christ
    Don't talk about their brothers and sisters
    \nextverse
    The Master is here
    He speaks very softly
    He teaches those who seek Him
    Leaving alone those who don't want to follow
    \nextverse
    Here I am saying
    For my brothers and sisters to hear me
    Those who are children are arriving
    And those who aren't are going to flee
    \nextverse
    It's no use to be great
    Without having nobility
    My Father and my Mother
    Show us your beauty
  \end{translation}
\endsong


\beginsong{Não Creia nos Mestres que te Aparecem}[by={Padr. Sebastião},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/9/N\%C3\%A3oCreiaNosMestresQueTeAparecem}
  \audio[key={D},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1411s}
  \newchords{chords_naocreianosmestres_a}\newchords{chords_naocreianosmestres_b}
  \mnbeginchorus\memorize[chords_naocreianosmestres_a]
    \[^\mn{G}]Não |\[\mnc{C}C]creia nos \[^\mn{D}]mes\[G]tres \[^\mn{C}]que \[^\mn{A}]te a\[^\mn{C}]pa|\[C]recem
    E nem \[^\mn{E}]com |\[\mnc{G}G]eles no ca\[F]min\[^\mn{E}]ho \[^\mn{C}]quei\[^\mn{F}]ra an|\[\mnc{E}E]dar
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_naocreianosmestres_b]
    |\[\mnc{G}C]Creia \[^\mn{E}]so\[\mnc{A}G]men\[^\mn{G}]te em \[^\mn{F}]seu \[^\mn{E}]Je|\[\mncii{C}{A}Am]sus
    \[^\mn{E}]Que |\[\mnc{C}F]E\[^\mn{A}]le é \[^\mn{D}]quem \[G]tem \[^\mn{C}]pa\[^\mn{A}]ra \[^\mn{C}]te |\[C]dar
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_naocreianosmestres_a]
    Meu |^Mestre a^qui a vós eu |^peço \altchords{\id[2]{MK (C)}|C G7 |C}
    |^Para ^Vós me gui|^ar \altchords{|G C |Am}
  \endchorus\glueverses\beginchorus\replay[chords_naocreianosmestres_b]
    Me |^guie no ca^minho da santa |^luz \altchords{|C |Am}
    Não |^deixa nin^guém me ata|^car \altchords{|F G7 |C}
  \endchorus
  \beginchorus\replay[chords_naocreianosmestres_a]
    |^Segue ^sempre o teu ca|^minho
    |^Deixa ^quem quiser fa|^lar
  \endchorus\glueverses\beginchorus\replay[chords_naocreianosmestres_b]
    Re|^cebe a tu^a luz de cris|^tal
    Te |^firma e te com^põe em teu lu|^gar
  \endchorus
  \beginchorus\replay[chords_naocreianosmestres_a]
    Re|^cebe ^todos que che|^gar
    |^Faz o que ^eu te man|^dar
  \endchorus\glueverses\beginchorus\replay[chords_naocreianosmestres_b]
    Não |^deixa fa^zer o que eles |^querem
    Es|^pera atá o ^dia que eu che|^gar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g4 | c8 c8 c8 d8 d8 c8 a8 c8 | c2 c8 c8 c8 e8
        | g8 g8 g8 g8 g8 e8 c8 f8 | e2.
      } %\break
      \repeat volta 2 {
        \parenthesize e4 | g4 g8 e8 a8 g8 f8 e8 | c2( a4) e'4
        | c4 a8 d8 d8 c8 a8 c8 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
          Não | crei -- a nos mes -- tres que te~a -- pa -- | re -- cem;
          E nem com | e -- les no ca -- min -- ho quei -- ra~an -- | dar;
      }
      \repeat volta 2 {
        \skip 1 | Crei -- a so -- men -- te~em seu Je -- | sus; __
        Que E -- le~é quem tem pa -- ra te | dar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2 g | c1
        | g2 f | e2.
      }
      \repeat volta 2 {
        s4 | c2 g | a1:m
        | f2 g | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Don't believe in the masters who appear to you; Nor walk on the path with them
    Believe only in your Jesus; For it's He who can give to you
    \nextverse
    My Master, here I ask You; For You to guide me
    Guide me on the path of the holy light; Don't let anyone attack me
    \nextverse
    Always follow your path; Let whoever wants to talk
    Receive your crystal light; Be firm and composed in your place
    \nextverse
    Receive all who arrive; Do as I tell you
    Don't let be done what they want; Wait until the day that I arrive
  \end{translation}
\endsong


\beginsong{Peço que Vós me Ouça}[by={Padr. Sebastião},tags={valsa},key={C},sks={C}]
  \audio[]{https://www.nossairmandade.com/hymn/10/Pe\%C3\%A7oQueV\%C3\%B3sMeOu\%C3\%A7a}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1564s}
  % Note: This hino is sometimes sung two times, but not in Oração
  \newchords{chords_pecoquevosmeouca_a}\newchords{chords_pecoquevosmeouca_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_pecoquevosmeouca_a]
    \[^\mn{G}]Meu |\[\mnc{C}C]Pai \[^\mn{F}]pe\[^\mn{E}]ço |\[\mnc{D}G]que \[^\mn{F}]Vós \[^\mn{E}]me |\[\mnc{C}C]ou|\[C7]ça
    |\[\mnc{A}Fmaj7]Para eu pe|\[\mnc{G}C]dir \[^\mn{C}]o \[^\mn{E}]per|\[\mnc{G}G]dão | \e
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_pecoquevosmeouca_b]
    \[^\mn{C}]Eu |\[\mnc{A}F]peço não |\[\mnc{G}G]só \[^\mn{F}]pa\[^\mn{E}]ra |\[\mnc{C}C]mi|\[Am]m
    \[^\mn{A}]Pa\[^\mn{C}]ra |\[\mnc{E}C]mim \[^\mn{G}]e |\[\mnc{D}G7]os \[^\mn{F}]meus \[^\mn{E}]ir|\[\mnc{C}C]mãos |\[\up{1}C7] \e
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_pecoquevosmeouca_a]
    Meu |^Pai quando |^for perdo|^ar |^ \e \altchords{\id[2]{MK (C)}|C |G7 |C |C7}
    Per|^{doa co}|^mo lhe con|^vém | \e \altchords{|Fmaj7 |C |G |\up{1}G7 \up{2}(C)}
  \endchorus\glueverses\beginchorus\replay[chords_pecoquevosmeouca_b]
    Eu |^peço que |^vós nos per|^do|^e \altchords{|F |G |Am |F}
    Como |^perdo|^ou em Be|^lém |^ \e \altchords{|C |G7 |C |\up{1}C7}
  \endchorus
  \beginchorus\replay[chords_pecoquevosmeouca_a]
    A |^barca que |^corre no |^mar |^ \e
    |^Corre no |^meu cora|^ção | \e
  \endchorus\glueverses\beginchorus\replay[chords_pecoquevosmeouca_b]
    A|^quele que |^aqui ba|^ti|^za
    Bati|^zou {\noteson\[\mnlow{G}]no \[\mnlow{F}]ri}|^{o de} Jor|^dão |^ \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 4
      \repeat volta 2 {
        g4 | c4 f4 e4 | d4 f4 e4 | c2.( | c2)( c4)
        | a'4 a4 a4 | g4 c,4 e4 | g2.~ | g2
      }
      \repeat volta 2 {
        c,4 | a'4 a4 a4 | g4 f4 e4 | c2.(
        | c4) a4 c4 
        \set melismaBusyProperties = #'() \slurDown
        | e4( << e4) \parenthesize g4\sectionmark "! (3.)" >> << g4 \parenthesize f4 >> | d4 f4 e4 | c2.~ | c2
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Meu | Pai pe -- ço | que Vós me | ou -- | ça; __ _
        | Pa -- ra~eu pe -- | dir o per -- | dão. __ _
      }
      \repeat volta 2 {
        Eu | pe -- ço não | só pa -- ra | mim; __ _
        Pa -- ra | mim __ _ e | os meus ir -- | mãos. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Meu | Pai quan -- do | for per -- do -- | ar; __ _
        Per -- | do -- a co -- | mo lhe con -- | vém. __ _
      }
      \repeat volta 2 {
        Eu | pe -- ço que | vós nos per -- |do -- | e;
        Co -- mo | per __ _ -- do -- | ou em Be -- | lém. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        A | bar -- ca que | cor -- re no | mar; __ _ _
        | Cor -- re no | meu co -- ra -- | ção. __ _
      }
      \repeat volta 2 {
        A -- | que -- le que | a -- qui ba -- | ti -- |za;
        Ba -- ti -- | zou \parenthesize no \parenthesize ri -- | o de Jor -- | dão. __ _
      }
    }
    theChords = \chordmode {
     \repeat volta 2 {
       s4 | c2. | g | c | c:7
       | f:maj7 | c | g | g2
     }
     \repeat volta 2 {
       s4 | f2. | g | c | a:m
       | c | g:7 | c | \mark \markup{\hspace #1 \super{"1"}} \parenthesize c2:7
     }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}\footnotesize % to fit whole song on one spread
    My Father I ask that You hear me, for me to ask for forgiveness
    I ask not only for me, but for me and my brothers and sisters
    \nextverse
    My Father when He forgives, he forgives as it befits Him
    I ask that You forgive us, as You forgave in Bethlehem
    \nextverse
    The boat which sails on the sea sails within my heart
    The one who baptizes here, is baptized in the Jordan River
  \end{translation}
\endsong


\beginsong{O Amor}[by={Padr. Sebastião},key={D},sks={D}]
  \audio[]{https://www.nossairmandade.com/hymn/11/OAmor}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1736s}
  \transpose{2}
  \newchords{chords_oamor_a}\newchords{chords_oamor_b}
  \mnbeginchorus\memorize[chords_oamor_a]
    \[^\mn{C}]O \[^\mn{E}]a|\[\mnc{G}C]mor é para \[^\mn{A}]ser \[^\mn{G}]distri\[^\mn{E}]bu|\[^\mn{G}]ído \altchords{\id[1]{(C)}|C | \e}
    \[^\mn{C}]E \[^\mn{E}]não \[^\mn{C}]amor \[^\mn{A}]fin|\[\mnc{G}G]gido por\[^\mn{B}]que \[\mncii{D}{C}F]ele \[^\mn{A}]cau\[^\mn{C}]sa |\[C]dor \altchords{|G F |C}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_oamor_b]
    \[^\mn{E}]O \[^\mn{G}]a|\[G]mor é o \[^\mn{B}]cam\[^\mn{D}]po \[^\mn{C}]da \[^\mn{A}]for\[^\mn{C}]mo|\[\mnc{E}C]su\[^\mn{C}]ra \altchords{|G |C}
    Onde es\[^\mn{A}]tá \[^\mn{G}]minha i\[^\mn{E}]ma\[^\mn{G}]gem |\[G]pu\[^\mn{C}]ra, \[\mnc{D}F]Deus \[^\mn{C}]foi \[^\mn{A}]quem \[^\mn{C}]cri|\[C]ou \altchords{|G F |C}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_oamor_a]
    O a|^mor é o trono da ver|dade \altchords{\id[2]{MK (D)}|D | \e}
    Onde está a majes|^tade Cris^to Nosso Se|^nhor \altchords{Bm |A A7 |D}
  \endchorus\glueverses\beginchorus\replay[chords_oamor_b]
    O a|^mor deve ser bem pro|^fundo \altchords{|A |Bm}
    Mas não é em todo |^mundo, é para ^quem acredi|^tou \altchords{|A A7 |D}
  \endchorus
  \beginchorus\replay[chords_oamor_a]
    O a|^mor é o trono de harmo|nia
    Aonde eu des|^canso e ^rezo todo |^dia
  \endchorus\glueverses\beginchorus\replay[chords_oamor_b]
    O a|^mor é da Sempre Virgem Ma|^ria
    Jesus Cristo Salva|^dor, ^Ele é quem nos |^guia
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose c d \relative c'' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        c8 e8 | g8. g16 g8 g8 a8 g8 g8 e8 | g4 g8 c,8 e8 c8 c8 a8
        | g8. g16 g8 b8 d8 c8 a8 c8 | c2.
      } \break
      \repeat volta 2 {
        e,8 g8 | g8. g16 g8 b8 d8 c8 a8 c8 | e8 c8 c8 c8 a8 g8 e8 g8
        | g4. c8 d8 c8 a8 c8 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        O a -- | mor é pa -- ra ser di -- stri -- bu -- | í -- do;
        E não a -- mor fin -- | gi -- do por -- que e -- le cau -- sa | dor.
      }
      \repeat volta 2 {
        O a -- | mor é o cam -- po da for -- mo -- | su -- ra;
        On -- de~es -- tá minha~i -- ma -- gem | pu -- ra Deus foi quem cri -- | ou.
      }
    }
    theChords = \transpose c d \chordmode {
      \repeat volta 2 {
        s4 | c1 | c1
        | g2 f2 | c2.
      }
      \repeat volta 2 {
        s4 | g1 | c1
        | g2 f2 | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}\footnotesize % to fit the whole song on one spread:
    Love is to be shared; Not to be feigned because it causes pain
    Love is the field of beauty; Where my pure image is, it was God who created it
    \nextverse
    Love is the throne of truth; Where the majesty is Christ Our Lord
    Love must be very deep; But it is not in everyone, it's for those who believed
    \nextverse
    Love is the throne of harmony; Where I rest and pray every day
    Love is of the Ever Virgin Mary; Jesus Christ the Savior, it's He who guides me
  \end{translation}
\endsong

\scleardpage
\beginsong{Eu Não sou Deus}[by={Padr. Sebastião},tags={2x, de pé},key={D},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/12/EuN\%C3\%A3oSouDeus}
  \audio[key={F},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=1857s}
  \newchords{chords_eunaosoudeus_a}\newchords{chords_eunaosoudeus_b}
  \transpose{2}
  \musicnote{Tocar 2 vezes}
  \mnbeginchorus\memorize[chords_eunaosoudeus_a]
    \[^\mn{C}]Eu \[^\mn{A}]não \[^\mn{C}]sou |\[\mnc{E}C]Deus \altchords{\id[1]{(C)}|C}
    \[^\mn{C}]Mas \[\mnc{A}Am]tenho uma \[^\mn{E}]es\[^\mn{G}]pe|\[G]rança \altchords{Am |G}
    Eu \[^\mn{B}]não \[^\mn{D}]sou |\[\mnc{F}F]Deus \altchords{|F}
    \[^\mn{E}]Mas \[\bm\mn{A}]sou \[^\mn{C}]sua semel|\[C]hança \altchords{G |C}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eunaosoudeus_b]
    \ind \[^\mn{A}]Deus \[^\mn{C}]é |\[\mnc{E}C]fo\[^\mn{C}]go, \altchords{|C}
    \ind Deus é \[^\mn{A}]á\[^\mn{G}]gua, \[^\mn{E}]Deus \[^\mn{G}]é |\[\mnc{G}G]tudo \altchords{|G}
    \ind Eu convido os \[^\mn{B}]meus \[^\mn{D}]ir|\[\mnc{F}F]mãos \altchords{|F}
    \ind Para co\[^\mn{E}]me\[\bm\mn{A}]çar \[^\mn{C}]nossos es|\[C]tudos \altchords{|C}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eunaosoudeus_a]
    Eu não sou |^Deus \altchords{\id[2]{MK (D)}|Bm}
    Mas ^tenho uma espe|^rança \altchords{|A}
    Eu não sou |^Deus \altchords{|G}
    Mas ^sou sua seme|^lhança \altchords{|D}
  \endchorus\glueverses\beginchorus\replay[chords_eunaosoudeus_b]
    \ind Deus no |^céu, \altchords{|Bm}
    \ind Deus na terra, Deus no |^mar \altchords{|A}
    \ind Eu convido os meus ir|^mãos \altchords{|G}
    \ind Para fi^car em seu lu|^gar \altchords{|D}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose c d \relative c'' {
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        c8 a8 c8 | e4. c8 a8 a8 e8 g8 | g4 g4. g8 b8 d8
        | f4. e8 a,8 c8 c8 c8
      } \alternative {
        { | c4 c4. }
        { | c4 c2 }
      }
      \repeat volta 2 {
        a8\sectionmark "B" c8 | e8. \parenthesize c16 c8 c8 a8 g8 e8 g8 | g8. \parenthesize g16 g8 g8 g8 g8 b8 d8
        | f8 f16 f16 f8 e8 a,8 c8 c8 c8 | c4 c2
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu não sou | Deus; Mas tenho uma es -- pe -- | ran -- ça;
        Eu não sou | Deus; Mas sou sua se -- me --
      } \alternative {
        { | lhan -- ça. }
        { | lhan -- ça. }
      }
      \repeat volta 2 {
        Deus é | fo -- \parenthesize go Deus é á -- gua Deus é | tu -- \parenthesize do;
        Eu con -- vi -- do~os meus ir -- | mãos; pa -- ra co -- me -- çar nos -- sos es -- | tu -- dos.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Eu não sou | Deus; Mas tenho uma es -- pe -- | ran -- ça;
        Eu não sou | Deus; Mas sou sua se -- me --
      } \alternative {
        { | lhan -- ça. }
        { | lhan -- ça. }
      }
      \repeat volta 2 {
        Deus no | céu; __ _ Deus na ter -- ra Deus no | mar; __ _
        Eu con -- vi -- do~os meus ir -- | mã -- os; pa -- ra fi -- car em seu lu -- | gar. __ _
      }
    }
    theChords = \transpose c d \chordmode {
      \repeat volta 2 {
        s4. | c2 a:m
        | g1
        | f
      } \alternative {
         { | c2~ c8 }
         { | c2~ c4 }
      }
      \repeat volta 2 {
        s4 | c1
        | g
        | f
        | c2.
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I am not God; But I have a hope
    I am not God; But I am His likeness
    \nextverse
    God is fire; God is water, God is everything
    I invite my brothers and sisters; To begin our studies
    \nextverse
    I am not God; But I have a hope
    I am not God; But I am his likeness
    \nextverse
    God in heaven; God on earth, God in the sea
    I invite my brothers and sisters; To remain in their places
  \end{translation}
\endsong


\scleardpage
\beginsong{Eu Pedi e Tive o Toque}[by={Padr. Alfredo},key={G},sks={A, G}]
  \audio[]{https://www.nossairmandade.com/hymn/534/EuPediETiveOToque}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=2009s}
  \newchords{chords_eupedietive_a}\newchords{chords_eupedietive_b}
  \transpose{-5}
  \mnbeginchorus\memorize[chords_eupedietive_a]
    \[^\mn{E}]Eu \[^\mn{F}]pe|\[\mnc{G}C]di e \[^\mn{C}]ti\[^\mn{A}]ve o |\[Fmaj7]toque \altchords{\id[1]{(A)}|A |Dmaj7}
   \[^\mn{D}]Da \[^\mn{E}]Flo|\[\mnc{F}Dm]res\[^\mn{D}]ta e \[\mnc{G}C]do Ast|\[G]ral \altchords{|Bm A |E}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eupedietive_b]
    \[^\mn{C}]A\[^\mn{D}]qui |\[\mnc{E}C]estou \[\mnc{D}Dm7]a\[^\mn{C}]vi|\[\mnc{G}G]sando \altchords{|A Bm7 |E}
    \[^\mn{D}]Que \[^\mn{B}]de|\[^\mn{G}]vemos \[\mnc{D}G7]ser \[^\mn{E}]i|\[\mnc{C}C]gual \altchords{|- E7 |A}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eupedietive_a]
    Exami|^nando o firma|^mento \altchords{\id[2]{MK (G)}|G |Cmaj7}
    O te|^souro u^niver|^sal \altchords{|Am7 |D}
  \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Sinto |^profundo ^este |^toque \altchords{|G Am7 |D}
    Deste |Rei Im^peri|^al \altchords{|- D7 |G}
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    Digo as|^sim esclare|^cendo \altchords{\id[3]{O (G)}|G |C}
    E most|^rando a ^todos |^que \altchords{|Am |D}
  \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Es|^tá nes^{te ca}|^minho \altchords{|G Am |D}
    Que pro|cure ^compreen|^der \altchords{|- D7 |G}
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    Vou di|^zendo e quero |^ver
    Esta |^ora^ção vib|^rar
  \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    No co|^ração ^{de quem} |^ama
    Para |sempre ^confor|^tar
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    Digo |^sempre com fir|^meza
    Pois sou |^capaz ^de pro|^var
  \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Quem é |^firme ^balan|^ceia
    E quem zom|bar po^de tom|^bar
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    Esta |^força balan|^ceia
    Faz as |^Estre^las bri|^lhar
  \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Foge o |^Vento ^das al|^turas
    Treme a |Terra e ^geme o |^Mar
  \endchorus
  \beginchorus\replay[chords_eupedietive_a]
    A Meu |^Pai eu agra|^deço
    Por es|^ta com^preen|^são
  \endchorus\glueverses\beginchorus\replay[chords_eupedietive_b]
    Todos |^busquem a ^Santa |^Paz
    Para |si e ^seus ir|^mãos
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \transpose c g, \relative e'' {
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        e8 f8 | g4 g4 c4 a8 a8 | a2 a4 d,8 e8
        | f4 d8 d8 g4 g4 | g2.
      } \break
      \repeat volta 2 {
        c,8 d8 | e4 e4 d4 c4 | g'4. g8 d4 b4
        | g'4. g8 d4 e4 | c2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Eu pe -- di e ti -- ve o to -- que;
        Da Flo -- res -- ta e do As -- tral.
      }
      \repeat volta 2 {
        A -- qui es -- tou a -- vi -- san -- do;
        Que de -- ve -- mos ser i -- gual.
      }
    }
    theChords = \transpose c g, \chordmode {
      \repeat volta 2 {
        s4 | c1 | f:maj7
        | d2:m c | g2.
      }
      \repeat volta 2 {
        s4 | c2 d2:m7 | g1
        | g2 g:7 | c2.
      }
    }
    \layout { #(layout-set-staff-size 16) } % to fit whole song on one spread
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I asked and received the touch
    Of the forest and the Astral
    Here I am advising
    That we must be equal
    \nextverse
    Examining the firmament
    The universal treasure
    Deep inside I feel this touch
    Of this Imperial King
    \nextverse
    I say this clarifying
    And showing to everyone
    Who is on this path
    Should try to understand
    \nextverse
    I keep saying and I want to see
    This prayer vibrate
    In the heart of those who love
    Forever giving comfort
    \nextverse
    I always say with firmness
    For I am capable of proving
    Who is firm shakes
    And who mocks can fall down
    \nextverse
    This force shakes
    It makes the stars shine
    The wind of the heights flees
    The earth trembles and the sea groans
    \nextverse
    My Father I thank you
    For this comprehension
    Everyone seek the Holy Peace
    For themselves and their brothers and sisters
  \end{translation}
\endsong


\scleardpage
\beginsong{A Magia da Oração}[by={Madr. Nonata},key={C},sks={D, C}]
  \audio[]{https://www.nossairmandade.com/hymn/14/AMagiaDaOra\%C3\%A7\%C3\%A3o}
  \audio[key={C},title={Ceu da Santa Luz}]{https://www.youtube.com/watch?v=wKMY4YGdYeY\&t=2229s}
  \newchords{songs_amagiadaoracao_a}\newchords{songs_amagiadaoracao_b}
  \mnbeginchorus\memorize[songs_amagiadaoracao_a]
    \[^\mn{C}]Meu São \[^\mn{E}]Jo|\[\mnc{G}C]ão, \[^\mn{E}]Meu \[^\mn{C}]São \[^\mn{E}]Jo|\[^\mn{G}]ão
    \[^\mn{C}]Foi quem can|\[\mnc{E}Am]tou \[^\mn{C}]es\[\mnc{G}G]ta \[^\mn{D}]can|\[\mnc{C}C]ção
  \mnendchorus\glueverses\mnbeginchorus\memorize[songs_amagiadaoracao_b]
    \[^\mn{C}]Para |\[\mnc{G}G]mim \[^\mn{C}]e para |\[\mnc{E}Em]ti
    \[^\mn{G}]Na \[^\mn{C}]ma|\[\mnc{E}Am]gi\[^\mn{C}]a da \[\mnc{G}G7]O\[^\mn{D}]ra|\[\mnc{C}C]ção
  \mnendchorus
  \notesoff
  \beginchorus\replay[songs_amagiadaoracao_a]
    Exa|^mine a consci|ência \altchords{\id[2]{MK (C)}|C | \e}
    E a|^calme seu ^cora|^ção \altchords{|Am G7 |C}
  \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    Atra|^vés da minha pa|^lavra \altchords{|Cmaj7 |Am}
    Refle|^tida na ^Ora|^ção \altchords{|C G7 |C}
  \endchorus
  \beginchorus\replay[songs_amagiadaoracao_a]
    A meu |^Pai peço fir|meza
    E não sai|^o do ^meu lu|^gar
  \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    Eu |^vivo com meu |^Mestre
    Na barca |^que cor^re no |^mar
  \endchorus
  \beginchorus\replay[songs_amagiadaoracao_a]
    É pe|^dindo e ro|gando
    Que de|^vemos ^sempre es|^tar
  \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    As |^seis horas da |^tarde
    Com a|^mor va^mos can|^tar
  \endchorus
  \beginchorus\replay[songs_amagiadaoracao_a]
    Dem |^Dum, Dem Dum Dem |Dum
    Eu não sou |^Deus Mais ten^ho espe|^rança
  \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    Eu pe|^di e tive o |^toque
    Quen rezar com |^Deus nun^ca se |^cansa
  \endchorus
  \beginchorus\replay[songs_amagiadaoracao_a]
    Estou re|^zando e sempre ze|lando
    Dentro |^do meu ^cora|^ção
  \endchorus\glueverses\beginchorus\replay[songs_amagiadaoracao_b]
    O que o Se|^nhor deixou co|^migo
    A hora sa|^grada da ^Ora|^ção
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize c8 c8 \parenthesize e8 | g2~ g8 e8 c8 e8 | g2~ g8 c,8 c8 c8
        | e4 c4 g4 d'4 | c2~ c8
      } \break
      \repeat volta 2 {
        \parenthesize c8
        c8( c8) | g2~ g8 c8 c8 c8 | e2. g,8 c8
        | e4 c8 c8 g4 d'4 | c2~ c8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Meu São Jo -- | ão __ _ Meu São Jo -- | ão; __ _
        Foi quem can -- | tou es -- ta can -- | ção; __ _
      }
      \repeat volta 2 {
        \skip 1 Pa -- ra | mim __ _ e pa -- ra | ti;
        Na ma -- | gi -- a da O -- ra -- | ção. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1 | c1
        | a2:m g | c2~ c8
      }
      \repeat volta 2 {
        s4. | g1 | e:m
        | a2:m g:7 | c2~ c8
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    My Saint John, My Saint John
    Was who sang this song
    For me and for you
    The magic of the Oração
    \nextverse
    Examine your conscience
    And calm your heart
    Through my word
    Reflected in the Oração
    \nextverse
    My Father I ask for firmness
    And I don't leave my place
    I live with my master
    With the boat that sails on the sea
    \nextverse
    I am asking and praying
    That we must always be
    At six in the afternoon
    With love we will sing
    \nextverse
    Dem Dum, Dem Dum Dem Dum
    I am not God but I have hope
    I ask and receive the touch
    Because God never tires
    \nextverse
    I am praying and always caring for
    Within of my heart
    But you Lord left with me
    This is the hour of the Oração
  \end{translation}
\endsong


\beginsong{Recebendo}[by={Odemir Raulino da Silva},tags={valsa},key={C},sks={D, C}]
  \audio[key=D]{https://www.nossairmandade.com/hymn/1527/Recebendo}
  \audio[key={C},title={Play for Daime}]{https://www.youtube.com/watch?v=jJItq9efhqM}
  \meter{3}{4}
  \mnbeginchorus\memorize
    \lrep \[^\mn{G}]Rece|\[C]ben\[^\mn{E}]do \[^\mn{D}]no |\[^\mn{C}]meu \[^\mn{B}]co\[^\mn{C}]ra|\[\mncii{D}{A}Dm]ção | \e
    \[^\mn{F}]U\[^\mn{D}]ma |\[\mncii{B}{G}G]flor |\[\mnc{F}G7]que \[^\mn{E}]me \[^\mn{D}]con|\[\mnc{C}C]for|te \rrep
    \lrep Agra|\[\mnc{A}F]deço por |tudo \[^\mn{B}]de |\[\mncii{C}{G}C]bom |\[A7] \e
    \[^\mn{E}]Deus \[^\mn{D}]nos |\[\mnc{G}Dm]liv\[^\mn{F}]re \[^\mn{D}]do |\[\mnc{G}G7]que \[^\mn{B}]é \[^\mn{D}]a |\[\mnc{C}C]mor|te \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep Esta |^é uma |mensagem |^boa | \e
    Para |^nós vi|^ver consci|^en|te \rrep
    \lrep Aumen|^tai a nos|sa ale|^gria |^ \e
    E na tris|^teza um fi|^nal para |^sem|pre \rrep
  \endchorus
  \beginchorus
    \lrep É mais |^isto que eu |tenho a di|^zer | \e
    No meu |^ponto e|^spiritu|^al | \e \rrep
    \lrep Deus nos |^cubra com |a vossa |^glória |^ \e
    E nas mal|^dades um |^ponto fi|^nal | \e \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-08
    theMelody = \relative g'' {
      \key c \major \time 3/4 \partial 2
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        g4 g4 | g4 e4 d4 | c4 b4 c4 | d4( a2~) | a4
        f'4 d4 | b2( g4) | f'4 e4 d4 | c2.( | c4)
      }
      \repeat volta 2 {
        c4\sectionmark "B" c4 | a4 a4 a4 | a4 a4 b4 | c4( g2~ | g4)
        \grace{\parenthesize e'8} e4 d4 | g4 f4 d4 | g,4 b4 d4 | c2.( | c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Re -- ce -- | ben -- do no | meu co -- ra -- | çã -- o; __ _
        U -- ma | flor __ _ | que me con -- | for -- | te.
      }
      \repeat volta 2 {
        A -- gra -- | de -- ço por | tu -- do de | bom; __ _ _
        Deus nos | liv -- re do | que é a | mor -- | te.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Es -- ta | é u -- ma | men -- sa -- gem | bo -- a; __ _
        Pa -- ra | nós vi -- | ver con -- sci -- | en -- | te.

      }
      \repeat volta 2 {
        Au -- men -- | tai a nos -- | sa a -- le | gri -- a; __ _
        (E)~na tris -- | te -- za~um fi -- | nal pa -- ra | sem -- | pre.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        É mais | is -- to que~eu | te -- nho~a di -- | zer; __ _ _
        No meu | pon -- to~e -- | spi -- ri -- tu | al. __ _
      }
      \repeat volta 2 {
        Deus nos | cub -- ra com | a vos -- sa | gló -- ria; __ _
        (E)~nas mal -- | da -- des um | pon -- to fi -- | nal. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | c2. | c2. | d:m | d:m
        | g | g:7 | c | c4
      }
      \repeat volta 2 {
        s2 | f2. | f | c | a:7
        | d:m | g:7 | c | c4
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Receiving in my heart a flower that comforts me
    I give thanks to all that is good; God free us from that which is death
    \nextverse
    This is a good message for us to live consciously
    Increase our joy, and for sadness an end forever
    \nextverse
    This is more of what I have to say at my spiritual point
    God cover us with your glory, and for wickedness a final ending
  \end{translation}
\endsong
