% Santo Daime: Chamados dos Mensageiros de São Miguel
% ===================================================
%
\audio[title={Nossa Irmandade}]{https://www.nossairmandade.com/hinario/89/ChamadosDoS\%C3\%A3oMiguel}
\audio[]{https://soundcloud.com/andreza-lima-pav-o/sets/flor-do-norte-cura-de-sao}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Com o Poder do Céu}[by={Padr. Alfredo}, key={Am}, sks={Am, G\shrp{}m--Bm}, tags={valsa, 3x, perfilado}]
  \newchords{chords_comopoderdoceu_a}\newchords{chords_comopoderdoceu_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_comopoderdoceu_a]
    |\[\mnc{E}Am]Com o |\[^\mn{C}]po\[^\mn{A}]der \[^\mn{C}]do |\[^\mn{E}]Céu, | \[^\mn{A}]da |\[\mnc{E}A]Ter\[^\mn{C#}]ra \[^\mn{A}]e |\[\mnc{E}A7]tam\[^\mn{C#}]bém \[^\mn{A}]do |\[\mnc{D}Dm]Mar | \e
    \lrep \[^\mn{D}]Or|\[Dm]deno |a \[^\mn{C}]São \[^\mn{B}]Mi|\[\mnc{A}Am]guel, | \[^\mn{E}]a |\[\mnc{B}E7]for\[^\mn{G#}]ça |\[^\mn{C}]Deus é \[^\mn{B}]quem |\[\mnc{A}Am]dá | \e \rrep
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_comopoderdoceu_b]
    \ind \[^\mn{A}]A |\[A]força |\[A7]Deus é quem |\[\mnc{D}Dm]dá, | \[^\mn{F}]pa\[^\mn{G}]ra |\[\mnc{A}F]quem tem |\[\mnc{G}G]conhe\[^\mn{A}]ci|\[\mnc{E}Am]men|to
    \ind Re|\[\mnc{G}C]conhe|\[\mnc{F}Dm]cendo os \[^\mn{E}]pri|\[\mnc{B}E]mo|res, \[^\mn{E}]e |\[\mnc{C}Am]não \[^\mn{A}]tirar |\[\mnc{C}E7]do \[^\mn{B}]pen\[^\mn{C}]sa|\[\mnc{A}Am]men|to
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_comopoderdoceu_a]
    Só |^Deus, só |Deus, só |Deus, | é |^quem pode |^nos segu|^rar | \e
    \lrep Para |^nós ven|cer a ba|^ta|lha, para a|^diante |se alcan|^çar | \e \rrep
  \endchorus\glueverses
  \beginchorus\replay[chords_comopoderdoceu_b]
    \ind Para a|^diante |^se alcan|^çar, | o que |^custa gran|^de sofri|^men|to
    \ind Que |^é a|^mar com fir|^me|za, a |^Deus Pai |^do firma|^men|to
  \endchorus
  \beginchorus\replay[chords_comopoderdoceu_a]
    O |^Deus |do firma|men|to, |^é o |^Sol e a |^Lu|a
    \lrep No firma|^mento es|tá o car|^rei|ro, e o Cru|^zeiro, ca|minhada |^su|a \rrep
  \endchorus\glueverses
  \beginchorus\replay[chords_comopoderdoceu_b]
    \ind A |^conste|^lação che|^gou, | bem jun|^tinho da |^Virgem Ma|^ri|a
    \ind \noteson\[\mnlow{G}]No \[\mnlow{G}]Cru\notesoff{}|^zeiro es|^{tá o} Ro|^sá|rio, dos pe|^didos |^em ago|^ni|a
  \endchorus
  \beginchorus\replay[chords_comopoderdoceu_a]
    A |^força quem |tem é o |Rei, | Jesus |^Cristo, o |^Mestre de |^sem|pre
    \lrep Tudo |^no cora|ção de Ma|^ri|a, na |^Terra e em to|do firma|^men|to \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 2
      \repeat volta 2 {
        r4 \parenthesize a4 \posectionmark "(1, 3, 5, 7).A" | e'4( e4)( e4) | c( a) c | e2.( | e4)( e4) \parenthesize a4
        | e4 \parenthesize cis a' | e cis a | d2.( | d4)
          \altcol\grace d8 \altmark "5." \parenthesize d4 \sectionmark "B:i" d4 | d4( d4) d4 | d c b | a2.( | a4) \parenthesize e'4
          e4 | b8( b8)( b4) gis4 | c c b | a2.( | a4)
          \altcol\grace d8 \altmark "5." \parenthesize d4 \sectionmark "B:ii" d4 | d4( d4) d4 | d c b | a2.( | a4) \parenthesize e'4
          e4 | b8( b8)( b4) gis4 | c c b | a2.( | a4)
        }
      \repeat volta 2 {
        \parenthesize a4 \sectionmark "2., 4., 6." a4 | a2 a4 | a a a | d2.~ | d4 f g | a4( a4) a4 | g g a | e2. | \once\slurDown e4( << e4) \single\altcol g4 \altmark "6." >> << e4 \single\altcol g4 >>
        | g4( g4) g4 | f f e | b2. | b4( b4) e4 | c( a) a | c b c | a2. | a4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \skip 1 | Com __ _ o | po -- der do | Céu, __ | _ _
      da | Ter -- ra e | tam -- bém do | Mar. __ | _
        \set stanza = "1.B"
        \skip 1 Or -- | de -- _ no | a São Mi -- | guel, __ | _
        \skip 1 a | for -- _ _ ça | Deus é quem | dá. __ | _
        \skip 1 Or -- | de -- _ no | a São Mi -- | guel, __ | _
        \skip 1 a | for -- _ _ ça | Deus é quem | dá. __ | _
      \set stanza = "2."
      \skip 1 A | for -- ça | Deus é quem | dá, __ | _
      pa -- ra | quem __ _ tem | co -- nhe -- ci -- | men -- | to; __ _
      Re -- | co -- _ nhe -- | cen -- do~os pri -- | mo -- | res, __ _
      e | não ti -- rar | do pen -- sa -- | men -- | to.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "3.A"
      Só | Deus, __ _ só | Deus, __ _ só | Deus, __ | _ _
      é | quem po -- de | nos se -- gu -- | rar. __ | _
        \set stanza = "3.B"
        Pa -- ra | nós __ _ ven -- | cer a ba -- | ta -- | lha,
        pa -- ra~a -- | dian -- _ _ te | se al -- can -- | çar. __ | _
        Pa -- ra | nós __ _ ven -- | cer a ba -- | ta -- | lha,
        pa -- ra~a -- | dian -- _ _ te | se al -- can -- | çar. __ | _       
      \set stanza = "4."
      Pa -- ra~a -- | dian -- te | se al -- can -- | çar, __ | _
      o que | cus -- ta gran -- | de so -- fri -- | men -- | to; __ _
      Que | é __ _ a -- | mar com fir -- | me -- | za, __ _
      a | Deus __ _ Pai | do fir -- ma -- | men -- | to.
    }
    theLyricsThree = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "5.A"
      O | Deus __ _ _ | do fir -- ma -- | men -- | to, __ _
      \skip 1 | é \skip 1 o | Sol e a | Lu -- | a.
        \set stanza = "5.B"
        \altcol No fir -- ma -- | men -- to es -- | tá o car -- | rei -- | ro,
        e~o Cru -- | zei -- _ ro, ca -- | mi -- nha -- da | su -- | a.
        \altcol No fir -- ma -- | men -- to es -- | tá o car -- | rei -- | ro,
        e~o Cru -- | zei -- _ ro, ca -- | mi -- nha -- da | su -- | a.
      \set stanza = "6."
      \skip 1 A | cons -- te -- | la -- ção che -- | gou, __ | _
      bem jun -- | ti -- nho da | Vir -- gem Ma -- | ri -- | a;
      \altcol No \altcol Cru -- | zei -- ro es -- | tá o ro -- | sá -- | rio,
      dos pe -- | di -- _ dos | em a -- go -- | ni -- | a.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "7.A"
      A | for -- ça quem | tem é o | Rei __ | _
      Je -- sus | Cris -- to, o | Mes -- tre de | sem -- | pre.
        \set stanza = "7.B"
        Tu -- do | no co -- ra -- | ção de Ma -- | ri -- | a
        \skip 1 Na | Ter -- ra~e em to -- | do fir -- ma -- | men -- | to.
        Tu -- do | no co -- ra -- | ção de Ma -- | ri -- | a
        \skip 1 Na | Ter -- ra~e em to -- | do fir -- ma -- | men -- | \once\override LyricText.color = #darkgreen to.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | a2.:m | a:m | a:m | a:m
        | a | a:7 | d:m | d2:m
          % part B
          s4 | d2.:m | d:m | a:m | a:m
          | e:7 | e:7 | a:m | a2:m
          s4 | d2.:m | d:m | a:m | a:m
          | e:7 | e:7 | a:m | a4:m
      }
      \repeat volta 2 {
        s2 | a2. | a:7 | d:m | d:m
        | f | g | a:m | a:m
        | c | d:m | e | e
        | a:m | e:7 | a:m | a4:m
      }
    }
    \layout { #(layout-set-staff-size 13) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    With the power of heaven, of Earth and the Sea
    I order Saint Michael, the strength is given by God
    \ind The strength is given by God, for those who have understanding
    \ind Recognizing the splendors, and not forgetting them
    \nextverse
    Only God, only God, only God, is who can secure us
    For us to overcome the battle, to be able to attain afterwards
    \ind To be able to attain afterwards, which costs great suffering
    \ind That is to love with firmness, The Father God of the Firmament
    \nextverse
    The Father God of the Firmament, is the Sun and the Moon
    In the firmament is the trail, and the Cross is His path
    \ind The constellation arriver, very close to the Virgin Mary
    \ind On the Cross is the Rosary, of the prayers in agony
    \nextverse
    The King has the force, Jesus Christ, the Master of all time
    Everything in the heart of Mary, on the Earth, and in the whole Firmament
  \end{translation}
\endsong


\beginsong{A Chave da Justiça}[by={Alex Polari}, key={C}, sks={C, G--B}, tags={2x}]
  % Also in: songs_astral_unilaiva_tios_queridos.tex
  \audio{https://www.nossairmandade.com/hymn/989/AChaveDaJusti\%C3\%A7a}
  \audio{https://soundcloud.com/canaljagube/107_a-chave-da-justica}
  \mnbeginchorus\memorize
    |\[\mnc{C}C]Ei\[^\mn{G}]a, vem a\[\bm]qui \[^\mn{F}]no |\[\mnc{A}F]mei\[^\mn{F}]o, vem a\[\bm]qui \[^\mn{E}]com o |\[\mnc{G}G]re\[^\mn{D}]lho \altchords{\id{(B)}|B |E |F\shrp{}}
    Eia eu \[\bmc\mn{F}]vou \[^\mn{E}]che|\[\mnc{C}C]gar,\[\bm] |viva São Mi\[\bmc\mn{F}]guel \[^\mn{E}]que |\[^\mn{C}]veio \altchords{|B | - | \e}
    Veio a\[\bmc\mn{F}]brir \[^\mn{E}]a |\[\mnc{G}G7]ban\[^\mn{D}]ca lá dos \[\bm]O\[^\mn{C}]ri|\[\mnc{E}C]xás\[\bm] \altchords{|F\shrp{}7 |B}
  \mnendchorus
  \notesoff
  \beginchorus\replay
    |^Eia, São Mi^guel que |^veio com ba^laça e es|^pada
    Veio ^pra avi|^sar^ que |Jesus Cristo ^é o |dono
    Aqui des^se ter|^reiro, e é pra ^se entre|^gar^
  \endchorus
  \beginchorus\replay
    |^Eia, São Mi^guel que |^veio balan^çando a |^tropa
    Veio ^domi|^nar,^ |peia pra quem ^é re|belde
    O fis^cal que |^veio, foi pa^ra apu|^rar^
  \endchorus
  \beginchorus\replay
    |^Salve o meu ^Mestre Im|^pério, que nes^se Cru|^zeiro
    Bem fir^mado es|^tá,^ |deu para São ^João na |terra
    A chave ^da jus|^tiça no Santo ^Daime es|\noteson\[C \up{2}\mnlow{C}]tá. \[\bm]
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody =  \relative c''' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4
      \repeat volta 2 {
        c8 \pomark g8 g8 g8 g4 f4 | a8 f8 f8 f8 f4 e4
        | g8 d8 d8 d8 f4 e4 | c2~ c4. \parenthesize \altcol c8 \altmark "2."
        | c8 c8 c8 c8 f4 e4 | c8 c8 c8 c8 f4 e4
        | g8 d16 ( d16) d8 d8 d4 c4 | << e1 \parenthesize c1 \genmark "(4.:ii)" >>
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        | Ei -- a, vem a -- qui no | mei -- o,
        vem a -- qui com~o | re -- lho;
        Eia eu vou che -- | gar, __ _
        \skip 1 | vi -- va São Mi -- guel que | vei -- o;
        Vei -- o~a -- brir a | ban -- ca __ _
        lá dos O -- ri -- | xás.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        | Ei -- a, São Mi -- guel que | vei -- o
        com ba -- la -- ça~e~es -- | pa -- da;
        Vei -- o pra~a -- vi -- | sar __ _
        \altcol que | Je -- sus Cris -- to é o | do -- no;~A
        qui des -- se ter -- | rei -- ro, e
        é pra se~en -- tre -- | gar.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        | Ei -- a, São Mi -- guel que | vei -- o
        ba -- lan -- çan -- do~a | tro -- pa;
        Vei -- o do -- mi -- | nar, __ _ \skip 1
        | pei -- a pra quem é re -- | bel -- de;
        O fis -- cal que | vei -- o, __ _
        foi pa -- ra~a -- pu -- | rar.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        | Sal -- ve o meu Mes -- tre~Im -- | pé -- rio,
        que nes -- se Cru -- | zei -- ro;
        Bem fir -- ma -- do~es -- | tá, __ _ \skip 1
        | deu pa -- ra São João na | ter -- ra;~A
        cha -- ve da jus -- | ti -- ça no
        San -- to Dai -- me~es -- | \parenthesize tá.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        c1 | f
        | g | c
        | c | c
        | g:7 | c
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Eia come here in the middle, come here with the whip
    Eia, I will arrive, viva Saint Michael who came
    Came to open the banca of the Orixás
    \nextverse
    Eia Saint Michael who came with the scale and the sword
    Came to advise that Jesus Christ is the owner
    Here in this terreiro, and that it is for us to surrender
    \nextverse
    Eia São Michael who came rocking the army
    He comes to dominate, consequences for those who are rebellious
    The guardian who came, came to purify
    \nextverse
    Salve, Oh! My Imperial Master, That this Cross
    Is well firmed here, gave to Saint John on Earth
    The key of Justice is here in the Santo Daime
  \end{translation}
\endsong


\beginsong{Mensageiro do Anjo Azul}[by={Maria Alice}, key={C}, sks={D, C--D}, tags={mazurka}]
  \meter{6}{4}
  \mnbeginchorus
    \[\mn{C}]Sou Men\[\mn{E}]sa|\[\mnc{G}C]geiro do \[\mn{A}]Anjo A\[\bmc\mn{G}]zul
    Foi \[\mn{A}]São Mi|\[\mnc{G}G7]guel \[\mn{E}]quem \[\mn{F}]me \[\mn{D}]man\[\mnc{C}C]dou
    \mnendchorus\glueverses\mnbeginchorus
    \[\mn{C}]Eu venho a|\[\mnc{G}C]qui \[\mn{C}]para do\[\mnc{E}Am]mar
    \[\mn{G}]A ca|\[\mn{E}]beça \[\mn{G}]do dra\[\mnc{C}C]gão
  \mnendchorus
  \mnbeginverse
    \[\mn{C}]Aqui \[\mn{E}]na |\[\mnc{G}C]terra
    Ve\[\mn{A}]nho fa\[\mnc{G}G7]zer \[\mn{E}]a \[\mn{F}]li\[\mn{D}]ga|\[\mnc{C}C]ção
    \[\mn{C}]Aqui \[\mn{E}]na \[\bmc\mn{G}]terra
    Ve\[\mn{A}]nho fa|\[\mnc{G}G7]zer \[\mn{E}]a \[\mn{F}]li\[\mn{D}]ga\[\mnc{C}C]ção
    \mnendverse\glueverses\mnbeginchorus
    \[\mn{C}]Ma|\[\mnc{G}C]mãe \[\mn{C}]Ieman\[\mnc{E}Am]já
    \[\mn{G}]O|\[\mn{E}]gum da \[\mn{G}]Beira-\[\mnc{C}C]Mar
  \endchorus
  \begin{translation}
    I am the messenger of the Blue Angel, Saint Michael is who commands me
    I come here to tame the head of the dragon
    \nextverse
    Here on Earth I come to make a connection
    Mother Iemanjá, Ogum of the Sea-Shore
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 6/4 \partial 4.
      \repeat volta 2 {
        c8 \posectionmark "1.A" c e | g4 g8 g8 a8 a8  g4. g8 a8 a8
        | g4. e8 f8 d8  c4.
      }
      \repeat volta 2 {
        c8 \sectionmark "1.B" c8 c8 | g4. c8 c8 c8  e2 g,8 g8
        | e'4. e8 g,8 g8  c4.
      }
      % Section 2.A is 3/4 shorter than 1.A, thus filling the mazurka
      % bars only after two repeats -- that's why it's written unfolded
      c8 \sectionmark "2.A:i" c e | g4 g8 g8 a8 a8  g4. e8 f8 d8 | c4.
      c8 \sectionmark "ii" c e g4 g8 g8 a8 a8 | g4. e8 f8 d8 c4.
      \repeat volta 2 {
        r8 \sectionmark "2.B" c4 | g4. c8 c8 c8  e2 g,4
        | e'4. e8 g,8 g8  c4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Sou Men -- sa -- | gei -- ro do An -- jo~A -- zul;
        Foi São Mi -- | guel quem me man -- dou.
      \set stanza = "1.B"
        Eu ve -- nho~a -- | qui pa -- ra do -- mar;
        A ca -- | be -- ça do dra -- gão.
      \set stanza = "2.A"
        A -- qui na | ter -- ra;
        Ve -- nho fa -- zer a li -- ga -- | ção.
        A -- qui na ter -- ra;
        Ve -- nho fa -- | zer a li -- ga -- ção.
      \set stanza = "2.B"
        Ma -- | mãe I -- e -- man -- já;
        O -- | gum da Bei -- ra-Mar.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1. | g2.:7  c4.
      }
      \repeat volta 2 {
        s4. | c2.  a2.:m | a2.:m  c4.
      }
      s4. | c2.  g2.:7 | c4.
      s4.  c2. | g2.:7  c4.
      \repeat volta 2 {
        s4. | c2.  a2.:m | a2.:m  c4.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{São Miguel}[by={Lúcio Mortimer}, key={C}, sks={D, C--E}]
  \audio{https://www.nossairmandade.com/hymn/1424/S\%C3\%A3oMiguel}
  \mnbeginchorus\memorize
    \[^\mn{G}]Eu pe|\[\mnc{C}C]di para esta \[(Am)]Luz \[^\mn{A}]me \[^\mn{B}]cla\[^\mn{C}]re|\[\mnc{D}Dm]ar \[\bm] \altchords{\id[1]{(D)}|D (Bm) |Em}
    Eu \[^\mn{E}]pe|\[\mnc{F}F]di que eu tives\[(Dm)]se \[^\mn{D}]es\[^\mn{E}]te \[^\mn{F}]a|\[\mnc{G}G]mor \[\bm] \altchords{|G (Em) |A}
    Eu pe|di para ter \[(G7)]for\[^\mn{F}]ça \[^\mn{E}]de a\[^\mn{D}]ju|\[\mnc{C}C]dar \[\bm] \altchords{| - (A7) |D}
    \[^\mn{G}]Aos es|\[G]píritos neste \[(G7)]mundo \[^\mn{A}]so\[^\mn{B}]fre|\[\mnc{C}C]dor \[\bm] \altchords{|A (A7) |D}
  \mnendchorus
  \notesoff
  \beginchorus
    Rece|^bi de meu Je^{sus esta} mis|^são ^
    Fazer es|^forço de aju^{dar o} preci|^sa^do
    Rogando à |Deus com fé ^{e convic}|^ção ^
    Para o pe|^di do po^der ser escu|^ta^do
  \endchorus
  \beginchorus
    Vou se|^guindo firme e ^forte a jor|^na^da
    Estou fir|^mado com este ^meu sagrado |^vi^nho
    Rogando |sempre defen^{der destas} ci|^la^das
    Que o ini|^migo apre^senta no ca|^mi^nho
  \endchorus
  \beginchorus
    Com São Mi|^guel, meu Ar^canjo Prote|^tor ^
    Eu tenho |^força de pas^{sar em} toda |^pro^va
    Vou confi|ando, pois es^tou com meu Se|^nhor ^
    Que ao vence|^dor prome^teu a vida |^no^va
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize g8 \genmark "(4.)" \pomark g8 g8 | c8 c16( c16) c8 c c a b c | d2( \parenthesize d8)( \parenthesize d8) d8 e8
        | f8 f16( f16) f8 f8 f8 d e f | g2( \parenthesize g8 \parenthesize g8) g8 g8
        | g8( g) g g g f e d | c2( \parenthesize c8) \parenthesize g8 g g
        | g16( \parenthesize g16)( \parenthesize g16)( \parenthesize g16) g8 g8 g8 g8 a b | c2( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 Eu pe -- | di pa -- ra es -- ta Luz me cla -- re -- | ar; __ _ _
        Eu pe -- | di que eu ti -- ves -- se es -- te a -- | mor; __ _ _
        Eu pe -- | di pa -- ra ter for -- ça de~a -- ju -- | dar; __ _
        \skip 1 Aos es -- | pí -- ri -- tos __ _ nes -- te mun -- do so -- fre -- | dor. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        \skip 1 Re -- ce -- | bi de __ _ meu Je -- sus es -- ta mis -- | são; __ _
        Fa -- zer es -- | for -- ço __ _ de~a -- ju -- dar o pre -- ci -- | sa -- do;
        Ro -- gan -- do~à | Deus __ _ com fé e con -- vi -- c -- | ção; __ _
        Pa -- ra~o pe -- | di -- _ _ _ do po -- der ser es -- cu -- | ta -- do.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        \skip 1 Vou se -- | guin -- do __ _ fir -- me~e for -- te a jor -- | na -- da;
        Es -- tou fir -- | ma -- do com es -- te meu sa -- gra -- do | vi -- nho;
        Ro -- gan -- do | sem -- pre de -- fen -- der des -- tas ci -- | la -- das;
        Que~o i -- ni -- | mi -- _ _ go a -- pre -- sen -- ta no ca -- | mi -- nho.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Com São Mi -- | guel, __ _ _ meu Ar -- can -- jo Pro -- te -- | tor; __ _
        Eu te -- nho | for -- ça __ _ de pas -- sar em to -- da | pro -- va;
        Vou con -- fi -- | an -- do, pois es -- tou com meu Se -- | nhor; __ _
        Que~ao ven -- ce -- | dor __ _ _ _ pro -- me -- teu a vi -- da | no -- va.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 \parenthesize a:m | d1:m | f2 \parenthesize d:m | g1
        | g2 \parenthesize g:7 | c1 | g2 \parenthesize g:7 | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I ask for this light to get me clear, I ask that I will have this love
    I ask to have strength to help the spirits suffering in this world
    \nextverse
    I receive from Jesus this mission, to have strength to help those who need it
    Praying to God with faith and conviction, for this request to be able to be heard
    \nextverse
    I will follow firmly with strength on this journey, I am firm with my sacred wine
    Praying always to defend these ambushes that the enemy presents on the road
    \nextverse
    With Saint Michael my protector Archangel I have strength to pass through all the test
    I go trusting therefore I am with my Lord, to the winner He promised the new life
  \end{translation}
\endsong


\beginsong{Força do Céu}[by={Dalvina Corrente}, key={C}, sks={D, C--D}]
  \audio{https://www.nossairmandade.com/hymn/1969/For\%C3\%A7aDoC\%C3\%A9u}
  \mnbeginchorus\memorize
    \[^\mn{G}]Pe|\[\mnc{C}C]di força do \[\bm]céu, da flo|\[^\mn{E}]resta \[^\mn{D}]e do \[\mnc{C}(C7)]mar \altchords{\id[1]{(D)}|D | - (D7)}
    Pe|\[\mnc{F}F]di aos meus Ar\[\bm]canjos para |\[\mnc{A}(Am)]{vir e} \[^\mn{G}]aju\[\mnc{F}F]dar \altchords{|G |(Bm) G}
    \[^\mn{G}]Pe|\[G]di a São Mi\[\bm]guel para |\[^\mn{E}]me a\[^\mn{D}]benço\[\mnc{C}C]ar \altchords{|A | - D}
    \[^\mn{G}]Lim|\[^\mn{C}]par a minha es\[\bm]trada \[^\mn{G}]para eu |\[\mnc{E}G]poder \[^\mn{D}]cami\[\mnc{C}C]nhar \altchords{| - |A D}
  \mnendchorus
  \notesoff
  \beginchorus
    Pe|^di a Santa Es^trela para |me ilumi^nar
    Pe|^di meu Papai ^Velho, São Jo|^{sé de Ar}riba^mar
    Pe|^di a Virgem ^Mãe para |me purifi^car
    Eu |pedi um con^forto a minha |^Mãe Ieman^já
  \endchorus
  \begin{translation}
    I ask the force of heaven, of the forest and the sea
    I ask my Archangels to come and help me
    I ask Sain Michael in order to bless me
    Clean my path so that I can walk
    \nextverse
    I ask the Holy Star in order to illuminate me
    I ask my Papai Velho, São Jose de Arribamar
    I ask the Virgin Mother in order to purify me
    I ask for the comfort of my mother Iemanjá
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 8
      \repeat volta 2 {
        g8 \pomark | c c c c c( c) c c | e e d d c4. c8
        | f f f f f8. f16 f8 f | a8( a16) a16 g8 g f4. g8
        | g g g g g4 g8 g | e e d d c4. g8
        | c c c c c c g g | e'8( e16)( e16) d8 d c4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Pe -- | di for -- ça do céu, __ _
        da flo -- | res -- ta e do mar;
        Pe -- | di aos meus Ar -- can -- jos
        pa -- ra | vir __ _ e a -- ju -- dar;
        Pe -- | di a São Mi -- guel
        pa -- ra | me a -- ben -- ço -- ar;
        Lim -- | par a mi -- nha~es -- tra -- da
        pa -- ra~eu | po -- der __ _ ca -- mi -- nhar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Pe -- | di a San -- ta~Es -- tre -- la
        pa -- ra | me i -- lu -- mi -- nar;
        Pe -- | di meu Pa -- pai Ve -- lho,
        São Jo -- | sé de Ar -- ri -- ba -- mar;
        Pe -- | di a Vir -- gem Mãe
        pa -- ra | me pu -- ri -- fi -- car;
        Eu | pe -- di um con -- for -- to~a
        mi -- nha | Mãe __ _ I -- e -- man -- já.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | c1 | c2 \parenthesize c:7 | f1 | \parenthesize a2:m f | g1 | g2 c | c1 | g2 c4.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Sou Comando de Maria}[by={Padr. Corrente}, off={Maria Cristina Mota}, key={D}, sks={D, D--E}]
  \audio{https://www.nossairmandade.com/hymn/1222/S\%C3\%A3oMiguel}
  \mnbeginchorus\memorize
    \[^\mn{A}]Sou co|\[\mnc{D}D]man\[^\mn{A}]do \[^\mn{D}]de \[^\mn{F#}]Ma\[\bmc\mn{A}]ri\[^\mn{F#}]a \altchords{\id[1]{(E)}|E}
    \[^\mn{D}]Prote|tor de \[^\mn{A}]São \[^\mn{E}]Jo\[\bmc\mn{D}]sé \altchords{| -}
    \[^\mn{A}]O meu |\[\mnc{G}G]nome é \[^\mn{B}]São \[\mnc{D}D]Miguel \altchords{|A E}
    \[^\mn{A}]Ar|\[A]canjo de \[^\mn{C#}]Na\[^\mn{E}]za\[\mnc{D}D]ré \altchords{|B E}
  \mnendchorus
  \notesoff
  \beginchorus
    Ando, |^ando no es^paço
    Junto |com meu São Jo^ão
    Estou |^dentro desta ^guerra
    Com o Pa|^drinho Sebasti^ão
  \endchorus
  \beginchorus
    Pise |^firme, pise ^firme
    No ca|minho de Je^sus
    Vôo |^junto com vo^cês
    Vou ze|^lando esta ^Luz
  \endchorus
  \begin{translation}
    I am the command of Mary, protector of Saint Joseph
    My name is Saint Michael, Archangel of Nazareth
    \nextverse
    I walk, I walk within the space, together with Saint John
    I am within this war, with Pardrinho Sebastião
    \nextverse
    Step firmly, step firmly, on the path of Jesus
    I fly together with you, I watch over this light
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 8
      \repeat volta 2 {
        a16 a16 | d8 a d fis a fis4 d16 d16 | d8 d a e' d4 \parenthesize a8 a8
        | g8 g b d d8( d4) a16( a16) | a8 a16( a16) cis8 e d4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Sou co -- | man -- do de Ma -- ri -- a;
        Pro -- te -- | tor de São Jo -- sé;
        O meu | no -- me~é São Mi -- guel; __ _
        Ar -- _ | can -- jo de Na -- za -- ré.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        An -- do, | an -- do no es -- pa -- ço;
        Jun -- to | com meu São Jo -- ão;
        Es -- tou | den -- tro des -- ta guer -- ra;
        Com~o Pa -- | dri -- nho Se -- bas -- ti -- ão.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Pi -- se | fir -- me, pi -- se fir -- me;
        No ca -- | mi -- nho de Je -- sus;
        \skip 1 Vôo | jun -- to com vo -- cês; __ _
        Vou ze -- | lan -- do __ _ es -- ta Luz.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | d1 | d1 | g2 d2 | a2 d4.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Mensageiro da Luz}[by={Albertina Corrente}, key={C}, sks={C, C--D}, tags={valsa}, ex={Mesa Branca}]
  \audio{https://www.nossairmandade.com/hymn/2263/MensageiroDaLuz}
  \meter{3}{4}
  \mnbeginchorus\memorize
    \[^\mn{G}]Eu |\[\mnc{C}C]sou um men\[^\mn{E}]sa|\[^\mn{G}]geiro \altchords{\id[1]{(D)}|D | -}
    Mensa|\[\mnc{A}Dm]gei\[^\mn{F}]ro \[^\mn{D}]da |\[\mnc{C}C]Luz \altchords{|Em |D}
  \mnendchorus
  \notesoff
  \beginchorus
    Eu |^sigo o meu ca|minho
    Meu ca|^minho é de Je|^sus
  \endchorus
  \notesoff
  \beginchorus
    To|^quei minha cor|neta
    Pa|^{ra relem}|^brar
  \endchorus
  \beginchorus
    Para se|^guir neste Ca|minho
    Todos |^tem que se fir|^mar
  \endchorus
  \beginchorus
    Eu |^sou um beija-|flor
    Sou do |^reino do a|^mor
  \endchorus
  \beginchorus
    A|^qui vim afir|mar
    O que |^meu Pai man|^dou
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 4.
      \repeat volta 2 {
        \parenthesize g8 \genmark "(4.)" g8( \pomark g8)
        | c8( c8) c4 e | g( g) g8( g8)
        | a8( a8) f4 d4 | c4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \skip 1 Eu __ _ | sou um men -- sa -- | gei -- ro;
      Men -- sa -- | gei -- _ ro da | Luz.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \skip 1 Eu __ _ | si -- go~o meu ca -- | mi -- nho;
      Meu ca -- | mi -- nho~é de Je -- | sus.
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \skip 1 To -- _ | quei mi -- nha cor -- | ne -- ta;
      Pa -- _ | ra __ _ re -- lem -- brar.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      Pa -- ra se -- | guir nes -- te Ca -- | mi -- nho;
      To -- dos | tem que se fir -- mar.
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
      \skip 1 Eu __ _ | sou um bei -- ja -- | flor; __ _
      Sou do | rei -- _ no do~a -- | mor.
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
      \skip 1 A -- _ | qui vim a -- fir -- | mar;
      O que __ _ | meu __ _ Pai man -- | dou.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2. | c | d:m | c4.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I am a messenger, messenger of the Light
    \nextverse
    I follow my path, my path is of Jesus
    \nextverse
    I played my trumpet to remember
    \nextverse
    To follow this Path, everyone has to firm
    \nextverse
    I am a hummingbird, I'm from the realm of love
    \nextverse
    Here I came to affirm what my Father ordered
  \end{translation}
\endsong


\beginsong{Meu Beija-flor o Sol Raiou}[by={Alessandra}, key={Dm}, sks={Dm, Cm--Em}]
  \audio{https://www.nossairmandade.com/hymn/2264/MeuBeija-FlorOSolRaiou}
  \newchords{chords_meu_bf_sol_raiou_a}\newchords{chords_meu_bf_sol_raiou_b}
  \mnbeginchorus\memorize[chords_meu_bf_sol_raiou_a]
    \[^\mn{D}]Meu bei\[^\mn{E}]ja-|\[\mnc{F}Dm]flor \[^\mn{D}]o \[\bmc\mn{F}]sol \[^\mn{E}]rai|\[\mnc{A}A]ou \[\bm] \altchords{\id[1]{(Cm)}|Cm |G}
    \[^\mn{A}]Ouvi os |\[\mnc{G}Gm]pás\[^\mn{F}]sa\[\bmc\mn{E}]ros \[^\mn{D}]can|\[\mnc{A}A]tar \[\up{1}A7] \altchords{|Fm |G \up{1}G7}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_meu_bf_sol_raiou_b]
    \[^\mn{A}]Anunci|\[\mnc{G}Gm]an\[^\mn{F}]do o \[\bmc\mn{E}]Sal\[^\mn{D}]va|\[\mnc{A}Dm]dor \altchords{|Fm |Cm}
    \[\bmc\mn{D}]Que \[^\mn{E}]à |\[\mnc{F}(B&)]Ter\[^\mn{D}]ra i\[\mnc{F}A7]rá \[^\mn{E}]vol|\[\mnc{D}Dm]tar \[\up{1}D7] \altchords{|(A\flt) G7 |Cm \up{1}C7}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    No firma|^mento ^um cla|^rão ^
    Resplande|^ceu em ^todo |^Céu ^
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Tocou e |^tornou ^a to|^car
    A ^corne|^ta de ^São Mi|^guel ^
  \endchorus
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    Santa Ma|^{ria a}^nunci|^ou ^ \altchords{\id[2]{(Em)}|Em |B}
    Na tribo |^tocou ^o cla|^rim ^ \altchords{|Am |B \up{1}B7}
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Já vem des|^cendo ^das Es|^trelas \altchords{|Am |Em}
    ^Meu guer|^reiro ^Beija-|^mim ^ \altchords{|(C) B7 |Em \up{1}E7}
  \endchorus
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    Tu Beija-|^mim flor ^de a|^mor ^
    Guerreiro |^do Pai ^Cria|^dor ^
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Dainos Sa|^úde e ^Uni|^ão
    ^Vem cu|^rar nes^ta ses|^são ^
  \endchorus
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    Mensagei|^{ro do} ^fim dos |^tem^pos
    Rei Beija-|^mim se^nhor do |^Bem ^
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Vem decla|^{rar o} ^nasci|^mento
    ^Da No|^va Je^rusa|^lém ^
  \endchorus
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    Sigo na |^bata^lha do a|^mor ^
    Com espe|^rança ^de che|^gar ^
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Agrade|^cendo ao ^Sol e à |^Lua
    ^E a |^Rai^nha do |^Mar ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        d8 \posectionmark "A" d8 e8 | f4 d f e | a,2( a8) a' a a
        | g4 f e d | a2~ a8
      }
      \repeat volta 2 {
        a'8 \sectionmark "B" a8 a8 | g4 f e d | a4.( a8) d4 e
        | f d f e | d2~ d8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Meu bei -- ja -- | flor o sol rai -- | ou; __ _
        Ou -- vi os | pás -- sa -- ros can -- | tar. _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        A -- nun -- ci -- | an -- do~o Sal -- va -- | dor; __ _
        Que à | Ter -- ra~i -- rá vol -- | tar. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        No fir -- ma -- | men -- to um cla -- | rão; __ _
        Res -- plan -- de -- | ceu em to -- do | Céu. _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        To -- cou e | tor -- nou a to -- | car;
        A cor -- ne -- | ta de São Mi -- | guel. _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        San -- ta Ma -- | ri -- a~a -- nun -- ci -- | ou; __ _
        Na tri -- bo | to -- cou o cla -- | rim. _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Já vem des -- | cen -- do das Es -- | tre -- las;
        Meu guer -- | rei -- ro Bei -- ja -- | mim. _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Tu Bei -- ja -- | mim flor de a -- | mor; __ _
        Guer -- rei -- ro | do Pai Cri -- a -- | dor. _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Dai -- nos Sa -- | ú -- de~e U -- ni -- | ão; __ _
        Vem cu -- | rar nes -- ta ses -- | são. _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        Men -- sa -- gei -- | ro do fim dos | tem -- pos;
        Rei Bei -- ja -- | mim se -- nhor do | Bem. _
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Vem de -- cla -- | rar o nas -- ci -- | men -- to;
        Da No -- | va Je -- ru -- sa -- | lém. _
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \repeat volta 2 {
        Si -- go na | ba -- ta -- lha do~a -- | mor; __ _
        Com es -- pe -- | ran -- ça de che -- | gar. _
      }
      \set stanza = "6.B"
      \repeat volta 2 {
        A -- gra -- de -- | cen -- do~ao Sol e~à | Lu -- a;
        E a | Ra -- i -- nha do | Mar. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | d1:m | a1 | g1:m | a2 \mark \markup{\hspace #-1.5 \super{"1"}} \parenthesize a8:7
      }
      \repeat volta 2 {
        s4. | g1:m | d1:m | \parenthesize bes2 a:7 | d2:m \mark \markup{\hspace #-1.5 \super{"1"}} \parenthesize d8:7
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    My hummingbird, the Sun radiated, I heard the birds sing
    Announcing the Savior, who is coming back to Earth
    \nextverse
    In the firmament a flash shimmered all throughout the heavens
    Touched and became the sounding of the trumpet of Saint Michael
    \nextverse
    Holy Mary announced, the tribe sounded the bugle
    Already from the descending stars came my warrior Beija-mim
    \nextverse
    Your Beija-mim flower of love, warrior of the Father Creator
    Give us ouyr health and our union, come to heal in this session
    \nextverse
    Messenger of the end of times, king Beija-mim the Lord of Good
    He comes to declare the birth of the New Jerusalem
    \nextverse
    I follow in this battle of love, with hope to arrive
    Giving thanks to the sun and the moon, and the Queen of the Sea
  \end{translation}
\endsong


\beginsong{Santo Daime Beija-mim}[by={Marina Ruberti}, tags={mazurka}, key={Dm}, sks={Dm, Cm--Em}, ex={Mesa Branca}]
  \audio{https://www.nossairmandade.com/hymn/2265/SantoDaimeBeija-Mim}
  \newchords{chords_santodaimebm_a}\newchords{chords_santodaimebm_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_santodaimebm_a]
    \[^\mn{A}]Com a|\[\mnc{D}Dm]mor eu re\[^\mn{E}]ce\[\mnc{F}(F)]bi \altchords{\id[1]{(Cm)}|Cm (E\flt)}
    \[^\mn{A}]Com a|\[\mnc{E}A]mor \[^\mn{C#}]eu \[^\mn{F}]vou \[^\mn{E}]te \[\mnc{D}Dm]dar \altchords{|G Cm}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_santodaimebm_b]
    \[^\mn{D}]Santo |\[\mnc{G}Gm]Daime \[^\mn{F}]Bei\[^\mn{E}]ja-\[\mnc{F}Dm]mim \altchords{|Fm Cm}
    \[^\mn{D}]Com a|\[\mnc{E}A7]mor vou \[^\mn{D}]te \[^\mn{C#}]cu\[\mnc{D}Dm]rar \altchords{|G7 Cm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_santodaimebm_a]
    Com a|^mor eu rece^bi
    Com ver|^dade eu vou te ^dar
    \endchorus\glueverses\beginchorus\replay[chords_santodaimebm_b]
    Santo |^Daime Beija-^mim
    Um se|^gredo para desven^dar
  \mnendchorus
  \beginchorus\replay[chords_santodaimebm_a]
    Com a|^mor eu rece^bi \altchords{\id[2]{(Em)}|Em (G)}
    Com a|^mor eu vou te ^dar \altchords{|B Em}
    \endchorus\glueverses\beginchorus\replay[chords_santodaimebm_b]
    Santo |^Daime para se^guir \altchords{|Am Em}
    Este a|^mor para ze^lar \altchords{|B7 Em}
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 6/4 \partial 4
      \repeat volta 2 {
        a8 \posectionmark "A" a8
        | d4 d d8 e8  f2 a8 a8
        | e4 cis8( cis8) f e  d2
      }
      \repeat volta 2 {
        d8 \sectionmark "B" d8
        | g4 g8( g8) f8 e8  f2 d8 d8
        | e8( e8) e8( e8) d cis  d2
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Com a -- | mor eu re -- ce -- bi;
        Com a -- | mor eu __ _ vou te dar.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        San -- to | Dai -- me __ _ Bei -- ja -- mim
        Com a -- | mor __ _ vou __ _ te cu -- rar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Com a -- | mor eu re -- ce -- bi;
        Com ver -- | da -- de eu vou te dar.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        San -- to | Dai -- me __ _ Bei -- ja -- mim;
        Um se -- | gre -- do pa -- ra des -- ven -- dar.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Com a -- | mor eu re -- ce -- bi;
        Com a -- | mor eu __ _ vou te dar.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        San -- to | Dai -- me pa -- ra se -- guir;
        Es -- te~a -- | mor __ _ pa -- _ ra ze -- lar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d2.:m \parenthesize f | a d2:m
      }
      \repeat volta 2 {
        s4 | g2.:m d:m | a:7 d2:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    With love I receive, with love I am going to give you
    Santo Daime Beija-mim, with love I am going to heal you
    \nextverse
    With love I receive, with truth I am going to give you
    Santo Daime Beija-mim, a secret to reveal
    \nextverse
    With love I receive, with love I am going to give you
    Santo Daime to follow, this love to take care of
  \end{translation}
\endsong


\beginsong{Eu Peço a Meu São Miguel}[by={Padr. Valdete}, key={C}, sks={D, C--E}]
  \audio{https://www.nossairmandade.com/hymn/131/EuPe\%C3\%A7oAoMeuS\%C3\%A3oMiguel}
  \newchords{chords_eupecoameusaomiguel_a}\newchords{chords_eupecoameusaomiguel_b}
  \mnbeginchorus\memorize[chords_eupecoameusaomiguel_a]
    \[^\mn{G}]Eu |\[\mnc{C}C]peço \[^\mn{E}]a \[\bmc\mn{G}]meu \[^\mn{F}]São \[^\mn{E}]Mi|\[\mnc{G}G]guel\[\bm], para |\[\mnc{F}F]Vós \[^\mn{E}]com \[\mnc{G}G]a \[^\mn{F}]Sua \[^\mn{E}]es|\[\mnc{C}C]pa\[\bm]da.
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eupecoameusaomiguel_b]
    \[^\mn{C}]Aju|\[\mnc{E}C]dai a \[^\mn{C}]domi\[\mnc{A}F]nar \[^\mn{C}]este |\[C]po\[\bm]vo, para |\[^\mn{E}]se\[^\mn{C}]guir nu\[\mnc{A}F]ma \[^\mn{C}]boa es|\[C]tra\[\bm]da.
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    Para |^seguir nes^ta boa es|^tra^da, do |^Mestre ^que nos en|^si^na.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    É cum|^prir to^dos manda|^men^tos, con|tidos aqui ^nesta Dou|^tri^na.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    En|^xotando ^os malfa|^ze^jos, a|^qui na Li^nha do Tu|^cum^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    Meus ir|^mãos vamos ^prestar aten|^ção^, para |que nós não ^sejamos |^um^.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    Is|^to não é ^um julga|^men^to, mas |^é um a^viso se|^ríssi^mo.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    Para |^quem quer se^guir na Dou|^tri^na, e pres|tar bem con^ta do ser|^vi^ço.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    E pres|^tar bem con^ta do ser|^vi^ço, ao |^nosso Mes^tre ensina|^dor^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    Para |^ver se es^tamos se|^guin^do, ou se |somos só ^uns zomba|^do^res.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    Meu |^irmão se ^está zom|^ban^do, tra|^te de se ^arrepen|^der^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    E |^peça seu ^perdão a |^Deus^, para |ver se po^der mere|^cer^.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    É se ar|^repender ^de cora|^ção^, não |^é so por ^compara|^ção^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    Por|^que o nos^so Mestre |^sa^be, se |pode te ^dar o per|^dão^.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    Se se ar|^repender ^de cora|^ção^, dá |^para to^do mundo |^ver^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    No |^seu se^guir a Dou|^tri^na, e |nas ações ^que come|^ter^.
  \endchorus
  \beginverse % to present alt key chords only
    \altchords{\id[1]{(D)}|D |A |G A |D}
    \altchords{|D G |D | - G |D}
  \endverse
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8( \posectionmark "A" g8) | c4 c8 e8 g4 f8 e8
        | g2( g4) g8( g8) | f4( f8) e8 g4 f8 e8 | c4.( c8)( c4)
      }
      \repeat volta 2 {
        c8( \sectionmark "B" c8) | e8( e)( << c \parenthesize e) \genmark "(2., 8.)" >> c a4 c8 c | c2( c4) c8( c8)
        | e8( e8) c8 c8 a4 c8 c8 | c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu __ _ | pe -- ço a meu São Mi -- | guel, __ _
        pa -- ra | Vós __ _ com a Sua es -- | pa -- _ da.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        A -- ju -- | dai a do -- mi -- nar es -- te | po -- vo,
        pa -- ra | se -- _ guir nu -- ma boa es -- | tra -- da.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Pa -- ra | se -- guir nes -- ta boa es -- | tra -- da,
        do __ _ | Mes -- _ tre que nos en -- | si -- _ na.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        É cum -- | prir __ _ _ to -- dos man -- da -- | men -- tos,
        con -- _ | ti -- dos a -- qui nes -- ta Dou -- | tri -- na.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        En -- _ | xo -- tan -- do os mal -- fa -- | ze -- jos,
        a -- _ | qui na Li -- nha do Tu -- | cum. __ _ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Meus ir -- | mãos __ _ va -- mos pres -- tar aten -- | ção, __ _
        pa -- ra | que __ _ nós não se -- ja -- mos | um. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Is -- _ | to não é um jul -- ga -- | men -- to,
        mas __ _ | é um a -- vi -- so se -- | rís -- si -- mo.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Pa -- ra | quem __ _ quer se -- guir na Dou -- | tri -- na,
        e pres -- | tar __ _ bem con -- ta do ser -- | vi -- ço.
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        E pres -- | tar bem con -- ta do ser -- | vi -- ço,
        ao __ _ | nos -- so Mes -- tre~en -- si -- na -- | dor. __ _ _
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Pa -- ra | ver __ _ se es -- ta -- mos se -- | guin -- do,
        ou se | so -- _ mos só uns zom -- ba -- | do -- res.
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \repeat volta 2 {
        Meu __ _ | ir -- mão se es -- tá zom -- | ban -- do,
        tra -- _ | te de se ar -- re -- pen -- | der. __ _ _
      }
      \set stanza = "6.B"
      \repeat volta 2 {
        E __ _ | pe -- _ ça seu per -- dão a | Deus, __ _
        pa -- ra | ver __ _ se po -- der me -- re -- | cer. __ _
      }
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7.A"
      \repeat volta 2 {
        É se~ar -- | re -- pen -- der de co -- ra -- | ção, __ _
        não __ _ | é so por com -- pa -- ra -- | ção. __ _ _
      }
      \set stanza = "7.B"
      \repeat volta 2 {
        Por -- _ | que __ _  o nos -- so Mes -- tre | sa -- be,
        se __ _ | po -- _ de te dar o per -- | dão. __ _
      }
    }
    theLyricsEight = \lyricmode {
      \set stanza = "8.A"
      \repeat volta 2 {
        Se se~ar -- | re -- pen -- der de co -- ra -- | ção, __ _
        dá __ _ | pa -- ra to -- do mun -- do | ver. __ _ _
      }
      \set stanza = "8.B"
      \repeat volta 2 {
        No __ _ | seu __ _ _ se -- guir a Dou -- | tri -- na,
        e __ _ | nas __ _ a -- ções que co -- me -- | ter. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | g | f2 g2 | c2.
      }
      \repeat volta 2 {
        s4 | c2 f2 | c1 | c2 f2 | c2.
      }
    }
    \layout { #(layout-set-staff-size 13) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I ask my Saint Michael, for you with your sword.
    Help me have dominion over the people to follow on a good road.
    \nextverse
    To follow this good road of the Master who teaches us.
    We must abide by all the commandments that are contained in this doctrine.
    \nextverse
    Driving aways evildoers, here in the line of Tucum.
    My brothers and sisters, let's pay attention, so that we aren't one of those.
    \nextverse
    This is not a judgement, but it is a serious warning.
    For those who want to follow the doctrine and present a good record of service.
    \nextverse
    It is to present a good record of service to our Master Teacher.
    To see if we are following, or if we are only mockers.
    \nextverse
    My brothers and siters, if you're mocking, be sure to repent.
    And ask forgiveness from God to see if you can deserve it.
    \nextverse
    It is to repent in our hearts, it is not to compare.
    Because Our Master knows if He can give you the forgiveness.
    \nextverse
    It is to repent in your heart, everyone can see it.
    In the way you follow the doctrine, and in the actions that you take.
  \end{translation}
\endsong


\beginsong{As Seguranças do Céu \\ Papapapaparuê}[by={Padr. Valdete}, key={G}, sks={G, D\shrp{}--B}, tags={perfilado, à capela}]
  \audio{https://www.nossairmandade.com/hymn/139/AsSeguran\%C3\%A7asDoC\%C3\%A9u}
  \mnbeginchorus
    \ind[2]\[\bmc\mnlow{B}]Pa\[\mnlow{D}]pa|\[\mnlow{G}]papa\[\bmc\mnlow{D}]paru\[\mnlow{G}]ê |-\[\bm] | \e
    \ind[2]\[\bmc\mnlow{B}]Pa\[\mnlow{D}]pa|\[\mnlow{G}]papa\[\bmc\mnlow{D}]paru\[\mnlow{G}]á |-\[\bm] | \e
  \mnendchorus
  \mnbeginchorus
    \ind[1]\[\bmc\mnlow{B}]Vou \[\mnlow{D}]cha|\[\mnlow{G}]mar nes\[\bmc\mnlow{D}]te ter\[\mnlow{G}]r|ei\[\bm]ro
    \ind[1]O|\[\mnlow{B}]gum \[\mnlow{D}]da \[\bmc\mnlow{G}]Mata O|\[\mnlow{D}]gum do \[\mnlow{G}\bm]Mar | \e
  \mnendchorus
  \mnbeginchorus
    \[\bmc\mnlow{B}]Tam\[\mnlow{D}]bém |\[\mnlow{F#}]vou cha\[\bmc\mnlow{D}]mar a\[\mnlow{F#}]q|ui \[\bm]
    |\[\mnlow{D}]As se\[\bmc\mnlow{F#}]guran|\[\mnlow{D}]ças do \[\mnlow{G}\bm]Céu | \e
  \mnendchorus
  \beginchorus
    \[\bm]São Mi|guel, São \[\bm]Gabrie|l \[\bm]
    |Junto \[\bm]com São |Rafae\[\bm]l | \e
  \endchorus
  \beginchorus
    \[\bm]Para |vir nos \[\bm]ajud|ar \[\bm]
    A |segu\[\bm]ranças |do quarte\[\bm]l | \e
  \endchorus
  \beginchorus
    \[\bm]Para |só po\[\bm]der entr|ar \[\bm]
    |As fa\[\bm]langes que |vem do C\[\bm]éu | \e
  \endchorus
  \beginchorus
    \[\bm]E não |poder \[\bm]penetr|ar \[\bm]
    |As fa\[\bm]langes de |Lúcif\[\bm]er | \e
  \endchorus
  \mnbeginchorus
    \ind[1]\[\bmc\mnlow{B}]Pa\[\mnlow{D}]ra |\[\mnlow{G}]isto \[\bmc\mnlow{D}]é pre\[\mnlow{G}]c|i\[\bm]so
    \ind[1]|\[\mnlow{B}]Ser\[\mnlow{D}]mos \[\bmc\mnlow{G}]solda|\[\mnlow{D}]dos fi\[\mnlow{G}\bm]éis | \e
  \mnendchorus
  \mnbeginchorus
    \[\bmc\mnlow{B}]Pa\[\mnlow{D}]ra |\[\mnlow{F#}]poder \[\bmc\mnlow{D}]mere\[\mnlow{F#}]c|er \[\bm]
    |\[\mnlow{D}]A se\[\bmc\mnlow{F#}]guran|\[\mnlow{D}]ças do \[\mnlow{G}\bm]Céu | \e
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative b' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 2
      \repeat volta 2 {
        b4 \sectionmark "1." d | g g d d8. g16~ | g1~ | g2 b,4 d | g g d4 d8. g16~  | g1~ | g2
      } \break
      \repeat volta 2 {
        b,4 \sectionmark "2." d | g g d d8. g16~ | g2 g4. g8 | b,4 d g g8 g8 | d4 d8. g16~ g2~ | g2
      } \break
      \repeat volta 10 {
        \mark \markup {"10x"} b,4 \sectionmark "3.-7." d | fis fis d d8. fis16~ | \slurUp fis2.~8( << fis8 \parenthesize d8) \genmark "(5.)" >> | d4 d fis fis8( fis8) | d4 d8. g16~ g2~ | g2
      } \break
      \repeat volta 2 {
        b,4 \sectionmark "8." d | g g d d8. g16~ | g2 g2 | b,4 d g g | d d8. g16~ g2~ | g2
      } \break
      \repeat volta 2 {
        b,4 \sectionmark "9." d | fis fis d d8. fis16~ | fis1 | d4 d fis fis4 | d4 d8. g16~ g2~ | g2
      } \break
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Pa -- pa -- | pa -- pa -- pa -- ru -- ê; | _ | _
        Pa -- pa -- | pa -- pa -- pa -- ru -- á. | _ | _
      }
      \set stanza = "2."
      \repeat volta 2 {
        Vou cha -- | mar nes -- te ter -- rei -- | _ ro;
        O -- | gum da Ma -- ta O -- | gum do Mar. _ | _
      }
      <<
        {
          \set stanza = "3."
          \repeat volta 2 {
            Tam -- bém | vou cha -- mar a -- qui; | _ _ _
            | As se -- gu -- ran -- _ | ças do Céu. _ | _
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "4."
          \repeat volta 2 {
            São Mi -- | guel, São Ga -- bri -- el; | _ _ _
            | Jun -- to com São __ _ | Ra -- fa -- el. _ | _
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "5."
          \repeat volta 2 {
            Pa -- ra | vir nos a -- ju -- dar; | _ _ (A)
            | se -- gu -- ran -- ças __ _ | do quar -- tel. _ | _
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "6."
          \repeat volta 2 {
            Pa -- ra | só po -- der en -- trar; | _ _ _
            | As fa -- lan -- ges que | vem do Céu. _ | _
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "7."
          \repeat volta 2 {
            E não | po -- der pe -- ne -- trar; | _ _ _
            | As fa -- lan -- ges de | Lú -- ci -- fer. _ | _
          }
        }
      >>
      \set stanza = "8."
      \repeat volta 2 {
        Pa -- ra | is -- to é pre -- ci -- | _ so;
        | Ser -- mos sol -- da -- | dos fi -- éis. _ | _
      }
      \set stanza = "9."
      \repeat volta 2 {
        Pa -- ra | po -- der me -- re -- cer; | _
        | A se -- gu -- ran -- | ças do Céu. _ | _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | g1 | g1 | g1 | g1 | g1 | g2
      }
      \repeat volta 2 {
        s2 | g1 | g1 | g1 | g1 | g2
      }
      \repeat volta 10 {
        s2 | b1:m | b1:m | d1 | d2 g2 | g2
      }
      \repeat volta 2 {
        s2 | g1 | g1 | g1 | g1 | g2
      }
      \repeat volta 2 {
        s2 | b1:m | b1:m | d1 | d2 g2 | g2
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    Papapapaparuê, Papapapaparuá
    \nextverse
    I'm going to call in this sacred place: Ogum of the Forest and Ogum of the Sea
    \nextverse
    I am also going to call here the guards of heaven
    \nextverse
    Saint Michael, Saint Gabriel, together with Saint Raphael
    \nextverse
    To come to help us, to guard this fortress
    \nextverse
    To only allow the entrance of the armies that come from heaven
    \nextverse
    And not permit the penetration of the phalanxes of Lucifer
    \nextverse
    For this it is necessary to be faithful soldiers
    \nextverse
    To be able to merit the security of heaven
  \end{translation}
\endsong


\beginsong{Viva o Senhor São Miguel \\ Falanges do Céu}[by={Padr. Valdete}, key={C}, sks={D, C--E}, tags={2x, valsa}]
  \meter{3}{4}
  \mnbeginchorus\memorize
    \[^\mn{G}]Viva o \[^\mn{E}]Se|\[\mnc{G}C]nhor \[^\mn{E}]São \[^\mn{C}]Mi|\[^\mn{G}]guel \altchords{\id[1]{(D)}|D | \e}
    \[^\mn{G}]Viva as \[^\mn{E}]fa|\[^\mn{G}]lan\[^\mn{E}]ges \[^\mn{C}]do |\[^\mn{G}]Céu \altchords{| - | \e}
    \[^\mn{G}]{E os} arcan|jos Que\[^\mn{E}]ru|\[\mnc{G}G]bins | | \e \altchords{| - |A | - | \e}
  \mnendchorus
  \notesoff
  \beginchorus
    Viva a Mãe |^do Salva|dor
    E viva |Nosso Se|nhor
    E os an|jos Sera|^fins | | \e
  \endchorus
  \beginchorus
    Que com Deus |^não tem i|gual
    Nos livra |de todo |mal
    De tudo en|quanto é ru|^im | | \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative g'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 1*9/16
      \repeat volta 2 {
        g16 \pomark g4 e | g e c | g8. g'16 g4 e | g e c | g8. g'16 g4 g
        | g g e4 | g2.~ | g2.~ | g8.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Vi -- va~o Se -- | nhor São Mi -- | guel;
        Vi -- va~as fa -- | lan -- ges do | Céu;
        E~os ar -- can -- | jos Que -- ru -- | bins. | _ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Vi -- va~a Mãe | do Sal -- va -- | dor;
        E vi -- va | Nos -- so Se -- | nhor;
        E os an -- | jos Se -- ra -- | fins. | _ | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Que com Deus | não tem i -- | gual;
        Nos li -- vra | de to -- do | mal;
        De tu -- do~en -- | quan -- to~é ru -- | im. | _ | _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s16~s2 | c2. | c2. | c2. | c2.
        | c2. | g2. | g2. | g8.
      }

    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Viva the Lord Saint Michael
    Viva the phalanxes of heaven
    And the cherubim archangels
    \nextverse
    Viva the Mother of the Savior
    And viva our Lord
    And the seraphim angels
    \nextverse
    Because God has no equal
    He delivers us from all evil
    From everything that is bad
  \end{translation}
\endsong


\beginsong{Sete Cruzes de São Miguel}[by={Isabel Barsé}, key={Dm}, sks={Cm--Em}, tags={mazurca}]
  \audio{https://www.nossairmandade.com/hymn/2266/SeteCruzesDeS\%C3\%A3oMiguel}
  \meter{6}{4}
  \mnbeginchorus\memorize
    \lrep \[^\mn{A}]As sete |\[\mnc{D}Dm]cruzes de São \[^\mn{F}]Mi\[\bmc\mn{A}]guel \altchords{\id[1]{(Em)}|Em}
    \[^\mn{G}]Estão a|\[\mnc{F}A7]qui \[^\mn{E}]pra \[^\mn{C#}]te \[^\mn{E}]liber\[\mnc{D}Dm]tar \rrep \altchords{|B7 Em}
    \lrep \[^\mn{D}]São sete |\[Dm]cruzes, são sete \[\bm]cru\[^\mn{A}]zes \altchords{|Em}
    São sete |\[\mnc{F}A7]cruzes \[^\mn{E}]pra \[^\mn{C#}]te \[^\mn{E}]liber\[\mnc{D}Dm]tar \rrep \altchords{|B7 Em}
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep Todos os |^seres que me acom^panham
    Vós |^queiram me respei^tar \rrep
    \lrep Eu sou o |^chefe desta ^casa
    Estou a|^qui para coman^dar \rrep
  \endchorus
  \beginchorus
    \lrep Esta |^é a casa de ^Deus
    Esta |^é a casa de ^Deus \rrep
    \lrep Sou |^Luz, sou ^Luz
    Estou a|^qui pra te liber^tar \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 6/4 \partial 4.
      \repeat volta 2 {
        \parenthesize a8 \posectionmark "A" a a | d4 d8 d d f  a4( a8)( << a8) \parenthesize g8 \genmark "(1.)" >> g( g) | f4 e8 cis e e  d4.
      }
      \repeat volta 2 {
        \parenthesize d8 \sectionmark "B" d( d) | d4 d8( d) d( d)  d4 \parenthesize a8 a a a
      } \alternative {
        { | f'8( f) e cis e e  d4. }
        { | f8( f) e cis e e  d4. \dacapo  \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        As se -- te | cru -- zes de São Mi -- guel; __ _
        (Es) -- tão a -- | qui pra te li -- ber -- tar.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        São se -- te | cru -- zes, são se -- te cru -- zes;
        São se -- te 
      } \alternative {
        { | cru -- zes pra te li -- ber -- tar. }
        { | cru -- zes pra te li -- ber -- tar. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        To -- dos os | se -- res que me~a -- com -- pa -- nham; __ _
        Vós __ _ | quei -- ram me res -- pei -- tar.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Eu sou o | che -- fe __ _ des -- ta ca -- sa;
        Es -- tou a -- 
      } \alternative {
        { | qui __ _ pa -- ra co -- man -- dar. }
        { | qui __ _ pa -- ra co -- man -- dar. }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        \skip 1 Es -- ta | é a ca -- sa de Deus; __ _
        \skip 1 Es -- ta | é a ca -- sa de Deus.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 Sou __ _ | Luz, __ _ _ sou __ _ Luz;
        \skip 1 Es -- tou a --
      } \alternative {
        { | qui __ _ pra te li -- ber -- tar. }
        { | qui __ _ pra te li -- ber -- tar. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | d2.:m  d2.:m | a2.:7  d4.:m
      }
      \repeat volta 2 {
       s4. | d2.:m  d2.:m
      } \alternative {
        { | a2.:7  d4.:m }
        { | a2.:7  d4.:m }
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    These seven crosses of Saint Michael are here to set you free
    They are 7 crosses, they nare 7 crosses, they are 7 crosses to set you free
    \nextverse
    All the beings who accompany me, you all want me to respect
    I am the chief of this house, I am here to command
    \nextverse
    This is the house of Godd, this is the house of God
    I am light, I am light, I am light to set you free
  \end{translation}
\endsong


\beginsong{Clareia}[by={Paulo Roberto de Souza}, tags={perfilado, à capela}, key={D}, sks={D, C-E}]
  \audio{https://www.nossairmandade.com/hymn/2267/Clareia}
  \audio{https://soundcloud.com/spencer-stewart-3/11-clareia?in=spencer-stewart-3/sets/sao-miguel-work-with-padrinho}
  \mnbeginchorus
    \[\mnlow{A}]Cla\[\mnlow{F#}]reia, \[\mnlow{A}]cla\[\mnlow{D}]reia, \[\mnlow{F#}]cla\[\mnlow{A}]reia
    Estou ven\[\mnlow{C#}]do \[\mnlow{E}]tudo cla\[\mnlow{G}]re\[\mnlow{F#}\mnlow{D}]ar
    \mnendchorus\glueverses\mnbeginchorus
    \[\mnlow{D}]Lua \[\mnlow{G}]cheia, \[\mnlow{D}]lu\[\mnlow{E}]a \[\mnlow{F#}]cheia
    Ilu\[\mnlow{A}]mina, nas \[\mnlow{C#}]al\[\mnlow{E}]turas on\[\mnlow{G}]de es\[\mnlow{F#}\mnlow{D}]tás
  \mnendchorus
  \mnbeginchorus
    \[\mnlow{a}]Per\[\mnlow{F#}]fila, \[\mnlow{A}]te a\[\mnlow{D}]pruma, \[\mnlow{F#}]te \[\mnlow{A}]firma
    Em honra ao Glo\[\mnlow{C#}]rio\[\mnlow{E}]síssimo São \[\mnlow{G}]Mi\[\mnlow{F#}\mnlow{D}]guel
    \mnendchorus\glueverses\mnbeginchorus
    \[\mnlow{D}]Para ser\[\mnlow{G}]vir ao valoro\[\mnlow{D}]so \[\mnlow{B}]Guar\[\mnlow{D}]di\[\mnlow{F#}]ão
    Prín\[\mnlow{A}]cipe dos \[\mnlow{C#}]e\[\mnlow{E}]xércitos \[\mnlow{G}]dos \[\mnlow{F#}\mnlow{D}]céus
  \mnendchorus
  \mnbeginchorus
    \[\mnlow{A}]Com a sua es\[\mnlow{F#}]pada \[\mnlow{A}]de \[\mnlow{D}]fogo
    \[\mnlow{A}]Com \[\mnlow{C#}]seu \[\mnlow{E}]escudo \[\mnlow{G}]de \[\mnlow{F#}\mnlow{D}]luz
    \mnendchorus\glueverses\mnbeginchorus
    \[\mnlow{D}]Onde está es\[\mnlow{G}]crito ''Quem como D\[\mnlow{D}]eus, \[\mnlow{E}]nin\[\mnlow{F#}]guém``
    Seja na \[\mnlow{A}]Terra, lá \[\mnlow{C#}]no \[\mnlow{E}]Céu ou no \[\mnlow{G}]a\[\mnlow{F#}\mnlow{D}]lém
  \mnendchorus
  \begin{translation}
    Clareia, clareia, clareia
    I'm seeing everything getting clearer
    Full moon, full moon
    Illuminates in the heights where she is
    \nextverse
    Align yourself, center yourself, firm yourself
    To honor the glorious Archangel Saint Michael
    To serve the greatest guardian
    Prince of the Celestial army
    \nextverse
    With His sword of fire
    With His shield of light
    Where it is written ``Who is as God, nobody''
    Here on Earth, there in the heavens and in the beyond
  \end{translation}
\endsong


\beginsong{A São Miguel que Domine}[by={Francisco Cavalcante de Lima}, tags={valsa}, ex={Mesa Branca}, key={Gm}, sks={Gm, (F\shrp{}m)--(Gm)}]
  \audio{https://www.nossairmandade.com/hymn/2268/AS\%C3\%A3oMiguelQueDomine}
  \newchords{chords_asaomiguelquedomine_a}\newchords{chords_asaomiguelquedomine_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_asaomiguelquedomine_a]
    \[^\mn{D}]Eu |\[\mnc{G}Gm]peço \[^\mn{A}]o |\[^\mn{B&}]meu São \[^\mn{A}]Mi|\[\mnc{C}Cm]guel \altchords{\id[1]{(Em) \capo{3}}|Em | - |Am}
    Que \[^\mn{B&}]do|\[^\mn{A}]mine \[^\mn{G}]o |\[\mnc{F#}D]mal \[^\mn{D}]que a|\[\mnc{E&}Cm]qui \[^\mn{D}]e\[^\mn{C}]xis|\[\mnc{D}D]tir |\[\up{1}D7] \e \altchords{| - |B |Am |B |\up{1}B7}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_asaomiguelquedomine_b]
    \[^\mn{D}]A|\[\mnc{C}Cm]qui nós \[^\mn{D}]bus|\[^\mn{E&}]ca\[^\mn{D}]mos \[^\mn{C}]o |\[\mnc{G}Gm]bem \[^\mn{D}]e \[^\mn{B&}]a \altchords{|Am | - |Em}
    |\[^\mn{G}]Fa\[^\mn{D}]zer \[^\mn{E&}]o |\[^\mn{D}]bem \[^\mn{C}]e \[^\mn{B&}]sem |\[\mnc{A}D7]o\[^\mn{B&}]lhar \[^\mn{A}]a |\[\mnc{G}Gm]quem |\[\up{1}G7] \e \altchords{| - | - |B7 |Em |\up{1}E7}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_asaomiguelquedomine_a]
    O |^centro |do Mestre é |^livre
    Na |linha di|^reita nós |^vamos se|^guir |^ \e
    \endchorus\glueverses\beginchorus\replay[chords_asaomiguelquedomine_b]
    Consa|^grando |este apo|^sento ze|lando
    A |luz, que é o |^nosso ali|^men|^to
  \endchorus
  \beginchorus\replay[chords_asaomiguelquedomine_a]
    Conser|^vando |a Santa |^Luz \altchords{\id[2]{(Am)}|Am | - |Dm}
    Ela é |quem nós con|^duz va|^mos cami|^nhar |^ \e \altchords{| - |E |Dm |E |\up{1}E7}
    \endchorus\glueverses\beginchorus\replay[chords_asaomiguelquedomine_b]
    Todos |^seres que |devem res|^peito \altchords{|Dm | - |Am}
    To|da natu|reza cons|^pira e|^fei|^to \altchords{| - | - |E7 |Am |\up{1}A7}
  \endchorus
  \beginchorus\replay[chords_asaomiguelquedomine_a]
    Curru|^pipi|pipira|^guá o |Mestre
    Cha|^mou va|^mos traba|^lhar |^ \e
    \endchorus\glueverses\beginchorus\replay[chords_asaomiguelquedomine_b]
    Agrade|^cemos a |força Di|^vina
    Jun|to a São Mi|guel é |^quem nós do|^mi|^na
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \minor \time 3/4 \partial 1*5/8
      \repeat volta 2 {
        r8 \posectionmark "A" \parenthesize d4( d) | g( g) a | bes bes a | c( c) bes | a a g
        | fis( d) d | es d c | d2.~ | d8 
      }
      \repeat volta 2 {
        \parenthesize d8 \sectionmark "B" \parenthesize d4 d | c( c) d | es d c | g' d bes | g d' es
        | d( c) bes | a bes a | g2.~ | g8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        \skip 1 Eu | pe -- ço o | meu São Mi -- | guel;
        Que do -- | mi -- ne o | mal que a -- | qui e -- xis -- | tir. __ | _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        \skip 1 \skip 1 A -- | qui nós bus -- | ca -- mos o | bem e a;
        | Fa -- zer o | bem e sem | o -- lhar a | quem. __ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        \skip 1 O | cen -- _ tro | do Mes -- tre~é | li -- vre;
        Na | li -- nha di -- | rei -- ta nós | va -- mos se -- | guir. __ | _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 Con -- sa -- | gran -- _ do | es -- te~a -- po -- | sen -- to ze -- | lan -- do;
        A | luz, que~é o | nos -- so~a -- li -- | men -- | to.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Con -- ser -- | van -- _ do | a San -- ta | Luz;
        E -- la~é | quem nós con -- | duz __ _ va -- | mos ca -- mi -- | nhar. __ | _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 To -- dos | se -- res que | de -- vem res -- | pei -- to;
        To -- | da na -- tu -- | re -- za cons -- | pi -- ra e -- | fei -- | to.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Cur -- ru -- | pi -- _ pi -- | pi -- pi -- ra -- | guá __ _ o | Mes -- tre;
        Cha -- | mou __ _ va -- | mos tra -- ba -- | lhar. __ | _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        A -- gra -- de -- | ce -- mos a | for -- ça Di -- | vi -- na;
        Jun -- | to~a São Mi -- | guel __ _ é | quem nós do -- | mi -- | na.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 s8 | g2.:m | g:m | c:m | c:m
        | d | c:m | d | \mark\markup{\super{"1"}}\parenthesize d8:7
      }
      \repeat volta 2 {
        s2 s8 | c2.:m | c2.:m | g:m | g:m
        | g:m | d:7 | g:m | \mark\markup{\super{"1"}}\parenthesize g8:7
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I ask of my Saint Michael who dominates over the negativity that exists here
    Here we seek the good and we do good work without regard to who it is
    \nextverse
    The center of the Master is free, in the direct line we are going to follow
    Consecrating this space, caring for the light, which is our food
    \nextverse
    Conserving the Holy Light, it is what directs us, let's walk
    All beings that can respect, all of nature conspires in this effect
    \nextverse
    Currupipipipiraguá the Master calls us to work
    We give thanks to the divine strength who, together with Saint Michael, dominates
  \end{translation}
\endsong


\beginsong{Espada de São Miguel \\ Da Terra Ao Astral}[by={Baixinha}, key={Dm}, sks={Dm, Cm--Em}]
  % Also in: songs_astral_cura_diversos.tex
  \audio{https://www.nossairmandade.com/hymn/2399/DaTerraAoAstral}
  \mnbeginchorus\memorize
    \[^\mn{A}]Da \[\bmc\mn{D}]Terra \[^\mn{F}]ao as|\[\mnc{A}Dm]tral \[\bm] | \e \altchords{\id[1]{(Em)}|Em | \e}
    Os i\[^\mn{F}]ni\[\bm]mi\[^\mn{D}]gos a\[^\mn{B&}]ta|\[\mnc{A}A]car \[\bm] | \e \altchords{|B | \e}
    Na es\[\bmc\mn{C#}]pada de \[^\mn{E}]São Mi|\[\mnc{G}Gm]guel \[\bm] |\[A7] \e \altchords{|Am |B7}
    \[^\mn{E}]Todos \[\bmc\mn{F}]vão se \[^\mn{E}]transfor|\[\mnc{D}Dm]mar \[\bm] | \e \altchords{|Em | \e}
  \mnendchorus
  \notesoff
  \beginchorus
    As ^estrelas do |^Céu ^ | \e
    Brilham ^pra quem tem a|^mor ^ | \e
    Nas ^matas do meu |^Pai ^ |^ \e
    Corre ^água e nasce |^flor ^ | \e
  \endchorus
  \beginchorus
    As ^curas estão a|^ber^-|'tas \altchords{\id[2]{(Cm)}|Cm | \e}
    Aos ^bons de cora|^ção ^ | \e \altchords{|G | \e }
    Quem ^recebe me|^re^|^ce \altchords{|Fm |G7}
    Agra^dece, nunca es|^que^-|ce \altchords{|Cm | \e}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, 2021-09
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 1*5/8
      \repeat volta 4 {
        a8\pomark d16( d16) d8 f f | a1~ | a8( a8) a8 f f d d bes | a1~
        a4( a8) a cis cis e e | g1( | g4) e8 e f f e e | d1( | d4.)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Da Ter -- _ ra ao as -- | tral; __ | _
        Os i -- ni -- mi -- gos a -- ta -- | car; __ | _
        Na es -- pa -- da~de São Mi -- | guel; __ | _
        To -- dos vão se trans -- for -- | mar. __ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        As es -- _ tre -- las do | Céu; __ | _
        \skip 1 Bri -- lham pra quem tem a -- | mor; __ | _
        \skip 1 Nas ma -- tas do meu | Pai; __ | _
        Cor -- re á -- gua~e nas -- ce | flor. __ | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        As cu -- ras es -- tão a -- | ber -- | _ _ tas;
        Aos bons de co -- ra -- | ção; __ | _ _
        Quem re -- ce -- be me -- | re -- | ce;
        A -- gra -- de -- ce, nun -- ca~es -- | que -- | ce.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2~ s8 | d1:m | d:m | a
        | a | g:m | a:7 | d:m | d4.:m
      }
    }
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    On Earth and in the Astral, the enemies attack
    On the sword of Saint Michael all will be transformed
    \nextverse
    The stars of heaven shine for who has love
    In the forests of my Father runs water and flower births
    \nextverse
    The healings are open for those who are goodhearted
    Who receives, deserves, gives thanks, never forgets
  \end{translation}
\endsong


\beginsong{A Estrela Azul}[by={Baixinha}, key={A}, sks={A, G--B}, tags={2x}]
  \audio{https://www.nossairmandade.com/hymn/1158/AEstrelaAzul}
  \meter{4}{4}
  \transpose{2}
  \mnbeginchorus\memorize
    \[^\mn{G}]Vem \[^\mn{B}]le\[^\mn{D}]van|\[\mnc{G}G]ta\[\bm]n|-do do fun\[\bmc\mn{F#}]do \[^\mn{E}]do |\[\mnc{D}D]mar \[\bm] | \e \altchords{\id[1]{(G)}|G | - |D | \e}
    \[^\mn{B}]A Es\[\bmc\mn{E}]tre\[^\mn{D}]la A|\[\mnc{A}Am]zul \[\bm] \[^\mn{C}]em seu \meter{2}{4}|\[\mnc{B}D]trono \[^\mn{A}]divi\meter{4}{4}|\[\mnc{G}G]nal \[\bm] | \e \altchords{|Am \meter{2}{4}|D \meter{4}{4}|G | \e}
  \mnendchorus
  \notesoff
  \beginchorus
    Lá vem, lá |^vem^ | para ^nos cu|^rar ^ | \e \altchords{|G | - |D | \e}
    A Es^trela A|^zul ^ em seu \meter{2}{4}|^trono divi\meter{4}{4}|^nal ^ \up{1}(| \e) \altchords{|Am \meter{2}{4}|D \meter{4}{4}|G \up{1}(| \e)}
  \endchorus
  \mnbeginchorus\noteson
    \ind \[\mn{G}]Ela \meter{2}{4}|\[\mnc{B}G]vem \[\mn{D}]cu\meter{4}{4}|\[\mnc{A}Am]rar \[\bm] \[\mn{C}]quem a\meter{2}{4}|\[\mn{B}]cre\[\mn{A}]di\meter{4}{4}|\[\mnc{G}G]tar\[\bm] \altchords{\meter{2}{4}|G \meter{4}{4}|Am \meter{2}{4}| - \meter{4}{4}|G}
    \ind A Es\meter{2}{4}|\[\mn{B}]tre\[\mn{D}]la A\meter{4}{4}|\[\mnc{A}Am]zul \[\bm] \[\mn{C}]em seu \meter{2}{4}|\[\mnc{B}D]trono \[\mn{A}]divi\meter{4}{4}|\[\mnc{G}G]nal \[\bm] \up{2}(| \e) \altchords{\meter{2}{4}| - \meter{4}{4}|Am \meter{2}{4}|D \meter{4}{4}|G \up{2}(| \e)}
  \mnendchorus
  \begin{translation}
    It comes rising from the depth of the sea
    The Blue Star in its divine throne
    \nextverse
    It comes, it comes to cure us
    The Blue Star in its divine throne
    \nextverse
    It comes to cure those who believe
    The Blue Star in its divine throne
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \transpose g a \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 2.
      \repeat volta 4 {
        \mark \markup {"4x"} \bar ".|:"
        g4 \posectionmark "1., 2." b d | g1~ | g8( g) g g fis4 e | d1~ | d4 b8 b8 e4 d
        | a2. c8 c \time 2/4 | b b a a \time 4/4
      } \alternative {
        { | g1~ | g4 }
        { | g2. }
      }
      \repeat volta 2 {
        g8 \sectionmark "3." g \time 2/4 | b4 d \time 4/4 | a2. c8 c \time 2/4 | b4 a \time 4/4 | g2.
        g8 g \time 2/4 | b4 d \time 4/4 | a2. c8 c \time 2/4 | b8 b a a \time 4/4
      } \alternative {
        { | g2. }
        { | g1~ | g4 \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Vem le -- van -- | tan -- | _ do do fun -- do do | mar; __ | _
        A Es -- tre -- la~A -- | zul em seu | tro -- no di -- vi --
      } \alternative {
        { | nal. __ | _ }
        { | nal. }
      }
      \set stanza = "3."
      \repeat volta 2 {
        E -- la | vem cu -- | rar quem a -- | cre -- di -- | tar;
        A Es -- | tre -- la~A -- | zul em seu | tro -- no di -- vi --
      } \alternative {
        { | nal. }
        { | nal. __ | _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Lá vem, lá | vem __ | _ _ pa -- ra nos cu -- | rar; __ | _
        A Es -- tre -- la~A -- | zul em seu | tro -- no di -- vi --
      } \alternative {
        { | nal. __ | _ }
        { | nal. }
      }
    }
    theChords = \transpose g a \chordmode {
      \repeat volta 4 {
        s2. | g1 | g | d | d
        | a:m | d2
      } \alternative {
        { | g1 | g4 }
        { | g2. }
      }
      \repeat volta 2 {
        s4 | g2 | a1:m | a2:m | g1 | g2 | a1:m | d2
      } \alternative {
        { | g2. }
        { | g1 | g4 }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{O Anjo de Deus}[by={Padr. Alfredo}, tags={valsa}, key={Am}, sks={Am, (G\shrp{m})--(Cm)}]
  \audio{https://www.nossairmandade.com/hymn/609/OAnjoDeDeus}
  \newchords{chords_oanjodedeus_a}\newchords{chords_oanjodedeus_b}\newchords{chords_oanjodedeus_c}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_oanjodedeus_a]
    \[^\mn{E}]O |\[\mnc{A}Am]anjo \[^\mn{B}]de |\[^\mn{C}]Deus nos \[^\mn{B}]pro|\[^\mn{A}]te|\[^\mn{E}]ge
    Com |\[\mnc{D}Bm7&5]{seu san}\[^\mn{B}]to |\[\mnc{G#}E]manto \[^\mn{E}]a|\[\mnc{A}Am]zul \up{1}(| \e)
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_oanjodedeus_b]
    \ind \[^\mn{A}]De |\[\mnc{D}Dm]leste a o|este, |\[^\mn{F}]de \[^\mn{D}]nor\[^\mn{F}]te a |\[\mnc{E}Am]sul
    \ind |\[E7]Vi\[^\mn{F}]va a \[^\mn{E}]Es|\[^\mn{D}]tre\[^\mn{C}]la \[^\mn{B}]do a|\[\mnc{A}Am]zul
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_oanjodedeus_c]
    \ind |\[\mnc{D}Dm]Que faz bri|lhar as Es|\[^\mn{F}]tre\[^\mn{D}]las \[^\mn{F}]do |\[\mnc{E}Am]Céu
    \ind |\[E7]Do \[^\mn{F}]ar\[^\mn{E}]can|\[^\mn{D}]jo \[^\mn{C}]Ra\[^\mn{B}]fa|\[\mnc{A}Am]el \up{2}(| \e)
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_oanjodedeus_a]
    Este |^globo |gira per|fei|to
    Com di|^versas amos|^tragens de |^cor \up{1}(| \e)
    \endchorus\glueverses\beginchorus\replay[chords_oanjodedeus_b]
    \ind |^{É Deus} em |tudo, é o |fruto, é a |^flor
    \ind |^Vida do |meu Cria|^dor
    \endchorus\glueverses\beginchorus\replay[chords_oanjodedeus_c]
    \ind |^Que faz bro|tar com |todo vi|^gor
    \ind |^Vida do |Rei do a|^mor \up{2}(| \e)
  \endchorus
  \begin{translation}
    The angel of God protects us with his holy blue mantle
    From east to west, from north to south, viva the Blue Star
    Which makes the stars of heaven shine of the Archangel Raphael
    \nextverse
    This globe turns perfectly, with diverse patterns of color
    It's God in everything, it's the fruit, it's the flower; life of my creator
    That causes budding with all vigor; life of the King of love
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 2
      \repeat volta 2 {
        \parenthesize e4 \sectionmark "A" e | a( a) b | c c b | a2. | e4( e) e
        | d d b8( b) | gis4 gis e
      } \alternative {
        { | a2.~ | a4 }
        { | a2 }
      } \break
      \repeat volta 2 {
        \parenthesize a4 \sectionmark "B" | d d d | d( d) d | f d f | e2.
        | e4 f e | d c b
      } \alternative {
        { | a2 }
        { | a2. }
      } \break
      \repeat volta 2 {
        | d4 \posectionmark "C" d d | d4.( d8) d4 | f d f | e2.
        | e4 f e | d c b
      } \alternative {
        { | a2. }
        { | a2.~ | a4 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        \skip 1 O | an -- jo de | Deus nos pro -- | te -- | ge; __ _
        Com | seu san -- to __ _ | man -- to a --
      } \alternative {
        { | zul. | _ }
        { | zul. }
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        De | les -- te~a o -- | es -- _ te, | de nor -- te~a | sul;
        | Vi -- va~a Es -- | tre -- la do~a --
      } \alternative {
        { | zul. }
        { | zul. }
      }
      \set stanza = "1.C"
      \repeat volta 2 {
        | Que faz bri -- | lhar as Es -- | tre -- las do | Céu;
        | Do ar -- can -- | jo Ra -- fa --
      } \alternative {
        { | el. }
        { | el. | _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Es -- te | glo -- _ bo | gi -- ra per -- | fei -- | to;
        Com di -- | ver -- sas a -- mos -- | tra -- gens de
      } \alternative {
        { | cor. | _ }
        { | cor. }
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 | É Deus em | tu -- do,~é o | fru -- to,~é a | flor;
        | Vi -- da do | meu Cri -- a --
      } \alternative {
        { | dor. }
        { | dor. }
      }
      \set stanza = "2.C"
      \repeat volta 2 {
        | Que faz bro -- | tar __ _ com | to -- do vi -- | gor;
        | Vi -- da do | Rei do a --
      } \alternative {
        { | mor. }
        { | mor. | _ }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | a2.:m | a:m | a:m | a:m
        | b:m7.5- | e 
      } \alternative {
        { | a:m | a4:m}
        { | a2:m }
      }
      \repeat volta 2 {
        s4 | d2.:m | d:m | d:m | a:m
        | e:7 | e:7 
      } \alternative {
        { | a2:m }
        { | a2.:m }
      }
      \repeat volta 2 {
        | d2.:m | d:m | d:m | a:m
        | e:7 | e:7
      } \alternative {
        { | a2.:m }
        { | a2.:m | a4:m}
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong
