% Santo Daime: Cruzeirinho (Mestre Irineu)
% ========================================
%
% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{117}

\beginsong{Dou Viva a Deus nas Alturas}[by={Mestre Irineu Serra},tags={valsa},key={C},sks={C, D}]
  \audio{https://www.nossairmandade.com/hymn/85/DouVivaADeusNasAlturas}
  \newchords{chords_douvivaadeus_a}\newchords{chords_douvivaadeus_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_douvivaadeus_a]
    \[^\mn{G}]Dou |\[\mnc{C}C]viva a |Deus nas \[^\mn{E}]al|\[\mnc{G}G]turas \altchords{\id[1]{(D)}|D | |A}
    \[^\mn{E}]E a |\[\mnc{A}Am]Vir\[^\mn{G}]gem |\[\mnc{F}F]Mãe \[^\mn{A}]nos\[^\mn{B}]so a|\[\mnc{C}C]mor \altchords{|Bm |G |D}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_douvivaadeus_b]
    |\[\mnc{C}C]Vi\[^\mn{B}]va \[^\mn{A}]to|\[\mnc{C}Am]do \[^\mn{B}]Ser \[^\mn{A}]Di|\[\mnc{D}Dm]vino \altchords{|D |Bm |Em}
    E Je|\[\mnc{G}G]sus Cris|\[\mnc{E}Em]to \[^\mn{C}]Reden|\[C]tor \altchords{|A |F\#m |D}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_douvivaadeus_a]
    Eu |^peço a |Deus nas al|^turas
    Pa|^ra Vós |^me ilumi|^nar
    \endchorus\glueverses\beginchorus\replay[chords_douvivaadeus_b]
    Bo|^tai-me |^no bom ca|^minho
    E li|^vrai-me |^de todo |^mal
  \endchorus
  \beginchorus\replay[chords_douvivaadeus_a]
    Eu |^vivo a|qui neste |^mundo \altchords{\id[2]{ED (C)}|C |Am |Em}
    Encos|^tado a |^este Cru|^zeiro \altchords{|F |G |C}
    \endchorus\glueverses\beginchorus\replay[chords_douvivaadeus_b]
    Ve|^jo tan|^ta ilumi|^nária \altchords{|C |Am |Dm}
    Do |^nosso |^Deus Verda|^deiro \altchords{|G |G7 |C}
  \endchorus
  \beginchorus\replay[chords_douvivaadeus_a]
    Es|^ta ilumi|nária que eu |^vejo \altchords{\id[3]{MK (C)}|C |Am |C}
    A|^legra o |^meu cora|^ção \altchords{|Dm7 |G7 |C}
    \endchorus\glueverses\beginchorus\replay[chords_douvivaadeus_b]
    Es|^tas flores |^que rece|^bemos \altchords{|Am |Am7 |Dm}
    Pa|^ra nos|^sa Salva|^ção \altchords{|G |Fmaj7 |C}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 3/4 \partial 4
      \repeat volta 2 {
        g4\posectionmark "A" | c4. c8 c4 | c4 c4 e4 
        | g4 g4 e4 | a2 g4 | f4 a,4 b4 | c4( c4)
      } \break
      \repeat volta 2 {
        \parenthesize g4\sectionmark "B" | c4 b4 a4 | c4 b4 a4
        | d4 d8 d8 d4 | g2 g4 | e4 c4 c4 | c4( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Dou | vi -- va a | Deus nas al -- | tu -- ras;
        E~a | Vir -- gem | Mãe nos -- so~a -- | mor. __ _
      }
      \repeat volta 2 {
        \skip 1 | Vi -- va to -- | do Ser Di -- | vi -- no;
        E Je -- | sus Cris -- | to Re -- den -- | tor. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Eu | pe -- ço a | Deus nas al -- | tu -- ras;
        Pa -- | ra Vós | me~i -- lu -- mi -- | nar. __ _
      }
      \repeat volta 2 {
        Bo -- | tai -- _ me no bom ca -- | mi -- nho;
        E li -- | vrai -- me | de to -- do | mal. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Eu | vi -- vo a -- | qui nes -- te | mun -- do;~En
        cos -- | ta -- do~a | es -- te Cru -- | zei -- ro.
      }
      \repeat volta 2 {
        Ve -- | jo __ _ tan -- | ta~i -- lu -- mi -- | ná -- ri -- a;
        Do | nos -- so | Deus Ver -- da -- | dei -- ro.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Es -- | ta~i -- lu -- mi -- | ná -- ria que~eu | ve -- jo;
        A -- | le -- gra~o | meu co -- ra -- | ção. __ _
      }
      \repeat volta 2 {
        Es -- | tas flo -- res | que re -- ce -- | be -- mos; __ _
        Pa -- | ra nos -- | sa Sal -- va -- | ção. __ _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c2. | c | g
        | a:m | f | c2
      }
      \repeat volta 2 {
        \set chordChanges = ##f
        s4 | c2. | a:m | d:m
        | g | e:m | c2
        \set chordChanges = ##t
      }
    }
    \layout { #(layout-set-staff-size 15) }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    I give viva to God in the Heights, and to the Virgin Mary, our love
    I give viva to every Divine Being, and Jesus Christ the Redeemer
    \nextverse
    I ask the God in the Heights, for Thou to illuminate me
    Put me on the right path and deliver me from all evil
    \nextverse
    I live here in this world, next to this Cross
    I see so much Light from our true God
    \nextverse
    This brightness that I see gladdens my heart
    These flowers that we receive for our salvation
  \end{translation}
\endsong

\beginsong{Todos Querem Ser Irmão}[by={Mestre Irineu Serra},key={Am},sks={Am}]
  \audio{https://www.nossairmandade.com/hymn/86/TodosQueremSerIrm\%C3\%A3o}
  \newchords{chords_todosquerem_a}\newchords{chords_todosquerem_b}
  \mnbeginchorus\memorize[chords_todosquerem_a]
    \[^\mn{E}]Todos |\[\mnc{A}Am]que\[^\mn{E}]rem \[\bmc\mn{C}]ser \[^\mn{A}]ir|\[\mnc{B}E/B]mã\[^\mn{A}]os
    \[\mnc{E}E]Mas \[^\mn{G}]não |\[G]têm a \[\mnc{D}Dm]leal|\[\mnc{C}C]da\[^\mn{A}]de\[Am]
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_todosquerem_b]
    \[^\mn{E}]Para \[^\mn{G}]se|\[\mnc{G}G]guir \[^\mn{D}]na \[Dm]Vida \[^\mn{G}]E|\[\mnc{A}Am]spírita
    Que \[\bmc\mn{A}]é \[^\mn{C}]o |\[\mnc{E}E]Rei\[^\mn{D}]no \[\mnc{B}E7/B]da \[^\mn{C}]Ver|\[\mnc{A}Am]dade
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_todosquerem_a]
    É o |^Reino ^da Ver|^dade \altchords{\id[2]{ED}|Am |F}
    É ^a Es|^trada ^do A|^mor^ \altchords{|G |Am}
    \endchorus\glueverses\beginchorus\replay[chords_todosquerem_b]
    É todos |^prestar ^aten|^ção \altchords{|G |F}
    ^Os en|^sinos do ^profes|^sor \altchords{|E E7 |Am}
  \endchorus
  \beginchorus\replay[chords_todosquerem_a]
    Os en|^sinos do ^profes|^sor \altchords{\id[3]{MK}|Am |\e}
    É ^quem nos |^traz be^las li|^ções^ \altchords{|G Dm |Am}
    \endchorus\glueverses\beginchorus\replay[chords_todosquerem_b]
    Para |^todos ^se u|^nir \altchords{|G Dm |Am}
    E ^respei|^tar os ^seus ir|^mãos \altchords{|C G |Am}
  \endchorus
  \beginchorus\replay[chords_todosquerem_a]
    Respei|^tar os ^seus ir|^mãos
    Com ^ale|^gria e ^com a|^mor^
    \endchorus\glueverses\beginchorus\replay[chords_todosquerem_b]
    Para |^todos ^conhe|^cer
    E ^saber |^dar o ^seu va|^lor
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        r8\posectionmark "A" e8 e8 | a4. e8 c'4. a8 | b4 a4 e4. g8
        | g4. g8 d4. d8 | c4( a4.)
      }
      \repeat volta 2 {
        \parenthesize e'8\sectionmark "B" e8 g8 | g4. d8 d4 d8( \parenthesize g8) | a8( a a a) a,4. c8
        | e4( e8) d8 b4. c8 | a2( a8)
      }
    }
    theLyricsOne = \lyricmode { % no repeats 'coz begin with a rest
      \set stanza = "1."
      To -- dos | que -- rem ser ir -- | mã -- os;
      Mas não | têm a le -- al -- | da -- de.
      \set stanza = "1.B"
      Pa -- ra se -- | guir na Vi -- da E -- | spí -- ri -- ta;
      Que é o | Rei -- _ no da Ver -- | da -- de.
  }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      É o | Rei -- no da Ver -- | da -- de;~É
      a Es -- | tra -- da do A -- | mor. __ _
      \set stanza = "2.B"
      É to -- dos | pres -- tar a -- ten -- _ | ção; __ _ _ _
      Os en -- | si -- nos  do pro -- fes -- | sor. __ _
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Os en -- | sinos do pro -- fes -- | sor;
      é quem nos | traz be -- las li -- | çõ -- es.
      \set stanza = "3.B"
      \skip 1 Pa -- ra | to -- dos se u -- _ | nir; __ _ _
      E res -- pei -- | tar __ _ os seus ir -- | mã -- os.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      Res -- pei -- | tar os seus ir -- | mãos;
      Com a -- le -- | gria e com a -- | mor. __ _
      \set stanza = "4.B"
      \skip 1 Pa -- ra | to -- dos co -- nhe -- _ | cer; __ _ _
      E sa -- ber | dar __ _ o seu va -- | lor. __ _
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | a1:m | e2/b e
        | g2 d:m | c a8:m
      }
      \repeat volta 2 {
        s4. | g2 d:m | a:m a:m
        | e e:7/b | a2:m~ a8:m
      }
    }
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    All want to be brothers
    But don't have loyalty
    To follow the Spiritual Life
    Which is the Kingdom of Truth
    \nextverse
    It's the Kingdom of Truth
    It's the path of Love
    And everybody must pay attention
    To the teachings of the professor
    \nextverse
    The teachings of the professor
    Bring us beautiful lessons
    For everybody to come together
    And respect one's brothers and sisters
    \nextverse
    To respect one's brothers and sisters
    With happiness and with love
    For everybody to know
    And learn to appreciate one another
  \end{translation}
\endsong
