% Santo Daime: O Proximo Nivel
% ============================
%

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Saint Germain}[by={Léo Artese}, tags={valsa}, key={Bm}, gk={Cm, (Bm)--(Cm)}]
  \audio[key=Em]{https://soundcloud.com/sergio-moreira-slmore/24-saint-germain}
  \audio[key=Em]{https://www.youtube.com/watch?v=wZ5x4su95eg}
  \newchords{chords_saintgermain_a}\newchords{chords_saintgermain_b}
  \meter{3}{4}
  \transpose{-5}
  \mnbeginverse\memorize[chords_saintgermain_a]
    \[^\mn{B}]Vou \[^\mn{G}]di|\[\mnc{E}Em]zer |{ } o que |deves fa|zer \[^\mn{G}]pa\[^\mn{E}]ra |\[\mnc{F#}B7]al\[^\mn{D#}]can|\[^\mn{B}]çar |{ }{ }{ } | \e
    \[^\mn{B}]Um \[^\mn{G}]lu|\[\mnc{E}Em]gar |{ } na infi|nita cons|ciên\[^\mn{G}]cia \[^\mn{E}]de |\[\mnc{F#}B7]Deus |{ }{ }{ } |{ }{ }{ } | \e
    \mnendverse\glueverses\mnbeginchorus\memorize[chords_saintgermain_b]
    \[^\mn{F#}]Com\[^\mn{G}]preen|\[\mnc{A}Am]der |{ } que \[^\mn{B}]Deus |\[^\mn{C}]é{ } |{ }{ } \[^\mn{E}]tu|\[\mnc{B}Em]do |{ }{ } \[^\mn{G}]que |\[^\mn{E}]há | \e
    \[^\mn{G}]Eu |\[\mnc{F#}B7]e |{ }{ } \[^\mn{D#}]vo|\[^\mn{B}]cê, |{ } \[^\mn{G}]meu \[^\mn{F#}]ir|\[\mnc{E}Em]mão |{ }{ }{ } |\[\ac(1){E7}]{ } | \e
  \mnendchorus
  \notesoff
  \beginverse\replay[chords_saintgermain_a]
    Eu sou |^Luz, |{ } sou A|mor, sou Sa|úde, eu sou |^Perfei|ção |{ }{ }{ } | \e
    Sei que eu |^sou |{ } a pre|sença de |Deus em a|^ção |{ }{ }{ } |{ }{ }{ }  | \e
    \endverse\glueverses\beginchorus\replay[chords_saintgermain_b]
    Sou que |^sou, |{ } sou fi|lho |{ }{ } da |^Cri|{ }{ } a|ção | \e
    Eu |^e |{ }{ } vo|cê, |{ } meu ir|^mão |{ }{ }{ } |^{ } | \e
  \endchorus
  \beginverse\replay[chords_saintgermain_a]
    Eu Sou |^Pai, |{ } eu sou |Mãe, sou Fi|lho também |^sou Ir|mão |{ }{ }{ } | \e
    Sou o |^Yin |{ } e o |Yang em per|feita uni|^ão |{ }{ }{ } |{ }{ }{ } | \e
    \endverse\glueverses\beginchorus\replay[chords_saintgermain_b]
    Sou a |^Cha{ - }|{ } ma Vio|le{ - }|{ } ta em |^ex{ - }|{ }{ } pan|são | \e
    Sou |^Saint |{ } Ger|main, |{ } meu ir|^mão |{ }{ }{ } |^{ } | \e
  \endchorus
  \beginverse\replay[chords_saintgermain_a]
    Vás bus|^car |{ } a cons|ciência do |Cristo In|^teri|or |{ }{ }{ } | \e
    Prati|^can{ - }|{ } do o a|mor que não |tem condi|^ção |{ }{ }{ } |{ }{ }{ } | \e
    \endverse\glueverses\beginchorus\replay[chords_saintgermain_b]
    Nova |^e|{ } ra, na |ter|ra se i|^ni|{ }{ } ci|ou | \e
    Quem |^é |{ } vo|cê, |{ } meu ir|^mão? |{ }{ }{ } |^{ } | \e
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-10
    theMelody = \transpose e b, \relative b'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key e \minor \time 3/4 \partial 2
      b4 _\posectionmark "A" g4 | e2.~ | e4 e4 e4 | e e e | e g e | fis2 dis4 | b2.~ | b2.~ | b4
      b'4 g4 | e2.~ | e4 e4 e4 | e e e | e g e | fis2.~ | fis2.~ | fis2.~ | fis4
      \repeat volta 2 {
        fis4 \sectionmark "B" g | a2.~ | a4 a4 b4 | c2.( | c2) e4 | b2.~ | b2 g4 | e2.~ | e2
        g4 | fis2.~ | fis2 dis4 | b2.~ | b4 g'4 fis4 | e2.~ | e2.~
      } \alternative {
        { | e2.~ | e4 }
        { | e2.~ \repeatTie | e4 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      Vou di -- | zer __ | _ o que | de -- ves fa -- | zer pa -- ra | al -- can -- | çar; __ | _ | _
      Um lu -- | gar __ | _ na~in -- fi -- | ni -- ta cons -- | ciên -- cia de | Deus. __ | _ | _ | _
      \set stanza = "1.B"
      \repeat volta 2 {
        Com -- preen -- | der __ | _ Que Deus | é __ | _ tu -- | do __ | _ que | há; __ | _
        Eu | e __ | _ vo -- | cê, __ | _ meu ir -- | mão. __ | _ | _ | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      Eu sou | Luz, __ | _  sou A -- | mor, sou Sa -- | ú -- de,~eu sou | Per -- fei -- | ção; __ | _ | _
      Sei que~eu | sou __ | _ a pre -- | sen -- ça de | Deus em a -- | ção. __ | _ | _  | _
      \set stanza = "2.B"
      \repeat volta 2 {
        Sou que | sou, __ | _ sou fi -- | lho __ | _ da | Cri -- | _ a -- | ção; __ | _
        Eu | e __ | _ vo -- | cê, __ | _ meu ir -- | mão. __ | _ | _ | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      Eu sou | Pai, __ | _ eu sou | Mãe, sou Fi -- | lho, tam -- bém | sou Ir -- | mão; __ | _ | _
      Sou o | Yin __ | _ e o | Yang em per -- | fei -- ta~u -- ni -- | ão. __ | _ | _ | _
      \set stanza = "3.B"
      \repeat volta 2 {
        Sou a | Cha -- | _ ma Vio -- | le -- | _ ta~em | ex -- | _ pan -- | são; __ | _
        Sou | Saint __ | _ Ger -- | main, __ | _ meu ir -- | mão. __ | _ | _ | _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      Vás bus -- | car __ | _ a cons -- | ciên -- cia do | Cris -- to In -- | te -- ri -- | or; __ | _ | _
      Pra -- ti -- | can -- | _ do~o a -- | mor que não | tem con -- di -- | ção. __ | _ | _ | _
      \set stanza = "4.B"
      \repeat volta 2 {
        No -- va | e -- | _ ra, na | ter -- | ra se~i -- | ni -- | _ ci -- | ou; __ | _
        Quem | é __ | _ vo -- | cê, __ | _ meu ir -- | mão? __ | _ | _ | _
      }
    }
    theChords = \transpose e b, \chordmode {
      r2 | e2.:m | e:m | e:m | e:m
      | b2.:7 | b:7 | b:7 | b:7
      | e2.:m | e2.:m | e:m | e:m
      | b2.:7 | b:7 | b:7 | b4:7
      \repeat volta 2 {
        s2 | a2.:m | a:m | a:m | a:m
        | e2.:m | e2.:m | e:m | e:m
        | b2.:7 | b:7 | b:7 | b:7
        | e2.:m | e2.:m
      } \alternative {
        { | e2.:7 | e4:7 }
        { | e2.:m | e4:m }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \iflyriconly\forcebrk\fi
  \begin{translation}[EN]
    I will tell you what you must do to achieve
    A place in the infinite consciousness of God
    Understanding that God is all there is
    I and you, my brother
    \nextverse
    I am Light, I am Love, I am Health, I am Perfection
    I know that I am the presence of God in action
    I am who I am, I am a child of Creation
    I and you, my brother
    \nextverse
    I am a Father, I am a Mother, I am a Son, I am a brother too
    I am Yin and Yang in perfect union
    I am the expanding Violet Flame
    I am Saint Germain, my brother
    \nextverse
    Go seek the consciousness of the Inner Christ
    Practicing the love that has no condition
    A new age on Earth has begun
    Who are you, my brother?
  \end{translation}
  % Only on if no lilypond, for the song to fit a spread:
  \ifshowlilypond\else%
    \begin{explanation}[EN]
      \textbf{Saint Germain} (also sometimes referred to as Master Rákóczi or Master R)
      is a legendary spiritual master of the ancient wisdom in various Theosophical
      and post-Theosophical teachings, said to be responsible for the New Age culture
      of the Age of Aquarius and identified with the Count Saint Germain (fl. 1710–-1784).
    \end{explanation}
  \fi
\endsong





\beginsong{Verdade Pura}[by={William Vilas Boas}, key={Gm}, gk={Gm}]
  \audio[key=Gm]{https://www.youtube.com/watch?v=VtNEgkn707I}
  \mnbeginchorus\memorize
    \lrep \[^\mn{D}]Esta é \[\bmc\mn{B&}]a \[^\mn{A}]dou|\[\mnc{D}Gm]tri\[\bm]na, | do Sol \[\bmc\mn{E&}]e \[^\mn{D}]da |\[\mnc{C}Cm]Lu\[\bm]a |\[Cm6]{} \e
    \[^\mn{A}]E \[\bm]das \[^\mn{G}]Es|\[\mnc{F#}D]tre\[\bmc\mn{D}]las, |\[D7]{} e da \[^\mn{E&}]Ver\[\bmc\mn{D}]da\[^\mn{C}]de |\[\mnc{D}Gm]Pu\[\bm]ra |\[\ac(2){G7}]{} \e \rrep
    \ind \lrep \[^\mn{D}]Para \[\bmc\mn{E&}]com\[^\mn{D}]preen|\[\mnc{C}Cm]der, pa\[^\mn{D}]ra \[\bmc\mn{E&}]com\[^\mn{D}]preen|\[^\mn{C}]der
    \ind \ilsl{\[^\mn{A}]É} \[^\mn{B&}]ter \[^\mn{C}]e\[\bmc\mn{D}]du\[^\mn{C}]ca|\[\mnc{B&}B&]ção, \[^\mn{A}]é \[^\mn{B&}]ter \[^\mn{C}]e\[\bmc\mn{D}]du\[^\mn{C}]ca|\[^\mn{B&}]ção
    \ind Não \[\bmc\mn{C}]se \[^\mn{B&}]jul|\[\mnc{A}D]gar,\[\bm]{} |\[D7]{} nem jul\[\bmc\mn{B&}]gar os \[^\mn{A}]seus ir|\[\mnc{/}Gm]mãos\[\bm]{} |\[\ac(1){G7}]{} \e \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep Quem ^mais quer |^ser ^ | é quem ^menos |^é ^ |^
    Sigamos ^o ex|^em^plo |^ do bom Je^sus de Naza|^ré ^ |^ \e \rrep
    \ind Tanto ^que so|^freu, tanto ^que so|freu
    \ind Que se ^humi|^lhou, que se ^humi|lhou
    \ind So^freu na |^cruz^ |^ e a todos ^Ele perdo|^ou ^ |\[G7]{} \e
    \ind Tanto \[\bm]que so|\[Cm]freu, tanto \[\bm]que so|freu
    \ind Que se \[\bm]humi|\[B&]lhou, que se \[\bm]humi|lhou
    \ind Mor\[\bm]reu na |\[D]cruz\[\bm]{} |\[D7]{} para ensi\[\bm]nar o que é o A|\[Gm]mor \[\bm]{} | \e
  \endchorus
  \begin{translation}[EN]\scriptsize % to fit on a page
    This is the doctrine of the Sun and the Moon
    And of the Stars and the Pure Truth
    \ind To understand, to understand
    \ind It's education, it's education
    \ind Do not judge yourself or judge your brothers
    \nextverse
    Who more wants to be, is who least is
    Let us follow the example of the good Jesus of Nazareth
    \ind So much he suffered, so much he suffered
    \ind Who humbled himself, who humbled himself
    \ind \up{1}Suffered on the cross, and all He forgave
    \ind \up{2}He died on the cross to teach what love is
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-07
    \include "tex/lp-include-head.ly"
    theMelody = \relative d'' {
      \key g \minor \time 4/4 \partial 2.
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        d8( \posectionmark "A" d) bes'4 a
        | d,2( d2)~ | d4 d8 d8 es4 d4 | c2( c2)~ | \once\slurDown c8\parenthesize a' a8( a) a4 g4
        | fis2 d2~ | d8 d8 8 es d8( d) c( c)
      } \alternative {
        { | d2( d2)~ | d4 }
        { | d2( d2)~ | d4 }
      } \break
      \repeat volta 2 {
        d8 \sectionmark "B" d es4 d
        | c c8 d es4 d | c8 \parenthesize a bes c d4 c | bes8 \parenthesize a bes c d4 c | bes bes c bes
        | a1~ | a8( a8) a8 a bes bes a a
      } \alternative {
        { | d1~ | d4 }
        { | g,1~ | g4 \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Es -- ta~é a dou -- | tri -- na | _
        Do Sol e da | Lu -- a; | _ _
        E __ _ das Es -- | tre -- las | _
        E da Ver -- da -- _ de __ _
      } \alternative {
        { | Pu -- ra. | _ }
        { | Pu -- ra. | _ }
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Pa -- ra com -- preen -- | der
        Pa -- ra com -- preen -- | der;
        É ter e -- du -- ca -- | ção
        É ter e -- du -- ca -- | ção;
        Não se jul -- | gar __ | _ _
        Nem jul -- gar os seus ir --
      } \alternative {
        { | mãos. | _ }
        { | mãos. | _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Quem __ _ mais quer | ser __ _ | _
        É quem me -- nos | é; __ _ | _
        Si -- ga -- mos o ex -- | em -- plo | _
        Do bom Je -- sus de Na -- za --
      } \alternative {
        { | ré. __ _ | _ }
        { | ré. __ _ | _}
      }
      <<
        {
          \set stanza = "2.B:i"
          \repeat volta 2 {
            Tan -- to que so -- | freu
            Tan -- to que so -- | freu;
            \skip 1 Que se hu -- mi -- | lhou
            \skip 1 Que se hu -- mi -- | lhou;
            So -- freu na | cruz | _
            E~a to -- dos E -- le per -- do --
          } \alternative {
            { | ou. | _ }
            { | | }
          }
        }
        \new Lyrics { \set associatedVoice = "theMelody"
          \set stanza = "2.B:ii"
          \repeat volta 2 {
            Tan -- to que so -- | freu
            Tan -- to que so -- | freu;
            \skip 1 Que se hu -- mi -- | lhou
            \skip 1 Que se hu -- mi -- | lhou;
            Mor -- reu na | cruz | _
            Pa -- ra~en -- si -- nar o que~é~o A-
          } \alternative {
            { }
            { | _ | _ | mor. | _ }
          }
        }
      >>
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2.
        | g1:m | 1 | c:m | c:m6
        | d | d:7
      } \alternative {
        { | g1:m | 4 }
        { | g1:m | g4:7~ }
      }
      \repeat volta 2 {
        2.
        | c1:m | 1 | bes
        | bes | d | d:7
      } \alternative {
        { | g1:m | g4:7 }
        { | g1:m | 4~ }
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Pena de Prata}[by={Sonia Maria Palhares}, key={Dm}, gk={Dm, Cm--F\shrp{}m}]
  \audio[key=Dm]{https://nossairmandade.com/hymn.php?hid=1377}
  \mnbeginchorus\memorize
    \[^\mn{A}]No |\[\mnc{D}Dm]al\[^\mn{F}]to \[\bmc\mn{E}]da \[^\mn{C#}]mon\[^\mn{E}]ta|-\[^\mn{D}]nha \[\bm] \altchords{\id[1]{(Em)}|Em | \e}
    \[^\mn{A}]Lá no |\[^\mn{D}]al\[^\mn{F}]to \[\bmc\mn{E}]mui\[^\mn{D}]to a\[^\mn{E}]lé|\[A]m \[\bm] \altchords{| - |B}
    Tem um |palá\[\bm]cio de \[^\mn{G}]ge|\[\mncadj{1ex}{F}Gm]{-lo} \[^\mn{E}]tão \[^\mn{D}]su\[\bmc\mn{C#}]bli\[^\mn{A}]me \altchords{| - |Am}
    \[^\mn{E}]Que vi|\[A]ra \[^\mn{G}]á\[\mnc{F}A7]gua \[^\mn{E}]tam\[^\mn{D}]bé|\[Dm]m \[\bm] \altchords{|B B7 |Em}
  \mnendchorus
  \notesoff
  \beginchorus
    A |^água ^vai pra ma|-ta ^
    Mãe Ju|rema a^bençoo|^u ^
    Uma |cabo^cla de pe|^{-na} cor de ^prata
    Que Pai |^Oxa^lá crio|^u ^
  \endchorus
  \beginchorus
    O |^Sol bri^lha na Ter|-ra ^
    E dá |luz aos ^que sofre|^u ^
    E |põe um ^Ser Divi|^{-no} em cada ^folha
    Pra cu|^rar os ^filhos Seu|^s ^
  \endchorus
  \beginchorus
    Minha |^Mãe, mi^nha Rai|-nha ^
    Quero as |almas i^lumina|^r ^
    Com es|se cris^tal tão pu|^{-ro} e verda^deiro
    Que vei|^o me a^companha|^r ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-10
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4
      \repeat volta 2 {
        a8( a) | d4 f e cis8 e8~ | e8 d8~ 2
        a8 a | d4 f8( f8) e4 d8 e8~ | e2.
        e8( e8) | e4 e e e8 g8~ | g8 f e d cis a e' e
        | e4 g f e8 d8~ | d2.
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        No __ _ | al -- to da mon -- ta -- | _ nha; _
        Lá no | al -- to __ _ mui -- to~a -- lém; | _
        Tem um | pa -- lá -- cio de ge -- | _ lo tão su -- bli -- me;
        Que vi -- | ra á -- gua tam -- bém. | _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        A __ _ | á -- gua vai pra ma -- | _ ta; _
        Mãe Ju -- | re -- ma a -- ben -- ço -- ou; | _
        U -- ma | ca -- bo -- cla de pe -- | _ na cor de pra -- ta;
        Que Pai | O -- xa -- lá cri -- ou. | _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        O __ _ | Sol bri -- lha na Ter -- | _ ra; _
        E dá | luz aos __ _ que so -- freu; | _
        E __ _ | põe um Ser Di -- vi -- | _ no~em ca -- da fo -- lha;
        Pra cu -- | rar os fi -- lhos Seus. | _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Mi -- nha | Mãe, mi -- nha Ra -- i -- | _ nha; _
        Que -- ro~as | al -- mas i -- lu -- mi -- nar; | _
        Com es -- | se cris -- tal tão pu -- | _ ro~e ver -- da -- dei -- ro;
        Que vei -- | o me~a -- com -- pa -- nhar. | _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4
        | d1:m | d:m | d:m | a
        | a | g:m | a2 a2:7 | d2.:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    On the heights of the mountain, there in the heights far always
    Is an ice palace so sublime that it turns into water
    \nextverse
    The water comes by the forest, mother Jurema blesses it
    A cabocla of silver feathers that Father Oxala created
    \nextverse
    The Sun shines on the Earth and gives light to those who suffer
    And puts a Divine being in every leaf to heal His children
    \nextverse
    My Mother, my Queen, I want to illuminate the souls
    With this crystal so pure and true, that comes to accompany me
  \end{translation}
\endsong


\beginsong{Coração Alado}[by={Madr. Regina Pereira}, key={Dm}, gk={Dm, Cm--E\flt{}m}, tags={valsa}]
  \audio[key=Am]{https://soundcloud.com/canaljagube/coracao-alado}
  \audio[key=Dm]{https://www.youtube.com/watch?v=S8LsAn4BGU0}
  \newchords{chords_coracaoalado_a}\newchords{chords_coracaoalado_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_coracaoalado_a]
    \[^\mn{A}]Nes|\[\mnc{D}Dm]{se dom} \[^\mn{E}]Di|\[\mnc{F}F]vino ouço |\[\mnc{E}A]o \[^\mn{D}]men\[^\mn{C#}]sa|\[\mnc{D}Dm]geiro
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_coracaoalado_b]
    \[^\mn{D}]Que é o |\[Dm]Se\[^\mn{G}]nhor \[^\mn{A}]do |\[\mnc{B&}Gm]tempo, em |mar\[^\mn{G}]cha \[^\mn{F}]se |\[\mnc{E}C]põe
    E|le \[^\mn{F}]vem \[^\mn{G}]lem|\[\mnc{A}A]brar, que o |tem\[^\mn{F}]po \[^\mn{E}]vol|\[\mnc{D}Dm]tou
    E que o |Rei\[^\mn{E}]no \[^\mn{F}]de |\[\mncii{G}{E}Gm6]Paz |\[^\mn{G}]e \[^\mn{E}]de \[^\mn{D}]A|\[\mnc{C#}A]mor com cer|\[A7]te\[^\mn{D}]za \[^\mn{E}]vi|\[\mnc{D}Dm]rá
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_coracaoalado_a]
    Con|^centre na |^força do |^seu pensa|^mento \altchords{\id[1]{Am}|Am |C |E |Am}
    \endchorus\glueverses\beginchorus\replay[chords_coracaoalado_b]
    E Res|^pire na |^força des|se beija-|^flor \altchords{|Am |Dm | - |G}
    Que |te ali|^menta e te |dá o a|^lento \altchords{| - |E | - |Am}
    Co|ração a|^lado |voa na |^força do |^seu beija-|^flor \altchords{| - |Dm6 | - |E |E7 |Am}
  \endchorus
  \beginchorus\replay[chords_coracaoalado_a]
    Co|^ração a|^lado, o se|^gredo é can|^tar
    \endchorus\glueverses\beginchorus\replay[chords_coracaoalado_b]
    Nes|^{sa vira}|^ção que |o tempo |^dá
    O |vento que |^sopra faz |alivi|^ar
    Tan|gendo a tris|^teza |e toda |^dor pra |^outro lu|^gar
  \endchorus
  \beginchorus\replay[chords_coracaoalado_a]
    |^Neste oce|^ano va|^mos nave|^gar
    \endchorus\glueverses\beginchorus\replay[chords_coracaoalado_b]
    Es|^tar no bar|^quinho, a fir|meza é can|^tar
    Com |os meus ir|^mãos, pres|tando aten|^ção
    |Nessa jor|^nada do |Rei Salo|^mão e do |^meu São Jo|^ão
  \endchorus
  \beginchorus\replay[chords_coracaoalado_a]
    Meu |^Pai eu lhe |^peço, me |^dê a ben|^ção
    \endchorus\glueverses\beginchorus\replay[chords_coracaoalado_b]
    Pa|^{ra eu} se|^guir nessa |apura|^ção
    A|legre con|^tente com |os meus ir|^mãos
    |Nessa mis|^são |da Virgem |^Mãe e de |^Jurami|^dam
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-11
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \key d \minor \time 3/4 \partial 4
      \set melismaBusyProperties = #'() \slurDashed
      \repeat volta 2 {
        \parenthesize a4 \posectionmark "A" | d d e | f f f8( f) | e4 d cis | d( d)
      }
      \repeat volta 2 {
        \altcol\grace d4 d4 \posectionmark "B" | d g a | bes( bes) bes | bes g f | e2
        e4 | e f g | a( a) a | a f e | d4( d4)(
        d4) | d e f | g4( g4)( e4) | g e d | cis4( cis4)
        cis4 | cis d e | d2
      }
    }
    theLyricsOne = \lyricmode { \set includeGraceNotes = ##f
      \set stanza = "1."
      \repeat volta 2 {
        Nes -- | se dom Di -- | vi -- no ou -- ço | o men -- sa -- | gei -- ro.
      }
      \repeat volta 2 {
        Que~é~o | Se -- nhor do | tem -- po, em | mar -- cha se | põe;
        E -- | le vem lem -- | brar, que o | tem -- po vol -- | tou;
        E que~o | Rei -- no de | Paz __ _ _ | e de A -- | mor com cer -- | te -- za vi -- | rá.
      }
    }
    theLyricsTwo = \lyricmode { \set includeGraceNotes = ##t
      \set stanza = "2."
      \repeat volta 2 {
        Con -- | cen -- tre na | for -- ça do __ _ | seu pen -- sa -- | men -- to.
      }
      \repeat volta 2 {
        \altcol E Res -- | pi -- re na | for -- ça des -- | se bei -- ja -- | flor;
        Que | te a -- li -- | men -- ta~e te | dá o a -- | len -- to;
        Co -- | ra -- ção a -- | la -- _ do | vo -- a na | for -- ça do | seu bei -- ja -- | flor.
      }
    }
    theLyricsThree = \lyricmode { \set includeGraceNotes = ##f
      \set stanza = "3."
      \repeat volta 2 {
        Co -- | ra -- ção a -- | la -- do,~o se -- _ | gre -- do~é can -- | tar. __ _
      }
      \repeat volta 2 {
        Nes -- | sa vi -- ra -- | ção __ _ que | o tem -- po | dá;
        O | ven -- to que | so -- pra faz | a -- li -- vi -- | ar; __ _
        Tan -- | gen -- do~a tris -- | te -- _ za | e to -- da | dor __ _ pra | ou -- tro lu -- | gar.
      }
    }
    theLyricsFour = \lyricmode { \set includeGraceNotes = ##f
      \set stanza = "4."
      \repeat volta 2 {
        \skip 1 | Nes -- te~o -- ce -- | a -- no va -- _ | mos na -- ve -- | gar. __ _
      }
      \repeat volta 2 {
        Es -- | tar no bar -- | qui -- nho,~a fir -- | me -- za~é can -- | tar;
        Com | os meus ir -- | mãos, __ _ pres -- | tan -- do~a -- ten -- | ção; __ _ _
        | Nes -- sa jor -- | na -- da do | Rei Sa -- lo -- | mão e do | meu São Jo -- | ão.
      }
    }
    theLyricsFive = \lyricmode { \set includeGraceNotes = ##f
      \set stanza = "5."
      \repeat volta 2 {
        Meu | Pai eu lhe | pe -- ço, me __ _ | dê a ben -- | ção. __ _
      }
      \repeat volta 2 {
        Pa -- | ra eu se -- | guir nes -- sa | a -- pu -- ra -- | ção;
        A -- | le -- gre con -- | ten -- te com | os meus ir -- | mãos; __ _ _
        | Nes -- sa mis -- | são __ _ _ | da Vir -- gem | Mãe e de | Ju -- ra -- mi -- | dam.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d2.:m | f | a | d2:m
      }
      \repeat volta 2 { % must have the invisible grace note here
        \grace s4 s4 | d2.:m | g:m | g:m | c
        | c | a | a | d:m
        | d:m| g:m | g:m | a
        | a:7 | d2:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    In this divine gift, I hear the messenger
    Who is the Lord of time, setting out on a journey
    He comes to remind us that time has returned
    And that the Kingdom of Peace and Love will surely come
    \nextverse
    Focus on the power of your thoughts
    And breathe in the strength of that hummingbird
    That nourishes you and gives you courage
    A winged heart soars in the strength of your hummingbird
    \nextverse
    Winged heart, the secret is to sing
    In this breeze that time provides
    The wind that blows brings relief
    Chasing away sadness and all pain to another place
    \nextverse
    In this ocean, we will sail
    Being on the little boat, the firmness is in singing
    With my brothers, paying attention
    On this journey of King Solomon and my Saint John
    \nextverse
    My Father, I ask for your blessing
    So I can continue in this investigation
    Joyful and content with my brothers
    In this mission of the Virgin Mother and Juramidam
  \end{translation}
\endsong


\beginsong{Eu Chamo a Força do Cipó}[by={Chico Corrente}, tags={mazurca}, key={Am}, gk={Am, Gm--Bm}]
  % also in songs_astral_daime.tex
  \audio[key=Am]{https://soundcloud.com/canaljagube/eu-chamo-a-forca-do-cipo-1}
  \audio{https://nossairmandade.com/hymn/2005/EuChamoAFor\%C3\%A7aDoCip\%C3\%B3}
  \newchords{chords_euchamocipo_tios_a}\newchords{chords_euchamocipo_tios_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_euchamocipo_tios_a]
    \[^\mn{C}]Eu chamo a |\[\mnc{B}Am]for\[^\mn{A}]ça \[^\mn{C}]do \[^\mn{E}]ci\[\bmc\mn{A}]pó \altchords{\id[1]{(Gm)}|Gm \e}
    \[^\mn{G}]Da folha a |\[Em]luz, \[^\mn{E}]a \[^\mn{C}]mi\[^\mn{B}]ra\[\mnc{A}Am]ção \altchords{|Dm Gm}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_euchamocipo_tios_b]
    \[^\mn{D}]Da água a |\[Dm]pure\[^\mn{C}]za \[^\mn{B}]di\[\mnc{A}Am]vina \altchords{|Cm Gm}
    \[^\mn{C}]Do fogo |\[\mnc{B}E]toda \[^\mn{D}]a\[^\mn{C}]pu\[^\mn{B}]ra\[\mnc{A}Am]ção \altchords{|D Gm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_euchamocipo_tios_a]
    O Daime |^ferve no caldei^rão
    Borbulha a |^força do Seu po^der
    \endchorus\glueverses\beginchorus\replay[chords_euchamocipo_tios_b]
    A mira|^ção vem se aproxi^mando
    Para mos|^trar para quem quer ^ver
  \endchorus
  \beginchorus\replay[chords_euchamocipo_tios_a]
    Poder de |^Deus que se mani^festa \altchords{\id[2]{(Bm)}|Bm \e}
    Agora a|^qui vai se reve^lar \altchords{|F\shrp{}m Bm}
    \endchorus\glueverses\beginchorus\replay[chords_euchamocipo_tios_b]
    O grande |^segredo da Flo^resta \altchords{|Em Bm}
    Do Sol, da |^Lua, do Vento e ^Mar \altchords{|F\shrp{} Bm}
  \endchorus
  \beginchorus\replay[chords_euchamocipo_tios_a]
    Para quem |^quer conheci^mento
    Estou a|^qui para ensi^nar
    \endchorus\glueverses\beginchorus\replay[chords_euchamocipo_tios_b]
    É ter fir|^meza no pensa^mento
    Perdão e a|^mor para alcan^çar
  \endchorus
  \beginchorus\replay[chords_euchamocipo_tios_a]
    Todos os |^Seres se apro^ximam
    As santa |^cruz que aqui es^tá
    \endchorus\glueverses\beginchorus\replay[chords_euchamocipo_tios_b]
    Vamos pe|^dir força e co^ragem
    Saúde |^para nós traba^lhar
  \endchorus
  \beginchorus\replay[chords_euchamocipo_tios_a]
    Viva o Di|^vino Pai E^terno
    Viva a Ra|^inha Ieman^já
    \endchorus\glueverses\beginchorus\replay[chords_euchamocipo_tios_b]
    E viva |^todos Seres Di^vinos
    Que aqui es|^tão a ilumi^nar
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    %% transcribed by larva, latest update on 2024-06
    % \header {
    %   title = "Eu Chamo A Força Do Cipó"
    %   composer = "Chico Corrente"
    % }
    \include "tex/lp-include-head.ly"
    theMelody = \relative c'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 6/4 \partial 4.
        \sectionLabel "A"
        \repeat volta 2 {
          c8 \pomark c8 c8 | b4 a8( a8) c8 e8  a4( a8) g8 g8 g8
          | g4 \parenthesize e8 e8 c b  a4.
        }
        \sectionLabel "B"
        \repeat volta 2 {
          d8 d d | d4 d8( d8) c8 b  a4 a8 c8 c c
          | b4 b8 d8 c8 b8  a4.
        }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu cha -- mo~a | for -- ça __ _ do ci -- pó; __ _
        Da fo -- lha~a | luz, \skip 1 a mi -- ra -- ção.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Da á -- gua~a | pu -- re _ -- za di -- vi -- na;
        Do fo -- go | to -- da a -- pu -- ra -- ção.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        O Dai -- me | fer -- ve no cal -- dei -- rão; __ _
        Bor -- bu -- lha~a | for -- ça do Seu po -- der.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        A mi -- ra -- | ção vem se~a -- pro -- xi -- man -- do;
        Pa -- ra mos -- | trar pa -- ra quem quer ver.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Po -- der de | Deus que se ma -- ni -- fes -- ta;
        A -- go -- ra~a -- | qui vai se re -- ve -- lar.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        O gran -- de | se -- gre -- do da Flo -- res -- ta;
        Do Sol, da | Lu -- a, do Ven -- to~e Mar.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Pa -- ra quem | quer co _ -- nhe -- ci -- men -- to;
        Es -- tou a -- | qui pa -- ra en -- si -- nar.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        É ter fir -- | me -- za no pen -- sa -- men -- to;
        Per -- dão e~a | mor pa -- ra al -- can -- çar.
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        To -- dos os | Se -- res se a -- pro -- xi -- mam;
        As san -- ta | cruz que a -- qui es -- tá.
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Va -- mos pe -- | dir for -- ça e co -- ra -- gem;
        Sa -- ú -- de | pa -- ra nós tra -- ba -- lhar.
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \repeat volta 2 {
        Vi -- va~o Di -- | vi -- no __ _ Pai E -- ter -- no;
        Vi -- va~a Ra -- | i -- nha I -- e -- man -- já.
      }
      \set stanza = "6.B"
      \repeat volta 2 {
        E vi -- va | to -- dos Se -- res Di -- vi -- nos;
        Que~a -- qui es -- | tão a i -- lu -- mi -- nar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4.
        | a2.:m  a:m | e:m  a4.:m
      }
      \repeat volta 2 {
        s4.
        | d2.:m  a:m | e  a4.:m
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    I call the force of the vine, of the leaf, the miração
    From the water the divine purity, from the fire total ascertainment
    \nextverse
    The Daime brews in the cauldron, bubbles with the force of Its power
    The miração is coming near to show to those who want to see
    \nextverse
    Power of God that it manifests, here now will reveal
    The great secret of the Forest, the Sun, the Moon, the Wind, and Sea
    \nextverse
    For those who seek understanding, I am here to teach
    It is to have firmness in thought to attain forgiveness and love
    \nextverse
    All beings approach the holy cross that is here
    Let us ask for strength and courage, health for us to work
    \nextverse
    Viva the Eternal Divine Father, viva the Queen Iemanjá
    And viva all Divine Beings, that are here to illuminate
  \end{translation}
\endsong


% \beginsong{O Poder Divino}[by={Lúcio Mortimer}, tags={valsa}, key={C}, gk={C, G--B}]
%   \audio{https://www.nossairmandade.com/hymn/1411/OPoderDivino}
%   \meter{3}{4}
%   \mnbeginchorus\memorize
%     |\[\mnc{C}C]Para \[^\mn{D}]ser|\[^\mn{E}]vir \[^\mn{D}]e \[^\mn{C}]lou|\[\mnc{G}(G)]var \altchords{\id[1]{(A)}|A | - |(E)}
%     Ao |\[\mnc{C}C]poder di|\[\mnc{D}Dm]vino \[^\mn{E}]que |\[\mnc{F}\ac(2){G7}]a\[^\mn{E}]qui \[^\mn{/}]es|\[\mnc{/}\ac(1){G}\ac(2){C}]tá | \e \altchords{|A |Bm |\ac(2){E7} |\ac(1){E}\ac(2){A} | \e}
%   \mnendchorus
%   \notesoff
%   \beginchorus
%     |^Peço fir|meza na |^mente
%     O a|^mor verda|^deiro sem|^{pre apresen}|^tar | \e
%   \endchorus
%   \beginchorus
%     |^Para ser|vir e lou|^var
%     Ao |^Poder Di|^vino que |^aqui es|^tá | \e
%   \endchorus
%   \beginchorus
%     |^Peço pa|lavras de |^força
%     Cla|^reza na |^vista para |^não trope|^çar | \e
%   \endchorus
%   \beginchorus
%     |^Para ser|vir e lou|^var
%     Ao |^Poder Di|^vino que |^aqui es|^tá | \e
%   \endchorus
%   \beginchorus
%     |^Peço este |santo per|^dão
%     Uma |^vida apru|^mada e sa|^{ir da} ilu|^são | \e
%   \endchorus
%   \beginchorus
%     |^Que a dou|trina está |^viva \altchords{\id[4]{alt. (C)}|C |Am |G}
%     O |^tempo é che|^gado de |^todos can|^tar | \e \altchords{|\ac(1){Am}\ac(2){C} |\ac(1){Dm}\ac(2){G}}
%         \altchords{|\ac(1){F}\ac(2){G7} |\ac(1){G}\ac(2){C} | \e}
%   \endchorus
%   \beginchorus
%     Pe|^dindo e ro|gando u|^nidos
%     O |^dom que o |^Mestre tem |^para nos |^dar | \e
%   \endchorus
%   \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
%     theMelody = \relative c'' {
%       \set melismaBusyProperties = #'() \slurDashed
%       \key c \major \time 3/4 \partial 4
%       \repeat volta 2 {
%         \altcol \parenthesize c4 \altmark "8." \pomark | c4 c d | e d c | g'( g) g
%         | c c c | d, d e8( \altcol e8 \altmark "4." )
%       } \alternative {
%         { | f4 e f | g2.~ | g2 }
%         { | f4 e d | c2.~ | c2 \bar "|." }
%       }
%     }
%     theLyricsOne = \lyricmode {
%       \set stanza = "1."
%       \repeat volta 2 {
%         \skip 1 Pa -- ra ser -- | vir e lou -- | var; __ _
%         Ao | po -- der di -- | vi -- no que __ _
%       } \alternative {
%         { | a -- qui es -- | tá. __ | _ }
%         { | a -- qui es -- | tá. __ | _ }
%       }
%     }
%     theLyricsTwo = \lyricmode {
%       \set stanza = "2."
%       \repeat volta 2 {
%         \skip 1 | Pe -- ço fir -- | me -- za na | men -- te;~O
%         a -- | mor ver -- da -- | dei -- ro sem -- _
%       } \alternative {
%         { | pre~a -- pre -- sen -- | tar. __ | _ }
%         { | pre~a -- pre -- sen -- | tar. __ | _ }
%       }
%     }
%     theLyricsThree = \lyricmode {
%       \set stanza = "3."
%       \repeat volta 2 {
%         \skip 1 | Pa -- ra ser -- | vir e lou -- | var; __ _
%         Ao | Po -- der Di -- | vi -- no que __ _
%       } \alternative {
%         { | a -- qui es -- | tá. __ | _ }
%         { | a -- qui es -- | tá. __ | _ }
%       }
%     }
%     theLyricsFour = \lyricmode {
%       \set stanza = "4."
%       \repeat volta 2 {
%         \skip 1 | Pe -- ço pa -- | la -- vras de | for -- ça;
%         Cla -- | re -- za na | vis -- ta pa -- ra
%       } \alternative {
%         { | não tro -- pe -- | çar. __ | _ }
%         { | não tro -- pe -- | çar. __ | _ }
%       }
%     }
%     theLyricsFive = \lyricmode {
%       \set stanza = "5."
%       \repeat volta 2 {
%         \skip 1 | Pa -- ra ser -- | vir e lou -- | var; __ _
%         Ao | Po -- der Di -- | vi -- no que __ _
%       } \alternative {
%         { | a -- qui es -- | tá. __ | _ }
%         { | a -- qui es -- | tá. __ | _ }
%       }
%     }
%     theLyricsSix = \lyricmode {
%       \set stanza = "6."
%       \repeat volta 2 {
%         \skip 1 | Pe -- ço~es -- te | san -- to per -- | dão;
%         U -- ma | vi -- da~a -- pru -- | ma -- da~e sa -- _
%       } \alternative {
%         { | ir da~i -- lu | são. __ | _ }
%         { | ir da~i -- lu | são. __ | _ }
%       }
%     }
%     theLyricsSeven = \lyricmode {
%       \set stanza = "7."
%       \repeat volta 2 {
%         \skip 1 | Que a dou -- | tri -- na~es -- tá | vi -- va;
%         O | tem -- po~é che -- | ga -- do de __ _
%       } \alternative {
%         { | to -- dos can -- | tar. __ | _ }
%         { | to -- dos can -- | tar. __ | _ }
%       }
%     }
%     theLyricsEight = \lyricmode {
%       \set stanza = "8."
%       \repeat volta 2 {
%         Pe -- | din -- do~e ro -- | gan -- do u -- | ni -- dos;
%         O | dom que o | Mes -- tre tem __ _
%       } \alternative {
%         { | pa -- ra nos | dar. __ | _ }
%         { | pa -- ra nos | dar. __ | _ }
%       }
%     }
%     theChords = \chordmode {
%       \repeat volta 2 {
%         s4 | c2. | c | \parenthesize g
%         | c | d:m
%       } \alternative {
%         { | c | g | g2 }
%         { | g2.:7 | c | c2 }
%       }
%     }
%     %\layout { #(layout-set-staff-size 11) } % for better fit
%     \include "tex/lp-include-tail-notab.ly"
%   \end{lilypond}\end{lilywrap}
%   \begin{translation}[EN]
%     To serve and praise, to the divine power that is here
%     \nextverse
%     I ask for firmness in mind, the true love always present
%     \nextverse
%     To serve and praise, to the divine power that is here
%     \nextverse
%     I ask for words of strength, clarity in view, not to trip
%     \nextverse
%     To serve and praise, to the divine power that is here
%     \nextverse
%     I ask this holy pardon, a straight life, and to get out of the illusion
%     \nextverse
%     That the doctrine is alive, the time has come for all to sing
%     \nextverse
%     Asking and begging unity, the gift that the Master has to give us
%   \end{translation}
% \endsong


\beginsong{Chamei Mamãe Jurema}[by={Padr. Valdete}, key={C\shrp{}m}, gk={Cm, (Bm)--Cm--D\shrp{}m}]
  \audio{https://nossairmandade.com/hymn/149/ChameiMam\%C3\%A3eJurema}
  \audio[key=Bm]{https://soundcloud.com/spencer-stewart-3/15-chamei-mamae-jurema-06}
  \audio[key=Bm]{https://www.youtube.com/watch?v=hCAdRdcadVU}
  \transpose{2}
  \mnbeginchorus\memorize
    \[^\mn{F#}]Cha|\[\mnc{B}Bm]mei \[\bmc\mn{D}]Mamãe Ju|\[^\mn{C#}]re\[^\mn{B}]ma\[\bm], \[^\mn{F#}]cha|\[^\mn{B}]mei \[^\mn{C#}]Ma\[\mnc{D}B7]mãe \[^\mn{C#}]Ie\[^\mn{B}]man|\[\mnc{E}Em]já \[\bm]
    \lrep \[^\mn{E}]Cha|\[Em]mei Papai \[\bmc\mn{G}]Ogum \[^\mn{F#}]da |\[\mnc{D}Bm]Ma\[^\mn{B}]ta\[\bm], \[^\mn{D}]cha|\[\mnc{C#}F#]mei Pa\[^\mn{D}]pai \[\mnc{E}F#7]O\[^\mn{D}]gum \[^\mn{C#}]do |\[\mnc{B}Bm]Mar \[\ac(1){B7}]{} \rrep
  \mnendchorus
  \notesoff
  \beginchorus
    Cha|^mei to^dos os ca|boclos^, cha|mei to^dos Ori|^xás ^
    \lrep Cha|^mei to^das as fa|^langes^, que Deus do|^mina na ^terra e no |^mar ^ \rrep
  \endchorus
  \beginchorus
    Cha|^mei to^das essas |forças^, para |virem ^me aju|^dar ^
    \lrep Me |^defender ^das tenta|^ções^, que |^so querem ^me derri|^bar ^ \rrep
  \endchorus
  \beginchorus
    Tenho |^fé no ^meu Pai E|terno^, e na |minha Mãe ^Imacu|^la^da
    \lrep Que |^com meu Se^nhor São Mi|^guel^, eu |^vou ven^cer a jor|^na^da \rrep
  \endchorus
  \beginchorus
    É |^so pres^tar aten|ção^, na li|ção que es^ta estu|^dan^do
    \lrep |^Para ^poder pas|^sar^, nas |^provas ^que vem che|^gan^do \rrep
  \endchorus
  \beginchorus\ifshowlilypond\normalsize\fi % to fit on a spread
    Es|^tuda ^com aten|ção^, na es|cola que se ^matricu|^lou ^
    \lrep Para pro|^var que ^é bom a|^luno^: e es|^ta com o ^seu Profes|^sor ^ \rrep
  \endchorus
  \beginchorus\ifshowlilypond\normalsize\fi % to fit on a spread
    |^Eu pro^meto a meu |Mestre^, que eu |vou pi^sar no ba|^ten^te
    \lrep |^Que de a^gora pra |^frente, e ^olho por |^olho e ^dente por |^den^te \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2023-02
    theMelody = \transpose b cis \relative fis' {
      \set melismaBusyProperties = #'() \slurDashed
      \key b \minor \time 4/4 \partial 4.
      r8 \posectionmark "A" fis8( fis8) | b4. ( b8 ) d8( d8)( d8) d8 | cis4( b2)
      fis8( fis8) | b8( b8)( b8) cis8 d4 cis8 b8 | e2( e8)
      \repeat volta 2 {
        \parenthesize e8 \sectionmark "B" e8( e8) | e4( e8) e8 g4 g8 fis8 | d4( b8)( b8)
        \parenthesize d8( \parenthesize d8) d8( d8) | cis4( cis8) d8 e4 d8 cis8
      } \alternative {
        { | b2( b8) }
        { | b2( b8) \dacapo s16 \bar "|." } % s16 is to allow space for D.C.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      Cha -- _ | mei __ _ Ma -- mãe __ _ Ju -- | re -- ma;
      cha -- _ | mei __ _ _ Ma -- mãe Ie -- man -- | já; __ _
      \repeat volta 2 {
        \skip 1 Cha -- _ | mei Pa -- pai O -- gum da | Ma -- ta; __ _
        \skip 1 \skip 1 cha -- _ | mei Pa -- pai O -- gum do
      } \alternative {
        { | Mar. __ _ }
        { | Mar. __ _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      Cha -- _ | mei to -- dos __ _ os ca -- | bo -- clos,
      cha -- _ | mei __ _ _ to -- dos O -- ri -- | xás; __ _
      \repeat volta 2 {
        \skip 1 Cha -- _ | mei __ _ to -- das as fa -- | lan -- ges, __ _
        \skip 1 que Deus do -- | mi -- na na ter -- ra~e no 
      } \alternative {
        { | mar. __ _ }
        { | mar. __ _ }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      Cha -- _ | mei to -- das __ _ es -- sas | for -- ças,
      pa -- ra | vi -- _ _ rem me a -- ju -- | dar; __ _
      \repeat volta 2 {
        \skip 1 Me __ _ | de -- fen -- der das ten -- ta -- ções, __ _ _
        \skip 1 \skip 1 que __ _ so que -- rem me der -- ri -- 
      } \alternative {
        { | bar. __ _ }
        { | bar. __ _ }
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      Te -- nho | fé no meu __ _ Pai E -- | ter -- no,
      e na | mi -- _ nha Mãe I -- ma -- cu -- | la -- da;
      \repeat volta 2 {
        \skip 1 Que __ _ | com meu Se -- nhor São Mi -- | guel, __ _ _
        \skip 1 \skip 1 eu __ _ | vou __ _ ven -- cer a jor --
      } \alternative {
        { | na -- da. }
        { | na -- da. }
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5."
        É __ _ | so pres -- tar __ _ a -- ten -- | ção, __ _
        na li -- | ção __ _ que es -- ta es -- tu -- | dan -- do;
      \repeat volta 2 {
        \skip 1 \skip 1 \skip 1 | Pa -- _ ra po -- der pas -- | sar, __ _ _
        \skip 1 \skip 1 nas __ _ | pro -- _ vas que vem che --
      } \alternative {
        { | gan -- do. }
        { | gan -- do. }
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6."
        Es -- _ | tu -- da com __ _ a -- ten -- ção; __ _
        na es -- | co -- la que se ma -- tri -- cu -- | lou, __ _
      \repeat volta 2 {
          Pa -- ra pro -- | var __ _ que é bom a -- | lu -- no: __ _
          \skip 1 \skip 1 e es -- | ta com o seu Pro -- fes --
      } \alternative {
        { | sor. __ _ }
        { | sor. __ _ }
      }
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7."
      \skip 1 \skip 1 | Eu pro -- me -- _ to~a meu | Mes -- tre,
      que eu | vou __ _ _ pi -- sar no ba -- | ten -- te;
      \repeat volta 2 {
        \skip 1 \skip 1 \skip 1 | Que de a -- go -- ra pra | fren -- te,
        e o -- _ lho por | o -- lho e den -- te por
      } \alternative {
        { | den -- te. }
        { | den -- te. }
      }
    }
    theChords = \transpose b cis \chordmode {
        s4. | b1:m | b1:m | b2:m b2:7 | e'2:m~8
      \repeat volta 2 {
        s4. | \once \set chordChanges = ##f e'1:m | b1:m | fis2 fis2:7
      } \alternative {
        { | b2:m b8:7 }
        { | b2.:m~8 }
      }
    }
    \layout { #(layout-set-staff-size 14) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    I called on Mother Jurema, I called on Mother Yemanja
    I called on Father Ogum of the forest, I called on Father Ogum of the sea
    \nextverse
    I called on all the caboclos, I called on all the Orixás
    I called on all the phalanxes that God rules on land and sea
    \nextverse
    I called on all these forces to come and help me
    To defend me from the temptations that only want to bring me down
    \nextverse
    I have faith in my Eternal Father and in my Immaculate Mother
    that with my Lord Saint Michael, I will overcome the journey
    \nextverse
    Just pay attention to the lesson you are studying
    So that you can pass the tests that are coming
    \nextverse
    Study attentively in the school you enrolled in
    To prove that you are a good student and are with your Teacher
    \nextverse
    I promise my Master that I will work hard
    From now on it's an eye for an eye and a tooth for a tooth.
  \end{translation}
  \ifchorded % a possible stop for this chapter
    \vfill\hfill\makebox[0pt][r]{%
      \fontsize{28pt}{30pt}\coloredchaptersymbol{gray}\color{gray}⭢\raisebox{0.9ex}[0pt][0pt]{17?}%
    }%
  \fi
\endsong


\beginsong{Ciranda do Amor \\ Ciranda do Santo Daime}[by={Padr. Alfredo}, key={Bm}, gk={Bm, (Am)--(Cm)}, tags={marcha e meia valsa}, off={April, Lemoni e Grace}]
  \audio{https://nossairmandade.com/hymn/3237/CirandaDoSantoDaime}
  \audio[key=Am]{https://soundcloud.com/violeiro-daime/ciranda-do-santo-daime?in=violeiro-daime/sets/hinario-nova-dimensao}
  \transpose{2}
  \newchords{chords_cirandadoamor_a}\newchords{chords_cirandadoamor_b}
  \mnbeginchorus\memorize[chords_cirandadoamor_a]
    \ind \[^\mn{E}]O |\[\mnc{A}Am]que Pa\[\bm]pai \[^\mn{B}]me |\[^\mn{A}]de\[\mnc{G}Am7]{-u} \altchords{\id[1]{(Bm)}|Bm | - Bm7}
    \ind |\[Em]Ma\[^\mn{F#}]mãe \[\bmc\mn{G}]con\[^\mn{A}]sa|\[\mnc{E}E]grou \[E7]{} \altchords{|F\shrp{}m |F\shrp{} F\shrp{}7}
  \mnendchorus
  \mnbeginchorus\memorize[chords_cirandadoamor_b]
    \[^\mn{A}]Gira, |\[Am]gira, \[^\mn{E}]crian\[\bmc\mn{C}]ci\[^\mn{A}]nha, |\[^\mn{C}]gi\[^\mn{A}]ra \altchords{|Bm | \e}
    \[\bm]Na ci|\[\mnc{E}E]randa \[\bmc\mn{A}]do a|\[\mnc{C}C]mor \[\bm]{} \altchords{|F\shrp{} |D}
    \[^\mn{A}]Gira, |\[Am]gira, \[^\mn{E}]crian\[\bmc\mn{C}]ci\[^\mn{A}]nha, |\[^\mn{C}]gi\[^\mn{A}]ra \altchords{|Bm | \e}
    \[\bm]Que a |\[\mnc{E}E]Virgem \[\bmc\mn{C}]Mãe \[^\mn{B}]man|\[\mnc{A}Am]dou \[\bm]{} \altchords{|F\shrp{} |Bm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_cirandadoamor_a]
    \ind O |^que Ma^mãe me |dis^se \altchords{\id[4]{alt. (Am)}|Am | - G}
    \ind |^Papai ^confir|^mou ^ \altchords{| - |E7}
  \endchorus
  \beginchorus\replay[chords_cirandadoamor_b]
    Gira, |^gira, cabo^clinha, |gira \altchords{|Am C | - Am}
    ^Gira |^na gi^ra do a|^mor ^ \altchords{|E7 Am |C}
    Gira, |^gira, cabo^clinha, |gira \altchords{|Am C | - Am}
    ^Na gi|^ra que ^Deus man|^dou ^ \altchords{|E7 C |Am}
  \endchorus
  \beginchorus\replay[chords_cirandadoamor_a]
    \ind O |^velho ^tempo |pas^sa \altchords{\id[5]{alt. (Bm)}|Bm | - A}
    \ind No|^vo tem^po che|^gou ^ \altchords{| - |F\shrp{}7}
  \endchorus
  \beginchorus\replay[chords_cirandadoamor_b]
    Novo |^mundo, novo ^povo, nova |era, \altchords{|Bm D | - Bm}
    ^E um |^novo ^profes|^sor ^ \altchords{|F\shrp{}7 Bm |D}
    Novo |^mundo, novo ^povo, nova |era \altchords{|Bm D | - Bm}
    ^E um |^novo ^profes|^sor ^ \altchords{|F\shrp{}7 D |Bm}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2024-05
    theMelody = \transpose a b \relative a'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \repeat volta 2 {
        e4 \posectionmark "A" | a a a b | a2( g4)( g) | g fis g a | e2.
      }
      \repeat volta 2 {
        a8 \sectionmark "B" a | a a e e c8( c8) a8( a8) | c4 a4 a4 a4 | e4 e a a | c2.
        a'8 a | a a e e c8( c8) a8( a8) | c4 a4 a4 a4 | e4 e c' b | a2.
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        O | que Pa -- pai me | deu; __ _ _
        | Ma -- mãe con -- sa -- | grou.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        Gi -- ra, | gi -- ra, cri -- an -- ci -- _ nha, __ _ | gi -- ra
        Na ci -- | ran -- da do a -- | mor;
        Gi -- ra, | gi -- ra, cri -- an -- ci -- _ nha, __ _ | gi -- ra
        Que a | Vir -- gem Mãe man -- | dou.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        O | que Ma -- mãe me | dis -- se; __ _
        | Pa -- pai con -- fir -- | mou.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Gi -- ra, | gi -- ra, ca -- bo -- cli -- _ nha, __ _ | gi -- ra
        Gi -- ra | na gi -- ra do~a -- | mor;
        Gi -- ra, | gi -- ra, ca -- bo -- cli -- _ nha, __ _ | gi -- ra
        Na gi -- | ra que Deus man -- | dou.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        O | ve -- lho tem -- po | pas -- sa;
        No -- | vo tem -- po che -- | gou.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        No -- vo | mun -- do, no -- vo po -- vo, no -- va | e -- ra,
        E um | no -- vo pro -- fes -- | sor;
        No -- vo | mun -- do, no -- vo po -- vo, no -- va | e -- ra
        E um | no -- vo pro -- fes -- | sor.
      }
    }
    theChords = \transpose a b \chordmode {
      \repeat volta 2 {
        s4 | a1:m | a2:m a2:m7 | e1:m | e2 e4:7
      }
      \repeat volta 2 {
        s4 | a1:m  | a:m | e1 | c1
        | a1:m | a:m | e1 | a2.:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi
  \begin{translation}[EN]
    That which Daddy gave to me, Mommy consecrated it
    Go around, go around, little child, go around in the ciranda of love
    Go around, go around, little child, go around because the Virgin Mother ordered it
    \nextverse
    What Mommy told me, Daddy confirmed it.
    Go around, go around, little cabocla, go around
    Go around, go around, little cabocla, go around in the ring, because God ordered it
    \nextverse
    The old time passes, the new time has arrived
    New world, new people, new age, and a new teacher
    New world, new people, new age, and a new teacher
  \end{translation}
\endsong


\beginsong{Rei da Ciência}[by={Padr. Alfredo}, key={Am}, gk={Am, Gm--G\shrp{}m--(Am)}, off={Lúcio \& Cristiane}, tags={mazurca}]
  \audio{https://nossairmandade.com/hymn/3801/ReiDaCi\%C3\%AAncia}
  \audio[key=Am]{https://soundcloud.com/violeiro-daime/mundo-novo?in=violeiro-daime/sets/hinario-nova-dimensao}
  \newchords{chords_reidaciencia_a}\newchords{chords_reidaciencia_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_reidaciencia_a]
    \[^\mn{A}]Pesqui|\[\mnc{C}Am]san\[^\mn{A}]do a \[^\mn{C}]Na\[^\mn{E}]tu\[\bmc\mn{A}]reza \altchords{\id[1]{(Gm)}|Gm}
    Não \[^\mn{B}]se |\[^\mn{C}]tem \[^\mn{A}]na\[^\mn{E}]da \[^\mn{D}]mai\[\mnc{C}C]or \altchords{| - B\flt{}}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_reidaciencia_b]
    \[^\mn{A}]To\[^\mn{C}]da |\[\mnc{E}E]vida \[^\mn{F}]vai \[^\mn{E}]ao \[^\mn{D}]a\[\mncii{C}{A}Am]lém \altchords{|D Gm}
    Toda \[^\mn{B}]ma|\[\mnc{C}E]téria \[^\mn{D}]fi\[^\mn{B}]ca \[^\mn{C}]no \[\mnc{A}Am]pó \altchords{|D Gm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_reidaciencia_a]
    Estu|^dando a Mãe da ^Vida
    O pla|neta do A^mor
    \endchorus\glueverses\beginchorus\replay[chords_reidaciencia_b]
    Salve as |^águas e salve a ^Terra
    Onde Je|^sus Cristo pi^sou
  \endchorus
  \beginchorus\replay[chords_reidaciencia_a]
    Vamos |^todos meus ir^mãos
    Constru|ir um mundo ^novo
    \endchorus\glueverses\beginchorus\replay[chords_reidaciencia_b]
    O ver|^de Paz da flo^resta
    O ver|^melho, justiça do ^fogo
  \endchorus
  \beginchorus\replay[chords_reidaciencia_a]
    Aqui |^com a juven^tude
    Rezo |esta ora^ção
    \endchorus\glueverses\beginchorus\replay[chords_reidaciencia_b]
    Me lem|^brar do Pai E^terno
    O dono |^Rei Jurami^dam
  \endchorus
  \beginchorus\replay[chords_reidaciencia_a]
    Feito a|^qui este con^vite
    Em ple|no dois mil e ^doze
    \endchorus\glueverses\beginchorus\replay[chords_reidaciencia_b]
    Lembran|^do o Rei da Ci^ência
    Mais ma|^duro e mais i^doso
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 6/4 \partial 4
      \repeat volta 2 {
        a8 \posectionmark "A" a8
        | c4 a8( a) c e  a4( a) a8 b
        | c4 a e8 d  c4( c)
      }
      \repeat volta 2 {
        a8 \sectionmark "B" c8
        | e4 << e8 \once\slurUp \single\altcol f \altmark "3., 4., 5." \single\altcol ( >> f) e d  \once\slurUp c4( a8)( a) a b
        | c8( c) << c8 \once\slurUp \single\altcol d \altmark "2., 4." \single\altcol ( >> d) b c  a4( a)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Pes -- qui -- | san -- do a Na -- tu -- re -- za;
        Não se | tem na -- da mai -- or. __ _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        To -- da | vi -- da vai ao a -- lém; __ _
        To -- da ma -- | té -- _ ria fi -- ca no pó. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Es -- tu -- | dan -- do a Mãe da Vi -- da;
        O pla -- | ne -- ta do A -- mor. __ _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Sal -- ve~as | á -- guas e sal -- ve~a Ter -- ra;
        On -- de Je -- | sus __ _ \altcol Cris -- _ to pi -- sou. __ _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Va -- mos | to -- dos __ _ meus ir -- mãos; __ _
        Cons -- tru -- | ir um mun -- do no -- vo.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        O ver -- | de \altcol Paz __ _ da flo -- res -- ta; __ _
        O ver -- | me -- lho, jus -- ti -- ça do fo -- go.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        A -- qui | com a __ _ ju -- ven -- tu -- de;
        Re -- zo | es -- ta o -- ra -- ção. __ _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Me lem -- | brar \altcol do __ _ Pai E -- ter -- no; __
        O do -- no | Rei __ _ \altcol Ju -- _ ra -- mi -- dam. __ _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        Fei -- to~a -- | qui es -- _ te con -- vi -- te;
        Em ple -- | no dois mil e do -- ze.
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Lem -- bran -- | do~o \altcol Rei __ _ da Ci -- ên -- cia; __ _
        Mais ma -- | du -- _ ro e mais i -- do -- so.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a2.:m a:m | a:m c2
      }
      \repeat volta 2 {
        s4 | e2. a:m | e a2:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]\iflyriconly\scriptsize\fi % to fit on one page in lyrics-only book
    Searching for Nature, there has been no greater way
    All life goes to the beyond, all matter remains in dust
    \nextverse
    Studying the Mother of Life, the planet of Love
    Hail the water and hail the Earth where Jesus Christ stepped
    \nextverse
    Let's all go my brothers and sisters to construct a new world
    The green, Peace of the forest; the red, justice of the fire
    \nextverse
    Here with the youth I pray this prayer
    I remember the Eternal Father, the owner, King Juramidam
    \nextverse
    Made here, this invitation, in the middle of two thousand and twelve
    Remembering the King of Science, more mature and older
  \end{translation}
\endsong


\beginsong{Eu Sou Flor das Águas}[by={Padr. Alfredo}, key={Bm}, gk={Bm, G\shrp{}m--Bm}, off={Mariana, Mikael}, tags={valsa, 2x}]
  \audio{https://nossairmandade.com/hymn/4282/EuSouFlorDas\%C3\%81guas}
  \newchords{chords_eusouflordasaguas_a}\newchords{chords_eusouflordasaguas_b}
  \transpose{2}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_eusouflordasaguas_a]
    \[^\mn{E}]Eu |\[Am]sou \[^\mn{F}]flor \[^\mn{E}]das |\[^\mn{C}]á\[^\mn{A}]guas \altchords{\id[1]{(Bm)}|Bm | \e}
    E |\[^\mn{C}]te\[^\mn{A}]nho \[^\mn{C}]po|\[\mnc{B}E]der \altchords{| - |F\shrp{}}
    \[^\mn{D}]Eu |\[E7/D]sa\[^\mn{E}]cio \[^\mn{D}]a |\[\mnc{B}E]se\[^\mn{G#}]de \altchords{|F\shrp{}7/E |F\shrp{}}
    \[^\mn{B}]De |\[\mnc{D}Dm]quem \[^\mn{E}]me\[^\mn{F}]re|\[\mnc{E}E]cer \altchords{|Em |F\shrp{}}
  \mnendchorus
  \mnbeginchorus\memorize[chords_eusouflordasaguas_b]
    \ind |\[^\mn{E}]Da \[^\mn{F}]on\[^\mn{E}]de |\[\mnc{D}Dm]vens \altchords{| - |Em}
    \ind Pa|\[^\mn{F}]ra on\[^\mn{A}]de |\[\mnc{E}E]vais \altchords{| - |F\shrp{}}
    \ind Eu |sou \[^\mn{F}]flor \[^\mn{E}]das |\[\mnc{D}Dm]á\[^\mn{B}]guas \altchords{| - |Em}
    \ind \[^\mn{C}]Somos |\[\mnc{D}E7]e \[^\mn{G#}]de\[^\mn{B}]ve |\[\mnc{A}Am]ser \altchords{|F\shrp{}7 |Bm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eusouflordasaguas_a]
    Fa|^zer a lim|peza
    No |meu cora|^ção
    Dou |^{viva a} Je|^sus
    Dou |^{viva a} São Jo|^ão
  \endchorus
  \beginchorus\replay[chords_eusouflordasaguas_b]
    \ind E |Nossa Se|^nhora
    \ind |Da Concei|^ção
    \ind Na |Santa Dou|^trina
    \ind Nos |^dá a ben|^ção
  \endchorus
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2024-05
    \include "tex/lp-include-head.ly"
    theMelody = \transpose a b \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 4
      \repeat volta 2 {
        \sectionLabel "A"
        e4 \pomark
        | e f e | c a a | c a c | b2 d4
        | d e d | b( gis) b | d e f8( f8)
      } \alternative {
        { | e2 }
        { | e2 \sectionLabel "B" \parenthesize e4 | e f e }
      }
      \repeat volta 2 { 
        | d2 d4 | f f a | e2 e4
        | e f e | d b c8( c8) | d4 gis, b
      } \alternative {
        { | a2 \parenthesize e'4 | e f e  }
        { | a2 }
      }
      \fine
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu | sou flor das | á -- guas;
        E | te -- nho po -- | der;
        Eu | sa -- cio a | se -- de;
        De | quem me -- re _ --
      } \alternative {
        { | cer. }
        { | cer. \set stanza = "1.B" \skip 1 | Da on -- de  }
      }
      \repeat volta 2 {
        | vens;
        Pa -- | ra on -- de | vais;
        Eu | sou flor das | á -- guas;
        So -- mos | e de -- ve
      } \alternative {
        { | ser. \skip 1 | Da on -- de }
        { | ser. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Fa -- | zer a lim -- | pe -- za;
        No | meu co -- ra -- | ção;
        Dou | vi -- va~a Je -- | sus; __ _
        Dou | vi -- va~a São Jo --
      } \alternative {
        { | ão. }
        { | ão. \set stanza = "2.B" E | Nos -- sa Se -- }
      }
      \repeat volta 2 {
        | nho -- ra;
        | Da Con -- cei -- | ção;
        Na | San -- ta Dou -- | tri -- na;
        Nos __ _ | dá a ben --
      } \alternative {
        { | ção. E | Nos -- sa Se -- }
        { | ção. }
      }
    }
    theChords = \transpose a b \chordmode {
      \repeat volta 2 {
        s4
        | a2.:m | a:m | a:m | e
        | e:7/d | e | d:m
      } \alternative {
        { | e2 }
        { | e2. | e2. }
      }
      \repeat volta 2 {
        | d:m | d:m | e | e
        | d:m | e:7
      } \alternative {
        { | a2.:m | a2.:m }
        { | a2:m }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    I am the flower of the waters, and I have power
    I quench the thirst of those who merit it
    \nextverse
    From where you come, where you go
    I am the flower of the waters, we are and we must be
    \nextverse
    To do a cleansing in my heart
    I give viva to Jesus, I give viva to St. John
    \nextverse
    And Our Lady of Conception
    In the Holy Doctrine gives us the blessing
  \end{translation}
\endsong


\beginsong{Excelência}[by={Padr. Alfredo}, key={Bm}, gk={Am, Gm--Bm}, off={Kelly Cristina}, tags={3x}]
  \transpose{2}
  \mnbeginchorus\memorize
    \[^\mn{A}]Meu São \[^\mn{B}]Jo|\[\mnc{C}C]ão,\[\bm]{} meu São \[^\mn{B}]Jo|\[\mnc{A}Am]ão \[\bm]
    Vos\[^\mn{C}]sa ex\[^\mn{E}]ce|\[^\mn{A}]lência e Jesus \[\bm]Cristo Reden|\[\mnc{D}Dm]tor \[\bm]
    São quem \[^\mn{C}]me en|\[\mnc{B}E]sinam nesta es\[\bm]cola \[^\mn{C}]do \[^\mn{D}]a|\[\mnc{E}Am]mor \[\bm]
    \[^\mn{A}]A Vir\[^\mn{C}]gem |\[\mnc{E}E]Mãe e o \[^\mn{D}]nosso \[\bmc\mn{C}]Mestre En\[^\mn{B}]sina|\[\mnc{A}Am]dor \[\bm]
  \mnendchorus
  \notesoff
  \beginchorus
    Santo Cru|^zei^ro, Santa Dou|^tri^na
    O Santo |Daime, esta ^luz que nos en|^si^na
    Para |^sempre só nos ^resta agrade|^cer ^
    Para |^sempre com a^mor hei de ven|^cer ^
  \endchorus
  \begin{translation}[EN]
    My Saint John, my Saint John
    Your Excellency and Jesus Christ the Redeemer
    They are who teach me in this school of love
    The Virgin Mother and our Master Teacher
    \nextverse
    Holy Cross, Holy Doctrine
    The Santo Daime, this light that teaches us
    Forever all that remains is for us to be thankful
    Forever with love I will overcome
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[]
    % transcribed by larva, latest update on 2023-05
    \include "tex/lp-include-head.ly"
    theMelody = \transpose a b \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        a8 \pomark a b
        | c2( 8) c8 c b | a2( 8) a8 c e | a a a a a a a a | d,2( 8)( d8) d c
        | b b b b b b c d | e2~ 8 \parenthesize a,8 a c | e e d d c c b b | a2~ 8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Meu São Jo -- | ão, __ _ meu São Jo -- | ão; __ _
        Vos -- sa~ex -- ce -- | lên -- cia~e Je -- sus Cris -- to Re -- den -- | tor; __ _
        São quem me~en -- | si -- nam nes -- ta~es -- co -- la do a -- | mor; _
        A Vir -- gem | Mãe e~o nos -- so Mes -- tre~En -- si -- na -- | dor. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        San -- to Cru -- | zei -- ro, San -- ta Dou -- | tri -- na;
        O San -- to | Dai -- me, es -- ta luz que nos en -- | si -- na; __ _
        Pa -- ra | sem -- pre só nos res -- ta~a -- gra -- de -- | cer; _
        \skip 1 Pa -- ra | sem -- pre com a -- mor hei de ven -- | cer. _
      }
    }
    theChords = \transpose a b \chordmode {
      \repeat volta 2 {
        s4.
        | c1 | a:m | a:m | d:m | e | a:m | e | a2:m~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \ifchorded % a possible stop for this chapter
    \vfill\hfill\makebox[0pt][r]{%
      \fontsize{28pt}{30pt}\coloredchaptersymbol{gray}\color{gray}⭢\raisebox{0.9ex}[0pt][0pt]{17?}%
    }%
  \fi
\endsong


\beginsong{Meu Beija-flor o Sol Raiou}[by={Alessandra}, key={Dm}, gk={Dm, Cm--Em}]
  \audio{https://www.nossairmandade.com/hymn/2264/MeuBeija-FlorOSolRaiou}
  \newchords{chords_meu_bf_sol_raiou_a}\newchords{chords_meu_bf_sol_raiou_b}
  \mnbeginchorus\memorize[chords_meu_bf_sol_raiou_a]
    \[^\mn{D}]Meu bei\[^\mn{E}]ja-|\[\mnc{F}Dm]flor \[^\mn{D}]o \[\bmc\mn{F}]sol \[^\mn{E}]rai|\[\mnc{A}A]ou \[\bm]{} \altchords{\id[1]{(Cm)}|Cm |G}
    \[^\mn{A}]Ouvi os |\[\mnc{G}Gm]pás\[^\mn{F}]sa\[\bmc\mn{E}]ros \[^\mn{D}]can|\[\mnc{A}A]tar \[\ac(1){A7}]{} \altchords{|Fm |G \ac(1){G7}}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_meu_bf_sol_raiou_b]
    \[^\mn{A}]Anunci|\[\mnc{G}Gm]an\[^\mn{F}]do o \[\bmc\mn{E}]Sal\[^\mn{D}]va|\[\mnc{A}Dm]dor \altchords{|Fm |Cm}
    \[\bmc\mn{D}]Que \[^\mn{E}]à |\[\mnc{F}(B&)]Ter\[^\mn{D}]ra i\[\mnc{F}A7]rá \[^\mn{E}]vol|\[\mnc{D}Dm]tar \[\ac(1){D7}]{} \altchords{|(A\flt) G7 |Cm \ac(1){C7}}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    No firma|^mento ^um cla|^rão ^
    Resplande|^ceu em ^todo |^Céu ^
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Tocou e |^tornou ^a to|^car
    A ^corne|^ta de ^São Mi|^guel ^
  \endchorus
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    Santa Ma|^{ria a}^nunci|^ou ^ \altchords{\id[2]{(Em)}|Em |B}
    Na tribo |^tocou ^o cla|^rim ^ \altchords{|Am |B \ac(1){B7}}
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Já vem des|^cendo ^das Es|^trelas \altchords{|Am |Em}
    ^Meu guer|^reiro ^Beija-|^mim ^ \altchords{|(C) B7 |Em \ac(1){E7}}
  \endchorus
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    Tu Beija-|^mim flor ^de a|^mor ^
    Guerreiro |^do Pai ^Cria|^dor ^
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Dainos Sa|^úde e ^Uni|^ão
    ^Vem cu|^rar nes^ta ses|^são ^
  \endchorus
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    Mensagei|^{ro do} ^fim dos |^tem^pos
    Rei Beija-|^mim se^nhor do |^Bem ^
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Vem decla|^{rar o} ^nasci|^mento
    ^Da No|^va Je^rusa|^lém ^
  \endchorus
  \beginchorus\replay[chords_meu_bf_sol_raiou_a]
    Sigo na |^bata^lha do a|^mor ^
    Com espe|^rança ^de che|^gar ^
    \endchorus\glueverses\beginchorus\replay[chords_meu_bf_sol_raiou_b]
    Agrade|^cendo ao ^Sol e à |^Lua
    ^E a |^Rai^nha do |^Mar ^
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative d'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 4/4 \partial 4.
      \repeat volta 2 {
        d8 \posectionmark "A" d8 e8 | f4 d f e | a,2( a8) a' a a
        | g4 f e d | a2~ a8
      }
      \repeat volta 2 {
        a'8 \sectionmark "B" a8 a8 | g4 f e d | a4.( a8) d4 e
        | f d f e | d2~ d8
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Meu bei -- ja -- | flor o sol rai -- | ou; __ _
        Ou -- vi os | pás -- sa -- ros can -- | tar. _
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        A -- nun -- ci -- | an -- do~o Sal -- va -- | dor; __ _
        Que à | Ter -- ra~i -- rá vol -- | tar. _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        No fir -- ma -- | men -- to um cla -- | rão; __ _
        Res -- plan -- de -- | ceu em to -- do | Céu. _
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        To -- cou e | tor -- nou a to -- | car;
        A cor -- ne -- | ta de São Mi -- | guel. _
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        San -- ta Ma -- | ri -- a~a -- nun -- ci -- | ou; __ _
        Na tri -- bo | to -- cou o cla -- | rim. _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Já vem des -- | cen -- do das Es -- | tre -- las;
        Meu guer -- | rei -- ro Bei -- ja -- | mim. _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Tu Bei -- ja -- | mim flor de a -- | mor; __ _
        Guer -- rei -- ro | do Pai Cri -- a -- | dor. _
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Dai -- nos Sa -- | ú -- de~e U -- ni -- | ão; __ _
        Vem cu -- | rar nes -- ta ses -- | são. _
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        Men -- sa -- gei -- | ro do fim dos | tem -- pos;
        Rei Bei -- ja -- | mim se -- nhor do | Bem. _
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Vem de -- cla -- | rar o nas -- ci -- | men -- to;
        Da No -- | va Je -- ru -- sa -- | lém. _
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \repeat volta 2 {
        Si -- go na | ba -- ta -- lha do~a -- | mor; __ _
        Com es -- pe -- | ran -- ça de che -- | gar. _
      }
      \set stanza = "6.B"
      \repeat volta 2 {
        A -- gra -- de -- | cen -- do~ao Sol e~à | Lu -- a;
        E a | Ra -- i -- nha do | Mar. _
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | d1:m | a1 | g1:m | a2 \mark \markup{\hspace #-1.5 \super{"1"}} \parenthesize a8:7
      }
      \repeat volta 2 {
        s4. | g1:m | d1:m | \parenthesize bes2 a:7 | d2:m \mark \markup{\hspace #-1.5 \super{"1"}} \parenthesize d8:7
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    My hummingbird, the Sun radiated, I heard the birds sing
    Announcing the Savior, who is coming back to Earth
    \nextverse
    In the firmament a flash shimmered all throughout the heavens
    Touched and became the sounding of the trumpet of Saint Michael
    \nextverse
    Holy Mary announced, the tribe sounded the bugle
    Already from the descending stars came my warrior Beija-mim
    \nextverse
    Your Beija-mim flower of love, warrior of the Father Creator
    Give us ouyr health and our union, come to heal in this session
    \nextverse
    Messenger of the end of times, king Beija-mim the Lord of Good
    He comes to declare the birth of the New Jerusalem
    \nextverse
    I follow in this battle of love, with hope to arrive
    Giving thanks to the sun and the moon, and the Queen of the Sea
  \end{translation}
\endsong

\ifchorded\sclearpage\fi\chapcornermarkdashedtrue
\beginsong{Santo Daime Beija-mim}[by={Marina Ruberti}, tags={mazurka, Mesa Branca}, key={Dm}, gk={Dm, Cm--Em}]
  \audio{https://www.nossairmandade.com/hymn/2265/SantoDaimeBeija-Mim}
  \newchords{chords_santodaimebm_a}\newchords{chords_santodaimebm_b}
  \meter{6}{4}
  \mnbeginchorus\memorize[chords_santodaimebm_a]
    \[^\mn{A}]Com a|\[\mnc{D}Dm]mor eu re\[^\mn{E}]ce\[\mnc{F}(F)]bi \altchords{\id[1]{(Cm)}|Cm (E\flt)}
    \[^\mn{A}]Com a|\[\mnc{E}A]mor \[^\mn{C#}]eu \[^\mn{F}]vou \[^\mn{E}]te \[\mnc{D}Dm]dar \altchords{|G Cm}
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_santodaimebm_b]
    \[^\mn{D}]Santo |\[\mnc{G}Gm]Daime \[^\mn{F}]Bei\[^\mn{E}]ja-\[\mnc{F}Dm]mim \altchords{|Fm Cm}
    \[^\mn{D}]Com a|\[\mnc{E}A7]mor vou \[^\mn{D}]te \[^\mn{C#}]cu\[\mnc{D}Dm]rar \altchords{|G7 Cm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_santodaimebm_a]
    Com a|^mor eu rece^bi
    Com ver|^dade eu vou te ^dar
    \endchorus\glueverses\beginchorus\replay[chords_santodaimebm_b]
    Santo |^Daime Beija-^mim
    Um se|^gredo para desven^dar
  \mnendchorus
  \beginchorus\replay[chords_santodaimebm_a]
    Com a|^mor eu rece^bi \altchords{\id[2]{(Em)}|Em (G)}
    Com a|^mor eu vou te ^dar \altchords{|B Em}
    \endchorus\glueverses\beginchorus\replay[chords_santodaimebm_b]
    Santo |^Daime para se^guir \altchords{|Am Em}
    Este a|^mor para ze^lar \altchords{|B7 Em}
  \mnendchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 6/4 \partial 4
      \repeat volta 2 {
        a8 \posectionmark "A" a8
        | d4 d d8 e8  f2 a8 a8
        | e4 cis8( cis8) f e  d2
      }
      \repeat volta 2 {
        d8 \sectionmark "B" d8
        | g4 g8( g8) f8 e8  f2 d8 d8
        | e8( e8) e8( e8) d cis  d2
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Com a -- | mor eu re -- ce -- bi;
        Com a -- | mor eu __ _ vou te dar.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        San -- to | Dai -- me __ _ Bei -- ja -- mim
        Com a -- | mor __ _ vou __ _ te cu -- rar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Com a -- | mor eu re -- ce -- bi;
        Com ver -- | da -- de eu vou te dar.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        San -- to | Dai -- me __ _ Bei -- ja -- mim;
        Um se -- | gre -- do pa -- ra des -- ven -- dar.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        Com a -- | mor eu re -- ce -- bi;
        Com a -- | mor eu __ _ vou te dar.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        San -- to | Dai -- me pa -- ra se -- guir;
        Es -- te~a -- | mor __ _ pa -- _ ra ze -- lar.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | d2.:m \parenthesize f | a d2:m
      }
      \repeat volta 2 {
        s4 | g2.:m d:m | a:7 d2:m
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    With love I receive, with love I am going to give you
    Santo Daime Beija-mim, with love I am going to heal you
    \nextverse
    With love I receive, with truth I am going to give you
    Santo Daime Beija-mim, a secret to reveal
    \nextverse
    With love I receive, with love I am going to give you
    Santo Daime to follow, this love to take care of
  \end{translation}
\endsong
\sclearpage\chapcornermarkdashedfalse


\beginsong{Eu Peço a Meu São Miguel}[by={Padr. Valdete}, key={D}, gk={D, C--E}]
  \audio{https://www.nossairmandade.com/hymn/131/EuPe\%C3\%A7oAoMeuS\%C3\%A3oMiguel}
  \transpose{2}
  \newchords{chords_eupecoameusaomiguel_a}\newchords{chords_eupecoameusaomiguel_b}
  \mnbeginchorus\memorize[chords_eupecoameusaomiguel_a]
    \[^\mn{G}]Eu |\[\mnc{C}C]peço \[^\mn{E}]a \[\bmc\mn{G}]meu \[^\mn{F}]São \[^\mn{E}]Mi|\[\mnc{G}G]guel\[\bm], para |\[\mnc{F}F]Vós \[^\mn{E}]com \[\mnc{G}G]a \[^\mn{F}]Sua \[^\mn{E}]es|\[\mnc{C}C]pa\[\bm]da.
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_eupecoameusaomiguel_b]
    \[^\mn{C}]Aju|\[\mnc{E}C]dai a \[^\mn{C}]domi\[\mnc{A}F]nar \[^\mn{C}]este |\[C]po\[\bm]vo, para |\[^\mn{E}]se\[^\mn{C}]guir nu\[\mnc{A}F]ma \[^\mn{C}]boa es|\[C]tra\[\bm]da.
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    Para |^seguir nes^ta boa es|^tra^da, do |^Mestre ^que nos en|^si^na.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    É cum|^prir to^dos manda|^men^tos, con|tidos aqui ^nesta Dou|^tri^na.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    En|^xotando ^os malfa|^ze^jos, a|^qui na Li^nha do Tu|^cum^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    Meus ir|^mãos vamos ^prestar aten|^ção^, para |que nós não ^sejamos |^um^.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    Is|^to não é ^um julga|^men^to, mas |^é um a^viso se|^ríssi^mo.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    Para |^quem quer se^guir na Dou|^tri^na, e pres|tar bem con^ta do ser|^vi^ço.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    E pres|^tar bem con^ta do ser|^vi^ço, ao |^nosso Mes^tre ensina|^dor^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    Para |^ver se es^tamos se|^guin^do, ou se |somos só ^uns zomba|^do^res.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    Meu |^irmão se ^está zom|^ban^do, tra|^te de se ^arrepen|^der^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    E |^peça seu ^perdão a |^Deus^, para |ver se po^der mere|^cer^.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    É se ar|^repender ^de cora|^ção^, não |^é so por ^compara|^ção^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    Por|^que o nos^so Mestre |^sa^be, se |pode te ^dar o per|^dão^.
  \endchorus
  \beginchorus\replay[chords_eupecoameusaomiguel_a]
    Se se ar|^repender ^de cora|^ção^, dá |^para to^do mundo |^ver^.
    \mnendchorus\glueverses\mnbeginchorus\replay[chords_eupecoameusaomiguel_b]
    No |^seu se^guir a Dou|^tri^na, e |nas ações ^que come|^ter^.
  \endchorus
  \beginverse % to present alt key chords only
    \altchords{\id[1]{(D)}|D |A |G A |D}
    \altchords{|D G |D | - G |D}
  \endverse
  \ifshowlilypond\vspace{-1ex}\fi% for better fit
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \transpose c d \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        g8( \posectionmark "A" g8) | c4 c8 e8 g4 f8 e8
        | g2( g4) g8( g8) | f4( f8) e8 g4 f8 e8 | c4.( c8)( c4)
      }
      \repeat volta 2 {
        c8( \sectionmark "B" c8) | e8( e)( << c \parenthesize e) \genmark "(2., 8.)" >> c a4 c8 c | c2( c4) c8( c8)
        | e8( e8) c8 c8 a4 c8 c8 | c2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        Eu __ _ | pe -- ço a meu São Mi -- | guel, __ _
        pa -- ra | Vós __ _ com a Sua es -- | pa -- _ da.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        A -- ju -- | dai a do -- mi -- nar es -- te | po -- vo,
        pa -- ra | se -- _ guir nu -- ma boa es -- | tra -- da.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Pa -- ra | se -- guir nes -- ta boa es -- | tra -- da,
        do __ _ | Mes -- _ tre que nos en -- | si -- _ na.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        É cum -- | prir __ _ _ to -- dos man -- da -- | men -- tos,
        con -- _ | ti -- dos a -- qui nes -- ta Dou -- | tri -- na.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        En -- _ | xo -- tan -- do os mal -- fa -- | ze -- jos,
        a -- _ | qui na Li -- nha do Tu -- | cum. __ _ _
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        Meus ir -- | mãos __ _ va -- mos pres -- tar aten -- | ção, __ _
        pa -- ra | que __ _ nós não se -- ja -- mos | um. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4.A"
      \repeat volta 2 {
        Is -- _ | to não é um jul -- ga -- | men -- to,
        mas __ _ | é um a -- vi -- so se -- | rís -- si -- mo.
      }
      \set stanza = "4.B"
      \repeat volta 2 {
        Pa -- ra | quem __ _ quer se -- guir na Dou -- | tri -- na,
        e pres -- | tar __ _ bem con -- ta do ser -- | vi -- ço.
      }
    }
    theLyricsFive = \lyricmode {
      \set stanza = "5.A"
      \repeat volta 2 {
        E pres -- | tar bem con -- ta do ser -- | vi -- ço,
        ao __ _ | nos -- so Mes -- tre~en -- si -- na -- | dor. __ _ _
      }
      \set stanza = "5.B"
      \repeat volta 2 {
        Pa -- ra | ver __ _ se es -- ta -- mos se -- | guin -- do,
        ou se | so -- _ mos só uns zom -- ba -- | do -- res.
      }
    }
    theLyricsSix = \lyricmode {
      \set stanza = "6.A"
      \repeat volta 2 {
        Meu __ _ | ir -- mão se es -- tá zom -- | ban -- do,
        tra -- _ | te de se ar -- re -- pen -- | der. __ _ _
      }
      \set stanza = "6.B"
      \repeat volta 2 {
        E __ _ | pe -- _ ça seu per -- dão a | Deus, __ _
        pa -- ra | ver __ _ se po -- der me -- re -- | cer. __ _
      }
    }
    theLyricsSeven = \lyricmode {
      \set stanza = "7.A"
      \repeat volta 2 {
        É se~ar -- | re -- pen -- der de co -- ra -- | ção, __ _
        não __ _ | é so por com -- pa -- ra -- | ção. __ _ _
      }
      \set stanza = "7.B"
      \repeat volta 2 {
        Por -- _ | que __ _  o nos -- so Mes -- tre | sa -- be,
        se __ _ | po -- _ de te dar o per -- | dão. __ _
      }
    }
    theLyricsEight = \lyricmode {
      \set stanza = "8.A"
      \repeat volta 2 {
        Se se~ar -- | re -- pen -- der de co -- ra -- | ção, __ _
        dá __ _ | pa -- ra to -- do mun -- do | ver. __ _ _
      }
      \set stanza = "8.B"
      \repeat volta 2 {
        No __ _ | seu __ _ _ se -- guir a Dou -- | tri -- na,
        e __ _ | nas __ _ a -- ções que co -- me -- | ter. __ _
      }
    }
    theChords = \transpose c d \chordmode {
      \repeat volta 2 {
        s4 | c1 | g | f2 g2 | c2.
      }
      \repeat volta 2 {
        s4 | c2 f2 | c1 | c2 f2 | c2.
      }
    }
    \layout { #(layout-set-staff-size 12.5) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    I ask my Saint Michael, for you with your sword.
    Help me have dominion over the people to follow on a good road.
    \nextverse
    To follow this good road of the Master who teaches us.
    We must abide by all the commandments that are contained in this doctrine.
    \nextverse
    Driving aways evildoers, here in the line of Tucum.
    My brothers and sisters, let's pay attention, so that we aren't one of those.
    \nextverse
    This is not a judgement, but it is a serious warning.
    For those who want to follow the doctrine and present a good record of service.
    \nextverse
    It is to present a good record of service to our Master Teacher.
    To see if we are following, or if we are only mockers.
    \nextverse
    My brothers and siters, if you're mocking, be sure to repent.
    And ask forgiveness from God to see if you can deserve it.
    \nextverse
    It is to repent in our hearts, it is not to compare.
    Because Our Master knows if He can give you the forgiveness.
    \nextverse
    It is to repent in your heart, everyone can see it.
    In the way you follow the doctrine, and in the actions that you take.
  \end{translation}
\endsong


\beginsong{Sete Cruzes de São Miguel}[by={Isabel Barsé}, key={Dm}, gk={Cm--Em}, tags={mazurca}]
  \audio{https://www.nossairmandade.com/hymn/2266/SeteCruzesDeS\%C3\%A3oMiguel}
  \meter{6}{4}
  \mnbeginchorus\memorize
    \lrep \[^\mn{A}]As sete |\[\mnc{D}Dm]cruzes de São \[^\mn{F}]Mi\[\bmc\mn{A}]guel \altchords{\id[1]{(Em)}|Em}
    \[^\mn{G}]Estão a|\[\mnc{F}A7]qui \[^\mn{E}]pra \[^\mn{C#}]te \[^\mn{E}]liber\[\mnc{D}Dm]tar \rrep \altchords{|B7 Em}
    \lrep \[^\mn{D}]São sete |\[Dm]cruzes, são sete \[\bm]cru\[^\mn{A}]zes \altchords{|Em}
    São sete |\[\mnc{F}A7]cruzes \[^\mn{E}]pra \[^\mn{C#}]te \[^\mn{E}]liber\[\mnc{D}Dm]tar \rrep \altchords{|B7 Em}
  \mnendchorus
  \notesoff
  \beginchorus
    \lrep Todos os |^seres que me acom^panham
    Vós |^queiram me respei^tar \rrep
    \lrep Eu sou o |^chefe desta ^casa
    Estou a|^qui para coman^dar \rrep
  \endchorus
  \beginchorus
    \lrep Esta |^é a casa de ^Deus
    Esta |^é a casa de ^Deus \rrep
    \lrep Sou |^Luz, sou ^Luz
    Estou a|^qui pra te liber^tar \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \minor \time 6/4 \partial 4.
      \repeat volta 2 {
        \parenthesize a8 \posectionmark "A" a a | d4 d8 d d f  a4( a8)( << a8) \parenthesize g8 \genmark "(1.)" >> g( g) | f4 e8 cis e e  d4.
      }
      \repeat volta 2 {
        \parenthesize d8 \sectionmark "B" d( d) | d4 d8( d) d( d)  d4 \parenthesize a8 a a a
      } \alternative {
        { | f'8( f) e cis e e  d4. }
        { | f8( f) e cis e e  d4. \dacapo  \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        As se -- te | cru -- zes de São Mi -- guel; __ _
        (Es) -- tão a -- | qui pra te li -- ber -- tar.
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        São se -- te | cru -- zes, são se -- te cru -- zes;
        São se -- te 
      } \alternative {
        { | cru -- zes pra te li -- ber -- tar. }
        { | cru -- zes pra te li -- ber -- tar. }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        To -- dos os | se -- res que me~a -- com -- pa -- nham; __ _
        Vós __ _ | quei -- ram me res -- pei -- tar.
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Eu sou o | che -- fe __ _ des -- ta ca -- sa;
        Es -- tou a -- 
      } \alternative {
        { | qui __ _ pa -- ra co -- man -- dar. }
        { | qui __ _ pa -- ra co -- man -- dar. }
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        \skip 1 Es -- ta | é a ca -- sa de Deus; __ _
        \skip 1 Es -- ta | é a ca -- sa de Deus.
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        \skip 1 Sou __ _ | Luz, __ _ _ sou __ _ Luz;
        \skip 1 Es -- tou a --
      } \alternative {
        { | qui __ _ pra te li -- ber -- tar. }
        { | qui __ _ pra te li -- ber -- tar. }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | d2.:m  d2.:m | a2.:7  d4.:m
      }
      \repeat volta 2 {
       s4. | d2.:m  d2.:m
      } \alternative {
        { | a2.:7  d4.:m }
        { | a2.:7  d4.:m }
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    These seven crosses of Saint Michael are here to set you free
    They are 7 crosses, they nare 7 crosses, they are 7 crosses to set you free
    \nextverse
    All the beings who accompany me, you all want me to respect
    I am the chief of this house, I am here to command
    \nextverse
    This is the house of Godd, this is the house of God
    I am light, I am light, I am light to set you free
  \end{translation}
\endsong

\beginsong{A Estrela Azul}[by={Baixinha}, key={A}, gk={A, G--B}, tags={2x}]
  \audio{https://www.nossairmandade.com/hymn/1158/AEstrelaAzul}
  \meter{4}{4}
  \transpose{2}
  \mnbeginchorus\memorize
    \[^\mn{G}]Vem \[\bmc\mn{B}]le\[^\mn{D}]van|\[\mnc{G}G]ta\[\bm]n|-do do fun\[\bmc\mn{F#}]do \[^\mn{E}]do |\[\mnc{D}D]mar \[\bm]{} | \e \altchords{\id[1]{(G)}|G | - |D | \e}
    \[^\mn{B}]A Es\[\bmc\mn{E}]tre\[^\mn{D}]la A|\[\mnc{A}Am]zul \[\bm]{} \[^\mn{C}]em seu \meter{2}{4}|\[\mnc{B}D]trono \[^\mn{A}]divi\meter{4}{4}|\[\mnc{G}G]nal \[\bm]{} | \e \altchords{|Am \meter{2}{4}|D \meter{4}{4}|G | \e}
  \mnendchorus
  \notesoff
  \beginchorus
    Lá ^vem, lá |^vem^ | para ^nos cu|^rar ^ | \e \altchords{|G | - |D | \e}
    A Es^trela A|^zul ^ em seu \meter{2}{4}|^trono divi\meter{4}{4}|^nal ^ \up{1}(| \e) \altchords{|Am \meter{2}{4}|D \meter{4}{4}|G \ac(1){| \e}}
  \endchorus
  \mnbeginchorus\noteson
    \ind \[\mn{G}]Ela \meter{2}{4}|\[\mnc{B}G]vem \[\mn{D}]cu\meter{4}{4}|\[\mnc{A}Am]rar \[\bm]{} \[\mn{C}]quem a\meter{2}{4}|\[\mn{B}]cre\[\mn{A}]di\meter{4}{4}|\[\mnc{G}G]tar\[\bm]{} \altchords{\meter{2}{4}|G \meter{4}{4}|Am \meter{2}{4}| - \meter{4}{4}|G}
    \ind A Es\meter{2}{4}|\[\mn{B}]tre\[\mn{D}]la A\meter{4}{4}|\[\mnc{A}Am]zul \[\bm]{} \[\mn{C}]em seu \meter{2}{4}|\[\mnc{B}D]trono \[\mn{A}]divi\meter{4}{4}|\[\mnc{G}G]nal \[\bm]{} \up{2}(| \e) \altchords{\meter{2}{4}| - \meter{4}{4}|Am \meter{2}{4}|D \meter{4}{4}|G \ac(2){| \e}}
  \mnendchorus
  \begin{translation}[EN]
    It comes rising from the depth of the sea
    The Blue Star in its divine throne
    \nextverse
    It comes, it comes to cure us
    The Blue Star in its divine throne
    \nextverse
    It comes to cure those who believe
    The Blue Star in its divine throne
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \transpose g a \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key g \major \time 4/4 \partial 2.
      \repeat volta 4 {
        \mark \markup {"4x"} \bar ".|:"
        g4 \posectionmark "1., 2." b d | g1~ | g8( g) g g fis4 e | d1~ | d4 b8 b8 e4 d
        | a2. c8 c \time 2/4 | b b a a \time 4/4
      } \alternative {
        { | g1~ | g4 }
        { | g2. }
      }
      \repeat volta 2 {
        g8 \sectionmark "3." g \time 2/4 | b4 d \time 4/4 | a2. c8 c \time 2/4 | b4 a \time 4/4 | g2.
        g8 g \time 2/4 | b4 d \time 4/4 | a2. c8 c \time 2/4 | b8 b a a \time 4/4
      } \alternative {
        { | g2. }
        { | g1~ | g4 \dacapo \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Vem le -- van -- | tan -- | _ do do fun -- do do | mar; __ | _
        A Es -- tre -- la~A -- | zul em seu | tro -- no di -- vi --
      } \alternative {
        { | nal. __ | _ }
        { | nal. }
      }
      \set stanza = "3."
      \repeat volta 2 {
        E -- la | vem cu -- | rar quem a -- | cre -- di -- | tar;
        A Es -- | tre -- la~A -- | zul em seu | tro -- no di -- vi --
      } \alternative {
        { | nal. }
        { | nal. __ | _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Lá vem, lá | vem __ | _ _ pa -- ra nos cu -- | rar; __ | _
        A Es -- tre -- la~A -- | zul em seu | tro -- no di -- vi --
      } \alternative {
        { | nal. __ | _ }
        { | nal. }
      }
    }
    theChords = \transpose g a \chordmode {
      \repeat volta 4 {
        s2. | g1 | g | d | d
        | a:m | d2
      } \alternative {
        { | g1 | g4 }
        { | g2. }
      }
      \repeat volta 2 {
        s4 | g2 | a1:m | a2:m | g1 | g2 | a1:m | d2
      } \alternative {
        { | g2. }
        { | g1 | g4 }
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{O Anjo de Deus}[by={Padr. Alfredo}, tags={valsa}, key={Am}, gk={Am, (G\shrp{m})--(Cm)}]
  \audio{https://www.nossairmandade.com/hymn/609/OAnjoDeDeus}
  \newchords{chords_oanjodedeus_a}\newchords{chords_oanjodedeus_b}\newchords{chords_oanjodedeus_c}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_oanjodedeus_a]
    \[^\mn{E}]O |\[\mnc{A}Am]anjo \[^\mn{B}]de |\[^\mn{C}]Deus nos \[^\mn{B}]pro|\[^\mn{A}]te|\[^\mn{E}]ge
    Com |\[\mnc{D}Bm7&5]{seu san}\[^\mn{B}]to |\[\mnc{G#}E]manto \[^\mn{E}]a|\[\mnc{A}Am]zul \up{1}(| \e)
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_oanjodedeus_b]
    \ind \[^\mn{A}]De |\[\mnc{D}Dm]leste a o|este, |\[^\mn{F}]de \[^\mn{D}]nor\[^\mn{F}]te a |\[\mnc{E}Am]sul
    \ind |\[E7]Vi\[^\mn{F}]va a \[^\mn{E}]Es|\[^\mn{D}]tre\[^\mn{C}]la \[^\mn{B}]do a|\[\mnc{A}Am]zul
    \mnendchorus\glueverses\mnbeginchorus\memorize[chords_oanjodedeus_c]
    \ind |\[\mnc{D}Dm]Que faz bri|lhar as Es|\[^\mn{F}]tre\[^\mn{D}]las \[^\mn{F}]do |\[\mnc{E}Am]Céu
    \ind |\[E7]Do \[^\mn{F}]ar\[^\mn{E}]can|\[^\mn{D}]jo \[^\mn{C}]Ra\[^\mn{B}]fa|\[\mnc{A}Am]el \up{2}(| \e)
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_oanjodedeus_a]
    Este |^globo |gira per|fei|to
    Com di|^versas amos|^tragens de |^cor \up{1}(| \e)
    \endchorus\glueverses\beginchorus\replay[chords_oanjodedeus_b]
    \ind |^{É Deus} em |tudo, é o |fruto, é a |^flor
    \ind |^Vida do |meu Cria|^dor
    \endchorus\glueverses\beginchorus\replay[chords_oanjodedeus_c]
    \ind |^Que faz bro|tar com |todo vi|^gor
    \ind |^Vida do |Rei do a|^mor \up{2}(| \e)
  \endchorus
  \begin{translation}[EN]
    The angel of God protects us with his holy blue mantle
    From east to west, from north to south, viva the Blue Star
    Which makes the stars of heaven shine of the Archangel Raphael
    \nextverse
    This globe turns perfectly, with diverse patterns of color
    It's God in everything, it's the fruit, it's the flower; life of my creator
    That causes budding with all vigor; life of the King of love
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 2
      \repeat volta 2 {
        \parenthesize e4 \sectionmark "A" e | a( a) b | c c b | a2. | e4( e) e
        | d d b8( b) | gis4 gis e
      } \alternative {
        { | a2.~ | a4 }
        { | a2 }
      } \break
      \repeat volta 2 {
        \parenthesize a4 \sectionmark "B" | d d d | d( d) d | f d f | e2.
        | e4 f e | d c b
      } \alternative {
        { | a2 }
        { | a2. }
      } \break
      \repeat volta 2 {
        | d4 \posectionmark "C" d d | d4.( d8) d4 | f d f | e2.
        | e4 f e | d c b
      } \alternative {
        { | a2. }
        { | a2.~ | a4 \bar "|." }
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        \skip 1 O | an -- jo de | Deus nos pro -- | te -- | ge; __ _
        Com | seu san -- to __ _ | man -- to a --
      } \alternative {
        { | zul. | _ }
        { | zul. }
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        De | les -- te~a o -- | es -- _ te, | de nor -- te~a | sul;
        | Vi -- va~a Es -- | tre -- la do~a --
      } \alternative {
        { | zul. }
        { | zul. }
      }
      \set stanza = "1.C"
      \repeat volta 2 {
        | Que faz bri -- | lhar as Es -- | tre -- las do | Céu;
        | Do ar -- can -- | jo Ra -- fa --
      } \alternative {
        { | el. }
        { | el. | _ }
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Es -- te | glo -- _ bo | gi -- ra per -- | fei -- | to;
        Com di -- | ver -- sas a -- mos -- | tra -- gens de
      } \alternative {
        { | cor. | _ }
        { | cor. }
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        \skip 1 | É Deus em | tu -- do,~é o | fru -- to,~é a | flor;
        | Vi -- da do | meu Cri -- a --
      } \alternative {
        { | dor. }
        { | dor. }
      }
      \set stanza = "2.C"
      \repeat volta 2 {
        | Que faz bro -- | tar __ _ com | to -- do vi -- | gor;
        | Vi -- da do | Rei do a --
      } \alternative {
        { | mor. }
        { | mor. | _ }
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | a2.:m | a:m | a:m | a:m
        | b:m7.5- | e 
      } \alternative {
        { | a:m | a4:m}
        { | a2:m }
      }
      \repeat volta 2 {
        s4 | d2.:m | d:m | d:m | a:m
        | e:7 | e:7 
      } \alternative {
        { | a2:m }
        { | a2.:m }
      }
      \repeat volta 2 {
        | d2.:m | d:m | d:m | a:m
        | e:7 | e:7
      } \alternative {
        { | a2.:m }
        { | a2.:m | a4:m}
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Viva a Liberdade do Santo Daime}[by={Marco}, off={Chico Corrente}, tags={2x}, key={Am}, gk={Am, G\shrp{}m--Bm}]
  \audio[key=Am]{https://soundcloud.com/unilarva/viva-a-liberdade-do-santo-daime}
  \audio[key=Am]{https://www.youtube.com/watch?v=UA3vqCsrILo}
  \newchords{chords_viva_a_liberdade_a}\newchords{chords_viva_a_liberdade_b}
  \mnbeginchorus\memorize[chords_viva_a_liberdade_a]
    \[^\mn{E}]Olha a |\[\mnc{A}Am]Luz, olha a \[\mnc{G}G]Cruz, \[^\mn{E}]olha a |\[\mncii{C}{B}C]Lu\[\mnc{A}Am]a \altchords{\id[1]{(Bm)}|Bm A |D Bm}
    O\[^\mn{C}]lha \[^\mn{B}]ll|\[^\mn{A}]ê, olha ll\[\bm]ê, olha \[^\mn{C}]ll|\[\mnc{E}\ac(1){E}]ê \[\bm]{} \altchords{|Bm |\ac(1){F\shrp{}}}
  \mnendchorus\glueverses\mnbeginchorus\memorize[chords_viva_a_liberdade_b]
    \[^\mn{A}]Oxa|\[\mnc{D}Dm]lá, Pai Xan\[\bmc\mn{F}]go, Rei \[^\mn{D}]Sa\[^\mn{C}]lo|\[\mnc{A}Am]mâo\[\bm]{} \altchords{|Em |Bm}
    \[^\mn{E}]Firmam a Jus|\[\mnc{B}E7]tica \[^\mn{D}]da Dou\[\bmc\mn{G#}]trina \[^\mn{B}]do Se|\[\mnc{A}Am]nhor\[\bm]{} \altchords{|F\shrp{}7 |Bm}
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_viva_a_liberdade_a]
    Eu dou |^Viva a Liber^dade do Santo |^Dai^me
    Do Pai E|terno e Jesus ^Cristo Reden|^tor ^
  \endchorus\glueverses\beginchorus\replay[chords_viva_a_liberdade_b]
    Se|^guindo ^Mestre Iri|^neu^
    Com leal|^dade, paci^encia e a|^mor^
  \endchorus
  \beginchorus\replay[chords_viva_a_liberdade_a]
    Obri|^gado a to^dos Seres Di|^vi^nos \altchords{\id[4]{MK (Am)}|Am C |Am}
    Por inspi|rar e mos^trar nossa mis|^sâo^ \altchords{| - | \e}
  \endchorus\glueverses\beginchorus\replay[chords_viva_a_liberdade_b]
    A Ra|^inha ela ^nos abenço|^ou ^ \altchords{|Dm |Am}
    Obri|^gado a for^ça que nos cri|^ou ^ \altchords{|E7 |Am}
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 4/4 \partial 4
      \repeat volta 2 {
        e8. \posectionmark "A" e16 | a8.( a16) a8. a16  g8( g16 g16) e8. e16 | \once\slurSolid c4.( b8) a8. a16 c8. b16
        | a8.( a16) a8. a16 a8. a16 a8. c16
      } \alternative {
        { | e2. }
        { | e2. }
      }
      \repeat volta 2 {
        a,8.( \sectionmark "B" a16) | d8.( d16)( d8.) d16 f8. f16 d8. c16 | a2~8 \parenthesize e'8 e8. e16
        | b8. b16 d8. d16 gis,8. gis16 b8. b16 | a2.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \repeat volta 2 {
        O -- lha~a | Luz, __ _ o -- lha~a Cruz, __ _ _ o -- lha~a | Lu -- _ a;
        O -- lha ll -- | ê, o -- lha ll -- ê, o -- lha ll --
      } \alternative {
        { | ê. }
        { | ê. }
      }
      \set stanza = "1.B"
      \repeat volta 2 {
        O -- xa -- | lá, __ _ Pai Xan -- go, Rei Sa -- lo -- | mâo; __ _
        Fir -- mam~a Jus -- | ti -- ca da Dou -- tri -- na do Se -- | nhor.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2.A"
      \repeat volta 2 {
        Eu dou | Vi -- va~a Li -- ber -- da -- de do San -- to | Dai -- _ me;
        Do Pai E -- | ter -- no~e Je -- sus Cris -- to Re -- den --
      } \alternative {
        { | tor. }
        { | tor. }
      }
      \set stanza = "2.B"
      \repeat volta 2 {
        Se -- _ | guin -- _ _ do Mes -- tre I -- ri -- | neu; __ _
        Com le -- al -- | da -- de, pa -- ci -- en -- cia e a -- | mor.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3.A"
      \repeat volta 2 {
        O -- bri -- | ga -- do a to -- dos Se -- _ res Di -- | vi -- _ nos;
        Por ins -- pi -- | rar __ _ e mos -- trar nos -- sa mis --
      } \alternative {
        { | sâo. }
        { | sâo. }
      }
      \set stanza = "3.B"
      \repeat volta 2 {
        A Ra -- | i -- nha e -- la nos a -- ben -- ço -- | ou; __ _
        \skip 1 O -- bri -- | ga -- do a for -- ça que nos cri -- | ou.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | a2:m g2 | c2 a2:m | a1:m
      } \alternative {
        { | \parenthesize e2. }
        { | a2.:m }
      }
      \repeat volta 2 {
        s4 | d1:m | a1:m | e1:7 | a2.:m
      }
    }
    \layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-notab.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Look at the Light, look at the Cross, look at the Moon
    Look at it, look at it, look at it
    Oxalá, Father Xango, King Solomon
    Firm the Justice of the Doctrine of the Lord
    \nextverse
    I give \emph{Viva} to the liberation of Santo Daime
    Of the Eternal Father and Jesus Christ the Redeemer
    Following Master Irineu
    With loyalty, patience and love
    \nextverse
    I thank all the Divine Beings
    For inspiring and showing our mission
    The Queen, she blessed us
    I thank the force that created us
  \end{translation}
\endsong
