% Santo Daime: Cura de São Miguel
% ===============================
%
\audio[title={Nossa Irmandade}]{https://www.nossairmandade.com/hinario/89/ChamadosDoS\%C3\%A3oMiguel}
\audio[]{https://soundcloud.com/andreza-lima-pav-o/sets/flor-do-norte-cura-de-sao}

% The following sets the song number for the first song in this file.
% The number will automatically be incremented by one for each song.
% Please do not change this! Changing would make different versions of
% the songbook to have different numbers for the same songs, and it
% would totally mess up the selection booklets causing them to have
% wrong songs in them. (For the same reason, add new songs only to the
% end of each songs_ file.)
\setcounter{songnum}{1}

\beginsong{Com o Poder do Céu}[by={Padr. Alfredo}, key={Am}, sks={Am, G\shrp{}m--Bm}, tags={valsa, 3x, de pé}]
  \newchords{chords_comopoderdoceu_a}\newchords{chords_comopoderdoceu_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_comopoderdoceu_a]
    |\[\mnc{E}Am]Com o |\[^\mn{C}]po\[^\mn{A}]der \[^\mn{C}]do |\[^\mn{E}]Céu, | \[^\mn{A}]da |\[\mnc{E}A]Ter\[^\mn{C#}]ra \[^\mn{A}]e |\[\mnc{E}A7]tam\[^\mn{C#}]bém \[^\mn{A}]do |\[\mnc{D}Dm]Mar | \e
    \lrep \[^\mn{D}]Or|\[Dm]deno |a \[^\mn{C}]São \[^\mn{B}]Mi|\[\mnc{A}Am]guel, | \[^\mn{E}]a |\[\mnc{B}E7]for\[^\mn{G#}]ça |\[^\mn{C}]Deus é \[^\mn{B}]quem |\[\mnc{A}Am]dá | \e \rrep
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_comopoderdoceu_b]
    \ind \[^\mn{A}]A |\[A]força |\[A7]Deus é quem |\[\mnc{D}Dm]dá, | \[^\mn{F}]pa\[^\mn{G}]ra |\[\mnc{A}F]quem tem |\[\mnc{G}G]conhe\[^\mn{A}]ci|\[\mnc{E}Am]men|to
    \ind Re|\[\mnc{G}C]conhe|\[\mnc{F}Dm]cendo os \[^\mn{E}]pri|\[\mnc{B}E]mo|res, \[^\mn{E}]e |\[\mnc{C}Am]não \[^\mn{A}]tirar |\[\mnc{C}E7]do \[^\mn{B}]pen\[^\mn{C}]sa|\[\mnc{A}Am]men|to
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_comopoderdoceu_a]
    Só |^Deus, só |Deus, só |Deus, | é |^quem pode |^nos segu|^rar | \e
    \lrep Para |^nós ven|cer a ba|^ta|lha, para a|^diante |se alcan|^çar | \e \rrep
  \endchorus\glueverses
  \beginchorus\replay[chords_comopoderdoceu_b]
    \ind Para a|^diante |^se alcan|^çar, | o que |^custa gran|^de sofri|^men|to
    \ind Que |^é a|^mar com fir|^me|za, a |^Deus Pai |^do firma|^men|to
  \endchorus
  \beginchorus\replay[chords_comopoderdoceu_a]
    O |^Deus |do firma|men|to, |^é o |^Sol e a |^Lu|a
    \lrep No firma|^mento es|tá o car|^rei|ro, e o Cru|^zeiro, ca|minhada |^su|a \rrep
  \endchorus\glueverses
  \beginchorus\replay[chords_comopoderdoceu_b]
    \ind A |^conste|^lação che|^gou, | bem jun|^tinho da |^Virgem Ma|^ri|a
    \ind \noteson\[\mnlow{G}]No \[\mnlow{G}]Cru\notesoff{}|^zeiro es|^{tá o} Ro|^sá|rio, dos pe|^didos |^em ago|^ni|a
  \endchorus
  \beginchorus\replay[chords_comopoderdoceu_a]
    A |^força quem |tem é o |Rei, | Jesus |^Cristo, o |^Mestre de |^sem|pre
    \lrep Tudo |^no cora|ção de Ma|^ri|a, na |^Terra e em to|do firma|^men|to \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 2
      \repeat volta 2 {
        r4 \parenthesize a4 \posectionmark "(1, 3, 5, 7).A" | e'4( e4)( e4) | c( a) c | e2.( | e4)( e4) \parenthesize a4
        | e4 \parenthesize cis a' | e cis a | d2.( | d4)
          \altcol\grace d8 \altmark "5." \parenthesize d4 \sectionmark "B:i" d4 | d4( d4) d4 | d c b | a2.( | a4) \parenthesize e'4
          e4 | b8( b8)( b4) gis4 | c c b | a2.( | a4)
          \altcol\grace d8 \altmark "5." \parenthesize d4 \sectionmark "B:ii" d4 | d4( d4) d4 | d c b | a2.( | a4) \parenthesize e'4
          e4 | b8( b8)( b4) gis4 | c c b | a2.( | a4)
        }
      \repeat volta 2 {
        \parenthesize a4 \sectionmark "2., 4., 6." a4 | a2 a4 | a a a | d2.~ | d4 f g | a4( a4) a4 | g g a | e2. | \once\slurDown e4( << e4) \single\altcol g4 \altmark "6." >> << e4 \single\altcol g4 >>
        | g4( g4) g4 | f f e | b2. | b4( b4) e4 | c( a) a | c b c | a2. | a4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \skip 1 | Com __ _ o | po -- der do | Céu, __ | _ _
      da | Ter -- ra e | tam -- bém do | Mar. __ | _
        \set stanza = "1.B"
        \skip 1 Or -- | de -- _ no | a São Mi -- | guel, __ | _
        \skip 1 a | for -- _ _ ça | Deus é quem | dá. __ | _
        \skip 1 Or -- | de -- _ no | a São Mi -- | guel, __ | _
        \skip 1 a | for -- _ _ ça | Deus é quem | dá. __ | _
      \set stanza = "2."
      \skip 1 A | for -- ça | Deus é quem | dá, __ | _
      pa -- ra | quem __ _ tem | co -- nhe -- ci -- | men -- | to; __ _
      Re -- | co -- _ nhe -- | cen -- do~os pri -- | mo -- | res, __ _
      e | não ti -- rar | do pen -- sa -- | men -- | to.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "3.A"
      Só | Deus, __ _ só | Deus, __ _ só | Deus, __ | _ _
      é | quem po -- de | nos se -- gu -- | rar. __ | _
        \set stanza = "3.B"
        Pa -- ra | nós __ _ ven -- | cer a ba -- | ta -- | lha,
        pa -- ra~a -- | dian -- _ _ te | se al -- can -- | çar. __ | _
        Pa -- ra | nós __ _ ven -- | cer a ba -- | ta -- | lha,
        pa -- ra~a -- | dian -- _ _ te | se al -- can -- | çar. __ | _       
      \set stanza = "4."
      Pa -- ra~a -- | dian -- te | se al -- can -- | çar, __ | _
      o que | cus -- ta gran -- | de so -- fri -- | men -- | to; __ _
      Que | é __ _ a -- | mar com fir -- | me -- | za, __ _
      a | Deus __ _ Pai | do fir -- ma -- | men -- | to.
    }
    theLyricsThree = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "5.A"
      O | Deus __ _ _ | do fir -- ma -- | men -- | to, __ _
      \skip 1 | é \skip 1 o | Sol e a | Lu -- | a.
        \set stanza = "5.B"
        \altcol No fir -- ma -- | men -- to es -- | tá o car -- | rei -- | ro,
        e~o Cru -- | zei -- _ ro, ca -- | mi -- nha -- da | su -- | a.
        \altcol No fir -- ma -- | men -- to es -- | tá o car -- | rei -- | ro,
        e~o Cru -- | zei -- _ ro, ca -- | mi -- nha -- da | su -- | a.
      \set stanza = "6."
      \skip 1 A | cons -- te -- | la -- ção che -- | gou, __ | _
      bem jun -- | ti -- nho da | Vir -- gem Ma -- | ri -- | a;
      \altcol No \altcol Cru -- | zei -- ro es -- | tá o ro -- | sá -- | rio,
      dos pe -- | di -- _ dos | em a -- go -- | ni -- | a.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "7.A"
      A | for -- ça quem | tem é o | Rei __ | _
      Je -- sus | Cris -- to, o | Mes -- tre de | sem -- | pre.
        \set stanza = "7.B"
        Tu -- do | no co -- ra -- | ção de Ma -- | ri -- | a
        \skip 1 Na | Ter -- ra~e em to -- | do fir -- ma -- | men -- | to.
        Tu -- do | no co -- ra -- | ção de Ma -- | ri -- | a
        \skip 1 Na | Ter -- ra~e em to -- | do fir -- ma -- | men -- | \once\override LyricText.color = #darkgreen to.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | a2.:m | a:m | a:m | a:m
        | a | a:7 | d:m | d2:m
          % part B
          s4 | d2.:m | d:m | a:m | a:m
          | e:7 | e:7 | a:m | a2:m
          s4 | d2.:m | d:m | a:m | a:m
          | e:7 | e:7 | a:m | a4:m
      }
      \repeat volta 2 {
        s2 | a2. | a:7 | d:m | d:m
        | f | g | a:m | a:m
        | c | d:m | e | e
        | a:m | e:7 | a:m | a4:m
      }
    }
    \layout { #(layout-set-staff-size 13) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    With the power of heaven, of Earth and the Sea
    I order Saint Michael, the strength is given by God
    \ind The strength is given by God, for those who have understanding
    \ind Recognizing the splendors, and not forgetting them
    \nextverse
    Only God, only God, only God, is who can secure us
    For us to overcome the battle, to be able to attain afterwards
    \ind To be able to attain afterwards, which costs great suffering
    \ind That is to love with firmness, The Father God of the Firmament
    \nextverse
    The Father God of the Firmament, is the Sun and the Moon
    In the firmament is the trail, and the Cross is His path
    \ind The constellation arriver, very close to the Virgin Mary
    \ind On the Cross is the Rosary, of the prayers in agony
    \nextverse
    The King has the force, Jesus Christ, the Master of all time
    Everything in the heart of Mary, on the Earth, and in the whole Firmament
  \end{translation}
\endsong


\beginsong{A Chave da Justiça}[by={Alex Polari}, key={C}, sks={C, G--B}, tags={2x}]
  % Also in: songs_astral_unilaiva_tios_queridos.tex
  \audio{https://www.nossairmandade.com/hymn/989/AChaveDaJusti\%C3\%A7a}
  \audio{https://soundcloud.com/canaljagube/107_a-chave-da-justica}
  \mnbeginchorus\memorize
    |\[\mnc{C}C]Ei\[^\mn{G}]a, vem a\[\bm]qui \[^\mn{F}]no |\[\mnc{A}F]mei\[^\mn{F}]o, vem a\[\bm]qui \[^\mn{E}]com o |\[\mnc{G}G]re\[^\mn{D}]lho \altchords{\id{(B)}|B |E |F\shrp{}}
    Eia eu \[\bmc\mn{F}]vou \[^\mn{E}]che|\[\mnc{C}C]gar,\[\bm] |viva São Mi\[\bmc\mn{F}]guel \[^\mn{E}]que |\[^\mn{C}]veio \altchords{|B | - | \e}
    Veio a\[\bmc\mn{F}]brir \[^\mn{E}]a |\[\mnc{G}G7]ban\[^\mn{D}]ca lá dos \[\bm]O\[^\mn{C}]ri|\[\mnc{E}C]xás\[\bm] \altchords{|F\shrp{}7 |B}
  \mnendchorus
  \notesoff
  \beginchorus\replay
    |^Eia, São Mi^guel que |^veio com ba^laça e es|^pada
    Veio ^pra avi|^sar^ que |Jesus Cristo ^é o |dono
    Aqui des^se ter|^reiro, e é pra ^se entre|^gar^
  \endchorus
  \beginchorus\replay
    |^Eia, São Mi^guel que |^veio balan^çando a |^tropa
    Veio ^domi|^nar,^ |peia pra quem ^é re|belde
    O fis^cal que |^veio, foi pa^ra apu|^rar^
  \endchorus
  \beginchorus\replay
    |^Salve o meu ^Mestre Im|^pério, que nes^se Cru|^zeiro
    Bem fir^mado es|^tá,^ |deu para São ^João na |terra
    A chave ^da jus|^tiça no Santo ^Daime es|\noteson\[C \up{2}\mnlow{C}]tá. \[\bm]
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    theMelody =  \relative c''' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4
      \repeat volta 2 {
        c8 \pomark g8 g8 g8 g4 f4 | a8 f8 f8 f8 f4 e4
        | g8 d8 d8 d8 f4 e4 | c2~ c4. \parenthesize \altcol c8 \altmark "2."
        | c8 c8 c8 c8 f4 e4 | c8 c8 c8 c8 f4 e4
        | g8 d16 ( d16) d8 d8 d4 c4 | << e1 \parenthesize c1 \genmark "(4.:ii)" >>
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        | Ei -- a, vem a -- qui no | mei -- o,
        vem a -- qui com~o | re -- lho;
        Eia eu vou che -- | gar, __ _
        \skip 1 | vi -- va São Mi -- guel que | vei -- o;
        Vei -- o~a -- brir a | ban -- ca __ _
        lá dos O -- ri -- | xás.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        | Ei -- a, São Mi -- guel que | vei -- o
        com ba -- la -- ça~e~es -- | pa -- da;
        Vei -- o pra~a -- vi -- | sar __ _
        \altcol que | Je -- sus Cris -- to é o | do -- no;~A
        qui des -- se ter -- | rei -- ro, e
        é pra se~en -- tre -- | gar.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        | Ei -- a, São Mi -- guel que | vei -- o
        ba -- lan -- çan -- do~a | tro -- pa;
        Vei -- o do -- mi -- | nar, __ _ \skip 1
        | pei -- a pra quem é re -- | bel -- de;
        O fis -- cal que | vei -- o, __ _
        foi pa -- ra~a -- pu -- | rar.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        | Sal -- ve o meu Mes -- tre~Im -- | pé -- rio,
        que nes -- se Cru -- | zei -- ro;
        Bem fir -- ma -- do~es -- | tá, __ _ \skip 1
        | deu pa -- ra São João na | ter -- ra;~A
        cha -- ve da jus -- | ti -- ça no
        San -- to Dai -- me~es -- | \parenthesize tá.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        c1 | f
        | g | c
        | c | c
        | g:7 | c
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}
    Eia come here in the middle, come here with the whip
    Eia, I will arrive, viva Saint Michael who came
    Came to open the banca of the Orixás
    \nextverse
    Eia Saint Michael who came with the scale and the sword
    Came to advise that Jesus Christ is the owner
    Here in this terreiro, and that it is for us to surrender
    \nextverse
    Eia São Michael who came rocking the army
    He comes to dominate, consequences for those who are rebellious
    The guardian who came, came to purify
    \nextverse
    Salve, Oh! My Imperial Master, That this Cross
    Is well firmed here, gave to Saint John on Earth
    The key of Justice is here in the Santo Daime
  \end{translation}
\endsong


\beginsong{Mensageiro do Anjo Azul}[by={Maria Alice}, key={C}, sks={D, C--D}, tags={mazurka}]
  \meter{6}{4}
  \mnbeginchorus
    \[\mn{C}]Sou Men\[\mn{E}]sa|\[\mnc{G}C]geiro do \[\mn{A}]Anjo A\[\bmc\mn{G}]zul
    Foi \[\mn{A}]São Mi|\[\mnc{G}G7]guel \[\mn{E}]quem \[\mn{F}]me \[\mn{D}]man\[\mnc{C}C]dou
    \mnendchorus\glueverses\mnbeginchorus
    \[\mn{C}]Eu venho a|\[\mnc{G}C]qui \[\mn{C}]para do\[\mnc{E}Am]mar
    \[\mn{G}]A ca|\[\mn{E}]beça \[\mn{G}]do dra\[\mnc{C}C]gão
  \mnendchorus
  \mnbeginverse
    \[\mn{C}]Aqui \[\mn{E}]na |\[\mnc{G}C]terra
    Ve\[\mn{A}]nho fa\[\mnc{G}G7]zer \[\mn{E}]a \[\mn{F}]li\[\mn{D}]ga|\[\mnc{C}C]ção
    \[\mn{C}]Aqui \[\mn{E}]na \[\bmc\mn{G}]terra
    Ve\[\mn{A}]nho fa|\[\mnc{G}G7]zer \[\mn{E}]a \[\mn{F}]li\[\mn{D}]ga\[\mnc{C}C]ção
    \mnendverse\glueverses\mnbeginchorus
    \[\mn{C}]Ma|\[\mnc{G}C]mãe \[\mn{C}]Ieman\[\mnc{E}Am]já
    \[\mn{G}]O|\[\mn{E}]gum da \[\mn{G}]Beira-\[\mnc{C}C]Mar
  \endchorus
  \begin{translation}
    I am the messenger of the Blue Angel, Saint Michael is who commands me
    I come here to tame the head of the dragon
    \nextverse
    Here on Earth I come to make a connection
    Mother Iemanjá, Ogum of the Sea-Shore
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 6/4 \partial 4.
      \repeat volta 2 {
        c8 \posectionmark "1.A" c e | g4 g8 g8 a8 a8  g4. g8 a8 a8
        | g4. e8 f8 d8  c4.
      }
      \repeat volta 2 {
        c8 \sectionmark "1.B" c8 c8 | g4. c8 c8 c8  e2 g,8 g8
        | e'4. e8 g,8 g8  c4.
      }
      % Section 2.A is 3/4 shorter than 1.A, thus filling the mazurka
      % bars only after two repeats -- that's why it's written unfolded
      c8 \sectionmark "2.A:i" c e | g4 g8 g8 a8 a8  g4. e8 f8 d8 | c4.
      c8 \sectionmark "ii" c e g4 g8 g8 a8 a8 | g4. e8 f8 d8 c4.
      \repeat volta 2 {
        r8 \sectionmark "2.B" c4 | g4. c8 c8 c8  e2 g,4
        | e'4. e8 g,8 g8  c4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
        Sou Men -- sa -- | gei -- ro do An -- jo~A -- zul;
        Foi São Mi -- | guel quem me man -- dou.
      \set stanza = "1.B"
        Eu ve -- nho~a -- | qui pa -- ra do -- mar;
        A ca -- | be -- ça do dra -- gão.
      \set stanza = "2.A"
        A -- qui na | ter -- ra;
        Ve -- nho fa -- zer a li -- ga -- | ção.
        A -- qui na ter -- ra;
        Ve -- nho fa -- | zer a li -- ga -- ção.
      \set stanza = "2.B"
        Ma -- | mãe I -- e -- man -- já;
        O -- | gum da Bei -- ra-Mar.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c1. | g2.:7  c4.
      }
      \repeat volta 2 {
        s4. | c2.  a2.:m | a2.:m  c4.
      }
      s4. | c2.  g2.:7 | c4.
      s4.  c2. | g2.:7  c4.
      \repeat volta 2 {
        s4. | c2.  a2.:m | a2.:m  c4.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{São Miguel}[by={Lúcio Mortimer}, key={C}, sks={D, C--E}]
  \audio{https://www.nossairmandade.com/hymn/1424/S\%C3\%A3oMiguel}
  \mnbeginchorus\memorize
    \[^\mn{G}]Eu pe|\[\mnc{C}C]di para esta \[(Am)]Luz \[^\mn{A}]me \[^\mn{B}]cla\[^\mn{C}]re|\[\mnc{D}Dm]ar \[\bm] \altchords{\id[1]{(D)}|D (Bm) |Em}
    Eu \[^\mn{E}]pe|\[\mnc{F}F]di que eu tives\[(Dm)]se \[^\mn{D}]es\[^\mn{E}]te \[^\mn{F}]a|\[\mnc{G}G]mor \[\bm] \altchords{|G (Em) |A}
    Eu pe|di para ter \[(G7)]for\[^\mn{F}]ça \[^\mn{E}]de a\[^\mn{D}]ju|\[\mnc{C}C]dar \[\bm] \altchords{| - (A7) |D}
    \[^\mn{G}]Aos es|\[G]píritos neste \[(G7)]mundo \[^\mn{A}]so\[^\mn{B}]fre|\[\mnc{C}C]dor \[\bm] \altchords{|A (A7) |D}
  \mnendchorus
  \notesoff
  \beginchorus
    Rece|^bi de meu Je^{sus esta} mis|^são ^
    Fazer es|^forço de aju^{dar o} preci|^sa^do
    Rogando à |Deus com fé ^{e convic}|^ção ^
    Para o pe|^di do po^der ser escu|^ta^do
  \endchorus
  \beginchorus
    Vou se|^guindo firme e ^forte a jor|^na^da
    Estou fir|^mado com este ^meu sagrado |^vi^nho
    Rogando |sempre defen^{der destas} ci|^la^das
    Que o ini|^migo apre^senta no ca|^mi^nho
  \endchorus
  \beginchorus
    Com São Mi|^guel, meu Ar^canjo Prote|^tor ^
    Eu tenho |^força de pas^{sar em} toda |^pro^va
    Vou confi|ando, pois es^tou com meu Se|^nhor ^
    Que ao vence|^dor prome^teu a vida |^no^va
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4.
      \repeat volta 2 {
        \parenthesize g8 \genmark "(4.)" \pomark g8 g8 | c8 c16( c16) c8 c c a b c | d2( \parenthesize d8)( \parenthesize d8) d8 e8
        | f8 f16( f16) f8 f8 f8 d e f | g2( \parenthesize g8 \parenthesize g8) g8 g8
        | g8( g) g g g f e d | c2( \parenthesize c8) \parenthesize g8 g g
        | g16( \parenthesize g16)( \parenthesize g16)( \parenthesize g16) g8 g8 g8 g8 a b | c2( c8)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 Eu pe -- | di pa -- ra es -- ta Luz me cla -- re -- | ar; __ _ _
        Eu pe -- | di que eu ti -- ves -- se es -- te a -- | mor; __ _ _
        Eu pe -- | di pa -- ra ter for -- ça de~a -- ju -- | dar; __ _
        \skip 1 Aos es -- | pí -- ri -- tos __ _ nes -- te mun -- do so -- fre -- | dor. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        \skip 1 Re -- ce -- | bi de __ _ meu Je -- sus es -- ta mis -- | são; __ _
        Fa -- zer es -- | for -- ço __ _ de~a -- ju -- dar o pre -- ci -- | sa -- do;
        Ro -- gan -- do~à | Deus __ _ com fé e con -- vi -- c -- | ção; __ _
        Pa -- ra~o pe -- | di -- _ _ _ do po -- der ser es -- cu -- | ta -- do.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        \skip 1 Vou se -- | guin -- do __ _ fir -- me~e for -- te a jor -- | na -- da;
        Es -- tou fir -- | ma -- do com es -- te meu sa -- gra -- do | vi -- nho;
        Ro -- gan -- do | sem -- pre de -- fen -- der des -- tas ci -- | la -- das;
        Que~o i -- ni -- | mi -- _ _ go a -- pre -- sen -- ta no ca -- | mi -- nho.
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Com São Mi -- | guel, __ _ _ meu Ar -- can -- jo Pro -- te -- | tor; __ _
        Eu te -- nho | for -- ça __ _ de pas -- sar em to -- da | pro -- va;
        Vou con -- fi -- | an -- do, pois es -- tou com meu Se -- | nhor; __ _
        Que~ao ven -- ce -- | dor __ _ _ _ pro -- me -- teu a vi -- da | no -- va.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4. | c2 \parenthesize a:m | d1:m | f2 \parenthesize d:m | g1
        | g2 \parenthesize g:7 | c1 | g2 \parenthesize g:7 | c2~8
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
  \translationoff
  \begin{translation}
    I ask for this light to get me clear, I ask that I will have this love
    I ask to have strength to help the spirits suffering in this world
    \nextverse
    I receive from Jesus this mission, to have strength to help those who need it
    Praying to God with faith and conviction, for this request to be able to be heard
    \nextverse
    I will follow firmly with strength on this journey, I am firm with my sacred wine
    Praying always to defend these ambushes that the enemy presents on the road
    \nextverse
    With Saint Michael my protector Archangel I have strength to pass through all the test
    I go trusting therefore I am with my Lord, to the winner He promised the new life
  \end{translation}
\endsong


\beginsong{Força do Céu}[by={Dalvina Corrente}, key={C}, sks={D, C--D}]
  \audio{https://www.nossairmandade.com/hymn/1969/For\%C3\%A7aDoC\%C3\%A9u}
  \mnbeginchorus\memorize
    \[^\mn{G}]Pe|\[\mnc{C}C]di força do \[\bm]céu, da flo|\[^\mn{E}]resta \[^\mn{D}]e do \[\mnc{C}(C7)]mar \altchords{\id[1]{(D)}|D | - (D7)}
    Pe|\[\mnc{F}F]di aos meus Ar\[\bm]canjos para |\[\mnc{A}(Am)]{vir e} \[^\mn{G}]aju\[\mnc{F}F]dar \altchords{|G |(Bm) G}
    \[^\mn{G}]Pe|\[G]di a São Mi\[\bm]guel para |\[^\mn{E}]me a\[^\mn{D}]benço\[\mnc{C}C]ar \altchords{|A | - D}
    \[^\mn{G}]Lim|\[^\mn{C}]par a minha es\[\bm]trada \[^\mn{G}]para eu |\[\mnc{E}G]poder \[^\mn{D}]cami\[\mnc{C}C]nhar \altchords{| - |A D}
  \mnendchorus
  \notesoff
  \beginchorus
    Pe|^di a Santa Es^trela para |me ilumi^nar
    Pe|^di meu Papai ^Velho, São Jo|^{sé de Ar}riba^mar
    Pe|^di a Virgem ^Mãe para |me purifi^car
    Eu |pedi um con^forto a minha |^Mãe Ieman^já
  \endchorus
  \begin{translation}
    I ask the force of heaven, of the forest and the sea
    I ask my Archangels to come and help me
    I ask Sain Michael in order to bless me
    Clean my path so that I can walk
    \nextverse
    I ask the Holy Star in order to illuminate me
    I ask my Papai Velho, São Jose de Arribamar
    I ask the Virgin Mother in order to purify me
    I ask for the comfort of my mother Iemanjá
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative g' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 8
      \repeat volta 2 {
        g8 \pomark | c c c c c( c) c c | e e d d c4. c8
        | f f f f f8. f16 f8 f | a8( a16) a16 g8 g f4. g8
        | g g g g g4 g8 g | e e d d c4. g8
        | c c c c c c g g | e'8( e16)( e16) d8 d c4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Pe -- | di for -- ça do céu, __ _
        da flo -- | res -- ta e do mar;
        Pe -- | di aos meus Ar -- can -- jos
        pa -- ra | vir __ _ e a -- ju -- dar;
        Pe -- | di a São Mi -- guel
        pa -- ra | me a -- ben -- ço -- ar;
        Lim -- | par a mi -- nha~es -- tra -- da
        pa -- ra~eu | po -- der __ _ ca -- mi -- nhar.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        Pe -- | di a San -- ta~Es -- tre -- la
        pa -- ra | me i -- lu -- mi -- nar;
        Pe -- | di meu Pa -- pai Ve -- lho,
        São Jo -- | sé de Ar -- ri -- ba -- mar;
        Pe -- | di a Vir -- gem Mãe
        pa -- ra | me pu -- ri -- fi -- car;
        Eu | pe -- di um con -- for -- to~a
        mi -- nha | Mãe __ _ I -- e -- man -- já.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | c1 | c2 \parenthesize c:7 | f1 | \parenthesize a2:m f | g1 | g2 c | c1 | g2 c4.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong


\beginsong{Sou Comando de Maria}[by={Padr. Corrente}, key={D}, sks={D, D--E}]
  \audio{https://www.nossairmandade.com/hymn/1222/S\%C3\%A3oMiguel}
  \mnbeginchorus\memorize
    \[^\mn{A}]Sou co|\[\mnc{D}D]man\[^\mn{A}]do \[^\mn{D}]de \[^\mn{F#}]Ma\[\bmc\mn{A}]ri\[^\mn{F#}]a \altchords{\id[1]{(E)}|E}
    \[^\mn{D}]Prote|tor de \[^\mn{A}]São \[^\mn{E}]Jo\[\bmc\mn{D}]sé \altchords{| -}
    \[^\mn{A}]O meu |\[\mnc{G}G]nome é \[^\mn{B}]São \[\mnc{D}D]Miguel \altchords{|A E}
    \[^\mn{A}]Ar|\[A]canjo de \[^\mn{C#}]Na\[^\mn{E}]za\[\mnc{D}D]ré \altchords{|B E}
  \mnendchorus
  \notesoff
  \beginchorus
    Ando, |^ando no es^paço
    Junto |com meu São Jo^ão
    Estou |^dentro desta ^guerra
    Com o Pa|^drinho Sebasti^ão
  \endchorus
  \beginchorus
    Pise |^firme, pise ^firme
    No ca|minho de Je^sus
    Vôo |^junto com vo^cês
    Vou ze|^lando esta ^Luz
  \endchorus
  \begin{translation}
    I am the command of Mary, protector of Saint Joseph
    My name is Saint Michael, Archangel of Nazareth
    \nextverse
    I walk, I walk within the space, together with Saint John
    I am within this war, with Pardrinho Sebastião
    \nextverse
    Step firmly, step firmly, on the path of Jesus
    I fly together with you, I watch over this light
  \end{translation}
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key d \major \time 4/4 \partial 8
      \repeat volta 2 {
        a16 a16 | d8 a d fis a fis4 d16 d16 | d8 d a e' d4 \parenthesize a8 a8
        | g8 g b d d8( d4) a16( a16) | a8 a16( a16) cis8 e d4.
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        Sou co -- | man -- do de Ma -- ri -- a;
        Pro -- te -- | tor de São Jo -- sé;
        O meu | no -- me~é São Mi -- guel; __ _
        Ar -- _ | can -- jo de Na -- za -- ré.
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        An -- do, | an -- do no es -- pa -- ço;
        Jun -- to | com meu São Jo -- ão;
        Es -- tou | den -- tro des -- ta guer -- ra;
        Com~o Pa -- | dri -- nho Se -- bas -- ti -- ão.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        Pi -- se | fir -- me, pi -- se fir -- me;
        No ca -- | mi -- nho de Je -- sus;
        \skip 1 Vôo | jun -- to com vo -- cês; __ _
        Vou ze -- | lan -- do __ _ es -- ta Luz.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s8 | d1 | d1 | g2 d2 | a2 d4.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail-lyricsbelow.ly"
  \end{lilypond}\end{lilywrap}
\endsong
