% Santo Daime: Cura de São Miguel, Abertura dos portões celestiais
% ================================================================
%

{ % Put everything in this file in a block to not bleed settings

% use Roman numerals for song (prayer) numbering:
\renewcommand{\thesongnum}{\Roman{songnum}}
\setcounter{songnum}{1}

\scleardpage
\beginsong{Sol, Lua, Estrela}[by={Mestre Irineu Serra}, key={C}, gk={C, (B)--(C)}, tags={perfilado, 3x}]
  \audio{https://www.nossairmandade.com/hymn/219/Sol,Lua,Estrela}
  \mnbeginchorus\memorize
    |\[\mnc{E}C]Sol, \[\bm]Lua, \[^\mn{D}]Es|\[^\mn{E}]tre\[\bmc\mn{C}]la \altchords{\id[1]{(A) \capo{3}}|A | \e}
    \[^\mn{E}]A |\[\mnc{G}G]Ter\[^\mn{A}]ra o \[\bmc\mn{G}]Ven\[^\mn{A}]to e o |\[\mncii{G}{F}C]Mar\[\bmc\mn{E}] \altchords{|E |A}
    \ilsl{\[^\mn{G}]É} a |\[\mnc{C}F]Luz \[^\mn{B}]do \[\bmc\mn{A}]Fir\[^\mn{G}]ma|\[\mnc{E}C]men\[^\mn{G}]to \[\bm]{} \altchords{|D |A}
    É \[^\mn{E}]só |\[\mnc{G}G]quem \[^\mn{C}]eu \[\bmc\mn{E}]de\[^\mn{G}]vo a|\[\mnc{C}C]mar \[\bm]{} \altchords{|E |A}
  \mnendchorus
  \notesoff
  \beginchorus
    É só |^quem eu ^devo a|mar ^
    Trago |^sempre ^na lem|^bran^ça
    É |^Deus que es^tá no |^Céu ^
    Aonde es|^tá minha ^espe|^ran^ça
  \endchorus
  \beginchorus
    A |^Virgem ^Mãe man|dou ^
    Para |^mim es^ta li|^ção ^
    Me lem|^brar de ^Jesus |^Cristo^
    E esque|^cer a ^ilu|^são ^
  \endchorus
  \beginchorus
    Tri|^lhar es^te ca|mi^nho
    Toda |^hora e ^todo |^di^a
    O Di|^vino es^tá no |^Céu ^
    Jesus |^filho ^de Ma|^ri^a
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-12
    theMelody = \relative e'' {
      \set melismaBusyProperties = #'() \slurDashed
      \key c \major \time 4/4 \partial 4
      \repeat volta 2 {
        \parenthesize e8 \pomark \parenthesize e | e4( e4) e4 \once\slurDown << \parenthesize \single\altcol e8 \altmark "(1.)" d8( >> d) | e2( c4) e8( e) | g4 a g a | g4.( f8 e4)
        g8( g) | c4 b a g | e( g4.) \parenthesize g8 \genmark "(2., 3.)"g8 e | g,4 c8( c) e4 g | c,2( c4)
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1."
      \repeat volta 2 {
        \skip 1 \skip 1 | Sol, __ _ Lu -- a, Es -- | tre -- la;
        A __ _ | Ter -- ra~o Ven -- to~e~o | Mar; __ _ _
        É a | Luz do Fir -- ma -- | men -- to;
        \skip 1 É só | quem eu __ _ de -- vo~a | mar. __ _
      }
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "2."
      \repeat volta 2 {
        É só | quem eu de -- vo a -- | mar; __ _
        Tra -- go | sem -- pre na lem -- | bran -- _ ça;
        É __ _ | Deus que~es -- tá no | Céu; __ _
        A -- on -- de~es -- | tá mi -- nha es -- pe -- | ran -- ça.
      }
    }
    theLyricsThree = \lyricmode {
      \set stanza = "3."
      \repeat volta 2 {
        A __ _ | Vir -- gem Mãe man -- _ | dou; __ _
        Pa -- ra | mim es -- ta li -- | ção; __ _ _
        Me lem -- | brar de Je -- sus | Cris -- to;
        E es -- que -- | cer a __ _ i -- lu -- | são. __ _
      }
    }
    theLyricsFour = \lyricmode {
      \set stanza = "4."
      \repeat volta 2 {
        Tri -- _ | lhar es -- te ca -- _ | mi -- nho;
        To -- da | ho -- ra~e to -- do | di -- _ a;
        O Di -- | vi -- no~es -- tá no | Céu; __ _
        \skip 1 Je -- sus | fi -- lho __ _ de Ma -- | ri -- a.
      }
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s4 | c1 | c | g | c | f | c | g | c2.
      }
    }
    %\layout { #(layout-set-staff-size 15) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \begin{translation}[EN]
    Sun, Moon, Star, the Earth, the Wind and the Sea
    It's the light of the firmament, it's only this that I must love
    \nextverse
    It's only this that I must love, I always carry it in my memory
    It's God who is in heaven where my hope is
    \nextverse
    The Virgin Mother sent this lesson for me
    To remember Jesus Christ, and to forget the illusion
    \nextverse
    To tread this path, every hour and every day
    The Divine is in heaven, Jesus, Son of Mary
  \end{translation}
\endsong


\beginsong{Prece para o Começo da Reunião}[by={Allan Kardec}]
  \begin{passage}[PT]{}
    \passagenote*{Antes que esta oração seja recitada o Consagração do Aposento}
    Ao Senhor Deus Todo-poderoso pedimos que envie bons
    espíritos para nos assistirem, que afaste os que
    puderem induzir-nos ao erro, e que nos dê a luz de
    que precisamos para distinguir a verdade da impostura.
    \par
    Afastai de nós também, Senhor, os espíritos malévolos,
    encarnados ou descarnados, que tentem lançar a
    desunião entre nós e, bem assim, desviar-nos da
    caridade e do amor do próximo. Se alguns procurarem
    introduzir-se aqui, fazei Senhor, que não achem acesso
    em nossos corações.
    \par
    Bons espíritos que vos dignais vir instruir-nos, tornai-
    nos dóceis aos vossos conselhos, isentai-nos de qualquer
    pensamento de egoísmo, de orgulho, de inveja e de ciúme;
    inspirai-nos indulgência e benevolência para com os
    nossos semelhantes, presentes ou ausentes, amigos ou
    inimigos; fazei, enfim, que pelos sentimentos que nos
    animam, reconheçamos a vossa salutar influência.
    \par
    Dai aos médiuns que encarregardes de nos transmitir os
    vossos ensinamentos, consciência da santidade do mandato
    que lhes é confiado e da gravidade do ato que vão
    desempenhar, a fim de que o pratiquem com o fervor e o
    recolhimento necessários.
    \par
    Se entre nós se encontrarem pessoas dominadas por
    sentimentos que não sejam do bem, abri-lhes os olhos à
    luz e perdoai-lhes como lhe perdoamos, se por ventura
    trazem malévolas intenções.
    \par
    Pedimos especialmente a nosso guia espiritual, São João
    Batista, que nos assista e por nós vele.
  \end{passage}
  \begin{passage}[EN]{Prayer for the Beginning of the Meeting}
    \passagenote*{Before this prayer, recite the Consecration of the Space}
    We implore You, oh God, the All Powerful, to send us
    the good spirits to help us and keep away any spirits
    that may lead us into error. Give us the necessary light
    to distinguish truth from falsehood.
    \par
    Keep away wicked spirits, whether incarnate or
    discarnate, that might try to cause dissension among us
    and turn us away from charity and the love of our
    neighbors. If any such spirits try to disturb our
    meeting, don't let them have access to our hearts.
    \par
    Good spirits, who see fit to come and teach us, make us
    yielding to your direction. Turn us away from all
    selfish, proud, jealous, and envious thoughts. Inspire
    in us tolerance and goodwill toward our fellow human
    beings, present or absent, friend or enemy. Finally
    help us to acknowledge your uplifting presence in the
    feelings that hearten our souls.
    \par
    God, give the mediums who have been charged with the
    responsibility of transmitting higher teachings an
    awareness of their high commission. Give them a sense
    of the seriousness of their task so that they can
    undertake it with the necessary fervor and
    introspection.
    \par
    If, at our meeting, there are individuals motivated by
    feelings other than goodwill, open their eyes to the
    light and forgive them --- as we forgive them --- for
    any malevolent disposition they may display
    \par
    We ask especially that the spirit of Saint John the
    Baptist, our spiritual guide, help and watch over us.
  \end{passage}
\endsong

\scleardpage
\beginsong{Prece para os Médiuns}[by={Allan Kardec}]
  \begin{passage}[PT]{}
    Deus Onipotente, permiti que os bons espíritos me
    assistam na comunicação que solicito. Preservai-me da
    presunção de me acreditar ao abrigo dos maus espíritos;
    do orgulho que poderia induzir-me ao erro acerca do
    valor que obtenho; de todo sentimento contrário
    caridade para com os outros médiuns.
    \par
    Se for lavado ao erro, inspirai a alguém o pensamento
    de advertir-me, e dai-me hulmildade para receber, chei
    de reconhecimento, a crítica que me façam, para tomar
    por dados a mim mesmo, e não aos outros, os conselhos
    que os bons espíritos hajam por bem ditar-me.
    \par
    Se me vir tentado a abusar, seja no que for, ou me
    envaidecer da faculdade que vos aprouve conceder-me,
    eu vos peço que ma retireis antes que consistais se
    afaste ela do seu fim providencial, que é o bem de
    todos e o meu próprio adiantamento moral.
  \end{passage}
  \begin{passage}[EN]{Prayer for the Mediums}
    Almighty God, let the good spirits come and help me
    with the requested communication. Keep me from
    presuming that I am immune to the influence of wrong-
    doing spirits; to pride, which can lead me to
    misinterpret the value of what I receiveM and to any
    feelings of uncharitableness toward other mediums.
    \par
    If I make mistakes, inspire someone to alert me to
    this fact, and give me the humility to accept the
    deserved criticism. May I also realize that the
    advice the good spirits give through me is not only
    directed to others but also me.
    \par
    If I am tempted in any way to abuse, in any form,
    the gift bestowed on me by Your grace, or if I become
    proud of it, I ask that You take it back rather than
    let it stray from its providential objective, which
    is the good of all and my own moral advancement.
  \end{passage}
\endsong


\scleardpage
\beginsong{Com o Poder do Céu}[by={Padr. Alfredo}, key={Am}, gk={Am, G\shrp{}m--Bm}, tags={perfilado, valsa, 3x}]
  \newchords{chords_comopoderdoceu_a}\newchords{chords_comopoderdoceu_b}
  \meter{3}{4}
  \mnbeginchorus\memorize[chords_comopoderdoceu_a]
    |\[\mnc{E}Am]Com o |\[^\mn{C}]po\[^\mn{A}]der \[^\mn{C}]do |\[^\mn{E}]Céu, | \[^\mn{A}]da |\[\mnc{E}A]Ter\[^\mn{C#}]ra \[^\mn{A}]e |\[\mnc{E}A7]tam\[^\mn{C#}]bém \[^\mn{A}]do |\[\mnc{D}Dm]Mar | \e
    \lrep \[^\mn{D}]Or|\[Dm]deno |a \[^\mn{C}]São \[^\mn{B}]Mi|\[\mnc{A}Am]guel, | \[^\mn{E}]a |\[\mnc{B}E7]for\[^\mn{G#}]ça |\[^\mn{C}]Deus é \[^\mn{B}]quem |\[\mnc{A}Am]dá | \e \rrep
  \mnendchorus\glueverses
  \mnbeginchorus\memorize[chords_comopoderdoceu_b]
    \ind \[^\mn{A}]A |\[A]força |\[A7]Deus é quem |\[\mnc{D}Dm]dá, | \[^\mn{F}]pa\[^\mn{G}]ra |\[\mnc{A}F]quem tem |\[\mnc{G}G]conhe\[^\mn{A}]ci|\[\mnc{E}Am]men|to
    \ind Re|\[\mnc{G}C]conhe|\[\mnc{F}Dm]cendo os \[^\mn{E}]pri|\[\mnc{B}E]mo|res, \[^\mn{E}]e |\[\mnc{C}Am]não \[^\mn{A}]tirar |\[\mnc{C}E7]do \[^\mn{B}]pen\[^\mn{C}]sa|\[\mnc{A}Am]men|to
  \mnendchorus
  \notesoff
  \beginchorus\replay[chords_comopoderdoceu_a]
    Só |^Deus, só |Deus, só |Deus, | é |^quem pode |^nos segu|^rar | \e
    \lrep Para |^nós ven|cer a ba|^ta|lha, para a|^diante |se alcan|^çar | \e \rrep
  \endchorus\glueverses
  \beginchorus\replay[chords_comopoderdoceu_b]
    \ind Para a|^diante |^se alcan|^çar, | o que |^custa gran|^de sofri|^men|to
    \ind Que |^é a|^mar com fir|^me|za, a |^Deus Pai |^do firma|^men|to
  \endchorus
  \beginchorus\replay[chords_comopoderdoceu_a]
    O |^Deus |do firma|men|to, |^é o |^Sol e a |^Lu|a
    \lrep No firma|^mento es|tá o car|^rei|ro, e o Cru|^zeiro, ca|minhada |^su|a \rrep
  \endchorus\glueverses
  \beginchorus\replay[chords_comopoderdoceu_b]
    \ind A |^conste|^lação che|^gou, | bem jun|^tinho da |^Virgem Ma|^ri|a
    \ind \noteson\[\mnd{G}]No \[\mnd{G}]Cru\notesoff{}|^zeiro es|^{tá o} Ro|^sá|rio, dos pe|^didos |^em ago|^ni|a
  \endchorus
  \beginchorus\replay[chords_comopoderdoceu_a]
    A |^força quem |tem é o |Rei, | Jesus |^Cristo, o |^Mestre de |^sem|pre
    \lrep Tudo |^no cora|ção de Ma|^ri|a, na |^Terra e em to|do firma|^men|to \rrep
  \endchorus
  \begin{lilywrap}\begin{lilypond}[] \include "tex/lp-include-head.ly"
    % transcribed by larva, updated on 2022-11
    theMelody = \relative a' {
      \set melismaBusyProperties = #'() \slurDashed
      \key a \minor \time 3/4 \partial 2
      \repeat volta 2 {
        r4 \parenthesize a4 \posectionmark "(1, 3, 5, 7).A" | e'4( e4)( e4) | c( a) c | e2.( | e4)( e4) \parenthesize a4
        | e4 \parenthesize cis a' | e cis a | d2.( | d4)
          \altcol\grace d8 \altmark "5." \parenthesize d4 \sectionmark "B:i" d4 | d4( d4) d4 | d c b | a2.( | a4) \parenthesize e'4
          e4 | b8( b8)( b4) gis4 | c c b | a2.( | a4)
          \altcol\grace d8 \altmark "5." \parenthesize d4 \sectionmark "B:ii" d4 | d4( d4) d4 | d c b | a2.( | a4) \parenthesize e'4
          e4 | b8( b8)( b4) gis4 | c c b | a2.( | a4)
        }
      \repeat volta 2 {
        \parenthesize a4 \sectionmark "2., 4., 6." a4 | a2 a4 | a a a | d2.~ | d4 f g | a4( a4) a4 | g g a | e2. | \once\slurDown e4( << e4) \single\altcol g4 \altmark "6." >> << e4 \single\altcol g4 >>
        | g4( g4) g4 | f f e | b2. | b4( b4) e4 | c( a) a | c b c | a2. | a4
      }
    }
    theLyricsOne = \lyricmode {
      \set stanza = "1.A"
      \skip 1 | Com __ _ o | po -- der do | Céu, __ | _ _
      da | Ter -- ra e | tam -- bém do | Mar. __ | _
        \set stanza = "1.B"
        \skip 1 Or -- | de -- _ no | a São Mi -- | guel, __ | _
        \skip 1 a | for -- _ _ ça | Deus é quem | dá. __ | _
        \skip 1 Or -- | de -- _ no | a São Mi -- | guel, __ | _
        \skip 1 a | for -- _ _ ça | Deus é quem | dá. __ | _
      \set stanza = "2."
      \skip 1 A | for -- ça | Deus é quem | dá, __ | _
      pa -- ra | quem __ _ tem | co -- nhe -- ci -- | men -- | to; __ _
      Re -- | co -- _ nhe -- | cen -- do~os pri -- | mo -- | res, __ _
      e | não ti -- rar | do pen -- sa -- | men -- | to.
    }
    theLyricsTwo = \lyricmode {
      \set stanza = "3.A"
      Só | Deus, __ _ só | Deus, __ _ só | Deus, __ | _ _
      é | quem po -- de | nos se -- gu -- | rar. __ | _
        \set stanza = "3.B"
        Pa -- ra | nós __ _ ven -- | cer a ba -- | ta -- | lha,
        pa -- ra~a -- | dian -- _ _ te | se al -- can -- | çar. __ | _
        Pa -- ra | nós __ _ ven -- | cer a ba -- | ta -- | lha,
        pa -- ra~a -- | dian -- _ _ te | se al -- can -- | çar. __ | _
      \set stanza = "4."
      Pa -- ra~a -- | dian -- te | se al -- can -- | çar, __ | _
      o que | cus -- ta gran -- | de so -- fri -- | men -- | to; __ _
      Que | é __ _ a -- | mar com fir -- | me -- | za, __ _
      a | Deus __ _ Pai | do fir -- ma -- | men -- | to.
    }
    theLyricsThree = \lyricmode {
      \set includeGraceNotes = ##t
      \set stanza = "5.A"
      O | Deus __ _ _ | do fir -- ma -- | men -- | to, __ _
      \skip 1 | é \skip 1 o | Sol e a | Lu -- | a.
        \set stanza = "5.B"
        \altcol No fir -- ma -- | men -- to es -- | tá o car -- | rei -- | ro,
        e~o Cru -- | zei -- _ ro, ca -- | mi -- nha -- da | su -- | a.
        \altcol No fir -- ma -- | men -- to es -- | tá o car -- | rei -- | ro,
        e~o Cru -- | zei -- _ ro, ca -- | mi -- nha -- da | su -- | a.
      \set stanza = "6."
      \skip 1 A | cons -- te -- | la -- ção che -- | gou, __ | _
      bem jun -- | ti -- nho da | Vir -- gem Ma -- | ri -- | a;
      \altcol No \altcol Cru -- | zei -- ro es -- | tá o ro -- | sá -- | rio,
      dos pe -- | di -- _ dos | em a -- go -- | ni -- | a.
    }
    theLyricsFour = \lyricmode {
      \set stanza = "7.A"
      A | for -- ça quem | tem é o | Rei __ | _
      Je -- sus | Cris -- to, o | Mes -- tre de | sem -- | pre.
        \set stanza = "7.B"
        Tu -- do | no co -- ra -- | ção de Ma -- | ri -- | a
        \skip 1 Na | Ter -- ra~e em to -- | do fir -- ma -- | men -- | to.
        Tu -- do | no co -- ra -- | ção de Ma -- | ri -- | a
        \skip 1 Na | Ter -- ra~e em to -- | do fir -- ma -- | men -- | \once\override LyricText.color = #darkgreen to.
    }
    theChords = \chordmode {
      \repeat volta 2 {
        s2 | a2.:m | a:m | a:m | a:m
        | a | a:7 | d:m | d2:m
          % part B
          s4 | d2.:m | d:m | a:m | a:m
          | e:7 | e:7 | a:m | a2:m
          s4 | d2.:m | d:m | a:m | a:m
          | e:7 | e:7 | a:m | a4:m
      }
      \repeat volta 2 {
        s2 | a2. | a:7 | d:m | d:m
        | f | g | a:m | a:m
        | c | d:m | e | e
        | a:m | e:7 | a:m | a4:m
      }
    }
    \layout { #(layout-set-staff-size 12) } % for better fit
    \include "tex/lp-include-tail.ly"
  \end{lilypond}\end{lilywrap}
  \ifshowlilypond\translationoff\fi % to fit whole song on one spread
  \begin{translation}[EN]
    With the power of heaven, of Earth and the Sea
    I order Saint Michael, the strength is given by God
    \ind The strength is given by God, for those who have understanding
    \ind Recognizing the splendors, and not forgetting them
    \nextverse
    Only God, only God, only God, is who can secure us
    For us to overcome the battle, to be able to attain afterwards
    \ind To be able to attain afterwards, which costs great suffering
    \ind That is to love with firmness, The Father God of the Firmament
    \nextverse
    The Father God of the Firmament, is the Sun and the Moon
    In the firmament is the trail, and the Cross is His path
    \ind The constellation arriver, very close to the Virgin Mary
    \ind On the Cross is the Rosary, of the prayers in agony
    \nextverse
    The King has the force, Jesus Christ, the Master of all time
    Everything in the heart of Mary, on the Earth, and in the whole Firmament
  \end{translation}
\endsong


\scleardpage
\beginsong{Prece para afastar os maus espîritos}[by={Allan Kardec}]
  \begin{passage}[PT]{}
    ``Ai de vós, escribas e fariseus hipócritas, que
    limpais por fora o copo e o prato, conservando-se
    por dentro, cheio de rapinas e de impurezas.
    Fariseus cegos, limpai primairamente o interior do
    copo e do prato a fim de que pelo interior também
    fiquem limpos.
    \par
    Ai de vós escribas e fariseus hipócritas, que vos
    assemelhais a sepulcros caiados, mas cheios por
    dentro, de toda sorte de podridões. Assim, por fora
    pareceis justos aos olhos dos homens, mas, por
    dentro, estais cheios de hipocrisia e indignidades.''
    \textit{(Mateus, cap. 23, vers. 25 á 28.)}
    \par
    Os maus espíritos vão onde acham meio de satisfazer
    a sua perversidade. Para os afastarmos não basta que
    lhes peçamos, nem mesmo lhes ordenemos que se retirem.
    É necessário que nos expurguemos daquilo que os atrai.
    Os maus espíritos farejam as chagas da alma, qual o
    fazem as moscas com as do corpo. Assim como se limpa
    o corpo para evitar a bicheira, também se deve limpar
    a alma de suas impurezas a para evitar os maus
    espíritos. Como vivemos no mundo onde eles pululam,
    nem sempre as boas qualidades de coração nos põem ao
    abrigo das suas tentativas; mas nos dão, forças para
    lhes resistir.
    \par
    \vspace{1ex}
    \textbf{PRECE}
    \par
    Que em nome de Deus Onipotente se afastem de mim os
    maus espíritos e que os bons me sirvam de escudo contra
    eles.
    \par
    Espíritos malfazejos, que aos homens inspirai maus
    pensamentos, espíritos zombeteiros que mofais da
    credulidade deles, eu vos repilo com todas as forças
    de minha alma e fecho os ouvidos às vossas sugestões,
    mas suplico para vós a misericórdia de Deus.
    \par
    Bons espíritos que vos dignais de me assistir, dai-me
    forças para resistir à influência dos maus espíritos
    e as luzes necessários para não ser vítima de seus
    embustes.
    \par
    Preservai-me do orgulho e da presunção; isentai o meu
    coração do ciúme, do ódio, da malevolência, e de
    qualquer sentimento contrário à caridade, que são
    outras tantas portas abertas ao espírito do mal.
  \end{passage}
  \begin{passage}[EN]{Prayer to Remove Wrong-doing Spirits}
    ``Woe unto you, scribes and Pharisees, hypocrites, for
    you clean the outside of the cup and dish, but you
    remain on the inside, full of plunders and impurities.
    Blind Pharisees, clean first the inside of the cup and
    dish, so that on the inside you may also be clean.
    \par
    Woe unto you, scribes and Pharisees, hypocrites, for
    you are like tombs that are whitewashed but full, on
    the inside, of all kinds of rottenness. In the same way,
    on the outside, you appear to people as righteous, but
    on the inside, you are full of hypocrisy and wickedness.''
    \textit{(Matthew, chapter 23, verses 25--28.)}
    \par
    Wrong-doing spirits can only be found where they have a
    chance to satisfy their desires. To keep them at bay, it
    isn't enough simply to ask them to go away or even to
    order them to go. It's essential first that we eliminate
    from ourselves whatever in us is attracting them. Wrong-
    doing spirits discover the ulcers of the soul in the same
    way flies discover wounds on the body. So, just as you
    wash your wounds in order to avoid maggots, clean your
    soul of its impurities in order to avoid bad spirits.
    We live in a world that teems with these spirits, and the
    good qualities of our hearts aren't always enough to stop
    their attempts on us. Nevertheless, these qualities give
    us strength in resisting them.
    \par
    \vspace{1ex}
    \textbf{PRAYER}
    \par
    In the name of Almighty God, may the wrong-doing spirits
    stay away from me and the good spirits protect me from
    their influence.
    \par
    Wicked spirits, that inspire bad thoughts, deceiving and
    lying spirits that delude the unwary, mocking spirits that
    delude the naive, I repel you with all the strength in my
    soul and close my ears to your suggestions. And I pray also
    that God have mercy on you.
    \par
    Good spirits that undertook to guide me, give me the
    strength I need to resist the influence of lower spirits
    and the discernment not to become a victim of their
    designs.
    \par
    Keep me safe from pride and presumption. Turn my heart
    away from all thoughts of jealousy, hate, badness, and any
    feelings opposed to charity, since these are all open doors
    to wrong-doing spirits.
  \end{passage}
\endsong


}
